### 2018-01-04 write_up/mixfishsim_ecolmod.tex
Starting write up

\documentclass[review]{elsarticle}

\usepackage{lineno,hyperref}
\modulolinenumbers[5]

\journal{Ecological Modelling}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}
%% Numbered without titles
%\bibliographystyle{model1a-num-names}
%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}
%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}
%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}
%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{A mixed fishery simulation framework}

%% Group authors per affiliation:
\author[1,2]{Paul J. Dolder\corref{c}}
\cortext[c]{Corresponding author}
\ead{paul.dolder@gmit.ie}

\author[1]{Coilin Minto}

\address[1]{Galway-Mayo Institute of Technology (GMIT), Dublin Road, Galway,
	Ireland} 
\address[2]{Centre for Environment, Fisheries and Aquaculture Science (Cefas),
	Pakefield Road, Lowestoft, UK}

\begin{abstract}
A concise and factual abstract is required. The abstract should state briefly
the purpose of the research, the principal results and major conclusions. An
abstract is often presented separately from the article, so it must be able to
stand alone. For this reason, References should be avoided, but if essential,
then cite the author(s) and year(s). Also, non-standard or uncommon
abbreviations should be avoided, but if essential they must be defined at their
first mention in the abstract itself.  
Graphical abstract: Although a graphical abstract is optional, its use is
encouraged as it draws more attention to the online article. The graphical
abstract should summarize the contents of the article in a concise, pictorial
form designed to capture the attention of a wide readership. Graphical
abstracts should be submitted as a separate file in the online submission
system. Image size: Please provide an image with a minimum of 531 × 1328 pixels
(h × w) or proportionally more. The image should be readable at a size of 5 x
13 cm using a regular screen resolution of 96 dpi.  Preferred file types: TIFF,
EPS, PDF or MS Office files.
\end{abstract}

\begin{keyword}
Some\sep keywords \sep here. Max 6, American "spelling" 
\MSC[2010] 00-01\sep  99-00
\end{keyword}

\end{frontmatter}

\linenumbers

\section{Introduction}

State the objectives of the work and provide an adequate background, avoiding a
detailed literature survey or a summary of the results.

\subsection{Can subsection like this}

\section{Materials and Methods}
Provide sufficient details to allow the work to be reproduced by an independent
researcher. Methods that are already published should be summarized, and
indicated by a reference.  If quoting directly from a previously published
method, use quotation marks and also cite the source. Any modifications to
existing methods should also be described.

\section{Theory/calculation}

A Theory section should extend, not repeat, the background to the article
already dealt with in the Introduction and lay the foundation for further work.
In contrast, a Calculation section represents a practical development from a
theoretical basis.

\section{Results}

Results should be clear and concise.

\section{Discussion}

This should explore the significance of the results of the work, not repeat
them. A combined Results
and Discussion section is often appropriate. Avoid extensive citations and
discussion of published
literature.

\section{Conclusions}

The main conclusions of the study may be presented in a short Conclusions
section, which may stand
alone or form a subsection of a Discussion or Results and Discussion section.

\section*{Appendices}

If there is more than one appendix, they should be identified as A, B, etc.
Formulae and equations in appendices should be given separate numbering: Eq.
(A.1), Eq. (A.2), etc.; in a subsequent appendix, Eq. (B.1) and so on.
Similarly for tables and figures: Table A.1; Fig. A.1, etc.

\section*{Abbreviations} Detail any unusual ones used.

\section*{Acknowledgements} those providing help during the research..

\section*{Funding} This work was supported by the MARES doctoral training
program; and the Centre for Environment, Fisheries and Aquaculture Science
seedcorn program.

\section*{References}

\bibliography{mybibfile}

\end{document}

### 2018-01-04 R/go_fish.R

@@ -19,7 +19,7 @@
 #' @export
 
 go_fish <- function(sim_init = NULL, fleet_params = NULL, fleet_catches = NULL, 
-		    sp_fleet_catches = NULL,pops = NULL, t = t) {
+		    sp_fleet_catches = NULL, pops = NULL, t = t) {
 
 ##### extract the relevant components ###########
 params <- fleet_params      # fleet parameter list
@@ -52,9 +52,10 @@ coords <- c(catch[t-1, "x"], catch[t-1,"y"]) # Previous coordinates
 
 # If incorporating past knowledge, and its a new trip...and not in the
 	# first year
-	if(is.null(PastKnowledge) & catch[t,"trip"] != catch[t-1,"trip"] & brk.idx[["year.breaks"]][t]>1)  {
+	if(!is.null(PastKnowledge) & catch[t,"trip"] != catch[t-1,"trip"] & brk.idx[["year.breaks"]][t]>1)  {
 
 print("USING PAST KNOWLEDGE!!!")
+#browser()
 	catch.df  <- as.data.frame(catch) # Needed for correct sub-setting
 
 	# 3 options, choose from good hauls i) same month last year, ii) past
@@ -69,8 +70,8 @@ print("USING PAST KNOWLEDGE!!!")
 	# Option 1 - same month (current and) previous years
 	if(params[["past_year_month"]] == TRUE & params[["past_trip"]] != TRUE) {
 	
-	q <- quantile(filter(catch.df,month==brk.idx[["month.breaks"]][t])$val,prob=c(params[["threshold"]]),na.rm=T) # Threshold for good hauls
-	goodhauls  <- filter(catch.df,month==brk.idx[["month.breaks"]][t] & val>=q)
+	q <- quantile(dplyr::filter(catch.df,month==brk.idx[["month.breaks"]][t])$val,prob=c(params[["threshold"]]),na.rm=T) # Threshold for good hauls
+	goodhauls  <- dplyr::filter(catch.df,month==brk.idx[["month.breaks"]][t] & val>=q)
 	goodhauls  <- goodhauls[complete.cases(goodhauls),] # Remove NAs
 	new.point   <- sample(paste(goodhauls$x,goodhauls$y,sep=","),1)  	# Randomly select from the good hauls
[…]

### 2018-01-09 write_up/mixfishsim_ecolmod.tex
Manuscript updates

@@
 \usepackage{lineno,hyperref}
+\usepackage[utf8]{inputenc}
+\usepackage{graphicx}
+\usepackage{amsfonts}
+\usepackage{mathtools}
+\usepackage{tikz}
+\usetikzlibrary{shapes,arrows,chains,calc}
+
+% Set up a few colours for tikz figure
+\colorlet{lcfree}{green}
+\colorlet{lcnorm}{blue}
+\colorlet{lccong}{red}
+
 \modulolinenumbers[5]
@@
 
-\title{A mixed fishery simulation framework}
+\title{A simulation framework for exploring spatio-temporal dynamics in mixed
+	fisheries}
 
@@
 
-\author[1]{Coilin Minto}
+\author[1]{Cóilín Minto}
+\author[3]{Jean-Marc Guarini}
+\author[4]{Jan-Jaap Poos}
 
@@
 	Pakefield Road, Lowestoft, UK}
+\address[3]{UPMC}
+\address[4]{Wageningen Marine}
 
 \begin{abstract}
-A concise and factual abstract is required. The abstract should state briefly
+[A concise and factual abstract is required. The abstract should state briefly
 the purpose of the research, the principal results and major conclusions. An
@@
 abstracts should be submitted as a separate file in the online submission
-system. Image size: Please provide an image with a minimum of 531 × 1328 pixels
-(h × w) or proportionally more. The image should be readable at a size of 5 x
+system. Image size: Please provide an image with a minimum of 531 X 1328 pixels
+(h X w) or proportionally more. The image should be readable at a size of 5 x
 13 cm using a regular screen resolution of 96 dpi.  Preferred file types: TIFF,
-EPS, PDF or MS Office files.
+EPS, PDF or MS Office files.]
 \end{abstract}
@@
 
-State the objectives of the work and provide an adequate background, avoiding a
-detailed literature survey or a summary of the results.
+Fishers exploit fish populations that are heterogenously distributed without
+prior knowledge of species distributions and non-selective fishing gear.
+Fisheries are managed by single-species quotas, leading to discarding of
+overquota catch. Increasing interest in technical solutions such as gear,
+spatial closures as a way of managing "fisheries" instead of fish stocks. \\
 
-\subsection{Can subsection like this}
+Provide some examples here of where this is the case..focus on spatial
+management and the increasing sophistication / resolution of data dervied from
+VMS and logbooks; refs: Geritsen et al, Mateo et al. \\
+
+Use of spatial management as a tool is hampered by lack of knowledge of fish
+and fishery spatiotemporal dyanmics and the scale at which processes are
+important for management. Need to understand these to implement effective
+management measures for species avoidance / targeting. Use Dunn et al as a
+ref.\\
+
+We develop a simulation model where underlying population dynamics are known
+rather than inferred from sampling or commercial catches. It includes
+population movement and a number of different fisheries exploiting four fish
+populations with different demographics.\\
+
+Using the model, we simulation 20 years of exploitation of the fish populations
+and use the results to draw inference on the underlying population structures -
+as done in species modelling approaches. \\
+
+We simulate a fishery closure to protect one species based on the
+fishery-dependent inferred distributions at a spatial and temporal scale
+typical in fisheries management, and assess a theoretical "benefit" to the
+population, and effect on the other three populations. Further, we extend our
+analysis to a range of spatial and temporal scales to assess the impact of
+these processes on the success of the management measure. \\
+
+[State the objectives of the work and provide an adequate background, avoiding a
+detailed literature survey or a summary of the results.]
 
 \section{Materials and Methods}
-Provide sufficient details to allow the work to be reproduced by an independent
+
+[Provide sufficient details to allow the work to be reproduced by an independent
 researcher. Methods that are already published should be summarized, and
@@
 method, use quotation marks and also cite the source. Any modifications to
-existing methods should also be described.
+existing methods should also be described.]
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Overview schematic  
+\begin{figure}[!ht]
+\begin{tikzpicture}[%
+    >=triangle 60,              % Nice arrows; your taste may be different
+    start chain=going below,    % General flow is top-to-bottom
+    node distance=8mm and 60mm, % Global setup of box spacing
+    every join/.style={norm}   % Default linetype for connecting boxes
+    ]                 
+    \label{fig:model}
+    % ------------------------------------------------- 
+% A few box styles 
+% <on chain> *and* <on grid> reduce the need for manual relative
+% positioning of nodes
+\tikzset{
+  base/.style={draw, on chain, on grid, align=center, minimum height=4ex},
+  proc/.style={base, rectangle, text width=8em},
+  test/.style={base, rectangle, text width=5em},
+  term/.style={proc, rounded corners},
+  % coord node style is used for placing corners of connecting lines
+  coord/.style={coordinate, on chain, on grid, node distance=6mm and 25mm},
+  % nmark node style is used for coordinate debugging marks
+  nmark/.style={draw, cyan, circle, font={\sffamily\bfseries}},
+  % -------------------------------------------------
+  % Connector line styles for different parts of the diagram
+  norm/.style={->, draw, lcnorm},
+  free/.style={->, draw, lcfree},
+  cong/.style={->, draw, lccong},
+  it/.style={font={\small\itshape}}
+}
+% -------------------------------------------------
+% Start by placing the nodes in the middle
+\node [proc, densely dotted, it] (p0) {start};
+% Use join to connect a node to the previous one 
+\node [term, join, fill=lcnorm!25]      {Choose random location to fish};
+\node [term, join, fill=lcfree!25] (p1){Sample catch};
+\node [test, densely dotted] (t1) {if $y > y-1$};
+\node [test, join, densely dotted] (t2) {if $spp_{t}$ != $spp_{t-1}$};
+\node [test, join, densely dotted] (wk) {if $week_{t}$ != $week_{t-1}$};
+\node [test, join, densely dotted] (t3) {if $trip_{t}$ != $trip_{t-1}$};
+\node [term, join, fill=lcnorm!25]  (p2) {Correlated Random Walk};
+\node [term, join, fill=lcnorm!25]  (p3) {Choose new fishing location};
+\node [proc, densely dotted, join, it] (p7) {end};
+
+% Right nodes
+\node [proc, fill=lcfree!25, right=of p1] (p4) {Popn depletion};
+\node [proc, fill=lcfree!25, right=of t1] (p5) {Popn Recruitment};
+\node [proc, fill=lcfree!25] (p6) {Popn movement};
+\node [proc, fill=lcfree!25, right=of wk] (wk1) {Growth and natural
+	mortality};
+
+% left nodes
+\node [test, fill=lcnorm!25, left=of t3] (t4) {Use past fishing locations};
+
+% -------------------------------------------------
+% A couple of boxes have annotations
+\node [below=of p0, it, yshift=1.5em,xshift=-3em] {$t==1$};
+\node [right=30mm of p3, it] {$1 < t < t_{max}$};
+\node [below=of p3, it,xshift=-3em, yshift=1.5em] {$t == t_{max}$};
+
+% -------------------------------------------------
+% First, the straight north-south connections. In each case, we first
+% draw a path with a (consistently positioned) annotation node, then
+% we draw the arrow itself.
+  \draw [*->,lcfree!50] (p1) -- (p4);
+\path (t1) to node [near start, xshift=2em, yshift=0.5em] {$y$} (p5); 
+  \draw [*->,lcfree!50] (t1) -- (p5);
+\path (t2) to node [near start, xshift=2em, yshift=0.5em] {$y$} (p6); 
+  \draw [*->,lcfree!50] (t2) -- (p6);
+\path (t3) to node [near start, xshift=-3em, yshift=0.5em] {$y$} (t4); 
+  \draw [*->,lccong!50] (t3) -- (t4);
+\path (wk) to node [near start, xshift=2em, yshift=0.5em] {$y$} (wk1); 
+  \draw [*->,lcfree!50] (wk) -- (wk1);
+
+% left to right paths
+\path (t1) to node [near start, yshift=-0.2em] {$n$} (t2) ;  
+\path (t2) to node [near start, yshift=0.8em] {$n$} (t3) ;  
+\path (wk) to node [near start, yshift=-0.2em] {$n$} (t3) ;  
+\path (t3) to node [near start, yshift=-0.3em] {$n$} (p2) ;
+
+% ------------------------------------------------- 
+% the twisty connectors. Again, we place the annotation
+% first, then draw the connector
+
+\node [coord, left=of p3] (c1)  {};  
+\draw [*->,lccong!50] (t4.south) -- (c1) |- (p3);
+
+\node[coord, below=of p4] (c2) {};
+\node[coord, above=of t1] (c3) {};
+\draw [-<,lcfree!50] (p4.south) -- (c2) |- (c3) |- (t1.north);
+
+\node[coord, below=of p5] (c4) {};
+\draw [->,lcfree!50] (p5.south) -- (c4) |- ($(t2.east) + (0,0.5)$);
+
+\node[coord, below=of p6] (c71) {};
+\draw [->,lcfree!50] (p6.south) -- (c71) |- ($(wk.east) + (0,0.56)$);
+
+\node[coord, below=of wk1] (c7) {};
+\draw [->,lcfree!50] (wk1.south) -- (c7) |- ($(t3.east) + (0,0.3)$);
+
+% -------------------------------------------------
+% A last flourish which breaks all the rules
+\draw [->,purple, dotted, thick, shorten >=1mm]
+  (p3.south) -- ++(5mm,-3mm)  -- ++(87mm,0mm) 
+  |- node [black, near end, yshift=1.75em, it]
+    {} ($(p1.north) + (0,0.3)$);
+% -------------------------------------------------
+\end{tikzpicture}
+\caption{Overview Schematic of simulation model}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Population dynamics}
+
+The basic population level processes are simulated using a modified two-stage
+Deriso-Schnute delay difference model \cite{Deriso1980, Schnute1985}
+occurring at the weekly time-step \cite{Dichmont2003}. Here, population
+biomass growth and depletion for pre-recruits and fish recruited to the fishery
+are modelled separately as a function of previous recruited biomass, intrinsic
+population growth and recruitment:
+
+\begin{equation*}
+	\begin{split}
+	B_{y,w+1} = &\\
+	& (1 + \rho) B_{y,w} \cdot e^{-Z_{y,w}} - \rho \cdot e^{-Z_{y,w}} \hspace{2.9cm}
+	\times \\  
+	& (B_{y,w-1} \cdot e^{-Z_{y,w-1}} + Wt_{R-1} \cdot \alpha_{w-1} \cdot R_{\tilde{y}(y,w-1)})
+	\hspace{0.4cm} + \\
+	& Wt_{R} \cdot \alpha_{w} \cdot R_{\tilde{y}(y,w)} 
+	\end{split}
+\end{equation*}
+
+$\rho$ is Brody's coefficient, shown to be approximately equal to $exp(-K)$,
+where $K$ is the growth rate from a von bertalanffy logistic growth model
+\cite{Schnute1985}.  $Wt_{R-1}$ is the weight of fish prior to recruitment,
+while $Wt_{R}$ is the recruited weight.  $\alpha_{w}$ represents the proportion of
+fish recruited during the week, while $R_{\tilde{y}}$ is the annual
+recruits. \\
+
+Mortality $Z$ can be decomposed to natural mortality, $M$, and fishing
+mortality, $F$, where both $M$ and $F$ are instantaneous rates with $M$ fixed
+and $F$ calculated by solving the Baranov catch equation \cite{Hilborn1992b}
+for $F$:
+
+\begin{equation*}
+C_{w} = \frac{F_{w}}{F_{w}+M_{w}} * (1 - e^{-(F_{w} + M_{w})}) * B
+\end{equation*}
+
+where $C$ is the summed catch from the fishing model across all fleets and
+vessels for the species, year and week respectively, and $B$ the weekly biomass
+for the species. \\
+
+\subsection{Recruitment dynamics}
+
+Recruitment is modelled through a function relating the biomass at time of
+recruitment to recruits, either as a stochastic Beverton-Holt stock-recruit
+form (\cite{Beverton1957}):
+
+\begin{equation*}
+	\begin{split}
+	\bar{R} = & \frac{(\alpha * B)}{(\beta + B)} \\
+	     R \sim & N[(\bar{R},\sigma^2)]
+	\end{split}
+\end{equation*}
+
+Where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock biomass (SSB)
+required to produce half the maximum, and $B$ current SSB; \\
+
+or a stochastic Ricker form \cite{Ricker1954}
+
+\begin{equation*}
+	\begin{split}
+	\bar{R} = & B * e^{(\alpha - \beta * B)} \\	
+   	     R \sim & N[(\bar{R},\sigma^2)]
+	\end{split}
+\end{equation*}
+
+where $\alpha$ is the maximum productivity per spawner and $\beta$ the density dependent
+reduction in productivity as the SSB increases.
+
+\subsection{Population movement}
+
+\subsection{Fleet dynamics}
 
@@
 
-A Theory section should extend, not repeat, the background to the article
+[A Theory section should extend, not repeat, the background to the article
 already dealt with in the Introduction and lay the foundation for further work.
 In contrast, a Calculation section represents a practical development from a
-theoretical basis.
+theoretical basis.]
+
+HERE DESCRIBE THE PARAMETERISATION, AND ANY COMPARISON AGAINST 'REAL' DATA
 
@@
 
-Results should be clear and concise.
+Present simulated closures in terms of \% change in population biomass and
+fishery.
+
+[Results should be clear and concise.]
 
@@
 
-\bibliography{mybibfile}
+\bibliography{simulation_framework}
 

### 2018-01-09 R/run_sim.R

@@ -235,6 +235,9 @@ spat_fs <- find_spat_f_pops(sim_init = sim_init, C = spp_catches, B = B,
 ## Fishing mortality rates
 print(sapply(names(spat_fs), function(x) weighted.mean(spat_fs[[x]], B[[x]])))
 
+## Or the summed values (fraction fished of pop)
+print(sapply(names(spp_catches), function(x) { sum(spp_catches[[x]]) / sum(B[[x]])}))
+
 # Apply the delay difference model
 Bp1 <- foreach(x = paste0("spp", seq_len(n_spp))) %dopar% {
 

### 2018-01-19 write_up/mixfishsim_ecolmod.tex
Updated manuscript outline and added timer to sim

@@
 %% Harvard
-%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
+%%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
 %% Vancouver numbered
@@
 %% APA style
-%\bibliographystyle{model5-names}\biboptions{authoryear}
+%%\bibliographystyle{model5-names}\biboptions{authoryear}
 %% AMA style
@@
 	Pakefield Road, Lowestoft, UK}
-\address[3]{UPMC}
-\address[4]{Wageningen Marine}
+\address[3]{Université Pierre et Marie Curie, 4 Place Jussieu, 75005 Paris,
+	France}
+\address[4]{Wageningen Marine Research, Haringkade 1 1976 CP IJmuiden,
+	Netherlands}
 
@@
 the purpose of the research, the principal results and major conclusions. An
-abstract is often presented separately from the article, so it must be able to
+abstract is often pnresented separately from the article, so it must be able to
 stand alone. For this reason, References should be avoided, but if essential,
@@
 
-Fishers exploit fish populations that are heterogenously distributed without
-prior knowledge of species distributions and non-selective fishing gear.
-Fisheries are managed by single-species quotas, leading to discarding of
-overquota catch. Increasing interest in technical solutions such as gear,
-spatial closures as a way of managing "fisheries" instead of fish stocks. \\
-
-Provide some examples here of where this is the case..focus on spatial
-management and the increasing sophistication / resolution of data dervied from
-VMS and logbooks; refs: Geritsen et al, Mateo et al. \\
+Fishers exploit fish populations that are heterogenously distributed in space
+and time without prior knowledge of species distributions and non-selective
+fishing gear. Fisheries managed by single-species quotas still catch an
+assemblage of species, known as mixed fisheries, leading to discarding of
+overquota catch. Reducing discarding is crucial to ensure biological and
+economic sustainability of fisheries and as such there is increasing interest
+in technical solutions such as gear, spatial closures as a way of avoiding
+discarding unwanted catch. \\
 
 Use of spatial management as a tool is hampered by lack of knowledge of fish
-and fishery spatiotemporal dyanmics and the scale at which processes are
-important for management. Need to understand these to implement effective
-management measures for species avoidance / targeting. Use Dunn et al as a
-ref.\\
+and fishery spatiotemporal dyanmics and understanding of the scale at which
+processes are important for management, crucial in order to implement measures
+at the right resolution to ensure effective management\cite{Dunn2016} which
+promote species avoidance for vulnerable or low quota species while allowing
+continance of sustainable fisheries for available quota species. \\
 
-We develop a simulation model where underlying population dynamics are known
-rather than inferred from sampling or commercial catches. It includes
-population movement and a number of different fisheries exploiting four fish
-populations with different demographics.\\
+Ensuring measures are implemented at an appropriate scale has been a challenge
+in the a past that has led to ineffectual measures with unitended consequences
+such as limited impact towards the management objective wirth increased benthic
+impact on previously unexploited areas (e.g. the cod closure in the North
+Sea\cite{Rijnsdorp2001,Dinmore2003}). Since then more refined spatial
+information has become available through the combination of logbook and Vessel
+Monitoring System (VMS) data\cite{Lee2010, Bastardie2010, Gerritsen2012,
+	Mateo2016}, though such information is patchy and derived from a biased
+sampling programme (i.e.  targeted fishing). Further, generally fishers only
+recorded landings (not catch) on a daily basis. This leads to questions about the
+validity of inferences that can be drawn from landings data assigned to VMS
+activity pings. \\
 
-Using the model, we simulation 20 years of exploitation of the fish populations
-and use the results to draw inference on the underlying population structures -
-as done in species modelling approaches. \\
+In order to test the assumption that VMS associated landings data can be used
+to draw inference on the underlying population structures we develop a
+simulation model where population dynamics are known rather than inferred from
+sampling or commercial catches, population movement driven by a random
+(diffusive) and directed (advective) process and characterisation of a number
+of different fisheries exploiting four fish populations with different spatial
+and population demographics.\\
+
+Using our model we simulation 20 years of exploitation of the fish populations
+and use the results to draw inference on the underlying population structures.
+We compare this inference to i) a simulated stratified fixed-site sampling
+design commonly used for fisheries monitoring purposes, ii) the underlying
+population structures input to the simulation.\\
+
+[Could fit a geostatistical model (e.g. VAST) to the fisheries-dependent and
+fisheries-independent data, though may be overkill...] \\
 
@@
 
-[State the objectives of the work and provide an adequate background, avoiding a
-detailed literature survey or a summary of the results.]
+[Guidance:: State the objectives of the work and provide an adequate
+background, avoiding a detailed literature survey or a summary of the results.]
+\\
 
@@
 
-[Provide sufficient details to allow the work to be reproduced by an independent
-researcher. Methods that are already published should be summarized, and
-indicated by a reference.  If quoting directly from a previously published
-method, use quotation marks and also cite the source. Any modifications to
-existing methods should also be described.]
+[Provide sufficient details to allow the work to be reproduced by an
+independent researcher. Methods that are already published should be
+summarized, and indicated by a reference.  If quoting directly from a
+previously published method, use quotation marks and also cite the source. Any
+modifications to existing methods should also be described.] \\
+
+We developed a simulation model with a modular discrete-event approach to each
+of the processes so that they can occur on different time-scales. The fishing
+model operated on a tow-by-tow basis, while population dynamics (fishing and
+natural mortality, growth) operate on a daily time-step.  Population movement
+occurs on a two-weekly time-step, while recruitment occurs periodcally each
+year for a set time period (e.g. 3 weeks) at at specified point individual to a
+species. The model structure is summerised in Figure 1.  \\
 
@@
 \begin{figure}[!ht]
+	\hspace{-4em}
 \begin{tikzpicture}[%
@@
     node distance=8mm and 60mm, % Global setup of box spacing
-    every join/.style={norm}   % Default linetype for connecting boxes
-    ]                 
+    every join/.style={norm},   % Default linetype for connecting boxes
+    scale=0.9,
+    every node/.style={scale=0.8}]                 
     \label{fig:model}

### 2018-01-19 R/run_sim.R

@@ -20,6 +20,8 @@
 run_sim <- function (sim_init = NULL, pop_init = NULL, fleets_init = NULL, hab_init = NULL, InParallel = TRUE, cores = 3, ...) {
 # Overarching function for running the simulations
 
+start.time <- Sys.time() # for printing runtime
+
 require(doParallel)
 registerDoParallel(cores = cores)
 
@@ -343,6 +345,9 @@ pop_init[["Pop_record"]][[s]][["Rec.mat"]][1, year.breaks[t]] <- sum(Rec[[s]], p
 
 } # end loop control
 
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+print(paste("time taken is :", format(time.taken, units = "auto"), sep = " "))
 
 return(list(fleets_catches = catches, pop_summary = pop_init[["Pop_record"]]))
 

### 2018-01-19 write_up/mixfishsim_ecolmod.tex
Manuscript edits

@@
 
-We developed a simulation model with a modular discrete-event approach to each
-of the processes so that they can occur on different time-scales. The fishing
-model operated on a tow-by-tow basis, while population dynamics (fishing and
-natural mortality, growth) operate on a daily time-step.  Population movement
-occurs on a two-weekly time-step, while recruitment occurs periodcally each
-year for a set time period (e.g. 3 weeks) at at specified point individual to a
-species. The model structure is summerised in Figure 1.  \\
+We developed a simulation model with a modular discrete event-based approach to
+each of the processes so that they can occur on independent time-scales
+suitable for the processes. The fishing model operated on a tow-by-tow basis,
+while population dynamics (fishing and natural mortality, growth) operate on a
+daily time-step.  Population movement occurs on a two-weekly time-step, while
+recruitment occurs periodcally each year for a set time period (e.g. 3 weeks)
+at at specified point individual to a species. The model structure is
+summerised in Figure 1.  \\
+
+In the following section, we describe each of the model components; 1)
+Population dynamics, 2) Recruitment dynamics, 3) Population movement, 4)
+fishery dynamics. \\
 

### 2018-01-29 write_up/mixfishsim_ecolmod.tex
Manuscript development and plot refinement

--- 2018-01-19 write_up/mixfishsim_ecolmod.tex
@@
 
+[Guidance:: State the objectives of the work and provide an adequate
+background, avoiding a detailed literature survey or a summary of the results.]
+\\
+
 Fishers exploit fish populations that are heterogenously distributed in space
 and time without prior knowledge of species distributions and non-selective
-fishing gear. Fisheries managed by single-species quotas still catch an
-assemblage of species, known as mixed fisheries, leading to discarding of
-overquota catch. Reducing discarding is crucial to ensure biological and
-economic sustainability of fisheries and as such there is increasing interest
-in technical solutions such as gear, spatial closures as a way of avoiding
-discarding unwanted catch. \\
+fishing gear. Fisheries managed by single-species quotas catch an assemblage of
+species, known as mixed fisheries, leading to discarding of overquota catch.
+Reducing discarding is crucial to ensure biological and economic sustainability
+of fisheries. As such there is increasing interest in technical solutions
+such as gear, spatial closures as a way of avoiding discarding unwanted catch.
+\\
 
@@
 and fishery spatiotemporal dyanmics and understanding of the scale at which
-processes are important for management, crucial in order to implement measures
-at the right resolution to ensure effective management\cite{Dunn2016} which
-promote species avoidance for vulnerable or low quota species while allowing
-continance of sustainable fisheries for available quota species. \\
+processes are important for management. Understanding of the correct scale for
+spatial management is crucial in order to implement measures at a resolution
+that ensures effective management\cite{Dunn2016} while minimising economic
+impact; for example a scale which promote species avoidance for vulnerable or
+low quota species while allowing continance of sustainable fisheries for
+available quota species. \\
 
@@
 in the a past that has led to ineffectual measures with unitended consequences
-such as limited impact towards the management objective wirth increased benthic
+such as limited impact towards the management objective or increased benthic
 impact on previously unexploited areas (e.g. the cod closure in the North
@@
 Monitoring System (VMS) data\cite{Lee2010, Bastardie2010, Gerritsen2012,
-	Mateo2016}, though such information is patchy and derived from a biased
-sampling programme (i.e.  targeted fishing). Further, generally fishers only
-recorded landings (not catch) on a daily basis. This leads to questions about the
-validity of inferences that can be drawn from landings data assigned to VMS
-activity pings. \\
+	Mateo2016}, though such information is patchy and derived from an
+inherently biased sampling programme (i.e. targeted fishing). Further,
+generally fishers only recorded landings (not catch) on a daily basis. This
+leads to questions about the validity of inferences that can be drawn from
+landings data assigned to VMS activity pings. \\
 
@@
 simulation model where population dynamics are known rather than inferred from
-sampling or commercial catches, population movement driven by a random
-(diffusive) and directed (advective) process and characterisation of a number
-of different fisheries exploiting four fish populations with different spatial
-and population demographics.\\
+sampling or commercial catches. Population movement is driven by a random
+(diffusive) and directed (advective) process and we incorporate
+characterisation of a number of different fisheries exploiting four fish
+populations with different spatial and population demographics.\\
 
 Using our model we simulation 20 years of exploitation of the fish populations
-and use the results to draw inference on the underlying population structures.
-We compare this inference to i) a simulated stratified fixed-site sampling
-design commonly used for fisheries monitoring purposes, ii) the underlying
-population structures input to the simulation.\\
+and use the results from the fishing model to draw inference on the underlying
+population structures.  We compare this inference to i) a simulated
+[stratified] fixed-site sampling design commonly used for fisheries monitoring
+purposes, ii) the underlying population structures input to the simulation.\\
 
@@
 
-[Guidance:: State the objectives of the work and provide an adequate
-background, avoiding a detailed literature survey or a summary of the results.]
-\\
-
 \section{Materials and Methods}
 
-[Provide sufficient details to allow the work to be reproduced by an
+[Guidance: Provide sufficient details to allow the work to be reproduced by an
 independent researcher. Methods that are already published should be
@@
 
-We developed a simulation model with a modular discrete-event approach to each
-of the processes so that they can occur on different time-scales. The fishing
-model operated on a tow-by-tow basis, while population dynamics (fishing and
-natural mortality, growth) operate on a daily time-step.  Population movement
-occurs on a two-weekly time-step, while recruitment occurs periodcally each
-year for a set time period (e.g. 3 weeks) at at specified point individual to a
-species. The model structure is summerised in Figure 1.  \\
+We develop a simulation model with a modular event-based approach, where
+modules occur on independent time-scales appropriate to capture the
+characteristic of the process modelled. The fishing model operated on a
+tow-by-tow basis, while population dynamics (fishing and natural mortality,
+growth) operate on a daily time-step.  Population movement occurs on a
+two-weekly time-step, while recruitment occurs periodcally each year for a set
+time period (e.g. 3 weeks) at at specified point individual to a species. The
+model structure is summerised in Figure 1.\\
+
+In the following section, we describe each of the model components; 1)
+Population dynamics, 2) Recruitment dynamics, 3) Population movement, 4)
+fishery dynamics.\\
 
@@
 \node [test, densely dotted] (t1) {if $y > y-1$};
-\node [test, join, densely dotted] (t2) {if $spp_{t}$ != $spp_{t-1}$};
-\node [test, join, densely dotted] (wk) {if $week_{t}$ != $week_{t-1}$};
+\node [test, join, densely dotted] (t2) {if $pop_{t}$ != $pop_{t-1}$};
+\node [test, join, densely dotted] (wk) {if $day_{t}$ != $day_{t-1}$};
 \node [test, join, densely dotted] (t3) {if $trip_{t}$ != $trip_{t-1}$};
@@
 The basic population level processes are simulated using a modified two-stage
-Deriso-Schnute delay difference model \cite{Deriso1980, Schnute1985}
-occurring at the weekly time-step \cite{Dichmont2003}. Here, population
-biomass growth and depletion for pre-recruits and fish recruited to the fishery
-are modelled separately as a function of previous recruited biomass, intrinsic
+Deriso-Schnute delay difference model \cite{Deriso1980, Schnute1985,
+	Dichmont2003} occurring at a daily time-step. Here, population biomass
+growth and depletion for pre-recruits and fish recruited to the fishery are
+modelled separately as a function of previous recruited biomass, intrinsic
 population growth and recruitment:
@@
 
-$\rho$ is Brody's coefficient, shown to be approximately equal to $exp(-K)$,
-where $K$ is the growth rate from a von bertalanffy logistic growth model
-\cite{Schnute1985}.  $Wt_{R-1}$ is the weight of fish prior to recruitment,
-while $Wt_{R}$ is the recruited weight.  $\alpha_{w}$ represents the proportion of
-fish recruited during the week, while $R_{\tilde{y}}$ is the annual
-recruits. \\
+where $\rho$ is Brody's coefficient, shown to be approximately equal to
+$exp(-K)$, where $K$ is the growth rate from a von bertalanffy logistic growth
+model \cite{Schnute1985}. $Wt_{R-1}$ is the weight of fish prior to
+recruitment, while $Wt_{R}$ is the recruited weight. $\alpha_{w}$ represents
+the proportion of fish recruited during the week, while $R_{\tilde{y}}$ is the
+annual recruits. \\
 
@@
 where $C$ is the summed catch from the fishing model across all fleets and
-vessels for the species, year and week respectively, and $B$ the weekly biomass
-for the species. \\
+vessels for the population during the day, and $B$ the daily biomass for the
+species. \\
 
@@
 
-Where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock biomass (SSB)
-required to produce half the maximum, and $B$ current SSB; \\
+Where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
+biomass (SSB) required to produce half the maximum, and $B$ current SSB; \\
 
@@
 
-where $\alpha$ is the maximum productivity per spawner and $\beta$ the density dependent
-reduction in productivity as the SSB increases.
+where $\alpha$ is the maximum productivity per spawner and $\beta$ the density
+dependent reduction in productivity as the SSB increases.
 
@@
 
+In order to simulate how fish populations might be distributed in space and
+time, we employed a Gaussian spatial process to model habitat suitability for
+each of the populations, with an advection-diffusion process to control how the
+populations moved in time. \\
+
+For the habitat we define a Gaussian random field process, $\{S(x) : x \in
+\mathbb{R}^2\}$, that is a stochastic process where any collection of locations
+$x_{1}, \dots, x_{n}$ where for each $x_{i} \in \mathbb{R}^2$, the joint
+distribution of $S = \{S(x1),\dots S(x_{n})\}$ is multivariate Gaussian. The
+distribution is specified by its \textit{mean function}, $\mu(x) = E[S(x)]$ and
+its \textit{covariance function}, $\gamma(x,x') = Cov\{S(x),S(x')\}$
+\cite{Diggle2007}.\\
+
+The specification of the covariance structure directly affects the smoothness
+of the surfaces which the process generates.  We used the \textit{Matérn}
+family of covariance structures, one where the correlation strength weakens the
+further the distance apart (i.e. the correlation between $S(x)$ and $S(x')$
+decreases as the distance $u = ||x - x'||$ increases).  The \textit{Matérn}
+correlation is a two-parameter family where: \\
+
+\begin{center}
+	$\rho(u) = \{2^{\kappa -
+		1}\Gamma{\kappa}\}^{-1}(u/\phi)^{\kappa}K_{\kappa}(u/\phi)$
+\end{center}
+
+$K_{\kappa}(.)$ is a modified Bessel function of order $\kappa$, $\phi >
+0$ is a scale parameter with the dimensions of distance, and $\kappa > 0$,
+called the order, is a shape parameter which determines the smoothness of the
+underlying process. \\
+
+The population is initialised at a single location, and subsequently moves
+according to a probabilistic distribtion based on habitat suitability and
+distance from current cell.
+
+\begin{equation}
+	Pr(B | A) = \frac{e^{-\lambda * d_{AB}} \cdot
+		Hab_{B}^2}{\sum\limits_{c=1}^{C}e^{-\lambda * d} \cdot
+		Hab^2}
+\end{equation}
+
+Where $d_{AB}$ is the euclidean distance between cell $A$ and cell $B$, and
+$\lambda$ is some rate of decay.\\
+
+During specified weeks of the year, the habitat quality is modified for
+spawning habitats, meaning each population has a concentrated area where
+spawning takes place and the population moves towards this in the weeks prior
+to spawning. \\
+
 \subsection{Fleet dynamics}
+
+The fleet dynamics can be broadly categorised into three components; fleet
+targeting - which determines the fleet catch efficiency and preference towards
+a particular species; trip-level decisions, which determine the initial
+location to be fished at the beginning of a trip; and within-trip decisions,
+determining movement from one fishing spot to another within a trip.  A further
+sub-model controls local depletion of fish populations at fished sites.
+
+\subsubsection{Fleet targeting}
+
+Each fleet of \textit{n} vessels is characterised by both a general efficiency,
+\textit{Q}, and a species specific efficiency, ${Q_{s}}$.  Thus, the product of
+these parameters affects the overall catch rates for the fleet and the
+preferential targeting of one species over another.  This, in combination with
+the parameter choice for the step-function (as well as some randomness from the
+exploratory fishing process) determines the preference of fishing locations for
+the fleet.  All species prices are kept the same, across fleets, though can be
+made to vary seasonally.
+
+\subsubsection{Trip-level decisions}
+
+Several studies (e.g.\cite{Hutton2004, Tidd2012, Girardin2015}) have confirmed
+past activity and past catch rates are strong predictors of fishing location
+choice. For this reason, the fleet dynamics sub-model includes a learning
+component, where a vessels initial fishing location in a trip is based on
+selecting from previously successful fishing locations. This is achieved by
+sorting all previous fishing events in the previous trip as well as the
+previous time periods in past years, and choosing randomly from the top x \% of
+fishing events in value.  Simulation testing indicating this increased the mean
+value of catches for the vessels, over just relying on the correlated random
+walk function.
+
+\subsubsection{Within-trip decisions}
+
+Fishing locations within a trip are determined by a Random Walk process. A
+Random walk was chosen as it is commonly used in ecology to describe animal
+movement which searching for homogeneously distributed prey about which there
+is uncertain knowledge. In a random walk, movement is a stochastic process
+through a series of steps that can either be equal in length or take some other
+functional form.  The direction of the random walk can be correlated, a
+characteristic known as 'persistence', providing some overall location
+directional movement \cite{Codling2008} or uncorrelated. \\
+
+A \textit{lévy walk} is a particular form of random walk characterised by a
+heavy-tailed distribution of step-length and has received a lot of attention in
+ecological theory in recent years as having shown to have very similar
+characteristics as those observed by animals in nature, and being a near
+optimum searching strategy for predators pursuing patchily distributed prey
+\cite{Bartumeus2005, Sims2008}.  \cite{Bertrand2007} showed that Peruvian
+anchovy fishermen have a stochastic search pattern similar to that observed
+with a lévy walk. However, it remains a subject of debate, with the contention
+that search patterns may be more simply characteristed as random walks
+\cite{Sakiyama2013} with specific patterns related to the characteristics of
+the prey field \cite{Sims2012}. \\
+
+We use a modified random walk where directional change is based on a correlated
+circular distribution where a favourable fishing ground is likely to be "fished
+back over" by the vessel returning in the direction it came from and step
+length (i.e. the distance travelled from the current to the next fishing
+location) is determined by relating recent fishing success, measured as the
+summed value of fish caught, $$Rev = \sum_{s=1}^{\infty} C_{s} \cdot Pr_{s}$$
+where $C_{s}$ is catch of a species, and $Pr_{s}$ price of a species, to step
+distance. Here, when fishing is successful vessels remain in a similar location
+and continue to exploit the local fishing grounds. When unsuccessful, they move
+some distance away from the current fishing location. The movement distance
+retains some degree of stochasticity, which can be controlled separately. \\
+
+The step function takes the form:
+
+\begin{equation*}
+	StepL = e^{log(\beta_{1}) + log(\beta_{2}) - (log(\frac{\beta_{1}}{\beta_{3}}))} * Rev
+\end{equation*}
+
+So that, a step from (x1,y1) to (x2, y2) is defined by:
+
+\begin{equation*}
+	\begin{split}
+ (x2, y2) =  & x1 + StepL \cdot \cos (\frac{\pi \cdot Br}{180}), \\
+             & y1 + StepL \cdot \sin (\frac{\pi \cdot Br}{180}) \\	
+ where \hspace{0.5cm}     & Br \sim U[(0,360)]
+	\end{split}
+\end{equation*}
+
+\subsubsection{Local population depletion}
+
+Where several fishing vessels are exploiting the same fish population
+competition is known to play an important role in local distribution of fishing
+effort \cite{Gillis1998}. If several vessels are fishing on the same patch of
+fish, local depletion and interference will affect fishing location choice of
+the fleet as a whole \cite{Rijnsdorp2000, Poos2007a}. In order to account for
+this behaviour, the fishing sub-model operates spatially on a daily time-step
+so that for future days the biomass available to the fishery is reduced in the
+areas fished. The cumulative effect is to make heavily fished areas less
+attractive as future fishing opportunities. \\
+
+\subsection{Fisheries independent survey}
+
+A fisheries-independent survey is simulated where fishing on a regular grid
+begins each year at the same time for a given number of stations (a fixed
+station survey design). Catches of the populations present are recorded but not
+removed from the population. This provides a fishery independent snap shot of
+the populations at a regular spatial distribution each year, similar to
+scientific surveys undertaken by fisheries research agencies. \\
 
@@
 
-[A Theory section should extend, not repeat, the background to the article
-already dealt with in the Introduction and lay the foundation for further work.
-In contrast, a Calculation section represents a practical development from a
-theoretical basis.]
+[Guidance: A Theory section should extend, not repeat, the background to the
+article already dealt with in the Introduction and lay the foundation for
+further work.  In contrast, a Calculation section represents a practical
+development from a theoretical basis.]
 
@@
 
-[Results should be clear and concise.]
+[Guidance: Results should be clear and concise.]
 
@@
 
-This should explore the significance of the results of the work, not repeat
-them. A combined Results
-and Discussion section is often appropriate. Avoid extensive citations and
-discussion of published
-literature.
+[Guidance: This should explore the significance of the results of the work, not
+repeat them. A combined Results and Discussion section is often appropriate.
+Avoid extensive citations and discussion of published literature.]
 
@@
 
-The main conclusions of the study may be presented in a short Conclusions
-section, which may stand
-alone or form a subsection of a Discussion or Results and Discussion section.
+[Guidance: The main conclusions of the study may be presented in a short Conclusions
+section, which may stand alone or form a subsection of a Discussion or Results
+and Discussion section.]
 
@@
 
-If there is more than one appendix, they should be identified as A, B, etc.
+[Guidance: If there is more than one appendix, they should be identified as A, B, etc.
 Formulae and equations in appendices should be given separate numbering: Eq.
 (A.1), Eq. (A.2), etc.; in a subsequent appendix, Eq. (B.1) and so on.
-Similarly for tables and figures: Table A.1; Fig. A.1, etc.
+Similarly for tables and figures: Table A.1; Fig. A.1, etc.]
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{../tests/plots/habitat}
+		\caption{habitat}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{../tests/plots/annual_summary}
+		\caption{Annual Summmary}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{../tests/plots/fDynamics}
+		\caption{f dynamics}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{../tests/plots/vessel_move}
+		\caption{vessel movement}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{../tests/plots/vessel_multi_move}
+		\caption{vessel movement multi}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{../tests/plots/vessel_move_value}
+		\caption{vessel movement value}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{../tests/plots/fleet_moves}
+		\caption{fleet movement}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{../tests/plots/catch_comp}
+		\caption{spatial catch composition}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{../tests/plots/catch_comp_clusters}
+		\caption{spatial catch composition with clustering}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{../tests/plots/survey_index}
+		\caption{survey index}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{../tests/plots/spatial_survey}
+		\caption{survey spatial abundance}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{../tests/plots/step_function}
+		\caption{Realised step function}
+\end{figure}
+
+\newpage
 

### 2018-01-29 R/plot_pop_summary.R

@@ -59,7 +59,7 @@ plot_pop_summary <- function(results = res, timestep = 'daily', save = FALSE, sa
 
 	results_df_annual <- rbind(results_df_an1, results_df_an2) 
 
-	print(ggplot(results_df_annual, aes(x = year, y = data, group = 2)) + geom_point() + 
+	print(ggplot(results_df_annual, aes(x = year, y = data, group = 2)) + geom_point() + geom_line() + 
 	facet_wrap(pop ~ metric, scale = "free") + expand_limits(y = 0))
 	}
 

### 2018-01-29 R/plot_survey.R

@@ -1,0 +1,45 @@
+#' @title Plot the fisheries independent survey results
+
+#' @description \code{plot_survey} plots the spatial abundances and an index
+#' from the fisheries independent survey, for each population.
+
+#' @param survey is the survey results from the \link{run_sim} function.
+#' @param type is a character indicating if \emph{spatial} or \emph{index}
+
+#' @return is a plot of the spatial distribution of survey catches and an
+#' inter-annual abundance index
+
+#' @examples
+#' plot_survey(survey = survey, type = "spatial")
+
+#' @export
+
+plot_survey <- function (survey = NULL, type = "spatial") {
+	require(ggplot2)
+	require(dplyr)
+	require(reshape2)
+
+	# spatial catches
+	log.mat  <- as.data.frame(survey[["log.mat"]])
+
+
+	if(type == "spatial") {
+	log.spat <- melt(log.mat, id = c("station_no", "x", "y", "day", "tow", "year"))
+
+	print(ggplot(log.spat, aes(x = x, y = y, size = value)) +
+		geom_point(shape = 21, aes(fill = value)) +
+		facet_grid(variable ~ year))
+
+	}
+
+	if(type == "index") {
+	log.idx <- melt(log.mat, id = c("station_no", "x", "y", "day", "tow", "year"))
+
+log.idx <- 	log.idx %>% group_by(year, variable) %>% summarise(mean= mean(value), se = (sd(value, na.rm = T) / sqrt(n())))
+
+	print(ggplot(log.idx, aes(x = factor(year), y = mean, group = variable)) + geom_point() + geom_line() + geom_linerange(aes(ymin = mean - 1.96 * se, ymax = mean + 1.96 * se)) + facet_wrap(~variable) +
+	      xlab("") + ylab("abundance index"))
+
+	}
+	
+}

### 2018-01-29 R/plot_vessel_move.R

@@ -14,12 +14,12 @@
 #' = TRUE
 
 #' @examples
-#' plot_vessel_move(logs = logs, fleet_no = 1, vessel_no = 1, year_trip = 1,
+#' plot_vessel_move(sim_init = NULL, logs = logs, fleet_no = 1, vessel_no = 1, year_trip = 1,
 #' trip_no = 1, fleets_init = NULL, pop_bios = NULL)
 
 #' @export
 
-plot_vessel_move <- function (logs = logs, fleet_no = 1, vessel_no = 1, year_trip = 1, trip_no = 1, fleets_init = NULL, pop_bios = NULL) {
+plot_vessel_move <- function (sim_init = NULL, logs = logs, fleet_no = 1, vessel_no = 1, year_trip = 1, trip_no = 1, fleets_init = NULL, pop_bios = NULL) {
 
 require(ggplot2)
 require(dplyr)
@@ -30,7 +30,7 @@ log <- filter(as.data.frame(logs), fleet %in% fleet_no, vessel %in% vessel_no, y
 
 if(is.null(fleets_init) | is.null(pop_bios)) {
 
-print(ggplot(log, aes(x = x, y = y, group = paste(vessel, trip))) + geom_point(aes(colour = tow)) + geom_path(aes(colour = tow)))
+print(ggplot(log, aes(x = x, y = y, group = paste(vessel, trip))) + geom_point(aes(colour = tow)) + geom_path(aes(colour = tow))+ expand_limits(y = c(0,sim_init[["idx"]][["ncols"]]), x = c(0,sim_init[["idx"]][["nrows"]])))
 
 }
 
@@ -49,11 +49,11 @@ Value <- lapply(names(Bs), function(x) {
 TotVal <- Reduce("+", Value)
 
 TotValDF <- tidyr::gather(as.data.frame(TotVal), factor_key = TRUE)
-TotValDF$x <- rep(1:100, times = 100)
-TotValDF$y <- rep(1:100, each = 100)
+TotValDF$x <- rep(seq_len(sim_init[["idx"]][["nrows"]]), times = sim_init[["idx"]][["nrows"]])
+TotValDF$y <- rep(seq_len(sim_init[["idx"]][["ncols"]]), each = sim_init[["idx"]][["ncols"]])
 
 print(ggplot(TotValDF, aes(x = x, y = y)) + geom_tile(aes(fill = value)) +
[…]

### 2018-01-29 R/run_sim.R

@@ -242,9 +242,6 @@ spat_fs <- find_spat_f_pops(sim_init = sim_init, C = spp_catches, B = B,
 ## Fishing mortality rates
 print(sapply(names(spat_fs), function(x) weighted.mean(spat_fs[[x]], B[[x]])))
 
-## Or the summed values (fraction fished of pop)
-print(sapply(names(spp_catches), function(x) { sum(spp_catches[[x]]) / sum(B[[x]])}))
-
 # Apply the delay difference model
 Bp1 <- foreach(x = paste0("spp", seq_len(n_spp))) %dopar% {
 
@@ -268,7 +265,7 @@ B <- Bp1
 ## scientific survey
 ####################
 
-if(sim_init[["brk.idx"]][["day.breaks"]][t] %in% survey[["log.mat"]][,"day"]) {
+if(sim_init[["brk.idx"]][["day.breaks"]][t] %in% survey[["log.mat"]][,"day"] & !is.null(survey)) {
 
 print("undertaking scientific survey") 
 
@@ -280,15 +277,15 @@ print("undertaking scientific survey")
 	log.mat <- survey[["log.mat"]]
 
 	# survey locations
-	x_loc <- subset(log.mat, log.mat[,"day"== doy] & log.mat[,"year"==y])[,"x"]
-	y_loc <- subset(log.mat, log.mat[,"day"== doy] & log.mat[,"year"==y])[,"y"]
-	
+	x_loc <- log.mat[log.mat[,"day"] == doy & log.mat[,"year"] == y, "x"]
+	y_loc <- log.mat[log.mat[,"day"] == doy & log.mat[,"year"] == y, "y"]
+
 	# For each set of locations
 	for(i in seq_len(length(x_loc))) {
-
-		# For each species
+		
+# For each species
 for(s in seq_len(n_spp)) {
-log.mat[log.mat[,"day"]==doy & log.mat[,"year"]==y,paste0("spp",s)][i]  <-  	B[[s]][x_loc[i],y_loc[i]] * survey[["survey_settings"]][[paste0("Qs.spp",s)]]
+log.mat[log.mat[,"day"]==doy & log.mat[,"year"]==y,paste0("spp",s)][i]  <-  	B[[s]][x_loc[i],y_loc[i]] * as.numeric(survey[["survey_settings"]][[paste0("Qs.spp",s)]])
 }
 	}
 

### 2018-01-30 write_up/mixfishsim_ecolmod.tex
Updates to manuscript

@@
 \begin{abstract}
-[A concise and factual abstract is required. The abstract should state briefly
-the purpose of the research, the principal results and major conclusions. An
-abstract is often pnresented separately from the article, so it must be able to
-stand alone. For this reason, References should be avoided, but if essential,
-then cite the author(s) and year(s). Also, non-standard or uncommon
-abbreviations should be avoided, but if essential they must be defined at their
-first mention in the abstract itself.  
-Graphical abstract: Although a graphical abstract is optional, its use is
-encouraged as it draws more attention to the online article. The graphical
-abstract should summarize the contents of the article in a concise, pictorial
-form designed to capture the attention of a wide readership. Graphical
-abstracts should be submitted as a separate file in the online submission
-system. Image size: Please provide an image with a minimum of 531 X 1328 pixels
-(h X w) or proportionally more. The image should be readable at a size of 5 x
-13 cm using a regular screen resolution of 96 dpi.  Preferred file types: TIFF,
-EPS, PDF or MS Office files.]
+[Guidance: A concise and factual abstract is required. The abstract should
+state briefly the purpose of the research, the principal results and major
+conclusions. An abstract is often pnresented separately from the article, so it
+must be able to stand alone. For this reason, References should be avoided, but
+if essential, then cite the author(s) and year(s). Also, non-standard or
+uncommon abbreviations should be avoided, but if essential they must be defined
+at their first mention in the abstract itself.  Graphical abstract: Although a
+graphical abstract is optional, its use is encouraged as it draws more
+attention to the online article. The graphical abstract should summarize the
+contents of the article in a concise, pictorial form designed to capture the
+attention of a wide readership. Graphical abstracts should be submitted as a
+separate file in the online submission system. Image size: Please provide an
+image with a minimum of 531 X 1328 pixels (h X w) or proportionally more. The
+image should be readable at a size of 5 x 13 cm using a regular screen
+resolution of 96 dpi.  Preferred file types: TIFF, EPS, PDF or MS Office
+files.]
 \end{abstract}
@@
              & y1 + StepL \cdot \sin (\frac{\pi \cdot Br}{180}) \\	
- where \hspace{0.5cm}     & Br \sim U[(0,360)]
+ with  \hspace{0.5cm}     & Br_{t-1} < 180, Br_{t} = 180 + \sim vm[(0,360), k] \\
+ 			  & Br_{t-1} > 180, Br_{t} = 180 - \sim vm[(0,360), k] \\
 	\end{split}
 \end{equation*}
+
+with $k$ the concentration parameter from the von mises distribution which we
+correlate with the revenue so that $k = (revenue + 1 / maxRevenue) * max_{k}$
+
+where $max_{k}$ is the maximum concentration value, $k$, and maxRevenue is
+parameterised as for $\beta_{3}$ in the step length function. \\
 
@@
 further work.  In contrast, a Calculation section represents a practical
-development from a theoretical basis.]
+development from a theoretical basis.] \\
 
-HERE DESCRIBE THE PARAMETERISATION, AND ANY COMPARISON AGAINST 'REAL' DATA
+\subsection{Simulation settings}
+
+We set up with simulation to run for 20 years based on a 100 X 100 square grid,
+with five fleets of 20 vessels each and four fish populations. Fishing takes
+place four times a day per vessel and five days a week, while population
+movement is every two weeks. \\
+
+\subsection{Population parameterisation}
+
+We parameterised the simulation model for four populations with differing
+habitat preference (Figure \ref{fig:1}) and defined two spawning areas for each
+of the populations (Table \ref{tab:1}). \\
+
+\begin{table}[!ht]
+\caption{Population dynamics and movement parameter setting}
+	\begin{tabular}{ p{4cm } p{2cm} p{2cm} p{2cm} p{2cm}}
+	Parameter & Pop 1 & Pop 2 & Pop 3 & Pop 4 \\
+	\hline
+	Habitat quality & & & \\
+	\hline
+	Matérn $\nu$ & 1/0.15 & 1/0.05 & 1/0.55 & 1/0.05  \\
+	Matérn $\kappa$ & 1 & 2 & 1 & 1  \\
+	Anisotropy & 1.5,3,-3,4 & 1,2,-1,2 & 2.5,1,-1,2 & 0.1,2,-1,0.2 \\
+	Spawning areas (bound box) & 40,50,40,50; 80,90,60,70 &
+	50,60,30,40; 80,90,90,90 & 30,34,10,20; 60,70,20,30 & 50,55,80,85; 30,40,30,40 \\
+	Spawning multiplier & 10 & 10 & 10 & 10 \\
+	Movement $\lambda$ & 0.3 & 0.3 & 0.3 & 0.3 \\
+	\hline
+	Population dynamics & & & & \\
+	\hline
+	Starting Biomass & 1e5 & 2e5 & 1e5 & 1e4 \\
+	Beverton-Holt Recruit 'a' & 60 & 100 & 80 & 2 \\
+	Beverton-Holt Recruit 'b' & 250 & 250 & 200 & 50 \\
+	Beverton-Holt Recruit $\sigma$ & 0.2 & 0.1 & 0.2 & 0.1 \\
+	Recruit week & 13-16 & 12-16 & 14-16 & 16-20 \\
+	Population dynamics and movement parameter settingSpawn week & 16-18 & 16-19 & 16-18 & 18-20 \\
+	M (annual) & 0.2 & 0.2 & 0.2 & 0.1 \\
+	\hline
+\end{tabular}
+\label{tab:1}
+\end{table}
+
+\subsection{Fleet parameterisation}
+
+\begin{table}[!ht]
+\caption{Fleet dynamics parameter setting}
+\begin{tabular}{ p{4cm } p{1cm} p{1cm} p{1cm} p{1cm} p{1cm}}
+	\hline
+	Parameter & Fleet 1 & Fleet 2 & Fleet 3 & Fleet 4 & Fleet 5 \\
+	\hline
+	Targeting preferences &&&& \\
+	\hline
+	Price Pop1 & 100 & 100 & 100 & 100 & 100 \\
+	Price Pop2 & 200 & 200 & 200 & 200 & 200 \\
+	Price Pop3 & 600 & 600 & 600 & 600 & 600 \\
+	Price Pop4 & 1600 & 1600 & 1600 & 1600 & 1600 \\
+	$Q$ Pop1 & 0.01 & 0.02 & 0.02 & 0.02 & 0.02 \\
+	$Q$ Pop2 & 0.02 & 0.01 & 0.01 & 0.01 & 0.01\\
+	$Q$ Pop3 & 0.01 & 0.02 & 0.02 & 0.02 & 0.02 \\
+	$Q$ Pop4 & 0.02 & 0.01 & 0.01 & 0.01 & 0.01 \\
+	\hline
+	Exploitation dynamics &&&& \\
+	\hline
+	step function $\beta_1$ & 1 & 2 & 1 & 2 & 3 \\
+	step function $\beta_2$ & 10 & 10 & 8 & 12 & 7 \\
+	step function $\beta_3$ & MaxRev & MaxRev & MaxRev & MaxRev & MaxRev \\
+	step function $rate$ & 10 & 20 & 15 & 25 & 10 \\
+	Past Knowledge & T & T & T & T & T \\
+	Past Year \& Month & T & T & T & T & T \\
+	Past Trip & T & T & T & T & T \\
+	Threshold & 0.75 & 0.75 & 0.75 & 0.75 & 0.75 \\
+	\hline
+\end{tabular}
+\label{tab:2}
+\end{table}
 
@@
 	\includegraphics[width = \linewidth]{../tests/plots/habitat}
-		\caption{habitat}
+	\caption{habitat preference}
+	\label{fig:1}
 \end{figure}
@@
 	\caption{Annual Summmary}
+	\label{fig:2}
 \end{figure}
@@
 	\caption{f dynamics}
+	\label{fig:3}
 \end{figure}
@@
 	\caption{vessel movement}
+	\label{fig:4}
 \end{figure}
@@
 	\caption{vessel movement multi}
+	\label{fig:5}
 \end{figure}
@@
 	\caption{vessel movement value}
+	\label{fig:6}
 \end{figure}
@@
 	\caption{fleet movement}
+	\label{fig:7}
 \end{figure}
@@
 	\caption{spatial catch composition}
+	\label{fig:8}
 \end{figure}
@@
 	\caption{spatial catch composition with clustering}
+	\label{fig:9}
 \end{figure}
@@
 	\caption{survey index}
+	\label{fig:10}
 \end{figure}
@@
 	\caption{survey spatial abundance}
+	\label{fig:11}
 \end{figure}
@@
 	\caption{Realised step function}
+	\label{fig:12}
 \end{figure}
@@
 
+\newpage
+
 \section*{References}

### 2018-01-30 R/go_fish.R

@@ -139,7 +139,9 @@ coords <- c(catch[t-1, "x"], catch[t-1,"y"]) # Previous coordinates
 	
 	#Bear = runif(1,0,360) # bearing - to be replaced with a correlated von mises dist
 	b <- ifelse(t = 1, 0, catch[t-1,"angles"]) # base on most recent bearing
-	k = 50/params[["step_params"]][["B3"]] + 1 # concentration parameter, a proportion of the maximum haul + 1 (to avoid infinity)
+	max_k <- 20
+	k = ((catch[t-1,"val"]+1) / params[["step_params"]][["B3"]]) * max_k
+	# concentration parameter, a proportion of the maximum haul + 1 (to avoid infinity)
 	Bear <- get_bearing(b = b, k = k)
 	catch[t, "angles"] <- Bear
 	new.point <- round(make_step(stepD = stepD, Bear = Bear, start.x = coords[1], start.y = coords[2])) # returns c(x2,y2)

### 2018-01-30 R/survey_settings.R

@@ -12,7 +12,7 @@
 #' @param start_day is a Numeric for the first day of the survey each year
 #' @param stations_per_day is a Numeric for the number of stations surveyed per
 #' day
-#' @params Qs is a named Numeric Vector containing any survey catchabilities, assumed to be time invariant.
+#' @param Qs is a named Numeric Vector containing any survey catchabilities, assumed to be time invariant.
 #'
 #' @return is a list consisting of the survey setting and a a matrix for
 #' storing the log of catches from the survey, to be used as an input to

### 2018-01-30 write_up/mixfishsim_ecolmod.tex
Updates to manuscript

@@
 \begin{abstract}
-[Guidance: A concise and factual abstract is required. The abstract should
-state briefly the purpose of the research, the principal results and major
-conclusions. An abstract is often pnresented separately from the article, so it
-must be able to stand alone. For this reason, References should be avoided, but
-if essential, then cite the author(s) and year(s). Also, non-standard or
-uncommon abbreviations should be avoided, but if essential they must be defined
-at their first mention in the abstract itself.  Graphical abstract: Although a
-graphical abstract is optional, its use is encouraged as it draws more
-attention to the online article. The graphical abstract should summarize the
-contents of the article in a concise, pictorial form designed to capture the
-attention of a wide readership. Graphical abstracts should be submitted as a
-separate file in the online submission system. Image size: Please provide an
-image with a minimum of 531 X 1328 pixels (h X w) or proportionally more. The
-image should be readable at a size of 5 x 13 cm using a regular screen
-resolution of 96 dpi.  Preferred file types: TIFF, EPS, PDF or MS Office
-files.]
+\textcolor{gray}{[Guidance: A concise and factual abstract is required. The abstract 
+should state briefly the purpose of the research, the principal results and
+major conclusions. An abstract is often pnresented separately from the article,
+so it must be able to stand alone. For this reason, References should be
+avoided, but if essential, then cite the author(s) and year(s). Also,
+non-standard or uncommon abbreviations should be avoided, but if essential they
+must be defined at their first mention in the abstract itself.  Graphical
+abstract: Although a graphical abstract is optional, its use is encouraged as
+it draws more attention to the online article. The graphical abstract should
+summarize the contents of the article in a concise, pictorial form designed to
+capture the attention of a wide readership. Graphical abstracts should be
+submitted as a separate file in the online submission system. Image size:
+Please provide an image with a minimum of 531 X 1328 pixels (h X w) or
+proportionally more. The image should be readable at a size of 5 x 13 cm using
+a regular screen resolution of 96 dpi.  Preferred file types: TIFF, EPS, PDF or
+MS Office files.] \\}
+
+Fishing exploits spatio-temporally hetergenous fish populations without fully
+selective gear which can result in unintended, unwanted catch of low quota or
+protected species. Reducing these unwanted catches is crucial for biological
+and economic sustainability of 'mixed fisheries'. \\
+
+Understanding of spatio-temporal fishery dynamics is limited by a lack of full
+understanding of population distribution and how fishers interact with the
+different populations. We develop a spatio-temporal simulation model that
+incorporate i) delay-difference population dynamics, ii) population movement
+dynamics using Gaussian Random Fields, iii) fishery dynamics for multiple fleet
+characteristics based on a correlated random walk and learned behaviour. \\
+
+Using our model we simulation 20 years of exploitation of the fish populations
+and use the results from the fishing model to draw inference on the underlying
+population structures.  We compare this inference to i) a simulated fixed-site
+sampling design commonly used for fisheries monitoring purposes, ii) the
+underlying population structures input to the simulation.\\
+
+We find that... \\
+
 \end{abstract}
@@
 \begin{keyword}
-Some\sep keywords \sep here. Max 6, American "spelling" 
+Some\sep keywords \sep here. Max 6 
 \MSC[2010] 00-01\sep  99-00
@@
 
-[Guidance:: State the objectives of the work and provide an adequate
+\textcolor{gray}{[Guidance:: State the objectives of the work and provide an adequate
 background, avoiding a detailed literature survey or a summary of the results.]
-\\
+\\}
 
@@
 
-[Guidance: Provide sufficient details to allow the work to be reproduced by an
-independent researcher. Methods that are already published should be
-summarized, and indicated by a reference.  If quoting directly from a
+\textcolor{gray}{[Guidance: Provide sufficient details to allow the work to be
+reproduced by an independent researcher. Methods that are already published
+should be summarized, and indicated by a reference.  If quoting directly from a
 previously published method, use quotation marks and also cite the source. Any
-modifications to existing methods should also be described.] \\
+modifications to existing methods should also be described.] \\ }
 
@@
 
-[Guidance: A Theory section should extend, not repeat, the background to the
-article already dealt with in the Introduction and lay the foundation for
-further work.  In contrast, a Calculation section represents a practical
-development from a theoretical basis.] \\
+\textcolor{gray}{[Guidance: A Theory section should extend, not repeat, 
+the background to the article already dealt with in the Introduction and lay
+the foundation for further work.  In contrast, a Calculation section represents
+a practical development from a theoretical basis.] \\}
 
@@
 
+The fleets were parameterised to reflect five different characteristics based
+on targeting preference and exploitation dynamics (Table \ref{tab:2}). This
+ensures that different fleets have different spatial dynamics, preferentially
+targeted different fish populations. The stochasticity in the random walk
+process ensures that different vessels within a fleet have slightly different
+spatial distributions based on individual experience. \\
+
+Each fleet was set so that, after the first year, fishing locations were chosen
+based on experience built up in the same month from previous years and from
+past trip fishing success. 'Success' in this context was defined as the
+locations where the top 75 \% of revenue from previous trips was found. \\
+
 \begin{table}[!ht]
@@
 
+\subsection{Survey settings}
+
+The survey simulation was set up with follow a fixed gridded station design
+with 49 stations fished each year, starting on day 92 with same catchability
+parameters for all populations (Q = 1). \\
+
 \section{Results}
@@
 
-[Guidance: Results should be clear and concise.]
+\textcolor{gray}{[Guidance: Results should be clear and concise.]}
 
@@
 
-[Guidance: This should explore the significance of the results of the work, not
-repeat them. A combined Results and Discussion section is often appropriate.
-Avoid extensive citations and discussion of published literature.]
+\textcolor{gray}{[Guidance: This should explore the significance of the results 
+of the work, not repeat them. A combined Results and Discussion section is
+often appropriate.  Avoid extensive citations and discussion of published
+literature.]}
 
@@
 
-[Guidance: The main conclusions of the study may be presented in a short Conclusions
-section, which may stand alone or form a subsection of a Discussion or Results
-and Discussion section.]
+textcolor{gray}{[Guidance: The main conclusions of the study may be presented 
+in a short Conclusions section, which may stand alone or form a subsection of a
+Discussion or Results and Discussion section.]}
 
@@
 
-[Guidance: If there is more than one appendix, they should be identified as A, B, etc.
-Formulae and equations in appendices should be given separate numbering: Eq.
-(A.1), Eq. (A.2), etc.; in a subsequent appendix, Eq. (B.1) and so on.
-Similarly for tables and figures: Table A.1; Fig. A.1, etc.]
+\textcolor{gray}{[Guidance: If there is more than one appendix, they should 
+be identified as A, B, etc.  Formulae and equations in appendices should be
+given separate numbering: Eq.  (A.1), Eq. (A.2), etc.; in a subsequent
+appendix, Eq. (B.1) and so on.  Similarly for tables and figures: Table A.1;
+Fig. A.1, etc.]}
 

### 2018-01-31 write_up/mixfishsim_ecolmod.tex
manu updates

@@
 protected species. Reducing these unwanted catches is crucial for biological
-and economic sustainability of 'mixed fisheries'. \\
+and economic sustainability of 'mixed fisheries' and implementation of an
+ecosystem approach to fishing. \\
 
-Understanding of spatio-temporal fishery dynamics is limited by a lack of full
-understanding of population distribution and how fishers interact with the
-different populations. We develop a spatio-temporal simulation model that
-incorporate i) delay-difference population dynamics, ii) population movement
-dynamics using Gaussian Random Fields, iii) fishery dynamics for multiple fleet
-characteristics based on a correlated random walk and learned behaviour. \\
+In order to implement effective spatial measures to reduce discards there needs
+to be a good understanding of spatio-temporal fishery dynamics. However,
+scientific advice is limited by a lack of knowledge of population distribution,
+movement and how fishers interact with different fish populations. This is
+because data on location of fish at high temporal and spatial resolutions is
+expensive and difficult to collect and therefore proxy inferred from either
+scientific survey or commercial catch data is often used to model
+distributions, but often limited in its spatial or temporal resolution. \\
+
+We develop a highly resolved spatio-temporal simulation model that incorporate
+i) delay-difference population dynamics, ii) population movement dynamics using
+Gaussian Random Fields to simulate patchy, hetergenously distributed
+populations, iii) fishery dynamics for multiple fleet characteristics based on
+a correlated random walk and learned behaviour. \\
 
@@
 sampling design commonly used for fisheries monitoring purposes, ii) the
-underlying population structures input to the simulation.\\
+underlying population structures input to the simulation, to establish whether
+fishing dependent data, which is obtained from a biased sampling due to fishers
+targeting, provides a robust picture of spatio-temporal distributions. [We
+simulate a closure based on areas defined from commercial catch data and assess
+its effectiveness on reducing catches of a fish population.] \\
 
-We find that... \\
+We conclude that... \\
+
+[233 words]
 
@@
 
-\textcolor{gray}{[Guidance:: State the objectives of the work and provide an adequate
-background, avoiding a detailed literature survey or a summary of the results.]
-\\}
+\textcolor{gray}{[Guidance:: State the objectives of the work and provide an 
+adequate background, avoiding a detailed literature survey or a summary of the
+results.] \\}
 
 Fishers exploit fish populations that are heterogenously distributed in space
-and time without prior knowledge of species distributions and non-selective
-fishing gear. Fisheries managed by single-species quotas catch an assemblage of
-species, known as mixed fisheries, leading to discarding of overquota catch.
-Reducing discarding is crucial to ensure biological and economic sustainability
-of fisheries. As such there is increasing interest in technical solutions
-such as gear, spatial closures as a way of avoiding discarding unwanted catch.
-\\
+and time without prior knowledge of species distributions using non-selective
+fishing gear. Fisheries that catch an assemblage of species, known as mixed
+fisheries, when managed by single-species quotas can end up discarding
+overquota catch leading to overexploitation of fish populations. Reducing
+discarding is crucial to ensure biological and economic sustainability of
+fisheries and implementation of an ecosystem approach to fisheries. As such
+there is increasing interest in technical solutions such as gear, spatial
+closures as a way of avoiding discards.  \\
 
-Use of spatial management as a tool is hampered by lack of knowledge of fish
+Use of spatial management as a tool has been proposed as a method to reduce
+discards. However, its implementation is hampered by lack of knowledge of fish
 and fishery spatiotemporal dyanmics and understanding of the scale at which
@@
 Monitoring System (VMS) data\cite{Lee2010, Bastardie2010, Gerritsen2012,
-	Mateo2016}, though such information is patchy and derived from an
-inherently biased sampling programme (i.e. targeted fishing). Further,
-generally fishers only recorded landings (not catch) on a daily basis. This
-leads to questions about the validity of inferences that can be drawn from
+	Mateo2016} and more real-time spatial management has been able to be
+implemented (e.g. \cite{Holmes2011}), though such information is patchy and
+derived from an inherently biased sampling programme (i.e. targeted fishing).
+Further, fishers generally only recorded landings (not catch) on a daily basis.
+This leads to questions about the validity of inferences that can be drawn from
 landings data assigned to VMS activity pings. \\
@@
 We develop a simulation model with a modular event-based approach, where
-modules occur on independent time-scales appropriate to capture the
+modules are implemented on independent time-scales appropriate to capture the
 characteristic of the process modelled. The fishing model operated on a
@@
 growth) operate on a daily time-step.  Population movement occurs on a
-two-weekly time-step, while recruitment occurs periodcally each year for a set
+weekly time-step, while recruitment occurs periodcally each year for a set
 time period (e.g. 3 weeks) at at specified point individual to a species. The
-model structure is summerised in Figure 1.\\
+simulation framework is implemented in the statistical software package R
+\cite{RCoreTeam2017}; available as an R package from the authors github
+(\url{www.github.com/pdolder/MixFishSim}). The overall model structure is
+summerised in Figure 1.\\
 
@@
 Population dynamics, 2) Recruitment dynamics, 3) Population movement, 4)
-fishery dynamics.\\
+fishery dynamics.
 
@@
 	\begin{split}
-	B_{y,w+1} = &\\
-	& (1 + \rho) B_{y,w} \cdot e^{-Z_{y,w}} - \rho \cdot e^{-Z_{y,w}} \hspace{2.9cm}
+	B_{y,d+1} = &\\
+	& (1 + \rho) B_{y,d} \cdot e^{-Z_{y,d}} - \rho \cdot e^{-Z_{y,d}} \hspace{2.9cm}
 	\times \\  
-	& (B_{y,w-1} \cdot e^{-Z_{y,w-1}} + Wt_{R-1} \cdot \alpha_{w-1} \cdot R_{\tilde{y}(y,w-1)})
+	& (B_{y,d-1} \cdot e^{-Z_{y,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot R_{\tilde{y}(y,d-1)})
 	\hspace{0.4cm} + \\
-	& Wt_{R} \cdot \alpha_{w} \cdot R_{\tilde{y}(y,w)} 
+	& Wt_{R} \cdot \alpha_{d} \cdot R_{\tilde{y}(y,d)} 
 	\end{split}
@@
 model \cite{Schnute1985}. $Wt_{R-1}$ is the weight of fish prior to
-recruitment, while $Wt_{R}$ is the recruited weight. $\alpha_{w}$ represents
-the proportion of fish recruited during the week, while $R_{\tilde{y}}$ is the
-annual recruits. \\
+recruitment, while $Wt_{R}$ is the recruited weight. $\alpha_{d}$ represents
+the proportion of fish recruited during that day for the year, while
+$R_{\tilde{y}}$ is the annual recruits. \\
 
@@
 \begin{equation*}
-C_{w} = \frac{F_{w}}{F_{w}+M_{w}} * (1 - e^{-(F_{w} + M_{w})}) * B
+C_{d} = \frac{F_{d}}{F_{d}+M_{d}} * (1 - e^{-(F_{d} + M_{d})}) * B
 \end{equation*}
@@
 Recruitment is modelled through a function relating the biomass at time of
-recruitment to recruits, either as a stochastic Beverton-Holt stock-recruit
-form (\cite{Beverton1957}):
+recruitment to recruits. In the simulation, it can be modelled either either as
+a stochastic Beverton-Holt stock-recruit form (\cite{Beverton1957}):
 
@@
 each of the populations, with an advection-diffusion process to control how the
-populations moved in time. \\
+populations moved over time. \\
 
@@
 
-The specification of the covariance structure directly affects the smoothness
-of the surfaces which the process generates.  We used the \textit{Matérn}
-family of covariance structures, one where the correlation strength weakens the
-further the distance apart (i.e. the correlation between $S(x)$ and $S(x')$
-decreases as the distance $u = ||x - x'||$ increases).  The \textit{Matérn}
-correlation is a two-parameter family where: \\
+The covariance structure affects the smoothness of the surfaces which the
+process generates, and we used the \textit{Matérn} family of covariance
+structures, one where the correlation strength weakens the further the distance
+apart (i.e. the correlation between $S(x)$ and $S(x')$ decreases as the
+distance $u = ||x - x'||$ increases).  The \textit{Matérn} correlation is a
+two-parameter family where: \\
 
@@
 
-The population is initialised at a single location, and subsequently moves
-according to a probabilistic distribtion based on habitat suitability and
-distance from current cell.
+In the simulation model, the habitat for each of the populations is generated
+through the \textit{RFSimulate} function of the \textit{RandomFields} R package
+\cite{Schlater2015}, implementing different parameter settings to affect the
+patchiness of the populations. Each population is initialised at a single
+location, and subsequently moves according to a probabilistic distribtion based
+on habitat suitability and distance from current cell.
 
@@
 Where $d_{AB}$ is the euclidean distance between cell $A$ and cell $B$, and
-$\lambda$ is some rate of decay.\\
+$\lambda$ is a given rate of decay.\\
 
@@
 location to be fished at the beginning of a trip; and within-trip decisions,
-determining movement from one fishing spot to another within a trip.  A further
-sub-model controls local depletion of fish populations at fished sites.
+determining movement from one fishing spot to another within a trip.
 
@@
 Each fleet of \textit{n} vessels is characterised by both a general efficiency,
-\textit{Q}, and a species specific efficiency, ${Q_{s}}$.  Thus, the product of
-these parameters affects the overall catch rates for the fleet and the
-preferential targeting of one species over another.  This, in combination with
-the parameter choice for the step-function (as well as some randomness from the
-exploratory fishing process) determines the preference of fishing locations for
-the fleet.  All species prices are kept the same, across fleets, though can be
-made to vary seasonally.
+\textit{Q}, and a population specific efficiency, ${Q_{p}}$.  Thus, the product
+of these parameters affects the overall catch rates for the fleet and the
+preferential targeting of one population over another. This, in combination
+with the parameter choice for the step-function (as well as some randomness
+from the exploratory fishing process) determines the preference of fishing
+locations for the fleet.  All species prices are kept the same, across fleets,
+though can be made to vary seasonally.
 
@@
 characteristic known as 'persistence', providing some overall location
-directional movement \cite{Codling2008} or uncorrelated. \\
+of directional movement \cite{Codling2008} or uncorrelated. \\
 
@@
 some distance away from the current fishing location. The movement distance
-retains some degree of stochasticity, which can be controlled separately. \\
+retains some degree of stochasticity, which can be controlled separately.
 
@@
 with $k$ the concentration parameter from the von mises distribution which we
-correlate with the revenue so that $k = (revenue + 1 / maxRevenue) * max_{k}$
-
-where $max_{k}$ is the maximum concentration value, $k$, and maxRevenue is
-parameterised as for $\beta_{3}$ in the step length function. \\
+correlate with the revenue so that $k = (Rev + 1 / RefRev) * max_{k}$,
+where $max_{k}$ is the maximum concentration value, $k$, and RefRev is
+parameterised as for $\beta_{3}$ in the step length function.
 
@@
 areas fished. The cumulative effect is to make heavily fished areas less
-attractive as future fishing opportunities. \\
+attractive as future fishing opportunities.
 
@@
 the populations at a regular spatial distribution each year, similar to
-scientific surveys undertaken by fisheries research agencies. \\
+scientific surveys undertaken by fisheries research agencies.
 
-\section{Theory/calculation}
+\section{Calculation}
 
-\textcolor{gray}{[Guidance: A Theory section should extend, not repeat, 
-the background to the article already dealt with in the Introduction and lay
-the foundation for further work.  In contrast, a Calculation section represents
-a practical development from a theoretical basis.] \\}
+\textcolor{gray}{[Guidance: A \underline{Theory} section should extend, not
+repeat, the background to the article already dealt with in the	Introduction
+and lay the foundation for further work.  In contrast, a
+\underline{Calculation} section represents a practical development from a
+theoretical basis.] \\}
 
@@
 place four times a day per vessel and five days a week, while population
-movement is every two weeks. \\
+movement is every week.
 
@@
 We parameterised the simulation model for four populations with differing
-habitat preference (Figure \ref{fig:1}) and defined two spawning areas for each
-of the populations (Table \ref{tab:1}). \\
+habitat preference (Figure \ref{fig:1}), population demographic and recruitment
+functions; each of the populations also has two defined spawning areas and
+movement rates (Table \ref{tab:1}). \\
+
+\subsection{Fleet parameterisation}
+
+The fleets were parameterised to reflect five different characteristics based
+on targeting preference and exploitation dynamics (Table \ref{tab:2}). This
+ensures that different fleets have different spatial dynamics, preferentially
+targeted different fish populations. The stochasticity in the random walk
+process ensures that different vessels within a fleet have slightly different
+spatial distributions based on individual experience, while the step function
+was parameterised dynamically so that vessels take smaller steps where the
+fishing location yields in the top X Quartile of the value available in that
+year (as defined per fleet in Table \ref{tab:2}). \\
+
+Each fleet was set so that, after the first year, fishing locations were chosen
+based on experience built up in the same month from previous years and from
+past trip fishing success. 'Success' in this context was defined as the
+locations where the top 75 \% of revenue from was found in previous trips.
+
+\subsection{Survey settings}
+
+The survey simulation was set up with follow a fixed gridded station design
+with 49 stations fished each year, starting on day 92 with same catchability
+parameters for all populations (Q = 1).
+
+\section{Results}
+
+Need to consider what best to present here as 4 / 5 figures:
+
+\begin{itemize}
+	\item Spatial dynamics: e.g. Figure 14. showing the population movement
+		across weeks, including a spawning period.
+	\item Overall population trends: e.g. Figure 3, showing the population
+		dynamics at play.
+	\item Realised step function: e.g. Figure 13, showing how the movement
+		and turning angle responds. This could be combined with Figure
+		7 for a more complete visualisaiton.
+	\item Catch composition and spatial clustering: e.g. Figure 10, showing
+		the importance of spatial resolution.
+	\item Some measure of temporal trends/changes in spatial composition -
+		could pick a certain cell and show how the proportions change
+		over time ? An example is Figure 15, though there is little
+		variation here. I think this is because the static habitat with
+		population movement is far more stable than the previous
+		directly affected population distributions (where there was an
+		advective-diffusive process from the SPDE). Might need to
+		consider how to change this?  Could include a spatio-temporally
+		changing habitat suitability covariate, e.g. temperature ??
+	\item Comparison of population structure from i) commercial sampling,
+		ii) fisheries independent survey, iii) real population. This
+		should be some statistical measure...not sure best approach
+		here.
+	\item [If we perform the closure, some measure of cost/benefit based on
+		different resolutions of data and data used (i.e. commercial,
+		survey, real populations). This could be on the basis of
+		closing x cells, giving cell references to the model so they
+		cannot be fished. Need to consider whether this is also a
+		seasonal closure.]
+\end{itemize}
+
+Present simulated closures in terms of \% change in population biomass and
+fishery.
+
+\textcolor{gray}{[Guidance: Results should be clear and concise.]}
+
+\section{Discussion}
+
+\textcolor{gray}{[Guidance: This should explore the significance of the results 
+of the work, not repeat them. A combined Results and Discussion section is
+often appropriate.  Avoid extensive citations and discussion of published
+literature.]}
+
+\section{Conclusions}
+
+\textcolor{gray}{[Guidance: The main conclusions of the study may be presented 
+in a short Conclusions section, which may stand alone or form a subsection of a
+Discussion or Results and Discussion section.]}
+
+\section*{Appendices}
+
+\textcolor{gray}{[Guidance: If there is more than one appendix, they should 
+be identified as A, B, etc.  Formulae and equations in appendices should be
+given separate numbering: Eq.  (A.1), Eq. (A.2), etc.; in a subsequent
+appendix, Eq. (B.1) and so on.  Similarly for tables and figures: Table A.1;
+Fig. A.1, etc.]}
 
@@
 	Beverton-Holt Recruit 'b' & 250 & 250 & 200 & 50 \\
-	Beverton-Holt Recruit $\sigma$ & 0.2 & 0.1 & 0.2 & 0.1 \\
+	Beverton-Holt Recruit $\sigma^2$ & 0.4 & 0.3 & 0.4 & 0.3 \\
 	Recruit week & 13-16 & 12-16 & 14-16 & 16-20 \\
-	Population dynamics and movement parameter settingSpawn week & 16-18 & 16-19 & 16-18 & 18-20 \\
+	Spawn week & 16-18 & 16-19 & 16-18 & 18-20 \\
+	$K$ & 0.3 & 0.3 & 0.3 & 0.3 \\
+	$wt$ & 1 & 1 & 1 & 1 \\
+	$wt_{d-1}$ & 0.1 & 0.1 & 0.1 & 0.1 \\
 	M (annual) & 0.2 & 0.2 & 0.2 & 0.1 \\
@@
 \end{table}
-
-\subsection{Fleet parameterisation}
-
-The fleets were parameterised to reflect five different characteristics based
-on targeting preference and exploitation dynamics (Table \ref{tab:2}). This
-ensures that different fleets have different spatial dynamics, preferentially
-targeted different fish populations. The stochasticity in the random walk
-process ensures that different vessels within a fleet have slightly different
-spatial distributions based on individual experience. \\
-
-Each fleet was set so that, after the first year, fishing locations were chosen
-based on experience built up in the same month from previous years and from
-past trip fishing success. 'Success' in this context was defined as the
-locations where the top 75 \% of revenue from previous trips was found. \\
 
@@
 	Price Pop4 & 1600 & 1600 & 1600 & 1600 & 1600 \\
-	$Q$ Pop1 & 0.01 & 0.02 & 0.02 & 0.02 & 0.02 \\
-	$Q$ Pop2 & 0.02 & 0.01 & 0.01 & 0.01 & 0.01\\
-	$Q$ Pop3 & 0.01 & 0.02 & 0.02 & 0.02 & 0.02 \\
-	$Q$ Pop4 & 0.02 & 0.01 & 0.01 & 0.01 & 0.01 \\
+	$Q$ Pop1 & 0.01 & 0.02 & 0.02 & 0.01 & 0.01 \\
+	$Q$ Pop2 & 0.02 & 0.01 & 0.02 & 0.01 & 0.03\\
+	$Q$ Pop3 & 0.01 & 0.02 & 0.02 & 0.01 & 0.02 \\
+	$Q$ Pop4 & 0.02 & 0.01 & 0.02 & 0.05 & 0.01 \\
 	\hline
@@
 	step function $\beta_2$ & 10 & 10 & 8 & 12 & 7 \\
-	step function $\beta_3$ & MaxRev & MaxRev & MaxRev & MaxRev & MaxRev \\
+	step function $\beta_3$ & Q90 & Q90 & Q85 & Q90 & Q80 \\
 	step function $rate$ & 10 & 20 & 15 & 25 & 10 \\
@@
 
-\subsection{Survey settings}
-
-The survey simulation was set up with follow a fixed gridded station design
-with 49 stations fished each year, starting on day 92 with same catchability
-parameters for all populations (Q = 1). \\
-
-\section{Results}
-
-Present simulated closures in terms of \% change in population biomass and
-fishery.
-
-\textcolor{gray}{[Guidance: Results should be clear and concise.]}
-
-\section{Discussion}
-
-\textcolor{gray}{[Guidance: This should explore the significance of the results 
-of the work, not repeat them. A combined Results and Discussion section is
-often appropriate.  Avoid extensive citations and discussion of published
-literature.]}
-
-\section{Conclusions}
-
-textcolor{gray}{[Guidance: The main conclusions of the study may be presented 
-in a short Conclusions section, which may stand alone or form a subsection of a
-Discussion or Results and Discussion section.]}
-
-\section*{Appendices}
-
-\textcolor{gray}{[Guidance: If there is more than one appendix, they should 
-be identified as A, B, etc.  Formulae and equations in appendices should be
-given separate numbering: Eq.  (A.1), Eq. (A.2), etc.; in a subsequent
-appendix, Eq. (B.1) and so on.  Similarly for tables and figures: Table A.1;
-Fig. A.1, etc.]}
-
 \begin{figure}[!ht]
@@
 	\includegraphics[width = \linewidth]{../tests/plots/annual_summary}
-	\caption{Annual Summmary}
+	\caption{Summary of annualised metrics: biomass, catch, fishing
+		mortality and recruitment. x-axis is the year, y the value}
 	\label{fig:2}
@@
 	\includegraphics[width = \linewidth]{../tests/plots/fDynamics}
-	\caption{f dynamics}
+	\caption{f dynamics - the daily fishing mortalities, each year is a
+		different colour}
 	\label{fig:3}
@@
 	\includegraphics[width = \linewidth]{../tests/plots/vessel_move}
-	\caption{vessel movement}
+	\caption{vessel movement - a single trip movement for one vessel}
 	\label{fig:4}
@@
 	\includegraphics[width = \linewidth]{../tests/plots/vessel_multi_move}
-	\caption{vessel movement multi}
+	\caption{vessel movement for multiple trips from a single vessel. Note
+	the movement off the side pops up the other side, but is joined by a
+	line across the grid. This is from the torus approach rather than the
+	edges being barriers}
 	\label{fig:5}
@@
 	\includegraphics[width = \linewidth]{../tests/plots/vessel_move_value}
-	\caption{vessel movement value}
+	\caption{movement of a single vessel over a few trips overlaid on the
+		value field (i.e. sum of the population abundance x catchability x value}
 	\label{fig:6}
@@
 	\includegraphics[width = \linewidth]{../tests/plots/fleet_moves}
-	\caption{fleet movement}
+	\caption{An entire fleets (20 vessels) movement for a single trip}
 	\label{fig:7}
@@
 	\includegraphics[width = \linewidth]{../tests/plots/catch_comp}
-	\caption{spatial catch composition}
+	\caption{spatial catch composition - the raw catches per cell at 4
+		different spatial resolutions. Sorry, its a bit small at the
+		moment!}
 	\label{fig:8}
@@
 	\includegraphics[width = \linewidth]{../tests/plots/catch_comp_clusters}
-	\caption{spatial catch composition with clustering}
+	\caption{spatial catch composition (as above) but with clustering of
+		cells performs on the bottom row. I'm confused as to why some
+		entirely blue cells in the raw catch composition get allocated
+	to the same cluster as some entirely red cells - needs investigating,
+	it may be the clustering is not optimal}
 	\label{fig:9}
@@
 	\includegraphics[width = \linewidth]{../tests/plots/survey_index}
-	\caption{survey index}
+	\caption{survey index - a non-spatial index generated from the fishery independent
+	survey}
 	\label{fig:10}
@@
 	\includegraphics[width = \linewidth]{../tests/plots/spatial_survey}
-	\caption{survey spatial abundance}
+	\caption{survey spatial abundance - a bubble plot of the survey
+		abundances, not really useful for the paper}
 	\label{fig:11}
@@
 	\includegraphics[width = \linewidth]{../tests/plots/step_function}
-	\caption{Realised step function}
+	\caption{Realised step function - the step function as realised for a
+		single fleet. For turning angles, it can be seen that at higher
+	values, the turning range is less}
 	\label{fig:12}
@@
 
-\newpage
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{../tests/plots/pop_dist}
+	\caption{Spatial dynamics - the four populations at four time steps.
+		Not really happy about the lack of dynamics here - mainly down
+	to the static habitat leading to the populations settle in same cells
+	over most time steps (exception: during the spawning period). Could
+	include a temperature covariate or something to force some more
+	temporal changes?}
+	\label{fig:13}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{../tests/plots/Proportion_in_cell}
+	\caption{Temporal dynamics - the proportion of each population in a
+		randomly chosen cell. Similar criticism as above}
+	\label{fig:14}
+\end{figure}
 
@@
 
-\newpage
+\clearpage
 

### 2018-01-31 R/go_fish.R

@@ -140,8 +140,8 @@ coords <- c(catch[t-1, "x"], catch[t-1,"y"]) # Previous coordinates
 					  val_mat <- Q[[x]] * pops[[x]] * VPT[[x]]
 					})
 		ValMat <- Reduce("+", ValMat)
-		maxVal <- max(ValMat, na.rm = T)
-		params[["step_params"]][["B3"]] <- maxVal
+		B3_rev <- quantile(ValMat, prob = 0.9)
+		params[["step_params"]][["B3"]] <- B3_rev 
 	
 	stepD     <- step_length(revenue = catch[t-1,"val"],step_params = params[["step_params"]])  # Calculate step distance based on last tow value
         catch[t,"stepD"] <- stepD    # record the step distance	

### 2018-01-31 R/init_pop.R

@@ -25,6 +25,7 @@
 #' vector of the weeks in which spawning takes place for the population
 #' @param M is a named vector, with the annual natural mortality rate for each
 #' population
+#' @param K is a named vector, with the annual growth rate for each population
 #'
 #' @return The function returns the recording vectors at the population level,
 #' the spatial matrices for the starting population densities and the
@@ -35,12 +36,13 @@
 #' 0.2, "spp2" = 0.3), init_move_steps = 10), rec_params = list("spp1" =
 #' c("model" = "BH", "a" = 10, "b" = 50, "cv" = 0.2), "spp2" = c("model" = "BH",
 #' "a" = 1, "b" = 8, "cv" = 0.2)), rec_wk = list("spp1" = 13:16, "spp2" =
-#' 13:18, spwn_wk = list("spp1" = 15:18, "spp2" = 18:20),M = c("spp1" = 0.2, "spp2" = 0.1)))
+#' 13:18), spwn_wk = list("spp1" = 15:18, "spp2" = 18:20),M = c("spp1" = 0.2,
+#' "spp2" = 0.1), K = c("spp1" = 0.3, "spp2" = 0.2))
 #' Note, example will not have the right biomass
 
 #' @export
 
-init_pop <- function(sim_init = sim_init, Bio = NULL, hab = NULL, start_cell = NULL, lambda = NULL, init_move_steps = 10, rec_params = NULL, rec_wk = NULL, spwn_wk = NULL, M = NULL, cores = 3) {
+init_pop <- function(sim_init = sim_init, Bio = NULL, hab = NULL, start_cell = NULL, lambda = NULL, init_move_steps = 10, rec_params = NULL, rec_wk = NULL, spwn_wk = NULL, M = NULL, K = NULL, cores = 3) {
 
 require(doParallel)
 registerDoParallel(cores = cores)
@@ -109,7 +111,7 @@ names(Pop_vec) <- paste("spp",seq(idx[["n.spp"]]), sep ="")
 
 dem_params <- lapply(names(Bio), function(x) {
 
-dem_params = list(rec_params = rec_params[[x]], rec_wk = rec_wk[[x]], spwn_wk = spwn_wk[[x]], M = M[[x]])
+dem_params = list(rec_params = rec_params[[x]], rec_wk = rec_wk[[x]], spwn_wk = spwn_wk[[x]], M = M[[x]], K = K[[x]])
 
 return(dem_params)
 		  

### 2018-01-31 R/run_sim.R

@@ -250,7 +250,7 @@ al   <- ifelse(week.breaks[t] %in% pop_init[["dem_params"]][[x]][["rec_wk"]],
 alm1 <- ifelse(c(week.breaks[t]-1) %in% pop_init[["dem_params"]][[x]][["rec_wk"]],
 	     1/length(pop_init[["dem_params"]][[x]][["rec_wk"]]), 0)
 
-res <- delay_diff(K = 0.3, F = spat_fs[[x]], 
+res <- delay_diff(K = pop_init[["dem_params"]][[x]][["K"]], F = spat_fs[[x]], 
 	   M = pop_init[["dem_params"]][[x]][["M"]]/365, 
 	   wt = 1, wtm1 = 0.1, R = Rec[[x]], B = B[[x]],
           Bm1 = Bm1[[x]], al = al,  alm1 = alm1)

### 2018-02-04 write_up/mixfishsim_ecolmod.tex
modulolinenumbers changed to discuss
Rough edit

@@
 
-\modulolinenumbers[5]
+\modulolinenumbers[1]
 
@@
 \begin{frontmatter}
+\title{\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics}
 
-\title{A simulation framework for exploring spatio-temporal dynamics in mixed
-	fisheries}
+%%\title{A simulation framework for exploring spatio-temporal dynamics in mixed
+%%	fisheries}
 
@@
 \author[3]{Jean-Marc Guarini}
-\author[4]{Jan-Jaap Poos}
+\author[4]{Jan Jaap Poos}
 
@@
 
-Fishing exploits spatio-temporally hetergenous fish populations without fully
-selective gear which can result in unintended, unwanted catch of low quota or
+Fishing exploits spatially and temporally hetergenous fish populations, using species-unselective 
+gear that can result in unintended, unwanted catch of low quota or
 protected species. Reducing these unwanted catches is crucial for biological
-and economic sustainability of 'mixed fisheries' and implementation of an
+and economic sustainability of `mixed fisheries' and implementation of an
 ecosystem approach to fishing. \\
 
-In order to implement effective spatial measures to reduce discards there needs
-to be a good understanding of spatio-temporal fishery dynamics. However,
-scientific advice is limited by a lack of knowledge of population distribution,
-movement and how fishers interact with different fish populations. This is
-because data on location of fish at high temporal and spatial resolutions is
-expensive and difficult to collect and therefore proxy inferred from either
-scientific survey or commercial catch data is often used to model
-distributions, but often limited in its spatial or temporal resolution. \\
+To implement effective spatial measures to reduce discards 
+a good understanding of spatio-temporal fishery dynamics is required. However,
+traditional scientific advice is limited by a lack of highly resolved knowledge of population distribution,
+movement and how fishers interact with different fish populations. This reflects that 
+data on fish location at high temporal and spatial resolutions is
+expensive and difficult to collect and therefore proxies inferred from either
+scientific surveys or commercial catch data are often used to model
+distributions, often with limited spatial and temporal resolution. \\
 
-We develop a highly resolved spatio-temporal simulation model that incorporate
-i) delay-difference population dynamics, ii) population movement dynamics using
+To understand how resolution impacts mixed fisheries inference, we develop a highly 
+resolved spatio-temporal simulation model incorporating:
+i) delay-difference population dynamics, ii) population movement using
 Gaussian Random Fields to simulate patchy, hetergenously distributed
-populations, iii) fishery dynamics for multiple fleet characteristics based on
-a correlated random walk and learned behaviour. \\
+populations, and iii) fishery dynamics for multiple fleet characteristics based on
+targetting via correlated random walk movement and learned behaviour. \\
 
-Using our model we simulation 20 years of exploitation of the fish populations
+We simulate 20 years of exploitation of the fish populations
 and use the results from the fishing model to draw inference on the underlying
 population structures. We compare this inference to i) a simulated fixed-site
-sampling design commonly used for fisheries monitoring purposes, ii) the
-underlying population structures input to the simulation, to establish whether
-fishing dependent data, which is obtained from a biased sampling due to fishers
-targeting, provides a robust picture of spatio-temporal distributions. [We
+sampling design commonly used for fisheries monitoring purposes, and ii) the
+true underlying population structures input to the simulation, to establish the potential and limitations of
+fishery-dependent data - an inherently biased sampling method due to fisher's
+targeting- to provide a robust picture of spatio-temporal distributions. [We
 simulate a closure based on areas defined from commercial catch data and assess
@@
 Fishers exploit fish populations that are heterogenously distributed in space
-and time without prior knowledge of species distributions using non-selective
+and time with verying knowledge of species distributions using species-unselective
 fishing gear. Fisheries that catch an assemblage of species, known as mixed
@@
 fisheries and implementation of an ecosystem approach to fisheries. As such
-there is increasing interest in technical solutions such as gear, spatial
-closures as a way of avoiding discards.  \\
+there is increasing interest in technical solutions such as gear and spatial
+closures as ways of avoiding discards.  \\
 
@@
 discards. However, its implementation is hampered by lack of knowledge of fish
-and fishery spatiotemporal dyanmics and understanding of the scale at which
-processes are important for management. Understanding of the correct scale for
+and fishery spatiotemporal \textcolor{red}{[use this spelling throughout]} dynamics and understanding of the scale at which
+processes are important for management. Understanding the correct scale for
 spatial management is crucial in order to implement measures at a resolution
 that ensures effective management\cite{Dunn2016} while minimising economic
-impact; for example a scale which promote species avoidance for vulnerable or
-low quota species while allowing continance of sustainable fisheries for
+impact. For example, a scale that promotes species avoidance for vulnerable or
+low quota species while allowing continuance of sustainable fisheries for
 available quota species. \\
@@
 Ensuring measures are implemented at an appropriate scale has been a challenge
-in the a past that has led to ineffectual measures with unitended consequences
+in the past that has led to ineffectual measures with unitended consequences
 such as limited impact towards the management objective or increased benthic
@@
 Monitoring System (VMS) data\cite{Lee2010, Bastardie2010, Gerritsen2012,
-	Mateo2016} and more real-time spatial management has been able to be
-implemented (e.g. \cite{Holmes2011}), though such information is patchy and
+	Mateo2016} and more real-time spatial management has been possible 
+	(e.g. \cite{Holmes2011}). Such information is, however, patchy and
 derived from an inherently biased sampling programme (i.e. targeted fishing).
 Further, fishers generally only recorded landings (not catch) on a daily basis.
-This leads to questions about the validity of inferences that can be drawn from
+This leads to questions about the validity of inference that can be drawn from
 landings data assigned to VMS activity pings. \\
 
-In order to test the assumption that VMS associated landings data can be used
-to draw inference on the underlying population structures we develop a
-simulation model where population dynamics are known rather than inferred from
+In order to understand challenges that face VMS-linked landings 
+to draw inference on the underlying population structure we develop a
+simulation model where population dynamics are highly-resolved in space and time and are 
+known rather than inferred from
 sampling or commercial catches. Population movement is driven by a random
@@
 
-Using our model we simulation 20 years of exploitation of the fish populations
+Using our model we simulate 20 years of exploitation of the fish populations
 and use the results from the fishing model to draw inference on the underlying
-population structures.  We compare this inference to i) a simulated
-[stratified] fixed-site sampling design commonly used for fisheries monitoring
-purposes, ii) the underlying population structures input to the simulation.\\
+population structures.  We compare this inference to: i) a stratified fixed-site sampling survey 
+design commonly used for fisheries monitoring
+purposes \textcolor{red}{[not sure if this is the fisheries-independent survey?]} and ii) the underlying population structures input to the simulation.\\
 
@@
 modules are implemented on independent time-scales appropriate to capture the
-characteristic of the process modelled. The fishing model operated on a
+characteristic of the process modelled (Figure 1). The fishing model operated on a
 tow-by-tow basis, while population dynamics (fishing and natural mortality,
@@
 \cite{RCoreTeam2017}; available as an R package from the authors github
-(\url{www.github.com/pdolder/MixFishSim}). The overall model structure is
-summerised in Figure 1.\\
+(\url{www.github.com/pdolder/MixFishSim}).\\
 
-In the following section, we describe each of the model components; 1)
+Here we describe each of the model components; 1)
 Population dynamics, 2) Recruitment dynamics, 3) Population movement, 4)
@@
 \end{tikzpicture}
-\caption{Overview Schematic of simulation model}
+\caption{Overview Schematic of simulation model \textcolor{red}{Make a table with all variables and symbols so that you can reference them in the caption.
+Expand the caption to give as much standalone info as possible, e.g., what's blue, what's green, arrow colours, etc.}}
+\label{fig:overview}
 \end{figure}
@@
 vessels for the population during the day, and $B$ the daily biomass for the
-species. \\
+species. \textcolor{red}{[link $F$ to effort and catchability - as I think we have F as an emergent property of the fleets rather than something we solve for (I could be wrong though!)]}\\
 
@@
 
-Recruitment is modelled through a function relating the biomass at time of
-recruitment to recruits. In the simulation, it can be modelled either either as
+Recruitment is modelled through a function relating the mature biomass to recruits at time of
+recruitment. In \emph{mixfishsim}, it can be modelled either either as
 a stochastic Beverton-Holt stock-recruit form (\cite{Beverton1957}):
@@
 \end{equation*}
-
+\textcolor{red}{[better to use lognormal variability to avoid negative recruitment events at low biomasses.]}
 Where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
@@
 
-In order to simulate how fish populations might be distributed in space and
+To simulate how fish populations might be distributed in space and
 time, we employed a Gaussian spatial process to model habitat suitability for
 each of the populations, with an advection-diffusion process to control how the
-populations moved over time. \\
+populations moved over time. \textcolor{red}{[say why - balance between realism and practicalities of IBMs for the fish population]}\\
 
@@
 Where $d_{AB}$ is the euclidean distance between cell $A$ and cell $B$, and
-$\lambda$ is a given rate of decay.\\
+$\lambda$ is a given rate of decay. \textcolor{red}{[this is great but do explain $H_{ab}$ and all variables immediately on presentation throughout.]}\\
 
@@
 choice. For this reason, the fleet dynamics sub-model includes a learning
-component, where a vessels initial fishing location in a trip is based on
+component, where a vessel's initial fishing location in a trip is based on
 selecting from previously successful fishing locations. This is achieved by
@@
 previous time periods in past years, and choosing randomly from the top x \% of
-fishing events in value.  Simulation testing indicating this increased the mean
+fishing events in value.  Simulation testing indicated that this learning increased the mean
 value of catches for the vessels, over just relying on the correlated random
@@
 
-Fishing locations within a trip are determined by a Random Walk process. A
-Random walk was chosen as it is commonly used in ecology to describe animal
+Fishing locations within a trip are determined by a modified random walk process. A
+random walk type was chosen as it is the simplest assumption commonly used in ecology to describe animal
 movement which searching for homogeneously distributed prey about which there
@@
 functional form.  The direction of the random walk can be correlated, a
-characteristic known as 'persistence', providing some overall location
+characteristic known as `persistence', providing some overall location
 of directional movement \cite{Codling2008} or uncorrelated. \\
@@
 We use a modified random walk where directional change is based on a correlated
-circular distribution where a favourable fishing ground is likely to be "fished
+circular distribution where a favourable fishing ground is likely to be ``fished
 back over" by the vessel returning in the direction it came from and step
@@
 where $max_{k}$ is the maximum concentration value, $k$, and RefRev is
-parameterised as for $\beta_{3}$ in the step length function.
+parameterised as for $\beta_{3}$ in the step length function \textcolor{red}{[wonderful!]}.
 
@@
 station survey design). Catches of the populations present are recorded but not
-removed from the population. This provides a fishery independent snap shot of
+removed from the population. This provides a fishery independent snapshot of
 the populations at a regular spatial distribution each year, similar to
@@
 
-We set up with simulation to run for 20 years based on a 100 X 100 square grid,
+To illustrate the capabilities on \emph{MixFishSim}, we investigate the influence of ...
+\textcolor{red}{[expand]}.
+To do so, we first set up with simulation to run for 20 years based on a 100 X 100 square grid,
 with five fleets of 20 vessels each and four fish populations. Fishing takes
@@
 was parameterised dynamically so that vessels take smaller steps where the
-fishing location yields in the top X Quartile of the value available in that
+fishing location yields in the top X \textcolor{red}{[??]}quartile of the value available in that
 year (as defined per fleet in Table \ref{tab:2}). \\
@@
 		consider how to change this?  Could include a spatio-temporally
-		changing habitat suitability covariate, e.g. temperature ??
+		changing habitat suitability covariate, e.g. temperature ?? \textcolor{red}{[temperature would be very interesting and cover varying spatial fields]}
 	\item Comparison of population structure from i) commercial sampling,

### 2018-02-05 write_up/mixfishsim_ecolmod.tex
Manuscript edits and VAST fit to commercial data

@@
 \begin{frontmatter}
-\title{\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics}
+\title{\emph{MixFishSim}: highly resolved spatiotemporal simulations for
+	exploring mixed fishery dynamics}
 
-%%\title{A simulation framework for exploring spatio-temporal dynamics in mixed
+%%\title{A simulation framework for exploring spatiotemporal dynamics in mixed
 %%	fisheries}
@@
 
-Fishing exploits spatially and temporally hetergenous fish populations, using species-unselective 
-gear that can result in unintended, unwanted catch of low quota or
-protected species. Reducing these unwanted catches is crucial for biological
-and economic sustainability of `mixed fisheries' and implementation of an
-ecosystem approach to fishing. \\
+Fishing exploits spatially and temporally hetergenous fish populations, using
+species-unselective gear that can result in unintended, unwanted catch of low
+quota or protected species. Reducing these unwanted catches is crucial for
+biological and economic sustainability of `mixed fisheries' and implementation
+of an ecosystem approach to fishing. \\
 
-To implement effective spatial measures to reduce discards 
-a good understanding of spatio-temporal fishery dynamics is required. However,
-traditional scientific advice is limited by a lack of highly resolved knowledge of population distribution,
-movement and how fishers interact with different fish populations. This reflects that 
-data on fish location at high temporal and spatial resolutions is
-expensive and difficult to collect and therefore proxies inferred from either
-scientific surveys or commercial catch data are often used to model
-distributions, often with limited spatial and temporal resolution. \\
+To implement effective spatial measures to reduce discards a good understanding
+of spatiotemporal fishery dynamics is required. However, traditional
+scientific advice is limited by a lack of highly resolved knowledge of
+population distribution, movement and how fishers interact with different fish
+populations. This reflects that data on fish location at high temporal and
+spatial resolutions is expensive and difficult to collect and therefore proxies
+inferred from either scientific surveys or commercial catch data are often used
+to model distributions, often with limited spatial and temporal resolution. \\
 
-To understand how resolution impacts mixed fisheries inference, we develop a highly 
-resolved spatio-temporal simulation model incorporating:
-i) delay-difference population dynamics, ii) population movement using
-Gaussian Random Fields to simulate patchy, hetergenously distributed
-populations, and iii) fishery dynamics for multiple fleet characteristics based on
-targetting via correlated random walk movement and learned behaviour. \\
+To understand how resolution impacts mixed fisheries inference, we develop a
+highly resolved spatiotemporal simulation model incorporating: i)
+delay-difference population dynamics, ii) population movement using Gaussian
+Random Fields to simulate patchy, hetergenously distributed populations, and
+iii) fishery dynamics for multiple fleet characteristics based on targetting
+via correlated random walk movement and learned behaviour. \\
 
-We simulate 20 years of exploitation of the fish populations
-and use the results from the fishing model to draw inference on the underlying
-population structures. We compare this inference to i) a simulated fixed-site
-sampling design commonly used for fisheries monitoring purposes, and ii) the
-true underlying population structures input to the simulation, to establish the potential and limitations of
-fishery-dependent data - an inherently biased sampling method due to fisher's
-targeting- to provide a robust picture of spatio-temporal distributions. [We
-simulate a closure based on areas defined from commercial catch data and assess
-its effectiveness on reducing catches of a fish population.] \\
+We simulate 20 years of exploitation of the fish populations and use the
+results from the fishing model to draw inference on the underlying population
+structures. We compare this inference to i) a simulated fixed-site sampling
+design commonly used for fisheries monitoring purposes, and ii) the true
+underlying population structures input to the simulation, to establish the
+potential and limitations of fishery-dependent data - an inherently biased
+sampling method due to fisher's targeting- to provide a robust picture of
+spatiotemporal distributions. [We simulate a closure based on areas defined
+from commercial catch data and assess its effectiveness on reducing catches of
+a fish population.] \\
 
@@
 Fishers exploit fish populations that are heterogenously distributed in space
-and time with verying knowledge of species distributions using species-unselective
-fishing gear. Fisheries that catch an assemblage of species, known as mixed
-fisheries, when managed by single-species quotas can end up discarding
-overquota catch leading to overexploitation of fish populations. Reducing
-discarding is crucial to ensure biological and economic sustainability of
-fisheries and implementation of an ecosystem approach to fisheries. As such
-there is increasing interest in technical solutions such as gear and spatial
-closures as ways of avoiding discards.  \\
+and time with verying knowledge of species distributions using
+species-unselective fishing gear. Fisheries that catch an assemblage of
+species, known as mixed fisheries, when managed by single-species quotas can
+end up discarding overquota catch leading to overexploitation of fish
+populations. Reducing discarding is crucial to ensure biological and economic
+sustainability of fisheries and implementation of an ecosystem approach to
+fisheries. As such there is increasing interest in technical solutions such as
+gear and spatial closures as ways of avoiding discards.  \\
 
@@
 discards. However, its implementation is hampered by lack of knowledge of fish
-and fishery spatiotemporal \textcolor{red}{[use this spelling throughout]} dynamics and understanding of the scale at which
+and fishery spatiotemporal dynamics and understanding of the scale at which
 processes are important for management. Understanding the correct scale for
@@
 
-In order to understand challenges that face VMS-linked landings 
-to draw inference on the underlying population structure we develop a
-simulation model where population dynamics are highly-resolved in space and time and are 
-known rather than inferred from
-sampling or commercial catches. Population movement is driven by a random
-(diffusive) and directed (advective) process and we incorporate
-characterisation of a number of different fisheries exploiting four fish
-populations with different spatial and population demographics.\\
+In order to understand challenges that face VMS-linked landings to draw
+inference on the underlying population structure we develop a simulation model
+where population dynamics are highly-resolved in space and time and are known
+rather than inferred from sampling or commercial catches. Population movement
+is driven by a random (diffusive) and directed (advective) process and we
+incorporate characterisation of a number of different fisheries exploiting four
+fish populations with different spatial and population demographics.\\
 
@@
 and use the results from the fishing model to draw inference on the underlying
-population structures.  We compare this inference to: i) a stratified fixed-site sampling survey 
-design commonly used for fisheries monitoring
-purposes \textcolor{red}{[not sure if this is the fisheries-independent survey?]} and ii) the underlying population structures input to the simulation.\\
+population structures.  We compare this inference to: i) a stratified
+fixed-site sampling survey design commonly used for fisheries monitoring
+purposes, otherwise know as a fisheries-independent
+	survey, and ii) the underlying population structures input to the
+simulation.\\
 
@@
 \end{tikzpicture}
-\caption{Overview Schematic of simulation model \textcolor{red}{Make a table with all variables and symbols so that you can reference them in the caption.
-Expand the caption to give as much standalone info as possible, e.g., what's blue, what's green, arrow colours, etc.}}
+\caption{Overview Schematic of simulation model. The blue boxes indicate fleet
+	dynamics processes, the green boxes population dynamics processes while
+	the white boxes are the timesteps at which processes occur; $t$ = tow,
+	$tmax$ is the total number of tows, $y$ = year, $pop_{t}$ is time of
+	population movement, $day$ is a day timestep, $trip$ is a trip time
+	step. 
+	} 
 \label{fig:overview}
@@
 vessels for the population during the day, and $B$ the daily biomass for the
-species. \textcolor{red}{[link $F$ to effort and catchability - as I think we have F as an emergent property of the fleets rather than something we solve for (I could be wrong though!)]}\\
+species. \textcolor{red}{[link $F$ to effort and catchability - as I think we
+	have F as an emergent property of the fleets rather than something we
+	solve for (I could be wrong though!) - catch for a vessel is a product of
+	catchability and biomass, i.e. C = qB, but this catch is summed to
+	solve for F. So its both really]}\\
 
@@
 
-Recruitment is modelled through a function relating the mature biomass to recruits at time of
-recruitment. In \emph{mixfishsim}, it can be modelled either either as
-a stochastic Beverton-Holt stock-recruit form (\cite{Beverton1957}):
+Recruitment is modelled through a function relating the mature biomass to
+recruits at time of recruitment. In \emph{mixfishsim}, it can be modelled
+either either as a stochastic Beverton-Holt stock-recruit form
+(\cite{Beverton1957}):
 
@@
 \end{equation*}
-\textcolor{red}{[better to use lognormal variability to avoid negative recruitment events at low biomasses.]}
-Where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
-biomass (SSB) required to produce half the maximum, and $B$ current SSB; \\
+\textcolor{red}{[better to use lognormal variability to avoid negative
+	recruitment events at low biomasses.]} Where $\alpha$ is the maximum
+recruitment rate, $\beta$ the spawning stock biomass (SSB) required to produce
+half the maximum, and $B$ current SSB; \\
 
@@
 
-To simulate how fish populations might be distributed in space and
-time, we employed a Gaussian spatial process to model habitat suitability for
-each of the populations, with an advection-diffusion process to control how the
-populations moved over time. \textcolor{red}{[say why - balance between realism and practicalities of IBMs for the fish population]}\\
+To simulate how fish populations might be distributed in space and time, we
+employed a Gaussian spatial process to model habitat suitability for each of
+the populations, with an advection-diffusion process to control how the
+populations moved over time. \textcolor{red}{[say why - balance between realism
+	and practicalities of IBMs for the fish population]}\\
 
@@
 		Hab_{B}^2}{\sum\limits_{c=1}^{C}e^{-\lambda * d} \cdot
-		Hab^2}
+		Hab_{B}^2}
 \end{equation}
 
-Where $d_{AB}$ is the euclidean distance between cell $A$ and cell $B$, and
-$\lambda$ is a given rate of decay. \textcolor{red}{[this is great but do explain $H_{ab}$ and all variables immediately on presentation throughout.]}\\
+Where $d_{AB}$ is the euclidean distance between cell $A$ and cell $B$,
+$\lambda$ is a given rate of decay and $Hab_{B}^2$ is the squared index of
+habitat suitability for cell $B$.\\
 
@@
 previous time periods in past years, and choosing randomly from the top x \% of
-fishing events in value.  Simulation testing indicated that this learning increased the mean
-value of catches for the vessels, over just relying on the correlated random
-walk function.
+fishing events in value.  Simulation testing indicated that this learning
+increased the mean value of catches for the vessels, over just relying on the
+correlated random walk function.
 
@@
 
-Fishing locations within a trip are determined by a modified random walk process. A
-random walk type was chosen as it is the simplest assumption commonly used in ecology to describe animal
-movement which searching for homogeneously distributed prey about which there
-is uncertain knowledge. In a random walk, movement is a stochastic process
-through a series of steps that can either be equal in length or take some other
-functional form.  The direction of the random walk can be correlated, a
-characteristic known as `persistence', providing some overall location
-of directional movement \cite{Codling2008} or uncorrelated. \\
+Fishing locations within a trip are determined by a modified random walk
+process. A random walk type was chosen as it is the simplest assumption
+commonly used in ecology to describe animal movement which searching for
+homogeneously distributed prey about which there is uncertain knowledge. In a
+random walk, movement is a stochastic process through a series of steps that
+can either be equal in length or take some other functional form.  The
+direction of the random walk can be correlated, a characteristic known as
+`persistence', providing some overall location of directional movement
+\cite{Codling2008} or uncorrelated. \\
 
@@
 where $max_{k}$ is the maximum concentration value, $k$, and RefRev is
-parameterised as for $\beta_{3}$ in the step length function \textcolor{red}{[wonderful!]}.
+parameterised as for $\beta_{3}$ in the step length function.
 
@@
 
-To illustrate the capabilities on \emph{MixFishSim}, we investigate the influence of ...
-\textcolor{red}{[expand]}.
-To do so, we first set up with simulation to run for 20 years based on a 100 X 100 square grid,
-with five fleets of 20 vessels each and four fish populations. Fishing takes
-place four times a day per vessel and five days a week, while population
-movement is every week.
+To illustrate the capabilities on \emph{MixFishSim}, we investigate the
+influence of ... \textcolor{red}{[expand]}. To do so, we first set up with
+simulation to run for 20 years based on a 100 X 100 square grid, with five
+fleets of 20 vessels each and four fish populations. Fishing takes place four
+times a day per vessel and five days a week, while population movement is every
+week.
 
@@
 was parameterised dynamically so that vessels take smaller steps where the
-fishing location yields in the top X \textcolor{red}{[??]}quartile of the value available in that
-year (as defined per fleet in Table \ref{tab:2}). \\
+fishing location yields in the top X \textcolor{red}{[??]}quartile of the value
+available in that year (as defined per fleet in Table \ref{tab:2}). \\
 
@@
 		advective-diffusive process from the SPDE). Might need to
-		consider how to change this?  Could include a spatio-temporally
-		changing habitat suitability covariate, e.g. temperature ?? \textcolor{red}{[temperature would be very interesting and cover varying spatial fields]}
+		consider how to change this?  Could include a spatiotemporally
+		changing habitat suitability covariate, e.g. temperature ??
+		\textcolor{red}{[temperature would be very interesting and
+			cover varying spatial fields]}
 	\item Comparison of population structure from i) commercial sampling,

### 2018-02-05 write_up/VAST_fit/VAST_mixfishsim.R

@@ -1,0 +1,182 @@
+#############################################################
+#############################################################
+
+## VAST fit to simulated data from MixFishSim
+
+# 05/02/2018
+
+#############################################################
+#############################################################
+
+# Install TMB
+# Must be installed from: https://github.com/kaskr/adcomp
+
+# Install INLA
+# Must be installed from: http://www.r-inla.org/download
+
+#If Install geostatistical delta-GLMM package
+if(!"VAST" %in% installed.packages()[,1]) devtools::install_github("james-thorson/VAST")
+if(!"ThorsonUtilities" %in% installed.packages()[,1]) devtools::install_github("james-thorson/utilities")
+
+# Load libraries
+library(TMB)
+library(ThorsonUtilities)
+library(VAST)
+
+library(INLA)
+##INLA:::inla.dynload.workaround() ## Needed on older linux machines 
+
+library(MixFishSim)
+
+mod <- 'M0'
+run <- mod 
+
+# This is where all runs will be located
+DateFile  <- file.path('.','results',paste(Sys.Date(),'_',run,'/', sep = ""))
+
+dir.create(DateFile)
+
+###############
+# Settings
+###############
+
+#########################
+### VAST CPP version ###
+ # Version = "VAST_v2_8_0"
+Version = "VAST_v4_0_0"
+
+########################
+## Spatial settings ###
+########################
+  Method = c("Grid", "Mesh")[2]
+  n_x = c(10, 50, 100, 250, 500, 1000, 2000)[3] # Number of stations
+  Kmeans_Config = list( "randomseed"=1, "nstart"=100, "iter.max"=1e3 )     # Samples: Do K-means on trawl locs; Domain: Do K-means on extrapolation grid
+  strata.limits <- data.frame('STRATA'="All_areas") # Decide on strata for use when calculating indices
+  Region = "Mixtopia"# Determine region
+  Catch_units <- 'Kg'
+#  max_dist <- 50
+########################
+#### Model settings ####
+########################
+
[…]

### 2018-03-05 write_up/mixfishsim_ecolmod.tex
Manuscript changes to incorporate scenario runs

@@
 	\bar{R} = & \frac{(\alpha * B)}{(\beta + B)} \\
-	     R \sim & N[(\bar{R},\sigma^2)]
+	     R \sim & \log N[(\log(\bar{R}),\log(\sigma^2))]
 	\end{split}
 \end{equation*}
-\textcolor{red}{[better to use lognormal variability to avoid negative
-	recruitment events at low biomasses.]} Where $\alpha$ is the maximum
-recruitment rate, $\beta$ the spawning stock biomass (SSB) required to produce
-half the maximum, and $B$ current SSB; \\
+Where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
+biomass (SSB) required to produce half the maximum, $B$ current SSB and
+$\sigma^2$ the variability in the recruitment due to stochastic
+processes. \\
 
@@
 	\bar{R} = & B * e^{(\alpha - \beta * B)} \\	
-   	     R \sim & N[(\bar{R},\sigma^2)]
+   	     R \sim & \log N[(\log(\bar{R}),\log(\sigma^2))]
 	\end{split}
@@
 the populations, with an advection-diffusion process to control how the
-populations moved over time. \textcolor{red}{[say why - balance between realism
-	and practicalities of IBMs for the fish population]}\\
+populations moved over time with a moving temperature covariate to capture
+temporal dependencies. This was intended to balance realism in population
+movement, capturing the main directed and random processes, and practicality of
+modelling the population rather than individual fish. \\
 
@@
 
+The temperature field is simulated to be on a gradient from a South-Westerly to
+North-Easterly direction, with temperature in each cell changing gradually on a
+week-by-week basis so that initially high temperature areas cycle to lower
+temperatures and low temperature areas vice versa. Each population is assigned
+a thermal tolerance with mean, $\mu$ and variance, $\sigma^2$ so that each cell
+and population temperature suitability is defined that:
+
+\begin{equation}
+	Tol_{c, p} = \frac{1}{ \sqrt (2\pi \cdot \sigma^2_{p})} \cdot \exp(-
+		\frac{(T_{c} -
+		\mu_{p})^2}{2 \cdot \sigma^2_{p}} )	
+\end{equation}
+
+Where $Tol_{c,p}$ is the tolerance of population $p$ in cell $c$, $T_{c}$ is
+the temperature in the cell and $\mu$ and $\sigma^2$ the mean and standard
+deviation of the population temperature tolerance. \\
+
 In the simulation model, the habitat for each of the populations is generated
@@
 location, and subsequently moves according to a probabilistic distribtion based
-on habitat suitability and distance from current cell.
+on habitat suitability, temperature and distance from current cell.
 
@@
 	Pr(B | A) = \frac{e^{-\lambda * d_{AB}} \cdot
-		Hab_{B}^2}{\sum\limits_{c=1}^{C}e^{-\lambda * d} \cdot
-		Hab_{B}^2}
+		(Hab_{B}^2 \cdot Tol_{B,wk})}{\sum\limits_{c=1}^{C}e^{-\lambda * d} \cdot
+		(Hab_{B}^2 \cdot Tol_{B,wk})}
 \end{equation}
@@
 Where $d_{AB}$ is the euclidean distance between cell $A$ and cell $B$,
-$\lambda$ is a given rate of decay and $Hab_{B}^2$ is the squared index of
-habitat suitability for cell $B$.\\
+$\lambda$ is a given rate of decay, $Hab_{B}^2$ is the squared index of habitat
+suitability for cell $B$ and $Tol_{B,wk}$ the temperature tolerance for the
+cell in week $wk$; population index, $p$ has been dropped for simplicity.\\
 
@@
 
-\subsection{Simulation settings}
-
-To illustrate the capabilities on \emph{MixFishSim}, we investigate the
-influence of ... \textcolor{red}{[expand]}. To do so, we first set up with
-simulation to run for 20 years based on a 100 X 100 square grid, with five
-fleets of 20 vessels each and four fish populations. Fishing takes place four
-times a day per vessel and five days a week, while population movement is every
-week.
-
 \subsection{Population parameterisation}
@@
 parameters for all populations (Q = 1).
+
+\subsection{Simulation settings}
+
+To illustrate the capabilities on \emph{MixFishSim}, we investigate the
+influence of the temporal and spatial resolution of different data sources on
+the reduction in catches of a population given spatial closures. To do so, we
+first set up with simulation to run for 10 years based on a 100 X 100 square
+grid, with five fleets of 20 vessels each and four fish populations. Fishing
+takes place four times a day per vessel and five days a week, while population
+movement is every week. \\
+
+We allow the simulation to run unrestricted for 5 years, and subsequently close
+areas for the last 5 years of the simulation based on data (either derived from
+the commercial catches, fisheries-independent survey or the 'real population')
+used at different spatial and temporal scales.
+
+The following steps are undertaken to determine closures:
+
+i. Extract data source
+ii. Aggregate according to resolution
+iii. Interpolate across entire area at desired resoltion
+iv. Close top 5 \% of areas
+
+\begin{table}[!ht]
+\caption{Closure scenarios}
+\begin{tabular}{ p{4cm } p{4cm} p{4cm}}
+	\hline
+	Data type & Temporal resolution & Spatial resolution \\
+	\hline
+	Commercial logs, survey data, real population & weekly, monthly, years
+	& 1, 2, 5, 10 \\ 
+\end{tabular}
+\label{tab:x}
+\end{table}
+
+ABOVE WOULD BE BETTER AS SOME SORT OF GRAPHICAL ILLUSTRATION OF AGGREGATION
+CONSEQUENCES, E.G. 
+COMMERCIAL DATA SPARSITY, SURVEY DATA CONSISTENCY, REAL
+POPULATION IS ALL.
+
+TEMPORALLY VARYING PROPORTIONS DIVIDED BY WEEK, MONTH, YEAR
+
+CELLS AGGREGATED ACCORDING TO SIMULATION EXAMPLES !!!
+
+Total 56 scenarios.
 

### 2018-03-05 analysis/Plot_Bio.R

@@ -1,17 +1,29 @@
 
-load('Scenario_1_.RData')
+library(MixFishSim)
+
+Run <- 1
+
+load(file.path('.', 'Scenario_runs', paste0('Scenario_',Run,'_.RData')))
 
 pop <- res[["pop_bios"]]
+plot_pop_summary(res, timestep = "annual")
+
+logs <- combine_logs(res[["fleets_catches"]])
+
+plot_catch_comp(gran = c(1), logs = logs, fleets = 1:5,
+       vessels = 1:20, trips = 1:60, years = 1:5, cluster_plot = FALSE , 
+       cluster_k = 5, scale_data = FALSE)
+
 
 
 ## Simple plot of distribution changes over time
 
-png(file = file.path("plots", "pop_dist.png"), width = 1600, height = 1600)
+png(file = file.path("..", "tests","plots", "pop_dist.png"), width = 1600, height = 1600)
 par(mfrow=c(4,4), mar = c(1,1,1,1))
 
 for(j in round(seq.int(1,52,length.out = 4),0)) {
 for(i in 1:4) {
-image(seq_len(100), seq_len(100), pop[[10,j]][[i]], col = terrain.colors(100))
+image(seq_len(100), seq_len(100), pop[[9,j]][[i]], col = terrain.colors(100))
 if(i==1) {text(x = 9, y = 94, labels = paste("t =",j), cex= 2, font = 2)}
 if(j==1) {text(x = 92, y = 94, labels = paste("Pop ",i), cex = 2, font = 2)}
 }
@@ -27,14 +39,14 @@ catch_comp <- matrix(NA, nc = 52, nr = 4)
 for(i in 1:4) {
 	for(j in 1:52) {
 		
-		B <- pop[[10,j]][[i]][55,42] 
-		allB <- lapply(pop[[10,j]], function(x) x[55,42])
+		B <- pop[[1,j]][[i]][50,82] 
+		allB <- lapply(pop[[1,j]], function(x) x[50,82])
 		allB <- Reduce("+", allB)
 
     catch_comp[i,j] <- B / allB 	}
 }
 
-png(file.path("plots", "Proportion_in_cell.png"), width = 800, height = 800)
+png(file.path("..","tests" , "plots", "Proportion_in_cell.png"), width = 800, height = 800)
 matplot(t(catch_comp), type = "l", ylab = "Proportion of population in cell")
[…]

### 2018-03-05 analysis/Plots.R

@@ -7,8 +7,8 @@ library(MixFishSim)
 
 load('Common_Params.RData')
 
-Run <- 1
-load(paste0("Scenario_", Run, "_.RData"))
+Run <- 43
+load(file.path('Scenario_runs', paste0("Scenario_", Run, "_.RData")))
 
 plot_pop_summary(res, timestep = "annual", save = FALSE)
 

### 2018-03-05 analysis/Plots_Combined.R

@@ -9,7 +9,6 @@ load('scenarios.RData')
 load('Common_Params.RData')
 
 runs <- 1:56
-runs <- runs[!runs %in% c(44)]  ## These didn't work..
 
 for(i in runs) {
 load(file.path('Scenario_runs', paste('Scenario', i, '.RData', sep = "_")))

### 2018-03-14 analysis/KillerFigure.R
Update to plots

@@ -157,7 +157,7 @@ cols <- c("red", "blue", "purple", "green")
 #par(mar = c(0,0,0,0), pty = 'm')
 basemap(xlim = c(0,100), ylim = c(0,100), xlab = "", ylab = "", bg = "white", xaxt = 'n', yaxt = "n")
 draw.barplot2D(catch_comp[[1]]$x,catch_comp[[1]]$y,z = catch_comp[[1]]$z, width = gran,
-	       height = gran, xlab = "", ylab = "", col = cols, lwd.frame = 0.1, col.frame = "white")
+	       height = gran, xlab = "", ylab = "", col = cols, lwd.frame = 0, col.frame = "white")
 
 
 }
@@ -190,8 +190,9 @@ plot_comp(gran = 1, dataIn = dataIn)
 
 ##############################################
 ## Setting out the plot
-setEPS()
-postscript('Data_Aggregation_space.eps', width = 8 * 2, height = 8 * 3, bg = "white")
+##setEPS()
+##postscript('Data_Aggregation_space.eps', width = 8 * 2, height = 8 * 3, bg = "white")
+pdf('Data_Aggregation_space.pdf', width = 8 * 2, height = 8 * 3, bg = "white")
 
 par(oma = c(12,2,12,12), mar = c(0,0,0,0), mfrow = c(4,3))
 
@@ -246,8 +247,8 @@ logs_wk_mn <- unique(paste(logs$month, logs$week, sep = "_"))
 ## Some measure of temporal change in distribtions
 plot_temp <- function(timestep = NULL, basis = NULL) {
 
-xs <- 1:100
-ys <- 1:100
+xs <- 60:80
+ys <- 20:40
 
 ## weekly 
 if(timestep == 'week') {
@@ -284,7 +285,7 @@ dataPlot[,4:7][is.na(dataPlot[,4:7])] <- 0
 dataPlot <- dataPlot[order(dataPlot$year, dataPlot$month, dataPlot$week),]
 
 cols <- c("red", "blue", "purple", "green")
-barplot(t(dataPlot[,4:7]), names.arg = rep(paste(""), nrow(dataPlot)), col = cols)
+barplot(t(dataPlot[,4:7]), names.arg = rep(paste(""), nrow(dataPlot)), col = cols, border = NA)
 
 }
 
@@ -320,7 +321,7 @@ dataPlot[,3:6][is.na(dataPlot[,3:6])] <- 0
[…]

### 2018-03-14 analysis/Plot_activity.R

@@ -1,0 +1,45 @@
+
+library(MixFishSim)
+library(dplyr)
+library(ggplot2)
+
+
+load('Common_Params.RData')
+
+#Run <- 9
+Run <- 10 
+load(file.path('Scenario_runs', paste0("Scenario_", Run, "_.RData")))
+
+
+logs <- as.data.frame(combine_logs(res[["fleets_catches"]]))
+
+logs_b <- filter(logs, year %in% 2:4)
+#logs_b <- filter(logs, year %in% 2:4, week == 4)
+logs_b$time <- 'before'
+#logs_a <- filter(logs, year %in% 8:10, week == 4)
+logs_a <- filter(logs, year %in% 8:10)
+logs_a$time <- 'after'
+
+logs <- rbind(logs_a, logs_b)
+rm(logs_a, logs_b)
+
+## Summarise number of pings per square
+
+logs <- logs %>% group_by(time, x, y, month) %>% summarise(n = n())
+
+## Now to plot with geom_tile
+
+ggplot(logs, aes(x = x, y = y)) + geom_tile(aes(fill = log(n))) + facet_wrap(month ~time) + 
+	scale_fill_gradient2(low = "yellow", mid = "orange", high = "darkred")
+
+
+logs_diff <- reshape2::dcast(logs, x + y + month ~ time, value.var = "n")
+logs_diff[is.na(logs_diff)] <- 0
+
+logs_diff$difference <- logs_diff$after - logs_diff$before  
+
+ggplot(logs_diff, aes(x = x, y = y)) + geom_tile(aes(fill = difference)) + 
+	scale_fill_gradient2(low = "darkgreen", midpoint = 0, high = "red") +
+	facet_wrap(~month)
+
+

### 2018-03-15 write_up/mixfishsim_ecolmod.tex
Update to plots
Updated figure

@@
 the commercial catches, fisheries-independent survey or the 'real population')
-used at different spatial and temporal scales.
+used at different spatial and temporal scales. \\
 
@@
 
-i. Extract data source
-ii. Aggregate according to resolution
-iii. Interpolate across entire area at desired resoltion
-iv. Close top 5 \% of areas
+\begin{enumerate}
+	\item Extract data source
+	\item Aggregate according to resolution
+	\item Interpolate across entire area at desired resoltion
+	\item Close top 5 \% of areas
+\end{enumerate}
 
-\begin{table}[!ht]
-\caption{Closure scenarios}
-\begin{tabular}{ p{4cm } p{4cm} p{4cm}}
-	\hline
-	Data type & Temporal resolution & Spatial resolution \\
-	\hline
-	Commercial logs, survey data, real population & weekly, monthly, years
-	& 1, 2, 5, 10 \\ 
-\end{tabular}
-\label{tab:x}
-\end{table}
-
-ABOVE WOULD BE BETTER AS SOME SORT OF GRAPHICAL ILLUSTRATION OF AGGREGATION
-CONSEQUENCES, E.G. 
-COMMERCIAL DATA SPARSITY, SURVEY DATA CONSISTENCY, REAL
-POPULATION IS ALL.
-
-TEMPORALLY VARYING PROPORTIONS DIVIDED BY WEEK, MONTH, YEAR
-
-CELLS AGGREGATED ACCORDING TO SIMULATION EXAMPLES !!!
-
-Total 56 scenarios.
+In total 56 closure scenarios were run which represent combinations of: three
+data types; commercial logbook data, survey data and 'real population', three
+temporal resolutions; weekly, monthly and yearly closures, and four spatial
+resolutions; 1 x 1 grid, 5 x 5 grid, 10 x 10 grid and 20 x 20 grid. Survey
+closures were on an annual basis, as the most temporally resolved survey data
+available.
 
@@
 \begin{figure}[!ht]
+	\includegraphics[width =\linewidth]{../analysis/Data_Aggregation_space}
+	\caption{Data aggregation at different spatial resolutions}
+	\label{fig:0a}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{../analysis/Data_Aggregation_time}
+	\caption{Data aggregation at different temporal resolutions}
+	\label{fig:0b}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{../analysis/Overview_plot_highPop}
+	\caption{Comparison of closure scenarios}
+	\label{fig:0c}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{../analysis/F_trends}
+	\caption{Comparison of closure scenarios - F trends}
+	\label{fig:0d}
+\end{figure}
+
+// 
+//Supplementary
+//
+
+\begin{figure}[!ht]
 	\includegraphics[width = \linewidth]{../tests/plots/habitat}

### 2018-03-15 analysis/Plots_Combined.R

@@ -65,13 +65,9 @@ results_df_an2 <- combined_pop %>% filter(metric != "Bio") %>%
 
 combined_pop_an <- rbind(results_df_an1, results_df_an2) 
 
-pl <- c(2,5)
-
-ggplot(filter(combined_pop_an, scenario %in% pl, metric ==  "F"), aes(x = year, y = data)) +
-	geom_point(aes(colour = factor(scenario)))  + 
-	facet_wrap(~pop) + expand_limits(y= 0)
-
-## Averages years 1 - 4 and 5-10, then the difference per scenario
+#####################################################################
+## Averages years 1 - 4 and 5-10, then the difference per scenario ##
+#####################################################################
 
 avg2_4  <- combined_pop_an %>% filter(year %in% 2:4) %>% 
 	group_by(scenario, pop, metric) %>% summarise(value = mean(data, na.rm = T))
@@ -85,13 +81,10 @@ colnames(combined)[4:5] <- c("before", "after")
 
 combined$diff <- ((combined$after - combined$before) / combined$before)  * 100
 
-ggplot(combined, aes(x = scenario, y = diff)) + geom_point() + facet_wrap(pop ~ metric)
-
-val_ref <- range(combined$diff[combined$metric == "F" & combined$pop=='spp_1']) 
-
-combined[combined$diff %in% val_ref,]
-
+######################
 ## Label up scenarios
+######################
+
 load('scenarios.RData')
 sc <- sc[sc$scenario %in% runs,]
 
@@ -108,3 +101,29 @@ ggplot(filter(combined, basis == 'high_pop', metric == "F"), aes(x = data_type, 
 	scale_shape_discrete(solid = F)
 
 ggsave('Overview_plot_highPop.png', width = 12, height = 4)
+
+###########################
+### 
+### Plot of all scenarios
+############################
+
+## Add scenario labels
+
+combined_pop_an <- as.data.frame(combined_pop_an)
+
+sc$combined 		   <- paste(sc$basis, sc$data_type, sc$timescale, sc$resolution, sep = "_")
+combined_pop_an$combined   <- sc$combined[match(combined_pop_an$scenario, sc$scenario)]
+combined_pop_an$basis      <- sc$basis[match(combined_pop_an$scenario, sc$scenario)]
+combined_pop_an$timescale  <- sc$timescale[match(combined_pop_an$scenario, sc$scenario)]
[…]

### 2018-03-16 write_up/Supplementary.tex
Updates to manuscript and developments on results

--- 2018-02-05 write_up/mixfishsim_ecolmod.tex
@@
 \documentclass[review]{elsarticle}
+\usepackage{graphicx}
+\usepackage{hyperref}
 
-\usepackage{lineno,hyperref}
-\usepackage[utf8]{inputenc}
-\usepackage{graphicx}
-\usepackage{amsfonts}
-\usepackage{mathtools}
-\usepackage{tikz}
-\usetikzlibrary{shapes,arrows,chains,calc}
+%% To allow supplementary table and figure numbering
+%% http://bytesizebio.net/2013/03/11/adding-supplementary-tables-and-figures-in-latex/
 
-% Set up a few colours for tikz figure
-\colorlet{lcfree}{green}
-\colorlet{lcnorm}{blue}
-\colorlet{lccong}{red}
-
-\modulolinenumbers[1]
+\newcommand{\beginsupplement}{%
+		        \setcounter{table}{0}
+		        \renewcommand{\thetable}{S\arabic{table}}%
+		        \setcounter{figure}{0}
+		        \renewcommand{\thefigure}{S\arabic{figure}}%
+			     }
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%
-%% Elsevier bibliography styles
-%%%%%%%%%%%%%%%%%%%%%%%
-%% To change the style, put a % in front of the second line of the current style and
-%% remove the % from the second line of the style you would like to use.
-%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Numbered
-%\bibliographystyle{model1-num-names}
-%% Numbered without titles
-%\bibliographystyle{model1a-num-names}
-%% Harvard
-%%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
-%% Vancouver numbered
-%\usepackage{numcompress}\bibliographystyle{model3-num-names}
-%% Vancouver name/year
-%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
-%% APA style
-%%\bibliographystyle{model5-names}\biboptions{authoryear}
-%% AMA style
-%\usepackage{numcompress}\bibliographystyle{model6-num-names}
-%% `Elsevier LaTeX' style
-\bibliographystyle{elsarticle-num}
-%%%%%%%%%%%%%%%%%%%%%%%
+\title{MixFishSim: Supplementary Figures and Tables}
 
@@
 
-\begin{frontmatter}
-\title{\emph{MixFishSim}: highly resolved spatiotemporal simulations for
-	exploring mixed fishery dynamics}
-
-%%\title{A simulation framework for exploring spatiotemporal dynamics in mixed
-%%	fisheries}
-
-%% Group authors per affiliation:
-\author[1,2]{Paul J. Dolder\corref{c}}
-\cortext[c]{Corresponding author}
-\ead{paul.dolder@gmit.ie}
-
-\author[1]{Cóilín Minto}
-\author[3]{Jean-Marc Guarini}
-\author[4]{Jan Jaap Poos}
-
-\address[1]{Galway-Mayo Institute of Technology (GMIT), Dublin Road, Galway,
-	Ireland} 
-\address[2]{Centre for Environment, Fisheries and Aquaculture Science (Cefas),
-	Pakefield Road, Lowestoft, UK}
-\address[3]{Université Pierre et Marie Curie, 4 Place Jussieu, 75005 Paris,
-	France}
-\address[4]{Wageningen Marine Research, Haringkade 1 1976 CP IJmuiden,
-	Netherlands}
-
-\begin{abstract}
-\textcolor{gray}{[Guidance: A concise and factual abstract is required. The abstract 
-should state briefly the purpose of the research, the principal results and
-major conclusions. An abstract is often pnresented separately from the article,
-so it must be able to stand alone. For this reason, References should be
-avoided, but if essential, then cite the author(s) and year(s). Also,
-non-standard or uncommon abbreviations should be avoided, but if essential they
-must be defined at their first mention in the abstract itself.  Graphical
-abstract: Although a graphical abstract is optional, its use is encouraged as
-it draws more attention to the online article. The graphical abstract should
-summarize the contents of the article in a concise, pictorial form designed to
-capture the attention of a wide readership. Graphical abstracts should be
-submitted as a separate file in the online submission system. Image size:
-Please provide an image with a minimum of 531 X 1328 pixels (h X w) or
-proportionally more. The image should be readable at a size of 5 x 13 cm using
-a regular screen resolution of 96 dpi.  Preferred file types: TIFF, EPS, PDF or
-MS Office files.] \\}
-
-Fishing exploits spatially and temporally hetergenous fish populations, using
-species-unselective gear that can result in unintended, unwanted catch of low
-quota or protected species. Reducing these unwanted catches is crucial for
-biological and economic sustainability of `mixed fisheries' and implementation
-of an ecosystem approach to fishing. \\
-
-To implement effective spatial measures to reduce discards a good understanding
-of spatiotemporal fishery dynamics is required. However, traditional
-scientific advice is limited by a lack of highly resolved knowledge of
-population distribution, movement and how fishers interact with different fish
-populations. This reflects that data on fish location at high temporal and
-spatial resolutions is expensive and difficult to collect and therefore proxies
-inferred from either scientific surveys or commercial catch data are often used
-to model distributions, often with limited spatial and temporal resolution. \\
-
-To understand how resolution impacts mixed fisheries inference, we develop a
-highly resolved spatiotemporal simulation model incorporating: i)
-delay-difference population dynamics, ii) population movement using Gaussian
-Random Fields to simulate patchy, hetergenously distributed populations, and
-iii) fishery dynamics for multiple fleet characteristics based on targetting
-via correlated random walk movement and learned behaviour. \\
-
-We simulate 20 years of exploitation of the fish populations and use the
-results from the fishing model to draw inference on the underlying population
-structures. We compare this inference to i) a simulated fixed-site sampling
-design commonly used for fisheries monitoring purposes, and ii) the true
-underlying population structures input to the simulation, to establish the
-potential and limitations of fishery-dependent data - an inherently biased
-sampling method due to fisher's targeting- to provide a robust picture of
-spatiotemporal distributions. [We simulate a closure based on areas defined
-from commercial catch data and assess its effectiveness on reducing catches of
-a fish population.] \\
-
-We conclude that... \\
-
-[233 words]
-
-\end{abstract}
-
-\begin{keyword}
-Some\sep keywords \sep here. Max 6 
-\MSC[2010] 00-01\sep  99-00
-\end{keyword}
-
-\end{frontmatter}
-
-\linenumbers
-
-\section{Introduction}
-
-\textcolor{gray}{[Guidance:: State the objectives of the work and provide an 
-adequate background, avoiding a detailed literature survey or a summary of the
-results.] \\}
-
-Fishers exploit fish populations that are heterogenously distributed in space
-and time with verying knowledge of species distributions using
-species-unselective fishing gear. Fisheries that catch an assemblage of
-species, known as mixed fisheries, when managed by single-species quotas can
-end up discarding overquota catch leading to overexploitation of fish
-populations. Reducing discarding is crucial to ensure biological and economic
-sustainability of fisheries and implementation of an ecosystem approach to
-fisheries. As such there is increasing interest in technical solutions such as
-gear and spatial closures as ways of avoiding discards.  \\
-
-Use of spatial management as a tool has been proposed as a method to reduce
-discards. However, its implementation is hampered by lack of knowledge of fish
-and fishery spatiotemporal dynamics and understanding of the scale at which
-processes are important for management. Understanding the correct scale for
-spatial management is crucial in order to implement measures at a resolution
-that ensures effective management\cite{Dunn2016} while minimising economic
-impact. For example, a scale that promotes species avoidance for vulnerable or
-low quota species while allowing continuance of sustainable fisheries for
-available quota species. \\
-
-Ensuring measures are implemented at an appropriate scale has been a challenge
-in the past that has led to ineffectual measures with unitended consequences
-such as limited impact towards the management objective or increased benthic
-impact on previously unexploited areas (e.g. the cod closure in the North
-Sea\cite{Rijnsdorp2001,Dinmore2003}). Since then more refined spatial
-information has become available through the combination of logbook and Vessel
-Monitoring System (VMS) data\cite{Lee2010, Bastardie2010, Gerritsen2012,
-	Mateo2016} and more real-time spatial management has been possible 
-	(e.g. \cite{Holmes2011}). Such information is, however, patchy and
-derived from an inherently biased sampling programme (i.e. targeted fishing).
-Further, fishers generally only recorded landings (not catch) on a daily basis.
-This leads to questions about the validity of inference that can be drawn from
-landings data assigned to VMS activity pings. \\
-
-In order to understand challenges that face VMS-linked landings to draw
-inference on the underlying population structure we develop a simulation model
-where population dynamics are highly-resolved in space and time and are known
-rather than inferred from sampling or commercial catches. Population movement
-is driven by a random (diffusive) and directed (advective) process and we
-incorporate characterisation of a number of different fisheries exploiting four
-fish populations with different spatial and population demographics.\\
-
-Using our model we simulate 20 years of exploitation of the fish populations
-and use the results from the fishing model to draw inference on the underlying
-population structures.  We compare this inference to: i) a stratified
-fixed-site sampling survey design commonly used for fisheries monitoring
-purposes, otherwise know as a fisheries-independent
-	survey, and ii) the underlying population structures input to the
-simulation.\\
-
-[Could fit a geostatistical model (e.g. VAST) to the fisheries-dependent and
-fisheries-independent data, though may be overkill...] \\
-
-We simulate a fishery closure to protect one species based on the
-fishery-dependent inferred distributions at a spatial and temporal scale
-typical in fisheries management, and assess a theoretical "benefit" to the
-population, and effect on the other three populations. Further, we extend our
-analysis to a range of spatial and temporal scales to assess the impact of
-these processes on the success of the management measure. \\
-
-\section{Materials and Methods}
-
-\textcolor{gray}{[Guidance: Provide sufficient details to allow the work to be
-reproduced by an independent researcher. Methods that are already published
-should be summarized, and indicated by a reference.  If quoting directly from a
-previously published method, use quotation marks and also cite the source. Any
-modifications to existing methods should also be described.] \\ }
-
-We develop a simulation model with a modular event-based approach, where
-modules are implemented on independent time-scales appropriate to capture the
-characteristic of the process modelled (Figure 1). The fishing model operated on a
-tow-by-tow basis, while population dynamics (fishing and natural mortality,
-growth) operate on a daily time-step.  Population movement occurs on a
-weekly time-step, while recruitment occurs periodcally each year for a set
-time period (e.g. 3 weeks) at at specified point individual to a species. The
-simulation framework is implemented in the statistical software package R
-\cite{RCoreTeam2017}; available as an R package from the authors github
-(\url{www.github.com/pdolder/MixFishSim}).\\
-
-Here we describe each of the model components; 1)
-Population dynamics, 2) Recruitment dynamics, 3) Population movement, 4)
-fishery dynamics.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Overview schematic  
-\begin{figure}[!ht]
-	\hspace{-4em}
-\begin{tikzpicture}[%
-    >=triangle 60,              % Nice arrows; your taste may be different
-    start chain=going below,    % General flow is top-to-bottom
-    node distance=8mm and 60mm, % Global setup of box spacing
-    every join/.style={norm},   % Default linetype for connecting boxes
-    scale=0.9,
-    every node/.style={scale=0.8}]                 
-    \label{fig:model}
-    % ------------------------------------------------- 
-% A few box styles 
-% <on chain> *and* <on grid> reduce the need for manual relative
-% positioning of nodes
-\tikzset{
-  base/.style={draw, on chain, on grid, align=center, minimum height=4ex},
-  proc/.style={base, rectangle, text width=8em},
-  test/.style={base, rectangle, text width=5em},
-  term/.style={proc, rounded corners},
-  % coord node style is used for placing corners of connecting lines
-  coord/.style={coordinate, on chain, on grid, node distance=6mm and 25mm},
-  % nmark node style is used for coordinate debugging marks
-  nmark/.style={draw, cyan, circle, font={\sffamily\bfseries}},
-  % -------------------------------------------------
-  % Connector line styles for different parts of the diagram
-  norm/.style={->, draw, lcnorm},
-  free/.style={->, draw, lcfree},
-  cong/.style={->, draw, lccong},
-  it/.style={font={\small\itshape}}
-}
-% -------------------------------------------------
-% Start by placing the nodes in the middle
-\node [proc, densely dotted, it] (p0) {start};
-% Use join to connect a node to the previous one 
-\node [term, join, fill=lcnorm!25]      {Choose random location to fish};
-\node [term, join, fill=lcfree!25] (p1){Sample catch};
-\node [test, densely dotted] (t1) {if $y > y-1$};
-\node [test, join, densely dotted] (t2) {if $pop_{t}$ != $pop_{t-1}$};
-\node [test, join, densely dotted] (wk) {if $day_{t}$ != $day_{t-1}$};
-\node [test, join, densely dotted] (t3) {if $trip_{t}$ != $trip_{t-1}$};
-\node [term, join, fill=lcnorm!25]  (p2) {Correlated Random Walk};
-\node [term, join, fill=lcnorm!25]  (p3) {Choose new fishing location};
-\node [proc, densely dotted, join, it] (p7) {end};
-
-% Right nodes
-\node [proc, fill=lcfree!25, right=of p1] (p4) {Popn depletion};
-\node [proc, fill=lcfree!25, right=of t1] (p5) {Popn Recruitment};
-\node [proc, fill=lcfree!25] (p6) {Popn movement};
-\node [proc, fill=lcfree!25, right=of wk] (wk1) {Growth and natural
-	mortality};
-
-% left nodes
-\node [test, fill=lcnorm!25, left=of t3] (t4) {Use past fishing locations};
-
-% -------------------------------------------------
-% A couple of boxes have annotations
-\node [below=of p0, it, yshift=1.5em,xshift=-3em] {$t==1$};
-\node [right=30mm of p3, it] {$1 < t < t_{max}$};
-\node [below=of p3, it,xshift=-3em, yshift=1.5em] {$t == t_{max}$};
-
-% -------------------------------------------------
-% First, the straight north-south connections. In each case, we first
-% draw a path with a (consistently positioned) annotation node, then
-% we draw the arrow itself.
-  \draw [*->,lcfree!50] (p1) -- (p4);
-\path (t1) to node [near start, xshift=2em, yshift=0.5em] {$y$} (p5); 
-  \draw [*->,lcfree!50] (t1) -- (p5);
-\path (t2) to node [near start, xshift=2em, yshift=0.5em] {$y$} (p6); 
-  \draw [*->,lcfree!50] (t2) -- (p6);
-\path (t3) to node [near start, xshift=-3em, yshift=0.5em] {$y$} (t4); 
-  \draw [*->,lccong!50] (t3) -- (t4);
-\path (wk) to node [near start, xshift=2em, yshift=0.5em] {$y$} (wk1); 
-  \draw [*->,lcfree!50] (wk) -- (wk1);
-
-% left to right paths
-\path (t1) to node [near start, yshift=-0.2em] {$n$} (t2) ;  
-\path (t2) to node [near start, yshift=0.8em] {$n$} (t3) ;  
-\path (wk) to node [near start, yshift=-0.2em] {$n$} (t3) ;  
-\path (t3) to node [near start, yshift=-0.3em] {$n$} (p2) ;
-
-% ------------------------------------------------- 
-% the twisty connectors. Again, we place the annotation
-% first, then draw the connector
-
-\node [coord, left=of p3] (c1)  {};  
-\draw [*->,lccong!50] (t4.south) -- (c1) |- (p3);
-
-\node[coord, below=of p4] (c2) {};
-\node[coord, above=of t1] (c3) {};
-\draw [-<,lcfree!50] (p4.south) -- (c2) |- (c3) |- (t1.north);
-
-\node[coord, below=of p5] (c4) {};
-\draw [->,lcfree!50] (p5.south) -- (c4) |- ($(t2.east) + (0,0.5)$);
-
-\node[coord, below=of p6] (c71) {};
-\draw [->,lcfree!50] (p6.south) -- (c71) |- ($(wk.east) + (0,0.56)$);
-
-\node[coord, below=of wk1] (c7) {};
-\draw [->,lcfree!50] (wk1.south) -- (c7) |- ($(t3.east) + (0,0.3)$);
-
-% -------------------------------------------------
-% A last flourish which breaks all the rules
-\draw [->,purple, dotted, thick, shorten >=1mm]
-  (p3.south) -- ++(5mm,-3mm)  -- ++(87mm,0mm) 
-  |- node [black, near end, yshift=1.75em, it]
-    {} ($(p1.north) + (0,0.3)$);
-% -------------------------------------------------
-\end{tikzpicture}
-\caption{Overview Schematic of simulation model. The blue boxes indicate fleet
-	dynamics processes, the green boxes population dynamics processes while
-	the white boxes are the timesteps at which processes occur; $t$ = tow,
-	$tmax$ is the total number of tows, $y$ = year, $pop_{t}$ is time of
-	population movement, $day$ is a day timestep, $trip$ is a trip time
-	step. 
-	} 
-\label{fig:overview}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Population dynamics}
-
-The basic population level processes are simulated using a modified two-stage
-Deriso-Schnute delay difference model \cite{Deriso1980, Schnute1985,
-	Dichmont2003} occurring at a daily time-step. Here, population biomass
-growth and depletion for pre-recruits and fish recruited to the fishery are
-modelled separately as a function of previous recruited biomass, intrinsic
-population growth and recruitment:
-
-\begin{equation*}
-	\begin{split}
-	B_{y,d+1} = &\\
-	& (1 + \rho) B_{y,d} \cdot e^{-Z_{y,d}} - \rho \cdot e^{-Z_{y,d}} \hspace{2.9cm}
-	\times \\  
-	& (B_{y,d-1} \cdot e^{-Z_{y,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot R_{\tilde{y}(y,d-1)})
-	\hspace{0.4cm} + \\
-	& Wt_{R} \cdot \alpha_{d} \cdot R_{\tilde{y}(y,d)} 
-	\end{split}
-\end{equation*}
-
-where $\rho$ is Brody's coefficient, shown to be approximately equal to
-$exp(-K)$, where $K$ is the growth rate from a von bertalanffy logistic growth
-model \cite{Schnute1985}. $Wt_{R-1}$ is the weight of fish prior to
-recruitment, while $Wt_{R}$ is the recruited weight. $\alpha_{d}$ represents
-the proportion of fish recruited during that day for the year, while
-$R_{\tilde{y}}$ is the annual recruits. \\
-
-Mortality $Z$ can be decomposed to natural mortality, $M$, and fishing
-mortality, $F$, where both $M$ and $F$ are instantaneous rates with $M$ fixed
-and $F$ calculated by solving the Baranov catch equation \cite{Hilborn1992b}
-for $F$:
-
-\begin{equation*}
-C_{d} = \frac{F_{d}}{F_{d}+M_{d}} * (1 - e^{-(F_{d} + M_{d})}) * B
-\end{equation*}
-
-where $C$ is the summed catch from the fishing model across all fleets and
-vessels for the population during the day, and $B$ the daily biomass for the
-species. \textcolor{red}{[link $F$ to effort and catchability - as I think we
-	have F as an emergent property of the fleets rather than something we
-	solve for (I could be wrong though!) - catch for a vessel is a product of
-	catchability and biomass, i.e. C = qB, but this catch is summed to
-	solve for F. So its both really]}\\
-
-\subsection{Recruitment dynamics}
-
-Recruitment is modelled through a function relating the mature biomass to
-recruits at time of recruitment. In \emph{mixfishsim}, it can be modelled
-either either as a stochastic Beverton-Holt stock-recruit form
-(\cite{Beverton1957}):
-
-\begin{equation*}
-	\begin{split}
-	\bar{R} = & \frac{(\alpha * B)}{(\beta + B)} \\
-	     R \sim & N[(\bar{R},\sigma^2)]
-	\end{split}
-\end{equation*}
-\textcolor{red}{[better to use lognormal variability to avoid negative
-	recruitment events at low biomasses.]} Where $\alpha$ is the maximum
-recruitment rate, $\beta$ the spawning stock biomass (SSB) required to produce
-half the maximum, and $B$ current SSB; \\
-
-or a stochastic Ricker form \cite{Ricker1954}
-
-\begin{equation*}
-	\begin{split}
-	\bar{R} = & B * e^{(\alpha - \beta * B)} \\	
-   	     R \sim & N[(\bar{R},\sigma^2)]
-	\end{split}
-\end{equation*}
-
-where $\alpha$ is the maximum productivity per spawner and $\beta$ the density
-dependent reduction in productivity as the SSB increases.
-
-\subsection{Population movement}
-
-To simulate how fish populations might be distributed in space and time, we
-employed a Gaussian spatial process to model habitat suitability for each of
-the populations, with an advection-diffusion process to control how the
-populations moved over time. \textcolor{red}{[say why - balance between realism
-	and practicalities of IBMs for the fish population]}\\
-
-For the habitat we define a Gaussian random field process, $\{S(x) : x \in
-\mathbb{R}^2\}$, that is a stochastic process where any collection of locations
-$x_{1}, \dots, x_{n}$ where for each $x_{i} \in \mathbb{R}^2$, the joint
-distribution of $S = \{S(x1),\dots S(x_{n})\}$ is multivariate Gaussian. The
-distribution is specified by its \textit{mean function}, $\mu(x) = E[S(x)]$ and
-its \textit{covariance function}, $\gamma(x,x') = Cov\{S(x),S(x')\}$
-\cite{Diggle2007}.\\
-
-The covariance structure affects the smoothness of the surfaces which the
-process generates, and we used the \textit{Matérn} family of covariance
-structures, one where the correlation strength weakens the further the distance
-apart (i.e. the correlation between $S(x)$ and $S(x')$ decreases as the
-distance $u = ||x - x'||$ increases).  The \textit{Matérn} correlation is a
-two-parameter family where: \\
-
-\begin{center}
-	$\rho(u) = \{2^{\kappa -
-		1}\Gamma{\kappa}\}^{-1}(u/\phi)^{\kappa}K_{\kappa}(u/\phi)$
-\end{center}
-
-$K_{\kappa}(.)$ is a modified Bessel function of order $\kappa$, $\phi >
-0$ is a scale parameter with the dimensions of distance, and $\kappa > 0$,
-called the order, is a shape parameter which determines the smoothness of the
-underlying process. \\
-
-In the simulation model, the habitat for each of the populations is generated
-through the \textit{RFSimulate} function of the \textit{RandomFields} R package
-\cite{Schlater2015}, implementing different parameter settings to affect the
-patchiness of the populations. Each population is initialised at a single
-location, and subsequently moves according to a probabilistic distribtion based
-on habitat suitability and distance from current cell.
-
-\begin{equation}
-	Pr(B | A) = \frac{e^{-\lambda * d_{AB}} \cdot
-		Hab_{B}^2}{\sum\limits_{c=1}^{C}e^{-\lambda * d} \cdot
-		Hab_{B}^2}
-\end{equation}
-
-Where $d_{AB}$ is the euclidean distance between cell $A$ and cell $B$,
-$\lambda$ is a given rate of decay and $Hab_{B}^2$ is the squared index of
-habitat suitability for cell $B$.\\
-
-During specified weeks of the year, the habitat quality is modified for
-spawning habitats, meaning each population has a concentrated area where
-spawning takes place and the population moves towards this in the weeks prior
-to spawning. \\
-
-\subsection{Fleet dynamics}
-
-The fleet dynamics can be broadly categorised into three components; fleet
-targeting - which determines the fleet catch efficiency and preference towards
-a particular species; trip-level decisions, which determine the initial
-location to be fished at the beginning of a trip; and within-trip decisions,
-determining movement from one fishing spot to another within a trip.
-
-\subsubsection{Fleet targeting}
-
-Each fleet of \textit{n} vessels is characterised by both a general efficiency,
-\textit{Q}, and a population specific efficiency, ${Q_{p}}$.  Thus, the product
-of these parameters affects the overall catch rates for the fleet and the
-preferential targeting of one population over another. This, in combination
-with the parameter choice for the step-function (as well as some randomness
-from the exploratory fishing process) determines the preference of fishing
-locations for the fleet.  All species prices are kept the same, across fleets,
-though can be made to vary seasonally.
-
-\subsubsection{Trip-level decisions}
-
-Several studies (e.g.\cite{Hutton2004, Tidd2012, Girardin2015}) have confirmed
-past activity and past catch rates are strong predictors of fishing location
-choice. For this reason, the fleet dynamics sub-model includes a learning
-component, where a vessel's initial fishing location in a trip is based on
-selecting from previously successful fishing locations. This is achieved by
-sorting all previous fishing events in the previous trip as well as the
-previous time periods in past years, and choosing randomly from the top x \% of
-fishing events in value.  Simulation testing indicated that this learning
-increased the mean value of catches for the vessels, over just relying on the
-correlated random walk function.
-
-\subsubsection{Within-trip decisions}
-
-Fishing locations within a trip are determined by a modified random walk
-process. A random walk type was chosen as it is the simplest assumption
-commonly used in ecology to describe animal movement which searching for
-homogeneously distributed prey about which there is uncertain knowledge. In a
-random walk, movement is a stochastic process through a series of steps that
-can either be equal in length or take some other functional form.  The
-direction of the random walk can be correlated, a characteristic known as
-`persistence', providing some overall location of directional movement
-\cite{Codling2008} or uncorrelated. \\
-
-A \textit{lévy walk} is a particular form of random walk characterised by a
-heavy-tailed distribution of step-length and has received a lot of attention in
-ecological theory in recent years as having shown to have very similar
-characteristics as those observed by animals in nature, and being a near
-optimum searching strategy for predators pursuing patchily distributed prey
-\cite{Bartumeus2005, Sims2008}.  \cite{Bertrand2007} showed that Peruvian
-anchovy fishermen have a stochastic search pattern similar to that observed
-with a lévy walk. However, it remains a subject of debate, with the contention
-that search patterns may be more simply characteristed as random walks
-\cite{Sakiyama2013} with specific patterns related to the characteristics of
-the prey field \cite{Sims2012}. \\
-
-We use a modified random walk where directional change is based on a correlated
-circular distribution where a favourable fishing ground is likely to be ``fished
-back over" by the vessel returning in the direction it came from and step
-length (i.e. the distance travelled from the current to the next fishing
-location) is determined by relating recent fishing success, measured as the
-summed value of fish caught, $$Rev = \sum_{s=1}^{\infty} C_{s} \cdot Pr_{s}$$
-where $C_{s}$ is catch of a species, and $Pr_{s}$ price of a species, to step
-distance. Here, when fishing is successful vessels remain in a similar location
-and continue to exploit the local fishing grounds. When unsuccessful, they move
-some distance away from the current fishing location. The movement distance
-retains some degree of stochasticity, which can be controlled separately.
-
-The step function takes the form:
-
-\begin{equation*}
-	StepL = e^{log(\beta_{1}) + log(\beta_{2}) - (log(\frac{\beta_{1}}{\beta_{3}}))} * Rev
-\end{equation*}
-
-So that, a step from (x1,y1) to (x2, y2) is defined by:
-
-\begin{equation*}
-	\begin{split}
- (x2, y2) =  & x1 + StepL \cdot \cos (\frac{\pi \cdot Br}{180}), \\
-             & y1 + StepL \cdot \sin (\frac{\pi \cdot Br}{180}) \\	
- with  \hspace{0.5cm}     & Br_{t-1} < 180, Br_{t} = 180 + \sim vm[(0,360), k] \\
- 			  & Br_{t-1} > 180, Br_{t} = 180 - \sim vm[(0,360), k] \\
-	\end{split}
-\end{equation*}
-
-with $k$ the concentration parameter from the von mises distribution which we
-correlate with the revenue so that $k = (Rev + 1 / RefRev) * max_{k}$,
-where $max_{k}$ is the maximum concentration value, $k$, and RefRev is
-parameterised as for $\beta_{3}$ in the step length function.
-
-\subsubsection{Local population depletion}
-
-Where several fishing vessels are exploiting the same fish population
-competition is known to play an important role in local distribution of fishing
-effort \cite{Gillis1998}. If several vessels are fishing on the same patch of
-fish, local depletion and interference will affect fishing location choice of
-the fleet as a whole \cite{Rijnsdorp2000, Poos2007a}. In order to account for
-this behaviour, the fishing sub-model operates spatially on a daily time-step
-so that for future days the biomass available to the fishery is reduced in the
-areas fished. The cumulative effect is to make heavily fished areas less
-attractive as future fishing opportunities.
-
-\subsection{Fisheries independent survey}
-
-A fisheries-independent survey is simulated where fishing on a regular grid
-begins each year at the same time for a given number of stations (a fixed
-station survey design). Catches of the populations present are recorded but not
-removed from the population. This provides a fishery independent snapshot of
-the populations at a regular spatial distribution each year, similar to
-scientific surveys undertaken by fisheries research agencies.
-
-\section{Calculation}
-
-\textcolor{gray}{[Guidance: A \underline{Theory} section should extend, not
-repeat, the background to the article already dealt with in the	Introduction
-and lay the foundation for further work.  In contrast, a
-\underline{Calculation} section represents a practical development from a
-theoretical basis.] \\}
-
-\subsection{Simulation settings}
-
-To illustrate the capabilities on \emph{MixFishSim}, we investigate the
-influence of ... \textcolor{red}{[expand]}. To do so, we first set up with
-simulation to run for 20 years based on a 100 X 100 square grid, with five
-fleets of 20 vessels each and four fish populations. Fishing takes place four
-times a day per vessel and five days a week, while population movement is every
-week.
-
-\subsection{Population parameterisation}
-
-We parameterised the simulation model for four populations with differing
-habitat preference (Figure \ref{fig:1}), population demographic and recruitment
-functions; each of the populations also has two defined spawning areas and
-movement rates (Table \ref{tab:1}). \\
-
-\subsection{Fleet parameterisation}
-
-The fleets were parameterised to reflect five different characteristics based
-on targeting preference and exploitation dynamics (Table \ref{tab:2}). This
-ensures that different fleets have different spatial dynamics, preferentially
-targeted different fish populations. The stochasticity in the random walk
-process ensures that different vessels within a fleet have slightly different
-spatial distributions based on individual experience, while the step function
-was parameterised dynamically so that vessels take smaller steps where the
-fishing location yields in the top X \textcolor{red}{[??]}quartile of the value
-available in that year (as defined per fleet in Table \ref{tab:2}). \\
-
-Each fleet was set so that, after the first year, fishing locations were chosen
-based on experience built up in the same month from previous years and from
-past trip fishing success. 'Success' in this context was defined as the
-locations where the top 75 \% of revenue from was found in previous trips.
-
-\subsection{Survey settings}
-
-The survey simulation was set up with follow a fixed gridded station design
-with 49 stations fished each year, starting on day 92 with same catchability
-parameters for all populations (Q = 1).
-
-\section{Results}
-
-Need to consider what best to present here as 4 / 5 figures:
-
-\begin{itemize}
-	\item Spatial dynamics: e.g. Figure 14. showing the population movement
-		across weeks, including a spawning period.
-	\item Overall population trends: e.g. Figure 3, showing the population
-		dynamics at play.
-	\item Realised step function: e.g. Figure 13, showing how the movement
-		and turning angle responds. This could be combined with Figure
-		7 for a more complete visualisaiton.
-	\item Catch composition and spatial clustering: e.g. Figure 10, showing
-		the importance of spatial resolution.
-	\item Some measure of temporal trends/changes in spatial composition -
-		could pick a certain cell and show how the proportions change
-		over time ? An example is Figure 15, though there is little
-		variation here. I think this is because the static habitat with
-		population movement is far more stable than the previous
-		directly affected population distributions (where there was an
-		advective-diffusive process from the SPDE). Might need to
-		consider how to change this?  Could include a spatiotemporally
-		changing habitat suitability covariate, e.g. temperature ??
-		\textcolor{red}{[temperature would be very interesting and
-			cover varying spatial fields]}
-	\item Comparison of population structure from i) commercial sampling,
-		ii) fisheries independent survey, iii) real population. This
-		should be some statistical measure...not sure best approach
-		here.
-	\item [If we perform the closure, some measure of cost/benefit based on
-		different resolutions of data and data used (i.e. commercial,
-		survey, real populations). This could be on the basis of
-		closing x cells, giving cell references to the model so they
-		cannot be fished. Need to consider whether this is also a
-		seasonal closure.]
-\end{itemize}
-
-Present simulated closures in terms of \% change in population biomass and
-fishery.
-
-\textcolor{gray}{[Guidance: Results should be clear and concise.]}
-
-\section{Discussion}
-
-\textcolor{gray}{[Guidance: This should explore the significance of the results 
-of the work, not repeat them. A combined Results and Discussion section is
-often appropriate.  Avoid extensive citations and discussion of published
-literature.]}
-
-\section{Conclusions}
-
-\textcolor{gray}{[Guidance: The main conclusions of the study may be presented 
-in a short Conclusions section, which may stand alone or form a subsection of a
-Discussion or Results and Discussion section.]}
-
-\section*{Appendices}
-
-\textcolor{gray}{[Guidance: If there is more than one appendix, they should 
-be identified as A, B, etc.  Formulae and equations in appendices should be
-given separate numbering: Eq.  (A.1), Eq. (A.2), etc.; in a subsequent
-appendix, Eq. (B.1) and so on.  Similarly for tables and figures: Table A.1;
-Fig. A.1, etc.]}
-
-\begin{table}[!ht]
-\caption{Population dynamics and movement parameter setting}
-	\begin{tabular}{ p{4cm } p{2cm} p{2cm} p{2cm} p{2cm}}
-	Parameter & Pop 1 & Pop 2 & Pop 3 & Pop 4 \\
-	\hline
-	Habitat quality & & & \\
-	\hline
-	Matérn $\nu$ & 1/0.15 & 1/0.05 & 1/0.55 & 1/0.05  \\
-	Matérn $\kappa$ & 1 & 2 & 1 & 1  \\
-	Anisotropy & 1.5,3,-3,4 & 1,2,-1,2 & 2.5,1,-1,2 & 0.1,2,-1,0.2 \\
-	Spawning areas (bound box) & 40,50,40,50; 80,90,60,70 &
-	50,60,30,40; 80,90,90,90 & 30,34,10,20; 60,70,20,30 & 50,55,80,85; 30,40,30,40 \\
-	Spawning multiplier & 10 & 10 & 10 & 10 \\
-	Movement $\lambda$ & 0.3 & 0.3 & 0.3 & 0.3 \\
-	\hline
-	Population dynamics & & & & \\
-	\hline
-	Starting Biomass & 1e5 & 2e5 & 1e5 & 1e4 \\
-	Beverton-Holt Recruit 'a' & 60 & 100 & 80 & 2 \\
-	Beverton-Holt Recruit 'b' & 250 & 250 & 200 & 50 \\
-	Beverton-Holt Recruit $\sigma^2$ & 0.4 & 0.3 & 0.4 & 0.3 \\
-	Recruit week & 13-16 & 12-16 & 14-16 & 16-20 \\
-	Spawn week & 16-18 & 16-19 & 16-18 & 18-20 \\
-	$K$ & 0.3 & 0.3 & 0.3 & 0.3 \\
-	$wt$ & 1 & 1 & 1 & 1 \\
-	$wt_{d-1}$ & 0.1 & 0.1 & 0.1 & 0.1 \\
-	M (annual) & 0.2 & 0.2 & 0.2 & 0.1 \\
-	\hline
-\end{tabular}
-\label{tab:1}
-\end{table}
-
-\begin{table}[!ht]
-\caption{Fleet dynamics parameter setting}
-\begin{tabular}{ p{4cm } p{1cm} p{1cm} p{1cm} p{1cm} p{1cm}}
-	\hline
-	Parameter & Fleet 1 & Fleet 2 & Fleet 3 & Fleet 4 & Fleet 5 \\
-	\hline
-	Targeting preferences &&&& \\
-	\hline
-	Price Pop1 & 100 & 100 & 100 & 100 & 100 \\
-	Price Pop2 & 200 & 200 & 200 & 200 & 200 \\
-	Price Pop3 & 600 & 600 & 600 & 600 & 600 \\
-	Price Pop4 & 1600 & 1600 & 1600 & 1600 & 1600 \\
-	$Q$ Pop1 & 0.01 & 0.02 & 0.02 & 0.01 & 0.01 \\
-	$Q$ Pop2 & 0.02 & 0.01 & 0.02 & 0.01 & 0.03\\
-	$Q$ Pop3 & 0.01 & 0.02 & 0.02 & 0.01 & 0.02 \\
-	$Q$ Pop4 & 0.02 & 0.01 & 0.02 & 0.05 & 0.01 \\
-	\hline
-	Exploitation dynamics &&&& \\
-	\hline
-	step function $\beta_1$ & 1 & 2 & 1 & 2 & 3 \\
-	step function $\beta_2$ & 10 & 10 & 8 & 12 & 7 \\
-	step function $\beta_3$ & Q90 & Q90 & Q85 & Q90 & Q80 \\
-	step function $rate$ & 10 & 20 & 15 & 25 & 10 \\
-	Past Knowledge & T & T & T & T & T \\
-	Past Year \& Month & T & T & T & T & T \\
-	Past Trip & T & T & T & T & T \\
-	Threshold & 0.75 & 0.75 & 0.75 & 0.75 & 0.75 \\
-	\hline
-\end{tabular}
-\label{tab:2}
-\end{table}
+\beginsupplement
+\maketitle
 
@@
 \begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/annual_summary}
-	\caption{Summary of annualised metrics: biomass, catch, fishing
-		mortality and recruitment. x-axis is the year, y the value}
+	\includegraphics[width = \linewidth]{Plots/habitat_spwn}
+	\caption{spawning habitat preference}
 	\label{fig:2}
@@
 \begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/fDynamics}
-	\caption{f dynamics - the daily fishing mortalities, each year is a
-		different colour}
+	\includegraphics[width = \linewidth]{Plots/Temperature_gradient}
+	\caption{Spatiotemporal qemperature gradient}
 	\label{fig:3}
@@
 \begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/vessel_move}
-	\caption{vessel movement - a single trip movement for one vessel}
+	\includegraphics[width = \linewidth]{Plots/Species_tolerances}
+	\caption{Species thermal tolerances}
 	\label{fig:4}
@@
 \begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/vessel_multi_move}
+	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_1}
+	\caption{Spatiotemporal habitat suitability - population 1}
+	\label{fig:5}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_2}
+	\caption{Spatiotemporal habitat suitability - population 2}
+	\label{fig:6}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_3}
+	\caption{Spatiotemporal habitat suitability - population 3}
+	\label{fig:7}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_4}
+	\caption{Spatiotemporal habitat suitability - population 4}
+	\label{fig:8}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{Plots/pop_dist}
+	\caption{Simulated spatial dynamics - the four populations at four time steps.
+		}
+	\label{fig:9}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{Plots/f_dynamics}
+	\caption{f dynamics - the daily fishing mortalities, each year is a
+		different colour}
+	\label{fig:10}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{Plots/vessel_move}
+	\caption{vessel movement - a single trip movement for one vessel}
+	\label{fig:11}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width = \linewidth]{Plots/vessel_multi_move}
 	\caption{vessel movement for multiple trips from a single vessel. Note
@@
 	edges being barriers}
-	\label{fig:5}
+	\label{fig:12}
 \end{figure}
@@
 \begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/vessel_move_value}
+	\includegraphics[width = \linewidth]{Plots/vessel_move_value}
 	\caption{movement of a single vessel over a few trips overlaid on the
 		value field (i.e. sum of the population abundance x catchability x value}
-	\label{fig:6}
+	\label{fig:13}
 \end{figure}
@@
 \begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/fleet_moves}
+	\includegraphics[width = \linewidth]{Plots/fleet_moves}
 	\caption{An entire fleets (20 vessels) movement for a single trip}
-	\label{fig:7}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/catch_comp}
-	\caption{spatial catch composition - the raw catches per cell at 4
-		different spatial resolutions. Sorry, its a bit small at the
-		moment!}
-	\label{fig:8}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/catch_comp_clusters}
-	\caption{spatial catch composition (as above) but with clustering of
-		cells performs on the bottom row. I'm confused as to why some
-		entirely blue cells in the raw catch composition get allocated
-	to the same cluster as some entirely red cells - needs investigating,
-	it may be the clustering is not optimal}
-	\label{fig:9}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/survey_index}
-	\caption{survey index - a non-spatial index generated from the fishery independent
-	survey}
-	\label{fig:10}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/spatial_survey}
-	\caption{survey spatial abundance - a bubble plot of the survey
-		abundances, not really useful for the paper}
-	\label{fig:11}
+	\label{fig:14}
 \end{figure}
@@
 	values, the turning range is less}
-	\label{fig:12}
+	\label{fig:15}
 \end{figure}
 
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/pop_dist}
-	\caption{Spatial dynamics - the four populations at four time steps.
-		Not really happy about the lack of dynamics here - mainly down
-	to the static habitat leading to the populations settle in same cells
-	over most time steps (exception: during the spawning period). Could
-	include a temperature covariate or something to force some more
-	temporal changes?}
-	\label{fig:13}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/Proportion_in_cell}
-	\caption{Temporal dynamics - the proportion of each population in a
-		randomly chosen cell. Similar criticism as above}
-	\label{fig:14}
-\end{figure}
-
-\section*{Abbreviations} Detail any unusual ones used.
-
-\section*{Acknowledgements} those providing help during the research..
-
-\section*{Funding} This work was supported by the MARES doctoral training
-program; and the Centre for Environment, Fisheries and Aquaculture Science
-seedcorn program.
-
-\clearpage
-
-\section*{References}
-
-\bibliography{simulation_framework}
-
 \end{document}

### 2018-03-16 write_up/mixfishsim_ecolmod.tex
Updates to manuscript and developments on results

@@
 \documentclass[review]{elsarticle}
+
+\usepackage{xr} %% For cross-referencing supl figures
+\externaldocument[S-]{Supplementary}
 
@@
 sampling method due to fisher's targeting- to provide a robust picture of
-spatiotemporal distributions. [We simulate a closure based on areas defined
-from commercial catch data and assess its effectiveness on reducing catches of
-a fish population.] \\
+spatiotemporal distributions. Finally, we simulate an area closure based on
+areas defined from commercial the known ("real-population") distribution,
+commercial catch data and survey data at different temporal and spatial
+resolutions and assess their effectiveness on reducing catches of a fish
+population. \\
 
-We conclude that... \\
+We conclude from our simulations that commercial data, while not unbiased,
+provides a useful tool for managing catches in mixed fisheries if applied at
+the correct spatiotemporal scale. \\
 
@@
 simulation.\\
-
-[Could fit a geostatistical model (e.g. VAST) to the fisheries-dependent and
-fisheries-independent data, though may be overkill...] \\
 
@@
 We parameterised the simulation model for four populations with differing
-habitat preference (Figure \ref{fig:1}), population demographic and recruitment
-functions; each of the populations also has two defined spawning areas and
-movement rates (Table \ref{tab:1}). \\
+habitat preference and temperature tolerances (Figures \ref{S-fig:1},
+\ref{S-fig:3}, \ref{S-fig:4}, \ref{S-fig:5}, \ref{S-fig:6}, \ref{S-fig:7}),
+population demographic and recruitment functions; each of the populations also
+has two defined spawning areas (Figure \ref{S-fig:2}) and movement rates (Table
+\ref{tab:1}). The actual movement of the populations for a number of weeks is
+shown in Figure \ref{S-fig:9} while the realised daily fishing mortality are
+shown in Figure \ref{S-fig:10}. \\
 
@@
 was parameterised dynamically so that vessels take smaller steps where the
-fishing location yields in the top X \textcolor{red}{[??]}quartile of the value
-available in that year (as defined per fleet in Table \ref{tab:2}). \\
+fishing location yields in a top quartile of the value available in that year
+(as defined per fleet in Table \ref{tab:2}). \\
 
@@
 
+An example of the realised fleet movements for a single vessel during a single
+trip are given in Figure \ref{S-fig:11}, while Figure \ref{S-fig:12} shows
+multiple trips for a single vessel, \ref{S-fig:13} the vessel movements for
+some trips overlaid on the value field, \ref{S-fig:14} shows fishing locations
+for an entire fleet of 20 vessels for a single trip, while \ref{S-fig:15} shows
+an example of the step function realisation and turning angles from the
+correlated random walk.
+
 \subsection{Survey settings}
@@
 The survey simulation was set up with follow a fixed gridded station design
-with 49 stations fished each year, starting on day 92 with same catchability
+with 100 stations fished each year, starting on day 92 with same catchability
 parameters for all populations (Q = 1).
@@
 areas for the last 5 years of the simulation based on data (either derived from
-the commercial catches, fisheries-independent survey or the 'real population')
-used at different spatial and temporal scales. \\
+the commercial catches, fisheries-independent survey or the 'real population' -
+the underlying populations assumed to be known perfectly) used at different
+spatial and temporal scales. \\
 
@@
 
-In total 56 closure scenarios were run which represent combinations of: three
-data types; commercial logbook data, survey data and 'real population', three
-temporal resolutions; weekly, monthly and yearly closures, and four spatial
-resolutions; 1 x 1 grid, 5 x 5 grid, 10 x 10 grid and 20 x 20 grid. Survey
-closures were on an annual basis, as the most temporally resolved survey data
-available.
+In total 56 closure scenarios were run which represent combinations of
+
+\begin{itemize}
+	\item \textbf{data types:} commercial logbook data, survey data and
+		'real population',
+	\item \textbf{temporal resolutions:} weekly, monthly and yearly
+		closures,
+	\item \textbf{spatial resolutions:} 1 x 1 grid, 5 x 5 grid, 10 x 10
+		grid and 20 x 20 grid.
+\end{itemize}
+
+Survey closures were on an annual basis only, as this was the most temporally
+resolved survey data available.
 
@@
 
-Need to consider what best to present here as 4 / 5 figures:
+The species distribution themselves
 
-\begin{itemize}
-	\item Spatial dynamics: e.g. Figure 14. showing the population movement
-		across weeks, including a spawning period.
-	\item Overall population trends: e.g. Figure 3, showing the population
-		dynamics at play.
-	\item Realised step function: e.g. Figure 13, showing how the movement
-		and turning angle responds. This could be combined with Figure
-		7 for a more complete visualisaiton.
-	\item Catch composition and spatial clustering: e.g. Figure 10, showing
-		the importance of spatial resolution.
-	\item Some measure of temporal trends/changes in spatial composition -
-		could pick a certain cell and show how the proportions change
-		over time ? An example is Figure 15, though there is little
-		variation here. I think this is because the static habitat with
-		population movement is far more stable than the previous
-		directly affected population distributions (where there was an
-		advective-diffusive process from the SPDE). Might need to
-		consider how to change this?  Could include a spatiotemporally
-		changing habitat suitability covariate, e.g. temperature ??
-		\textcolor{red}{[temperature would be very interesting and
-			cover varying spatial fields]}
-	\item Comparison of population structure from i) commercial sampling,
-		ii) fisheries independent survey, iii) real population. This
-		should be some statistical measure...not sure best approach
-		here.
-	\item [If we perform the closure, some measure of cost/benefit based on
-		different resolutions of data and data used (i.e. commercial,
-		survey, real populations). This could be on the basis of
-		closing x cells, giving cell references to the model so they
-		cannot be fished. Need to consider whether this is also a
-		seasonal closure.]
-\end{itemize}
+The consequences of different spatial aggregations of the data are shown in
+Figure \ref{fig:1}, which represents the aggregation of catch from each of the
+data sources over a year at different spatial resolutions. \\
 
-Present simulated closures in terms of \% change in population biomass and
-fishery.
+The finer spatial grid for the the real population (top left) and commercial
+data (top middle) show similar patterns, though there are unsampled gaps in the
+commercial data from a lack of fishing activity (particularly in the lower left
+part of the sampling domain). The survey data at this spatial resolution shows
+very sparse and uninformative information about the spatial distributions of
+the populations. The slightly aggregated data on a 5 x 5 grid shows similar
+patterns, and while losing some of the spatial detail there remains good
+consistency between the 'real population' and the commercial data. Survey data
+starts to pick out some of the similar patterns as the other data sources, but
+lacks coverage. The spatial catch information on a 10 x 10 and 20 x 20 grid
+loses a significant amount of information about the spatial resolutions for all
+data sources, and some differences between the commercial and 'real population'
+data emerge. \\
+
+Figure \ref{fig:2} shows the consequences of different temporal aggregations of
+the data, with 156 weekly (top), 36 monthly (middle) and 3 yearly (bottom)
+catch compositions across a 20 x 20 area. \\
+
+As can be seen from the 'real population', the monthly aggregation captures the
+major patterns seen in the weekly data, albeit missing more subtle differences.
+The yearly data results in a constant catch pattern due to the aggregation
+process (sometimes known as an aggregation bias). The commercial data on a
+weekly basis shows some of the same patterns as the 'real population', though
+the first species (in red) is less well represented and some weeks are missing
+catches from the area. The monthly data. The monthly data shows some
+consistency between the 'real population' and commercial data for species 2 -
+4, though species 1 remains underrepresented. On an annual basis, interestingly
+the commercial data underrepresents the first species (in red) while the survey
+overrepresents species 1. This is likely due to the biases in commercial
+sampling, with the fisheries not targeting the areas where species 1 are
+present, and the biases in the survey sampling from overrepresentation of the
+spatial distribution. \\
+
+We implemented a spatial closure using the different data sources and spatial
+and temporal aggregations as outlined in the protocol in Section 3.4. We used
+this to assess the efficacy of a closure in reducing fishing mortality on
+species 1, given availability of data and its use at different resolutions in
+order to evaluate the trade-offs in data sources. Figure \ref{fig:3} shows the
+trend in fishing mortality for each species simulated (columns) given the data
+sources (rows), temporal aggregations (colour lines) and spatial aggregations
+(linestyles), while Figure \ref{fig:4} shows the change in fishing mortality
+from before the closure (average F years 2 - 4) to after the closure (average F
+years 8 - 10). \\
+
+For the closures based on 'real population' (bottom row), the most
+disaggregated data (a weekly timescale and 1 x 1 resolution) was most
+effective, reducing fishing mortality on species 1 (left) by $\sim$ 60 \%. Next
+was the monthly closures ($<$ $\sim$ 30 \%).  The least effective were the
+yearly closures (blue lines) at all spatial resolutions, which resulted in
+increased fishing mortalities ($>$ 30 \% - \textcolor{blue}{N.B. Note though,
+this is consistent with the increasing trends in F, which is probably more
+related to the fact that Fs hadn't stabilised in the simulation from the
+fishing vessels "learning" the best locations - I will rerun the sims for a
+longer time (20 - 30 years)}. \\
+
+For the survey data, which can only be implemented on a yearly timescale, the
+closures had no effect at any data resolution. The results are identical for
+the different data resolutions except 20 x 20, which is why you can't see more
+than 2 points. This is because of the sparsity of the sampling locations.\\
+
+For the commercial data, the most effective closure scenario was based on 1 x 1
+data at a monthly temporal resolution. This results in $\sim$ 10 \% reduction
+in F for species 1. \textcolor{blue}{This was the only closure scenario to have
+	positive effect according to Figure \ref{fig:4}, though looking at the
+	trend in Figure \ref{fig:3} this looks more related to the continued
+	increased in F trend, as other scenarios had an initial effect}.
+Interestingly the monthly data scenario was more effective than weekly data,
+which I'd posit is due to the increase amount of data available from the
+commercial sampling across a month compared to a week.i Commercial data used at
+an annual timestep was ineffective in bringing fishing mortality down for
+species 1. \\
+
+Given the scenarios above, it seems clear that spatial disaggregation is more
+important than the temporal disaggregation of the commercial data, except when
+its used at an annual timeframe, which is the scenario that gave the worst
+results.
+
+For the other species in the simulation (population 2 - 4) there was little
+difference in fishing mortalities across scenarios.
+
+\textcolor{blue}{Note: The monthly commercial data scenario is the most
+	effective of the realistic scenarios, as the 'real population' can only
+	be seen as a baseline comparison.}
 
@@
 	\caption{Data aggregation at different spatial resolutions}
-	\label{fig:0a}
+	\label{fig:1}
 \end{figure}
@@
 	\caption{Data aggregation at different temporal resolutions}
-	\label{fig:0b}
+	\label{fig:2}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{../analysis/F_trends}
+	\caption{Comparison of closure scenarios - F trends}
+	\label{fig:3}
 \end{figure}
@@
 	\caption{Comparison of closure scenarios}
-	\label{fig:0c}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../analysis/F_trends}
-	\caption{Comparison of closure scenarios - F trends}
-	\label{fig:0d}
-\end{figure}
-
-// 
-//Supplementary
-//
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/habitat}
-	\caption{habitat preference}
-	\label{fig:1}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/annual_summary}
-	\caption{Summary of annualised metrics: biomass, catch, fishing
-		mortality and recruitment. x-axis is the year, y the value}
-	\label{fig:2}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/fDynamics}
-	\caption{f dynamics - the daily fishing mortalities, each year is a
-		different colour}
-	\label{fig:3}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/vessel_move}
-	\caption{vessel movement - a single trip movement for one vessel}
 	\label{fig:4}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/vessel_multi_move}
-	\caption{vessel movement for multiple trips from a single vessel. Note
-	the movement off the side pops up the other side, but is joined by a
-	line across the grid. This is from the torus approach rather than the
-	edges being barriers}
-	\label{fig:5}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/vessel_move_value}
-	\caption{movement of a single vessel over a few trips overlaid on the
-		value field (i.e. sum of the population abundance x catchability x value}
-	\label{fig:6}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/fleet_moves}
-	\caption{An entire fleets (20 vessels) movement for a single trip}
-	\label{fig:7}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/catch_comp}
-	\caption{spatial catch composition - the raw catches per cell at 4
-		different spatial resolutions. Sorry, its a bit small at the
-		moment!}
-	\label{fig:8}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/catch_comp_clusters}
-	\caption{spatial catch composition (as above) but with clustering of
-		cells performs on the bottom row. I'm confused as to why some
-		entirely blue cells in the raw catch composition get allocated
-	to the same cluster as some entirely red cells - needs investigating,
-	it may be the clustering is not optimal}
-	\label{fig:9}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/survey_index}
-	\caption{survey index - a non-spatial index generated from the fishery independent
-	survey}
-	\label{fig:10}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/spatial_survey}
-	\caption{survey spatial abundance - a bubble plot of the survey
-		abundances, not really useful for the paper}
-	\label{fig:11}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/step_function}
-	\caption{Realised step function - the step function as realised for a
-		single fleet. For turning angles, it can be seen that at higher
-	values, the turning range is less}
-	\label{fig:12}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/pop_dist}
-	\caption{Spatial dynamics - the four populations at four time steps.
-		Not really happy about the lack of dynamics here - mainly down
-	to the static habitat leading to the populations settle in same cells
-	over most time steps (exception: during the spawning period). Could
-	include a temperature covariate or something to force some more
-	temporal changes?}
-	\label{fig:13}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/Proportion_in_cell}
-	\caption{Temporal dynamics - the proportion of each population in a
-		randomly chosen cell. Similar criticism as above}
-	\label{fig:14}
 \end{figure}

### 2018-03-16 analysis/Plots_Combined.R

@@ -127,3 +127,24 @@ facet_wrap(data_type ~ pop, scale = 'free') + expand_limits(y = 0) +theme_bw() +
 geom_vline(xintercept = 4.5, linetype = 2, colour = "grey")
 ggsave('F_trends.png', width = 10, height = 8)
 
+ggplot(filter(combined_pop_an,basis == 'high_pop', metric == 'Bio'), 
+       aes(x = year, y = data, group = combined)) + 
+geom_line(aes(colour = timescale, linetype = factor(res))) + 
+facet_wrap(data_type ~ pop, scale = 'free') + expand_limits(y = 0) +theme_bw() +
+geom_vline(xintercept = 4.5, linetype = 2, colour = "grey")
+ggsave('B_trends.png', width = 10, height = 8)
+
+ggplot(filter(combined_pop_an,basis == 'high_pop', metric == 'Rec'), 
+       aes(x = year, y = data, group = combined)) + 
+geom_line(aes(colour = timescale, linetype = factor(res))) + 
+facet_wrap(data_type ~ pop, scale = 'free') + expand_limits(y = 0) +theme_bw() +
+geom_vline(xintercept = 4.5, linetype = 2, colour = "grey")
+ggsave('R_trends.png', width = 10, height = 8)
+
+ggplot(filter(combined_pop_an,basis == 'high_pop', metric == 'Catch'), 
+       aes(x = year, y = data, group = combined)) + 
+geom_line(aes(colour = timescale, linetype = factor(res))) + 
+facet_wrap(data_type ~ pop, scale = 'free') + expand_limits(y = 0) +theme_bw() +
+geom_vline(xintercept = 4.5, linetype = 2, colour = "grey")
+ggsave('C_trends.png', width = 10, height = 8)
+

### 2018-03-16 write_up/Plots/Plot_temp_effect.R

@@ -1,0 +1,101 @@
+
+library(MixFishSim)
+
+set.seed(123, kind = "L'Ecuyer-CMRG")
+
+## initialise the simulation
+
+sim <- init_sim(nrows = 100, ncols = 100, n_years = 10, n_tows_day = 4, n_days_wk_fished = 5,
+     n_fleets = 5, n_vessels = 20, n_species = 4, move_freq = 2)
+
+## create the suitable habitat for each species
+
+hab <- create_hab(sim_init = sim,
+		  spp.ctrl = list(
+           'spp.1' = list('nu' = 1/0.15, var = 1, scale = 10, Aniso =
+           matrix(nc=2, c(1.5, 3, -3, 4))),
+           'spp.2' = list('nu' = 1/0.05, var = 2, scale = 20, Aniso =
+           matrix(nc=2, c(1, 2, -1, 2))),
+	   'spp.3' = list('nu' = 1/0.55, var = 1, scale = 5, Aniso =
+           matrix(nc=2, c(2.5, 1, -1, 2))),
+           'spp.4' = list('nu' = 1/0.05, var = 1, scale = 30, Aniso =
+           matrix(nc=2, c(0.1, 2, -1, 0.2)))
+				  ),
+		  spawn_areas = list("spp1" = list(area1 = c(40, 50, 40, 50), area2 =
+				   c(80, 90, 60, 70)), 
+		 "spp2" = list(area1 = c(50, 60, 30, 40), area2 = c(80, 90, 90, 90)),
+		 "spp3" = list(area1 = c(30, 34, 10, 20), area2 = c(60, 70, 20, 30)),
+		 "spp4" = list(area1 = c(50, 55, 80, 85), area2 = c(30, 40, 30, 40))
+		 ),
+		spwn_mult = 10, plot.dist = TRUE, plot.file = getwd())
+
+## Initialise the populations
+
+## Notes: A small lambda will speed up the spread of the population
+##        This will reduce the need for a larger number of init_move_steps
+##        which is the slower part of the function
+
+# Define the stock recruitment parameters - these will apply to the whole pop,
+# so I'm unsure of scale as yet
+
+#Recr(model = "BH", params = list("a" = 1000, "b" = 450), 
[…]

### 2018-03-16 write_up/mixfishsim_ecolmod.tex
Update abstract wordcount
Small textual changes

@@
 
-[233 words]
+[333 words]
 
@@
 \ref{S-fig:3}, \ref{S-fig:4}, \ref{S-fig:5}, \ref{S-fig:6}, \ref{S-fig:7}),
-population demographic and recruitment functions; each of the populations also
-has two defined spawning areas (Figure \ref{S-fig:2}) and movement rates (Table
-\ref{tab:1}). The actual movement of the populations for a number of weeks is
-shown in Figure \ref{S-fig:9} while the realised daily fishing mortality are
-shown in Figure \ref{S-fig:10}. \\
+population demographic and recruitment functions. In addition, each of the
+populations has two defined spawning areas which result in the populations
+moving towards these areas in given weeks (Figure \ref{S-fig:2}) and
+population-specific movement rates (Table \ref{tab:1}). The realised movement
+of the populations for a number of weeks is shown in Figure \ref{S-fig:9} while
+the realised daily fishing mortality are shown in Figure \ref{S-fig:10}. \\
 

### 2018-03-21 write_up/mixfishsim_ecolmod.tex
Removing guidance text

@@
 \begin{abstract}
-\textcolor{gray}{[Guidance: A concise and factual abstract is required. The abstract 
-should state briefly the purpose of the research, the principal results and
-major conclusions. An abstract is often pnresented separately from the article,
-so it must be able to stand alone. For this reason, References should be
-avoided, but if essential, then cite the author(s) and year(s). Also,
-non-standard or uncommon abbreviations should be avoided, but if essential they
-must be defined at their first mention in the abstract itself.  Graphical
-abstract: Although a graphical abstract is optional, its use is encouraged as
-it draws more attention to the online article. The graphical abstract should
-summarize the contents of the article in a concise, pictorial form designed to
-capture the attention of a wide readership. Graphical abstracts should be
-submitted as a separate file in the online submission system. Image size:
-Please provide an image with a minimum of 531 X 1328 pixels (h X w) or
-proportionally more. The image should be readable at a size of 5 x 13 cm using
-a regular screen resolution of 96 dpi.  Preferred file types: TIFF, EPS, PDF or
-MS Office files.] \\}
-
+%\textcolor{gray}{[Guidance: A concise and factual abstract is required. The abstract 
+%should state briefly the purpose of the research, the principal results and
+%major conclusions. An abstract is often pnresented separately from the article,
+%so it must be able to stand alone. For this reason, References should be
+%avoided, but if essential, then cite the author(s) and year(s). Also,
+%non-standard or uncommon abbreviations should be avoided, but if essential they
+%must be defined at their first mention in the abstract itself.  Graphical
+%abstract: Although a graphical abstract is optional, its use is encouraged as
+%it draws more attention to the online article. The graphical abstract should
+%summarize the contents of the article in a concise, pictorial form designed to
+%capture the attention of a wide readership. Graphical abstracts should be
+%submitted as a separate file in the online submission system. Image size:
+%Please provide an image with a minimum of 531 X 1328 pixels (h X w) or
+%proportionally more. The image should be readable at a size of 5 x 13 cm using
+%a regular screen resolution of 96 dpi.  Preferred file types: TIFF, EPS, PDF or
+%MS Office files.] \\}
+%
 Fishing exploits spatially and temporally hetergenous fish populations, using
@@
 
-\textcolor{gray}{[Guidance:: State the objectives of the work and provide an 
-adequate background, avoiding a detailed literature survey or a summary of the
-results.] \\}
-
+%\textcolor{gray}{[Guidance:: State the objectives of the work and provide an 
+%adequate background, avoiding a detailed literature survey or a summary of the
+%results.] \\}
+%
 Fishers exploit fish populations that are heterogenously distributed in space
@@
 
-\textcolor{gray}{[Guidance: Provide sufficient details to allow the work to be
-reproduced by an independent researcher. Methods that are already published
-should be summarized, and indicated by a reference.  If quoting directly from a
-previously published method, use quotation marks and also cite the source. Any
-modifications to existing methods should also be described.] \\ }
-
+%\textcolor{gray}{[Guidance: Provide sufficient details to allow the work to be
+%reproduced by an independent researcher. Methods that are already published
+%should be summarized, and indicated by a reference.  If quoting directly from a
+%previously published method, use quotation marks and also cite the source. Any
+%modifications to existing methods should also be described.] \\ }
+%
 We develop a simulation model with a modular event-based approach, where
@@
 
-\textcolor{gray}{[Guidance: A \underline{Theory} section should extend, not
-repeat, the background to the article already dealt with in the	Introduction
-and lay the foundation for further work.  In contrast, a
-\underline{Calculation} section represents a practical development from a
-theoretical basis.] \\}
-
+%\textcolor{gray}{[Guidance: A \underline{Theory} section should extend, not
+%repeat, the background to the article already dealt with in the	Introduction
+%and lay the foundation for further work.  In contrast, a
+%\underline{Calculation} section represents a practical development from a
+%theoretical basis.] \\}
+%
 \subsection{Population parameterisation}
@@
 
-\textcolor{gray}{[Guidance: Results should be clear and concise.]}
+%\textcolor{gray}{[Guidance: Results should be clear and concise.]}
 
@@
 
-\textcolor{gray}{[Guidance: This should explore the significance of the results 
-of the work, not repeat them. A combined Results and Discussion section is
-often appropriate.  Avoid extensive citations and discussion of published
-literature.]}
-
+%\textcolor{gray}{[Guidance: This should explore the significance of the results 
+%of the work, not repeat them. A combined Results and Discussion section is
+%often appropriate.  Avoid extensive citations and discussion of published
+%literature.]}
+%
 \section{Conclusions}
 
-\textcolor{gray}{[Guidance: The main conclusions of the study may be presented 
-in a short Conclusions section, which may stand alone or form a subsection of a
-Discussion or Results and Discussion section.]}
-
+%\textcolor{gray}{[Guidance: The main conclusions of the study may be presented 
+%in a short Conclusions section, which may stand alone or form a subsection of a
+%Discussion or Results and Discussion section.]}
+%
 \section*{Appendices}
 
-\textcolor{gray}{[Guidance: If there is more than one appendix, they should 
-be identified as A, B, etc.  Formulae and equations in appendices should be
-given separate numbering: Eq.  (A.1), Eq. (A.2), etc.; in a subsequent
-appendix, Eq. (B.1) and so on.  Similarly for tables and figures: Table A.1;
-Fig. A.1, etc.]}
-
+%\textcolor{gray}{[Guidance: If there is more than one appendix, they should 
+%be identified as A, B, etc.  Formulae and equations in appendices should be
+%given separate numbering: Eq.  (A.1), Eq. (A.2), etc.; in a subsequent
+%appendix, Eq. (B.1) and so on.  Similarly for tables and figures: Table A.1;
+%Fig. A.1, etc.]}
+%
 \begin{table}[!ht]

### 2018-03-27 write_up/mixfishsim_ecolmod.tex
Change bib style of authoryear

@@
 %% Harvard
-%%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
+\bibliographystyle{model2-names.bst}\biboptions{authoryear}
 %% Vancouver numbered
@@
 %% `Elsevier LaTeX' style
-\bibliographystyle{elsarticle-num}
+%%\bibliographystyle{elsarticle-num}
+%%\bibliographystyle{elsarticle-harv}
+
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 %so it must be able to stand alone. For this reason, References should be
-%avoided, but if essential, then cite the author(s) and year(s). Also,
+%avoided, but if essential, then citep the author(s) and year(s). Also,
 %non-standard or uncommon abbreviations should be avoided, but if essential they
@@
 spatial management is crucial in order to implement measures at a resolution
-that ensures effective management\cite{Dunn2016} while minimising economic
+that ensures effective management \citep{Dunn2016} while minimising economic
 impact. For example, a scale that promotes species avoidance for vulnerable or
@@
 impact on previously unexploited areas (e.g. the cod closure in the North
-Sea\cite{Rijnsdorp2001,Dinmore2003}). Since then more refined spatial
+Sea \citep{Rijnsdorp2001,Dinmore2003}). Since then more refined spatial
 information has become available through the combination of logbook and Vessel
-Monitoring System (VMS) data\cite{Lee2010, Bastardie2010, Gerritsen2012,
+Monitoring System (VMS) data \citep{Lee2010, Bastardie2010, Gerritsen2012,
 	Mateo2016} and more real-time spatial management has been possible 
-	(e.g. \cite{Holmes2011}). Such information is, however, patchy and
+	\citep[e.g.][]{Holmes2011}. Such information is, however, patchy and
 derived from an inherently biased sampling programme (i.e. targeted fishing).
@@
 %should be summarized, and indicated by a reference.  If quoting directly from a
-%previously published method, use quotation marks and also cite the source. Any
+%previously published method, use quotation marks and also citep the source. Any
 %modifications to existing methods should also be described.] \\ }
@@
 simulation framework is implemented in the statistical software package R
-\cite{RCoreTeam2017}; available as an R package from the authors github
+\citep{RCoreTeam2017}; available as an R package from the authors github
 (\url{www.github.com/pdolder/MixFishSim}).\\
@@
 The basic population level processes are simulated using a modified two-stage
-Deriso-Schnute delay difference model \cite{Deriso1980, Schnute1985,
+Deriso-Schnute delay difference model \citep{Deriso1980, Schnute1985,
 	Dichmont2003} occurring at a daily time-step. Here, population biomass
@@
 $exp(-K)$, where $K$ is the growth rate from a von bertalanffy logistic growth
-model \cite{Schnute1985}. $Wt_{R-1}$ is the weight of fish prior to
+model \citep{Schnute1985}. $Wt_{R-1}$ is the weight of fish prior to
 recruitment, while $Wt_{R}$ is the recruited weight. $\alpha_{d}$ represents
@@
 mortality, $F$, where both $M$ and $F$ are instantaneous rates with $M$ fixed
-and $F$ calculated by solving the Baranov catch equation \cite{Hilborn1992b}
+and $F$ calculated by solving the Baranov catch equation \citep{Hilborn1992b}
 for $F$:
@@
 either either as a stochastic Beverton-Holt stock-recruit form
-(\cite{Beverton1957}):
+\citep{Beverton1957}:
 
@@
 
-or a stochastic Ricker form \cite{Ricker1954}
+or a stochastic Ricker form \citep{Ricker1954}:
 
@@
 its \textit{covariance function}, $\gamma(x,x') = Cov\{S(x),S(x')\}$
-\cite{Diggle2007}.\\
+\citep{Diggle2007}.\\
 
@@
 through the \textit{RFSimulate} function of the \textit{RandomFields} R package
-\cite{Schlater2015}, implementing different parameter settings to affect the
+\citep{Schlater2015}, implementing different parameter settings to affect the
 patchiness of the populations. Each population is initialised at a single
@@
 
-Several studies (e.g.\cite{Hutton2004, Tidd2012, Girardin2015}) have confirmed
+Several studies \citep[e.g.][]{Hutton2004, Tidd2012, Girardin2015} have confirmed
 past activity and past catch rates are strong predictors of fishing location
@@
 `persistence', providing some overall location of directional movement
-\cite{Codling2008} or uncorrelated. \\
+\citep{Codling2008} or uncorrelated. \\
 
@@
 optimum searching strategy for predators pursuing patchily distributed prey
-\cite{Bartumeus2005, Sims2008}.  \cite{Bertrand2007} showed that Peruvian
+\citep{Bartumeus2005, Sims2008}.  \citet{Bertrand2007} showed that Peruvian
 anchovy fishermen have a stochastic search pattern similar to that observed
@@
 that search patterns may be more simply characteristed as random walks
-\cite{Sakiyama2013} with specific patterns related to the characteristics of
-the prey field \cite{Sims2012}. \\
+\citep{Sakiyama2013} with specific patterns related to the characteristics of
+the prey field \citep{Sims2012}. \\
 
@@
 competition is known to play an important role in local distribution of fishing
-effort \cite{Gillis1998}. If several vessels are fishing on the same patch of
+effort \citep{Gillis1998}. If several vessels are fishing on the same patch of
 fish, local depletion and interference will affect fishing location choice of
-the fleet as a whole \cite{Rijnsdorp2000, Poos2007a}. In order to account for
+the fleet as a whole \citep{Rijnsdorp2000, Poos2007a}. In order to account for
 this behaviour, the fishing sub-model operates spatially on a daily time-step

### 2018-04-05 write_up/mixfishsim_ecolmod.tex
Responses to JM and JJP comments

@@
 \usetikzlibrary{shapes,arrows,chains,calc}
+\usepackage{hhline}
+\usepackage{booktabs}
+
+% For track-changes
+\usepackage[draft]{changes}
+%\usepackage[final]{changes}
+\definechangesauthor[color = red]{JM}
+\definechangesauthor[color = blue]{PD}
+\definechangesauthor[color = green!40!black]{JJ}
+\definechangesauthor[color = purple]{CM}
 
@@
 	Pakefield Road, Lowestoft, UK}
-\address[3]{Université Pierre et Marie Curie, 4 Place Jussieu, 75005 Paris,
-	France}
+\address[3]{\replaced[id=JM]{Sorbonne Université, Faculty of
+		Sciences}{Université Pierre et Marie Curie}, 4 Place Jussieu,
+	75005 Paris, France}
 \address[4]{Wageningen Marine Research, Haringkade 1 1976 CP IJmuiden,
@@
 %
-Fishing exploits spatially and temporally hetergenous fish populations, using
-species-unselective gear that can result in unintended, unwanted catch of low
-quota or protected species. Reducing these unwanted catches is crucial for
-biological and economic sustainability of `mixed fisheries' and implementation
-of an ecosystem approach to fishing. \\
+\replaced[id = JJ]{Most fisheries}{Fishing} exploit\deleted[id=JJ]{s} spatially
+and temporally hetergenous fish populations, using species-unselective gear
+that can result in unintended, unwanted catch of low quota or protected
+species. Reducing these unwanted catches is crucial for biological and economic
+sustainability of `mixed fisheries' and implementation of an ecosystem approach
+to fishing. \\
 
@@
 species-unselective fishing gear. Fisheries that catch an assemblage of
-species, known as mixed fisheries, when managed by single-species quotas can
-end up discarding overquota catch leading to overexploitation of fish
-populations. Reducing discarding is crucial to ensure biological and economic
-sustainability of fisheries and implementation of an ecosystem approach to
-fisheries. As such there is increasing interest in technical solutions such as
-gear and spatial closures as ways of avoiding discards.  \\
+species, known as mixed fisheries \replaced[id=JJ]{may}{, when managed by
+	single-species quotas can end up} discard\deleted[id=JJ]{ing} overquota
+catch \added[id=JJ]{when managed by single species quotas,} leading to
+overexploitation of fish populations \added[id=JJ]{\citep{Ulrich2011a,
+		Batsleer2015}}.  \added[id=JJ]{This discarding of fish in
+	excess of quota hampers the ability to limit fishing mortality to
+	within sustainable limits \citep{Alverson1994, Crowder1998,
+		Rijnsdorp2007}.} Reducing discarding is crucial to ensure
+biological and economic sustainability of fisheries\deleted[id=JJ]{ and
+	implementation of an ecosystem approach to
+	fisheries}\replaced[id=PD]{and}{. As such} there is increasing interest
+in technical solutions such as gear and spatial closures as ways of avoiding
+discard\replaced[id=JJ]{ing of fish \citep{Kennelly2002, Catchpole2008,
+		Bellido2011}}{s}.  \\
 
 Use of spatial management as a tool has been proposed as a method to reduce
-discards. However, its implementation is hampered by lack of knowledge of fish
-and fishery spatiotemporal dynamics and understanding of the scale at which
-processes are important for management. Understanding the correct scale for
-spatial management is crucial in order to implement measures at a resolution
-that ensures effective management \citep{Dunn2016} while minimising economic
-impact. For example, a scale that promotes species avoidance for vulnerable or
-low quota species while allowing continuance of sustainable fisheries for
-available quota species. \\
+discards \added[id=PD]{\citep{Holmes2011, Little2014, Dunn2014a}}. However, its
+implementation is hampered by lack of knowledge of fish and fishery
+spatiotemporal dynamics and understanding of the scale at which processes are
+important for management. Understanding the correct scale for spatial
+management is crucial in order to implement measures at a resolution that
+ensures effective management \citep{Dunn2016} while minimising economic impact.
+For example, a scale that promotes species avoidance for vulnerable or low
+quota species while allowing continuance of sustainable fisheries for available
+quota species. \\
 
@@
 derived from an inherently biased sampling programme (i.e. targeted fishing).
-Further, fishers generally only recorded landings (not catch) on a daily basis.
+Further, fishers generally only recorded landings (not catch) on a daily
+basis\footnote{\added[id=JJ]{Its not clear what the problem is: landed
+		collected on daily basis or landings recorded rather than catch}}.
 This leads to questions about the validity of inference that can be drawn from
-landings data assigned to VMS activity pings. \\
+landings data assigned to VMS activity pings\footnote{\added[id=JJ]{This comes as a
+	surprise: I thought this was going to be about discards}}. \\
 
@@
 typical in fisheries management, and assess a theoretical "benefit" to the
-population, and effect on the other three populations. Further, we extend our
-analysis to a range of spatial and temporal scales to assess the impact of
-these processes on the success of the management measure. \\
+population, and effect on the other three populations\footnote{\added[id=JJ]{If
+		the paper has two goals this should be clear from the start,
+		but may be better over 2 MSs}}. Further, we extend our analysis
+to a range of spatial and temporal scales to assess the impact of these
+processes on the success of the management measure. \\
 
@@
 %
-We develop a simulation model with a modular event-based approach, where
-modules are implemented on independent time-scales appropriate to capture the
-characteristic of the process modelled (Figure 1). The fishing model operated on a
-tow-by-tow basis, while population dynamics (fishing and natural mortality,
-growth) operate on a daily time-step.  Population movement occurs on a
-weekly time-step, while recruitment occurs periodcally each year for a set
-time period (e.g. 3 weeks) at at specified point individual to a species. The
+\replaced[id=PD]{A}{We developed and implemented a simulation model with a}
+modular event-based \replaced{simulation model was developed with}{approach,
+	where} \added[id=PD]{sub-}modules \deleted[id=PD]{are} implemented on
+independent time-scales appropriate to capture the characteristic of the
+\replaced[id=PD]{different processes}{process modelled} (Figure 1).
+\added[id=PD]{The following sub-modules were included to capture the full
+	system: 1) Population dynamics, 2) Recruitment dynamics, 3) Population
+	movement, 4) fishery dynamics.} \\
+
+\deleted[id=PD]{The fishing model operated on a tow-by-tow basis, while}
+\replaced[id=PD]{P}{p}opulation dynamics (fishing and natural mortality,
+growth) operate on a daily time-step\replaced[id=PD]{, while p}{. P}opulation
+movement occurs on a weekly time-step\replaced[id=PD]{. R}{, while r}ecruitment
+\replaced[id=PD]{takes place}{occurs} periodcally each year for a set time
+\replaced[id=PD]{duration}{period (e.g. 3 weeks)} at at specified point
+individual to a species\deleted[id=PD]{.}\added[id=PD]{, while the fishing
+	module operates on a tow-by-tow basis (multiple events a day)}. The
 simulation framework is implemented in the statistical software package R
-\citep{RCoreTeam2017}; available as an R package from the authors github
-(\url{www.github.com/pdolder/MixFishSim}).\\
+\citep{RCoreTeam2017} \replaced[id=PD]{and}{;} available as an R package from
+the authors github (\url{www.github.com/pdolder/MixFishSim}).\\
 
-Here we describe each of the model components; 1)
-Population dynamics, 2) Recruitment dynamics, 3) Population movement, 4)
-fishery dynamics.
+\deleted[id=PD]{Here we describe each of the model components; 1)
+Population dynamics, 2) Recruitment dynamics, 3) Population movement dynamics, 4)
+fishery dynamics.}
 
@@
 Deriso-Schnute delay difference model \citep{Deriso1980, Schnute1985,
-	Dichmont2003} occurring at a daily time-step. Here, population biomass
-growth and depletion for pre-recruits and fish recruited to the fishery are
-modelled separately as a function of previous recruited biomass, intrinsic
-population growth and recruitment:
+	Dichmont2003} occurring at a daily time-step. \added[id=PD]{A daily
+	time-step was chosen as to discretise continuous population processes
+	on a biologically relevent and computationally tractable timescale.}
+\replaced[id=PD]{Under the popualation dynamics module}{Here,} population
+biomass growth and depletion for pre-recruits and \deleted[id=PD]{fish}
+recruited \added[id=PD]{fish} \deleted[id=PD]{to the fishery} are modelled
+separately as a function of previous recruited biomass, intrinsic population
+growth and recruitment:
 
@@
 	\begin{split}
-	B_{y,d+1} = &\\
-	& (1 + \rho) B_{y,d} \cdot e^{-Z_{y,d}} - \rho \cdot e^{-Z_{y,d}} \hspace{2.9cm}
+	B_{c,d+1} = &\\
+	& (1 + \rho) B_{c,d} \cdot e^{-Z_{c,d}} - \rho \cdot e^{-Z_{c,d}} \hspace{2.9cm}
 	\times \\  
-	& (B_{y,d-1} \cdot e^{-Z_{y,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot R_{\tilde{y}(y,d-1)})
+	& (B_{c,d-1} \cdot e^{-Z_{c,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot
+	R_{\tilde{y}(c,y,d-1)})
 	\hspace{0.4cm} + \\
-	& Wt_{R} \cdot \alpha_{d} \cdot R_{\tilde{y}(y,d)} 
+	& Wt_{R} \cdot \alpha_{d} \cdot R_{\tilde{y}(c,y,d)} 
 	\end{split}
@@
 the proportion of fish recruited during that day for the year, while
-$R_{\tilde{y}}$ is the annual recruits. \\
+$R_{\tilde{c,y}}$ is the annual recruits in cell $c$ for year $y$. \\
 
-Mortality $Z$ can be decomposed to natural mortality, $M$, and fishing
-mortality, $F$, where both $M$ and $F$ are instantaneous rates with $M$ fixed
-and $F$ calculated by solving the Baranov catch equation \citep{Hilborn1992b}
-for $F$:
+Mortality $Z_{c,d}$ can be decomposed to natural mortality, $M_{c,d}$, and
+fishing mortality, $F_{c,d}$, where both $M_{c,d}$ and $F_{c,d}$ are
+instantaneous rates with $M_{c,d}$ fixed and $F_{c,d}$ calculated by solving
+the Baranov catch equation \citep{Hilborn1992b} for $F_{c,d}$:
 
 \begin{equation*}
-C_{d} = \frac{F_{d}}{F_{d}+M_{d}} * (1 - e^{-(F_{d} + M_{d})}) * B
+C_{c,d} = \frac{F_{c,d}}{F_{c,d} + M_{c,d}} * (1 - e^{-(F_{c,d} + M_{c,d})}) *
+B_{c,d}
 \end{equation*}
 
-where $C$ is the summed catch from the fishing model across all fleets and
-vessels for the population during the day, and $B$ the daily biomass for the
-species. \textcolor{red}{[link $F$ to effort and catchability - as I think we
-	have F as an emergent property of the fleets rather than something we
-	solve for (I could be wrong though!) - catch for a vessel is a product of
-	catchability and biomass, i.e. C = qB, but this catch is summed to
-	solve for F. So its both really]}\\
+where $C_{c,d}$ is the summed catch from the fishing model across all fleets
+and vessels in cell $c$ for the population during the day $d$, and $B_{c,d}$
+the daily biomass for the population in the cell. \textcolor{red}{[link $F$ to
+	effort and catchability - as I think we have F as an emergent property
+	of the fleets rather than something we solve for (I could be wrong
+	though!) - catch for a vessel is a product of catchability and biomass,
+	i.e. C = qB, but this catch is summed to solve for F. So its both
+	really]}\\
 
@@
 	\begin{split}
-	\bar{R} = & \frac{(\alpha * B)}{(\beta + B)} \\
-	     R \sim & \log N[(\log(\bar{R}),\log(\sigma^2))]
+	\bar{R}_{c,d} = & \frac{(\alpha * B_{c,d})}{(\beta + B_{c,d})} \\
+	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\log(\sigma^2))]
 	\end{split}
@@
 	\begin{split}
-	\bar{R} = & B * e^{(\alpha - \beta * B)} \\	
-   	     R \sim & \log N[(\log(\bar{R}),\log(\sigma^2))]
+	\bar{R}_{c,d} = & B_{c,d} * e^{(\alpha - \beta * B_{c,d})} \\	
+   	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\log(\sigma^2))]
 	\end{split}
@@
 
-\subsection{Population movement}
+\subsection{Population movement dynamics}
 
@@
 %
+
+\begin{table}[!ht]
+	\centering
+	\caption{Description of variables for sub-modules}
+	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
+		\toprule
+		Variable & Meaning & Units \\
+		\hline
+		\multicolumn{3}{c}{\textbf{Population dynamics}}  \\
+		\hhline{===}
+		\multicolumn{3}{l}{\textit{Delay-difference model}} \\
+		\hline
+		$B_{c,d}$ & Biomass in cell $c$ and day $d$ & kg \\
+		$Z_{c,d}$ & Total mortality in cell $c$ for day $d$ & - \\
+		$R_{c, \tilde{y}}$  &Annualy recruited fish in cell &  yr\textsuperscript{-1} \\
+		$\rho$ & Brody's growth coefficient & yr\textsuperscript{-1} \\
+		$Wt_{R}$ & Weight of a fully recruited fish & kg \\
+		$Wt_{R-1}$ & Weight of a pre-recruit fish & kg \\
+		$\alpha_{d}$ & Proportion of annually recruited fish recruited
+		during day $d$ & - \\
+		\hline
+		\multicolumn{3}{l}{\textit{Baranov catch equation}} \\
+		\hline
+		$C_{c,d}$ & Catch from cell $c$ for day $d$ & kg \\
+		$F_{c,d}$ & Instantaneous rate of fishing mortality in cell $c$
+		on day $d$ & - \\
+		$M_{c,d}$ & Instantaneous rate of natural mortality in cell $c$
+		on day $d$ & - \\
+		$B_{c,d}$ & Biomass in cell $c$ on day $d$ & kg \\
+		\hline
+		\multicolumn{3}{c}{\textbf{Recruitment dynamics}} \\
+		\hhline{===}
+		$\tilde{R}_{c,d}$ & is the recruitment in cell $c$ for day $d$ & $d^{-1}$ \\
+		$B_{c,d}$ & is the Biomass in cell $c$ for day $d$ & $d^{-1}$ \\
+		$\alpha$ & the maximum recruitment rate & kg  \\
+		$\beta$ & the biomass required to produce half the maximum rate
+		of recruitment & kg \\
+		\hline
+		\multicolumn{3}{c}{\textbf{Population movement dynamics}} \\
+		\hhline{===}
+		a & b & c \\
+		a & b & c \\
+		\hline
+		\multicolumn{3}{c}{\textbf{Fleet dynamics}} \\
+		\hhline{===}
+		a & b & c \\
+		a & b & c \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
 \begin{table}[!ht]

### 2018-04-06 write_up/mixfishsim_ecolmod.tex
Continued text edits in response to comments

@@
 \usepackage{booktabs}
+\usepackage[textsize=scriptsize]{todonotes}
+%\usepackage[textsize=scriptsize, disable]{todonotes}  %% to turn off notes
 
@@
 \usepackage[draft]{changes}
-%\usepackage[final]{changes}
+%\usepackage[final]{changes} %% to turn off changes
 \definechangesauthor[color = red]{JM}
@@
 Further, fishers generally only recorded landings (not catch) on a daily
-basis\footnote{\added[id=JJ]{Its not clear what the problem is: landed
+basis\todo{\added[id=JJ]{Its not clear what the problem is: landed
 		collected on daily basis or landings recorded rather than catch}}.
 This leads to questions about the validity of inference that can be drawn from
-landings data assigned to VMS activity pings\footnote{\added[id=JJ]{This comes as a
+landings data assigned to VMS activity pings\todo{\added[id=JJ]{This comes as a
 	surprise: I thought this was going to be about discards}}. \\
@@
 typical in fisheries management, and assess a theoretical "benefit" to the
-population, and effect on the other three populations\footnote{\added[id=JJ]{If
+population, and effect on the other three populations\todo{\added[id=JJ]{If
 		the paper has two goals this should be clear from the start,
@@
 and vessels in cell $c$ for the population during the day $d$, and $B_{c,d}$
-the daily biomass for the population in the cell. \textcolor{red}{[link $F$ to
+the daily biomass for the population in the cell. \todo{\added[id=CM]{[link $F$ to
 	effort and catchability - as I think we have F as an emergent property
@@
 	i.e. C = qB, but this catch is summed to solve for F. So its both
-	really]}\\
+	really]}}\\
 
@@
 
-To simulate how fish populations might be distributed in space and time, we
-employed a Gaussian spatial process to model habitat suitability for each of
-the populations, with an advection-diffusion process to control how the
-populations moved over time with a moving temperature covariate to capture
-temporal dependencies. This was intended to balance realism in population
-movement, capturing the main directed and random processes, and practicality of
-modelling the population rather than individual fish. \\
-
-For the habitat we define a Gaussian random field process, $\{S(x) : x \in
-\mathbb{R}^2\}$, that is a stochastic process where any collection of locations
-$x_{1}, \dots, x_{n}$ where for each $x_{i} \in \mathbb{R}^2$, the joint
-distribution of $S = \{S(x1),\dots S(x_{n})\}$ is multivariate Gaussian. The
-distribution is specified by its \textit{mean function}, $\mu(x) = E[S(x)]$ and
-its \textit{covariance function}, $\gamma(x,x') = Cov\{S(x),S(x')\}$
-\citep{Diggle2007}.\\
+To simulate \deleted[id=JJ]{how} fish population\deleted[id=JJ]{s might be}
+distribut\replaced[id=JJ]{ion}{ed} in space and time\deleted[id=JJ]{, we
+	employed} a Gaussian spatial process \added[id=JJ]{was employed} to
+model habitat suitability for each of the populations\replaced[id=JJ]{. An}{,
+	with an} advection-diffusion process \deleted[id=JJ]{to}
+control\added[id=JJ]{led} \deleted[id=JJ]{how the} population\deleted[id=JJ]{s}
+move\replaced[id=JJ]{ment}{d} over time with a moving temperature covariate to
+capture temporal dependencies\todo{\added[id=JJ]{What have a temperature
+		covariate? Could just use time}\added[id=PD]{Was intended as
+		some biological meaning - species thermal tolerances load onto
+		the temperature effect}}. \deleted[id=JJ]{This was intended to
+	balance realism in population movement, capturing the main directed and
+	random processes, and practicality of modelling the population rather
+	than individual fish.} \\
+
+For \deleted[id=PD]{the} habitat we define\added[id=PD]{d} a Gaussian random
+field process\todo{\added[id=JJ]{Not clear how habitat/GRF affect local
+		abundances, only have $B_{y,d}$}\added[id=PD]{Have included
+		cell reference, $c$ to make spatial link explicit}}, $\{S(c) :
+c \in \mathbb{R}^2\}$, \deleted[id=PD]{that is a stochastic process} where
+\added[id=PD]{for} any set of cells $c_{1}, \dots, c_{n}$ \deleted[id=PD]{where
+	for each $c_{i} \in \mathbb{R}^2$}, the joint distribution of $S =
+\{S(c1),\dots S(c_{n})\}$ is multivariate Gaussian. The distribution is
+specified by its \textit{mean function}, $\mu(c) = E[S(c)]$ and its
+\textit{covariance function}\todo{\added[id=JM]{Introduce the gamma function,
+		and why this covariance structure? Why correlate values in the
+		random field?}\added[id=PD]{to allow populations to have
+		different aggregation densities: have tried to clarify}},
+$\gamma(c,c') = Cov\{S(c),S(c')\}$ \citep{Diggle2007}.\\
 
 The covariance structure affects the smoothness of the surfaces which the
-process generates, and we used the \textit{Matérn} family of covariance
-structures, one where the correlation strength weakens the further the distance
-apart (i.e. the correlation between $S(x)$ and $S(x')$ decreases as the
-distance $u = ||x - x'||$ increases).  The \textit{Matérn} correlation is a
-two-parameter family where: \\
+process generates\replaced[id=PD]{;}{, and} we used the \textit{Matérn}
+\deleted[id=PD]{family of} covariance structure\deleted[id=PD]{s},
+\replaced[id=PD]{as}{one where} the correlation strength weakens the further
+the distance apart \deleted[id=PD]{(i.e. the correlation between $S(x)$ and
+	$S(x')$ decreases as the distance $u = ||x - x'||$ increases)}.
+\added[id=PD]{The Matérn covariance structure models the spatial
+	autocorrelation observed with animal distributions \citep{Tobler1970,
+		F.Dormann2007}} \replaced[id=PD]{and}{The \textit{Matérn}
+	correlation} is a two-parameter family where:
 
@@
 
-The temperature field is simulated to be on a gradient from a South-Westerly to
-North-Easterly direction, with temperature in each cell changing gradually on a
-week-by-week basis so that initially high temperature areas cycle to lower
-temperatures and low temperature areas vice versa. Each population is assigned
-a thermal tolerance with mean, $\mu$ and variance, $\sigma^2$ so that each cell
-and population temperature suitability is defined that:
+\replaced[id=PD]{T}{In the simulation model, t}he habitat for each of the
+populations \replaced[id=PD]{was}{is} generated \replaced[id=PD]{with}{through}
+the \textit{RFSimulate} function of the \textit{RandomFields} R package
+\citep{Schlater2015}, implementing different parameter settings to affect the
+patchiness of the populations. Each population \replaced[id=PD]{was}{is}
+initialised at a single location, and subsequently move\replaced[id=PD]{ed}{s}
+according to a probabilistic distrib\added[id=PD]{u}tion based on habitat
+suitability, temperature and distance from current cell\replaced[id=PD]{:}{.}
+
+\begin{equation}
+	Pr(J | I) = \frac{e^{-\lambda * d_{IJ}} \cdot
+		(Hab_{J,p}^2 \cdot Tol_{J,p,wk})}{\sum\limits_{c=1}^{C}e^{-\lambda * d} \cdot
+		(Hab_{J,p}^2 \cdot Tol_{J,p,wk})}
+\end{equation}
+
+Where $d_{IJ}$ is the euclidean distance between cell $I$ and cell $J$,
+$\lambda$ is a given rate of decay, $Hab_{J,p}^2$ is the squared index of
+habitat suitability for cell $J$ and population $p$, with $Tol_{J,p,wk}$ the
+temperature tolerance for cell $J$ by population $p$ in week $wk$.\\
+
+During specified weeks of the year, the habitat quality
+\replaced[id=PD]{was}{is} modified for \added[id=PD]{user-defined} spawning
+habitat\deleted[id=PD]{s}, \replaced[id=PD]{resulting in}{meaning} each
+population \replaced[id=PD]{had}{has} a concentrated area where spawning takes
+place and the population move\replaced[id=PD]{d}{s} towards
+\replaced[id=PD]{these cells}{this} in the weeks prior to
+spawning.\todo{\added[id=JM]{What does it mean concisely? Areas are assigned?}
+\added[id=PD]{Yes, the areas are pre-defined - I have amended to reflect and
+	tried to clarify}} \\
+
+The temperature field \replaced[id=PD]{was}{is} simulated to be on a gradient
+from a South-Westerly to North-Easterly direction, with temperature in each
+cell changing gradually on a week-by-week basis so that initially high
+temperature areas cycle\added[id=PD]{d} to lower temperatures and low
+temperature areas vice versa. Each population $p$ \replaced[id=PD]{wa}{i}s
+assigned a thermal tolerance with mean, $\mu\added[id=PD]{_{p}}$ and variance,
+$\sigma^2\added[id=PD]{_{p}}$ so that each cell and population temperature
+suitability is defined that:
 
@@
 Where $Tol_{c,p}$ is the tolerance of population $p$ in cell $c$, $T_{c}$ is
-the temperature in the cell and $\mu$ and $\sigma^2$ the mean and standard
-deviation of the population temperature tolerance. \\
-
-In the simulation model, the habitat for each of the populations is generated
-through the \textit{RFSimulate} function of the \textit{RandomFields} R package
-\citep{Schlater2015}, implementing different parameter settings to affect the
-patchiness of the populations. Each population is initialised at a single
-location, and subsequently moves according to a probabilistic distribtion based
-on habitat suitability, temperature and distance from current cell.
-
-\begin{equation}
-	Pr(B | A) = \frac{e^{-\lambda * d_{AB}} \cdot
-		(Hab_{B}^2 \cdot Tol_{B,wk})}{\sum\limits_{c=1}^{C}e^{-\lambda * d} \cdot
-		(Hab_{B}^2 \cdot Tol_{B,wk})}
-\end{equation}
-
-Where $d_{AB}$ is the euclidean distance between cell $A$ and cell $B$,
-$\lambda$ is a given rate of decay, $Hab_{B}^2$ is the squared index of habitat
-suitability for cell $B$ and $Tol_{B,wk}$ the temperature tolerance for the
-cell in week $wk$; population index, $p$ has been dropped for simplicity.\\
-
-During specified weeks of the year, the habitat quality is modified for
-spawning habitats, meaning each population has a concentrated area where
-spawning takes place and the population moves towards this in the weeks prior
-to spawning. \\
+the temperature in the cell and $\mu\added[id=PD]{_{p}}$ and
+$\sigma^2\added[id=PD]{_{p}}$ the mean and standard deviation of the population
+temperature tolerance. \\
+
+\added[id=PD]{The final process resulted in independent populations structure
+	and movement patterns, with population movement occuring on a weekly
+	basis. This process approximated the demographic shifts in fish
+	populations throughout a year while maintaining seasonal patterns for
+	spawning.}
 

### 2018-04-06 write_up/mixfishsim_ecolmod.tex
Text updates

@@
 The fleet dynamics can be broadly categorised into three components; fleet
-targeting - which determines the fleet catch efficiency and preference towards
-a particular species; trip-level decisions, which determine the initial
-location to be fished at the beginning of a trip; and within-trip decisions,
-determining movement from one fishing spot to another within a trip.
+targeting - which determine\replaced[id=PD]{d}{s} the fleet catch efficiency
+and preference towards a particular species; trip-level decisions, which
+determine\added[id=PD]{d} the initial location to be fished at the beginning of
+a trip; and within-trip decisions, determining movement from one fishing spot
+to another within a trip.
 
@@
 
-Each fleet of \textit{n} vessels is characterised by both a general efficiency,
-\textit{Q}, and a population specific efficiency, ${Q_{p}}$.  Thus, the product
-of these parameters affects the overall catch rates for the fleet and the
-preferential targeting of one population over another. This, in combination
-with the parameter choice for the step-function (as well as some randomness
-from the exploratory fishing process) determines the preference of fishing
-locations for the fleet.  All species prices are kept the same, across fleets,
-though can be made to vary seasonally.
+Each fleet of \textit{n} vessels \replaced[id=PD]{was}{is} characterised by
+both a general efficiency, \textit{Q}, and a population specific efficiency,
+${Q_{p}}$.  Thus, the product of these parameters affect\replaced[id=PD]{s}{ed}
+the overall catch rates for the fleet and the preferential targeting of one
+population over another. This, in combination with the parameter choice for the
+step-function \added[id=PD]{defined below} (as well as some randomness from the
+exploratory fishing process) determine\replaced[id=PD]{d}{s} the preference of
+fishing locations for the fleet.  All species prices
+\replaced[id=PD]{were}{are} kept the same, across fleets\replaced[id=PD]{and
+seasons}{, though can be made to vary seasonally}.
 
@@
 
-Several studies \citep[e.g.][]{Hutton2004, Tidd2012, Girardin2015} have confirmed
-past activity and past catch rates are strong predictors of fishing location
-choice. For this reason, the fleet dynamics sub-model includes a learning
-component, where a vessel's initial fishing location in a trip is based on
-selecting from previously successful fishing locations. This is achieved by
-sorting all previous fishing events in the previous trip as well as the
-previous time periods in past years, and choosing randomly from the top x \% of
-fishing events in value.  Simulation testing indicated that this learning
-increased the mean value of catches for the vessels, over just relying on the
-correlated random walk function.
+Several studies \citep[e.g.][]{Hutton2004, Tidd2012, Girardin2015} have
+confirmed past activity and past catch rates are strong predictors of fishing
+location choice. For this reason, the fleet dynamics sub-model
+include\replaced[id=PD]{d}{s} a learning component, where a vessel's initial
+fishing location in a trip \replaced[id=PD]{wa}{i}s based on selecting from
+previously successful fishing locations. This \replaced[id=PD]{wa}{i}s achieved
+by sorting all previous fishing events in the previous trip as well as the
+previous time periods in past years, and choosing randomly from the top 75 \%
+of fishing events \replaced[id=PD]{as defined by the revenue gained}{in value}.
+Simulation testing indicated that this learning increased the mean value of
+catches for the vessels, over just relying on the correlated random
+walk \todo{\added[id=JJ]{Correlated random walk of what}} function
+\added[id=PD]{as described for the 'within trip' decisions below}.
 
@@
 process. A random walk type was chosen as it is the simplest assumption
-commonly used in ecology to describe animal movement which searching for
-homogeneously distributed prey about which there is uncertain knowledge. In a
-random walk, movement is a stochastic process through a series of steps that
-can either be equal in length or take some other functional form.  The
-direction of the random walk can be correlated, a characteristic known as
-`persistence', providing some overall location of directional movement
-\citep{Codling2008} or uncorrelated. \\
-
-A \textit{lévy walk} is a particular form of random walk characterised by a
-heavy-tailed distribution of step-length and has received a lot of attention in
+commonly used in ecology to describe \added[id=PD]{optimal} animal
+\deleted[id=PD]{movement which} search\replaced[id=PD]{ strategy}{ing} for
+\added[id=PD]{exploiting} homogeneously distributed prey about which there is
+uncertain knowledge \citep{Viswanathan1999}. In a random walk, movement is a
+stochastic process through a series of steps\added[id=JJ]{. These steps have a
+	length, and a direction} that can either be equal in length or take
+some other functional form. The direction of the random walk can be correlated,
+a characteristic known as `persistence', providing some overall
+\deleted[id=PD]{location of} directional movement \citep{Codling2008}
+\deleted[id=PD]{or uncorrelated}. \\
+
+A \textit{\replaced[id=JJ]{Lévy flight} {lévy walk}} is a particular form of
+random walk characterised by a heavy-tailed distribution of step-length
+\replaced[id=JJ]{. The Lévy flight}{and} has received a lot of attention in
 ecological theory in recent years as having shown to have very similar
@@
 optimum searching strategy for predators pursuing patchily distributed prey
-\citep{Bartumeus2005, Sims2008}.  \citet{Bertrand2007} showed that Peruvian
-anchovy fishermen have a stochastic search pattern similar to that observed
-with a lévy walk. However, it remains a subject of debate, with the contention
-that search patterns may be more simply characteristed as random walks
-\citep{Sakiyama2013} with specific patterns related to the characteristics of
-the prey field \citep{Sims2012}. \\
+\citep{Viswanathan1999, Bartumeus2005, Sims2008}.  \citet{Bertrand2007} showed
+that Peruvian anchovy fishermen have a stochastic search pattern similar to
+that observed with a lévy walk. However, it remains a subject of debate
+\added[id=PD]{\citep[e.g. see][]{Edwards2011, Reynolds2015}}, with the
+contention that search patterns may be more simply characteristed as random
+walks \citep{Sakiyama2013} with specific patterns related to the
+characteristics of the prey field \citep{Sims2012}. \\
 
 We use a modified random walk where directional change is based on a correlated
-circular distribution where a favourable fishing ground is likely to be ``fished
-back over" by the vessel returning in the direction it came from and step
-length (i.e. the distance travelled from the current to the next fishing
-location) is determined by relating recent fishing success, measured as the
-summed value of fish caught, $$Rev = \sum_{s=1}^{\infty} C_{s} \cdot Pr_{s}$$
-where $C_{s}$ is catch of a species, and $Pr_{s}$ price of a species, to step
-distance. Here, when fishing is successful vessels remain in a similar location
-and continue to exploit the local fishing grounds. When unsuccessful, they move
-some distance away from the current fishing location. The movement distance
-retains some degree of stochasticity, which can be controlled separately.
+circular distribution where a favourable fishing ground is likely to be
+``fished back over" by the vessel returning in the direction it came from and
+step length (i.e. the distance travelled from the current to the next fishing
+location) is determined by \deleted[id=JJ]{relating} recent fishing success,
+measured as the summed value of fish caught (revenue, $Rev$), $$Rev =
+\sum_{p=1}^{P} \replaced[id=PD]{L}{C}_{p} \cdot Pr_{p}$$ where
+$\replaced[id=PD]{L}{C}_{p}$ is \replaced[id=PD]{landings}{catch} of a
+population $p$, and $Pr_{p}$ price of a population, to step distance. Here,
+when fishing is successful vessels remain in a similar location and continue to
+exploit the local fishing grounds.  When unsuccessful, they move some distance
+away from the current fishing location.  The movement distance retains some
+degree of stochasticity, which can be controlled separately.
 
@@
 \begin{equation*}
-	StepL = e^{log(\beta_{1}) + log(\beta_{2}) - (log(\frac{\beta_{1}}{\beta_{3}}))} * Rev
-\end{equation*}
+	StepL = e^{log(\beta_{1}) + log(\beta_{2}) -
+		(log(\frac{\beta_{1}}{\beta_{3}}))} * Rev
+\end{equation*}\todo{\added[id=JJ]{So
+			step length increases with increasingly gross
+			revenue?}\added[id=PD]{No, the opposite}}
 
@@
 
-with $k$ the concentration parameter from the von mises distribution which we
-correlate with the revenue so that $k = (Rev + 1 / RefRev) * max_{k}$,
-where $max_{k}$ is the maximum concentration value, $k$, and RefRev is
-parameterised as for $\beta_{3}$ in the step length function.
+with $k$ the concentration parameter from the von \replaced[id=JJ]{M}{m}ises
+distribution which we correlate with the revenue so that $k = (Rev + 1 /
+RefRev) * max_{k}$, where $max_{k}$ is the maximum concentration value, $k$,
+and RefRev is parameterised as for $\beta_{3}$ in the step length function.
 
@@
 effort \citep{Gillis1998}. If several vessels are fishing on the same patch of
-fish, local depletion and interference will affect fishing location choice of
-the fleet as a whole \citep{Rijnsdorp2000, Poos2007a}. In order to account for
-this behaviour, the fishing sub-model operates spatially on a daily time-step
-so that for future days the biomass available to the fishery is reduced in the
-areas fished. The cumulative effect is to make heavily fished areas less
-attractive as future fishing opportunities.
+fish, local depletion and interference \added[id=JJ]{competition} will affect
+fishing location choice of the fleet as a whole \citep{Rijnsdorp2000,
+	Poos2007a}. In order to account for this behaviour, the fishing
+sub-model operates spatially on a daily time-step so that for future days the
+biomass available to the fishery is reduced in the areas fished. The cumulative
+effect is to make heavily fished areas less attractive as future fishing
+opportunities.
 
@@
 begins each year at the same time for a given number of stations (a fixed
-station survey design). Catches of the populations present are recorded but not
-removed from the population. This provides a fishery independent snapshot of
-the populations at a regular spatial distribution each year, similar to
-scientific surveys undertaken by fisheries research agencies.
+station survey design). Catches of the populations \replaced[id=JJ]{at each
+station}{present} are recorded but not removed from the population. This
+provides a fishery independent snapshot of the populations at a regular spatial
+\replaced[id=JJ]{intervals}{distribution} each year, similar to scientific
+surveys undertaken by fisheries research agencies.
 

### 2018-04-06 write_up/mixfishsim_ecolmod.tex
Text updates

@@
 	population movement, $day$ is a day timestep, $trip$ is a trip time
-	step. 
+	step. \textcolor{red}{I NEED TO REDO THIS TO MAKE NOTATION MORE CONCISE
+		AND CONSISTENT} 
 	} 
@@
 We parameterised the simulation model for four populations with differing
-habitat preference and temperature tolerances (Figures \ref{S-fig:1},
-\ref{S-fig:3}, \ref{S-fig:4}, \ref{S-fig:5}, \ref{S-fig:6}, \ref{S-fig:7}),
-population demographic and recruitment functions. In addition, each of the
-populations has two defined spawning areas which result in the populations
-moving towards these areas in given weeks (Figure \ref{S-fig:2}) and
-population-specific movement rates (Table \ref{tab:1}). The realised movement
-of the populations for a number of weeks is shown in Figure \ref{S-fig:9} while
-the realised daily fishing mortality are shown in Figure \ref{S-fig:10}. \\
+habitat preference\replaced{,}{ and} temperature tolerances (Figures
+\ref{S-fig:1}, \ref{S-fig:3}, \ref{S-fig:4}, \ref{S-fig:5}, \ref{S-fig:6},
+\ref{S-fig:7}), population demographic\replaced{,}{ and} recruitment functions.
+In addition, each of the populations has two defined spawning areas which
+result in the populations moving towards these areas in given weeks (Figure
+\ref{S-fig:2}) and population-specific movement rates (Table \ref{tab:1}). The
+realised movement of the populations for a number of weeks is shown in Figure
+\ref{S-fig:9} while the realised daily fishing mortality are shown in Figure
+\ref{S-fig:10}. \\
 
@@
 The fleets were parameterised to reflect five different characteristics based
-on targeting preference and exploitation dynamics (Table \ref{tab:2}). This
-ensures that different fleets have different spatial dynamics, preferentially
-targeted different fish populations. The stochasticity in the random walk
-process ensures that different vessels within a fleet have slightly different
-spatial distributions based on individual experience, while the step function
-was parameterised dynamically so that vessels take smaller steps where the
-fishing location yields in a top quartile of the value available in that year
-(as defined per fleet in Table \ref{tab:2}). \\
+on targeting preference and exploitation dynamics (Table \ref{tab:2}).
+\replaced[id=PD]{Setting a targeting parameter ($Q$) that differed across
+	fleets ensured different spatial dynamics, due to preferential
+	targeting of populations that differ in their spatial
+	distributions}{This ensures that different fleets have different
+	spatial dynamics, preferentially targeted different fish populations}.
+The stochasticity in the random walk process ensures that different vessels
+within a fleet have slightly different spatial distributions based on
+individual experience, while the step function was parameterised dynamically so
+that vessels take smaller steps where the fishing location yields in a top
+quartile of the value available in that year (as defined per fleet in Table
+\ref{tab:2}). \\
 
@@
 trip are given in Figure \ref{S-fig:11}, while Figure \ref{S-fig:12} shows
-multiple trips for a single vessel, \ref{S-fig:13} the vessel movements for
-some trips overlaid on the value field, \ref{S-fig:14} shows fishing locations
-for an entire fleet of 20 vessels for a single trip, while \ref{S-fig:15} shows
-an example of the step function realisation and turning angles from the
-correlated random walk.
+multiple trips for a single vessel, \added[id=PD]{Figure} \ref{S-fig:13} the
+vessel movements for some trips overlaid on the value field,
+\added[id=PD]{Figure} \ref{S-fig:14} shows fishing locations for an entire
+fleet of 20 vessels for a single trip, \replaced[id=PD]{and Figure}{while}
+\ref{S-fig:15} shows an example of the step function realisation and turning
+angles from the correlated random walk.\todo{\added[id=JJ]{Move some of the
+	supplementary figures to the manuscript}}
 
@@
 The survey simulation was set up with follow a fixed gridded station design
-with 100 stations fished each year, starting on day 92 with same catchability
-parameters for all populations (Q = 1).
+with 100 stations fished each year, starting on day 92 \added[id=PD]{and ending
+	on day 112 (5 stations per day)} with same catchability parameters for
+all populations ($Q_{p} = 1$).
 
@@
 takes place four times a day per vessel and five days a week, while population
-movement is every week. \\
-
-We allow the simulation to run unrestricted for 5 years, and subsequently close
-areas for the last 5 years of the simulation based on data (either derived from
-the commercial catches, fisheries-independent survey or the 'real population' -
-the underlying populations assumed to be known perfectly) used at different
-spatial and temporal scales. \\
-
-The following steps are undertaken to determine closures:
+movement is every week.\todo{\added[id=JJ]{move to start of methods
+		section}\added[id=PD]{I think ecological modelling wants the
+		'calculations' section here..will check}} \\
+
+We allow the simulation to run unrestricted for 5 years\todo{\added[id=JJ]{Is
+		there equilibrium after 5 years or still some trend in
+		B}\added[id=PD]{Not at equilibrium yet...I need to rerun until
+		steady state, looks 20 years. Will update}}, and
+subsequently close areas for the last 5 years of the simulation based on data
+(either derived from the commercial catches, fisheries-independent survey or
+the 'real population' - the underlying populations assumed to be known
+perfectly) used at different spatial and temporal scales. \\
+
+The following steps are undertaken to determine
+closures:\todo{\added[id=JJ]{Procedure unclear. Refer to symbols in
+		methods section or switch order starting with description of
+		data type	etc..}\added[id=PD]{Yes, will redo}}
 

### 2018-04-10 write_up/mixfishsim_ecolmod.tex
manuscript updates: table for models

@@
 %\usepackage[textsize=scriptsize, disable]{todonotes}  %% to turn off notes
+\usepackage{eurosym}
 
@@
 		(Hab_{J,p}^2 \cdot Tol_{J,p,wk})}{\sum\limits_{c=1}^{C}e^{-\lambda * d} \cdot
-		(Hab_{J,p}^2 \cdot Tol_{J,p,wk})}
+		(Hab_{c,p}^2 \cdot Tol_{c,p,wk})}
 \end{equation}
@@
 \begin{equation}
-	Tol_{c, p} = \frac{1}{ \sqrt (2\pi \cdot \sigma^2_{p})} \cdot \exp(-
-		\frac{(T_{c} -
-		\mu_{p})^2}{2 \cdot \sigma^2_{p}} )	
+	Tol_{c, p\added[id=PD]{, wk}} = \frac{1}{ \sqrt (2\pi \cdot \sigma^2_{p})} \cdot \exp(-
+		\frac{(T_{c\added[id=PD]{, wk}} - \mu_{p})^2}{2 \cdot \sigma^2_{p}} )	
 \end{equation}
 
-Where $Tol_{c,p}$ is the tolerance of population $p$ in cell $c$, $T_{c}$ is
-the temperature in the cell and $\mu\added[id=PD]{_{p}}$ and
-$\sigma^2\added[id=PD]{_{p}}$ the mean and standard deviation of the population
-temperature tolerance. \\
+Where $Tol_{c, p, \added[id=PD]{wk}}$ is the tolerance of population $p$ in
+cell $c$ \added[id=PD]{in week $wk$}, $T_{c, \added[id=PD]{wk}}$ is the
+temperature in the cell \added[id=PD]{given the week} and
+$\mu\added[id=PD]{_{p}}$ and $\sigma^2\added[id=PD]{_{p}}$ the mean and
+standard deviation of the population temperature tolerance. \\
 
@@
 	\centering
-	\caption{Description of variables for sub-modules}
+	\caption{Description of variables for population dynamics sub-module}
 	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
@@
 		of recruitment & kg \\
+		\bottomrule
+		\end{tabular}
+	\end{table}
+
+\begin{table}[!ht]
+	\centering
+	\caption{Description of variables for population movement sub-module}
+	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
+		\toprule
+		Variable & Meaning & Units \\
 		\hline
@@
 		\hhline{===}
+		\multicolumn{3}{l}{\textit{Habitat model}} \\
+		\hline
 		a & b & c \\
-		a & b & c \\
-		\hline
-		\multicolumn{3}{c}{\textbf{Fleet dynamics}} \\
+		\hline
+		\multicolumn{3}{l}{\textit{Thermal tolerance}} \\
+		\hline
+		$T_{c,wk}$ & Temperature for cell in week & $^\circ$C \\
+		$\mu_{p}$ & Mean of the thermal tolerance for population & $^\circ$C \\
+		$\sigma^{2}_{p}$ & Standard deviation of thermal tolerance for
+		the population & $^\circ$C \\
+		\hline
+		\multicolumn{3}{l}{\textit{Population movement model}} \\
+		\hline
+		$\lambda$ & decay rate for population movement & - \\
+		$Hab^{2}_{c,p}$ & Square of habitat suitability for cell $c$ and
+		population $p$ & - \\
+		$Tol_{c,p,wk}$ & Thermal tolerance for population $p$ in cell
+		$c$ at week $wk$ & - \\
+		$d_{IJ}$ & euclidean distance between cell $I$ and cell $J$ & - \\
+		\bottomrule
+		\end{tabular}
+	\end{table}
+
+\begin{table}[!ht]
+	\centering
+	\caption{Description of variables for fleet dynamics sub-module}
+	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
+		\toprule
+		Variable & Meaning & Units \\
+		\hline
+		\multicolumn{3}{c}{\textbf{Short-term fleet dynamics}} \\
 		\hhline{===}
-		a & b & c \\
-		a & b & c \\
+		$Rev$ & Revenue from fishing tow & \euro \\
+		$L_{p}$ & Landings of population $p$ & kg \\
+		$Pr_{p}$ & Average price of population $p$ & \euro
+		\hspace{0.1cm} kg$^{-1}$ \\
+		StepL & Step length for vessel & euclidean distance \\
+		Br & Bearing & degrees \\
+		$k$ & Concentration parameter for Von mises distribution & - \\
+		$\beta_{1}$ & shape parameter for step function & - \\
+		$\beta_{2}$ & shape parameter for step function & - \\
+		$\beta_{3}$ & shape parameter for step function & - \\
 		\bottomrule

### 2018-04-17 write_up/mixfishsim_ecolmod.tex
Updated plots with new simulation runs

@@
 Further, fishers generally only recorded landings (not catch) on a daily
-basis\todo{\added[id=JJ]{Its not clear what the problem is: landed
+basis\todo{\added[id=JJ]{Its not clear what the problem is: landings
 		collected on daily basis or landings recorded rather than catch}}.
@@
 \node [term, join, fill=lcfree!25] (p1){Sample catch};
-\node [test, densely dotted] (t1) {if $y > y-1$};
-\node [test, join, densely dotted] (t2) {if $pop_{t}$ != $pop_{t-1}$};
+\node [test, densely dotted] (t1) {if $spawn_{t}$};
+\node [test, join, densely dotted] (t2) {if $wk_{t}$ != $wk_{t-1}$};
 \node [test, join, densely dotted] (wk) {if $day_{t}$ != $day_{t-1}$};
@@
 	the white boxes are the timesteps at which processes occur; $t$ = tow,
-	$tmax$ is the total number of tows, $y$ = year, $pop_{t}$ is time of
-	population movement, $day$ is a day timestep, $trip$ is a trip time
-	step. \textcolor{red}{I NEED TO REDO THIS TO MAKE NOTATION MORE CONCISE
-		AND CONSISTENT} 
-	} 
+	$tmax$ is the total number of tows, $wk$ is a weekly timestep, $day$ is
+	a day timestep, $trip$ is a trip time step. \textcolor{red}{I NEED TO
+		REDO THIS TO MAKE NOTATION MORE CONCISE AND CONSISTENT} } 
 \label{fig:overview}

### 2018-04-17 analysis/KillerFigure.R

@@ -167,12 +167,12 @@ draw.barplot2D(catch_comp[[1]]$x,catch_comp[[1]]$y,z = catch_comp[[1]]$z, width 
 
 ## Test
 
-yr <- 2:4 
+yr <- 2:10 
 wk <- 1:52 
 mn <- 1:12
 
 ## Load the results
-load(file.path('.', 'Scenario_runs', paste0('Scenario_', 1, '_.RData')))
+load(file.path('.', 'Scenario_runs2', paste0('Scenario_', 0, '_.RData')))
 load(file.path('.', 'Common_Params.RData'))
 
 ## Commercial

### 2018-04-17 analysis/Plots.R

@@ -7,8 +7,8 @@ library(MixFishSim)
 
 load('Common_Params.RData')
 
-Run <- 1 
-load(file.path('Scenario_runs', paste0("Scenario_", Run, "_.RData")))
+Run <- 0 
+load(file.path('Scenario_runs2', paste0("Scenario_", Run, "_.RData")))
 
 plot_pop_summary(res, timestep = "annual", save = FALSE)
 
@@ -18,7 +18,7 @@ ggsave(file = file.path('..', 'write_up', 'Plots', 'f_dynamics.png'), width = 8,
 logs <- combine_logs(res[["fleets_catches"]])
 
 plot_vessel_move(sim_init = sim, logs = logs, fleet_no = 1, vessel_no = 1,
-       year_trip = 1, trip_no = 4)
+       year_trip = 10, trip_no = 4)
 ggsave(file = file.path("..", "write_up", "Plots", "vessel_move.png"), width = 8, height = 8)
 
 

### 2018-04-17 analysis/Plots_Combined.R

@@ -8,20 +8,20 @@ library(MixFishSim)
 load('scenarios.RData')
 load('Common_Params.RData')
 
-runs <- 1:56
+runs <- 0:56
 
-for(i in runs) {
-load(file.path('Scenario_runs', paste('Scenario', i, '.RData', sep = "_")))
-assign(paste0("sc",i),res)
-}
+for(r in runs) {
+load(file.path('Scenario_runs2', paste('Scenario', r, '.RData', sep = "_")))
+#assign(paste0("sc",r),res)
+#}
 
 ## Combine the population metrics
 
-combined_pop <- lapply(runs, function(r) {
-	n_spp <- length(get(paste("sc",r,sep=""))[["pop_summary"]]) 
+#combined_pop <- lapply(runs, function(r) {
+	n_spp <- length(res[["pop_summary"]]) 
 		res_df <- lapply(seq_len(n_spp), function(x) {
-	 		res_spp <- lapply(names(get(paste("sc",r,sep=""))[["pop_summary"]][[x]]), function(x1) {
-			      x1_res <- tidyr::gather(as.data.frame(t(get(paste("sc",r,sep=""))[["pop_summary"]][[x]][[x1]])), key = "year", factor_key = T)
+	 		res_spp <- lapply(names(res[["pop_summary"]][[x]]), function(x1) {
+			      x1_res <- tidyr::gather(as.data.frame(t(res[["pop_summary"]][[x]][[x1]])), key = "year", factor_key = T)
 		      	      if(x1 !="Rec.mat") {	res_out <- data.frame("pop" = rep(paste("spp",x, sep = "_"), length.out = nrow(x1_res)), 
 						              "metric" = rep(sapply(strsplit(x1,".",fixed = T),"[",1), length.out = nrow(x1_res)), 
 							      "year" = x1_res$year, 
@@ -40,17 +40,24 @@ combined_pop <- lapply(runs, function(r) {
 			return(do.call(rbind, res_spp))
 	   })
 	results_df <- do.call(rbind, res_df)
+	results_df$scenario <- r
 
-})
+	if(r == 1) { combined_pop <- results_df}
+	if(r > 1) {combined_pop <- rbind(combined_pop, results_df) }
 
-rm(list = ls(pattern = "sc"))
+rm(res)
 gc()
+}
+#})
 
-rows <- nrow(combined_pop[[1]])
+#rm(list = ls(pattern = "sc"))
+#gc()
 
[…]

### 2018-06-04 write_up/mixfishsim_ecolmod.tex
Parallelisation testing using omp - no obvious benefit

@@
 quota species while allowing continuance of sustainable fisheries for available
-quota species. \\
+quota species.\\
 
@@
 landings data assigned to VMS activity pings\todo{\added[id=JJ]{This comes as a
-	surprise: I thought this was going to be about discards}}. \\
+	surprise: I thought this was going to be about discards}}.\\
 
@@
 to a range of spatial and temporal scales to assess the impact of these
-processes on the success of the management measure. \\
+processes on the success of the management measure.\\
 
@@
 	system: 1) Population dynamics, 2) Recruitment dynamics, 3) Population
-	movement, 4) fishery dynamics.} \\
+	movement, 4) fishery dynamics.}\\
 

### 2018-06-04 analysis/Closure_Analysis_Cond2.R

@@ -1,0 +1,173 @@
+############################################################################
+## Code to run a number of scenarios testing data type (commercial, survey,
+## real population), resolution (spatio-temporal) and basis for closure (high
+## pop or high ratio spp1:spp2)
+#############################################################################
+#######################
+#
+## Conditioning
+#
+######################
+
+library(MixFishSim)
+
+set.seed(123, kind = "L'Ecuyer-CMRG")
+
+## initialise the simulation
+
+sim <- init_sim(nrows = 100, ncols = 100, n_years = 5, n_tows_day = 4, n_days_wk_fished = 5,
+     n_fleets = 5, n_vessels = 20, n_species = 4, move_freq = 2)
+
+## create the suitable habitat for each species
+
+hab <- create_hab(sim_init = sim,
+		  spp.ctrl = list(
+           'spp.1' = list('nu' = 1/0.015, var = 1, scale = 100, Aniso =
+           matrix(nc=2, c(1.5, 3, -3, 4))),
+           'spp.2' = list('nu' = 1/0.05, var = 2, scale = 12, Aniso =
+           matrix(nc=2, c(1, 2, -1, 2))),
+	   'spp.3' = list('nu' = 1/0.01, var = 1, scale = 29, Aniso =
+           matrix(nc=2, c(2.5, 1, -1, 2))),
+           'spp.4' = list('nu' = 1/0.005, var = 1, scale = 18, Aniso =
+           matrix(nc=2, c(0.1, 2, -1, 0.02)))
+				  ),
+		  spawn_areas = list("spp1" = list(area1 = c(40, 50, 40, 50), area2 =
+				   c(80, 90, 60, 70)), 
+		 "spp2" = list(area1 = c(50, 60, 30, 40), area2 = c(80, 90, 90, 90)),
+		 "spp3" = list(area1 = c(30, 34, 10, 20), area2 = c(60, 70, 20, 30)),
+		 "spp4" = list(area1 = c(50, 55, 80, 85), area2 = c(30, 40, 30, 40))
+		 ),
[…]

### 2018-06-04 analysis/Closure_Analysis_Runs0.R

@@ -14,7 +14,7 @@ library(MixFishSim)
 set.seed(123, kind = "L'Ecuyer-CMRG")
 
 ## Common settings
-load('Common_Params.RData')
+load('Common_Params2.RData')
 
 ## Scenarios here
 load('scenarios.RData')
@@ -26,7 +26,7 @@ r <- 0
 ## run_sim function for overall control
 res <- run_sim(sim_init = sim, pop_init = Pop, move_cov = moveCov, fleets_init = fleets, hab_init = hab, InParallel = TRUE, cores = 1, save_pop_bio = TRUE, survey = survey, closure = closure)
 
-save(res, file = paste('Scenario', r, '.RData',sep = "_"))
+save(res, file = file.path('.','Scenario_runs3',paste('Scenario', r, '.RData',sep = "_")))
 ############################################
 
 rm(res); gc()

### 2018-06-04 analysis/Plot_Clusters.R

@@ -1,0 +1,124 @@
+
+library(MixFishSim)
+
+load('Common_Params.RData')
+
+Run <- 2 
+load(file.path('Scenario_runs2', paste0("Scenario_", Run, "_.RData")))
+
+plot_pop_summary(res, timestep = 'annual')
+
+logs <- as.data.frame(combine_logs(res$fleets_catches))
+
+plot_catch_comp(gran = c(20, 10, 5, 2), logs = logs, fleets = 1:5,
+       vessels = 1:20, trips = 1:60, years = 26:30, cluster_plot = TRUE, 
+       scale_data = TRUE , cluster_k = 5)
+
+## Check function with the old results
+load(file.path('..', '..', 'Geostatistics', 'Sim_data','results','FullResults.RData'))
+
+
+plot_catch_comp(gran = c(20, 10, 5, 2), logs = catch_results, fleets = 1:5,
+       vessels = 1:20, trips = 1:60, years = 26:30, cluster_plot = TRUE, 
+       scale_data = FALSE, cluster_k = 5)
+
+###################################
+## Let's look at function itself ##
+## See if we can work out whats  ##
+## going on....                  ##
+###################################
+
+gran = c(20, 10, 5, 2)
+fleets = 1:5
+vessels = 1:20
+trips = 1:60
+years = 26:30
+cluster_plot = TRUE 
+scale_data = FALSE 
+cluster_k = 5
+
+require(dplyr)
+require(reshape2) 
+require(mapplots)
+require(cluster)
+
+## Filter catch logs as needed
+logs <- combine_logs(res$fleets_catches)
+logs <- as.data.frame(logs)
+logs <- filter(catch_results, fleet %in% fleets, vessel %in% vessels, trip %in% trips, year %in% years)
+
+## First, aggregate the catch data to the appropriate scales
+catch_comp <- lapply(gran, function(x) {
+
+breaks<-seq(0.001,1000.001,by=x)
+mid_break <- breaks + (x/2)
+mid_break <- mid_break[-length(mid_break)] 
+
+# Func to bin the data
+bin.func <- function (x) {
+	mid_break[which(abs(mid_break - x) == min(abs(mid_break - x)))]
+}
+
+# Then aggregate the data to the bins
+catch_grid <- logs 
[…]

### 2018-06-04 analysis/Plot_fishing.R

@@ -1,0 +1,66 @@
+
+###########################################################
+## Plot of fishing locations before and after closures...
+###########################################################
+library(MixFishSim)
+library(dplyr)
+library(ggplot2)
+
+load('Common_Params.RData')
+
+Run <- 2
+load(file.path('Scenario_runs2', paste0("Scenario_", Run, "_.RData")))
+
+logs <- as.data.frame(combine_logs(res[["fleets_catches"]]))
+
+logs$closure <- ifelse(logs$year %in% 26:30, "before", ifelse(logs$year %in% 36:40, "after", "NONE"))
+logs$closure <- factor(logs$closure)
+
+
+##########################
+## Extract the closures ##
+##########################
+# The common settings
+load(file.path('..', 'analysis', 'Common_Params.RData'))
+## Scenarios here
+load(file.path('..', 'analysis','scenarios.RData'))
+
+# Re-calc the closures as implemented
+r  <- 2 ## second closure settings
+closure <- init_closure(input_coords = NULL, basis = sc$data_type[r], rationale = sc$basis[r], spp1 = 'spp3', spp2 = 'spp2', year_start = 31, year_basis = c(21:30), closure_thresh = 0.95, sc = sc$resolution[r], temp_dyn = sc$timescale[r])
+
+# t for month 1:12 of year 31
+closure_areas <- lapply(1:12, function(m) {
+t <-which(sim$brk.idx$year.breaks == 21 & sim$brk.idx$month.breaks == m)[1]
+year <- 31
+month <- m
+#week <- sim$brk.idx$week.breaks[t] 
+AreaClosures <- close_areas(sim_init = sim, closure_init = closure, commercial_logs = res$fleets_catches, survey_logs = NULL, real_pop = NULL, t = t)
+AreaClosures$closure <- "after" # rename for consistency in the plot
+AreaClosures$month <- m
+return(AreaClosures)
+})
+
+##############
+## Plots    ##
+##############
+
+## Let's plot the first fleet only
+logs <- filter(logs, fleet == 1, closure %in% c("before", "after"))
+closure_areas <- do.call(rbind, closure_areas) # make closures list a combined df
+
+library(cowplot)
+
+p1 <- ggplot(filter(logs, closure == "before"), aes(x = x , y = y)) +
[…]

### 2018-06-04 analysis/Plots.R

@@ -33,7 +33,7 @@ ggsave(file = file.path("..", "write_up", "Plots", "vessel_move_value.png"), wid
 plot_fleet_trip(logs = logs, fleet_no = 1, year_trip = 10, trip_no = 1)
 ggsave(file = file.path("..", "write_up", "Plots", "fleet_moves.png"), width = 8, height = 8)
 
-plot_catch_comp(gran = c(20, 10, 5, 2), logs = logs, fleets = 1:5,
+plot_catch_comp(gran = c(20, 10, 5, 2), logs = logs, fleets = 1:5, scale_data = FALSE,
        vessels = 1:20, trips = 1:60, years = 1:10, cluster_plot = TRUE, cluster_k = 5)
 
 plot_survey(survey = res[["survey"]], type = "index")

### 2018-06-04 analysis/Plots_Combined.R

@@ -59,7 +59,6 @@ gc()
 
 #combined_pop$scenario <- rep(runs, each = rows)
 
-
 library(ggplot2)
 library(dplyr)
 
@@ -130,18 +129,23 @@ combined_pop_an$data_type  <- sc$data_type[match(combined_pop_an$scenario, sc$sc
 
 combined_pop_an <-  combined_pop_an[!is.na(combined_pop_an$year),] ## Remove R for last year
 
+combined_pop_an$year <- as.numeric(combined_pop_an$year) # to fix x-axis breaks
+
 ggplot(filter(combined_pop_an,basis == 'high_pop', metric == 'F'), 
        aes(x = year, y = data, group = combined)) + 
 geom_line(aes(colour = timescale, linetype = factor(res))) + 
 facet_wrap(data_type ~ pop, scale = 'free') + expand_limits(y = 0) +theme_bw() +
-geom_vline(xintercept = 30, linetype = 2, colour = "grey") + ylab("Fishing mortality")
+geom_vline(xintercept = 30, linetype = 2, colour = "grey") + ylab("Fishing mortality") +
+theme(axis.text.x = element_text(angle = -90, hjust = 0)) + scale_x_continuous(breaks = seq(0,40,5))
 ggsave('F_trends.png', width = 10, height = 8)
 
 ggplot(filter(combined_pop_an,basis == 'high_pop', metric == 'F', pop == "spp_3"), 
        aes(x = year, y = data, group = combined)) + 
 geom_line(aes(colour = timescale, linetype = factor(res))) + 
 facet_wrap(data_type ~ pop, scale = 'free', ncol = 1) + expand_limits(y = 0) +theme_bw() +
-geom_vline(xintercept = 30, linetype = 2, colour = "grey") + ylab("Fishing mortality")
+geom_vline(xintercept = 30, linetype = 2, colour = "grey") + ylab("Fishing mortality")+
+theme(axis.text.x = element_text(angle = -90, hjust = 0)) + scale_x_continuous(breaks = seq(0,40,5))
+
 ggsave('F_trends_spp3.png', width = 8, height = 12)
 
 
@@ -149,20 +153,26 @@ ggplot(filter(combined_pop_an,basis == 'high_pop', metric == 'Bio'),
        aes(x = year, y = data, group = combined)) + 
 geom_line(aes(colour = timescale, linetype = factor(res))) + 
[…]

### 2018-06-04 tests/closure_return_test.R

@@ -1,0 +1,33 @@
+
+library(MixFishSim)
+
+load(file.path('..', 'analysis', 'Common_Params.RData'))
+load(file.path('..', 'analysis', 'Scenario_runs2', 'Scenario_2_.RData'))
+load(file.path('..', 'analysis','scenarios.RData'))## Scenarios here
+
+run_no <- 2
+
+r  <- 2
+## Change closure per scenario
+closure <- init_closure(input_coords = NULL, basis = sc$data_type[r], rationale = sc$basis[r], spp1 = 'spp3', spp2 = 'spp2', year_start = 31, year_basis = c(21:30), closure_thresh = 0.95, sc = sc$resolution[r], temp_dyn = sc$timescale[r])
+
+catches <- as.data.frame(combine_logs(res$fleets_catches))
+
+# t for month 1:12 of year 31
+
+closure_areas <- lapply(1:12, function(m) {
+
+t <-which(sim$brk.idx$year.breaks == 21 & sim$brk.idx$month.breaks == m)[1]
+year <- 31
+month <- m
+week <- sim$brk.idx$week.breaks[t] 
+AreaClosures <- close_areas(sim_init = sim, closure_init = closure, commercial_logs = res$fleets_catches, survey_logs = NULL, real_pop = NULL, t = t)
+return(AreaClosures)
+})
+
+par(mfrow=c(3,4))
+for(m in 1:12) {
+plot(closure_areas[[m]]$x, closure_areas[[m]]$y)
+}
+
+

### 2018-06-04 tests/test_parallel_omp.R

@@ -1,0 +1,58 @@
+
+
+#source('build.R')
+
+library(MixFishSim)
+
+set.seed(123, kind = "L'Ecuyer-CMRG")
+
+## initialise the simulation
+
+sim <- init_sim(nrows = 100, ncols = 100, n_years = 2, n_tows_day = 4, n_days_wk_fished = 5,
+     n_fleets = 2, n_vessels = 10, n_species = 2, move_freq = 2)
+
+
+# Here's what is produced...
+#names(sim)
+
+## create the suitable habitat for each species
+
+hab <- create_hab(sim_init = sim,
+		  spp.ctrl = list(
+           'spp.1' = list('nu' = 1/0.15, var = 1, scale = 10, Aniso =
+           matrix(nc=2, c(1.5, 3, -3, 4))),
+           'spp.2' = list('nu' = 1/0.05, var = 2, scale = 20, Aniso =
+           matrix(nc=2, c(1, 2, -1, 2)))),
+		  spawn_areas = list("spp1" = list(area1 = c(40, 50, 40, 50), area2 =
+				   c(80, 90, 60, 70)), 
+		 "spp2" = list(area1 = c(50, 60, 30, 40), area2 = c(80, 90, 90, 90))),
+		spwn_mult = 10, plot.dist = TRUE, plot.file = ".")
+
+
+n_spp <- 2
+
+# Simple comparison
+suppressMessages(require(doParallel))
+registerDoParallel(cores = 1)
+
+
+## Simple application
+MoveProb  <- foreach(s = paste0("spp", seq_len(n_spp)))  %do% move_prob_Lst(lambda = 0.3, hab = hab[["hab"]][[s]])
+MoveProb_para  <- foreach(s = paste0("spp", seq_len(n_spp)))  %do% move_prob_Lst_para(lambda = 0.3, hab = hab[["hab"]][[s]])
+
+## Proper test
+library(microbenchmark)
+
+mbm <- microbenchmark("moveProb" = {  MoveProb  <- foreach(s = paste0("spp", seq_len(n_spp)))  %do% move_prob_Lst(lambda = 0.3, hab = hab[["hab"]][[s]])
+},
+#"moveProb_para" = {
+#	MoveProb_para  <- foreach(s = paste0("spp", seq_len(n_spp)))  %do% move_prob_Lst_para(lambda = 0.3, hab = hab[["hab"]][[s]])
+#},
+times = 10)
+
+mbm
+
+library(ggplot2)
+autoplot(mbm)
+
+

### 2018-06-05 R/go_fish.R
Corrections to go_fish call of distance calc

@@ -375,7 +375,7 @@ coords <- new.point # assign new fishing position
 	# and the costs and profit
 	# costs from the distance travelled * fuel cost
 	catch[t,"costs"] <- (distance_calc(x1 = catch[t-1, "x"], y1 = catch[t-1, "y"],
-					  x1 = catch[t, "x"], y1 = catch[t, "y"]) * fuelC)
+					  x2 = catch[t, "x"], y2 = catch[t, "y"]) * fuelC)
 
 	catch[t,"profit"] <- catch[t,"val"] - catch[t,"costs"] 
 

### 2018-06-05 tests/build.R

@@ -11,8 +11,7 @@ document()
 install()
 
 ## Note: document with 
-## R CMD Rd2pdf '../MixFishSim' ~~ in terminal
-
+## R CMD Rd2pdf '../MixFishSim' ~~ in terminal using :!
 
 #library(MixFishSim)
 
@@ -20,4 +19,4 @@ install()
 
 #move_prob(start = c(2,2), lambda = 0.3, hab = matrix(nc = 3, runif(9)))
 
-#move_prob_Lst(lambda = 0.3, hab = matrix(nc = 2, runif(4)))
+move_prob_Lst(lambda = 0.3, hab = matrix(nc = 2, runif(4)))

### 2018-06-13 write_up/mixfishsim_ecolmod.tex
Manuscript revisions

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%
-%% Elsevier bibliography styles
-%%%%%%%%%%%%%%%%%%%%%%%
-%% To change the style, put a % in front of the second line of the current style and
-%% remove the % from the second line of the style you would like to use.
-%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Numbered
-%\bibliographystyle{model1-num-names}
-%% Numbered without titles
-%\bibliographystyle{model1a-num-names}
 %% Harvard
 \bibliographystyle{model2-names.bst}\biboptions{authoryear}
-%% Vancouver numbered
-%\usepackage{numcompress}\bibliographystyle{model3-num-names}
-%% Vancouver name/year
-%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
-%% APA style
-%%\bibliographystyle{model5-names}\biboptions{authoryear}
-%% AMA style
-%\usepackage{numcompress}\bibliographystyle{model6-num-names}
-%% `Elsevier LaTeX' style
-%%\bibliographystyle{elsarticle-num}
-%%\bibliographystyle{elsarticle-harv}
-
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 	exploring mixed fishery dynamics}
-
-%%\title{A simulation framework for exploring spatiotemporal dynamics in mixed
-%%	fisheries}
 
@@
 \begin{abstract}
-%\textcolor{gray}{[Guidance: A concise and factual abstract is required. The abstract 
-%should state briefly the purpose of the research, the principal results and
-%major conclusions. An abstract is often pnresented separately from the article,
-%so it must be able to stand alone. For this reason, References should be
-%avoided, but if essential, then citep the author(s) and year(s). Also,
-%non-standard or uncommon abbreviations should be avoided, but if essential they
-%must be defined at their first mention in the abstract itself.  Graphical
-%abstract: Although a graphical abstract is optional, its use is encouraged as
-%it draws more attention to the online article. The graphical abstract should
-%summarize the contents of the article in a concise, pictorial form designed to
-%capture the attention of a wide readership. Graphical abstracts should be
-%submitted as a separate file in the online submission system. Image size:
-%Please provide an image with a minimum of 531 X 1328 pixels (h X w) or
-%proportionally more. The image should be readable at a size of 5 x 13 cm using
-%a regular screen resolution of 96 dpi.  Preferred file types: TIFF, EPS, PDF or
-%MS Office files.] \\}
-%
+
 \replaced[id = JJ]{Most fisheries}{Fishing} exploit\deleted[id=JJ]{s} spatially
-and temporally hetergenous fish populations, using species-unselective gear
+and temporally heterogeneous fish populations, using species-unselective gear
 that can result in unintended, unwanted catch of low quota or protected
@@
 
-To implement effective spatial measures to reduce discards a good understanding
-of spatiotemporal fishery dynamics is required. However, traditional
-scientific advice is limited by a lack of highly resolved knowledge of
-population distribution, movement and how fishers interact with different fish
+\replaced[id = PD]{If fisheries are to avoid unwanted catch}{To implement
+	effective spatial measures to reduce discards} a good understanding of
+spatiotemporal fishery dynamics is required. However, traditional scientific
+advice is limited by a lack of highly resolved knowledge of population
+distribution, movement and how fishers interact with different fish
 populations. This reflects that data on fish location at high temporal and
@@
 delay-difference population dynamics, ii) population movement using Gaussian
-Random Fields to simulate patchy, hetergenously distributed populations, and
-iii) fishery dynamics for multiple fleet characteristics based on targetting
+Random Fields to simulate patchy, heterogeneously distributed populations, and
+iii) fishery dynamics for multiple fleet characteristics based on targeting
 via correlated random walk movement and learned behaviour. \\
@@
 
-%\textcolor{gray}{[Guidance:: State the objectives of the work and provide an 
-%adequate background, avoiding a detailed literature survey or a summary of the
-%results.] \\}
-%
-Fishers exploit fish populations that are heterogenously distributed in space
-and time with verying knowledge of species distributions using
-species-unselective fishing gear. Fisheries that catch an assemblage of
-species, known as mixed fisheries \replaced[id=JJ]{may}{, when managed by
-	single-species quotas can end up} discard\deleted[id=JJ]{ing} overquota
-catch \added[id=JJ]{when managed by single species quotas,} leading to
-overexploitation of fish populations \added[id=JJ]{\citep{Ulrich2011a,
-		Batsleer2015}}.  \added[id=JJ]{This discarding of fish in
-	excess of quota hampers the ability to limit fishing mortality to
-	within sustainable limits \citep{Alverson1994, Crowder1998,
-		Rijnsdorp2007}.} Reducing discarding is crucial to ensure
-biological and economic sustainability of fisheries\deleted[id=JJ]{ and
-	implementation of an ecosystem approach to
-	fisheries}\replaced[id=PD]{and}{. As such} there is increasing interest
-in technical solutions such as gear and spatial closures as ways of avoiding
-discard\replaced[id=JJ]{ing of fish \citep{Kennelly2002, Catchpole2008,
-		Bellido2011}}{s}.  \\
-
-Use of spatial management as a tool has been proposed as a method to reduce
-discards \added[id=PD]{\citep{Holmes2011, Little2014, Dunn2014a}}. However, its
-implementation is hampered by lack of knowledge of fish and fishery
-spatiotemporal dynamics and understanding of the scale at which processes are
-important for management. Understanding the correct scale for spatial
-management is crucial in order to implement measures at a resolution that
-ensures effective management \citep{Dunn2016} while minimising economic impact.
-For example, a scale that promotes species avoidance for vulnerable or low
-quota species while allowing continuance of sustainable fisheries for available
-quota species.\\
-
-Ensuring measures are implemented at an appropriate scale has been a challenge
-in the past that has led to ineffectual measures with unitended consequences
-such as limited impact towards the management objective or increased benthic
-impact on previously unexploited areas (e.g. the cod closure in the North
-Sea \citep{Rijnsdorp2001,Dinmore2003}). Since then more refined spatial
-information has become available through the combination of logbook and Vessel
-Monitoring System (VMS) data \citep{Lee2010, Bastardie2010, Gerritsen2012,
-	Mateo2016} and more real-time spatial management has been possible 
-	\citep[e.g.][]{Holmes2011}. Such information is, however, patchy and
-derived from an inherently biased sampling programme (i.e. targeted fishing).
-Further, fishers generally only recorded landings (not catch) on a daily
-basis\todo{\added[id=JJ]{Its not clear what the problem is: landings
-		collected on daily basis or landings recorded rather than catch}}.
-This leads to questions about the validity of inference that can be drawn from
-landings data assigned to VMS activity pings\todo{\added[id=JJ]{This comes as a
-	surprise: I thought this was going to be about discards}}.\\
-
-In order to understand challenges that face VMS-linked landings to draw
-inference on the underlying population structure we develop a simulation model
-where population dynamics are highly-resolved in space and time and are known
-rather than inferred from sampling or commercial catches. Population movement
-is driven by a random (diffusive) and directed (advective) process and we
-incorporate characterisation of a number of different fisheries exploiting four
-fish populations with different spatial and population demographics.\\
-
-Using our model we simulate 20 years of exploitation of the fish populations
-and use the results from the fishing model to draw inference on the underlying
-population structures.  We compare this inference to: i) a stratified
-fixed-site sampling survey design commonly used for fisheries monitoring
-purposes, otherwise know as a fisheries-independent
-	survey, and ii) the underlying population structures input to the
-simulation.\\
-
-We simulate a fishery closure to protect one species based on the
-fishery-dependent inferred distributions at a spatial and temporal scale
-typical in fisheries management, and assess a theoretical "benefit" to the
-population, and effect on the other three populations\todo{\added[id=JJ]{If
-		the paper has two goals this should be clear from the start,
-		but may be better over 2 MSs}}. Further, we extend our analysis
-to a range of spatial and temporal scales to assess the impact of these
-processes on the success of the management measure.\\
+Fishers exploit fish populations that are heterogeneously distributed in space
+and time with varying knowledge of species distributions using
+species-unselective fishing gear. \added[id=PD]{In doing so} fisheries
+\deleted[id=PD]{that} catch an assemblage of species
+\added[id=PD]{and}\deleted{, known as mixed fisheries} \replaced[id=JJ]{may}{,
+	when managed by single-species quotas can end up}
+discard\deleted[id=JJ]{ing} overquota catch \added[id=JJ]{when managed by
+	single species quotas,} leading to overexploitation of fish populations
+\added[id=JJ]{\citep{Ulrich2011a, Batsleer2015}}.  \added[id=JJ]{This
+	discarding of fish in excess of quota hampers the ability to limit
+	fishing mortality to within sustainable limits \citep{Alverson1994,
+	Crowder1998, Rijnsdorp2007}} \deleted[id=PD]{; reducing
+discarding is crucial} to ensure biological and
+economic sustainability of fisheries\deleted[id=JJ]{ and implementation of an
+	ecosystem approach to fisheries}\replaced[id=PD]{and}{. As such} there
+is increasing interest in technical solutions such as gear and spatial closures
+as ways of \replaced[id=PD]{reducing unwanted catch}{avoiding
+	discard\added[id=JJ]{ing of fish}}\citep{Kennelly2002,
+		Catchpole2008, Bellido2011}.  \\
+
+\replaced[id=PD]{Changes to spatial fishing patterns have}{Use of spatial
+	management as a tools} been proposed as a method to reduce discards
+\added[id=PD]{\citep{Holmes2011, Little2014, Dunn2014a}}. However,
+\deleted[id=PD]{its} implementation is hampered by lack of knowledge of fish
+and fishery spatiotemporal dynamics and understanding of the scale at which
+processes are important for management. Understanding the correct scale for
+spatial management is crucial in order to implement measures at a resolution
+that ensures effective management \citep{Dunn2016} while minimising economic
+impact.  For example, a scale that promotes species avoidance for vulnerable or
+low quota species while allowing continuance of sustainable fisheries for
+available quota species.\\
+
+\replaced[id=PD]{Identifying}{Ensuring measures are implemented at} an
+appropriate scale has been a challenge in the past that has led to ineffectual
+measures with unintended consequences such as limited impact towards the
+management objective or increased benthic impact on previously unexploited
+areas (e.g. the cod closure in the North Sea
+\citep{Rijnsdorp2001,Dinmore2003}). \replaced[id=PD]{M}{Since then m}ore
+refined spatial information has \added[id=PD]{since} become available through
+the combination of logbook and Vessel Monitoring System (VMS) data
+\citep{Lee2010, Bastardie2010, Gerritsen2012, Mateo2016} and more real-time
+spatial management has been possible \citep[e.g.][]{Holmes2011}.  Such
+information is, however, patchy and derived from an inherently biased sampling
+programme (i.e. targeted fishing). \deleted[id=PD]{ Further, fishers generally only recorded
+landings (not catch) on a daily basis\todo{\added[id=JJ]{Its not clear what the
+		problem is: landings collected on daily basis or landings
+		recorded rather than catch}}.  This leads to questions about
+the validity of inference that can be drawn from landings data assigned to VMS
+activity pings.}\todo{\added[id=JJ]{This comes as a surprise: I thought this was
+		going to be about discards}\added[id=PD]{Agree, have removed
+		this to avoid confusion}}\\
+
+In order to understand \replaced[id=PD]{the consequences of using}{challenges
+	that face} VMS-linked landings to draw inference on the underlying
+population structure we develop a simulation model where population dynamics
+are highly-resolved in space and time\replaced[id=PD]{. Being}{ and are}
+known \added[id=PD]{directly} rather than inferred from sampling or commercial
+catches \added[id=PD]{, we can use the population model to evaluate how inference from
+	fisheries-dependent and fisheries independent sampling relates to the
+	real population structure}. \replaced[id=PD]{In our model system
+	p}{P}opulation movement is driven by random (diffusive) and directed
+(advective) processes and we incorporate characterisation of a number of
+different fisheries \added[id=PD]{dynamics} exploiting four fish populations
+with different spatial and population demographics.\\
+
+Using our model we simulate \replaced[id=PD]{20}{40} years of exploitation of
+the fish populations. \replaced[id=PD]{We}{ and} use the
+results\deleted[id=PD]{ from the fishing model:}
+
+\begin{enumerate}
+	\item to understand how sampling-derived data reflects the underlying
+		population structures. We compare at different spatial and
+		temporal aggregations of data the real population to: 
+		\begin{enumerate}
+			\item the inferred population from a stratified fixed-site sampling survey design
+				commonly used for fisheries monitoring purposes, otherwise know as a
+				fisheries-independent survey,
+			\item the inferred population from our fishery-dependent model which includes
+				fishery-induced sampling dynamics.\\
+		\end{enumerate}
+	\item to understand the impact of data aggregation and source on
+		spatial fisheries management measures we simulate a fishery closure to
+		protect a species based on different spatial and temporal data
+		aggregations:
+		\begin{enumerate}
+			\item as if the real spatial population structure were
+				known,
+			\item the fishery-independent inferred population
+				structure
+			\item the fishery-dependent inferred population
+				structure
+		\end{enumerate}
+		We evaluate the theoretical "benefit" to the population of the
+		closure(s), and effect on the other three
+		populations\todo{\added[id=JJ]{If the paper has two goals this
+				should be clear from the start, but may be
+				better over 2 MSs}\added[id=PD]{I would like to
+				keep both parts, but have made clearer in how
+				its set out. The closure scenarios form
+				validation of the data aggregation, rather than
+				effectiveness of the closures themselves - so
+				its a continuation of the same question in my
+				eyes}}\deleted[id=PD]{.  Further, we extend our
+			analysis to a range of spatial and temporal scales to
+			assess the impact of these processes on the success of
+			the management measure.}\\
+\end{enumerate}
 
@@
 
-%\textcolor{gray}{[Guidance: Provide sufficient details to allow the work to be
-%reproduced by an independent researcher. Methods that are already published
-%should be summarized, and indicated by a reference.  If quoting directly from a
-%previously published method, use quotation marks and also citep the source. Any
-%modifications to existing methods should also be described.] \\ }
-%
 \replaced[id=PD]{A}{We developed and implemented a simulation model with a}
@@
 individual to a species\deleted[id=PD]{.}\added[id=PD]{, while the fishing
-	module operates on a tow-by-tow basis (multiple events a day)}. The
-simulation framework is implemented in the statistical software package R
+	module operates on a tow-by-tow basis (i.e. multiple events a day)}.
+The simulation framework is implemented in the statistical software package R
 \citep{RCoreTeam2017} \replaced[id=PD]{and}{;} available as an R package from
@@
 
-%\textcolor{gray}{[Guidance: A \underline{Theory} section should extend, not
-%repeat, the background to the article already dealt with in the	Introduction
-%and lay the foundation for further work.  In contrast, a
-%\underline{Calculation} section represents a practical development from a
-%theoretical basis.] \\}
-%
 \subsection{Population parameterisation}
@@
 
-%\textcolor{gray}{[Guidance: Results should be clear and concise.]}
-
 \section{Discussion}
 
-%\textcolor{gray}{[Guidance: This should explore the significance of the results 
-%of the work, not repeat them. A combined Results and Discussion section is
-%often appropriate.  Avoid extensive citations and discussion of published
-%literature.]}
-%
 \section{Conclusions}
 
-%\textcolor{gray}{[Guidance: The main conclusions of the study may be presented 
-%in a short Conclusions section, which may stand alone or form a subsection of a
-%Discussion or Results and Discussion section.]}
-%
 \section*{Appendices}
-
-%\textcolor{gray}{[Guidance: If there is more than one appendix, they should 
-%be identified as A, B, etc.  Formulae and equations in appendices should be
-%given separate numbering: Eq.  (A.1), Eq. (A.2), etc.; in a subsequent
-%appendix, Eq. (B.1) and so on.  Similarly for tables and figures: Table A.1;
-%Fig. A.1, etc.]}
-%
 

### 2018-06-13 write_up/mixfishsim_ecolmod.tex
Updated overview figure for manuscript

@@
 \node [term, join, fill=lcfree!25] (p1){Sample catch};
-\node [test, densely dotted] (t1) {if $spawn_{t}$};
-\node [test, join, densely dotted] (t2) {if $wk_{t}$ != $wk_{t-1}$};
-\node [test, join, densely dotted] (wk) {if $day_{t}$ != $day_{t-1}$};
-\node [test, join, densely dotted] (t3) {if $trip_{t}$ != $trip_{t-1}$};
+\node [test, densely dotted] (t1) {if $Rec_{p}[t]$};
+\node [test, join, densely dotted] (t2) {if $wk[t] \neq  wk[t-1]$};
+\node [test, join, densely dotted] (wk) {if $day[t] \neq day[t-1]$};
+\node [test, join, densely dotted] (t3) {if $trip[t] \neq trip[t-1] \ | \ PK[t]$};
 \node [term, join, fill=lcnorm!25]  (p2) {Correlated Random Walk};
@@
 % A couple of boxes have annotations
-\node [below=of p0, it, yshift=1.5em,xshift=-3em] {$t==1$};
+\node [below=of p0, it, yshift=1.5em,xshift=-3em] {$t=1$};
 \node [right=30mm of p3, it] {$1 < t < t_{max}$};
-\node [below=of p3, it,xshift=-3em, yshift=1.5em] {$t == t_{max}$};
+\node [below=of p3, it,xshift=-3em, yshift=1.5em] {$t = t_{max}$};
 
@@
 	dynamics processes, the green boxes population dynamics processes while
-	the white boxes are the timesteps at which processes occur; $t$ = tow,
-	$tmax$ is the total number of tows, $wk$ is a weekly timestep, $day$ is
-	a day timestep, $trip$ is a trip time step. \textcolor{red}{I NEED TO
-		REDO THIS TO MAKE NOTATION MORE CONCISE AND CONSISTENT} } 
+	the white boxes are the timesteps at which processes occur; $Rec$
+	is a recruitment period for population $p$, $t$ = tow, $tmax$ is the
+	total number of tows, $wk$ is a weekly timestep, $day$ is a day
+	timestep, $trip$ is a trip time step.}
 \label{fig:overview}
@@
 previously successful fishing locations. This \replaced[id=PD]{wa}{i}s achieved
-by sorting all previous fishing events in the previous trip as well as the
-previous time periods in past years, and choosing randomly from the top 75 \%
-of fishing events \replaced[id=PD]{as defined by the revenue gained}{in value}.
-Simulation testing indicated that this learning increased the mean value of
-catches for the vessels, over just relying on the correlated random
-walk \todo{\added[id=JJ]{Correlated random walk of what}} function
+by \added[id=PD]{calculating expected profit from locations fished during}
+previous fishing events in the previous trip as well as the previous time
+periods in past years, and choosing randomly from the top 75 \% of fishing
+events \replaced[id=PD]{as defined by the expected profit}{in value}.
+\added[id=PD]{Expected profit was estimated from the revenue from previous
+	times fished at a location minus the fuel cost of travelling to the
+	location.} Simulation testing indicated that this learning increased
+the mean value of catches for the vessels, over just relying on the correlated
+random walk \todo{\added[id=JJ]{Correlated random walk of what}} function
 \added[id=PD]{as described for the 'within trip' decisions below}.
@@
 
-Fishing locations within a trip are determined by a modified random walk
-process. A random walk type was chosen as it is the simplest assumption
-commonly used in ecology to describe \added[id=PD]{optimal} animal
-\deleted[id=PD]{movement which} search\replaced[id=PD]{ strategy}{ing} for
+Fishing locations within a trip are \added[id=PD]{initially} determined by a
+modified random walk process. \added[id=PD]{As the simulation progresses, the
+	within-trip decision become gradually more influenced by past locations
+	fished, based on the same process as the initial location, influenced
+	by expected profit at a fishing location.} A random walk was chosen for
+the exploratory fishing process as it is the simplest assumption commonly used
+in ecology to describe \added[id=PD]{optimal} animal \deleted[id=PD]{movement
+	which} search\replaced[id=PD]{ strategy}{ing} for
 \added[id=PD]{exploiting} homogeneously distributed prey about which there is
@@
 some other functional form. The direction of the random walk can be correlated,
-a characteristic known as `persistence', providing some overall
-\deleted[id=PD]{location of} directional movement \citep{Codling2008}
-\deleted[id=PD]{or uncorrelated}. \\
+(known as `persistence'), providing some overall \deleted[id=PD]{location of}
+directional movement \citep{Codling2008} \deleted[id=PD]{or uncorrelated}. \\
 

### 2018-11-14 R/run_sim.R
Bug fix for annual closures

@@ -151,7 +151,7 @@ if(t==1 & closeArea & !is.null(closure[["input_coords"]]) & closure[["year_start
 if(t==1 & closeArea & !is.null(closure[["input_coords"]]) & closure[["year_start"]] > 1) {CalcClosures <- FALSE}
 
 if( t > 1 & closeArea ) 		{
-if(closure[["temp_dyn"]] == 'annual') {
+if(closure[["temp_dyn"]] == 'yearly') {
 CalcClosures <- ifelse(year.breaks[t] != year.breaks[t-1], TRUE, FALSE)
 }
 if(closure[["temp_dyn"]] == 'monthly') {
@@ -250,7 +250,7 @@ if(closeArea & CalcClosures & !is.null(closure[["input_coords"]]) & year.breaks[
 print("Setting manually defined closures")
 print(paste("Closures are", closure[["temp_dyn"]]))
 
-if(closure[["temp_dyn"]] == 'annual') {
+if(closure[["temp_dyn"]] == 'yearly') {
 AreaClosures <- closure[["input_coords"]]
 }
 

### 2018-11-14 analysis/KillerFigure.R

@@ -343,7 +343,7 @@ dev.off()
 
 ## all year, month and week combinations
 
-logs <- as.data.frame(combine_logs(res[["fleets_catches"]]))
+logs <- combine_logs(res[["fleets_catches"]])
 
 logs_wk_mn <- unique(paste(logs$month, logs$week, sep = "_"))
 

### 2018-11-14 analysis/Plot_Bio.R

@@ -1,9 +1,9 @@
 
 library(MixFishSim)
 
-Run <- 1
+Run <- 0
 
-load(file.path('.', 'Scenario_runs', paste0('Scenario_',Run,'_.RData')))
+load(file.path('.', 'Scenario_runs_Nov18', paste0('Scenario_',Run,'.RData')))
 
 pop <- res[["pop_bios"]]
 plot_pop_summary(res, timestep = "annual")

### 2018-11-14 analysis/Plot_activity.R

@@ -7,17 +7,17 @@ library(ggplot2)
 load('Common_Params.RData')
 
 #Run <- 9
-Run <- 10 
-load(file.path('Scenario_runs', paste0("Scenario_", Run, "_.RData")))
+Run <- 3 
+load(file.path('Scenario_runs_Nov18', paste0("Scenario_", Run, ".RData")))
 
 
-logs <- as.data.frame(combine_logs(res[["fleets_catches"]]))
+logs <- combine_logs(res[["fleets_catches"]])
 
-logs_b <- filter(logs, year %in% 2:4)
+logs_b <- filter(logs, year %in% 25:29)
 #logs_b <- filter(logs, year %in% 2:4, week == 4)
 logs_b$time <- 'before'
 #logs_a <- filter(logs, year %in% 8:10, week == 4)
-logs_a <- filter(logs, year %in% 8:10)
+logs_a <- filter(logs, year %in% 46:50)
 logs_a$time <- 'after'
 
 logs <- rbind(logs_a, logs_b)

### 2018-11-14 analysis/Plot_fishing.R

@@ -8,12 +8,12 @@ library(ggplot2)
 
 load('Common_Params.RData')
 
-Run <- 3
-load(file.path('Scenario_runs2', paste0("Scenario_", Run, "_.RData")))
+Run <- 2
+load(file.path('Scenario_runs_Nov18', paste0("Scenario_", Run, ".RData")))
 
-logs <- as.data.frame(combine_logs(res[["fleets_catches"]]))
+logs <- combine_logs(res[["fleets_catches"]])
 
-logs$closure <- ifelse(logs$year %in% 26:30, "before", ifelse(logs$year %in% 36:40, "after", "NONE"))
+logs$closure <- ifelse(logs$year %in% 26:30, "before", ifelse(logs$year %in% 46:50, "after", "NONE"))
 logs$closure <- factor(logs$closure)
 
 
@@ -26,18 +26,19 @@ load(file.path('..', 'analysis', 'Common_Params.RData'))
 load(file.path('..', 'analysis','scenarios.RData'))
 
 # Re-calc the closures as implemented
-r  <- 3 ## second closure settings
+r  <- 2 ## second closure settings
 closure <- init_closure(input_coords = NULL, basis = sc$data_type[r], rationale = sc$basis[r], spp1 = 'spp3', spp2 = 'spp2', year_start = 31, year_basis = c(21:30), closure_thresh = 0.95, sc = sc$resolution[r], temp_dyn = sc$timescale[r])
 
-mn <- 1:12
+#mn <- 1:12
 wk <- 1:52
-# t for month 1:12 of year 31
+# t for month 1:12 of year 41
 closure_areas <- lapply(1:12, function(m) {
-t <-which(sim$brk.idx$year.breaks == 21 & sim$brk.idx$month.breaks == m)[1]
-year <- 31
+t <-which(sim$brk.idx$year.breaks == 46 & sim$brk.idx$month.breaks == m)[1]
+year <- 46
 month <- m
 #week <- sim$brk.idx$week.breaks[t] 
 AreaClosures <- close_areas(sim_init = sim, closure_init = closure, commercial_logs = res$fleets_catches, survey_logs = NULL, real_pop = NULL, t = t)
+AreaClosures <- as.data.frame(AreaClosures)
 AreaClosures$closure <- "after" # rename for consistency in the plot
 AreaClosures$month <- m
 return(AreaClosures)
@@ -45,16 +46,17 @@ return(AreaClosures)
 
 
 # y for years 31-40
[…]

### 2018-11-14 analysis/Plots.R

@@ -18,7 +18,7 @@ ggsave(file = file.path('..', 'write_up', 'Plots', 'f_dynamics.png'), width = 8,
 logs <- combine_logs(res[["fleets_catches"]])
 
 plot_vessel_move(sim_init = sim, logs = logs, fleet_no = 2, vessel_no = 5,
-       year_trip = 3, trip_no = 1:8)
+       year_trip = 30, trip_no = 1:8)
 ggsave(file = file.path("..", "write_up", "Plots", "vessel_move.png"), width = 8, height = 8)
 
 
@@ -34,7 +34,7 @@ plot_fleet_trip(logs = logs, fleet_no = 1, year_trip = 10, trip_no = 1)
 ggsave(file = file.path("..", "write_up", "Plots", "fleet_moves.png"), width = 8, height = 8)
 
 plot_catch_comp(gran = c(20, 10, 5, 2), logs = logs, fleets = 1:5, scale_data = FALSE,
-       vessels = 1:20, trips = 1:60, years = 1:10, cluster_plot = TRUE, cluster_k = 6)
+       vessels = 1:20, trips = 1:60, years = 40:50, cluster_plot = TRUE, cluster_k = 6)
 
 plot_survey(survey = res[["survey"]], type = "index")
 

### 2018-11-14 analysis/Plots_Combined.R

@@ -11,7 +11,7 @@ load('Common_Params.RData')
 runs <- 0:56
 
 for(r in runs) {
-load(file.path('Scenario_runs2', paste('Scenario', r, '.RData', sep = "_")))
+load(file.path('Scenario_runs_Nov18', paste0('Scenario_', r, '.RData')))
 #assign(paste0("sc",r),res)
 #}
 
@@ -78,7 +78,7 @@ combined_pop_an <- rbind(results_df_an1, results_df_an2)
 avg2_4  <- combined_pop_an %>% filter(year %in% 26:30) %>% 
 	group_by(scenario, pop, metric) %>% summarise(value = mean(data, na.rm = T))
 
-avg8_10 <- combined_pop_an %>% filter(year %in% 36:40) %>% 
+avg8_10 <- combined_pop_an %>% filter(year %in% 46:50) %>% 
 	group_by(scenario, pop, metric) %>% summarise(value = mean(data, na.rm = T))
 
 combined <- merge(avg2_4, avg8_10, by = c("scenario","metric","pop"))
@@ -109,7 +109,7 @@ ggplot(filter(combined, basis == 'high_pop', metric == "F"), aes(x = data_type, 
 	coord_flip() + ylab("Difference before and after closure in % F") + theme_bw() + facet_grid(pop~.) + geom_hline(yintercept = 0, linetype = "dashed") + ggtitle("Effectiveness of closure in reducing Fishing mortality") + scale_colour_gradient2(high = "red", mid = "orange", low = "yellow") +
 	scale_shape_discrete(solid = F)
 
-ggsave('Overview_plot_highPop.png', width = 12, height = 4)
+ggsave('Overview_plot_highPopRev.png', width = 12, height = 4)
 
 ###########################
 ### 
@@ -137,7 +137,7 @@ geom_line(aes(colour = timescale, linetype = factor(res))) +
 facet_wrap(data_type ~ pop, scale = 'free') + expand_limits(y = 0) +theme_bw() +
 geom_vline(xintercept = 30, linetype = 2, colour = "grey") + ylab("Fishing mortality") +
 theme(axis.text.x = element_text(angle = -90, hjust = 0)) + scale_x_continuous(breaks = seq(0,40,5))
-ggsave('F_trends.png', width = 10, height = 8)
+ggsave('F_trendsREV.png', width = 10, height = 8)
 
[…]

### 2018-11-22 analysis/Plots_Combined.R
Revised plot

@@ -111,6 +111,20 @@ ggplot(filter(combined, basis == 'high_pop', metric == "F"), aes(x = data_type, 
 
 ggsave('Overview_plot_highPopRev.png', width = 12, height = 4)
 
+combined_bi <- filter(combined, basis == "high_pop", metric %in% c("F", "Catch")) 
+
+combined_bi <- reshape2::dcast(combined_bi, scenario + pop + timescale + basis + data_type + resolution ~ metric, value.var = "diff")
+
+ggplot(combined_bi, aes(x = F, y = Catch)) + 
+	geom_point(aes(colour = resolution, shape = timescale), size = 4) + 
+	facet_wrap(pop~.) + ylab("Catch") + theme_bw() + facet_grid(pop~.) + 
+	geom_hline(yintercept = 0, linetype = "dashed") + 
+	geom_vline(xintercept = 0, linetype = "dashed") +
+	ggtitle("Effectiveness of closure in reducing Fishing mortality") +
+	scale_colour_gradient2(high = "red", mid = "orange", low = "yellow") +
+	scale_shape_discrete(solid = F)
+
+
 ###########################
 ### 
 ### Plot of all scenarios

### 2018-11-22 write_up/mixfishsim_ecolmod.tex
Bug fix for annual closures
Revised plot
Text update

@@
 
-\replaced[id = JJ]{Most fisheries}{Fishing} exploit\deleted[id=JJ]{s} spatially
-and temporally heterogeneous fish populations, using species-unselective gear
-that can result in unintended, unwanted catch of low quota or protected
-species. Reducing these unwanted catches is crucial for biological and economic
-sustainability of `mixed fisheries' and implementation of an ecosystem approach
-to fishing. \\
+\replaced[id = JJ]{Most fisheries}{Fishing} exploit\deleted[id=JJ]{s} a variety 
+of spatially and temporally heterogeneous fish populations, using
+species-unselective gear that can result in unintended, unwanted catch of low
+quota or protected species. Reducing these unwanted catches is crucial for
+biological and economic sustainability of `mixed fisheries' and implementation
+of an ecosystem approach to fishing. \\
 
@@
 advice is limited by a lack of highly resolved knowledge of population
-distribution, movement and how fishers interact with different fish
-populations. This reflects that data on fish location at high temporal and
-spatial resolutions is expensive and difficult to collect and therefore proxies
-inferred from either scientific surveys or commercial catch data are often used
-to model distributions, often with limited spatial and temporal resolution. \\
-
-To understand how resolution impacts mixed fisheries inference, we develop a
-highly resolved spatiotemporal simulation model incorporating: i)
-delay-difference population dynamics, ii) population movement using Gaussian
-Random Fields to simulate patchy, heterogeneously distributed populations, and
-iii) fishery dynamics for multiple fleet characteristics based on targeting
-via correlated random walk movement and learned behaviour. \\
-
-We simulate 20 years of exploitation of the fish populations and use the
-results from the fishing model to draw inference on the underlying population
-structures. We compare this inference to i) a simulated fixed-site sampling
-design commonly used for fisheries monitoring purposes, and ii) the true
-underlying population structures input to the simulation, to establish the
-potential and limitations of fishery-dependent data - an inherently biased
-sampling method due to fisher's targeting- to provide a robust picture of
-spatiotemporal distributions. Finally, we simulate an area closure based on
-areas defined from commercial the known ("real-population") distribution,
-commercial catch data and survey data at different temporal and spatial
-resolutions and assess their effectiveness on reducing catches of a fish
-population. \\
+distributions, movement and how fishers interact with different fish
+populations. This reflects the fact that data on fish location at high temporal
+and spatial resolutions is expensive and difficult to collect. Proxies inferred
+from either scientific surveys or commercial catch data are often used to model
+distributions, often with data at limited spatial and temporal resolution. \\
+
+To understand how data resolution impacts inference on mixed fisheries
+interactions, we develop a highly resolved spatiotemporal simulation model
+incorporating: i) delay-difference population dynamics, ii) population movement
+using Gaussian Random Fields to simulate patchy, heterogeneously distributed
+populations, and iii) fishery dynamics for multiple fleet characteristics based
+on species targeting via a mix of correlated random walk movement (for
+exploration) and learned behaviour (for exploitation) phases of the fisheries.
+\\
+
+We simulate 50 years of fishing and use the results from the fisheries catch to
+draw inference on the underlying population structures. We compare this
+inference to i) a simulated fixed-site sampling design commonly used for
+fisheries monitoring purposes, and ii) the true underlying population
+structures input to the simulation, to establish the potential and limitations
+of fishery-dependent data - an inherently biased sampling method due to
+fisher's targeting- to provide a robust picture of spatiotemporal
+distributions. Finally, we simulate an area closure based on areas defined from
+commercial the known ("real-population") distribution, commercial catch data
+and survey data at different temporal and spatial resolutions and assess their
+effectiveness on reducing catches of a fish population. \\
 
@@
 
-Fishers exploit fish populations that are heterogeneously distributed in space
-and time with varying knowledge of species distributions using
-species-unselective fishing gear. \added[id=PD]{In doing so} fisheries
+Fishers exploit a variety of fish populations that are heterogeneously
+distributed in space and time with varying knowledge of species distributions
+using species-unselective fishing gear. \added[id=PD]{In doing so} fisheries
 \deleted[id=PD]{that} catch an assemblage of species
@@
 		Crowder1998, Rijnsdorp2007}} \deleted[id=PD]{; reducing
-discarding is crucial} to ensure biological and
-economic sustainability of fisheries\deleted[id=JJ]{ and implementation of an
-	ecosystem approach to fisheries}\replaced[id=PD]{and}{. As such} there
-is increasing interest in technical solutions such as gear and spatial closures
-as ways of \replaced[id=PD]{reducing unwanted catch}{avoiding
-	discard\added[id=JJ]{ing of fish}}\citep{Kennelly2002,
-		Catchpole2008, Bellido2011}.  \\
+	discarding is crucial}and ensure biological and economic sustainability
+of fisheries\deleted[id=JJ]{ and implementation of an ecosystem approach to
+	fisheries}. As such, there is increasing interest
+in technical solutions such as gear and spatial closures as ways of
+\replaced[id=PD]{reducing unwanted catch}{avoiding discard\added[id=JJ]{ing of
+		fish}}\citep{Kennelly2002, Catchpole2008, Bellido2011}.  \\
 
@@
 
-Using our model we simulate \replaced[id=PD]{20}{40} years of exploitation of
+Using our model we simulate \replaced[id=PD]{50}{40} years of exploitation of
 the fish populations. \replaced[id=PD]{We}{ and} use the
@@
 
+NOTE: THIS IS EXPLORE-EXPLOIT STRATEGY VIZ. BAILEY ET AL POSEIDON MODEL.
+
 Several studies \citep[e.g.][]{Hutton2004, Tidd2012, Girardin2015} have
@@
 \begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../analysis/F_trends}
+	\includegraphics[width = \linewidth]{../analysis/F_trendsREV}
 	\caption{Comparison of closure scenarios - F trends}
@@
 \begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../analysis/Overview_plot_highPop}
+	\includegraphics[width =\linewidth]{../analysis/Overview_plot_highPopRev}
 	\caption{Comparison of closure scenarios}

### 2018-11-26 write_up/mixfishsim_ecolmod.tex
Text revisions - clarifying and updating text

@@
 from either scientific surveys or commercial catch data are often used to model
-distributions, often with data at limited spatial and temporal resolution. \\
+distributions, often with sparse data at limited spatial and temporal
+resolution. \\
 
@@
 distributions. Finally, we simulate an area closure based on areas defined from
-commercial the known ("real-population") distribution, commercial catch data
-and survey data at different temporal and spatial resolutions and assess their
+the known ("real-population") distribution, commercial catch data and survey
+data at different temporal and spatial resolutions and assess their
 effectiveness on reducing catches of a fish population. \\
@@
 known \added[id=PD]{directly} rather than inferred from sampling or commercial
-catches \added[id=PD]{, we can use the population model to evaluate how inference from
+catch\added[id=PD]{, we can use the population model to evaluate how inference from
 	fisheries-dependent and fisheries independent sampling relates to the
@@
 (advective) processes and we incorporate characterisation of a number of
-different fisheries \added[id=PD]{dynamics} exploiting four fish populations
+different fishing \added[id=PD]{fleet dynamics} exploiting four fish populations
 with different spatial and population demographics.\\
@@
 		We evaluate the theoretical "benefit" to the population of the
-		closure(s), and effect on the other three
-		populations\todo{\added[id=JJ]{If the paper has two goals this
-				should be clear from the start, but may be
+		closure(s), the effect on the other three populations and
+		fishery catch.\todo{\added[id=JJ]{If the paper has two goals
+				this should be clear from the start, but may be
 				better over 2 MSs}\added[id=PD]{I would like to
@@
 \replaced[id=PD]{takes place}{occurs} periodcally each year for a set time
-\replaced[id=PD]{duration}{period (e.g. 3 weeks)} at at specified point
-individual to a species\deleted[id=PD]{.}\added[id=PD]{, while the fishing
-	module operates on a tow-by-tow basis (i.e. multiple events a day)}.
-The simulation framework is implemented in the statistical software package R
+\replaced[id=PD]{duration}{period (e.g. 3 weeks)} specified for each
+population\deleted[id=PD]{.}\added[id=PD]{, while the fishing module operates
+	on a tow-by-tow basis (i.e. multiple events a day)}.  The simulation
+framework is implemented in the statistical software package R
 \citep{RCoreTeam2017} \replaced[id=PD]{and}{;} available as an R package from
-the authors github (\url{www.github.com/pdolder/MixFishSim}).\\
-
-\deleted[id=PD]{Here we describe each of the model components; 1)
-Population dynamics, 2) Recruitment dynamics, 3) Population movement dynamics, 4)
+the authors github site (\url{www.github.com/pdolder/MixFishSim}).\\
+
+\deleted[id=PD]{Here we describe each of the model components; 1) Population
+	dynamics, 2) Recruitment dynamics, 3) Population movement dynamics, 4)
 	fishery dynamics.}
@@
 \node [term, join, fill=lcfree!25] (p1){Sample catch};
-\node [test, densely dotted] (t1) {if $Rec_{p}[t]$};
-\node [test, join, densely dotted] (t2) {if $wk[t] \neq  wk[t-1]$};
-\node [test, join, densely dotted] (wk) {if $day[t] \neq day[t-1]$};
-\node [test, join, densely dotted] (t3) {if $trip[t] \neq trip[t-1] \ | \ PK[t]$};
+\node [test, densely dotted] (t1) {if $(Rec)$};
+\node [test, join, densely dotted] (t2) {if (Pop Movement)};
+\node [test, join, densely dotted] (wk) {if (Pop Dynamics)};
+\node [test, join, densely dotted] (t3) {if (Past Knowledge)};
 \node [term, join, fill=lcnorm!25]  (p2) {Correlated Random Walk};
@@
 	dynamics processes, the green boxes population dynamics processes while
-	the white boxes are the timesteps at which processes occur; $Rec$
-	is a recruitment period for population $p$, $t$ = tow, $tmax$ is the
-	total number of tows, $wk$ is a weekly timestep, $day$ is a day
-	timestep, $trip$ is a trip time step.}
+	the white boxes are the time steps at which processes occur; $t$ = tow,
+	$tmax$ is the total number of tows; (Rec), (Pop Movement), (Pop
+	Dynamics) logic gates for recruitment periods, population movement and
+	population dynamics for each of the populations, (Past Knowledge) a
+	switch whether to use a random (exploratory) or past knowledge
+	(exploitation) fishing strategy.}
 \label{fig:overview}
@@
 	time-step was chosen as to discretise continuous population processes
-	on a biologically relevent and computationally tractable timescale.}
-\replaced[id=PD]{Under the popualation dynamics module}{Here,} population
+	on a biologically relevant and computationally tractable timescale.}
+\replaced[id=PD]{Under the population dynamics module}{Here,} population
 biomass growth and depletion for pre-recruits and \deleted[id=PD]{fish}
@@
 separately as a function of previous recruited biomass, intrinsic population
-growth and recruitment:
-
+growth and recruitment. Biomass for each cell is incremented each day as
+follows (the full parameter list is detailed in Table \ref{tab: pop_variable}):
 \begin{equation*}
@@
 \end{equation*}
-
 where $\rho$ is Brody's coefficient, shown to be approximately equal to
-$exp(-K)$, where $K$ is the growth rate from a von bertalanffy logistic growth
+$e^{-K}$ when $K$ is the growth rate from a von Bertalanffy logistic growth
 model \citep{Schnute1985}. $Wt_{R-1}$ is the weight of fish prior to
@@
 the proportion of fish recruited during that day for the year, while
-$R_{\tilde{c,y}}$ is the annual recruits in cell $c$ for year $y$. \\
+$R_{c,\tilde{y}}$ is the annual recruits in cell $c$ for year $y$. \\
 
@@
 the Baranov catch equation \citep{Hilborn1992b} for $F_{c,d}$:
-
 \begin{equation*}
@@
 \end{equation*}
-
 where $C_{c,d}$ is the summed catch from the fishing model across all fleets
@@
 Recruitment is modelled through a function relating the mature biomass to
-recruits at time of recruitment. In \emph{mixfishsim}, it can be modelled
+recruits at time of recruitment. In \emph{MixFishSim}, it can be modelled
 either either as a stochastic Beverton-Holt stock-recruit form
 \citep{Beverton1957}: 
-
 \begin{equation*}
@@
 $\sigma^2$ the variability in the recruitment due to stochastic
-processes. \\
-
-or a stochastic Ricker form \citep{Ricker1954}:
-
+processes, or a stochastic Ricker form \citep{Ricker1954}:
 \begin{equation*}
@@
 \end{equation*}
-
 where $\alpha$ is the maximum productivity per spawner and $\beta$ the density
@@
 		some biological meaning - species thermal tolerances load onto
-		the temperature effect}}. \deleted[id=JJ]{This was intended to
-	balance realism in population movement, capturing the main directed and
-	random processes, and practicality of modelling the population rather
-	than individual fish.} \\
+		the temperature effect - so could be different per species}}.
+\deleted[id=JJ]{This was intended to balance realism in population movement,
+	capturing the main directed and random processes, and practicality of
+	modelling the population rather than individual fish.} \\
 
@@
 \added[id=PD]{The Matérn covariance structure models the spatial
-	autocorrelation observed with animal distributions \citep{Tobler1970,
-		F.Dormann2007}} \replaced[id=PD]{and}{The \textit{Matérn}
+	autocorrelation, where animal densities are observed to be more similar
+	in nearby locations \citep{Tobler1970,
+		F.Dormann2007}}\replaced[id=PD]{. It is}{The \textit{Matérn}
 	correlation} is a two-parameter family where: 
-
 \begin{center}
@@
 \end{center}
-
 $K_{\kappa}(.)$ is a modified Bessel function of order $\kappa$, $\phi >
@@
 suitability, temperature and distance from current cell\replaced[id=PD]{:}{.} 
-
 \begin{equation}
@@
 \end{equation}
-
 Where $d_{IJ}$ is the euclidean distance between cell $I$ and cell $J$,
@@
 habitat\deleted[id=PD]{s}, \replaced[id=PD]{resulting in}{meaning} each
-population \replaced[id=PD]{had}{has} a concentrated area where spawning takes
+population \replaced[id=PD]{having}{has} a concentrated area where spawning takes
 place and the population move\replaced[id=PD]{d}{s} towards
@@
 suitability is defined that:
-
 \begin{equation}
@@
 \end{equation}
-
-Where $Tol_{c, p, \added[id=PD]{wk}}$ is the tolerance of population $p$ in
+Where $Tol_{c, p, \added[id=PD]{wk}}$ is the tolerance of population $p$ for
 cell $c$ \added[id=PD]{in week $wk$}, $T_{c, \added[id=PD]{wk}}$ is the
@@
 	basis. This process approximated the demographic shifts in fish
-	populations throughout a year while maintaining seasonal patterns for
-	spawning.}
+	populations throughout a year with seasonal spawning patterns.}
 
@@
 fishing locations for the fleet.  All species prices
-\replaced[id=PD]{were}{are} kept the same, across fleets\replaced[id=PD]{and
+\replaced[id=PD]{were}{are} kept the same across fleets \replaced[id=PD]{and
 	seasons}{, though can be made to vary seasonally}.
@@
 previously successful fishing locations. This \replaced[id=PD]{wa}{i}s achieved
-by \added[id=PD]{calculating expected profit from locations fished during}
-previous fishing events in the previous trip as well as the previous time
-periods in past years, and choosing randomly from the top 75 \% of fishing
-events \replaced[id=PD]{as defined by the expected profit}{in value}.
-\added[id=PD]{Expected profit was estimated from the revenue from previous
-	times fished at a location minus the fuel cost of travelling to the
-	location.} Simulation testing indicated that this learning increased
-the mean value of catches for the vessels, over just relying on the correlated
-random walk \todo{\added[id=JJ]{Correlated random walk of what}} function
-\added[id=PD]{as described for the 'within trip' decisions below}.
+by \added[id=PD]{calculating an expected profit based on the profit from
+	locations previously fished} in the preceding trip as well as the same
+month periods in preceding years, and choosing randomly from the top 75 \% of
+fishing events \replaced[id=PD]{as defined by the expected profit}{in value}.
+\added[id=PD]{Expected profit was estimated from the revenue achieved in
+	previous fishing events at a location minus the fuel cost of travelling
+	from the currently location to the new location.} Simulation testing
+indicated that this learning increased the mean value of catches for the
+vessels, over just relying on the correlated random walk
+\todo{\added[id=JJ]{Correlated random walk of what}} function \added[id=PD]{as
+	described for the 'within trip' decisions below} (MIGHT NEED TO INCLUDE
+IN SUPPLEMENTARY).
 
@@
 	within-trip decision become gradually more influenced by past locations
-	fished, based on the same process as the initial location, influenced
-	by expected profit at a fishing location.} A random walk was chosen for
-the exploratory fishing process as it is the simplest assumption commonly used
-in ecology to describe \added[id=PD]{optimal} animal \deleted[id=PD]{movement
-	which} search\replaced[id=PD]{ strategy}{ing} for
+	fished, based on the same process as the initial trip-level location,
+	influenced by expected profit at a fishing location.} A random walk was
+chosen for the exploratory fishing process as it is the simplest assumption
+commonly used in ecology to describe \added[id=PD]{optimal} animal
+\deleted[id=PD]{movement which} search\replaced[id=PD]{ strategy}{ing} for
 \added[id=PD]{exploiting} homogeneously distributed prey about which there is
@@
 that Peruvian anchovy fishermen have a stochastic search pattern similar to
-that observed with a lévy walk. However, it remains a subject of debate
+that observed with a lévy flight. However, it remains a subject of debate
 \added[id=PD]{\citep[e.g. see][]{Edwards2011, Reynolds2015}}, with the
-contention that search patterns may be more simply characteristed as random
+contention that search patterns may be more simply characterised as random
 walks \citep{Sakiyama2013} with specific patterns related to the
@@
 location) is determined by \deleted[id=JJ]{relating} recent fishing success,
-measured as the summed value of fish caught (revenue, $Rev$), $$Rev =
-\sum_{p=1}^{P} \replaced[id=PD]{L}{C}_{p} \cdot Pr_{p}$$ where
-$\replaced[id=PD]{L}{C}_{p}$ is \replaced[id=PD]{landings}{catch} of a
-population $p$, and $Pr_{p}$ price of a population, to step distance. Here,
-when fishing is successful vessels remain in a similar location and continue to
-exploit the local fishing grounds.  When unsuccessful, they move some distance
-away from the current fishing location.  The movement distance retains some
-degree of stochasticity, which can be controlled separately.
-
-The step function takes the form:
-
+measured as the summed value of fish caught (revenue, $Rev$),
+\begin{equation}
+Rev = \sum_{p=1}^{P} \replaced[id=PD]{L}{C}_{p} \cdot Pr_{p} 
+\end{equation}
+where $\replaced[id=PD]{L}{C}_{p}$ is \replaced[id=PD]{landings}{catch} of a
+population $p$, and $Pr_{p}$ price of a population. Here, when fishing is
+successful vessels remain in a similar location and continue to exploit the
+local fishing grounds. When unsuccessful, they move some distance away from
+the current fishing location.  The movement distance retains some degree of
+stochasticity, which can be controlled separately, but is determined by the
+relationship: 
 \begin{equation*}
@@
 			revenue?}\added[id=PD]{No, the opposite}}
-
-So that, a step from (x1,y1) to (x2, y2) is defined by:
-
+Where $\beta_{1}$, $\beta_{2}$ and $\beta_{3}$ are parameters determining the
+shape of the step function in its relation to revenue, so that, a step from
+(x1,y1) to (x2, y2) is defined by:
 \begin{equation*}
@@
 \end{equation*}
-
-with $k$ the concentration parameter from the von \replaced[id=JJ]{M}{m}ises
+where $k$ the concentration parameter from the von \replaced[id=JJ]{M}{m}ises
 distribution which we correlate with the revenue so that $k = (Rev + 1 /
 RefRev) * max_{k}$, where $max_{k}$ is the maximum concentration value, $k$,
-and RefRev is parameterised as for $\beta_{3}$ in the step length function.
+and $RefRev$ is parametrised as for $\beta_{3}$ in the step length function.
 
@@
 
-\subsection{Population parameterisation}
-
-We parameterised the simulation model for four populations with differing
+\subsection{Population parametrisation}
+
+We parametrised the simulation model for four populations with differing
 habitat preference\replaced{,}{ and} temperature tolerances (Figures
 \ref{S-fig:1}, \ref{S-fig:3}, \ref{S-fig:4}, \ref{S-fig:5}, \ref{S-fig:6},
-\ref{S-fig:7}), population demographic\replaced{,}{ and} recruitment functions.
-In addition, each of the populations has two defined spawning areas which
-result in the populations moving towards these areas in given weeks (Figure
-\ref{S-fig:2}) and population-specific movement rates (Table \ref{tab:1}). The
-realised movement of the populations for a number of weeks is shown in Figure
+\ref{S-fig:7}), population demographic and recruitment functions. In addition,
+each of the populations has two defined spawning areas which result in the
+populations moving towards these areas in given weeks (Figure \ref{S-fig:2})
+and population-specific movement rates (Table \ref{tab:1}). The realised
+movement of the populations for a number of weeks is shown in Figure
 \ref{S-fig:9} while the realised daily fishing mortality are shown in Figure
-\ref{S-fig:10}. \\
-
-\subsection{Fleet parameterisation}
-
-The fleets were parameterised to reflect five different characteristics based
+\ref{S-fig:10}.
+
+\subsection{Fleet parametrisation}
+
+The fleets were parametrised to reflect five different characteristics based
 on targeting preference and exploitation dynamics (Table \ref{tab:2}).
@@
 within a fleet have slightly different spatial distributions based on
-individual experience, while the step function was parameterised dynamically so
+individual experience, while the step function was parametrised dynamically so
 that vessels take smaller steps where the fishing location yields in a top
@@
 
-Each fleet was set so that, after the first year, fishing locations were chosen
-based on experience built up in the same month from previous years and from
-past trip fishing success. 'Success' in this context was defined as the
-locations where the top 75 \% of revenue from was found in previous trips.
+Each fleet was parametrised so that, after the first year, fishing locations
+were chosen based on experience built up in the same month from previous years
+and from past trip fishing success. 'Success' in this context was defined as
+the locations where the top 75 \% of expected profit would be found given
+previous trips revenue and cost of movement to the new fishing location. \\
 
@@
 the reduction in catches of a population given spatial closures. To do so, we
-first set up with simulation to run for 10 years based on a 100 X 100 square
-grid, with five fleets of 20 vessels each and four fish populations. Fishing
-takes place four times a day per vessel and five days a week, while population
-movement is every week.\todo{\added[id=JJ]{move to start of methods
-		section}\added[id=PD]{I think ecological modelling wants the
-		'calculations' section here..will check}} \\
-
-We allow the simulation to run unrestricted for 5 years\todo{\added[id=JJ]{Is
+set up a simulation to run for 50 years based on a 100 X 100 square grid, with
+five fleets of 20 vessels each and four fish populations. Fishing takes place
+four times a day per vessel and five days a week, while population movement is
+every week.\todo{\added[id=JJ]{move to start of methods section}\added[id=PD]{I
+		think ecological modelling wants the 'calculations' section
+		here..will check}} \\
+
+We allow the simulation to run unrestricted for 30 years\todo{\added[id=JJ]{Is
 		there equilibrium after 5 years or still some trend in
 		B}\added[id=PD]{Not at equilibrium yet...I need to rerun until
-		steady state, looks 20 years. Will update}}, and
-subsequently close areas for the last 5 years of the simulation based on data
-(either derived from the commercial catches, fisheries-independent survey or
-the 'real population' - the underlying populations assumed to be known
-perfectly) used at different spatial and temporal scales. \\
-
-The following steps are undertaken to determine
-closures:\todo{\added[id=JJ]{Procedure unclear. Refer to symbols in
-		methods section or switch order starting with description of
-		data type	etc..}\added[id=PD]{Yes, will redo}}
-
+		steady state, looks 20 years. Will update}}, and subsequently
+close areas for the last 20 years of the simulation based on data (either
+derived from the commercial catches, fisheries-independent survey or the 'real
+population' - the underlying populations assumed to be known perfectly) used at
+different spatial and temporal scales. \\
+
+The following steps are undertaken to determine closures:
+\todo{\added[id=JJ]{Procedure unclear. Refer to symbols in methods section or
+		switch order starting with description of data type
+		etc..}\added[id=PD]{Yes, will redo}}
 \begin{enumerate}
@@
 	\item Aggregate according to resolution
-	\item Interpolate across entire area at desired resoltion
-	\item Close top 5 \% of areas
+	\item Interpolate across entire area at desired resolution
+	\item Close area covering top 5 \% of catch 
 \end{enumerate}
-
 In total 56 closure scenarios were run which represent combinations of
@@
 	\item \textbf{spatial resolutions:} 1 x 1 grid, 5 x 5 grid, 10 x 10
-		grid and 20 x 20 grid.
+		grid and 20 x 20 grid,
+	\item \textbf{closure basis:} high catch rates of protected species, or
+		high ratio of protected species v secondary species.
 \end{itemize}
@@
 \section{Results}
-
-The species distribution themselves
 
@@
 	\caption{Description of variables for population dynamics sub-module}
+	\label{tab: pop_variable}
 	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}

### 2018-11-26 R/go_fish_old.R

@@ -1,375 +1,0 @@
-#' @title Go fish Old
-
-#' @description \code{go_fish_old} is a function used to apply the fishing
-#' simulation model
-
-#' @param sim_init is the initialised object from \code{init_sim}.
-#' @param fleet_params is the parameter settings initialised from \code{_init_fleets}
-#' @param fleet_catches is the DF initialised from \code{_init_fleets}
-#' @param sp_fleet_catches is a list of spatial catches (as a Numeric matrix)
-#' for the fleet of each population @param closed_areas is a dataframe with the
-#' x,y coordinates are any closed areas, provided internally by
-#' \link{close_areas}
-#' 
-
-#' @return is a list containing i) the fleet catch dataframes , ii) the spatial
-#' catches of each population
-
-#' @examples
-#'
-
-#' @export
-
-go_fish_old <- function(sim_init = NULL, fleet_params = NULL, fleet_catches = NULL, 
-		    sp_fleet_catches = NULL, pops = NULL, closed_areas = NULL, t = t) {
-
-##### extract the relevant components ###########
-params <- fleet_params      # fleet parameter list
-catch  <- fleet_catches     # fleet catches list
-catch_matrix <- sp_fleet_catches
-
-VPT <- params[["VPT"]] 			# Value per tonne
-Q <- params[["Qs"]]			# Catchability for vessel
-if(length(VPT) != length(Q)) stop("VPT and Q must be the same length")
-
-# 
-PastKnowledge <- params[["past_knowledge"]]
-
-######## indexes ##############
-idx <- sim_init$idx
-brk.idx <- sim_init$brk.idx
-###############################
-
-##### past knowledge decisions ####
-
-## If its the first location fished, need to choose a random location
-if(t == 1) {
-coords <- c(round(runif(1,1,idx[["nrows"]])),round(runif(1,1,idx[["ncols"]]))) # Choose a random lat and lon
-}
-	
-
-# For t > 1
-if(t > 1) {
-
-coords <- c(catch[t-1, "x"], catch[t-1,"y"]) # Previous coordinates
-
-# If incorporating past knowledge, and its a new trip...and not in the
-	# first year
[…]

### 2019-01-24 write_up/mixfishsim_ecolmod.tex
Bug fix in the real_pop closures on a monthly timescale - wasn't filtering, is now!

@@
 \usepackage{booktabs}
-\usepackage[textsize=scriptsize]{todonotes}
-%\usepackage[textsize=scriptsize, disable]{todonotes}  %% to turn off notes
+%\usepackage[textsize=scriptsize]{todonotes}
+\usepackage[textsize=scriptsize, disable]{todonotes}  %% to turn off notes
 \usepackage{eurosym}
@@
 % For track-changes
-\usepackage[draft]{changes}
-%\usepackage[final]{changes} %% to turn off changes
+%\usepackage[draft]{changes}
+\usepackage[final]{changes} %% to turn off changes
 \definechangesauthor[color = red]{JM}
@@
 advice is limited by a lack of highly resolved knowledge of population
-distributions, movement and how fishers interact with different fish
+distributions, population movement and how fishers interact with different fish
 populations. This reflects the fact that data on fish location at high temporal
@@
 fisheries monitoring purposes, and ii) the true underlying population
-structures input to the simulation, to establish the potential and limitations
-of fishery-dependent data - an inherently biased sampling method due to
-fisher's targeting- to provide a robust picture of spatiotemporal
-distributions. Finally, we simulate an area closure based on areas defined from
-the known ("real-population") distribution, commercial catch data and survey
-data at different temporal and spatial resolutions and assess their
-effectiveness on reducing catches of a fish population. \\
+structures input to the simulation. We use the results to establish the
+potential and limitations of fishery-dependent data - an inherently biased
+sampling method due to fisher's targeting- to provide a robust picture of
+spatiotemporal distributions. Finally, we simulate an area closure based on
+areas defined from the known ("real-population") distribution, commercial catch
+data and survey data at different temporal and spatial resolutions and assess
+their effectiveness on reducing catches of a fish population. \\
 
@@
 	\hline
-	Matérn $\nu$ & 1/0.15 & 1/0.05 & 1/0.55 & 1/0.05  \\
+	Matérn $\nu$ & 1/0.015 & 1/0.05 & 1/0.01 & 1/0.005  \\
 	Matérn $\kappa$ & 1 & 2 & 1 & 1  \\
@@
 	Spawning multiplier & 10 & 10 & 10 & 10 \\
-	Movement $\lambda$ & 0.3 & 0.3 & 0.3 & 0.3 \\
+	Movement $\lambda$ & 0.1 & 0.1 & 0.1 & 0.1 \\
 	\hline
@@
 	Starting Biomass & 1e5 & 2e5 & 1e5 & 1e4 \\
-	Beverton-Holt Recruit 'a' & 60 & 100 & 80 & 2 \\
-	Beverton-Holt Recruit 'b' & 250 & 250 & 200 & 50 \\
-	Beverton-Holt Recruit $\sigma^2$ & 0.4 & 0.3 & 0.4 & 0.3 \\
+	Beverton-Holt Recruit 'a' & 6 & 27 & 18 & 0.3  \\
+	Beverton-Holt Recruit 'b' & 4 & 4 & 11 & 0.5 \\
+	Beverton-Holt Recruit $\sigma^2$ & 0.7 & 0.6 & 0.7 & 0.6 \\
 	Recruit week & 13-16 & 12-16 & 14-16 & 16-20 \\
@@
 	$wt_{d-1}$ & 0.1 & 0.1 & 0.1 & 0.1 \\
-	M (annual) & 0.2 & 0.2 & 0.2 & 0.1 \\
+	M (annual) & 0.2 & 0.1 & 0.2 & 0.1 \\
+	\hline
+	Movement dynamics & & & & \\
+	\hline
+	$\mu$ & 12 & 15 & 17 & 14 \\
+	$\sigma^2$ & 8 & 9 & 7 & 10 \\
 	\hline
@@
 	Price Pop2 & 200 & 200 & 200 & 200 & 200 \\
-	Price Pop3 & 600 & 600 & 600 & 600 & 600 \\
-	Price Pop4 & 1600 & 1600 & 1600 & 1600 & 1600 \\
+	Price Pop3 & 350 & 350 & 350 & 350 & 350 \\
+	Price Pop4 & 600 & 600 & 600 & 600 & 600 \\
 	$Q$ Pop1 & 0.01 & 0.02 & 0.02 & 0.01 & 0.01 \\
@@
 	step function $\beta_1$ & 1 & 2 & 1 & 2 & 3 \\
-	step function $\beta_2$ & 10 & 10 & 8 & 12 & 7 \\
+	step function $\beta_2$ & 10 & 15 & 8 & 12 & 7 \\
 	step function $\beta_3$ & Q90 & Q90 & Q85 & Q90 & Q80 \\
-	step function $rate$ & 10 & 20 & 15 & 25 & 10 \\
+	step function $rate$ & 20 & 30 & 25 & 35 & 20 \\
 	Past Knowledge & T & T & T & T & T \\
@@
 	Past Trip & T & T & T & T & T \\
-	Threshold & 0.75 & 0.75 & 0.75 & 0.75 & 0.75 \\
+	Threshold & 0.7 & 0.7 & 0.7 & 0.7 & 0.7 \\
+	Fuel Cost & 3 & 2 & 5 & 2 & 1 \\
 	\hline

### 2019-01-24 R/close_areas.R

@@ -195,12 +195,12 @@ if(basis == 'real_pop') {
 
 		if(rationale == 'high_pop') {
 		## Filter as appropriate:- here based on either yr_base or
-		interpdat <- filter(logs, year %in% yr) %>% group_by(x, y) %>% summarise(dat= sum(get(spp_1))/n())
+		interpdat <- filter(logs, year %in% yr, month %in% mn) %>% group_by(x, y) %>% summarise(dat= sum(get(spp_1))/n())
 		}
 
 		if(rationale == 'high_ratio') {
 		## Filter as appropriate:- here based on either yr_base or
-		interpdat <- filter(logs, year %in% yr) %>% group_by(x, y) %>% summarise(dat1 = sum(get(spp_1))/n(), dat2 =sum(get(spp_2))/n())
+		interpdat <- filter(logs, year %in% yr, month %in% mn) %>% group_by(x, y) %>% summarise(dat1 = sum(get(spp_1))/n(), dat2 =sum(get(spp_2))/n())
 		## Calculate the ratios
 		interpdat$dat <- interpdat$dat2 / interpdat$dat1
 		## Deal with any NaN and Infs - calculate the Infs as large

### 2019-01-24 analysis/Plot_Bio.R

@@ -1,9 +1,12 @@
 
 library(MixFishSim)
 
-Run <- 0
+#Run <- 0
 
-load(file.path('.', 'Scenario_runs_Nov18', paste0('Scenario_',Run,'.RData')))
+#load(file.path('.', 'Scenario_runs_Nov18', paste0('Scenario_',Run,'.RData')))
+load(file.path('.', 'Scenario_runs_Nov18', paste0('Comparison_Run.RData')))
+
+
 
 pop <- res[["pop_bios"]]
 plot_pop_summary(res, timestep = "annual")

### 2019-01-24 analysis/Plots.R

@@ -8,7 +8,8 @@ library(MixFishSim)
 load('Common_Params.RData')
 
 Run <- 0 
-load(file.path('Scenario_runs_Nov18', paste0("Scenario_", Run, ".RData")))
+#load(file.path('Scenario_runs_Nov18', paste0("Scenario_", Run, ".RData")))
+load(file.path('Scenario_runs_Nov18', paste0("Comparison_Run.RData")))
 
 plot_pop_summary(res, timestep = "annual", save = FALSE)
 

### 2019-01-24 analysis/Plots_Combined.R

@@ -10,7 +10,8 @@ load('Common_Params.RData')
 
 runs <- 0:56
 
-for(r in runs) {
+for(r in runs){
+print(r)
 load(file.path('Scenario_runs_Nov18', paste0('Scenario_', r, '.RData')))
 #assign(paste0("sc",r),res)
 #}

### 2019-01-24 analysis/Run_for_Model_Comparison.R

@@ -22,7 +22,7 @@ load('Common_Params.RData')
 load('Fixed_Closure_Locations.RData')
 
 ## Change closure per scenario
-closure <- init_closure(input_coords = cl[,c("x","y")], year_start = 1, temp_dyn = "yearly")
+closure <- init_closure(input_coords = cl[,c("x","y")], year_start = 30, temp_dyn = "yearly")
 
 ## run_sim function for overall control
 res <- run_sim(sim_init = sim, pop_init = Pop, move_cov = moveCov, fleets_init = fleets, hab_init = hab, InParallel = TRUE, cores = 1, save_pop_bio = TRUE, survey = survey, closure = closure)

### 2019-01-28 write_up/C_changes.tex
Updated text and output latex table of results

% latex table generated in R 3.5.2 by xtable 1.8-3 package
% Mon Jan 28 16:59:10 2019
\begin{longtable}{rllrrrlllr}
\caption{Catch effects of the closure scenarios} \\ 
  \hline
scenario & metric & pop & before & after & diff & timescale & basis & data\_type & resolution \\ 
  \hline
 53 & Catch & spp\_3 & 112112.36 & 112521.76 & 0.37 & yearly & high\_pop & real\_pop & 20.00 \\ 
   49 & Catch & spp\_3 & 112112.36 & 113686.57 & 1.40 & yearly & high\_pop & survey & 20.00 \\ 
   31 & Catch & spp\_3 & 112112.36 & 114683.92 & 2.29 & yearly & high\_pop & commercial & 10.00 \\ 
   52 & Catch & spp\_3 & 112112.36 & 118512.95 & 5.71 & monthly & high\_pop & real\_pop & 20.00 \\ 
   51 & Catch & spp\_3 & 112112.36 & 120188.28 & 7.20 & weekly & high\_pop & real\_pop & 20.00 \\ 
   30 & Catch & spp\_3 & 112112.36 & 121325.90 & 8.22 & monthly & high\_pop & commercial & 10.00 \\ 
   29 & Catch & spp\_3 & 112112.36 & 122650.01 & 9.40 & weekly & high\_pop & commercial & 10.00 \\ 
   21 & Catch & spp\_3 & 112112.36 & 127010.38 & 13.29 & yearly & high\_pop & survey & 5.00 \\ 
   44 & Catch & spp\_3 & 112112.36 & 131095.21 & 16.93 & monthly & high\_pop & commercial & 20.00 \\ 
   35 & Catch & spp\_3 & 112112.36 & 133798.31 & 19.34 & yearly & high\_pop & survey & 10.00 \\ 
   38 & Catch & spp\_3 & 112112.36 & 135496.66 & 20.86 & monthly & high\_pop & real\_pop & 10.00 \\ 
    7 & Catch & spp\_3 & 112112.36 & 137987.16 & 23.08 & yearly & high\_pop & survey & 1.00 \\ 
   37 & Catch & spp\_3 & 112112.36 & 138717.85 & 23.73 & weekly & high\_pop & real\_pop & 10.00 \\ 
   43 & Catch & spp\_3 & 112112.36 & 139107.65 & 24.08 & weekly & high\_pop & commercial & 20.00 \\ 
   39 & Catch & spp\_3 & 112112.36 & 139763.03 & 24.66 & yearly & high\_pop & real\_pop & 10.00 \\ 
   15 & Catch & spp\_3 & 112112.36 & 143183.40 & 27.71 & weekly & high\_pop & commercial & 5.00 \\ 
    2 & Catch & spp\_3 & 112112.36 & 146551.20 & 30.72 & monthly & high\_pop & commercial & 1.00 \\ 
   45 & Catch & spp\_3 & 112112.36 & 146581.28 & 30.74 & yearly & high\_pop & commercial & 20.00 \\ 
   16 & Catch & spp\_3 & 112112.36 & 147719.91 & 31.76 & monthly & high\_pop & commercial & 5.00 \\ 
    1 & Catch & spp\_3 & 112112.36 & 149313.55 & 33.18 & weekly & high\_pop & commercial & 1.00 \\ 
   25 & Catch & spp\_3 & 112112.36 & 152756.42 & 36.25 & yearly & high\_pop & real\_pop & 5.00 \\ 
   23 & Catch & spp\_3 & 112112.36 & 155199.82 & 38.43 & weekly & high\_pop & real\_pop & 5.00 \\ 
   24 & Catch & spp\_3 & 112112.36 & 156523.19 & 39.61 & monthly & high\_pop & real\_pop & 5.00 \\ 
    3 & Catch & spp\_3 & 112112.36 & 157369.75 & 40.37 & yearly & high\_pop & commercial & 1.00 \\ 
   17 & Catch & spp\_3 & 112112.36 & 157786.23 & 40.74 & yearly & high\_pop & commercial & 5.00 \\ 
   10 & Catch & spp\_3 & 112112.36 & 160278.27 & 42.96 & monthly & high\_pop & real\_pop & 1.00 \\ 
    9 & Catch & spp\_3 & 112112.36 & 161276.13 & 43.85 & weekly & high\_pop & real\_pop & 1.00 \\ 
   11 & Catch & spp\_3 & 112112.36 & 165538.03 & 47.65 & yearly & high\_pop & real\_pop & 1.00 \\ 
   \hline
\hline
\label{tab:7}
\end{longtable}

### 2019-01-28 write_up/F_changes.tex
Updated text and output latex table of results

% latex table generated in R 3.5.2 by xtable 1.8-3 package
% Mon Jan 28 16:57:19 2019
\begin{longtable}{rllrrrlllr}
\caption{Fishing mortality effects of the closure scenarios} \\ 
  \hline
scenario & metric & pop & before & after & diff (\%) & timescale & basis & data\_type & resolution \\ 
  \hline
  9 & F & spp\_3 & 1.08 & 0.29 & -73.47 & weekly & high\_pop & real\_pop & 1.00 \\ 
   10 & F & spp\_3 & 1.08 & 0.29 & -72.94 & monthly & high\_pop & real\_pop & 1.00 \\ 
   11 & F & spp\_3 & 1.08 & 0.35 & -68.04 & yearly & high\_pop & real\_pop & 1.00 \\ 
   45 & F & spp\_3 & 1.08 & 0.58 & -46.70 & yearly & high\_pop & commercial & 20.00 \\ 
    1 & F & spp\_3 & 1.08 & 0.58 & -46.21 & weekly & high\_pop & commercial & 1.00 \\ 
   23 & F & spp\_3 & 1.08 & 0.59 & -45.27 & weekly & high\_pop & real\_pop & 5.00 \\ 
    2 & F & spp\_3 & 1.08 & 0.59 & -45.06 & monthly & high\_pop & commercial & 1.00 \\ 
    7 & F & spp\_3 & 1.08 & 0.60 & -44.48 & yearly & high\_pop & survey & 1.00 \\ 
   24 & F & spp\_3 & 1.08 & 0.61 & -43.20 & monthly & high\_pop & real\_pop & 5.00 \\ 
    3 & F & spp\_3 & 1.08 & 0.64 & -40.82 & yearly & high\_pop & commercial & 1.00 \\ 
   25 & F & spp\_3 & 1.08 & 0.65 & -39.94 & yearly & high\_pop & real\_pop & 5.00 \\ 
   17 & F & spp\_3 & 1.08 & 0.67 & -38.11 & yearly & high\_pop & commercial & 5.00 \\ 
   15 & F & spp\_3 & 1.08 & 0.71 & -34.38 & weekly & high\_pop & commercial & 5.00 \\ 
   43 & F & spp\_3 & 1.08 & 0.71 & -34.31 & weekly & high\_pop & commercial & 20.00 \\ 
   16 & F & spp\_3 & 1.08 & 0.73 & -32.58 & monthly & high\_pop & commercial & 5.00 \\ 
   51 & F & spp\_3 & 1.08 & 0.78 & -27.92 & weekly & high\_pop & real\_pop & 20.00 \\ 
   37 & F & spp\_3 & 1.08 & 0.78 & -27.76 & weekly & high\_pop & real\_pop & 10.00 \\ 
   39 & F & spp\_3 & 1.08 & 0.79 & -26.98 & yearly & high\_pop & real\_pop & 10.00 \\ 
   38 & F & spp\_3 & 1.08 & 0.81 & -25.47 & monthly & high\_pop & real\_pop & 10.00 \\ 
   21 & F & spp\_3 & 1.08 & 0.81 & -25.21 & yearly & high\_pop & survey & 5.00 \\ 
   35 & F & spp\_3 & 1.08 & 0.81 & -25.05 & yearly & high\_pop & survey & 10.00 \\ 
   44 & F & spp\_3 & 1.08 & 0.87 & -19.91 & monthly & high\_pop & commercial & 20.00 \\ 
   52 & F & spp\_3 & 1.08 & 0.88 & -18.39 & monthly & high\_pop & real\_pop & 20.00 \\ 
   30 & F & spp\_3 & 1.08 & 0.96 & -11.06 & monthly & high\_pop & commercial & 10.00 \\ 
   29 & F & spp\_3 & 1.08 & 0.98 & -9.80 & weekly & high\_pop & commercial & 10.00 \\ 
   31 & F & spp\_3 & 1.08 & 1.03 & -4.36 & yearly & high\_pop & commercial & 10.00 \\ 
   53 & F & spp\_3 & 1.08 & 1.06 & -1.64 & yearly & high\_pop & real\_pop & 20.00 \\ 
   49 & F & spp\_3 & 1.08 & 1.07 & -1.01 & yearly & high\_pop & survey & 20.00 \\ 
   \hline
\hline
\label{tab:6}
\end{longtable}

### 2019-01-28 write_up/mixfishsim_ecolmod.tex
Updated text and output latex table of results

@@
 \usepackage{booktabs}
-%\usepackage[textsize=scriptsize]{todonotes}
-\usepackage[textsize=scriptsize, disable]{todonotes}  %% to turn off notes
+\usepackage[textsize=scriptsize]{todonotes}
+%\usepackage[textsize=scriptsize, disable]{todonotes}  %% to turn off notes
 \usepackage{eurosym}
+\usepackage{longtable}
 
@@
 structures input to the simulation. We use the results to establish the
-potential and limitations of fishery-dependent data - an inherently biased
-sampling method due to fisher's targeting- to provide a robust picture of
-spatiotemporal distributions. Finally, we simulate an area closure based on
-areas defined from the known ("real-population") distribution, commercial catch
-data and survey data at different temporal and spatial resolutions and assess
-their effectiveness on reducing catches of a fish population. \\
-
-We conclude from our simulations that commercial data, while not unbiased,
+potential and limitations of fishery-dependent data in providing a robust
+picture of spatiotemporal distributions. Finally, we simulate an area closure
+based on areas defined from the known ("real-population") distribution,
+commercial catch data and survey data at different temporal and spatial
+resolutions and assess their effectiveness on reducing catches of a fish
+population. \\
+
+We conclude from our simulations that commercial data, while containing bias,
 provides a useful tool for managing catches in mixed fisheries if applied at
@@
 using species-unselective fishing gear. \added[id=PD]{In doing so} fisheries
-\deleted[id=PD]{that} catch an assemblage of species
+\deleted[id=PD]{that}catch an assemblage of species
 \added[id=PD]{and}\deleted{, known as mixed fisheries} \replaced[id=JJ]{may}{,
@@
 discard\deleted[id=JJ]{ing} overquota catch \added[id=JJ]{when managed by
-	single species quotas,} leading to overexploitation of fish populations
-\added[id=JJ]{\citep{Ulrich2011a, Batsleer2015}}.  \added[id=JJ]{This
-	discarding of fish in excess of quota hampers the ability to limit
-	fishing mortality to within sustainable limits \citep{Alverson1994,
-		Crowder1998, Rijnsdorp2007}} \deleted[id=PD]{; reducing
-	discarding is crucial}and ensure biological and economic sustainability
-of fisheries\deleted[id=JJ]{ and implementation of an ecosystem approach to
-	fisheries}. As such, there is increasing interest
-in technical solutions such as gear and spatial closures as ways of
+	single species quotas and fishers exhaust or more quota, may} lead to
+overexploitation of fish populations \added[id=JJ]{\citep{Ulrich2011a,
+		Batsleer2015}}.  \added[id=JJ]{This discarding of fish in
+	excess of quota hampers the ability to limit fishing mortality to
+	within sustainable limits \citep{Alverson1994, Crowder1998,
+		Rijnsdorp2007}} \deleted[id=PD]{; reducing discarding is
+	crucial}and the ability to manage for the biological and economic
+sustainability of fisheries\deleted[id=JJ]{ and implementation of an ecosystem
+	approach to fisheries}. As such, there is increasing interest in
+technical solutions such as gear and spatial closures as ways of
 \replaced[id=PD]{reducing unwanted catch}{avoiding discard\added[id=JJ]{ing of
@@
 \added[id=PD]{\citep{Holmes2011, Little2014, Dunn2014a}}. However,
-\deleted[id=PD]{its} implementation is hampered by lack of knowledge of fish
-and fishery spatiotemporal dynamics and understanding of the scale at which
-processes are important for management. Understanding the correct scale for
-spatial management is crucial in order to implement measures at a resolution
-that ensures effective management \citep{Dunn2016} while minimising economic
-impact.  For example, a scale that promotes species avoidance for vulnerable or
-low quota species while allowing continuance of sustainable fisheries for
-available quota species.\\
+\deleted[id=PD]{its} implementation of avoidance measures is hampered by lack
+of knowledge of fish and fishery spatiotemporal dynamics and understanding of
+the scale at which processes are important for management. Understanding the
+correct scale for spatial measures is crucial in order to implement measures at
+a resolution that ensures effective management \citep{Dunn2016} while
+minimising economic impact.  For example, a scale that promotes species
+avoidance for vulnerable or low quota species while allowing continuance of
+sustainable fisheries for available quota species.\\
 
@@
 \citep{Lee2010, Bastardie2010, Gerritsen2012, Mateo2016} and more real-time
-spatial management has been possible \citep[e.g.][]{Holmes2011}.  Such
-information is, however, patchy and derived from an inherently biased sampling
-programme (i.e. targeted fishing). \deleted[id=PD]{ Further, fishers generally only recorded
-landings (not catch) on a daily basis\todo{\added[id=JJ]{Its not clear what the
-		problem is: landings collected on daily basis or landings
-		recorded rather than catch}}.  This leads to questions about
-the validity of inference that can be drawn from landings data assigned to VMS
-activity pings.}\todo{\added[id=JJ]{This comes as a surprise: I thought this was
-		going to be about discards}\added[id=PD]{Agree, have removed
-		this to avoid confusion}}\\
+spatial management has been possible \citep[e.g.][]{Holmes2011}.  However, such
+information is derived from an inherently biased sampling programme, targeted
+fishing. \deleted[id=PD]{ Further, fishers generally only recorded landings
+	(not catch) on a daily basis\todo{\added[id=JJ]{Its not clear what the
+			problem is: landings collected on daily basis or
+			landings recorded rather than catch}}.  This leads to
+	questions about the validity of inference that can be drawn from
+	landings data assigned to VMS activity pings.}\todo{\added[id=JJ]{This
+		comes as a surprise: I thought this was going to be about
+		discards}\added[id=PD]{Agree, have removed this to avoid
+		confusion}}\\
 
@@
 		population structures. We compare at different spatial and
-		temporal aggregations of data the real population to: 
+		temporal aggregations of the simulated population distributions
+		to: 
 		\begin{enumerate}
-			\item the inferred population from a stratified fixed-site sampling survey design
-				commonly used for fisheries monitoring purposes, otherwise know as a
-				fisheries-independent survey,
-			\item the inferred population from our fishery-dependent model which includes
+			\item the inferred population from a stratified
+				fixed-site sampling survey design commonly used
+				for fisheries monitoring purposes, otherwise
+				know as a fisheries-independent survey,
+			\item the inferred population from our
+				fishery-dependent model which includes
 				fishery-induced sampling dynamics.\\
 		\end{enumerate}
-	\item to understand the impact of data aggregation and source on
-		spatial fisheries management measures we simulate a fishery closure to
-		protect a species based on different spatial and temporal data
-		aggregations:
+	\item to understand the impact of data aggregation and data source on
+		spatial fisheries management measures we simulate a fishery
+		closure to protect a species based on different spatial and
+		temporal data aggregations:
 		\begin{enumerate}
@@
 and vessels in cell $c$ for the population during the day $d$, and $B_{c,d}$
-the daily biomass for the population in the cell. \todo{\added[id=CM]{[link $F$ to
-	effort and catchability - as I think we have F as an emergent property
-	of the fleets rather than something we solve for (I could be wrong
-	though!) - catch for a vessel is a product of catchability and biomass,
-	i.e. C = qB, but this catch is summed to solve for F. So its both
-	really]}}\\
+the daily biomass for the population in the cell. Here, catch and fishing
+mortality are the sum of those across all fleets and vessels, where $F_{fl, v,
+	c, d, p} = E_{fl, v, c, d} \cdot Q_{fl, p} \cdot B_{c, d, p}$ with
+$fl$, $v$ and $p$ the fleet, vessel and population respectively and $E$ and $Q$
+fishing effort and catchability. \todo{\added[id=CM]{[link $F$ to effort and
+		catchability - as I think we have F as an emergent property of
+		the fleets rather than something we solve for (I could be wrong
+		though!) - catch for a vessel is a product of catchability and
+		biomass, i.e. C = qB, but this catch is summed to solve for F.
+		So its both really]}}\\
 
@@
 where $\alpha$ is the maximum productivity per spawner and $\beta$ the density
-dependent reduction in productivity as the SSB increases.
+dependent reduction in productivity as the SSB increases. In this study, the
+Beverton-Holt form of stock recruit relationship was used for all populations.
 
@@
 	employed} a Gaussian spatial process \added[id=JJ]{was employed} to
-model habitat suitability for each of the populations\replaced[id=JJ]{. An}{,
-	with an} advection-diffusion process \deleted[id=JJ]{to}
-control\added[id=JJ]{led} \deleted[id=JJ]{how the} population\deleted[id=JJ]{s}
-move\replaced[id=JJ]{ment}{d} over time with a moving temperature covariate to
-capture temporal dependencies\todo{\added[id=JJ]{What have a temperature
-		covariate? Could just use time}\added[id=PD]{Was intended as
-		some biological meaning - species thermal tolerances load onto
-		the temperature effect - so could be different per species}}.
-\deleted[id=JJ]{This was intended to balance realism in population movement,
-	capturing the main directed and random processes, and practicality of
-	modelling the population rather than individual fish.} \\
-
-For \deleted[id=PD]{the} habitat we define\added[id=PD]{d} a Gaussian random
-field process\todo{\added[id=JJ]{Not clear how habitat/GRF affect local
+model habitat suitability for each of the populations on a 2d
+grid\replaced[id=JJ]{. An}{, with an} advection-diffusion process
+\deleted[id=JJ]{to} control\added[id=JJ]{led} \deleted[id=JJ]{how the}
+population\deleted[id=JJ]{s} move\replaced[id=JJ]{ment}{d}, with a time-varying
+temperature covariate used to change the spatial bounds of suitable habitat
+on a weekly time-step\todo{\added[id=JJ]{What have a temperature covariate? Could just
+		use time}\added[id=PD]{Was intended as some biological meaning
+		- species thermal tolerances load onto the temperature effect -
+		so could be different per species}}.  \deleted[id=JJ]{This was
+	intended to balance realism in population movement, capturing the main
+	directed and random processes, and practicality of modelling the
+	population rather than individual fish.} \\
+
+For \deleted[id=PD]{the}habitat we first define\added[id=PD]{d} a Gaussian
+random field process\todo{\added[id=JJ]{Not clear how habitat/GRF affect local
 		abundances, only have $B_{y,d}$}\added[id=PD]{Have included
@@
 process generates\replaced[id=PD]{;}{, and} we used the \textit{Matérn}
-\deleted[id=PD]{family of} covariance structure\deleted[id=PD]{s},
-\replaced[id=PD]{as}{one where} the correlation strength weakens the further
-the distance apart \deleted[id=PD]{(i.e. the correlation between $S(x)$ and
-	$S(x')$ decreases as the distance $u = ||x - x'||$ increases)}.
-\added[id=PD]{The Matérn covariance structure models the spatial
-	autocorrelation, where animal densities are observed to be more similar
-	in nearby locations \citep{Tobler1970,
-		F.Dormann2007}}\replaced[id=PD]{. It is}{The \textit{Matérn}
-	correlation} is a two-parameter family where: 
+\deleted[id=PD]{family of}covariance structure\deleted[id=PD]{s},
+\replaced[id=PD]{where}{one where} the correlation strength weakens with
+distance\deleted[id=PD]{(i.e. the correlation between $S(x)$ and $S(x')$
+	decreases as the distance $u = ||x - x'||$ increases)}.
+\added[id=PD]{This enables us to model the spatial autocorrelation observed in
+	animal populations where density is more similar in nearby locations
+	\citep{Tobler1970, F.Dormann2007}} and we change the parameters to
+implement different spatial structures for the populations. The \textit{Matérn}
+correlation is a two-parameter family where: 
 	\begin{center}
@@
 called the order, is a shape parameter which determines the smoothness of the
-underlying process. \\
+underlying process (Figure \ref{S-fig:16}). \\
 
@@
 the \textit{RFSimulate} function of the \textit{RandomFields} R package
-\citep{Schlater2015}, implementing different parameter settings to affect the
-patchiness of the populations. Each population \replaced[id=PD]{was}{is}
-initialised at a single location, and subsequently move\replaced[id=PD]{ed}{s}
-according to a probabilistic distrib\added[id=PD]{u}tion based on habitat
-suitability, temperature and distance from current cell\replaced[id=PD]{:}{.} 
+\citep{Schlater2015}. Each population \replaced[id=PD]{was}{is} initialised at
+a single location, and subsequently move\replaced[id=PD]{ed}{s} according to a
+probabilistic distrib\added[id=PD]{u}tion based on habitat suitability
+(represented by the normalised values from the GRFs), temperature and distance
+from current cell\replaced[id=PD]{:}{.} 
 \begin{equation}
@@
 
-During specified weeks of the year, the habitat quality
-\replaced[id=PD]{was}{is} modified for \added[id=PD]{user-defined} spawning
-habitat\deleted[id=PD]{s}, \replaced[id=PD]{resulting in}{meaning} each
-population \replaced[id=PD]{having}{has} a concentrated area where spawning takes
-place and the population move\replaced[id=PD]{d}{s} towards
-\replaced[id=PD]{these cells}{this} in the weeks prior to
-spawning.\todo{\added[id=JM]{What does it mean concisely? Areas are assigned?}
-\added[id=PD]{Yes, the areas are pre-defined - I have amended to reflect and
-	tried to clarify}} \\
-
-The temperature field \replaced[id=PD]{was}{is} simulated to be on a gradient
-from a South-Westerly to North-Easterly direction, with temperature in each
-cell changing gradually on a week-by-week basis so that initially high
-temperature areas cycle\added[id=PD]{d} to lower temperatures and low
-temperature areas vice versa. Each population $p$ \replaced[id=PD]{wa}{i}s
-assigned a thermal tolerance with mean, $\mu\added[id=PD]{_{p}}$ and variance,
+During pre-defined weeks of the year the habitat quality is modified with
+\added[id=PD]{user-defined} spawning habitat locations\deleted[id=PD]{s},
+\replaced[id=PD]{resulting in}{meaning} each population
+\replaced[id=PD]{having}{has} concentrated areas where spawning takes place. In
+the simulations the populations move\replaced[id=PD]{d}{s} towards
+\replaced[id=PD]{these cells}{this} in the weeks prior to spawning, resulting
+in directional movement towards the spawning grounds.\todo{\added[id=JM]{What
+		does it mean concisely? Areas are assigned?} \added[id=PD]{Yes,
+		the areas are pre-defined - I have amended to reflect and tried
+		to clarify}} \\
+
+The temperature field \replaced[id=PD]{was}{is} defined on a gradient from a
+South-Westerly to North-Easterly direction, with temperature in each cell
+changing gradually on a week-by-week basis so that initially high temperature
+areas cycle\added[id=PD]{d} to lower temperatures and low temperature areas
+\textit{vice versa}. Each population $p$ \replaced[id=PD]{wa}{i}s assigned a thermal
+tolerance with mean, $\mu\added[id=PD]{_{p}}$ and variance,
 $\sigma^2\added[id=PD]{_{p}}$ so that each cell and population temperature
@@
 \added[id=PD]{The final process resulted in independent populations structure
-	and movement patterns, with population movement occuring on a weekly
+	and movement patterns, with population movement occurring on a weekly
 	basis. This process approximated the demographic shifts in fish
-	populations throughout a year with seasonal spawning patterns.}
+	populations throughout a year with seasonal spawning patterns (e.g.
+	Figure \ref{S-fig:5}).}
 
@@
 a trip; and within-trip decisions, determining movement from one fishing spot
-to another within a trip.
+to another within a trip. Together, these element implement an explore-exploit
+type strategy for individual vessels to maximise their catch from an unknown
+resource distribution (\cite{Bailey2018}).
 
@@
 Each fleet of \textit{n} vessels \replaced[id=PD]{was}{is} characterised by
-both a general efficiency, \textit{Q}, and a population specific efficiency,
-${Q_{p}}$.  Thus, the product of these parameters affect\replaced[id=PD]{s}{ed}
-the overall catch rates for the fleet and the preferential targeting of one
-population over another. This, in combination with the parameter choice for the
-step-function \added[id=PD]{defined below} (as well as some randomness from the
-exploratory fishing process) determine\replaced[id=PD]{d}{s} the preference of
-fishing locations for the fleet.  All species prices
-\replaced[id=PD]{were}{are} kept the same across fleets \replaced[id=PD]{and
-	seasons}{, though can be made to vary seasonally}.
+both a general efficiency, $Q_{fl}$, and a population specific efficiency,
+${Q_{fl, p}}$.  Thus, the product of these parameters [$Q_{fl} \cdot Q_{fl,
+	p}$] affect\replaced[id=PD]{s}{ed} the overall catch rates for the
+fleet and the preferential targeting of one population over another. This, in
+combination with the parameter choice for the step-function
+\added[id=PD]{defined below} (as well as some randomness from the exploratory
+fishing process) determine\replaced[id=PD]{d}{s} the preference of fishing
+locations for the fleet.  All species prices \replaced[id=PD]{were}{are} kept
+the same across fleets \replaced[id=PD]{and seasons}{, though can be made to
+	vary seasonally}.
 
 \subsubsection{Trip-level decisions}
-
-NOTE: THIS IS EXPLORE-EXPLOIT STRATEGY VIZ. BAILEY ET AL POSEIDON MODEL.
 
@@
 previously successful fishing locations. This \replaced[id=PD]{wa}{i}s achieved
-by \added[id=PD]{calculating an expected profit based on the profit from
-	locations previously fished} in the preceding trip as well as the same
-month periods in preceding years, and choosing randomly from the top 75 \% of
-fishing events \replaced[id=PD]{as defined by the expected profit}{in value}.
-\added[id=PD]{Expected profit was estimated from the revenue achieved in
-	previous fishing events at a location minus the fuel cost of travelling
-	from the currently location to the new location.} Simulation testing
-indicated that this learning increased the mean value of catches for the
-vessels, over just relying on the correlated random walk
+by \added[id=PD]{calculating an expected revenue based on the catches from
+	locations fished} in the preceding trip as well as the same month
+periods in previous years and the travel costs from the port to the fishing
+grounds, and choosing randomly from the top 75 \% of fishing events
+\replaced[id=PD]{as defined by the expected profit}{in value}. Simulation
+testing indicated that this learning increased the mean value of catches for
+the vessels, over just relying on the correlated random walk
 \todo{\added[id=JJ]{Correlated random walk of what}} function \added[id=PD]{as
@@
 Fishing locations within a trip are \added[id=PD]{initially} determined by a
-modified random walk process. \added[id=PD]{As the simulation progresses, the
-	within-trip decision become gradually more influenced by past locations
-	fished, based on the same process as the initial trip-level location,
-	influenced by expected profit at a fishing location.} A random walk was
-chosen for the exploratory fishing process as it is the simplest assumption
-commonly used in ecology to describe \added[id=PD]{optimal} animal
-\deleted[id=PD]{movement which} search\replaced[id=PD]{ strategy}{ing} for
-\added[id=PD]{exploiting} homogeneously distributed prey about which there is
-uncertain knowledge \citep{Viswanathan1999}. In a random walk, movement is a
-stochastic process through a series of steps\added[id=JJ]{. These steps have a
-	length, and a direction} that can either be equal in length or take
-some other functional form. The direction of the random walk can be correlated,
-(known as `persistence'), providing some overall \deleted[id=PD]{location of}
-directional movement \citep{Codling2008} \deleted[id=PD]{or uncorrelated}. \\
-
-A \textit{\replaced[id=JJ]{Lévy flight} {lévy walk}} is a particular form of
-random walk characterised by a heavy-tailed distribution of step-length
-\replaced[id=JJ]{. The Lévy flight}{and} has received a lot of attention in
-ecological theory in recent years as having shown to have very similar
-characteristics as those observed by animals in nature, and being a near
-optimum searching strategy for predators pursuing patchily distributed prey
-\citep{Viswanathan1999, Bartumeus2005, Sims2008}.  \citet{Bertrand2007} showed
-that Peruvian anchovy fishermen have a stochastic search pattern similar to
-that observed with a lévy flight. However, it remains a subject of debate
+modified random walk process. \added[id=PD]{As the simulation progresses the
+	within-trip decision become gradually more influenced by experience
+	gained from past fishing locations (as per the initial trip-level
+	location choice), moving location choice towards areas of higher
+	perceived profit.} A random walk was chosen for the exploratory fishing
+process as it is the simplest assumption commonly used in ecology to describe
+\added[id=PD]{optimal} animal\deleted[id=PD]{movement which}
+search\replaced[id=PD]{ strategy}{ing} for \added[id=PD]{exploiting}
+homogeneously distributed prey about which there is uncertain knowledge
+\citep{Viswanathan1999}. In a random walk, movement is a stochastic process
+through a series of steps\added[id=JJ]{. These steps have a length, and a
+	direction} that can either be equal in length or take some other
+functional form. The direction of the random walk was also correlated (known as
+`persistence') providing some overall \deleted[id=PD]{location of}directional
+movement \citep{Codling2008} \deleted[id=PD]{or uncorrelated}. \\
+
+We use a \textit{\replaced[id=JJ]{Lévy flight} {lévy walk}} which is a
+particular form of random walk characterised by a heavy-tailed distribution of
+step-length\replaced[id=JJ]{. The Lévy flight}{and} has received a lot of
+attention in ecological theory in recent years as having shown to have very
+similar characteristics as those observed by animals in nature, and being a
+near optimum searching strategy for predators pursuing patchily distributed
+prey \citep{Viswanathan1999, Bartumeus2005, Sims2008}.  \citet{Bertrand2007}
+showed that Peruvian anchovy fishermen have a stochastic search pattern similar
+to that observed with a lévy flight. However, it remains a subject of debate
 \added[id=PD]{\citep[e.g. see][]{Edwards2011, Reynolds2015}}, with the
@@
 
-We use a modified random walk where directional change is based on a correlated
-circular distribution where a favourable fishing ground is likely to be
-``fished back over" by the vessel returning in the direction it came from and
-step length (i.e. the distance travelled from the current to the next fishing
-location) is determined by \deleted[id=JJ]{relating} recent fishing success,
-measured as the summed value of fish caught (revenue, $Rev$),
+For our implementation of a random walk directional change is based on a
+negatively correlated circular distribution where a favourable fishing ground
+is likely to be ``fished back over" by the vessel returning in the direction it
+came from.  The step length (i.e. the distance travelled from the current to
+the next fishing location) is determined by \deleted[id=JJ]{relating} recent
+fishing success, measured as the summed value of fish caught (revenue, $Rev$),
 \begin{equation}
@@
 RefRev) * max_{k}$, where $max_{k}$ is the maximum concentration value, $k$,
-and $RefRev$ is parametrised as for $\beta_{3}$ in the step length function.
+and $RefRev$ is parametrised as for $\beta_{3}$ in the step length function. A
+realised example of the step length and turning angle relationships to revenue
+can be seen at Figure \ref{S-fig:15}.
 
@@
 \ref{S-fig:1}, \ref{S-fig:3}, \ref{S-fig:4}, \ref{S-fig:5}, \ref{S-fig:6},
-\ref{S-fig:7}), population demographic and recruitment functions. In addition,
+\ref{S-fig:7}), population demographics and recruitment functions. In addition,
 each of the populations has two defined spawning areas which result in the
@@
 
-The fleets were parametrised to reflect five different characteristics based
-on targeting preference and exploitation dynamics (Table \ref{tab:2}).
-\replaced[id=PD]{Setting a targeting parameter ($Q$) that differed across
-	fleets ensured different spatial dynamics, due to preferential
-	targeting of populations that differ in their spatial
-	distributions}{This ensures that different fleets have different
-	spatial dynamics, preferentially targeted different fish populations}.
-The stochasticity in the random walk process ensures that different vessels
-within a fleet have slightly different spatial distributions based on
-individual experience, while the step function was parametrised dynamically so
-that vessels take smaller steps where the fishing location yields in a top
-quartile of the value available in that year (as defined per fleet in Table
-\ref{tab:2}). \\
-
-Each fleet was parametrised so that, after the first year, fishing locations
-were chosen based on experience built up in the same month from previous years
-and from past trip fishing success. 'Success' in this context was defined as
-the locations where the top 75 \% of expected profit would be found given
-previous trips revenue and cost of movement to the new fishing location. \\
+The fleets were parametrised to reflect five different characteristic fisheries
+with unique exploitation dynamics (Table \ref{tab:2}).  \replaced[id=PD]{By
+	setting different catchability parameters ($Q_{fl, p}$) we create
+	different targeting preferences between the fleets and hence spatial
+	dynamics}{This ensures that different fleets have different spatial
+	dynamics, preferentially targeted different fish populations}.  The
+stochasticity in the random walk process ensures that within a fleet different
+vessels have slightly different spatial distributions based on individual
+experience. The step function was parametrised dynamically within the
+simulations as the maximum revenue obtainable was not known beforehand. This
+was implemented so that vessels take smaller steps where the fishing location
+yields in a top quartile of the value experienced in each year (as defined per
+fleet in Table \ref{tab:2}). \\
+
+With an increasing probability throughout the simulation fishing locations were
+chosen based on experience built up in the same month from previous years and
+from past trip fishing success.  'Success' in this context was defined as the
+locations where the top 75 \% of expected profit would be found given previous
+trips revenue and cost of movement to the new fishing location. This
+probability was based on a logistic sigmoid function with a lower asymptote of
+0 and upper asymptote of 0.95, and a growth rate which ensures the upper
+asymptote (where decisions are mainly based on past knowledge) is reached
+$\sim$ halfway through the simulation).  \\
 
@@
 derived from the commercial catches, fisheries-independent survey or the 'real
-population' - the underlying populations assumed to be known perfectly) used at
-different spatial and temporal scales. \\
+population' - where the underlying populations assumed to be known perfectly)
+used at different spatial and temporal scales. \\
 
@@
 
+\newpage
+\input{F_changes.tex}
+
+%\newpage
+%\input{C_changes.tex}
+
+%%%% figures
 \begin{figure}[!ht]

### 2019-01-28 analysis/Plots_Combined.R

@@ -76,10 +76,10 @@ combined_pop_an <- rbind(results_df_an1, results_df_an2)
 ## Averages years 1 - 4 and 5-10, then the difference per scenario ##
 #####################################################################
 
-avg2_4  <- combined_pop_an %>% filter(year %in% 26:30) %>% 
+avg2_4  <- combined_pop_an %>% filter(year %in% 29:29) %>% 
 	group_by(scenario, pop, metric) %>% summarise(value = mean(data, na.rm = T))
 
-avg8_10 <- combined_pop_an %>% filter(year %in% 46:50) %>% 
+avg8_10 <- combined_pop_an %>% filter(year %in% 50:50) %>% 
 	group_by(scenario, pop, metric) %>% summarise(value = mean(data, na.rm = T))
 
 combined <- merge(avg2_4, avg8_10, by = c("scenario","metric","pop"))
@@ -128,6 +128,30 @@ ggplot(combined_bi, aes(x = F, y = Catch)) +
 ## Print out table of results
 
 write.table(combined[order(combined$diff),], file = "Closure_Analysis_Results.csv", sep =",", row.names = F)
+
+
+## Latex tables
+library(xtable)
+
+Fs <- filter(combined, metric == "F", basis == "high_pop", pop == "spp_3")
+Fs[,c(4:6)] <- round(Fs[,c(4:6)], 2)
+Fs <- Fs[order(Fs$pop, Fs$diff),]
+
+print(xtable(Fs, digits = 2, caption = "Fishing mortality effects of the closure scenarios", label = "tab:6"), caption.placement = "top", file =
+	     file.path("..","write_up", "F_changes.tex"),include.rownames =
+	     FALSE, tabular.environment= "longtable", floating = FALSE)
+
+
+Cs <- filter(combined, metric == "Catch", basis == "high_pop", pop == "spp_3")
+Cs[,c(4:6)] <- round(Cs[,c(4:6)], 2)
+Cs <- Cs[order(Cs$pop, Cs$diff),]
+
+print(xtable(Cs, digits = 2, caption = "Catch effects of the closure scenarios", label = "tab:7"), caption.placement = "top", file =
+	     file.path("..","write_up", "C_changes.tex"),include.rownames =
+	     FALSE, tabular.environment= "longtable", floating = FALSE)
+
+
+
 
 ###########################
 ### 
[…]

### 2019-02-19 write_up/Process_model.tex
Updating supplementary figures

--- 2018-11-26 write_up/mixfishsim_ecolmod.tex
@@
-\documentclass[review]{elsarticle}
-
-\usepackage{xr} %% For cross-referencing supl figures
-\externaldocument[S-]{Supplementary}
-
-\usepackage{lineno,hyperref}
-\usepackage[utf8]{inputenc}
-\usepackage{graphicx}
-\usepackage{amsfonts}
-\usepackage{mathtools}
-\usepackage{tikz}
-\usetikzlibrary{shapes,arrows,chains,calc}
-\usepackage{hhline}
-\usepackage{booktabs}
-\usepackage[textsize=scriptsize]{todonotes}
-%\usepackage[textsize=scriptsize, disable]{todonotes}  %% to turn off notes
-\usepackage{eurosym}
-
-% For track-changes
-\usepackage[draft]{changes}
-%\usepackage[final]{changes} %% to turn off changes
-\definechangesauthor[color = red]{JM}
-\definechangesauthor[color = blue]{PD}
-\definechangesauthor[color = green!40!black]{JJ}
-\definechangesauthor[color = purple]{CM}
-
-% Set up a few colours for tikz figure
-\colorlet{lcfree}{green}
-\colorlet{lcnorm}{blue}
-\colorlet{lccong}{red}
-
-\modulolinenumbers[1]
-
-\journal{Ecological Modelling}
-
-%% Harvard
-\bibliographystyle{model2-names.bst}\biboptions{authoryear}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-
-\begin{frontmatter}
-\title{\emph{MixFishSim}: highly resolved spatiotemporal simulations for
-	exploring mixed fishery dynamics}
-
-%% Group authors per affiliation:
-\author[1,2]{Paul J. Dolder\corref{c}}
-\cortext[c]{Corresponding author}
-\ead{paul.dolder@gmit.ie}
-
-\author[1]{Cóilín Minto}
-\author[3]{Jean-Marc Guarini}
-\author[4]{Jan Jaap Poos}
-
-\address[1]{Galway-Mayo Institute of Technology (GMIT), Dublin Road, Galway,
-	Ireland} 
-\address[2]{Centre for Environment, Fisheries and Aquaculture Science (Cefas),
-	Pakefield Road, Lowestoft, UK}
-\address[3]{\replaced[id=JM]{Sorbonne Université, Faculty of
-		Sciences}{Université Pierre et Marie Curie}, 4 Place Jussieu,
-	75005 Paris, France}
-\address[4]{Wageningen Marine Research, Haringkade 1 1976 CP IJmuiden,
-	Netherlands}
-
-\begin{abstract}
-
-\replaced[id = JJ]{Most fisheries}{Fishing} exploit\deleted[id=JJ]{s} a variety 
-of spatially and temporally heterogeneous fish populations, using
-species-unselective gear that can result in unintended, unwanted catch of low
-quota or protected species. Reducing these unwanted catches is crucial for
-biological and economic sustainability of `mixed fisheries' and implementation
-of an ecosystem approach to fishing. \\
-
-\replaced[id = PD]{If fisheries are to avoid unwanted catch}{To implement
-	effective spatial measures to reduce discards} a good understanding of
-spatiotemporal fishery dynamics is required. However, traditional scientific
-advice is limited by a lack of highly resolved knowledge of population
-distributions, movement and how fishers interact with different fish
-populations. This reflects the fact that data on fish location at high temporal
-and spatial resolutions is expensive and difficult to collect. Proxies inferred
-from either scientific surveys or commercial catch data are often used to model
-distributions, often with sparse data at limited spatial and temporal
-resolution. \\
-
-To understand how data resolution impacts inference on mixed fisheries
-interactions, we develop a highly resolved spatiotemporal simulation model
-incorporating: i) delay-difference population dynamics, ii) population movement
-using Gaussian Random Fields to simulate patchy, heterogeneously distributed
-populations, and iii) fishery dynamics for multiple fleet characteristics based
-on species targeting via a mix of correlated random walk movement (for
-exploration) and learned behaviour (for exploitation) phases of the fisheries.
-\\
-
-We simulate 50 years of fishing and use the results from the fisheries catch to
-draw inference on the underlying population structures. We compare this
-inference to i) a simulated fixed-site sampling design commonly used for
-fisheries monitoring purposes, and ii) the true underlying population
-structures input to the simulation, to establish the potential and limitations
-of fishery-dependent data - an inherently biased sampling method due to
-fisher's targeting- to provide a robust picture of spatiotemporal
-distributions. Finally, we simulate an area closure based on areas defined from
-the known ("real-population") distribution, commercial catch data and survey
-data at different temporal and spatial resolutions and assess their
-effectiveness on reducing catches of a fish population. \\
-
-We conclude from our simulations that commercial data, while not unbiased,
-provides a useful tool for managing catches in mixed fisheries if applied at
-the correct spatiotemporal scale. \\
-
-[333 words]
-
-\end{abstract}
-
-\begin{keyword}
-Some\sep keywords \sep here. Max 6 
-\MSC[2010] 00-01\sep  99-00
-\end{keyword}
-
-\end{frontmatter}
-
-\linenumbers
-
-\section{Introduction}
-
-Fishers exploit a variety of fish populations that are heterogeneously
-distributed in space and time with varying knowledge of species distributions
-using species-unselective fishing gear. \added[id=PD]{In doing so} fisheries
-\deleted[id=PD]{that} catch an assemblage of species
-\added[id=PD]{and}\deleted{, known as mixed fisheries} \replaced[id=JJ]{may}{,
-	when managed by single-species quotas can end up}
-discard\deleted[id=JJ]{ing} overquota catch \added[id=JJ]{when managed by
-	single species quotas,} leading to overexploitation of fish populations
-\added[id=JJ]{\citep{Ulrich2011a, Batsleer2015}}.  \added[id=JJ]{This
-	discarding of fish in excess of quota hampers the ability to limit
-	fishing mortality to within sustainable limits \citep{Alverson1994,
-		Crowder1998, Rijnsdorp2007}} \deleted[id=PD]{; reducing
-	discarding is crucial}and ensure biological and economic sustainability
-of fisheries\deleted[id=JJ]{ and implementation of an ecosystem approach to
-	fisheries}. As such, there is increasing interest
-in technical solutions such as gear and spatial closures as ways of
-\replaced[id=PD]{reducing unwanted catch}{avoiding discard\added[id=JJ]{ing of
-		fish}}\citep{Kennelly2002, Catchpole2008, Bellido2011}.  \\
-
-\replaced[id=PD]{Changes to spatial fishing patterns have}{Use of spatial
-	management as a tools} been proposed as a method to reduce discards
-\added[id=PD]{\citep{Holmes2011, Little2014, Dunn2014a}}. However,
-\deleted[id=PD]{its} implementation is hampered by lack of knowledge of fish
-and fishery spatiotemporal dynamics and understanding of the scale at which
-processes are important for management. Understanding the correct scale for
-spatial management is crucial in order to implement measures at a resolution
-that ensures effective management \citep{Dunn2016} while minimising economic
-impact.  For example, a scale that promotes species avoidance for vulnerable or
-low quota species while allowing continuance of sustainable fisheries for
-available quota species.\\
-
-\replaced[id=PD]{Identifying}{Ensuring measures are implemented at} an
-appropriate scale has been a challenge in the past that has led to ineffectual
-measures with unintended consequences such as limited impact towards the
-management objective or increased benthic impact on previously unexploited
-areas (e.g. the cod closure in the North Sea
-\citep{Rijnsdorp2001,Dinmore2003}). \replaced[id=PD]{M}{Since then m}ore
-refined spatial information has \added[id=PD]{since} become available through
-the combination of logbook and Vessel Monitoring System (VMS) data
-\citep{Lee2010, Bastardie2010, Gerritsen2012, Mateo2016} and more real-time
-spatial management has been possible \citep[e.g.][]{Holmes2011}.  Such
-information is, however, patchy and derived from an inherently biased sampling
-programme (i.e. targeted fishing). \deleted[id=PD]{ Further, fishers generally only recorded
-landings (not catch) on a daily basis\todo{\added[id=JJ]{Its not clear what the
-		problem is: landings collected on daily basis or landings
-		recorded rather than catch}}.  This leads to questions about
-the validity of inference that can be drawn from landings data assigned to VMS
-activity pings.}\todo{\added[id=JJ]{This comes as a surprise: I thought this was
-		going to be about discards}\added[id=PD]{Agree, have removed
-		this to avoid confusion}}\\
-
-In order to understand \replaced[id=PD]{the consequences of using}{challenges
-	that face} VMS-linked landings to draw inference on the underlying
-population structure we develop a simulation model where population dynamics
-are highly-resolved in space and time\replaced[id=PD]{. Being}{ and are}
-known \added[id=PD]{directly} rather than inferred from sampling or commercial
-catch\added[id=PD]{, we can use the population model to evaluate how inference from
-	fisheries-dependent and fisheries independent sampling relates to the
-	real population structure}. \replaced[id=PD]{In our model system
-	p}{P}opulation movement is driven by random (diffusive) and directed
-(advective) processes and we incorporate characterisation of a number of
-different fishing \added[id=PD]{fleet dynamics} exploiting four fish populations
-with different spatial and population demographics.\\
-
-Using our model we simulate \replaced[id=PD]{50}{40} years of exploitation of
-the fish populations. \replaced[id=PD]{We}{ and} use the
-results\deleted[id=PD]{ from the fishing model:}
-
-\begin{enumerate}
-	\item to understand how sampling-derived data reflects the underlying
-		population structures. We compare at different spatial and
-		temporal aggregations of data the real population to: 
-		\begin{enumerate}
-			\item the inferred population from a stratified fixed-site sampling survey design
-				commonly used for fisheries monitoring purposes, otherwise know as a
-				fisheries-independent survey,
-			\item the inferred population from our fishery-dependent model which includes
-				fishery-induced sampling dynamics.\\
-		\end{enumerate}
-	\item to understand the impact of data aggregation and source on
-		spatial fisheries management measures we simulate a fishery closure to
-		protect a species based on different spatial and temporal data
-		aggregations:
-		\begin{enumerate}
-			\item as if the real spatial population structure were
-				known,
-			\item the fishery-independent inferred population
-				structure
-			\item the fishery-dependent inferred population
-				structure
-		\end{enumerate}
-		We evaluate the theoretical "benefit" to the population of the
-		closure(s), the effect on the other three populations and
-		fishery catch.\todo{\added[id=JJ]{If the paper has two goals
-				this should be clear from the start, but may be
-				better over 2 MSs}\added[id=PD]{I would like to
-				keep both parts, but have made clearer in how
-				its set out. The closure scenarios form
-				validation of the data aggregation, rather than
-				effectiveness of the closures themselves - so
-				its a continuation of the same question in my
-				eyes}}\deleted[id=PD]{.  Further, we extend our
-			analysis to a range of spatial and temporal scales to
-			assess the impact of these processes on the success of
-			the management measure.}\\
-\end{enumerate}
-
-\section{Materials and Methods}
-
-\replaced[id=PD]{A}{We developed and implemented a simulation model with a}
-modular event-based \replaced{simulation model was developed with}{approach,
-	where} \added[id=PD]{sub-}modules \deleted[id=PD]{are} implemented on
-independent time-scales appropriate to capture the characteristic of the
-\replaced[id=PD]{different processes}{process modelled} (Figure 1).
-\added[id=PD]{The following sub-modules were included to capture the full
-	system: 1) Population dynamics, 2) Recruitment dynamics, 3) Population
-	movement, 4) fishery dynamics.}\\
-
-\deleted[id=PD]{The fishing model operated on a tow-by-tow basis, while}
-\replaced[id=PD]{P}{p}opulation dynamics (fishing and natural mortality,
-growth) operate on a daily time-step\replaced[id=PD]{, while p}{. P}opulation
-movement occurs on a weekly time-step\replaced[id=PD]{. R}{, while r}ecruitment
-\replaced[id=PD]{takes place}{occurs} periodcally each year for a set time
-\replaced[id=PD]{duration}{period (e.g. 3 weeks)} specified for each
-population\deleted[id=PD]{.}\added[id=PD]{, while the fishing module operates
-	on a tow-by-tow basis (i.e. multiple events a day)}.  The simulation
-framework is implemented in the statistical software package R
-\citep{RCoreTeam2017} \replaced[id=PD]{and}{;} available as an R package from
-the authors github site (\url{www.github.com/pdolder/MixFishSim}).\\
-
-\deleted[id=PD]{Here we describe each of the model components; 1) Population
-	dynamics, 2) Recruitment dynamics, 3) Population movement dynamics, 4)
-	fishery dynamics.}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 	(exploitation) fishing strategy.}
-\label{fig:overview}
+%%\label{fig:overview}
 \end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Population dynamics}
-
-The basic population level processes are simulated using a modified two-stage
-Deriso-Schnute delay difference model \citep{Deriso1980, Schnute1985,
-	Dichmont2003} occurring at a daily time-step. \added[id=PD]{A daily
-	time-step was chosen as to discretise continuous population processes
-	on a biologically relevant and computationally tractable timescale.}
-\replaced[id=PD]{Under the population dynamics module}{Here,} population
-biomass growth and depletion for pre-recruits and \deleted[id=PD]{fish}
-recruited \added[id=PD]{fish} \deleted[id=PD]{to the fishery} are modelled
-separately as a function of previous recruited biomass, intrinsic population
-growth and recruitment. Biomass for each cell is incremented each day as
-follows (the full parameter list is detailed in Table \ref{tab: pop_variable}):
-\begin{equation*}
-	\begin{split}
-	B_{c,d+1} = &\\
-	& (1 + \rho) B_{c,d} \cdot e^{-Z_{c,d}} - \rho \cdot e^{-Z_{c,d}} \hspace{2.9cm}
-	\times \\  
-	& (B_{c,d-1} \cdot e^{-Z_{c,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot
-	R_{\tilde{y}(c,y,d-1)})
-	\hspace{0.4cm} + \\
-	& Wt_{R} \cdot \alpha_{d} \cdot R_{\tilde{y}(c,y,d)} 
-	\end{split}
-\end{equation*}
-where $\rho$ is Brody's coefficient, shown to be approximately equal to
-$e^{-K}$ when $K$ is the growth rate from a von Bertalanffy logistic growth
-model \citep{Schnute1985}. $Wt_{R-1}$ is the weight of fish prior to
-recruitment, while $Wt_{R}$ is the recruited weight. $\alpha_{d}$ represents
-the proportion of fish recruited during that day for the year, while
-$R_{c,\tilde{y}}$ is the annual recruits in cell $c$ for year $y$. \\
-
-Mortality $Z_{c,d}$ can be decomposed to natural mortality, $M_{c,d}$, and
-fishing mortality, $F_{c,d}$, where both $M_{c,d}$ and $F_{c,d}$ are
-instantaneous rates with $M_{c,d}$ fixed and $F_{c,d}$ calculated by solving
-the Baranov catch equation \citep{Hilborn1992b} for $F_{c,d}$:
-\begin{equation*}
-C_{c,d} = \frac{F_{c,d}}{F_{c,d} + M_{c,d}} * (1 - e^{-(F_{c,d} + M_{c,d})}) *
-B_{c,d}
-\end{equation*}
-where $C_{c,d}$ is the summed catch from the fishing model across all fleets
-and vessels in cell $c$ for the population during the day $d$, and $B_{c,d}$
-the daily biomass for the population in the cell. \todo{\added[id=CM]{[link $F$ to
-	effort and catchability - as I think we have F as an emergent property
-	of the fleets rather than something we solve for (I could be wrong
-	though!) - catch for a vessel is a product of catchability and biomass,
-	i.e. C = qB, but this catch is summed to solve for F. So its both
-	really]}}\\
-
-\subsection{Recruitment dynamics}
-
-Recruitment is modelled through a function relating the mature biomass to
-recruits at time of recruitment. In \emph{MixFishSim}, it can be modelled
-either either as a stochastic Beverton-Holt stock-recruit form
-\citep{Beverton1957}: 
-\begin{equation*}
-	\begin{split}
-	\bar{R}_{c,d} = & \frac{(\alpha * B_{c,d})}{(\beta + B_{c,d})} \\
-	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\log(\sigma^2))]
-	\end{split}
-\end{equation*}
-Where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
-biomass (SSB) required to produce half the maximum, $B$ current SSB and
-$\sigma^2$ the variability in the recruitment due to stochastic
-processes, or a stochastic Ricker form \citep{Ricker1954}:
-\begin{equation*}
-	\begin{split}
-	\bar{R}_{c,d} = & B_{c,d} * e^{(\alpha - \beta * B_{c,d})} \\	
-   	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\log(\sigma^2))]
-	\end{split}
-\end{equation*}
-where $\alpha$ is the maximum productivity per spawner and $\beta$ the density
-dependent reduction in productivity as the SSB increases.
-
-\subsection{Population movement dynamics}
-
-To simulate \deleted[id=JJ]{how} fish population\deleted[id=JJ]{s might be}
-distribut\replaced[id=JJ]{ion}{ed} in space and time\deleted[id=JJ]{, we
-	employed} a Gaussian spatial process \added[id=JJ]{was employed} to
-model habitat suitability for each of the populations\replaced[id=JJ]{. An}{,
-	with an} advection-diffusion process \deleted[id=JJ]{to}
-control\added[id=JJ]{led} \deleted[id=JJ]{how the} population\deleted[id=JJ]{s}
-move\replaced[id=JJ]{ment}{d} over time with a moving temperature covariate to
-capture temporal dependencies\todo{\added[id=JJ]{What have a temperature
-		covariate? Could just use time}\added[id=PD]{Was intended as
-		some biological meaning - species thermal tolerances load onto
-		the temperature effect - so could be different per species}}.
-\deleted[id=JJ]{This was intended to balance realism in population movement,
-	capturing the main directed and random processes, and practicality of
-	modelling the population rather than individual fish.} \\
-
-For \deleted[id=PD]{the} habitat we define\added[id=PD]{d} a Gaussian random
-field process\todo{\added[id=JJ]{Not clear how habitat/GRF affect local
-		abundances, only have $B_{y,d}$}\added[id=PD]{Have included
-		cell reference, $c$ to make spatial link explicit}}, $\{S(c) :
-c \in \mathbb{R}^2\}$, \deleted[id=PD]{that is a stochastic process} where
-\added[id=PD]{for} any set of cells $c_{1}, \dots, c_{n}$ \deleted[id=PD]{where
-	for each $c_{i} \in \mathbb{R}^2$}, the joint distribution of $S =
-\{S(c1),\dots S(c_{n})\}$ is multivariate Gaussian. The distribution is
-specified by its \textit{mean function}, $\mu(c) = E[S(c)]$ and its
-\textit{covariance function}\todo{\added[id=JM]{Introduce the gamma function,
-		and why this covariance structure? Why correlate values in the
-		random field?}\added[id=PD]{to allow populations to have
-		different aggregation densities: have tried to clarify}},
-$\gamma(c,c') = Cov\{S(c),S(c')\}$ \citep{Diggle2007}.\\
-
-The covariance structure affects the smoothness of the surfaces which the
-process generates\replaced[id=PD]{;}{, and} we used the \textit{Matérn}
-\deleted[id=PD]{family of} covariance structure\deleted[id=PD]{s},
-\replaced[id=PD]{as}{one where} the correlation strength weakens the further
-the distance apart \deleted[id=PD]{(i.e. the correlation between $S(x)$ and
-	$S(x')$ decreases as the distance $u = ||x - x'||$ increases)}.
-\added[id=PD]{The Matérn covariance structure models the spatial
-	autocorrelation, where animal densities are observed to be more similar
-	in nearby locations \citep{Tobler1970,
-		F.Dormann2007}}\replaced[id=PD]{. It is}{The \textit{Matérn}
-	correlation} is a two-parameter family where: 
-\begin{center}
-	$\rho(u) = \{2^{\kappa -
-		1}\Gamma{\kappa}\}^{-1}(u/\phi)^{\kappa}K_{\kappa}(u/\phi)$
-\end{center}
-$K_{\kappa}(.)$ is a modified Bessel function of order $\kappa$, $\phi >
-0$ is a scale parameter with the dimensions of distance, and $\kappa > 0$,
-called the order, is a shape parameter which determines the smoothness of the
-underlying process. \\
-
-\replaced[id=PD]{T}{In the simulation model, t}he habitat for each of the
-populations \replaced[id=PD]{was}{is} generated \replaced[id=PD]{with}{through}
-the \textit{RFSimulate} function of the \textit{RandomFields} R package
-\citep{Schlater2015}, implementing different parameter settings to affect the
-patchiness of the populations. Each population \replaced[id=PD]{was}{is}
-initialised at a single location, and subsequently move\replaced[id=PD]{ed}{s}
-according to a probabilistic distrib\added[id=PD]{u}tion based on habitat
-suitability, temperature and distance from current cell\replaced[id=PD]{:}{.} 
-\begin{equation}
-	Pr(J | I) = \frac{e^{-\lambda * d_{IJ}} \cdot
-		(Hab_{J,p}^2 \cdot Tol_{J,p,wk})}{\sum\limits_{c=1}^{C}e^{-\lambda * d} \cdot
-		(Hab_{c,p}^2 \cdot Tol_{c,p,wk})}
-\end{equation}
-Where $d_{IJ}$ is the euclidean distance between cell $I$ and cell $J$,
-$\lambda$ is a given rate of decay, $Hab_{J,p}^2$ is the squared index of
-habitat suitability for cell $J$ and population $p$, with $Tol_{J,p,wk}$ the
-temperature tolerance for cell $J$ by population $p$ in week $wk$.\\
-
-During specified weeks of the year, the habitat quality
-\replaced[id=PD]{was}{is} modified for \added[id=PD]{user-defined} spawning
-habitat\deleted[id=PD]{s}, \replaced[id=PD]{resulting in}{meaning} each
-population \replaced[id=PD]{having}{has} a concentrated area where spawning takes
-place and the population move\replaced[id=PD]{d}{s} towards
-\replaced[id=PD]{these cells}{this} in the weeks prior to
-spawning.\todo{\added[id=JM]{What does it mean concisely? Areas are assigned?}
-\added[id=PD]{Yes, the areas are pre-defined - I have amended to reflect and
-	tried to clarify}} \\
-
-The temperature field \replaced[id=PD]{was}{is} simulated to be on a gradient
-from a South-Westerly to North-Easterly direction, with temperature in each
-cell changing gradually on a week-by-week basis so that initially high
-temperature areas cycle\added[id=PD]{d} to lower temperatures and low
-temperature areas vice versa. Each population $p$ \replaced[id=PD]{wa}{i}s
-assigned a thermal tolerance with mean, $\mu\added[id=PD]{_{p}}$ and variance,
-$\sigma^2\added[id=PD]{_{p}}$ so that each cell and population temperature
-suitability is defined that:
-\begin{equation}
-	Tol_{c, p\added[id=PD]{, wk}} = \frac{1}{ \sqrt (2\pi \cdot \sigma^2_{p})} \cdot \exp(-
-		\frac{(T_{c\added[id=PD]{, wk}} - \mu_{p})^2}{2 \cdot \sigma^2_{p}} )	
-\end{equation}
-Where $Tol_{c, p, \added[id=PD]{wk}}$ is the tolerance of population $p$ for
-cell $c$ \added[id=PD]{in week $wk$}, $T_{c, \added[id=PD]{wk}}$ is the
-temperature in the cell \added[id=PD]{given the week} and
-$\mu\added[id=PD]{_{p}}$ and $\sigma^2\added[id=PD]{_{p}}$ the mean and
-standard deviation of the population temperature tolerance. \\
-
-\added[id=PD]{The final process resulted in independent populations structure
-	and movement patterns, with population movement occuring on a weekly
-	basis. This process approximated the demographic shifts in fish
-	populations throughout a year with seasonal spawning patterns.}
-
-\subsection{Fleet dynamics}
-
-The fleet dynamics can be broadly categorised into three components; fleet
-targeting - which determine\replaced[id=PD]{d}{s} the fleet catch efficiency
-and preference towards a particular species; trip-level decisions, which
-determine\added[id=PD]{d} the initial location to be fished at the beginning of
-a trip; and within-trip decisions, determining movement from one fishing spot
-to another within a trip.
-
-\subsubsection{Fleet targeting}
-
-Each fleet of \textit{n} vessels \replaced[id=PD]{was}{is} characterised by
-both a general efficiency, \textit{Q}, and a population specific efficiency,
-${Q_{p}}$.  Thus, the product of these parameters affect\replaced[id=PD]{s}{ed}
-the overall catch rates for the fleet and the preferential targeting of one
-population over another. This, in combination with the parameter choice for the
-step-function \added[id=PD]{defined below} (as well as some randomness from the
-exploratory fishing process) determine\replaced[id=PD]{d}{s} the preference of
-fishing locations for the fleet.  All species prices
-\replaced[id=PD]{were}{are} kept the same across fleets \replaced[id=PD]{and
-	seasons}{, though can be made to vary seasonally}.
-
-\subsubsection{Trip-level decisions}
-
-NOTE: THIS IS EXPLORE-EXPLOIT STRATEGY VIZ. BAILEY ET AL POSEIDON MODEL.
-
-Several studies \citep[e.g.][]{Hutton2004, Tidd2012, Girardin2015} have
-confirmed past activity and past catch rates are strong predictors of fishing
-location choice. For this reason, the fleet dynamics sub-model
-include\replaced[id=PD]{d}{s} a learning component, where a vessel's initial
-fishing location in a trip \replaced[id=PD]{wa}{i}s based on selecting from
-previously successful fishing locations. This \replaced[id=PD]{wa}{i}s achieved
-by \added[id=PD]{calculating an expected profit based on the profit from
-	locations previously fished} in the preceding trip as well as the same
-month periods in preceding years, and choosing randomly from the top 75 \% of
-fishing events \replaced[id=PD]{as defined by the expected profit}{in value}.
-\added[id=PD]{Expected profit was estimated from the revenue achieved in
-	previous fishing events at a location minus the fuel cost of travelling
-	from the currently location to the new location.} Simulation testing
-indicated that this learning increased the mean value of catches for the
-vessels, over just relying on the correlated random walk
-\todo{\added[id=JJ]{Correlated random walk of what}} function \added[id=PD]{as
-	described for the 'within trip' decisions below} (MIGHT NEED TO INCLUDE
-IN SUPPLEMENTARY).
-
-\subsubsection{Within-trip decisions}
-
-Fishing locations within a trip are \added[id=PD]{initially} determined by a
-modified random walk process. \added[id=PD]{As the simulation progresses, the
-	within-trip decision become gradually more influenced by past locations
-	fished, based on the same process as the initial trip-level location,
-	influenced by expected profit at a fishing location.} A random walk was
-chosen for the exploratory fishing process as it is the simplest assumption
-commonly used in ecology to describe \added[id=PD]{optimal} animal
-\deleted[id=PD]{movement which} search\replaced[id=PD]{ strategy}{ing} for
-\added[id=PD]{exploiting} homogeneously distributed prey about which there is
-uncertain knowledge \citep{Viswanathan1999}. In a random walk, movement is a
-stochastic process through a series of steps\added[id=JJ]{. These steps have a
-	length, and a direction} that can either be equal in length or take
-some other functional form. The direction of the random walk can be correlated,
-(known as `persistence'), providing some overall \deleted[id=PD]{location of}
-directional movement \citep{Codling2008} \deleted[id=PD]{or uncorrelated}. \\
-
-A \textit{\replaced[id=JJ]{Lévy flight} {lévy walk}} is a particular form of
-random walk characterised by a heavy-tailed distribution of step-length
-\replaced[id=JJ]{. The Lévy flight}{and} has received a lot of attention in
-ecological theory in recent years as having shown to have very similar
-characteristics as those observed by animals in nature, and being a near
-optimum searching strategy for predators pursuing patchily distributed prey
-\citep{Viswanathan1999, Bartumeus2005, Sims2008}.  \citet{Bertrand2007} showed
-that Peruvian anchovy fishermen have a stochastic search pattern similar to
-that observed with a lévy flight. However, it remains a subject of debate
-\added[id=PD]{\citep[e.g. see][]{Edwards2011, Reynolds2015}}, with the
-contention that search patterns may be more simply characterised as random
-walks \citep{Sakiyama2013} with specific patterns related to the
-characteristics of the prey field \citep{Sims2012}. \\
-
-We use a modified random walk where directional change is based on a correlated
-circular distribution where a favourable fishing ground is likely to be
-``fished back over" by the vessel returning in the direction it came from and
-step length (i.e. the distance travelled from the current to the next fishing
-location) is determined by \deleted[id=JJ]{relating} recent fishing success,
-measured as the summed value of fish caught (revenue, $Rev$),
-\begin{equation}
-Rev = \sum_{p=1}^{P} \replaced[id=PD]{L}{C}_{p} \cdot Pr_{p} 
-\end{equation}
-where $\replaced[id=PD]{L}{C}_{p}$ is \replaced[id=PD]{landings}{catch} of a
-population $p$, and $Pr_{p}$ price of a population. Here, when fishing is
-successful vessels remain in a similar location and continue to exploit the
-local fishing grounds. When unsuccessful, they move some distance away from
-the current fishing location.  The movement distance retains some degree of
-stochasticity, which can be controlled separately, but is determined by the
-relationship: 
-\begin{equation*}
-	StepL = e^{log(\beta_{1}) + log(\beta_{2}) -
-		(log(\frac{\beta_{1}}{\beta_{3}}))} * Rev
-\end{equation*}\todo{\added[id=JJ]{So
-			step length increases with increasingly gross
-			revenue?}\added[id=PD]{No, the opposite}}
-Where $\beta_{1}$, $\beta_{2}$ and $\beta_{3}$ are parameters determining the
-shape of the step function in its relation to revenue, so that, a step from
-(x1,y1) to (x2, y2) is defined by:
-\begin{equation*}
-	\begin{split}
- (x2, y2) =  & x1 + StepL \cdot \cos (\frac{\pi \cdot Br}{180}), \\
-             & y1 + StepL \cdot \sin (\frac{\pi \cdot Br}{180}) \\	
- with  \hspace{0.5cm}     & Br_{t-1} < 180, Br_{t} = 180 + \sim vm[(0,360), k] \\
- 			  & Br_{t-1} > 180, Br_{t} = 180 - \sim vm[(0,360), k] \\
-	\end{split}
-\end{equation*}
-where $k$ the concentration parameter from the von \replaced[id=JJ]{M}{m}ises
-distribution which we correlate with the revenue so that $k = (Rev + 1 /
-RefRev) * max_{k}$, where $max_{k}$ is the maximum concentration value, $k$,
-and $RefRev$ is parametrised as for $\beta_{3}$ in the step length function.
-
-\subsubsection{Local population depletion}
-
-Where several fishing vessels are exploiting the same fish population
-competition is known to play an important role in local distribution of fishing
-effort \citep{Gillis1998}. If several vessels are fishing on the same patch of
-fish, local depletion and interference \added[id=JJ]{competition} will affect
-fishing location choice of the fleet as a whole \citep{Rijnsdorp2000,
-	Poos2007a}. In order to account for this behaviour, the fishing
-sub-model operates spatially on a daily time-step so that for future days the
-biomass available to the fishery is reduced in the areas fished. The cumulative
-effect is to make heavily fished areas less attractive as future fishing
-opportunities.
-
-\subsection{Fisheries independent survey}
-
-A fisheries-independent survey is simulated where fishing on a regular grid
-begins each year at the same time for a given number of stations (a fixed
-station survey design). Catches of the populations \replaced[id=JJ]{at each
-station}{present} are recorded but not removed from the population. This
-provides a fishery independent snapshot of the populations at a regular spatial
-\replaced[id=JJ]{intervals}{distribution} each year, similar to scientific
-surveys undertaken by fisheries research agencies.
-
-\section{Calculation}
-
-\subsection{Population parametrisation}
-
-We parametrised the simulation model for four populations with differing
-habitat preference\replaced{,}{ and} temperature tolerances (Figures
-\ref{S-fig:1}, \ref{S-fig:3}, \ref{S-fig:4}, \ref{S-fig:5}, \ref{S-fig:6},
-\ref{S-fig:7}), population demographic and recruitment functions. In addition,
-each of the populations has two defined spawning areas which result in the
-populations moving towards these areas in given weeks (Figure \ref{S-fig:2})
-and population-specific movement rates (Table \ref{tab:1}). The realised
-movement of the populations for a number of weeks is shown in Figure
-\ref{S-fig:9} while the realised daily fishing mortality are shown in Figure
-\ref{S-fig:10}.
-
-\subsection{Fleet parametrisation}
-
-The fleets were parametrised to reflect five different characteristics based
-on targeting preference and exploitation dynamics (Table \ref{tab:2}).
-\replaced[id=PD]{Setting a targeting parameter ($Q$) that differed across
-	fleets ensured different spatial dynamics, due to preferential
-	targeting of populations that differ in their spatial
-	distributions}{This ensures that different fleets have different
-	spatial dynamics, preferentially targeted different fish populations}.
-The stochasticity in the random walk process ensures that different vessels
-within a fleet have slightly different spatial distributions based on
-individual experience, while the step function was parametrised dynamically so
-that vessels take smaller steps where the fishing location yields in a top
-quartile of the value available in that year (as defined per fleet in Table
-\ref{tab:2}). \\
-
-Each fleet was parametrised so that, after the first year, fishing locations
-were chosen based on experience built up in the same month from previous years
-and from past trip fishing success. 'Success' in this context was defined as
-the locations where the top 75 \% of expected profit would be found given
-previous trips revenue and cost of movement to the new fishing location. \\
-
-An example of the realised fleet movements for a single vessel during a single
-trip are given in Figure \ref{S-fig:11}, while Figure \ref{S-fig:12} shows
-multiple trips for a single vessel, \added[id=PD]{Figure} \ref{S-fig:13} the
-vessel movements for some trips overlaid on the value field,
-\added[id=PD]{Figure} \ref{S-fig:14} shows fishing locations for an entire
-fleet of 20 vessels for a single trip, \replaced[id=PD]{and Figure}{while}
-\ref{S-fig:15} shows an example of the step function realisation and turning
-angles from the correlated random walk.\todo{\added[id=JJ]{Move some of the
-	supplementary figures to the manuscript}}
-
-\subsection{Survey settings}
-
-The survey simulation was set up with follow a fixed gridded station design
-with 100 stations fished each year, starting on day 92 \added[id=PD]{and ending
-	on day 112 (5 stations per day)} with same catchability parameters for
-all populations ($Q_{p} = 1$).
-
-\subsection{Simulation settings}
-
-To illustrate the capabilities on \emph{MixFishSim}, we investigate the
-influence of the temporal and spatial resolution of different data sources on
-the reduction in catches of a population given spatial closures. To do so, we
-set up a simulation to run for 50 years based on a 100 X 100 square grid, with
-five fleets of 20 vessels each and four fish populations. Fishing takes place
-four times a day per vessel and five days a week, while population movement is
-every week.\todo{\added[id=JJ]{move to start of methods section}\added[id=PD]{I
-		think ecological modelling wants the 'calculations' section
-		here..will check}} \\
-
-We allow the simulation to run unrestricted for 30 years\todo{\added[id=JJ]{Is
-		there equilibrium after 5 years or still some trend in
-		B}\added[id=PD]{Not at equilibrium yet...I need to rerun until
-		steady state, looks 20 years. Will update}}, and subsequently
-close areas for the last 20 years of the simulation based on data (either
-derived from the commercial catches, fisheries-independent survey or the 'real
-population' - the underlying populations assumed to be known perfectly) used at
-different spatial and temporal scales. \\
-
-The following steps are undertaken to determine closures:
-\todo{\added[id=JJ]{Procedure unclear. Refer to symbols in methods section or
-		switch order starting with description of data type
-		etc..}\added[id=PD]{Yes, will redo}}
-\begin{enumerate}
-	\item Extract data source
-	\item Aggregate according to resolution
-	\item Interpolate across entire area at desired resolution
-	\item Close area covering top 5 \% of catch 
-\end{enumerate}
-In total 56 closure scenarios were run which represent combinations of
-
-\begin{itemize}
-	\item \textbf{data types:} commercial logbook data, survey data and
-		'real population',
-	\item \textbf{temporal resolutions:} weekly, monthly and yearly
-		closures,
-	\item \textbf{spatial resolutions:} 1 x 1 grid, 5 x 5 grid, 10 x 10
-		grid and 20 x 20 grid,
-	\item \textbf{closure basis:} high catch rates of protected species, or
-		high ratio of protected species v secondary species.
-\end{itemize}
-
-Survey closures were on an annual basis only, as this was the most temporally
-resolved survey data available.
-
-\section{Results}
-
-The consequences of different spatial aggregations of the data are shown in
-Figure \ref{fig:1}, which represents the aggregation of catch from each of the
-data sources over a year at different spatial resolutions. \\
-
-The finer spatial grid for the the real population (top left) and commercial
-data (top middle) show similar patterns, though there are unsampled gaps in the
-commercial data from a lack of fishing activity (particularly in the lower left
-part of the sampling domain). The survey data at this spatial resolution shows
-very sparse and uninformative information about the spatial distributions of
-the populations. The slightly aggregated data on a 5 x 5 grid shows similar
-patterns, and while losing some of the spatial detail there remains good
-consistency between the 'real population' and the commercial data. Survey data
-starts to pick out some of the similar patterns as the other data sources, but
-lacks coverage. The spatial catch information on a 10 x 10 and 20 x 20 grid
-loses a significant amount of information about the spatial resolutions for all
-data sources, and some differences between the commercial and 'real population'
-data emerge. \\
-
-Figure \ref{fig:2} shows the consequences of different temporal aggregations of
-the data, with 156 weekly (top), 36 monthly (middle) and 3 yearly (bottom)
-catch compositions across a 20 x 20 area. \\
-
-As can be seen from the 'real population', the monthly aggregation captures the
-major patterns seen in the weekly data, albeit missing more subtle differences.
-The yearly data results in a constant catch pattern due to the aggregation
-process (sometimes known as an aggregation bias). The commercial data on a
-weekly basis shows some of the same patterns as the 'real population', though
-the first species (in red) is less well represented and some weeks are missing
-catches from the area. The monthly data. The monthly data shows some
-consistency between the 'real population' and commercial data for species 2 -
-4, though species 1 remains underrepresented. On an annual basis, interestingly
-the commercial data underrepresents the first species (in red) while the survey
-overrepresents species 1. This is likely due to the biases in commercial
-sampling, with the fisheries not targeting the areas where species 1 are
-present, and the biases in the survey sampling from overrepresentation of the
-spatial distribution. \\
-
-We implemented a spatial closure using the different data sources and spatial
-and temporal aggregations as outlined in the protocol in Section 3.4. We used
-this to assess the efficacy of a closure in reducing fishing mortality on
-species 1, given availability of data and its use at different resolutions in
-order to evaluate the trade-offs in data sources. Figure \ref{fig:3} shows the
-trend in fishing mortality for each species simulated (columns) given the data
-sources (rows), temporal aggregations (colour lines) and spatial aggregations
-(linestyles), while Figure \ref{fig:4} shows the change in fishing mortality
-from before the closure (average F years 2 - 4) to after the closure (average F
-years 8 - 10). \\
-
-For the closures based on 'real population' (bottom row), the most
-disaggregated data (a weekly timescale and 1 x 1 resolution) was most
-effective, reducing fishing mortality on species 1 (left) by $\sim$ 60 \%. Next
-was the monthly closures ($<$ $\sim$ 30 \%).  The least effective were the
-yearly closures (blue lines) at all spatial resolutions, which resulted in
-increased fishing mortalities ($>$ 30 \% - \textcolor{blue}{N.B. Note though,
-this is consistent with the increasing trends in F, which is probably more
-related to the fact that Fs hadn't stabilised in the simulation from the
-fishing vessels "learning" the best locations - I will rerun the sims for a
-longer time (20 - 30 years)}. \\
-
-For the survey data, which can only be implemented on a yearly timescale, the
-closures had no effect at any data resolution. The results are identical for
-the different data resolutions except 20 x 20, which is why you can't see more
-than 2 points. This is because of the sparsity of the sampling locations.\\
-
-For the commercial data, the most effective closure scenario was based on 1 x 1
-data at a monthly temporal resolution. This results in $\sim$ 10 \% reduction
-in F for species 1. \textcolor{blue}{This was the only closure scenario to have
-	positive effect according to Figure \ref{fig:4}, though looking at the
-	trend in Figure \ref{fig:3} this looks more related to the continued
-	increased in F trend, as other scenarios had an initial effect}.
-Interestingly the monthly data scenario was more effective than weekly data,
-which I'd posit is due to the increase amount of data available from the
-commercial sampling across a month compared to a week.i Commercial data used at
-an annual timestep was ineffective in bringing fishing mortality down for
-species 1. \\
-
-Given the scenarios above, it seems clear that spatial disaggregation is more
-important than the temporal disaggregation of the commercial data, except when
-its used at an annual timeframe, which is the scenario that gave the worst
-results.
-
-For the other species in the simulation (population 2 - 4) there was little
-difference in fishing mortalities across scenarios.
-
-\textcolor{blue}{Note: The monthly commercial data scenario is the most
-	effective of the realistic scenarios, as the 'real population' can only
-	be seen as a baseline comparison.}
-
-\section{Discussion}
-
-\section{Conclusions}
-
-\section*{Appendices}
-
-\begin{table}[!ht]
-	\centering
-	\caption{Description of variables for population dynamics sub-module}
-	\label{tab: pop_variable}
-	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
-		\toprule
-		Variable & Meaning & Units \\
-		\hline
-		\multicolumn{3}{c}{\textbf{Population dynamics}}  \\
-		\hhline{===}
-		\multicolumn{3}{l}{\textit{Delay-difference model}} \\
-		\hline
-		$B_{c,d}$ & Biomass in cell $c$ and day $d$ & kg \\
-		$Z_{c,d}$ & Total mortality in cell $c$ for day $d$ & - \\
-		$R_{c, \tilde{y}}$  &Annualy recruited fish in cell &  yr\textsuperscript{-1} \\
-		$\rho$ & Brody's growth coefficient & yr\textsuperscript{-1} \\
-		$Wt_{R}$ & Weight of a fully recruited fish & kg \\
-		$Wt_{R-1}$ & Weight of a pre-recruit fish & kg \\
-		$\alpha_{d}$ & Proportion of annually recruited fish recruited
-		during day $d$ & - \\
-		\hline
-		\multicolumn{3}{l}{\textit{Baranov catch equation}} \\
-		\hline
-		$C_{c,d}$ & Catch from cell $c$ for day $d$ & kg \\
-		$F_{c,d}$ & Instantaneous rate of fishing mortality in cell $c$
-		on day $d$ & - \\
-		$M_{c,d}$ & Instantaneous rate of natural mortality in cell $c$
-		on day $d$ & - \\
-		$B_{c,d}$ & Biomass in cell $c$ on day $d$ & kg \\
-		\hline
-		\multicolumn{3}{c}{\textbf{Recruitment dynamics}} \\
-		\hhline{===}
-		$\tilde{R}_{c,d}$ & is the recruitment in cell $c$ for day $d$ & $d^{-1}$ \\
-		$B_{c,d}$ & is the Biomass in cell $c$ for day $d$ & $d^{-1}$ \\
-		$\alpha$ & the maximum recruitment rate & kg  \\
-		$\beta$ & the biomass required to produce half the maximum rate
-		of recruitment & kg \\
-		\bottomrule
-		\end{tabular}
-	\end{table}
-
-\begin{table}[!ht]
-	\centering
-	\caption{Description of variables for population movement sub-module}
-	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
-		\toprule
-		Variable & Meaning & Units \\
-		\hline
-		\multicolumn{3}{c}{\textbf{Population movement dynamics}} \\
-		\hhline{===}
-		\multicolumn{3}{l}{\textit{Habitat model}} \\
-		\hline
-		a & b & c \\
-		\hline
-		\multicolumn{3}{l}{\textit{Thermal tolerance}} \\
-		\hline
-		$T_{c,wk}$ & Temperature for cell in week & $^\circ$C \\
-		$\mu_{p}$ & Mean of the thermal tolerance for population & $^\circ$C \\
-		$\sigma^{2}_{p}$ & Standard deviation of thermal tolerance for
-		the population & $^\circ$C \\
-		\hline
-		\multicolumn{3}{l}{\textit{Population movement model}} \\
-		\hline
-		$\lambda$ & decay rate for population movement & - \\
-		$Hab^{2}_{c,p}$ & Square of habitat suitability for cell $c$ and
-		population $p$ & - \\
-		$Tol_{c,p,wk}$ & Thermal tolerance for population $p$ in cell
-		$c$ at week $wk$ & - \\
-		$d_{IJ}$ & euclidean distance between cell $I$ and cell $J$ & - \\
-		\bottomrule
-		\end{tabular}
-	\end{table}
-
-\begin{table}[!ht]
-	\centering
-	\caption{Description of variables for fleet dynamics sub-module}
-	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
-		\toprule
-		Variable & Meaning & Units \\
-		\hline
-		\multicolumn{3}{c}{\textbf{Short-term fleet dynamics}} \\
-		\hhline{===}
-		$Rev$ & Revenue from fishing tow & \euro \\
-		$L_{p}$ & Landings of population $p$ & kg \\
-		$Pr_{p}$ & Average price of population $p$ & \euro
-		\hspace{0.1cm} kg$^{-1}$ \\
-		StepL & Step length for vessel & euclidean distance \\
-		Br & Bearing & degrees \\
-		$k$ & Concentration parameter for Von mises distribution & - \\
-		$\beta_{1}$ & shape parameter for step function & - \\
-		$\beta_{2}$ & shape parameter for step function & - \\
-		$\beta_{3}$ & shape parameter for step function & - \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{table}[!ht]
-\caption{Population dynamics and movement parameter setting}
-	\begin{tabular}{ p{4cm } p{2cm} p{2cm} p{2cm} p{2cm}}
-	Parameter & Pop 1 & Pop 2 & Pop 3 & Pop 4 \\
-	\hline
-	Habitat quality & & & \\
-	\hline
-	Matérn $\nu$ & 1/0.15 & 1/0.05 & 1/0.55 & 1/0.05  \\
-	Matérn $\kappa$ & 1 & 2 & 1 & 1  \\
-	Anisotropy & 1.5,3,-3,4 & 1,2,-1,2 & 2.5,1,-1,2 & 0.1,2,-1,0.2 \\
-	Spawning areas (bound box) & 40,50,40,50; 80,90,60,70 &
-	50,60,30,40; 80,90,90,90 & 30,34,10,20; 60,70,20,30 & 50,55,80,85; 30,40,30,40 \\
-	Spawning multiplier & 10 & 10 & 10 & 10 \\
-	Movement $\lambda$ & 0.3 & 0.3 & 0.3 & 0.3 \\
-	\hline
-	Population dynamics & & & & \\
-	\hline
-	Starting Biomass & 1e5 & 2e5 & 1e5 & 1e4 \\
-	Beverton-Holt Recruit 'a' & 60 & 100 & 80 & 2 \\
-	Beverton-Holt Recruit 'b' & 250 & 250 & 200 & 50 \\
-	Beverton-Holt Recruit $\sigma^2$ & 0.4 & 0.3 & 0.4 & 0.3 \\
-	Recruit week & 13-16 & 12-16 & 14-16 & 16-20 \\
-	Spawn week & 16-18 & 16-19 & 16-18 & 18-20 \\
-	$K$ & 0.3 & 0.3 & 0.3 & 0.3 \\
-	$wt$ & 1 & 1 & 1 & 1 \\
-	$wt_{d-1}$ & 0.1 & 0.1 & 0.1 & 0.1 \\
-	M (annual) & 0.2 & 0.2 & 0.2 & 0.1 \\
-	\hline
-\end{tabular}
-\label{tab:1}
-\end{table}
-
-\begin{table}[!ht]
-\caption{Fleet dynamics parameter setting}
-\begin{tabular}{ p{4cm } p{1cm} p{1cm} p{1cm} p{1cm} p{1cm}}
-	\hline
-	Parameter & Fleet 1 & Fleet 2 & Fleet 3 & Fleet 4 & Fleet 5 \\
-	\hline
-	Targeting preferences &&&& \\
-	\hline
-	Price Pop1 & 100 & 100 & 100 & 100 & 100 \\
-	Price Pop2 & 200 & 200 & 200 & 200 & 200 \\
-	Price Pop3 & 600 & 600 & 600 & 600 & 600 \\
-	Price Pop4 & 1600 & 1600 & 1600 & 1600 & 1600 \\
-	$Q$ Pop1 & 0.01 & 0.02 & 0.02 & 0.01 & 0.01 \\
-	$Q$ Pop2 & 0.02 & 0.01 & 0.02 & 0.01 & 0.03\\
-	$Q$ Pop3 & 0.01 & 0.02 & 0.02 & 0.01 & 0.02 \\
-	$Q$ Pop4 & 0.02 & 0.01 & 0.02 & 0.05 & 0.01 \\
-	\hline
-	Exploitation dynamics &&&& \\
-	\hline
-	step function $\beta_1$ & 1 & 2 & 1 & 2 & 3 \\
-	step function $\beta_2$ & 10 & 10 & 8 & 12 & 7 \\
-	step function $\beta_3$ & Q90 & Q90 & Q85 & Q90 & Q80 \\
-	step function $rate$ & 10 & 20 & 15 & 25 & 10 \\
-	Past Knowledge & T & T & T & T & T \\
-	Past Year \& Month & T & T & T & T & T \\
-	Past Trip & T & T & T & T & T \\
-	Threshold & 0.75 & 0.75 & 0.75 & 0.75 & 0.75 \\
-	\hline
-\end{tabular}
-\label{tab:2}
-\end{table}
-
-\begin{figure}[!ht]
-	\includegraphics[width =\linewidth]{../analysis/Data_Aggregation_space}
-	\caption{Data aggregation at different spatial resolutions}
-	\label{fig:1}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../analysis/Data_Aggregation_time}
-	\caption{Data aggregation at different temporal resolutions}
-	\label{fig:2}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../analysis/F_trendsREV}
-	\caption{Comparison of closure scenarios - F trends}
-	\label{fig:3}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width =\linewidth]{../analysis/Overview_plot_highPopRev}
-	\caption{Comparison of closure scenarios}
-	\label{fig:4}
-\end{figure}
-
-\section*{Abbreviations} Detail any unusual ones used.
-
-\section*{Acknowledgements} those providing help during the research..
-
-\section*{Funding} This work was supported by the MARES doctoral training
-program; and the Centre for Environment, Fisheries and Aquaculture Science
-seedcorn program.
-
-\clearpage
-
-\section*{References}
-
-\bibliography{simulation_framework}
-
-\end{document}

### 2019-02-19 write_up/mixfishsim_ecolmod.tex
Updating supplementary figures

@@
 \usepackage{mathtools}
+
+%% for the annex figure
 \usepackage{tikz}
 \usetikzlibrary{shapes,arrows,chains,calc}
+% Set up a few colours for tikz figure
+\colorlet{lcfree}{green}
+\colorlet{lcnorm}{blue}
+\colorlet{lccong}{red}
+
 \usepackage{hhline}
@@
 \definechangesauthor[color = purple]{CM}
-
-% Set up a few colours for tikz figure
-\colorlet{lcfree}{green}
-\colorlet{lcnorm}{blue}
-\colorlet{lccong}{red}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Overview schematic  
-\begin{figure}[!ht]
-	\hspace{-4em}
-\begin{tikzpicture}[%
-    >=triangle 60,              % Nice arrows; your taste may be different
-    start chain=going below,    % General flow is top-to-bottom
-    node distance=8mm and 60mm, % Global setup of box spacing
-    every join/.style={norm},   % Default linetype for connecting boxes
-    scale=0.9,
-    every node/.style={scale=0.8}]                 
-    \label{fig:model}
-    % ------------------------------------------------- 
-% A few box styles 
-% <on chain> *and* <on grid> reduce the need for manual relative
-% positioning of nodes
-\tikzset{
-  base/.style={draw, on chain, on grid, align=center, minimum height=4ex},
-  proc/.style={base, rectangle, text width=8em},
-  test/.style={base, rectangle, text width=5em},
-  term/.style={proc, rounded corners},
-  % coord node style is used for placing corners of connecting lines
-  coord/.style={coordinate, on chain, on grid, node distance=6mm and 25mm},
-  % nmark node style is used for coordinate debugging marks
-  nmark/.style={draw, cyan, circle, font={\sffamily\bfseries}},
-  % -------------------------------------------------
-  % Connector line styles for different parts of the diagram
-  norm/.style={->, draw, lcnorm},
-  free/.style={->, draw, lcfree},
-  cong/.style={->, draw, lccong},
-  it/.style={font={\small\itshape}}
-}
-% -------------------------------------------------
-% Start by placing the nodes in the middle
-\node [proc, densely dotted, it] (p0) {start};
-% Use join to connect a node to the previous one 
-\node [term, join, fill=lcnorm!25]      {Choose random location to fish};
-\node [term, join, fill=lcfree!25] (p1){Sample catch};
-\node [test, densely dotted] (t1) {if $(Rec)$};
-\node [test, join, densely dotted] (t2) {if (Pop Movement)};
-\node [test, join, densely dotted] (wk) {if (Pop Dynamics)};
-\node [test, join, densely dotted] (t3) {if (Past Knowledge)};
-\node [term, join, fill=lcnorm!25]  (p2) {Correlated Random Walk};
-\node [term, join, fill=lcnorm!25]  (p3) {Choose new fishing location};
-\node [proc, densely dotted, join, it] (p7) {end};
-
-% Right nodes
-\node [proc, fill=lcfree!25, right=of p1] (p4) {Popn depletion};
-\node [proc, fill=lcfree!25, right=of t1] (p5) {Popn Recruitment};
-\node [proc, fill=lcfree!25] (p6) {Popn movement};
-\node [proc, fill=lcfree!25, right=of wk] (wk1) {Growth and natural
-	mortality};
-
-% left nodes
-\node [test, fill=lcnorm!25, left=of t3] (t4) {Use past fishing locations};
-
-% -------------------------------------------------
-% A couple of boxes have annotations
-\node [below=of p0, it, yshift=1.5em,xshift=-3em] {$t=1$};
-\node [right=30mm of p3, it] {$1 < t < t_{max}$};
-\node [below=of p3, it,xshift=-3em, yshift=1.5em] {$t = t_{max}$};
-
-% -------------------------------------------------
-% First, the straight north-south connections. In each case, we first
-% draw a path with a (consistently positioned) annotation node, then
-% we draw the arrow itself.
-  \draw [*->,lcfree!50] (p1) -- (p4);
-\path (t1) to node [near start, xshift=2em, yshift=0.5em] {$y$} (p5); 
-  \draw [*->,lcfree!50] (t1) -- (p5);
-\path (t2) to node [near start, xshift=2em, yshift=0.5em] {$y$} (p6); 
-  \draw [*->,lcfree!50] (t2) -- (p6);
-\path (t3) to node [near start, xshift=-3em, yshift=0.5em] {$y$} (t4); 
-  \draw [*->,lccong!50] (t3) -- (t4);
-\path (wk) to node [near start, xshift=2em, yshift=0.5em] {$y$} (wk1); 
-  \draw [*->,lcfree!50] (wk) -- (wk1);
-
-% left to right paths
-\path (t1) to node [near start, yshift=-0.2em] {$n$} (t2) ;  
-\path (t2) to node [near start, yshift=0.8em] {$n$} (t3) ;  
-\path (wk) to node [near start, yshift=-0.2em] {$n$} (t3) ;  
-\path (t3) to node [near start, yshift=-0.3em] {$n$} (p2) ;
-
-% ------------------------------------------------- 
-% the twisty connectors. Again, we place the annotation
-% first, then draw the connector
-
-\node [coord, left=of p3] (c1)  {};  
-\draw [*->,lccong!50] (t4.south) -- (c1) |- (p3);
-
-\node[coord, below=of p4] (c2) {};
-\node[coord, above=of t1] (c3) {};
-\draw [-<,lcfree!50] (p4.south) -- (c2) |- (c3) |- (t1.north);
-
-\node[coord, below=of p5] (c4) {};
-\draw [->,lcfree!50] (p5.south) -- (c4) |- ($(t2.east) + (0,0.5)$);
-
-\node[coord, below=of p6] (c71) {};
-\draw [->,lcfree!50] (p6.south) -- (c71) |- ($(wk.east) + (0,0.56)$);
-
-\node[coord, below=of wk1] (c7) {};
-\draw [->,lcfree!50] (wk1.south) -- (c7) |- ($(t3.east) + (0,0.3)$);
-
-% -------------------------------------------------
-% A last flourish which breaks all the rules
-\draw [->,purple, dotted, thick, shorten >=1mm]
-  (p3.south) -- ++(5mm,-3mm)  -- ++(87mm,0mm) 
-  |- node [black, near end, yshift=1.75em, it]
-    {} ($(p1.north) + (0,0.3)$);
-% -------------------------------------------------
-\end{tikzpicture}
-\caption{Overview Schematic of simulation model. The blue boxes indicate fleet
-	dynamics processes, the green boxes population dynamics processes while
-	the white boxes are the time steps at which processes occur; $t$ = tow,
-	$tmax$ is the total number of tows; (Rec), (Pop Movement), (Pop
-	Dynamics) logic gates for recruitment periods, population movement and
-	population dynamics for each of the populations, (Past Knowledge) a
-	switch whether to use a random (exploratory) or past knowledge
-	(exploitation) fishing strategy.}
-\label{fig:overview}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% the tikz figure
+\input{Process_model.tex}
 
@@
 
-%\newpage
-%\input{C_changes.tex}
-
 %%%% figures

### 2019-02-19 analysis/Plot_Bio.R

@@ -1,10 +1,10 @@
 
 library(MixFishSim)
 
-#Run <- 0
+Run <- 0
 
-#load(file.path('.', 'Scenario_runs_Nov18', paste0('Scenario_',Run,'.RData')))
-load(file.path('.', 'Scenario_runs_Nov18', paste0('Comparison_Run.RData')))
+load(file.path('.', 'Scenario_runs_Nov18', paste0('Scenario_',Run,'.RData')))
+#load(file.path('.', 'Scenario_runs_Nov18', paste0('Comparison_Run.RData')))
 
 
 
@@ -21,7 +21,7 @@ plot_catch_comp(gran = c(1), logs = logs, fleets = 1:5,
 
 ## Simple plot of distribution changes over time
 
-png(file = file.path("..", "tests","plots", "pop_dist.png"), width = 1600, height = 1600)
+png(file = file.path("..", "write_up","Plots", "pop_dist.png"), width = 1600, height = 1600)
 par(mfrow=c(4,4), mar = c(1,1,1,1))
 
 for(j in round(seq.int(1,52,length.out = 4),0)) {

### 2019-02-19 analysis/Plots.R

@@ -8,8 +8,8 @@ library(MixFishSim)
 load('Common_Params.RData')
 
 Run <- 0 
-#load(file.path('Scenario_runs_Nov18', paste0("Scenario_", Run, ".RData")))
-load(file.path('Scenario_runs_Nov18', paste0("Comparison_Run.RData")))
+load(file.path('Scenario_runs_Nov18', paste0("Scenario_", Run, ".RData")))
+#load(file.path('Scenario_runs_Nov18', paste0("Comparison_Run.RData")))
 
 plot_pop_summary(res, timestep = "annual", save = FALSE)
 
@@ -18,20 +18,20 @@ ggsave(file = file.path('..', 'write_up', 'Plots', 'f_dynamics.png'), width = 8,
 
 logs <- combine_logs(res[["fleets_catches"]])
 
-plot_vessel_move(sim_init = sim, logs = logs, fleet_no = 2, vessel_no = 5,
-       year_trip = 30, trip_no = 1:8)
+plot_vessel_move(sim_init = sim, logs = logs, fleet_no = 3, vessel_no = 14,
+       year_trip = 30, trip_no = 1)
 ggsave(file = file.path("..", "write_up", "Plots", "vessel_move.png"), width = 8, height = 8)
 
 
-plot_vessel_move(sim_init = sim, logs = logs, fleet_no = 1, vessel_no = 1:10,
-       year_trip = 10, trip_no = 43:52)
+plot_vessel_move(sim_init = sim, logs = logs, fleet_no = 3, vessel_no = 12,
+       year_trip = 30, trip_no = 43:52)
 ggsave(file = file.path("..", "write_up", "Plots", "vessel_multi_move.png"), width = 8, height = 8)
 
-plot_vessel_move(sim_init = sim, logs = logs, fleet_no = 2, vessel_no = 1:10,
+plot_vessel_move(sim_init = sim, logs = logs, fleet_no = 3, vessel_no = 1:20,
        year_trip = 34, trip_no = 43, fleets_init = fleets, pop_bios = res[["pop_bios"]])
 ggsave(file = file.path("..", "write_up", "Plots", "vessel_move_value.png"), width = 8, height = 8)
 
-plot_fleet_trip(logs = logs, fleet_no = 1, year_trip = 10, trip_no = 1)
+plot_fleet_trip(logs = logs, fleet_no = 3, year_trip = 30, trip_no = 2)
[…]

### 2019-02-19 write_up/Plots/Plot_temp_effect.R

@@ -5,27 +5,27 @@ set.seed(123, kind = "L'Ecuyer-CMRG")
 
 ## initialise the simulation
 
-sim <- init_sim(nrows = 100, ncols = 100, n_years = 10, n_tows_day = 4, n_days_wk_fished = 5,
+sim <- init_sim(nrows = 100, ncols = 100, n_years = 50, n_tows_day = 4, n_days_wk_fished = 5,
      n_fleets = 5, n_vessels = 20, n_species = 4, move_freq = 2)
 
 ## create the suitable habitat for each species
 
 hab <- create_hab(sim_init = sim,
 		  spp.ctrl = list(
-           'spp.1' = list('nu' = 1/0.15, var = 1, scale = 10, Aniso =
+           'spp.1' = list('nu' = 1/0.015, var = 1, scale = 10, Aniso =
            matrix(nc=2, c(1.5, 3, -3, 4))),
-           'spp.2' = list('nu' = 1/0.05, var = 2, scale = 20, Aniso =
+           'spp.2' = list('nu' = 1/0.05, var = 2, scale = 12, Aniso =
            matrix(nc=2, c(1, 2, -1, 2))),
-	   'spp.3' = list('nu' = 1/0.55, var = 1, scale = 5, Aniso =
+	   'spp.3' = list('nu' = 1/0.01, var = 1, scale = 12, Aniso =
            matrix(nc=2, c(2.5, 1, -1, 2))),
-           'spp.4' = list('nu' = 1/0.05, var = 1, scale = 30, Aniso =
-           matrix(nc=2, c(0.1, 2, -1, 0.2)))
+           'spp.4' = list('nu' = 1/0.005, var = 1, scale = 8, Aniso =
+           matrix(nc=2, c(0.1, 2, -1, 0.02)))
 				  ),
 		  spawn_areas = list("spp1" = list(area1 = c(40, 50, 40, 50), area2 =
 				   c(80, 90, 60, 70)), 
-		 "spp2" = list(area1 = c(50, 60, 30, 40), area2 = c(80, 90, 90, 90)),
-		 "spp3" = list(area1 = c(30, 34, 10, 20), area2 = c(60, 70, 20, 30)),
-		 "spp4" = list(area1 = c(50, 55, 80, 85), area2 = c(30, 40, 30, 40))
[…]

### 2019-02-19 write_up/F_changes.tex
Text updates and include test of effectiveness of knowledge parameters

@@
 % latex table generated in R 3.5.2 by xtable 1.8-3 package
-% Mon Jan 28 16:57:19 2019
+% Tue Feb 19 17:00:17 2019
 \begin{longtable}{rllrrrlllr}
-\caption{Fishing mortality effects of the closure scenarios} \\ 
+\caption{Fishing mortality effects of the
+     closure scenarios (ordered by most effective first)} \\ 
   \hline
-scenario & metric & pop & before & after & diff (\%) & timescale & basis & data\_type & resolution \\ 
+scenario & metric & pop & before & after & diff & timescale & basis & data\_type & resolution \\ 
   \hline

### 2019-02-19 write_up/F_changes_ratio.tex
Text updates and include test of effectiveness of knowledge parameters

% latex table generated in R 3.5.2 by xtable 1.8-3 package
% Tue Feb 19 17:01:38 2019
\begin{longtable}{rllrrrlllr}
\caption{Fishing mortality effects of the
     closure scenarios (based on highest ratio, ordered by most
effective first)} \\ 
  \hline
scenario & metric & pop & before & after & diff & timescale & basis & data\_type & resolution \\ 
  \hline
  6 & F & spp\_3 & 1.08 & 0.52 & -52.27 & yearly & high\_ratio & commercial & 1.00 \\ 
   48 & F & spp\_3 & 1.08 & 0.57 & -47.06 & yearly & high\_ratio & commercial & 20.00 \\ 
   50 & F & spp\_3 & 1.08 & 0.63 & -41.53 & yearly & high\_ratio & survey & 20.00 \\ 
   18 & F & spp\_3 & 1.08 & 0.71 & -34.23 & weekly & high\_ratio & commercial & 5.00 \\ 
   19 & F & spp\_3 & 1.08 & 0.72 & -33.42 & monthly & high\_ratio & commercial & 5.00 \\ 
   34 & F & spp\_3 & 1.08 & 0.78 & -27.75 & yearly & high\_ratio & commercial & 10.00 \\ 
    5 & F & spp\_3 & 1.08 & 0.80 & -25.99 & monthly & high\_ratio & commercial & 1.00 \\ 
   20 & F & spp\_3 & 1.08 & 0.81 & -25.27 & yearly & high\_ratio & commercial & 5.00 \\ 
    4 & F & spp\_3 & 1.08 & 0.85 & -21.52 & weekly & high\_ratio & commercial & 1.00 \\ 
   54 & F & spp\_3 & 1.08 & 0.89 & -17.46 & weekly & high\_ratio & real\_pop & 20.00 \\ 
   55 & F & spp\_3 & 1.08 & 0.89 & -17.46 & monthly & high\_ratio & real\_pop & 20.00 \\ 
   56 & F & spp\_3 & 1.08 & 0.89 & -17.46 & yearly & high\_ratio & real\_pop & 20.00 \\ 
   26 & F & spp\_3 & 1.08 & 0.92 & -14.73 & weekly & high\_ratio & real\_pop & 5.00 \\ 
   27 & F & spp\_3 & 1.08 & 0.92 & -14.73 & monthly & high\_ratio & real\_pop & 5.00 \\ 
   28 & F & spp\_3 & 1.08 & 0.92 & -14.73 & yearly & high\_ratio & real\_pop & 5.00 \\ 
   13 & F & spp\_3 & 1.08 & 0.96 & -11.53 & monthly & high\_ratio & real\_pop & 1.00 \\ 
   14 & F & spp\_3 & 1.08 & 0.96 & -11.01 & yearly & high\_ratio & real\_pop & 1.00 \\ 
   12 & F & spp\_3 & 1.08 & 0.97 & -10.66 & weekly & high\_ratio & real\_pop & 1.00 \\ 
   32 & F & spp\_3 & 1.08 & 1.02 & -5.94 & weekly & high\_ratio & commercial & 10.00 \\ 
   22 & F & spp\_3 & 1.08 & 1.02 & -5.64 & yearly & high\_ratio & survey & 5.00 \\ 
   33 & F & spp\_3 & 1.08 & 1.02 & -5.29 & monthly & high\_ratio & commercial & 10.00 \\ 
   36 & F & spp\_3 & 1.08 & 1.03 & -4.52 & yearly & high\_ratio & survey & 10.00 \\ 
   40 & F & spp\_3 & 1.08 & 1.03 & -4.52 & weekly & high\_ratio & real\_pop & 10.00 \\ 
   41 & F & spp\_3 & 1.08 & 1.03 & -4.52 & monthly & high\_ratio & real\_pop & 10.00 \\ 
   42 & F & spp\_3 & 1.08 & 1.03 & -4.52 & yearly & high\_ratio & real\_pop & 10.00 \\ 
   46 & F & spp\_3 & 1.08 & 1.04 & -3.50 & weekly & high\_ratio & commercial & 20.00 \\ 
    8 & F & spp\_3 & 1.08 & 1.06 & -2.42 & yearly & high\_ratio & survey & 1.00 \\ 
   47 & F & spp\_3 & 1.08 & 1.09 & 0.52 & monthly & high\_ratio & commercial & 20.00 \\ 
   \hline
\hline
\label{tab:7}
\end{longtable}

### 2019-02-19 write_up/mixfishsim_ecolmod.tex
Text updates and include test of effectiveness of knowledge parameters

@@
 \replaced[id = JJ]{Most fisheries}{Fishing} exploit\deleted[id=JJ]{s} a variety 
-of spatially and temporally heterogeneous fish populations, using
+of spatially and temporally heterogeneous fish populations using
 species-unselective gear that can result in unintended, unwanted catch of low
@@
 %% the tikz figure
+\clearpage
 \input{Process_model.tex}
@@
 
-We parametrised the simulation model for four populations with differing
-habitat preference\replaced{,}{ and} temperature tolerances (Figures
-\ref{S-fig:1}, \ref{S-fig:3}, \ref{S-fig:4}, \ref{S-fig:5}, \ref{S-fig:6},
-\ref{S-fig:7}), population demographics and recruitment functions. In addition,
-each of the populations has two defined spawning areas which result in the
-populations moving towards these areas in given weeks (Figure \ref{S-fig:2})
-and population-specific movement rates (Table \ref{tab:1}). The realised
-movement of the populations for a number of weeks is shown in Figure
-\ref{S-fig:9} while the realised daily fishing mortality are shown in Figure
-\ref{S-fig:10}.
+We parametrised the simulation model for four populations with different
+population demographics; growth rates, natural mortality and recruitment
+functions (Table \ref{tab:1}). Habitat preference (Figure \ref{S-fig:1}) and
+temperature tolerances (Figures \ref{S-fig:3}, \ref{S-fig:4}) were unique to
+each population resulting in differently weekly distribution patterns (Figures
+\ref{S-fig:5}-\ref{S-fig:7}). In addition, each of the populations has two
+defined spawning areas which result in the populations moving towards these
+areas in pre-defined weeks (Figure \ref{S-fig:2}) with population-specific
+movement rates (Table \ref{tab:1}). The realised movement of the populations
+for a number of weeks is shown in Figure \ref{S-fig:9} while the realised daily
+fishing mortality are shown in Figure \ref{S-fig:10}.
 
@@
 simulations as the maximum revenue obtainable was not known beforehand. This
-was implemented so that vessels take smaller steps where the fishing location
-yields in a top quartile of the value experienced in each year (as defined per
-fleet in Table \ref{tab:2}). \\
+was implemented so that vessels take smaller steps when fishing at a location
+yields landings value which is in the top 90th percentile of the value
+experienced in that year (as defined per fleet in Table \ref{tab:2}). \\
 
-With an increasing probability throughout the simulation fishing locations were
-chosen based on experience built up in the same month from previous years and
-from past trip fishing success.  'Success' in this context was defined as the
-locations where the top 75 \% of expected profit would be found given previous
-trips revenue and cost of movement to the new fishing location. This
-probability was based on a logistic sigmoid function with a lower asymptote of
-0 and upper asymptote of 0.95, and a growth rate which ensures the upper
-asymptote (where decisions are mainly based on past knowledge) is reached
-$\sim$ halfway through the simulation).  \\
+With increasing probability throughout the simulation, fishing locations were
+chosen based on experience of profitable catches built up in the same month
+from previous years and from the previous trip. 'Profitable' in this context
+was defined as the locations where the top 70 \% of expected profit would be
+found given previous trips revenue and cost of movement to the new fishing
+location.  This probability was based on a logistic sigmoid function with a
+lower asymptote of 0 and upper asymptote of 0.95, and a growth rate which
+ensures the upper asymptote (where decisions are mainly based on past
+knowledge) is reached $\sim$ halfway through the simulation.  \\
 
@@
 multiple trips for a single vessel, \added[id=PD]{Figure} \ref{S-fig:13} the
-vessel movements for some trips overlaid on the value field,
-\added[id=PD]{Figure} \ref{S-fig:14} shows fishing locations for an entire
-fleet of 20 vessels for a single trip, \replaced[id=PD]{and Figure}{while}
-\ref{S-fig:15} shows an example of the step function realisation and turning
-angles from the correlated random walk.\todo{\added[id=JJ]{Move some of the
-	supplementary figures to the manuscript}}
+vessel movements for several trips overlaid on the value field (sum of the
+population densities $\times$ price), \added[id=PD]{Figure} \ref{S-fig:14} shows
+fishing locations for an entire fleet of 20 vessels for a single trip,
+\replaced[id=PD]{and Figure}{while} \ref{S-fig:15} shows an example of the step
+function realisation and turning angles from the correlated random
+walk.\todo{\added[id=JJ]{Move some of the supplementary figures to the
+		manuscript}}
 
@@
 the reduction in catches of a population given spatial closures. To do so, we
-set up a simulation to run for 50 years based on a 100 X 100 square grid, with
-five fleets of 20 vessels each and four fish populations. Fishing takes place
-four times a day per vessel and five days a week, while population movement is
-every week.\todo{\added[id=JJ]{move to start of methods section}\added[id=PD]{I
-		think ecological modelling wants the 'calculations' section
-		here..will check}} \\
+set up a simulation to run for 50 years based on a 100 $\times$ 100 square
+grid, with five fleets of 20 vessels each and four fish populations. Fishing
+takes place four times a day per vessel and five days a week, while population
+movement is every week.\todo{\added[id=JJ]{move to start of methods
+		section}\added[id=PD]{I think ecological modelling wants the
+		'calculations' section here..will check}} \\
 
 We allow the simulation to run unrestricted for 30 years\todo{\added[id=JJ]{Is
-		there equilibrium after 5 years or still some trend in
-		B}\added[id=PD]{Not at equilibrium yet...I need to rerun until
-		steady state, looks 20 years. Will update}}, and subsequently
-close areas for the last 20 years of the simulation based on data (either
-derived from the commercial catches, fisheries-independent survey or the 'real
-population' - where the underlying populations assumed to be known perfectly)
-used at different spatial and temporal scales. \\
+		there equilibrium after 5 years or still some trend in B?
+	}\added[id=PD]{I have rerun to ensure some steady state dynamics}},
+then implement spatial closed areas for the last 20 years of the simulation
+based on data (either derived from the commercial catches,
+fisheries-independent survey or the 'real population') used at different
+spatial and temporal scales. \\
 
@@
 	\item Extract data source
-	\item Aggregate according to resolution
+	\item Aggregate according to desired spatial and temporal resolution
 	\item Interpolate across entire area at desired resolution
@@
 \end{enumerate}
-In total 56 closure scenarios were run which represent combinations of
+In total 56 closure scenarios were run which represent combinations of:
 
@@
 Figure \ref{fig:1}, which represents the aggregation of catch from each of the
-data sources over a year at different spatial resolutions. \\
+data sources over a ten year period (to average seasonal patterns) at different
+spatial resolutions. \\
 
-The finer spatial grid for the the real population (top left) and commercial
-data (top middle) show similar patterns, though there are unsampled gaps in the
+The finer spatial grid for the real population (top left) and commercial data
+(top middle) show similar patterns, though there are unsampled gaps in the
 commercial data from a lack of fishing activity (particularly in the lower left
 part of the sampling domain). The survey data at this spatial resolution shows
-very sparse and uninformative information about the spatial distributions of
-the populations. The slightly aggregated data on a 5 x 5 grid shows similar
-patterns, and while losing some of the spatial detail there remains good
-consistency between the 'real population' and the commercial data. Survey data
-starts to pick out some of the similar patterns as the other data sources, but
-lacks coverage. The spatial catch information on a 10 x 10 and 20 x 20 grid
-loses a significant amount of information about the spatial resolutions for all
-data sources, and some differences between the commercial and 'real population'
-data emerge. \\
+very sparse information about the spatial distributions of the populations. The
+slightly aggregated data on a 5 x 5 grid shows similar patterns, and while
+losing some of the spatial detail there remains good consistency between the
+'real population' and the commercial data. Survey data starts to pick out some
+of the similar patterns as the other data sources, but lacks coverage. The
+spatial catch information on a 10 x 10 and 20 x 20 grid loses a significant
+amount of information about the spatial resolutions for all data sources, and
+some differences between the survey, commercial and 'real population' data
+emerge. \\
 
 Figure \ref{fig:2} shows the consequences of different temporal aggregations of
-the data, with 156 weekly (top), 36 monthly (middle) and 3 yearly (bottom)
-catch compositions across a 20 x 20 area. \\
+the data over a three year period, with 156 weekly (top), 36 monthly (middle)
+and 3 yearly (bottom) catch compositions from across an aggregated 20 x 20
+area. \\
 
-As can be seen from the 'real population', the monthly aggregation captures the
-major patterns seen in the weekly data, albeit missing more subtle differences.
-The yearly data results in a constant catch pattern due to the aggregation
-process (sometimes known as an aggregation bias). The commercial data on a
-weekly basis shows some of the same patterns as the 'real population', though
-the first species (in red) is less well represented and some weeks are missing
-catches from the area. The monthly data. The monthly data shows some
-consistency between the 'real population' and commercial data for species 2 -
-4, though species 1 remains underrepresented. On an annual basis, interestingly
-the commercial data underrepresents the first species (in red) while the survey
-overrepresents species 1. This is likely due to the biases in commercial
-sampling, with the fisheries not targeting the areas where species 1 are
-present, and the biases in the survey sampling from overrepresentation of the
-spatial distribution. \\
+As can be seen by comparison to the 'real population', the monthly aggregation
+captures the major patterns seen in the weekly data, albeit missing more subtle
+differences. The yearly data results in a constant catch pattern due to the
+aggregation process (sometimes known as an aggregation bias). The commercial
+data on a weekly basis shows some of the same patterns as the 'real
+population', though the first species (in red) is less well represented and
+some weeks are missing catches from the area. The monthly data. The monthly
+data shows some consistency between the 'real population' and commercial data
+for species 2 - 4, though species 1 remains under-represented. On an annual
+basis, interestingly the commercial data under represents the first species (in
+red) while the survey over represents species 1. This is likely due to the
+biases in commercial sampling, with the fisheries not targeting the areas where
+species 1 are present, and the biases in the survey sampling from over
+representation of the spatial distribution. \\
 
@@
 sources (rows), temporal aggregations (colour lines) and spatial aggregations
-(linestyles), while Figure \ref{fig:4} shows the change in fishing mortality
-from before the closure (average F years 2 - 4) to after the closure (average F
-years 8 - 10). \\
+(line-styles), while Figure \ref{fig:4} shows the change in fishing mortality
+from before the closure (year 29) to after the closure (year 50). \\
 
@@
 increased fishing mortalities ($>$ 30 \% - \textcolor{blue}{N.B. Note though,
-this is consistent with the increasing trends in F, which is probably more
-related to the fact that Fs hadn't stabilised in the simulation from the
-fishing vessels "learning" the best locations - I will rerun the sims for a
-longer time (20 - 30 years)}. \\
+	this is consistent with the increasing trends in F, which is probably
+	more related to the fact that Fs hadn't stabilised in the simulation
+	from the fishing vessels "learning" the best locations - I will rerun
+	the sims for a longer time (20 - 30 years)}. \\
 
@@
 
-\section*{Appendices}
-
-\begin{table}[!ht]
-	\centering
-	\caption{Description of variables for population dynamics sub-module}
-	\label{tab: pop_variable}
-	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
-		\toprule
-		Variable & Meaning & Units \\
-		\hline
-		\multicolumn{3}{c}{\textbf{Population dynamics}}  \\
-		\hhline{===}
-		\multicolumn{3}{l}{\textit{Delay-difference model}} \\
-		\hline
-		$B_{c,d}$ & Biomass in cell $c$ and day $d$ & kg \\
-		$Z_{c,d}$ & Total mortality in cell $c$ for day $d$ & - \\
-		$R_{c, \tilde{y}}$  &Annualy recruited fish in cell &  yr\textsuperscript{-1} \\
-		$\rho$ & Brody's growth coefficient & yr\textsuperscript{-1} \\
-		$Wt_{R}$ & Weight of a fully recruited fish & kg \\
-		$Wt_{R-1}$ & Weight of a pre-recruit fish & kg \\
-		$\alpha_{d}$ & Proportion of annually recruited fish recruited
-		during day $d$ & - \\
-		\hline
-		\multicolumn{3}{l}{\textit{Baranov catch equation}} \\
-		\hline
-		$C_{c,d}$ & Catch from cell $c$ for day $d$ & kg \\
-		$F_{c,d}$ & Instantaneous rate of fishing mortality in cell $c$
-		on day $d$ & - \\
-		$M_{c,d}$ & Instantaneous rate of natural mortality in cell $c$
-		on day $d$ & - \\
-		$B_{c,d}$ & Biomass in cell $c$ on day $d$ & kg \\
-		\hline
-		\multicolumn{3}{c}{\textbf{Recruitment dynamics}} \\
-		\hhline{===}
-		$\tilde{R}_{c,d}$ & is the recruitment in cell $c$ for day $d$ & $d^{-1}$ \\
-		$B_{c,d}$ & is the Biomass in cell $c$ for day $d$ & $d^{-1}$ \\
-		$\alpha$ & the maximum recruitment rate & kg  \\
-		$\beta$ & the biomass required to produce half the maximum rate
-		of recruitment & kg \\
-		\bottomrule
-		\end{tabular}
-	\end{table}
-
-\begin{table}[!ht]
-	\centering
-	\caption{Description of variables for population movement sub-module}
-	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
-		\toprule
-		Variable & Meaning & Units \\
-		\hline
-		\multicolumn{3}{c}{\textbf{Population movement dynamics}} \\
-		\hhline{===}
-		\multicolumn{3}{l}{\textit{Habitat model}} \\
-		\hline
-		a & b & c \\
-		\hline
-		\multicolumn{3}{l}{\textit{Thermal tolerance}} \\
-		\hline
-		$T_{c,wk}$ & Temperature for cell in week & $^\circ$C \\
-		$\mu_{p}$ & Mean of the thermal tolerance for population & $^\circ$C \\
-		$\sigma^{2}_{p}$ & Standard deviation of thermal tolerance for
-		the population & $^\circ$C \\
-		\hline
-		\multicolumn{3}{l}{\textit{Population movement model}} \\
-		\hline
-		$\lambda$ & decay rate for population movement & - \\
-		$Hab^{2}_{c,p}$ & Square of habitat suitability for cell $c$ and
-		population $p$ & - \\
-		$Tol_{c,p,wk}$ & Thermal tolerance for population $p$ in cell
-		$c$ at week $wk$ & - \\
-		$d_{IJ}$ & euclidean distance between cell $I$ and cell $J$ & - \\
-		\bottomrule
-		\end{tabular}
-	\end{table}
-
-\begin{table}[!ht]
-	\centering
-	\caption{Description of variables for fleet dynamics sub-module}
-	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
-		\toprule
-		Variable & Meaning & Units \\
-		\hline
-		\multicolumn{3}{c}{\textbf{Short-term fleet dynamics}} \\
-		\hhline{===}
-		$Rev$ & Revenue from fishing tow & \euro \\
-		$L_{p}$ & Landings of population $p$ & kg \\
-		$Pr_{p}$ & Average price of population $p$ & \euro
-		\hspace{0.1cm} kg$^{-1}$ \\
-		StepL & Step length for vessel & euclidean distance \\
-		Br & Bearing & degrees \\
-		$k$ & Concentration parameter for Von mises distribution & - \\
-		$\beta_{1}$ & shape parameter for step function & - \\
-		$\beta_{2}$ & shape parameter for step function & - \\
-		$\beta_{3}$ & shape parameter for step function & - \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{table}[!ht]
-\caption{Population dynamics and movement parameter setting}
-	\begin{tabular}{ p{4cm } p{2cm} p{2cm} p{2cm} p{2cm}}
-	Parameter & Pop 1 & Pop 2 & Pop 3 & Pop 4 \\
-	\hline
-	Habitat quality & & & \\
-	\hline
-	Matérn $\nu$ & 1/0.015 & 1/0.05 & 1/0.01 & 1/0.005  \\
-	Matérn $\kappa$ & 1 & 2 & 1 & 1  \\
-	Anisotropy & 1.5,3,-3,4 & 1,2,-1,2 & 2.5,1,-1,2 & 0.1,2,-1,0.2 \\
-	Spawning areas (bound box) & 40,50,40,50; 80,90,60,70 &
-	50,60,30,40; 80,90,90,90 & 30,34,10,20; 60,70,20,30 & 50,55,80,85; 30,40,30,40 \\
-	Spawning multiplier & 10 & 10 & 10 & 10 \\
-	Movement $\lambda$ & 0.1 & 0.1 & 0.1 & 0.1 \\
-	\hline
-	Population dynamics & & & & \\
-	\hline
-	Starting Biomass & 1e5 & 2e5 & 1e5 & 1e4 \\
-	Beverton-Holt Recruit 'a' & 6 & 27 & 18 & 0.3  \\
-	Beverton-Holt Recruit 'b' & 4 & 4 & 11 & 0.5 \\
-	Beverton-Holt Recruit $\sigma^2$ & 0.7 & 0.6 & 0.7 & 0.6 \\
-	Recruit week & 13-16 & 12-16 & 14-16 & 16-20 \\
-	Spawn week & 16-18 & 16-19 & 16-18 & 18-20 \\
-	$K$ & 0.3 & 0.3 & 0.3 & 0.3 \\
-	$wt$ & 1 & 1 & 1 & 1 \\
-	$wt_{d-1}$ & 0.1 & 0.1 & 0.1 & 0.1 \\
-	M (annual) & 0.2 & 0.1 & 0.2 & 0.1 \\
-	\hline
-	Movement dynamics & & & & \\
-	\hline
-	$\mu$ & 12 & 15 & 17 & 14 \\
-	$\sigma^2$ & 8 & 9 & 7 & 10 \\
-	\hline
-\end{tabular}
-\label{tab:1}
-\end{table}
-
-\begin{table}[!ht]
-\caption{Fleet dynamics parameter setting}
-\begin{tabular}{ p{4cm } p{1cm} p{1cm} p{1cm} p{1cm} p{1cm}}
-	\hline
-	Parameter & Fleet 1 & Fleet 2 & Fleet 3 & Fleet 4 & Fleet 5 \\
-	\hline
-	Targeting preferences &&&& \\
-	\hline
-	Price Pop1 & 100 & 100 & 100 & 100 & 100 \\
-	Price Pop2 & 200 & 200 & 200 & 200 & 200 \\
-	Price Pop3 & 350 & 350 & 350 & 350 & 350 \\
-	Price Pop4 & 600 & 600 & 600 & 600 & 600 \\
-	$Q$ Pop1 & 0.01 & 0.02 & 0.02 & 0.01 & 0.01 \\
-	$Q$ Pop2 & 0.02 & 0.01 & 0.02 & 0.01 & 0.03\\
-	$Q$ Pop3 & 0.01 & 0.02 & 0.02 & 0.01 & 0.02 \\
-	$Q$ Pop4 & 0.02 & 0.01 & 0.02 & 0.05 & 0.01 \\
-	\hline
-	Exploitation dynamics &&&& \\
-	\hline
-	step function $\beta_1$ & 1 & 2 & 1 & 2 & 3 \\
-	step function $\beta_2$ & 10 & 15 & 8 & 12 & 7 \\
-	step function $\beta_3$ & Q90 & Q90 & Q85 & Q90 & Q80 \\
-	step function $rate$ & 20 & 30 & 25 & 35 & 20 \\
-	Past Knowledge & T & T & T & T & T \\
-	Past Year \& Month & T & T & T & T & T \\
-	Past Trip & T & T & T & T & T \\
-	Threshold & 0.7 & 0.7 & 0.7 & 0.7 & 0.7 \\
-	Fuel Cost & 3 & 2 & 5 & 2 & 1 \\
-	\hline
-\end{tabular}
-\label{tab:2}
-\end{table}
-
-\newpage
-\input{F_changes.tex}
-
-%%%% figures
-\begin{figure}[!ht]
-	\includegraphics[width =\linewidth]{../analysis/Data_Aggregation_space}
-	\caption{Data aggregation at different spatial resolutions}
-	\label{fig:1}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../analysis/Data_Aggregation_time}
-	\caption{Data aggregation at different temporal resolutions}
-	\label{fig:2}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../analysis/F_trendsREV}
-	\caption{Comparison of closure scenarios - F trends}
-	\label{fig:3}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width =\linewidth]{../analysis/Overview_plot_highPopRev}
-	\caption{Comparison of closure scenarios}
-	\label{fig:4}
-\end{figure}
-
 \section*{Abbreviations} Detail any unusual ones used.
@@
 
+\section*{Appendices}
+
+\input{parameter_tables.tex}
+
+\clearpage
+\footnotesize
+\input{F_changes.tex}
+
+\clearpage
+\footnotesize
+\input{F_changes_ratio.tex}
+
+%%%% figures
+\begin{figure}[!ht]
+	\includegraphics[width =\linewidth]{../analysis/Data_Aggregation_space}
+	\caption{Data aggregation at different spatial resolutions over a
+		ten year period}
+	\label{fig:1}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{../analysis/Data_Aggregation_time}
+	\caption{Data aggregation at different temporal resolutions over a
+		three year period}
+	\label{fig:2}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{../analysis/F_trendsREV}
+	\caption{Comparison of closure scenarios - Fishing mortality trends.
+		Only the scenarios based on high catch rates of population 3
+		are shown.}
+	\label{fig:3}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width =\linewidth]{../analysis/Overview_plot_highPopRev}
+	\caption{Comparison of closure scenarios. Points indicate the
+		difference between the fishing mortality pre-closure (year 29)
+		and post-closure (year 50) for population 3. Only the scenarios
+		based on high catch rates of population 3 are shown.}
+	\label{fig:4}
+\end{figure}
+
 \clearpage

### 2019-02-19 write_up/parameter_tables.tex
Text updates and include test of effectiveness of knowledge parameters

\begin{table}[!ht]
	\centering
	\caption{Description of variables for population dynamics sub-module}
	\label{tab: pop_variable}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{c}{\textbf{Population dynamics}}  \\
		\hhline{===}
		\multicolumn{3}{l}{\textit{Delay-difference model}} \\
		\hline
		$B_{c,d}$ & Biomass in cell $c$ and day $d$ & kg \\
		$Z_{c,d}$ & Total mortality in cell $c$ for day $d$ & - \\
		$R_{c, \tilde{y}}$  &Annualy recruited fish in cell &  yr\textsuperscript{-1} \\
		$\rho$ & Brody's growth coefficient & yr\textsuperscript{-1} \\
		$Wt_{R}$ & Weight of a fully recruited fish & kg \\
		$Wt_{R-1}$ & Weight of a pre-recruit fish & kg \\
		$\alpha_{d}$ & Proportion of annually recruited fish recruited
		during day $d$ & - \\
		\hline
		\multicolumn{3}{l}{\textit{Baranov catch equation}} \\
		\hline
		$C_{c,d}$ & Catch from cell $c$ for day $d$ & kg \\
		$F_{c,d}$ & Instantaneous rate of fishing mortality in cell $c$
		on day $d$ & - \\
		$M_{c,d}$ & Instantaneous rate of natural mortality in cell $c$
		on day $d$ & - \\
		$B_{c,d}$ & Biomass in cell $c$ on day $d$ & kg \\
		\hline
		\multicolumn{3}{c}{\textbf{Recruitment dynamics}} \\
		\hhline{===}
		$\tilde{R}_{c,d}$ & is the recruitment in cell $c$ for day $d$ & $d^{-1}$ \\
		$B_{c,d}$ & is the Biomass in cell $c$ for day $d$ & $d^{-1}$ \\
		$\alpha$ & the maximum recruitment rate & kg  \\
		$\beta$ & the biomass required to produce half the maximum rate
		of recruitment & kg \\
		\bottomrule
		\end{tabular}
\end{table}

\begin{table}[!ht]
	\centering
	\caption{Description of variables for population movement sub-module}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{c}{\textbf{Population movement dynamics}} \\
		\hhline{===}
		\multicolumn{3}{l}{\textit{Habitat model}} \\
		\hline
		a & b & c \\
		\hline
		\multicolumn{3}{l}{\textit{Thermal tolerance}} \\
		\hline
		$T_{c,wk}$ & Temperature for cell in week & $^\circ$C \\
		$\mu_{p}$ & Mean of the thermal tolerance for population & $^\circ$C \\
		$\sigma^{2}_{p}$ & Standard deviation of thermal tolerance for
		the population & $^\circ$C \\
		\hline
		\multicolumn{3}{l}{\textit{Population movement model}} \\
		\hline
		$\lambda$ & decay rate for population movement & - \\
		$Hab^{2}_{c,p}$ & Square of habitat suitability for cell $c$ and
		population $p$ & - \\
		$Tol_{c,p,wk}$ & Thermal tolerance for population $p$ in cell
		$c$ at week $wk$ & - \\
		$d_{IJ}$ & euclidean distance between cell $I$ and cell $J$ & - \\
		\bottomrule
		\end{tabular}
	\end{table}

\begin{table}[!ht]
	\centering
	\caption{Description of variables for fleet dynamics sub-module}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{c}{\textbf{Short-term fleet dynamics}} \\
		\hhline{===}
		$Rev$ & Revenue from fishing tow & \euro \\
		$L_{p}$ & Landings of population $p$ & kg \\
		$Pr_{p}$ & Average price of population $p$ & \euro
		\hspace{0.1cm} kg$^{-1}$ \\
		StepL & Step length for vessel & euclidean distance \\
		Br & Bearing & degrees \\
		$k$ & Concentration parameter for Von mises distribution & - \\
		$\beta_{1}$ & shape parameter for step function & - \\
		$\beta_{2}$ & shape parameter for step function & - \\
		$\beta_{3}$ & shape parameter for step function & - \\
		\bottomrule
	\end{tabular}
\end{table}

\begin{table}[!ht]
\caption{Population dynamics and movement parameter setting}
	\begin{tabular}{ p{4cm } p{2cm} p{2cm} p{2cm} p{2cm}}
	Parameter & Pop 1 & Pop 2 & Pop 3 & Pop 4 \\
	\hline
	Habitat quality & & & \\
	\hline
	Matérn $\nu$ & 1/0.015 & 1/0.05 & 1/0.01 & 1/0.005  \\
	Matérn $\kappa$ & 1 & 2 & 1 & 1  \\
	Anisotropy & 1.5,3,-3,4 & 1,2,-1,2 & 2.5,1,-1,2 & 0.1,2,-1,0.2 \\
	Spawning areas (bound box) & 40,50,40,50; 80,90,60,70 &
	50,60,30,40; 80,90,90,90 & 30,34,10,20; 60,70,20,30 & 50,55,80,85; 30,40,30,40 \\
	Spawning multiplier & 10 & 10 & 10 & 10 \\
	Movement $\lambda$ & 0.1 & 0.1 & 0.1 & 0.1 \\
	\hline
	Population dynamics & & & & \\
	\hline
	Starting Biomass & 1e5 & 2e5 & 1e5 & 1e4 \\
	Beverton-Holt Recruit 'a' & 6 & 27 & 18 & 0.3  \\
	Beverton-Holt Recruit 'b' & 4 & 4 & 11 & 0.5 \\
	Beverton-Holt Recruit $\sigma^2$ & 0.7 & 0.6 & 0.7 & 0.6 \\
	Recruit week & 13-16 & 12-16 & 14-16 & 16-20 \\
	Spawn week & 16-18 & 16-19 & 16-18 & 18-20 \\
	$K$ & 0.3 & 0.3 & 0.3 & 0.3 \\
	$wt$ & 1 & 1 & 1 & 1 \\
	$wt_{d-1}$ & 0.1 & 0.1 & 0.1 & 0.1 \\
	M (annual) & 0.2 & 0.1 & 0.2 & 0.1 \\
	\hline
	Movement dynamics & & & & \\
	\hline
	$\mu$ & 12 & 15 & 17 & 14 \\
	$\sigma^2$ & 8 & 9 & 7 & 10 \\
	\hline
\end{tabular}
\label{tab:1}
\end{table}

\begin{table}[!ht]
\caption{Fleet dynamics parameter setting}
\begin{tabular}{ p{4cm } p{1cm} p{1cm} p{1cm} p{1cm} p{1cm}}
	\hline
	Parameter & Fleet 1 & Fleet 2 & Fleet 3 & Fleet 4 & Fleet 5 \\
	\hline
	Targeting preferences &&&& \\
	\hline
	Price Pop1 & 100 & 100 & 100 & 100 & 100 \\
	Price Pop2 & 200 & 200 & 200 & 200 & 200 \\
	Price Pop3 & 350 & 350 & 350 & 350 & 350 \\
	Price Pop4 & 600 & 600 & 600 & 600 & 600 \\
	$Q$ Pop1 & 0.01 & 0.02 & 0.02 & 0.01 & 0.01 \\
	$Q$ Pop2 & 0.02 & 0.01 & 0.02 & 0.01 & 0.03\\
	$Q$ Pop3 & 0.01 & 0.02 & 0.02 & 0.01 & 0.02 \\
	$Q$ Pop4 & 0.02 & 0.01 & 0.02 & 0.05 & 0.01 \\
	\hline
	Exploitation dynamics &&&& \\
	\hline
	step function $\beta_1$ & 1 & 2 & 1 & 2 & 3 \\
	step function $\beta_2$ & 10 & 15 & 8 & 12 & 7 \\
	step function $\beta_3$ & Q90 & Q90 & Q85 & Q90 & Q80 \\
	step function $rate$ & 20 & 30 & 25 & 35 & 20 \\
	Past Knowledge & T & T & T & T & T \\
	Past Year \& Month & T & T & T & T & T \\
	Past Trip & T & T & T & T & T \\
	Threshold & 0.7 & 0.7 & 0.7 & 0.7 & 0.7 \\
	Fuel Cost & 3 & 2 & 5 & 2 & 1 \\
	\hline
\end{tabular}
\label{tab:2}
\end{table}

### 2019-02-19 analysis/Plots_Combined.R

@@ -3,6 +3,7 @@
 #######################################################
 
 library(MixFishSim)
+library(tidyverse)
 
 ## Load the scenarios
 load('scenarios.RData')
@@ -60,9 +61,6 @@ gc()
 
 #combined_pop$scenario <- rep(runs, each = rows)
 
-library(ggplot2)
-library(dplyr)
-
 ## Make results annual
 
 results_df_an1 <- combined_pop %>% filter(metric == "Bio", day == 1) %>% 
@@ -107,7 +105,9 @@ library(ggrepel)
 
 ggplot(filter(combined, basis == 'high_pop', metric == "F"), aes(x = data_type, y = diff)) + geom_point(aes(colour = resolution, shape = timescale), size = 4) + 
 	facet_wrap(pop~.) + #geom_text_repel(aes(data_type, diff, label = paste(timescale,"," ,resolution, sep = "")), direction = "both") +
-	coord_flip() + ylab("Difference before and after closure in % F") + theme_bw() + facet_grid(pop~.) + geom_hline(yintercept = 0, linetype = "dashed") + ggtitle("Effectiveness of closure in reducing Fishing mortality") + scale_colour_gradient2(high = "red", mid = "orange", low = "yellow") +
+	coord_flip() + ylab("Difference before and after closure in % F") + xlab("Data source") +
+	theme_bw() + facet_grid(pop~.) + geom_hline(yintercept = 0, linetype = "dashed") + ggtitle("Effectiveness of closure in reducing Fishing mortality") +
+	scale_colour_gradient2(high = "red", mid = "orange", low = "yellow") +
 	scale_shape_discrete(solid = F)
 
 ggsave('Overview_plot_highPopRev.png', width = 12, height = 4)
@@ -137,9 +137,22 @@ Fs <- filter(combined, metric == "F", basis == "high_pop", pop == "spp_3")
 Fs[,c(4:6)] <- round(Fs[,c(4:6)], 2)
 Fs <- Fs[order(Fs$pop, Fs$diff),]
 
-print(xtable(Fs, digits = 2, caption = "Fishing mortality effects of the closure scenarios", label = "tab:6"), caption.placement = "top", file =
-	     file.path("..","write_up", "F_changes.tex"),include.rownames =
-	     FALSE, tabular.environment= "longtable", floating = FALSE)
+print(xtable(Fs, digits = 2, caption = "Fishing mortality effects of the
[…]

### 2019-02-19 tests/KnowledgeTest/FisherKnowledgeTest.R

@@ -1,0 +1,219 @@
+############################################################################
+## Code to test efficiency of past knowledge over CRW 
+#############################################################################
+#######################
+#
+## Conditioning
+#
+######################
+
+library(MixFishSim)
+library(tidyverse)
+
+set.seed(123, kind = "L'Ecuyer-CMRG")
+
+## initialise the simulation
+
+sim <- init_sim(nrows = 20, ncols = 20, n_years = 10, n_tows_day = 4, n_days_wk_fished = 5,
+     n_fleets = 1, n_vessels = 1, n_species = 4, move_freq = 2)
+
+## create the suitable habitat for each species
+
+hab <- create_hab(sim_init = sim,
+		  spp.ctrl = list(
+           'spp.1' = list('nu' = 1/0.015, var = 1, scale = 10, Aniso =
+           matrix(nc=2, c(1.5, 3, -3, 4))),
+           'spp.2' = list('nu' = 1/0.05, var = 2, scale = 12, Aniso =
+           matrix(nc=2, c(1, 2, -1, 2))),
+	   'spp.3' = list('nu' = 1/0.01, var = 1, scale = 12, Aniso =
+           matrix(nc=2, c(2.5, 1, -1, 2))),
+           'spp.4' = list('nu' = 1/0.005, var = 1, scale = 8, Aniso =
+           matrix(nc=2, c(0.1, 2, -1, 0.02)))
+				  ),
+		  spawn_areas = list("spp1" = list(area1 = c(4, 5, 4, 5), area2 =
+				   c(8, 9, 6, 7)), 
+		 "spp2" = list(area1 = c(2, 4,  0, 2), area2 = c(8, 10, 9, 10)),
+		 "spp3" = list(area1 = c(2, 3, 1, 2), area2 = c(6, 7, 9, 10)),
+		 "spp4" = list(area1 = c(5, 6, 8, 9), area2 = c(3, 4, 3, 4))
+		 ),
+		spwn_mult = 10, plot.dist = TRUE, plot.file = getwd())
+
+## Look at overlaps of species habitats
+
+over<-hab[["hab"]]
+
+for(i in 1:4) {
+x<- over[[i]]
+x[which(x>0)] <-1
+over[[i]] <- x
+}
+
+plot <- F
+if(plot) {
[…]

### 2019-02-24 write_up/mixfishsim_ecolmod.tex
Text update

@@
 
+\underline{The why:} \\
+
+Dynamic management requires understanding of the interaction between fishers
+and heterogeneously distributed resources. \\
+
+Difficult because of a lack of knowledge of the scale interactions important at
+and detailed spatiotemp knowledge. \\
+
+\underline{The what:}  \\
+
+We develop a simulation model to understand scale.\\
+
+Detail of sim model important -- highly resolved, IBM. Make comparison to other
+models, e.g. DISPLACE, POSEIDON...\\
+
+Real world spatiotemp closures rarely been able to consider these issues /
+designed with these issues fully in mind - NS cod closures, plaice and trevose
+box... \\
+
+Use of commercial data increasing - likely to become more important in future.
+Also collaborative approach with industry, e.g. hotspot mapping, spatiotemp
+advice... \\
+
+\underline{The what it shows:} \\
+
+Our results show commercial data can be useful at right scale and resolution -
+depends on scale of process: pop movement etc... Important to consider how
+fishers interact / adapt to changes with the resoruce and mgmt. \\
+
+Closure scenarios demonstrate potential tor reduce F - not as high as with real
+pop, but good.  Make link to other studies -- read up on these. \\
+
+\underline{The what next:} \\
+
+Other potential uses of the model \\
+
+Survey design \\
+
+commercial index standardization methods \\
+
+Sampling scheme design \\
+
+Testing fleet dynamics models at an aggregated level \\
+
+Bigger picture stuff::  LO, increasing desire for more nuanced spatiotemp
+mgmt... Wider applicability: birds, wildlife ??
+
 \section{Conclusions}
+
+Study shows ....\\
+
+This is important because .... \\
+
+How we might apply this in future .... \\
 

### 2019-04-13 write_up/mixfishsim_ecolmod.tex
Discussion

@@
 distributed in space and time with varying knowledge of species distributions
-using species-unselective fishing gear. \added[id=PD]{In doing so} fisheries
+using species non-selective fishing gear. \added[id=PD]{In doing so} fisheries
 \deleted[id=PD]{that}catch an assemblage of species
@@
 	when managed by single-species quotas can end up}
-discard\deleted[id=JJ]{ing} overquota catch \added[id=JJ]{when managed by
+discard\deleted[id=JJ]{ing} over-quota catch \added[id=JJ]{when managed by
 	single species quotas and fishers exhaust or more quota, may} lead to
@@
 follows (the full parameter list is detailed in Table \ref{tab: pop_variable}):
-\begin{equation*}
+\begin{equation}
 	\begin{split}
@@
 	\end{split}
-\end{equation*}
+\end{equation}
 where $\rho$ is Brody's coefficient, shown to be approximately equal to
@@
 the Baranov catch equation \citep{Hilborn1992b} for $F_{c,d}$:
-\begin{equation*}
+\begin{equation}
 C_{c,d} = \frac{F_{c,d}}{F_{c,d} + M_{c,d}} * (1 - e^{-(F_{c,d} + M_{c,d})}) *
 B_{c,d}
-\end{equation*}
+\end{equation}
 where $C_{c,d}$ is the summed catch from the fishing model across all fleets
@@
 \citep{Beverton1957}: 
-\begin{equation*}
+\begin{equation}
 	\begin{split}
@@
 	\end{split}
-\end{equation*}
+\end{equation}
 Where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
@@
 processes, or a stochastic Ricker form \citep{Ricker1954}:
-\begin{equation*}
+\begin{equation}
 	\begin{split}
@@
 	\end{split}
-\end{equation*}
+\end{equation}
 where $\alpha$ is the maximum productivity per spawner and $\beta$ the density
@@
 relationship: 
-\begin{equation*}
+\begin{equation}
 	StepL = e^{log(\beta_{1}) + log(\beta_{2}) -
 		(log(\frac{\beta_{1}}{\beta_{3}}))} * Rev
-\end{equation*}\todo{\added[id=JJ]{So
+\end{equation}\todo{\added[id=JJ]{So
 			step length increases with increasingly gross
@@
 (x1,y1) to (x2, y2) is defined by:
-\begin{equation*}
+\begin{equation}
 	\begin{split}
@@
 	\end{split}
-\end{equation*}
+\end{equation}
 where $k$ the concentration parameter from the von \replaced[id=JJ]{M}{m}ises
@@
 The finer spatial grid for the real population (top left) and commercial data
-(top middle) show similar patterns, though there are unsampled gaps in the
-commercial data from a lack of fishing activity (particularly in the lower left
-part of the sampling domain). The survey data at this spatial resolution shows
-very sparse information about the spatial distributions of the populations. The
-slightly aggregated data on a 5 x 5 grid shows similar patterns, and while
-losing some of the spatial detail there remains good consistency between the
-'real population' and the commercial data. Survey data starts to pick out some
-of the similar patterns as the other data sources, but lacks coverage. The
-spatial catch information on a 10 x 10 and 20 x 20 grid loses a significant
-amount of information about the spatial resolutions for all data sources, and
-some differences between the survey, commercial and 'real population' data
-emerge. \\
+(top middle) show visually similar patterns, though there are large unsampled
+areas in the commercial data from a lack of fishing activity (particularly in
+the lower left part of the sampling domain). The survey data at this spatial
+resolution shows very sparse information about the spatial distributions of the
+populations. The slightly aggregated data on a 5 x 5 grid shows similar
+patterns and, while losing some of the spatial detail, there remains good
+consistency between the 'real population' and the commercial data. Survey data
+starts to pick out some of the similar patterns as the other data sources, but
+lacks coverage. The spatial catch information on a 10 x 10 and 20 x 20 grid
+loses a significant amount of information about the spatial resolutions for all
+data sources, and some differences between the survey, commercial and 'real
+population' data emerge. \\
 
@@
 commercial sampling across a month compared to a week.i Commercial data used at
-an annual timestep was ineffective in bringing fishing mortality down for
+an annual time-step was ineffective in bringing fishing mortality down for
 species 1. \\
@@
 important than the temporal disaggregation of the commercial data, except when
-its used at an annual timeframe, which is the scenario that gave the worst
+its used at an annual time-frame, which is the scenario that gave the worst
 results.
@@
 
-\underline{The why:} \\
+Our study evaluates the importance of data scaling and considers potential
+biases introduced through data aggregation when using commercial fisheries
+logbooks and Vessel Monitoring Systems for inference on spatio-temporal
+dynamics in fisheries. Understanding how fishers exploit multiple
+heterogeneously distributed fish populations with different catch limits or
+conservation status requires detailed understanding of the overlap of
+resources; this is difficult to achieve using conventional modelling approaches
+due to the patchy and irregular nature of fisheries resulting in preferential
+sampling \cite{Martinez-Minaya2018}. Often data is aggregated or extrapolated
+which requires assumptions about the spatial and temporal scale of processes.
+Our study explores the assumptions behind such aggregation and preferential
+sampling to identify potential impacts on management advice. With modern
+management approaches increasingly employing more nuanced spatio-temporal
+approaches in order to maximise productivity while taking account of both the
+biological and human processes operating on different time-frames
+\cite{Dunn2016}, understanding assumptions behind the data used is vital to
+ensure measures are effective. \\
 
-Dynamic management requires understanding of the interaction between fishers
-and heterogeneously distributed resources. \\
+We employ a simulation approach to model each of the population and fishery
+processes in a hypothetical 'mixed fishery', allowing us to i) evaluate the
+consequences of different aggregation assumptions on our understanding of the
+spatio-temporal distribution of the underlying fish populations, and ii)
+evaluate the effectiveness of a spatial closure given those assumptions. Our
+approach captures fine scale population and fishery dynamics not usually
+considered (although see \cite{Bastardie2010, Bailey2018}) which offers the
+advantage that larger scale fishery patterns are emergent properties of the
+system rather than the result of a statistical modelling framework. \\
 
-Difficult because of a lack of knowledge of the scale interactions important at
-and detailed spatiotemp knowledge. \\
+Our results show commercial data can provide at right scale and resolution -
+depends on scale of process: pop movement etc... Important to consider how
+fishers interact / adapt to changes with the resource and mgmt. \\
 
-\underline{The what:}  \\
+Closure scenarios demonstrate potential tor reduce F - not as high as with real
+pop, but good.  Make link to other studies -- read up on these. \\
 
-We develop a simulation model to understand scale.\\
-
-Detail of sim model important -- highly resolved, IBM. Make comparison to other
-models, e.g. DISPLACE, POSEIDON...\\
+\underline{The what next:} \\
 
@@
 advice... \\
-
-\underline{The what it shows:} \\
-
-Our results show commercial data can be useful at right scale and resolution -
-depends on scale of process: pop movement etc... Important to consider how
-fishers interact / adapt to changes with the resoruce and mgmt. \\
-
-Closure scenarios demonstrate potential tor reduce F - not as high as with real
-pop, but good.  Make link to other studies -- read up on these. \\
-
-\underline{The what next:} \\
 
@@
 \begin{figure}[!ht]
-	\includegraphics[width =\linewidth]{../analysis/Data_Aggregation_space}
+	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_space_Rev}
 	\caption{Data aggregation at different spatial resolutions over a
@@
 \begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../analysis/Data_Aggregation_time}
+	\includegraphics[width =\linewidth]{../analysis/Data_Aggregation_time_Rev}
 	\caption{Data aggregation at different temporal resolutions over a

### 2019-04-14 write_up/mixfishsim_ecolmod.tex
Discussion update

@@
 Our study evaluates the importance of data scaling and considers potential
-biases introduced through data aggregation when using commercial fisheries
-logbooks and Vessel Monitoring Systems for inference on spatio-temporal
-dynamics in fisheries. Understanding how fishers exploit multiple
-heterogeneously distributed fish populations with different catch limits or
-conservation status requires detailed understanding of the overlap of
-resources; this is difficult to achieve using conventional modelling approaches
-due to the patchy and irregular nature of fisheries resulting in preferential
-sampling \cite{Martinez-Minaya2018}. Often data is aggregated or extrapolated
-which requires assumptions about the spatial and temporal scale of processes.
-Our study explores the assumptions behind such aggregation and preferential
-sampling to identify potential impacts on management advice. With modern
-management approaches increasingly employing more nuanced spatio-temporal
-approaches in order to maximise productivity while taking account of both the
-biological and human processes operating on different time-frames
-\cite{Dunn2016}, understanding assumptions behind the data used is vital to
-ensure measures are effective. \\
+biases introduced through data aggregation when using commercial fisheries data
+for inference on spatio-temporal dynamics in fisheries. Understanding how
+fishers exploit multiple heterogeneously distributed fish populations with
+different catch limits or conservation status requires detailed understanding
+of the overlap of resources; this is difficult to achieve using conventional
+modelling approaches due to the patchy and irregular nature of fisheries
+resulting in preferential sampling \cite{Martinez-Minaya2018}. Often data is
+aggregated or extrapolated which requires assumptions about the spatial and
+temporal scale of processes. Our study explores the assumptions behind such
+aggregation and preferential sampling to identify potential impacts on
+management advice. With modern management approaches increasingly employing
+more nuanced spatio-temporal approaches in order to maximise productivity while
+taking account of both the biological and human processes operating on
+different time-frames \cite{Dunn2016}, understanding assumptions behind the
+data used - increasingly a combination of logbook and positional information
+from vessel monitoring systems - is vital to ensure measures are effective. \\
 

### 2019-04-28 write_up/mixfishsim_ecolmod.tex
Text update

--- 2019-04-13 write_up/mixfishsim_ecolmod.tex
@@
 which I'd posit is due to the increase amount of data available from the
-commercial sampling across a month compared to a week.i Commercial data used at
+commercial sampling across a month compared to a week. Commercial data used at
 an annual time-step was ineffective in bringing fishing mortality down for
@@
 
-Our study evaluates the importance of data scaling and considers potential
-biases introduced through data aggregation when using commercial fisheries
-logbooks and Vessel Monitoring Systems for inference on spatio-temporal
-dynamics in fisheries. Understanding how fishers exploit multiple
-heterogeneously distributed fish populations with different catch limits or
-conservation status requires detailed understanding of the overlap of
+Our study evaluates the importance of data scaling and considers potential bias
+introduced through data aggregation when using commercial fisheries data to
+infer spatio-temporal dynamics in fisheries. Understanding how fishers exploit
+multiple heterogeneously distributed fish populations with different catch
+limits or conservation status requires detailed understanding of the overlap of
 resources; this is difficult to achieve using conventional modelling approaches
-due to the patchy and irregular nature of fisheries resulting in preferential
-sampling \cite{Martinez-Minaya2018}. Often data is aggregated or extrapolated
-which requires assumptions about the spatial and temporal scale of processes.
-Our study explores the assumptions behind such aggregation and preferential
+due to species targeting in fisheries resulting in preferential sampling
+\cite{Martinez-Minaya2018}. Often data is aggregated or extrapolated which
+requires assumptions about the spatial and temporal scale of processes.  Our
+study explores the assumptions behind such aggregation and preferential
 sampling to identify potential impacts on management advice. With modern
@@
 biological and human processes operating on different time-frames
-\cite{Dunn2016}, understanding assumptions behind the data used is vital to
-ensure measures are effective. \\
+\cite{Dunn2016}, understanding assumptions behind the data used - increasingly
+a combination of logbook and positional information from vessel monitoring
+systems - is vital to ensure measures are effective. \\
 

### 2019-05-28 write_up/mixfishsim_ecolmod.tex
Correct temporal plot

@@
 yearly closures (blue lines) at all spatial resolutions, which resulted in
-increased fishing mortalities ($>$ 30 \% - \textcolor{blue}{N.B. Note though,
-	this is consistent with the increasing trends in F, which is probably
-	more related to the fact that Fs hadn't stabilised in the simulation
-	from the fishing vessels "learning" the best locations - I will rerun
-	the sims for a longer time (20 - 30 years)}. \\
+increased fishing mortalities ($>$ 30 \%). \\
 

### 2019-05-28 write_up/mixfishsim_ecolmod.tex
Revisions

@@
 Figure \ref{fig:1}, which represents the aggregation of catch from each of the
-data sources over a ten year period (to average seasonal patterns) at different
+data sources over a ten-year period (to average seasonal patterns) at different
 spatial resolutions. \\
@@
 Figure \ref{fig:2} shows the consequences of different temporal aggregations of
-the data over a three year period, with 156 weekly (top), 36 monthly (middle)
-and 3 yearly (bottom) catch compositions from across an aggregated 20 x 20
-area. \\
+the data over a ten-year period, with weekly (top), monthly (middle) and yearly
+(bottom) catch compositions from across an aggregated 20 x 20 area. \\
 
@@
 	\caption{Data aggregation at different temporal resolutions over a
-		three year period}
+		ten-year period}
 	\label{fig:2}

### 2019-06-25 write_up/Process_model.tex
Text updates and reworking plots

@@
 \end{tikzpicture}
-\caption{Overview Schematic of simulation model. The blue boxes indicate fleet
+\caption{Schematic overview of the simulation model. Blue boxes indicate fleet
 	dynamics processes, the green boxes population dynamics processes while

### 2019-06-25 write_up/mixfishsim_ecolmod.tex
Text updates and reworking plots

@@
 \usepackage{longtable}
+
+\usepackage{enumitem}
 
@@
 draw inference on the underlying population structures. We compare this
-inference to i) a simulated fixed-site sampling design commonly used for
-fisheries monitoring purposes, and ii) the true underlying population
-structures input to the simulation. We use the results to establish the
-potential and limitations of fishery-dependent data in providing a robust
-picture of spatiotemporal distributions. Finally, we simulate an area closure
-based on areas defined from the known ("real-population") distribution,
-commercial catch data and survey data at different temporal and spatial
-resolutions and assess their effectiveness on reducing catches of a fish
-population. \\
+inference to a simulated fixed-site sampling design commonly used for fisheries
+monitoring purposes and the true underlying population structures input to the
+simulation. We i) use the results to establish the potential and limitations of
+fishery-dependent data in providing a robust picture of spatiotemporal
+distributions; and ii) simulate an area closure based on areas defined from the
+different data sources at a range of temporal and spatial resolutions and
+assess their effectiveness on reducing catches of a fish population. \\
 
@@
 discard\deleted[id=JJ]{ing} over-quota catch \added[id=JJ]{when managed by
-	single species quotas and fishers exhaust or more quota, may} lead to
-overexploitation of fish populations \added[id=JJ]{\citep{Ulrich2011a,
+	single species quotas and fishers exhaust one or more quota which may}
+lead to overexploitation of fish populations \added[id=JJ]{\citep{Ulrich2011a,
 		Batsleer2015}}.  \added[id=JJ]{This discarding of fish in
-	excess of quota hampers the ability to limit fishing mortality to
-	within sustainable limits \citep{Alverson1994, Crowder1998,
-		Rijnsdorp2007}} \deleted[id=PD]{; reducing discarding is
-	crucial}and the ability to manage for the biological and economic
-sustainability of fisheries\deleted[id=JJ]{ and implementation of an ecosystem
-	approach to fisheries}. As such, there is increasing interest in
-technical solutions such as gear and spatial closures as ways of
-\replaced[id=PD]{reducing unwanted catch}{avoiding discard\added[id=JJ]{ing of
-		fish}}\citep{Kennelly2002, Catchpole2008, Bellido2011}.  \\
+	excess of quota limits the ability to maintain fishing mortality within
+	sustainable limits \citep{Alverson1994, Crowder1998, Rijnsdorp2007}}
+\deleted[id=PD]{; reducing discarding is crucial}and the ability to manage for
+the biological and economic sustainability of fisheries\deleted[id=JJ]{ and
+	implementation of an ecosystem approach to fisheries}. As such, there
+is increasing interest in technical solutions such as gear and spatial closures
+as measures to \replaced[id=PD]{reduce unwanted catch}{avoiding
+	discard\added[id=JJ]{ing of fish}}\citep{Kennelly2002, Catchpole2008,
+	Bellido2011}.  \\
 
@@
 	management as a tools} been proposed as a method to reduce discards
-\added[id=PD]{\citep{Holmes2011, Little2014, Dunn2014a}}. However,
-\deleted[id=PD]{its} implementation of avoidance measures is hampered by lack
-of knowledge of fish and fishery spatiotemporal dynamics and understanding of
-the scale at which processes are important for management. Understanding the
-correct scale for spatial measures is crucial in order to implement measures at
-a resolution that ensures effective management \citep{Dunn2016} while
-minimising economic impact.  For example, a scale that promotes species
-avoidance for vulnerable or low quota species while allowing continuance of
-sustainable fisheries for available quota species.\\
+\added[id=PD]{\citep{Holmes2011, Little2014, Dunn2014a}}.  \deleted[id=PD]{its}
+implementation of avoidance measures is, however, restricted by lack of
+knowledge of fish and fishery spatiotemporal dynamics and understanding of the
+scale at which processes become important for management. Understanding the
+correct scale for spatial measures is crucial for implementation at a
+resolution that ensures effective management \citep{Dunn2016} while minimising
+economic impact.  For example, a scale that promotes species avoidance for
+vulnerable or low quota species while allowing continuance of sustainable
+fisheries for available quota species.\\
 
@@
 \citep{Lee2010, Bastardie2010, Gerritsen2012, Mateo2016} and more real-time
-spatial management has been possible \citep[e.g.][]{Holmes2011}.  However, such
-information is derived from an inherently biased sampling programme, targeted
-fishing. \deleted[id=PD]{ Further, fishers generally only recorded landings
-	(not catch) on a daily basis\todo{\added[id=JJ]{Its not clear what the
-			problem is: landings collected on daily basis or
-			landings recorded rather than catch}}.  This leads to
-	questions about the validity of inference that can be drawn from
+spatial management has been possible \citep[e.g.][]{Holmes2011}.  Such
+information is, however, derived from an inherently biased sampling programme,
+targeted fishing. \deleted[id=PD]{ Further, fishers generally only recorded
+	landings (not catch) on a daily basis\todo{\added[id=JJ]{Its not clear
+			what the problem is: landings collected on daily basis
+			or landings recorded rather than catch}}.  This leads
+	to questions about the validity of inference that can be drawn from
 	landings data assigned to VMS activity pings.}\todo{\added[id=JJ]{This
@@
 
-In order to understand \replaced[id=PD]{the consequences of using}{challenges
-	that face} VMS-linked landings to draw inference on the underlying
-population structure we develop a simulation model where population dynamics
-are highly-resolved in space and time\replaced[id=PD]{. Being}{ and are}
-known \added[id=PD]{directly} rather than inferred from sampling or commercial
-catch\added[id=PD]{, we can use the population model to evaluate how inference from
-	fisheries-dependent and fisheries independent sampling relates to the
-	real population structure}. \replaced[id=PD]{In our model system
-	p}{P}opulation movement is driven by random (diffusive) and directed
-(advective) processes and we incorporate characterisation of a number of
-different fishing \added[id=PD]{fleet dynamics} exploiting four fish populations
-with different spatial and population demographics.\\
-
-Using our model we simulate \replaced[id=PD]{50}{40} years of exploitation of
-the fish populations. \replaced[id=PD]{We}{ and} use the
-results\deleted[id=PD]{ from the fishing model:}
+\replaced[id=PD]{We ask two fundamental questions regarding spatiotemporal
+	inference derived from observational data:}{ and use the
+	results}\deleted[id=PD]{ from the fishing model:}
 
 \begin{enumerate}
-	\item to understand how sampling-derived data reflects the underlying
-		population structures. We compare at different spatial and
-		temporal aggregations of the simulated population distributions
-		to: 
-		\begin{enumerate}
-			\item the inferred population from a stratified
-				fixed-site sampling survey design commonly used
-				for fisheries monitoring purposes, otherwise
-				know as a fisheries-independent survey,
-			\item the inferred population from our
-				fishery-dependent model which includes
-				fishery-induced sampling dynamics.\\
-		\end{enumerate}
-	\item to understand the impact of data aggregation and data source on
-		spatial fisheries management measures we simulate a fishery
-		closure to protect a species based on different spatial and
-		temporal data aggregations:
-		\begin{enumerate}
-			\item as if the real spatial population structure were
-				known,
-			\item the fishery-independent inferred population
-				structure
-			\item the fishery-dependent inferred population
-				structure
-		\end{enumerate}
-		We evaluate the theoretical "benefit" to the population of the
-		closure(s), the effect on the other three populations and
-		fishery catch.\todo{\added[id=JJ]{If the paper has two goals
-				this should be clear from the start, but may be
-				better over 2 MSs}\added[id=PD]{I would like to
-				keep both parts, but have made clearer in how
-				its set out. The closure scenarios form
-				validation of the data aggregation, rather than
-				effectiveness of the closures themselves - so
-				its a continuation of the same question in my
-				eyes}}\deleted[id=PD]{.  Further, we extend our
-			analysis to a range of spatial and temporal scales to
-			assess the impact of these processes on the success of
-			the management measure.}\\
-\end{enumerate}
+	\item How does sampling-derived data reflects the underlying population
+		structures? 	
+	\item How does data aggregation and source impact on monitoring spatial
+		fisheries management measures ? \end{enumerate}
+
+We i) develop a simulation model where population dynamics are highly-resolved
+in space and time to answer these questions\replaced[id=PD]{. Being}{ and are}
+known \added[id=PD]{directly} rather than inferred from sampling or commercial
+catch\added[id=PD]{, we can use the population model to evaluate how inference
+	from fisheries-dependent and fisheries independent sampling relates to
+	the real population structure}. We ii) compare at different spatial and
+temporal aggregations of the simulated population distributions to samples from
+fisheries-dependent and fisheries independent catches. We then iii) simulate a
+fishery closure to protect a species based on different spatial and temporal
+data aggregations. \\
+
+We compare the catch composition from fisheries independent and dependent
+sampling against the real population composition, as well as the theoretical
+"benefit" to the population spatial closures using the different data sources.
+We use these evaluations to draw inference on the utility of commercial data in
+supporting management decisions. \todo{\added[id=JJ]{If the paper has two goals
+		this should be clear from the start, but may be better over 2
+		MSs}\added[id=PD]{I would like to keep both parts, but have
+		made clearer in how its set out.  The closure scenarios form
+		validation of the data aggregation, rather than effectiveness
+		of the closures themselves - so its a continuation of the same
+		question in my eyes}}\deleted[id=PD]{.  Further, we extend our
+	analysis to a range of spatial and temporal scales to assess the impact
+	of these processes on the success of the management measure.}\\
 
@@
 movement occurs on a weekly time-step\replaced[id=PD]{. R}{, while r}ecruitment
-\replaced[id=PD]{takes place}{occurs} periodcally each year for a set time
+\replaced[id=PD]{takes place}{occurs} periodically each year for a set time
 \replaced[id=PD]{duration}{period (e.g. 3 weeks)} specified for each
 population\deleted[id=PD]{.}\added[id=PD]{, while the fishing module operates
-	on a tow-by-tow basis (i.e. multiple events a day)}.  The simulation
-framework is implemented in the statistical software package R
-\citep{RCoreTeam2017} \replaced[id=PD]{and}{;} available as an R package from
-the authors github site (\url{www.github.com/pdolder/MixFishSim}).\\
-
+	on a tow-by-tow basis (i.e. multiple events a day)}.  
 \deleted[id=PD]{Here we describe each of the model components; 1) Population
@@
 	fishery dynamics.}
+
+\replaced[id=PD]{In our model system p}{P}opulation movement is driven by
+random (diffusive) and directed (advective) processes and we incorporate
+characterisation of a number of different fishing \added[id=PD]{fleet dynamics}
+exploiting four fish populations with different spatial and population
+demographics. We use the model to simulate \replaced[id=PD]{50}{40} years of
+exploitation of the fish populations.
 
@@
 	Dichmont2003} occurring at a daily time-step. \added[id=PD]{A daily
-	time-step was chosen as to discretise continuous population processes
+	time-step was chosen to discretise continuous population processes
 	on a biologically relevant and computationally tractable timescale.}
@@
 separately as a function of previous recruited biomass, intrinsic population
-growth and recruitment. Biomass for each cell is incremented each day as
+growth and recruitment. Biomass for each cell $c$ is incremented each day $d$ as
 follows (the full parameter list is detailed in Table \ref{tab: pop_variable}):
@@
 $e^{-K}$ when $K$ is the growth rate from a von Bertalanffy logistic growth
-model \citep{Schnute1985}. $Wt_{R-1}$ is the weight of fish prior to
-recruitment, while $Wt_{R}$ is the recruited weight. $\alpha_{d}$ represents
-the proportion of fish recruited during that day for the year, while
+model \citep{Schnute1985}. $Wt_{R-1}$ is the average weight of fish prior to
+recruitment, while $Wt_{R}$ is the average recruited weight. $\alpha_{d}$
+represents the proportion of fish recruited during that day for the year, while
 $R_{c,\tilde{y}}$ is the annual recruits in cell $c$ for year $y$. \\
@@
 	\begin{split}
-	\bar{R}_{c,d} = & \frac{(\alpha * B_{c,d})}{(\beta + B_{c,d})} \\
-	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\log(\sigma^2))]
+	\bar{R}_{c,d} = & \frac{(\alpha * S_{c,d})}{(\beta + S_{c,d})} \\
+	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\sigma^2)]
 	\end{split}
@@
 Where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
-biomass (SSB) required to produce half the maximum, $B$ current SSB and
-$\sigma^2$ the variability in the recruitment due to stochastic
+biomass (SSB) required to produce half the maximum stock size, $S$ current
+stock size and $\sigma^2$ the variability in the recruitment due to stochastic
 processes, or a stochastic Ricker form \citep{Ricker1954}:
@@
 habitat suitability for cell $J$ and population $p$, with $Tol_{J,p,wk}$ the
-temperature tolerance for cell $J$ by population $p$ in week $wk$.\\
+temperature tolerance for cell $J$ by population $p$ in week $wk$ (see
+below).\\
 
@@
 
-Where several fishing vessels are exploiting the same fish population
-competition is known to play an important role in local distribution of fishing
-effort \citep{Gillis1998}. If several vessels are fishing on the same patch of
-fish, local depletion and interference \added[id=JJ]{competition} will affect
-fishing location choice of the fleet as a whole \citep{Rijnsdorp2000,
-	Poos2007a}. In order to account for this behaviour, the fishing
-sub-model operates spatially on a daily time-step so that for future days the
-biomass available to the fishery is reduced in the areas fished. The cumulative
-effect is to make heavily fished areas less attractive as future fishing
-opportunities.
+Where several fishing vessels exploit the same fish population competition is
+known to play an important role in local distribution of fishing effort
+\citep{Gillis1998}. If several vessels are fishing on the same patch of fish,
+local depletion and interference \added[id=JJ]{competition} will affect fishing
+location choice of the fleet as a whole \citep{Rijnsdorp2000, Poos2007a}. In
+order to account for this behaviour, the fishing sub-model operates spatially
+on a daily time-step so that for future days the biomass available to the
+fishery is reduced in the areas fished. The cumulative effect is to make
+heavily fished areas less attractive as future fishing opportunities.
 
@@
 \replaced[id=JJ]{intervals}{distribution} each year, similar to scientific
-surveys undertaken by fisheries research agencies.
+surveys undertaken by fisheries research agencies. \\
 
-\section{Calculation}
+\subsection{Software}
+
+The simulation framework is implemented in the statistical software package R
+\citep{RCoreTeam2017} \replaced[id=PD]{and}{;} available as an R package from
+the authors github site (\url{www.github.com/pdolder/MixFishSim}).\\
+
+\section{Calculation - used by journal / Parameterisation}
 
@@
 was implemented so that vessels take smaller steps when fishing at a location
-yields landings value which is in the top 90th percentile of the value
-experienced in that year (as defined per fleet in Table \ref{tab:2}). \\
+that yields landings value in the top 90th percentile of the value experienced
+in that year so far (as defined per fleet in Table \ref{tab:2}). \\
 
@@
 ensures the upper asymptote (where decisions are mainly based on past
-knowledge) is reached $\sim$ halfway through the simulation.  \\
+knowledge) is reached approximately halfway through the simulation.  \\
 
@@
 
-\subsection{Simulation settings}
+\subsection{Example research question scenario}
 
@@
 the reduction in catches of a population given spatial closures. To do so, we
-set up a simulation to run for 50 years based on a 100 $\times$ 100 square
-grid, with five fleets of 20 vessels each and four fish populations. Fishing
-takes place four times a day per vessel and five days a week, while population
-movement is every week.\todo{\added[id=JJ]{move to start of methods
-		section}\added[id=PD]{I think ecological modelling wants the
-		'calculations' section here..will check}} \\
+set up a simulation to run for 50 years based on a 100 $\times$ 100 square grid
+(undetermined units), with five fleets of 20 vessels each and four fish
+populations. Fishing takes place four times a day per vessel and five days a
+week, while population movement is every week.\todo{\added[id=JJ]{move to start
+		of methods section}\added[id=PD]{I think ecological modelling
+		wants the 'calculations' section here..will check}} \\
 
@@
 	\item \textbf{data types:} commercial logbook data, survey data and
-		'real population',
+		`real population',
 	\item \textbf{temporal resolutions:} weekly, monthly and yearly
@@
 
+In order to answer the question of how sampling-derived data reflects the
+underlying population structure we compare different spatial and temporal
+aggregations of the simulated population distributions to:
+\begin{enumerate}[label=\alph*)]
+	\item \textbf{fisheries-independent data:} the inferred population from
+		a fixed-site sampling survey design as commonly used for
+		fisheries monitoring purposes;
+	\item \textbf{fisheries-dependent data:} the inferred population from
+		our fleet model which includes fishery-induced sampling
+		dynamics.
+\end{enumerate}
+
 The consequences of different spatial aggregations of the data are shown in
@@
 the lower left part of the sampling domain). The survey data at this spatial
-resolution shows very sparse information about the spatial distributions of the
+resolution displays very sparse information about the spatial distributions of the
 populations. The slightly aggregated data on a 5 x 5 grid shows similar
 patterns and, while losing some of the spatial detail, there remains good
-consistency between the 'real population' and the commercial data. Survey data
+consistency between the `real population' and the commercial data. Survey data
 starts to pick out some of the similar patterns as the other data sources, but
 lacks coverage. The spatial catch information on a 10 x 10 and 20 x 20 grid
-loses a significant amount of information about the spatial resolutions for all
+lose a significant amount of information about the spatial resolutions for all
 data sources, and some differences between the survey, commercial and 'real
@@
 population', though the first species (in red) is less well represented and
-some weeks are missing catches from the area. The monthly data. The monthly
-data shows some consistency between the 'real population' and commercial data
-for species 2 - 4, though species 1 remains under-represented. On an annual
-basis, interestingly the commercial data under represents the first species (in
-red) while the survey over represents species 1. This is likely due to the
+some weeks are missing catches from the area. The monthly data shows some
+consistency between the 'real population' and commercial data for species 2 -
+4, though species 1 remains under-represented. On an annual basis,
+interestingly the commercial data under represents the first species (in red)
+while the survey over represents species 1. This is likely due to the
 biases in commercial sampling, with the fisheries not targeting the areas where
@@
 was the monthly closures ($<$ $\sim$ 30 \%).  The least effective were the
-yearly closures (blue lines) at all spatial resolutions, which resulted in
-increased fishing mortalities ($>$ 30 \%). \\
+yearly closures (blue lines) at all spatial resolutions, which conversely
+resulted in increased fishing mortalities ($>$ 30 \%). \\
 
@@
 Interestingly the monthly data scenario was more effective than weekly data,
-which I'd posit is due to the increase amount of data available from the
-commercial sampling across a month compared to a week. Commercial data used at
-an annual time-step was ineffective in bringing fishing mortality down for
-species 1. \\
+which we posit is due to the increased data available from the commercial
+sampling across a month compared to a week. Commercial data used at an annual
+time-step was ineffective in bringing fishing mortality down for species 1. \\
 
@@
 biological and human processes operating on different time-frames
-\cite{Dunn2016}, understanding assumptions behind the data used - increasingly
-a combination of logbook and positional information from vessel monitoring
-systems - is vital to ensure measures are effective. \\
+(\cite{Dunn2016}), understanding assumptions behind the data used -
+increasingly a combination of logbook and positional information from vessel
+monitoring systems - is vital to ensure measures are effective. \\
 

### 2019-06-25 analysis/effectiveness_plot.R

@@ -1,0 +1,88 @@
+##-----------------------------
+## Visualising the effectiveness of closures
+## in changing F based on various sources and
+## resolutions of data
+## For discussion with Paul
+##-----------------------------
+
+load("Combined_Results.RData")
+
+
+## Calculate the percentage difference 
+###################
+library(dplyr)
+
+avg2_4  <- combined %>% filter(year %in% 29:29) %>% 
+group_by(scenario, pop, metric, timescale, basis, data_type, resolution) %>% summarise(value = mean(data, na.rm = T))
+
+avg8_10 <- combined  %>% filter(year %in% 50:50) %>% 
+group_by(scenario, pop, metric, timescale, basis, data_type, resolution) %>% summarise(value = mean(data, na.rm = T))
+
+combined <- merge(avg2_4, avg8_10, by = c("scenario","metric","pop", "timescale", "basis", "data_type", "resolution"))
+
+colnames(combined)[8:9] <- c("before", "after")
+
+combined$diff <- ((combined$after - combined$before) / combined$before)  * 100
+
+##################
+library(ggplot2); theme_set(theme_bw())
+library(viridis)
+
+f_diff <- subset(combined, metric == "F" & basis == "high_pop")
+
+## similar to current plot
+ggplot(f_diff, aes(x = diff, y = data_type))+
+    geom_point(aes(pch = timescale, col = resolution)) +
+    facet_wrap(~ pop, ncol = 1)
+
+
+## a quick regression tree to see which variables are most important
+library(REEMtree)
+library(rpart.plot)
+
+f_diff$ftimescale <- factor(f_diff$timescale)
+f_diff$fresolution <- factor(f_diff$resolution)
+f_diff$fpop <- factor(f_diff$pop)
+
+## unpruned tree with a maximum depth set for visualisation
+rtree <- rpart(diff ~ fpop + ftimescale + data_type + fresolution,
+               data = f_diff,
+               control = list(minbucket = 2, minsplit = 2, cp = -1, maxdepth = 4))
+
+## variable importance
+barplot(rtree$variable.importance)
+## so it goes fpop > fresolution > data_type > ftimescale 
+
+## visualise the regression tree
+blue2red <- colorRampPalette(c("blue","white","red"))
+cols <- blue2red(100)
+breaks <- seq(min(f_diff$diff) - 1, max(f_diff$diff) + 1, length=101)
+
[…]

### 2019-06-27 write_up/mixfishsim_ecolmod.tex
Text updates

@@
 Fishers exploit a variety of fish populations that are heterogeneously
-distributed in space and time with varying knowledge of species distributions
-using species non-selective fishing gear. \added[id=PD]{In doing so} fisheries
-\deleted[id=PD]{that}catch an assemblage of species
+distributed in space and time, with varying knowledge of species distributions
+and using species non-selective fishing gear. \added[id=PD]{In doing so}
+fisheries \deleted[id=PD]{that}catch an assemblage of species
 \added[id=PD]{and}\deleted{, known as mixed fisheries} \replaced[id=JJ]{may}{,
@@
 discard\deleted[id=JJ]{ing} over-quota catch \added[id=JJ]{when managed by
-	single species quotas and fishers exhaust one or more quota which may}
+	single species quotas and fishers exhaust one or more quota. This may}
 lead to overexploitation of fish populations \added[id=JJ]{\citep{Ulrich2011a,
-		Batsleer2015}}.  \added[id=JJ]{This discarding of fish in
+		Batsleer2015}}.  \added[id=JJ]{Discarding of fish in
 	excess of quota limits the ability to maintain fishing mortality within
@@
 as measures to \replaced[id=PD]{reduce unwanted catch}{avoiding
-	discard\added[id=JJ]{ing of fish}}\citep{Kennelly2002, Catchpole2008,
+	discard\added[id=JJ]{ing of fish}} \citep{Kennelly2002, Catchpole2008,
 	Bellido2011}.  \\
@@
 \added[id=PD]{\citep{Holmes2011, Little2014, Dunn2014a}}.  \deleted[id=PD]{its}
-implementation of avoidance measures is, however, restricted by lack of
+Implementation of avoidance measures is, however, restricted by lack of
 knowledge of fish and fishery spatiotemporal dynamics and understanding of the
@@
 information is, however, derived from an inherently biased sampling programme,
-targeted fishing. \deleted[id=PD]{ Further, fishers generally only recorded
-	landings (not catch) on a daily basis\todo{\added[id=JJ]{Its not clear
-			what the problem is: landings collected on daily basis
-			or landings recorded rather than catch}}.  This leads
-	to questions about the validity of inference that can be drawn from
-	landings data assigned to VMS activity pings.}\todo{\added[id=JJ]{This
-		comes as a surprise: I thought this was going to be about
+targeted fishing, where fishers establish favoured fishing grounds first
+through an explore-exploit strategy \cite{Bailey2018} and then use experience
+to return to areas of high catch. \deleted[id=PD]{ Further, fishers generally
+	only recorded landings (not catch) on a daily
+	basis\todo{\added[id=JJ]{Its not clear what the problem is: landings
+			collected on daily basis or landings recorded rather
+			than catch}}.  This leads to questions about the
+	validity of inference that can be drawn from landings data assigned to
+	VMS activity pings.}\todo{\added[id=JJ]{This comes as a surprise: I
+		thought this was going to be about
 		discards}\added[id=PD]{Agree, have removed this to avoid
@@
 
-We i) develop a simulation model where population dynamics are highly-resolved
-in space and time to answer these questions\replaced[id=PD]{. Being}{ and are}
-known \added[id=PD]{directly} rather than inferred from sampling or commercial
-catch\added[id=PD]{, we can use the population model to evaluate how inference
-	from fisheries-dependent and fisheries independent sampling relates to
-	the real population structure}. We ii) compare at different spatial and
-temporal aggregations of the simulated population distributions to samples from
-fisheries-dependent and fisheries independent catches. We then iii) simulate a
-fishery closure to protect a species based on different spatial and temporal
-data aggregations. \\
+To answer these questions we i) develop a simulation model where population
+dynamics are highly-resolved in space and time \replaced[id=PD]{. Being}{ and
+	are} known \added[id=PD]{directly} rather than inferred from sampling
+or commercial catch\added[id=PD]{, we can use the population model to evaluate
+	how inference from fisheries-dependent and fisheries independent
+	sampling relates to the real population structure}. We ii) compare, at
+different spatial and temporal aggregations, the simulated population
+distributions to samples from fisheries-dependent and fisheries independent
+catches to test if these are a true reflection of the relative density of the
+populations. We then iii) simulate a fishery closure to protect a species based
+on different spatial and temporal data aggregations. We use these evaluations
+to draw inference on the utility of commercial data in supporting management
+decisions. \todo{\added[id=JJ]{If the paper has two goals this should be clear
+		from the start, but may be better over 2 MSs}\added[id=PD]{I
+		would like to keep both parts, but have made clearer in how its
+		set out.  The closure scenarios form validation of the data
+		aggregation, rather than effectiveness of the closures
+		themselves - so its a continuation of the same question in my
+		eyes}}\deleted[id=PD]{.  Further, we extend our analysis to a
+	range of spatial and temporal scales to assess the impact of these
+	processes on the success of the management measure.}\\
 
-We compare the catch composition from fisheries independent and dependent
-sampling against the real population composition, as well as the theoretical
-"benefit" to the population spatial closures using the different data sources.
-We use these evaluations to draw inference on the utility of commercial data in
-supporting management decisions. \todo{\added[id=JJ]{If the paper has two goals
-		this should be clear from the start, but may be better over 2
-		MSs}\added[id=PD]{I would like to keep both parts, but have
-		made clearer in how its set out.  The closure scenarios form
-		validation of the data aggregation, rather than effectiveness
-		of the closures themselves - so its a continuation of the same
-		question in my eyes}}\deleted[id=PD]{.  Further, we extend our
-	analysis to a range of spatial and temporal scales to assess the impact
-	of these processes on the success of the management measure.}\\
+[We find..]
 
@@
 \replaced[id=PD]{A}{We developed and implemented a simulation model with a}
-modular event-based \replaced{simulation model was developed with}{approach,
-	where} \added[id=PD]{sub-}modules \deleted[id=PD]{are} implemented on
-independent time-scales appropriate to capture the characteristic of the
+\replaced{simulation model that is modular and discrete-event based was
+	developed. This approach enables efficient computation by allowing
+	for}{approach, where} \added[id=PD]{sub-}modules \deleted[id=PD]{are}
+implemented on time-scales appropriate to capture the characteristic of the
 \replaced[id=PD]{different processes}{process modelled} (Figure 1).
@@
 
-\replaced[id=PD]{In our model system p}{P}opulation movement is driven by
+\replaced[id=PD]{In the model system p}{P}opulation movement is driven by
 random (diffusive) and directed (advective) processes and we incorporate
@@
 exploiting four fish populations with different spatial and population
-demographics. We use the model to simulate \replaced[id=PD]{50}{40} years of
-exploitation of the fish populations.
+demographics. The following describes the implementation of each of the
+sub-modules.
 
@@
 \replaced[id=PD]{Under the population dynamics module}{Here,} population
-biomass growth and depletion for pre-recruits and \deleted[id=PD]{fish}
+biomass growth and depletion for pre-recruits and\deleted[id=PD]{fish}
 recruited \added[id=PD]{fish} \deleted[id=PD]{to the fishery} are modelled
@@
 \end{equation}
-where $\rho$ is Brody's coefficient, shown to be approximately equal to
-$e^{-K}$ when $K$ is the growth rate from a von Bertalanffy logistic growth
-model \citep{Schnute1985}. $Wt_{R-1}$ is the average weight of fish prior to
+where $\rho$ is Brody's coefficient, shown to be equal to $e^{-K}$ when $K$ is
+the growth rate from a von Bertalanffy logistic growth model
+\citep{Schnute1985}. $Wt_{R-1}$ is the average weight of fish prior to
 recruitment, while $Wt_{R}$ is the average recruited weight. $\alpha_{d}$
@@
 where $\alpha$ is the maximum productivity per spawner and $\beta$ the density
-dependent reduction in productivity as the SSB increases. In this study, the
-Beverton-Holt form of stock recruit relationship was used for all populations.
+dependent reduction in productivity as the SSB increases. In our example
+application the Beverton-Holt form of stock recruit relationship was used for
+all populations though either functional form can be chosen.
 
@@
 	employed} a Gaussian spatial process \added[id=JJ]{was employed} to
-model habitat suitability for each of the populations on a 2d
-grid\replaced[id=JJ]{. An}{, with an} advection-diffusion process
-\deleted[id=JJ]{to} control\added[id=JJ]{led} \deleted[id=JJ]{how the}
-population\deleted[id=JJ]{s} move\replaced[id=JJ]{ment}{d}, with a time-varying
-temperature covariate used to change the spatial bounds of suitable habitat
-on a weekly time-step\todo{\added[id=JJ]{What have a temperature covariate? Could just
-		use time}\added[id=PD]{Was intended as some biological meaning
-		- species thermal tolerances load onto the temperature effect -
-		so could be different per species}}.  \deleted[id=JJ]{This was
-	intended to balance realism in population movement, capturing the main
-	directed and random processes, and practicality of modelling the
-	population rather than individual fish.} \\
+model habitat suitability for each of the populations on a 2d grid. \\
 
-For \deleted[id=PD]{the}habitat we first define\added[id=PD]{d} a Gaussian
-random field process\todo{\added[id=JJ]{Not clear how habitat/GRF affect local
+\deleted[id=PD]{the habitat}We first define\added[id=PD]{d} a Gaussian random
+field process\todo{\added[id=JJ]{Not clear how habitat/GRF affect local
 		abundances, only have $B_{y,d}$}\added[id=PD]{Have included
@@
 
-The temperature field \replaced[id=PD]{was}{is} defined on a gradient from a
-South-Westerly to North-Easterly direction, with temperature in each cell
-changing gradually on a week-by-week basis so that initially high temperature
-areas cycle\added[id=PD]{d} to lower temperatures and low temperature areas
-\textit{vice versa}. Each population $p$ \replaced[id=PD]{wa}{i}s assigned a thermal
-tolerance with mean, $\mu\added[id=PD]{_{p}}$ and variance,
-$\sigma^2\added[id=PD]{_{p}}$ so that each cell and population temperature
-suitability is defined that:
+\replaced[id=JJ]{An}{, with an} advection-diffusion process \deleted[id=JJ]{to}
+control\added[id=JJ]{led} \deleted[id=JJ]{how the} population\deleted[id=JJ]{s}
+move\replaced[id=JJ]{ment}{d}, with a time-varying temperature covariate used
+to change the interaction between time and suitable habitat on a weekly
+time-step\todo{\added[id=JJ]{What have a temperature covariate? Could just use
+		time}\added[id=PD]{Was intended as some biological meaning -
+		species thermal tolerances load onto the temperature effect -
+		so could be different per species}}.  \deleted[id=JJ]{This was
+	intended to balance realism in population movement, capturing the main
+	directed and random processes, and practicality of modelling the
+	population rather than individual fish.} Each population $p$
+\replaced[id=PD]{wa}{i}s assigned a thermal tolerance with mean,
+$\mu\added[id=PD]{_{p}}$ and variance, $\sigma^2\added[id=PD]{_{p}}$ so that
+each cell and population temperature suitability is defined that:
 \begin{equation}
@@
 
-\added[id=PD]{The final process resulted in independent populations structure
-	and movement patterns, with population movement occurring on a weekly
-	basis. This process approximated the demographic shifts in fish
+\added[id=PD]{The final process resulted in population structures and movement
+	patterns unique to each species, with population movement occurring on
+	a weekly basis. The decision to model population movement on a weekly
+	timescale was to reflect that fish tend to aggregate in species
+	specific locations and range within a week is fairly limited [REF!!].
+	Therefore this process approximated the demographic shifts in fish
 	populations throughout a year with seasonal spawning patterns (e.g.
@@
 type strategy for individual vessels to maximise their catch from an unknown
-resource distribution (\cite{Bailey2018}).
+resource distribution (\cite{Bailey2018}). The decision to use an individual
+based model for fishing vessels was taken because fishers as a group tend to
+show heterogeneity and individual rather than group dynamics. Thus this was the
+fleet dynamics is the productive of individual experiences rather than
+pre-ordained group dynamics.
 
@@
 `persistence') providing some overall \deleted[id=PD]{location of}directional
-movement \citep{Codling2008} \deleted[id=PD]{or uncorrelated}. \\
+movement \citep{Codling2008}\deleted[id=PD]{or uncorrelated}. \\
 

### 2019-06-27 write_up/mixfishsim_ecolmod.tex
Text update

@@
 	for each $c_{i} \in \mathbb{R}^2$}, the joint distribution of $S =
-\{S(c1),\dots S(c_{n})\}$ is multivariate Gaussian. The distribution is
-specified by its \textit{mean function}, $\mu(c) = E[S(c)]$ and its
-\textit{covariance function}\todo{\added[id=JM]{Introduce the gamma function,
-		and why this covariance structure? Why correlate values in the
-		random field?}\added[id=PD]{to allow populations to have
-		different aggregation densities: have tried to clarify}},
-$\gamma(c,c') = Cov\{S(c),S(c')\}$ \citep{Diggle2007}.\\
-
-The covariance structure affects the smoothness of the surfaces which the
-process generates\replaced[id=PD]{;}{, and} we used the \textit{Matérn}
+\{S(c1),\dots S(c_{n})\}$ is multivariate Gaussian with a \textit{Matérn}
 \deleted[id=PD]{family of}covariance structure\deleted[id=PD]{s},
@@
 	\citep{Tobler1970, F.Dormann2007}} and we change the parameters to
-implement different spatial structures for the populations. The \textit{Matérn}
-correlation is a two-parameter family where: 
-	\begin{center}
-		$\rho(u) = \{2^{\kappa -
-			1}\Gamma{\kappa}\}^{-1}(u/\phi)^{\kappa}K_{\kappa}(u/\phi)$
-	\end{center}
-$K_{\kappa}(.)$ is a modified Bessel function of order $\kappa$, $\phi >
-0$ is a scale parameter with the dimensions of distance, and $\kappa > 0$,
-called the order, is a shape parameter which determines the smoothness of the
-underlying process (Figure \ref{S-fig:16}). \\
+implement different spatial structures for the populations. \\
 
@@
 grounds, and choosing randomly from the top 75 \% of fishing events
-\replaced[id=PD]{as defined by the expected profit}{in value}. Simulation
-testing indicated that this learning increased the mean value of catches for
-the vessels, over just relying on the correlated random walk
-\todo{\added[id=JJ]{Correlated random walk of what}} function \added[id=PD]{as
-	described for the 'within trip' decisions below} (MIGHT NEED TO INCLUDE
-IN SUPPLEMENTARY).
+\replaced[id=PD]{as defined by the expected profit}{in value}.
 
@@
 
-\section{Calculation - used by journal / Parameterisation}
+\section{Parameterisation}
 
-\subsection{Population parametrisation}
+\subsection{Population models}
 
 We parametrised the simulation model for four populations with different
-population demographics; growth rates, natural mortality and recruitment
-functions (Table \ref{tab:1}). Habitat preference (Figure \ref{S-fig:1}) and
-temperature tolerances (Figures \ref{S-fig:3}, \ref{S-fig:4}) were unique to
-each population resulting in differently weekly distribution patterns (Figures
+demographics; growth rates, natural mortality and recruitment functions (Table
+\ref{tab:1}). Habitat preference (Figure \ref{S-fig:1}) and temperature
+tolerances (Figures \ref{S-fig:3}, \ref{S-fig:4}) were unique to each
+population resulting in differently weekly distribution patterns (Figures
 \ref{S-fig:5}-\ref{S-fig:7}). In addition, each of the populations has two
@@
 areas in pre-defined weeks (Figure \ref{S-fig:2}) with population-specific
-movement rates (Table \ref{tab:1}). The realised movement of the populations
-for a number of weeks is shown in Figure \ref{S-fig:9} while the realised daily
-fishing mortality are shown in Figure \ref{S-fig:10}.
+movement rates (Table \ref{tab:1}). The individual habitat preferences and
+thermal tolerances results different spatial habitat use for each population
+(Figure \ref{S-fig:9}) and consequently different seasonal exploitation
+patterns (Fishing mortality in Figure \ref{S-fig:10}).
 
@@
 
-An example of the realised fleet movements for a single vessel during a single
-trip are given in Figure \ref{S-fig:11}, while Figure \ref{S-fig:12} shows
-multiple trips for a single vessel, \added[id=PD]{Figure} \ref{S-fig:13} the
-vessel movements for several trips overlaid on the value field (sum of the
-population densities $\times$ price), \added[id=PD]{Figure} \ref{S-fig:14} shows
-fishing locations for an entire fleet of 20 vessels for a single trip,
-\replaced[id=PD]{and Figure}{while} \ref{S-fig:15} shows an example of the step
-function realisation and turning angles from the correlated random
-walk.\todo{\added[id=JJ]{Move some of the supplementary figures to the
-		manuscript}}
+It can be seen from a single vessels movements during a trip that the vessel
+exploits four different fishing grounds, three of them multiple time (Figure
+\ref{S-fig:11}), while across multiple trips fishing grounds that are further
+apart are fished (Figure \ref{S-fig:12}). These different locations relate to
+areas where the highest revenue were experienced, as shown by
+\added[id=PD]{Figure} \ref{S-fig:13}, which shows several trips for the vessel
+overlaid on the value field (sum of the population densities $\times$ price).
+Vessels from the same fleet (and therefore targeting preference) exploit
+similar but slightly different fishing grounds depending on their own personal
+experience during the explore phase of the fishery (\added[id=PD]{Figure}
+\ref{S-fig:14}), which is the result of the correlated random walk step
+function, with distance moved during the exploitation phase related to the
+revenue experienced on the fishing ground (\replaced[id=PD]{Figure}{while}
+\ref{S-fig:15}).\todo{\added[id=JJ]{Move some of the
+		supplementary figures to the manuscript}}
 

### 2019-06-27 write_up/F_changes.tex
Revised text

--- 2019-01-28 write_up/F_changes.tex
@@
-% latex table generated in R 3.5.2 by xtable 1.8-3 package
-% Mon Jan 28 16:57:19 2019
+% latex table generated in R 3.6.0 by xtable 1.8-4 package
+% Thu Jun 27 18:22:53 2019
 \begin{longtable}{rllrrrlllr}
-\caption{Fishing mortality effects of the closure scenarios} \\ 
+\caption{Fishing mortality effects of the closure scenarios. Results show the
+	fishing mortality before the closure (f\_before) and after the closure
+	(f\_after) and the percentage change in f (f\_change). The results are
+	ordered by most effective scenario first, least effective last.)} \\ 
   \hline
-scenario & metric & pop & before & after & diff (\%) & timescale & basis & data\_type & resolution \\ 
+scenario & metric & pop & f\_before & f\_after & f\_change & timescale & basis & data\_type & resolution \\ 
   \hline

### 2019-06-27 write_up/mixfishsim_ecolmod.tex
Revised text

@@
 		structures? 	
-	\item How does data aggregation and source impact on monitoring spatial
-		fisheries management measures ? \end{enumerate}
+	\item How does data aggregation and source impact on spatial fisheries
+	management measures?
+\end{enumerate}
 
@@
 
-It can be seen from a single vessels movements during a trip that the vessel
-exploits four different fishing grounds, three of them multiple time (Figure
-\ref{S-fig:11}), while across multiple trips fishing grounds that are further
-apart are fished (Figure \ref{S-fig:12}). These different locations relate to
-areas where the highest revenue were experienced, as shown by
-\added[id=PD]{Figure} \ref{S-fig:13}, which shows several trips for the vessel
-overlaid on the value field (sum of the population densities $\times$ price).
-Vessels from the same fleet (and therefore targeting preference) exploit
-similar but slightly different fishing grounds depending on their own personal
-experience during the explore phase of the fishery (\added[id=PD]{Figure}
-\ref{S-fig:14}), which is the result of the correlated random walk step
-function, with distance moved during the exploitation phase related to the
-revenue experienced on the fishing ground (\replaced[id=PD]{Figure}{while}
-\ref{S-fig:15}).\todo{\added[id=JJ]{Move some of the
-		supplementary figures to the manuscript}}
-
 \subsection{Survey settings}
@@
 
-\subsection{Example research question scenario}
+\subsection{Example research question}
 
-To illustrate the capabilities on \emph{MixFishSim}, we investigate the
+To illustrate the capabilities of \emph{MixFishSim}, we investigate the
 influence of the temporal and spatial resolution of different data sources on
@@
 populations. Fishing takes place four times a day per vessel and five days a
-week, while population movement is every week.\todo{\added[id=JJ]{move to start
-		of methods section}\added[id=PD]{I think ecological modelling
-		wants the 'calculations' section here..will check}} \\
+week, while population movement is every week.
 
@@
 \end{enumerate}
-In total 56 closure scenarios were run which represent combinations of:
+In total 28 closure scenarios were run which represent combinations of:
 
@@
 		grid and 20 x 20 grid,
-	\item \textbf{closure basis:} high catch rates of protected species, or
-		high ratio of protected species v secondary species.
+	\item \textbf{closure basis:} highest 5 \%  of catch rates for the
+		protected species
 \end{itemize}
@@
 
-In order to answer the question of how sampling-derived data reflects the
-underlying population structure we compare different spatial and temporal
+\subsection{Simulation dynamics}
+
+It can be seen from a single vessels movements during a trip that the vessel
+exploits four different fishing grounds, three of them multiple times (Figure
+\ref{S-fig:11}), while across several trips fishing grounds that are further
+apart are fished (Figure \ref{S-fig:12}). These different locations relate to
+areas where the highest revenue were experienced, as shown by
+\added[id=PD]{Figure} \ref{S-fig:13}, where several trips for the vessel
+overlaid on the revenue field, i.e. 
+$$\sum^c_{c=1}\sum^s_{s=1} B_{s,c} \cdot Q_{s,c}$$
+
+Vessels from the same fleet (and therefore targeting preference) exploit
+similar but slightly different fishing grounds depending on their own personal
+experience during the explore phase of the fishery (\added[id=PD]{Figure}
+\ref{S-fig:14}), which is the result of the randomness in the correlated random
+walk step function, with distance moved during the exploitation phase and the
+direction stochastically related to the revenue experienced on the fishing
+ground (\replaced[id=PD]{Figure}{while}
+\ref{S-fig:15}).\todo{\added[id=JJ]{Move some of the supplementary figures to
+		the manuscript}}
+
+\subsection{How does sampling-derived data reflect the underlying population
+	structure?}
+
+In order to answer this question we compare different spatial and temporal
 aggregations of the simulated population distributions to:
@@
 
-The consequences of different spatial aggregations of the data are shown in
-Figure \ref{fig:1}, which represents the aggregation of catch from each of the
-data sources over a ten-year period (to average seasonal patterns) at different
-spatial resolutions. \\
-
-The finer spatial grid for the real population (top left) and commercial data
-(top middle) show visually similar patterns, though there are large unsampled
-areas in the commercial data from a lack of fishing activity (particularly in
-the lower left part of the sampling domain). The survey data at this spatial
-resolution displays very sparse information about the spatial distributions of the
-populations. The slightly aggregated data on a 5 x 5 grid shows similar
-patterns and, while losing some of the spatial detail, there remains good
-consistency between the `real population' and the commercial data. Survey data
-starts to pick out some of the similar patterns as the other data sources, but
-lacks coverage. The spatial catch information on a 10 x 10 and 20 x 20 grid
-lose a significant amount of information about the spatial resolutions for all
-data sources, and some differences between the survey, commercial and 'real
-population' data emerge. \\
+Figure \ref{fig:1} shows the aggregated catch composition from each of the data
+sources over a ten-year period (to average seasonal patterns) at different
+spatial resolutions. The finer spatial grid for the real population (top left)
+and commercial data (top middle) show visually similar patterns, though there
+are large unsampled areas in the commercial data from a lack of fishing
+activity (particularly in the lower left part of the sampling domain). The
+survey data at this spatial resolution displays very sparse information about
+the spatial distributions of the populations. The slightly aggregated data on a
+5 x 5 grid shows similar patterns and, while losing some of the spatial detail,
+there remains good consistency between the `real population' and the commercial
+data. Survey data starts to pick out some of the similar patterns as the other
+data sources, but lacks coverage. The spatial catch information on a 10 x 10
+and 20 x 20 grid lose a significant amount of information about the spatial
+resolutions for all data sources, and some differences between the survey,
+commercial and 'real population' data emerge. \\
 
@@
 the data over a ten-year period, with weekly (top), monthly (middle) and yearly
-(bottom) catch compositions from across an aggregated 20 x 20 area. \\
-
-As can be seen by comparison to the 'real population', the monthly aggregation
-captures the major patterns seen in the weekly data, albeit missing more subtle
+(bottom) catch compositions from across an aggregated 20 x 20 area. As can be
+seen by comparison to the 'real population', the monthly aggregation captures
+the major patterns seen in the weekly data, albeit missing more subtle
 differences. The yearly data results in a constant catch pattern due to the
@@
 interestingly the commercial data under represents the first species (in red)
-while the survey over represents species 1. This is likely due to the
-biases in commercial sampling, with the fisheries not targeting the areas where
-species 1 are present, and the biases in the survey sampling from over
-representation of the spatial distribution. \\
+while the survey over represents species 1. This is likely due to the biases in
+commercial sampling, with the fisheries not targeting the areas where species 1
+are present, and the biases in the survey sampling from over representation of
+the spatial distribution.
+
+\subsection{How does data aggregation and source impact on spatial fisheries
+	management measures?}
 
@@
 this to assess the efficacy of a closure in reducing fishing mortality on
-species 1, given availability of data and its use at different resolutions in
-order to evaluate the trade-offs in data sources. Figure \ref{fig:3} shows the
-trend in fishing mortality for each species simulated (columns) given the data
-sources (rows), temporal aggregations (colour lines) and spatial aggregations
-(line-styles), while Figure \ref{fig:4} shows the change in fishing mortality
-from before the closure (year 29) to after the closure (year 50). \\
+species 3, given availability of data and its use at different resolutions in
+order to evaluate the trade-offs in data sources.
 
-For the closures based on 'real population' (bottom row), the most
-disaggregated data (a weekly timescale and 1 x 1 resolution) was most
-effective, reducing fishing mortality on species 1 (left) by $\sim$ 60 \%. Next
-was the monthly closures ($<$ $\sim$ 30 \%).  The least effective were the
-yearly closures (blue lines) at all spatial resolutions, which conversely
-resulted in increased fishing mortalities ($>$ 30 \%). \\
+The trend in fishing mortality for each species show that in most cases the
+fishery closure was successful in reducing fishing mortality on the species of
+interest (species 3; Figure \ref{fig:3}), though interestingly the largest
+reductions in fishing mortality happened immediately after the closures,
+following which the fisheries "adapted" to the closures and fishing mortality
+increased again somewhat. The exception to the success was the closures
+implemented based on the coarsest spatial (20 x 20) and temporal resolution
+which were ineffective with all data sources. As expected, closures based on
+the "known" population distribution were most effective, with differing degrees
+of success using the commercial data. Fishing mortality rates on the other
+species changed in different proportions, depending on whether the displaced
+fishing effort moved to areas where the populations were in more greater or
+lesser density. \\
 
-For the survey data, which can only be implemented on a yearly timescale, the
-closures had no effect at any data resolution. The results are identical for
-the different data resolutions except 20 x 20, which is why you can't see more
-than 2 points. This is because of the sparsity of the sampling locations.\\
-
-For the commercial data, the most effective closure scenario was based on 1 x 1
-data at a monthly temporal resolution. This results in $\sim$ 10 \% reduction
-in F for species 1. \textcolor{blue}{This was the only closure scenario to have
-	positive effect according to Figure \ref{fig:4}, though looking at the
-	trend in Figure \ref{fig:3} this looks more related to the continued
-	increased in F trend, as other scenarios had an initial effect}.
-Interestingly the monthly data scenario was more effective than weekly data,
-which we posit is due to the increased data available from the commercial
-sampling across a month compared to a week. Commercial data used at an annual
-time-step was ineffective in bringing fishing mortality down for species 1. \\
-
-Given the scenarios above, it seems clear that spatial disaggregation is more
-important than the temporal disaggregation of the commercial data, except when
-its used at an annual time-frame, which is the scenario that gave the worst
-results.
-
-For the other species in the simulation (population 2 - 4) there was little
-difference in fishing mortalities across scenarios.
-
-\textcolor{blue}{Note: The monthly commercial data scenario is the most
-	effective of the realistic scenarios, as the 'real population' can only
-	be seen as a baseline comparison.}
+A regression tree highlights that the most factor contributing to differences
+in fishing mortality before and after the closure was the population (72 \%
+showing that the closures were effective for population 3), followed by data
+resolution (21 \%), data type (7 \%) with the least important factor the
+timescale ($<$ 1 \%). In general the finer the spatial resolution of the data
+used the greater reduction in fishing mortality for population 3 after the
+closures (Figure\ref{fig:4}). The notable outliers are the commercial data at
+the coarsest spatial resolution (20 x 20) at a yearly and weekly timescale,
+where closures were nearly as effective as the fine-scale resolution. In this
+case the closures were sufficiently large to protect the population (and was as
+effective as when the closure was based on the "real population") but this may
+have consequences in terms of restricting a much larger area than necessary. \\
 
@@
 fishers interact / adapt to changes with the resource and mgmt. \\
+
+It seems clear that spatial disaggregation is more important than the temporal
+disaggregation of the commercial data... WHY
 
@@
 \section*{Funding} This work was supported by the MARES doctoral training
-program; and the Centre for Environment, Fisheries and Aquaculture Science
-seedcorn program.
+program (MARES\_14\_15) and the Centre for Environment, Fisheries and
+Aquaculture Science seedcorn program (DP227AC).
 
@@
 \input{F_changes.tex}
-
-\clearpage
-\footnotesize
-\input{F_changes_ratio.tex}
 
@@
 	\includegraphics[width = \linewidth]{../analysis/F_trendsREV}
-	\caption{Comparison of closure scenarios - Fishing mortality trends.
-		Only the scenarios based on high catch rates of population 3
-		are shown.}
+	\caption{Comparison of closure scenarios effect on fishing mortality
+		trends. Line colour denotes the timescale, while linestyle
+		denotes the spatial resolution.}
 	\label{fig:3}
@@
 \begin{figure}[!ht]
-	\includegraphics[width =\linewidth]{../analysis/Overview_plot_highPopRev}
-	\caption{Comparison of closure scenarios. Points indicate the
-		difference between the fishing mortality pre-closure (year 29)
-		and post-closure (year 50) for population 3. Only the scenarios
-		based on high catch rates of population 3 are shown.}
+	\includegraphics[width =\linewidth]{../analysis/f_diff_effectiveness}
+	\caption{Comparison of closure scenario effectiveness based on
+		different spatial and temporal resolutions.}
 	\label{fig:4}

### 2019-06-27 analysis/Plots_Combined.R

@@ -137,6 +137,8 @@ Fs <- filter(combined, metric == "F", basis == "high_pop", pop == "spp_3")
 Fs[,c(4:6)] <- round(Fs[,c(4:6)], 2)
 Fs <- Fs[order(Fs$pop, Fs$diff),]
 
+colnames(Fs)[4:6] <- c("f_before", "f_after", "f_change")
+
 print(xtable(Fs, digits = 2, caption = "Fishing mortality effects of the
 	     closure scenarios (ordered by most effective first)", label =
 	     "tab:6"), caption.placement = "top", file =
@@ -186,13 +188,20 @@ combined_pop_an <-  combined_pop_an[!is.na(combined_pop_an$year),] ## Remove R f
 
 combined_pop_an$year <- as.numeric(combined_pop_an$year) # to fix x-axis breaks
 
+combined_pop_an$res <- as.factor(combined_pop_an$res)
+
+png('F_trendsREV.png', units = "in", height = 8, width = 9, res = 600)
 ggplot(filter(combined_pop_an,basis == 'high_pop', metric == 'F'), 
        aes(x = year, y = data, group = combined)) + 
-geom_line(aes(colour = timescale, linetype = factor(res))) + 
-facet_wrap(data_type ~ pop, scale = 'free') + expand_limits(y = 0) +theme_bw() +
+geom_line(aes(colour = timescale, linetype = res), size = 1) + 
+facet_grid(data_type ~pop) + expand_limits(y = 0) +theme_bw() +
 geom_vline(xintercept = 30, linetype = 2, colour = "grey") + ylab("Fishing mortality") +
-theme(axis.text.x = element_text(angle = -90, hjust = 0)) + scale_x_continuous(breaks = seq(0,50,5))
-ggsave('F_trendsREV.png', width = 10, height = 8)
+theme(axis.text.x = element_text(angle = -90, hjust = 0),
+      panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+	  axis.text = element_text(size = 12, face = "bold"),
+	  axis.title = element_text(size = 12, face = "bold")) + 
+		  scale_x_continuous(breaks = seq(0,50,10))
+dev.off()
 
 ggplot(filter(combined_pop_an,basis == 'high_pop', metric == 'F', pop == "spp_3"), 
        aes(x = year, y = data, group = combined)) + 

### 2019-06-27 analysis/effectiveness_plot.R

@@ -53,6 +53,8 @@ rtree <- rpart(diff ~ fpop + ftimescale + data_type + fresolution,
 barplot(rtree$variable.importance)
 ## so it goes fpop > fresolution > data_type > ftimescale 
 
+rtree$variable.importance / sum(rtree$variable.importance)
+
 ## visualise the regression tree
 blue2red <- colorRampPalette(c("blue","white","red"))
 cols <- blue2red(100)
@@ -86,3 +88,21 @@ ggplot(f_diff, aes(x = resolution, y = diff))+
     xlab("Spatial resolution (high to low)") +
     ylab("Percentage difference in F before and after closure")
 dev.off()
+
+
+png("f_diff_effectiveness.png", units = "in", height = 8, width = 9, res = 600)
+
+ggplot(f_diff, aes(x = resolution, y = diff))+
+    geom_line(aes(colour = data_type), size = 2) +
+    facet_grid(timescale ~ fpop) +
+    geom_hline(yintercept = 0, linetype = 2, size = 1) +
+    scale_colour_manual("Data source", values = c("#d95f02", "#7570b3", "#1b9e77")) +
+    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+	  axis.text = element_text(size = 14, face = "bold"),
+	  axis.title = element_text(size = 14, face = "bold")) +
+    xlab("Spatial resolution (high to low)") +
+    ylab("Percentage difference in F before and after closure")
+dev.off()
+
+
+

### 2019-06-29 write_up/mixfishsim_ecolmod.tex
Clean up text

@@
 from either scientific surveys or commercial catch data are often used to model
-distributions, often with sparse data at limited spatial and temporal
+distributions, usually with sparse data at limited spatial and temporal
 resolution. \\
@@
 populations, and iii) fishery dynamics for multiple fleet characteristics based
-on species targeting via a mix of correlated random walk movement (for
-exploration) and learned behaviour (for exploitation) phases of the fisheries.
-\\
+on species targeting under an explore-exploit strategy via a mix of correlated
+random walk movement (for exploration) and learned behaviour (for exploitation)
+phases of the fisheries.  \\
 
@@
 inference to a simulated fixed-site sampling design commonly used for fisheries
-monitoring purposes and the true underlying population structures input to the
-simulation. We i) use the results to establish the potential and limitations of
-fishery-dependent data in providing a robust picture of spatiotemporal
-distributions; and ii) simulate an area closure based on areas defined from the
-different data sources at a range of temporal and spatial resolutions and
-assess their effectiveness on reducing catches of a fish population. \\
+monitoring purposes and the true underlying population structures. We i) use
+the results to establish the potential and limitations of fishery-dependent
+data in providing a robust picture of spatiotemporal distributions; and ii)
+simulate an area closure based on areas defined from the different data sources
+at a range of temporal and spatial resolutions and assess their effectiveness
+on reducing catches of a fish population. \\
 
@@
 information is, however, derived from an inherently biased sampling programme,
-targeted fishing, where fishers establish favoured fishing grounds first
-through an explore-exploit strategy \cite{Bailey2018} and then use experience
-to return to areas of high catch. \deleted[id=PD]{ Further, fishers generally
-	only recorded landings (not catch) on a daily
+targeted fishing, where fishers establish favoured fishing grounds through an
+explore-exploit strategy \citep{Bailey2018} where they search for areas with
+high catches and then use experience to return to areas where they've
+experienced high catch in the past.  \deleted[id=PD]{ Further, fishers
+	generally only recorded landings (not catch) on a daily
 	basis\todo{\added[id=JJ]{Its not clear what the problem is: landings
@@
 To answer these questions we i) develop a simulation model where population
-dynamics are highly-resolved in space and time \replaced[id=PD]{. Being}{ and
+dynamics are highly-resolved in space and time\replaced[id=PD]{. Being}{ and
 	are} known \added[id=PD]{directly} rather than inferred from sampling
-or commercial catch\added[id=PD]{, we can use the population model to evaluate
+or commercial catch\added[id=PD]{, we can use the population model to validate
 	how inference from fisheries-dependent and fisheries independent
-	sampling relates to the real population structure}. We ii) compare, at
-different spatial and temporal aggregations, the simulated population
-distributions to samples from fisheries-dependent and fisheries independent
-catches to test if these are a true reflection of the relative density of the
-populations. We then iii) simulate a fishery closure to protect a species based
-on different spatial and temporal data aggregations. We use these evaluations
-to draw inference on the utility of commercial data in supporting management
-decisions. \todo{\added[id=JJ]{If the paper has two goals this should be clear
-		from the start, but may be better over 2 MSs}\added[id=PD]{I
-		would like to keep both parts, but have made clearer in how its
-		set out.  The closure scenarios form validation of the data
-		aggregation, rather than effectiveness of the closures
-		themselves - so its a continuation of the same question in my
-		eyes}}\deleted[id=PD]{.  Further, we extend our analysis to a
-	range of spatial and temporal scales to assess the impact of these
-	processes on the success of the management measure.}\\
+	sampling relates to the real population structure in a way we could not
+	with real data}. We ii) compare, at different spatial and temporal
+aggregations, the simulated population distributions to samples from
+fisheries-dependent and fisheries independent catches to test if these are a
+true reflection of the relative density of the populations. We then iii)
+simulate a fishery closure to protect a species based on different spatial and
+temporal data aggregations. We use these evaluations to draw inference on the
+utility of commercial data in supporting management decisions.
+\todo{\added[id=JJ]{If the paper has two goals this should be clear from the
+		start, but may be better over 2 MSs}\added[id=PD]{I would like
+		to keep both parts, but have made clearer in how its set out.
+		The closure scenarios form validation of the data aggregation,
+		rather than effectiveness of the closures themselves - so its a
+		continuation of the same question in my eyes}}\deleted[id=PD]{.
+	Further, we extend our analysis to a range of spatial and temporal
+	scales to assess the impact of these processes on the success of the
+	management measure.}\\
 
@@
 	Dichmont2003} occurring at a daily time-step. \added[id=PD]{A daily
-	time-step was chosen to discretise continuous population processes
-	on a biologically relevant and computationally tractable timescale.}
+	time-step was chosen to discretise continuous population processes on a
+	biologically relevant and computationally tractable timescale.}
 \replaced[id=PD]{Under the population dynamics module}{Here,} population
 biomass growth and depletion for pre-recruits and\deleted[id=PD]{fish}
-recruited \added[id=PD]{fish} \deleted[id=PD]{to the fishery} are modelled
+recruited \added[id=PD]{fish}\deleted[id=PD]{to the fishery} are modelled
 separately as a function of previous recruited biomass, intrinsic population
-growth and recruitment. Biomass for each cell $c$ is incremented each day $d$ as
-follows (the full parameter list is detailed in Table \ref{tab: pop_variable}):
-\begin{equation}
+growth and recruitment functionally linked to the adult population size.
+Biomass for each cell $c$ is incremented each day $d$ as follows (the full
+parameter list is detailed in Table \ref{tab: pop_variable}): \begin{equation}
 	\begin{split}
@@
 
-Recruitment is modelled through a function relating the mature biomass to
+Recruitment is modelled through a function relating the adult biomass to
 recruits at time of recruitment. In \emph{MixFishSim}, it can be modelled
@@
 \replaced[id=PD]{having}{has} concentrated areas where spawning takes place. In
-the simulations the populations move\replaced[id=PD]{d}{s} towards
+the simulations the populations move\deleted[id=PD]{s} towards
 \replaced[id=PD]{these cells}{this} in the weeks prior to spawning, resulting
@@
 
-\replaced[id=JJ]{An}{, with an} advection-diffusion process \deleted[id=JJ]{to}
-control\added[id=JJ]{led} \deleted[id=JJ]{how the} population\deleted[id=JJ]{s}
+\replaced[id=JJ]{An}{, with an} advection-diffusion process\deleted[id=JJ]{to}
+control\added[id=JJ]{s}\deleted[id=JJ]{how the} population\deleted[id=JJ]{s}
 move\replaced[id=JJ]{ment}{d}, with a time-varying temperature covariate used
@@
 
-\added[id=PD]{The final process resulted in population structures and movement
-	patterns unique to each species, with population movement occurring on
-	a weekly basis. The decision to model population movement on a weekly
+\added[id=PD]{The final process results in a population structure and movement
+	pattern unique to each species, with population movement occurring on a
+	weekly basis. The decision to model population movement on a weekly
 	timescale was to reflect that fish tend to aggregate in species
-	specific locations and range within a week is fairly limited [REF!!].
-	Therefore this process approximated the demographic shifts in fish
-	populations throughout a year with seasonal spawning patterns (e.g.
-	Figure \ref{S-fig:5}).}
+	specific locations and range within a week is fairly limited
+	[\textcolor{red}{REF!!}].  Therefore this process approximated the
+	demographic shifts in fish populations throughout a year with seasonal
+	spawning patterns (e.g.  Figure \ref{S-fig:5}).}
 
@@
 based model for fishing vessels was taken because fishers as a group tend to
-show heterogeneity and individual rather than group dynamics. Thus this was the
-fleet dynamics is the productive of individual experiences rather than
-pre-ordained group dynamics.
+show heterogeneity and individual rather than group dynamics
+[\textcolor{red}{REF!}]. Thus this was the fleet dynamics is the productive of
+individual experiences rather than pre-ordained group dynamics.
 
@@
 grounds, and choosing randomly from the top 75 \% of fishing events
-\replaced[id=PD]{as defined by the expected profit}{in value}.
+\replaced[id=PD]{as defined by the expected profit, which has a seasonal
+	component}{in value}.
 
@@
 fishery is reduced in the areas fished. The cumulative effect is to make
-heavily fished areas less attractive as future fishing opportunities.
+heavily fished areas less attractive as a future fishing location choice as
+reduced catch rates will be experienced.
 
@@
 movement rates (Table \ref{tab:1}). The individual habitat preferences and
-thermal tolerances results different spatial habitat use for each population
+thermal tolerances result in different spatial habitat use for each population
 (Figure \ref{S-fig:9}) and consequently different seasonal exploitation
@@
 	on day 112 (5 stations per day)} with same catchability parameters for
-all populations ($Q_{p} = 1$).
+all populations ($Q_{p} = 1$). This was so as to approximate a real world
+survey design with limited seasonal and spatial coverage.
 
@@
 	\item Aggregate according to desired spatial and temporal resolution
-	\item Interpolate across entire area at desired resolution
-	\item Close area covering top 5 \% of catch 
+	\item Interpolate across entire area at desired resolution using simple
+		kriging using the \emph{interp} function from the R package
+		akima [\textcolor{red}{REF!}].
+	\item Close area covering top 5 \% of catch rates 
 \end{enumerate}
@@
 implemented based on the coarsest spatial (20 x 20) and temporal resolution
-which were ineffective with all data sources. As expected, closures based on
-the "known" population distribution were most effective, with differing degrees
-of success using the commercial data. Fishing mortality rates on the other
-species changed in different proportions, depending on whether the displaced
-fishing effort moved to areas where the populations were in more greater or
-lesser density. \\
+(yearly) which were ineffective with all data sources. As expected, closures
+based on the "known" population distribution were most effective, with
+differing degrees of success using the commercial data. Fishing mortality rates
+on the other species changed in different proportions, depending on whether the
+displaced fishing effort moved to areas where the populations were found in
+greater or lesser density. \\
 
-A regression tree highlights that the most factor contributing to differences
-in fishing mortality before and after the closure was the population (72 \%
-showing that the closures were effective for population 3), followed by data
-resolution (21 \%), data type (7 \%) with the least important factor the
-timescale ($<$ 1 \%). In general the finer the spatial resolution of the data
-used the greater reduction in fishing mortality for population 3 after the
-closures (Figure\ref{fig:4}). The notable outliers are the commercial data at
-the coarsest spatial resolution (20 x 20) at a yearly and weekly timescale,
-where closures were nearly as effective as the fine-scale resolution. In this
-case the closures were sufficiently large to protect the population (and was as
-effective as when the closure was based on the "real population") but this may
-have consequences in terms of restricting a much larger area than necessary. \\
+A regression tree (using the R package REEMtree [ref]) highlights that the
+factor most contributing to differences in fishing mortality before and after
+the closure was the population (72 \% showing that the closures were effective
+for population 3), followed by data resolution (21 \%), data type (7 \%) with
+the least important factor the timescale ($<$ 1 \%). In general the finer the
+spatial resolution of the data used the greater reduction in fishing mortality
+for population 3 after the closures (Figure \ref{fig:4}). The notable outliers
+are the commercial data at the coarsest spatial resolution (20 x 20) at a
+yearly and weekly timescale, where closures were nearly as effective as the
+fine-scale resolution. In this case the closures were sufficiently large to
+protect the population (and was as effective as when the closure was based on
+the "real population"; \textcolor{red}{CHECK THIS, COULD PLOT ACTUAL CLOSURE
+	LOCATIONS??}) but this may have consequences in terms of restricting a
+much larger area than necessary. \\
 
@@
 due to species targeting in fisheries resulting in preferential sampling
-\cite{Martinez-Minaya2018}. Often data is aggregated or extrapolated which
+\citep{Martinez-Minaya2018}. Often data is aggregated or extrapolated which
 requires assumptions about the spatial and temporal scale of processes. Our
@@
 biological and human processes operating on different time-frames
-(\cite{Dunn2016}), understanding assumptions behind the data used -
+\citep{Dunn2016}, understanding assumptions behind the data used -
 increasingly a combination of logbook and positional information from vessel
@@
 spatio-temporal distribution of the underlying fish populations, and ii)
-evaluate the effectiveness of a spatial closure given those assumptions. Our
-approach captures fine scale population and fishery dynamics not usually
+evaluate the effectiveness of a spatial closure given those assumptions. \\
+
+Our approach captures fine scale population and fishery dynamics not usually
 considered (although see \cite{Bastardie2010, Bailey2018}) which offers the
@@
 system rather than the result of a statistical modelling framework. \\
+
+WHAT'S ALREADY AVAILABLE - COMPARE AND CONTRAST
 

### 2019-07-02 write_up/mixfishsim_ecolmod.tex
text updated

@@
 Our study evaluates the importance of data scaling and considers potential bias
-introduced through data aggregation when using commercial fisheries data to
-infer spatio-temporal dynamics in fisheries. Understanding how fishers exploit
+introduced through data aggregation when using fisheries data to infer
+spatio-temporal dynamics of fish populations. Understanding how fishers exploit
 multiple heterogeneously distributed fish populations with different catch
@@
 due to species targeting in fisheries resulting in preferential sampling
-\citep{Martinez-Minaya2018}. Often data is aggregated or extrapolated which
+\citep{Martinez-Minaya2018}. Often data are aggregated or extrapolated which
 requires assumptions about the spatial and temporal scale of processes. Our
@@
 
-Our approach captures fine scale population and fishery dynamics not usually
-considered (although see \cite{Bastardie2010, Bailey2018}) which offers the
-advantage that larger scale fishery patterns are emergent properties of the
-system rather than the result of a statistical modelling framework. \\
+Our approach captures fine scale population and fishery dynamics and their
+interaction in a way not usually possible with real data and thus not usually
+considered in fisheries simulations. While other simulation frameworks seek to
+model individual vessel dynamics based on inferred dynamics from VMS and
+logbook records \citep{Bastardie2010}, or as a system to identify measures to
+meet particular management goals \citep{Bailey2018}, our framework allows users
+to explore the assumptions in modelling observations data and evaluate the
+underlying dynamics of such approaches at a fine spatial and temporal scale.
+This offers the advantage that larger scale fishery patterns are emergent
+properties of the system rather and results can be compared to those obtained
+under a statistical modelling framework. \\
 
-WHAT'S ALREADY AVAILABLE - COMPARE AND CONTRAST
-
-Our results show commercial data can provide at right scale and resolution -
+Our results demonstrate the importance of data scale and resolution when using
+observational data to support management measures. In doing so it highlights  
 depends on scale of process: pop movement etc... Important to consider how

### 2019-07-03 write_up/mixfishsim_ecolmod.tex
Text update

@@
 %%%%%%%%%%%%%%%%%%%%%%%
+%% correct equation line numbering
+
+\let\oldequation\equation
+\let\oldendequation\endequation
+\renewenvironment{equation}
+ {\linenomathNonumbers\oldequation}
+ {\oldendequation\endlinenomath}
+
+%%%%%%%%%%%%%%%%%%%%%%
 
@@
 	discard\added[id=JJ]{ing of fish}} \citep{Kennelly2002, Catchpole2008,
-	Bellido2011}.  \\
+	Bellido2011}\textcolor{red}{(ADD COSGROVE REFERENCE HERE)}.  \\
 
@@
 the \textit{RFSimulate} function of the \textit{RandomFields} R package
-\citep{Schlater2015}. Each population \replaced[id=PD]{was}{is} initialised at
-a single location, and subsequently move\replaced[id=PD]{ed}{s} according to a
-probabilistic distrib\added[id=PD]{u}tion based on habitat suitability
-(represented by the normalised values from the GRFs), temperature and distance
+\citep{Schlater2015}, which simulates a Gaussian Random Field process given a
+user defined error model and correlation structure. We define a stationary
+habitat field and combine with a temporally dynamic thermal tolerance field to
+imitate two key drivers of population dynamics. Each population
+\replaced[id=PD]{was}{is} initialised at a single location, and subsequently
+move\replaced[id=PD]{ed}{s} according to a probabilistic
+distrib\added[id=PD]{u}tion based on habitat suitability (represented by the
+normalised values from the GRFs), temperature and distance
 from current cell\replaced[id=PD]{:}{.} 
@@
 a trip; and within-trip decisions, determining movement from one fishing spot
-to another within a trip. Together, these element implement an explore-exploit
+to another within a trip. Together, these elements implement an explore-exploit
 type strategy for individual vessels to maximise their catch from an unknown
@@
 show heterogeneity and individual rather than group dynamics
-[\textcolor{red}{REF!}]. Thus this was the fleet dynamics is the productive of
-individual experiences rather than pre-ordained group dynamics.
+[\textcolor{red}{REF!}]. Therefore in the simulations fleet dynamics are the
+productive of individual experiences rather than pre-defined group dynamics.
 
@@
 
-The survey simulation was set up with follow a fixed gridded station design
-with 100 stations fished each year, starting on day 92 \added[id=PD]{and ending
-	on day 112 (5 stations per day)} with same catchability parameters for
-all populations ($Q_{p} = 1$). This was so as to approximate a real world
-survey design with limited seasonal and spatial coverage.
+The survey simulation was set up with a fixed gridded station design with 100
+stations fished each year, starting on day 92 \added[id=PD]{and ending on day
+	112 (5 stations per day)} with same catchability parameters for all
+populations ($Q_{p} = 1$). This approximates a real world survey design with
+limited seasonal and spatial coverage.
 
@@
 meet particular management goals \citep{Bailey2018}, our framework allows users
-to explore the assumptions in modelling observations data and evaluate the
+to explore the assumptions in modelling observational data and evaluate the
 underlying dynamics of such approaches at a fine spatial and temporal scale.
@@
 under a statistical modelling framework. \\
+
+COMPARE AGAINST OTHER MODELS: Osmose, Atlantis,... do they use rationale actors
+and economic profit making ?
 
@@
 
-Survey design \\
+Survey design - random, fixed, stratified - all possible to explore  \\
 
-commercial index standardization methods \\
+Assumptions in spatiotemporal models: GAMs, GLMMs, geostatistical models
+
+Natural mortality estimation
+
+Commercial index standardization methods - different spatial scales, individual
+vessels, data aggregation -- all these can be explored. \\
 

### 2019-07-11 write_up/Supplementary.tex
Updated text and output latex table of results
Updating supplementary figures
Tidying, discussion updates and additional figure

@@
 \begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/habitat}
+	\includegraphics[width = \linewidth]{../analysis/habitat}
 	\caption{habitat preference}
@@
 \begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{Plots/habitat_spwn}
+	\includegraphics[width = \linewidth]{../analysis/habitat_spwn}
 	\caption{spawning habitat preference}
@@
 	\includegraphics[width = \linewidth]{Plots/Temperature_gradient}
-	\caption{Spatiotemporal qemperature gradient}
+	\caption{Spatiotemporal temperature gradient}
 	\label{fig:3}
@@
 	\includegraphics[width = \linewidth]{Plots/vessel_move_value}
-	\caption{movement of a single vessel over a few trips overlaid on the
+	\caption{movement of a fleet over a single trip reference overlaid on the
 		value field (i.e. sum of the population abundance x catchability x value}
@@
 
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{./Plots/Matern}
+	\caption{Example of different implementation of the Matern correlation
+	function on autocorrelation distance}
+	\label{fig:16}
+\end{figure}
+
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width =0.6\linewidth]{./Plots/Closure_fishing_locations_yearly}
+	\caption{Closure fishing locations based on annual closures with a
+		coarse spatial resolution. Closure location can be seen in red
+	in relation to a) before the closure fishing locations, b) after the
+	closure fishing locations, c) species 3 habitat distribution}
+	\label{fig:17}
+\end{figure}
+
 \end{document}

### 2019-07-11 write_up/mixfishsim_ecolmod.tex
Added some text pointers
subheadings
Tidying, discussion updates and additional figure

@@
 	discard\added[id=JJ]{ing of fish}} \citep{Kennelly2002, Catchpole2008,
-	Bellido2011}\textcolor{red}{(ADD COSGROVE REFERENCE HERE)}.  \\
+	Bellido2011, Cosgrove2019}.  \\
 
@@
 	with real data}. We ii) compare, at different spatial and temporal
-aggregations, the simulated population distributions to samples from
+aggregations, the 'real population' distributions to samples from
 fisheries-dependent and fisheries independent catches to test if these are a
@@
 	timescale was to reflect that fish tend to aggregate in species
-	specific locations and range within a week is fairly limited
-	[\textcolor{red}{REF!!}].  Therefore this process approximated the
+	specific locations which have been observed to last around one to two
+	weeks \citep{Poos2007}.  Therefore this process approximated the
 	demographic shifts in fish populations throughout a year with seasonal
@@
 type strategy for individual vessels to maximise their catch from an unknown
-resource distribution (\cite{Bailey2018}). The decision to use an individual
-based model for fishing vessels was taken because fishers as a group tend to
-show heterogeneity and individual rather than group dynamics
-[\textcolor{red}{REF!}]. Therefore in the simulations fleet dynamics are the
-productive of individual experiences rather than pre-defined group dynamics.
+resource distribution \cite{Bailey2018}. The decision to use an individual
+based model for fishing vessels was taken because fishers are heterogeneous in
+their location choice behaviour due to different objectives, risk preference
+and targeting preference \citep{VanPutten2012a}. Therefore in the simulations
+fleet dynamics are the productive of individual experiences rather than
+pre-defined group dynamics.
 
@@
 		kriging using the \emph{interp} function from the R package
-		akima [\textcolor{red}{REF!}].
+		akima \citep{Akima2006}.
 	\item Close area covering top 5 \% of catch rates 
@@
 In order to answer this question we compare different spatial and temporal
-aggregations of the simulated population distributions to:
+aggregations of the 'real population' distributions to:
 \begin{enumerate}[label=\alph*)]
@@
 data. Survey data starts to pick out some of the similar patterns as the other
-data sources, but lacks coverage. The spatial catch information on a 10 x 10
-and 20 x 20 grid lose a significant amount of information about the spatial
-resolutions for all data sources, and some differences between the survey,
-commercial and 'real population' data emerge. \\
+data sources, but lacks spatiotemporal coverage. The spatial catch information
+on a 10 x 10 and 20 x 20 grid lose a significant amount of information about
+the spatial resolutions for all data sources, and some differences between the
+survey, commercial and 'real population' data emerge. \\
 
@@
 the data over a ten-year period, with weekly (top), monthly (middle) and yearly
-(bottom) catch compositions from across an aggregated 20 x 20 area. As can be
-seen by comparison to the 'real population', the monthly aggregation captures
-the major patterns seen in the weekly data, albeit missing more subtle
-differences. The yearly data results in a constant catch pattern due to the
-aggregation process (sometimes known as an aggregation bias). The commercial
-data on a weekly basis shows some of the same patterns as the 'real
-population', though the first species (in red) is less well represented and
-some weeks are missing catches from the area. The monthly data shows some
-consistency between the 'real population' and commercial data for species 2 -
-4, though species 1 remains under-represented. On an annual basis,
-interestingly the commercial data under represents the first species (in red)
-while the survey over represents species 1. This is likely due to the biases in
+(bottom) catch compositions from across an aggregated 20 x 20 area. By
+comparison to the 'real population', the monthly aggregation captures the major
+patterns seen in the weekly data, albeit missing more subtle differences. The
+yearly data results in a constant catch pattern due to the aggregation process
+(sometimes known as an aggregation bias). The commercial data on a weekly basis
+shows some of the same patterns as the 'real population', though the first
+species (in red) is less well represented and some weeks are missing catches
+from the area. The monthly data shows some consistency between the 'real
+population' and commercial data for species 2 - 4, though species 1 remains
+under-represented. On an annual basis, interestingly the commercial data under
+represents the first species (in red) while the survey over represents species
+1. This is likely due to the biases in
 commercial sampling, with the fisheries not targeting the areas where species 1
@@
 
-A regression tree (using the R package REEMtree [ref]) highlights that the
-factor most contributing to differences in fishing mortality before and after
-the closure was the population (72 \% showing that the closures were effective
-for population 3), followed by data resolution (21 \%), data type (7 \%) with
-the least important factor the timescale ($<$ 1 \%). In general the finer the
-spatial resolution of the data used the greater reduction in fishing mortality
-for population 3 after the closures (Figure \ref{fig:4}). The notable outliers
-are the commercial data at the coarsest spatial resolution (20 x 20) at a
-yearly and weekly timescale, where closures were nearly as effective as the
-fine-scale resolution. In this case the closures were sufficiently large to
-protect the population (and was as effective as when the closure was based on
-the "real population"; \textcolor{red}{CHECK THIS, COULD PLOT ACTUAL CLOSURE
-	LOCATIONS??}) but this may have consequences in terms of restricting a
-much larger area than necessary. \\
+A regression tree (using the R package REEMtree \citep{Sela2012}) highlights
+that the factor most contributing to differences in fishing mortality before
+and after the closure was the population (72 \% showing that the closures were
+effective for population 3), followed by data resolution (21 \%), data type (7
+\%) with the least important factor the timescale ($<$ 1 \%). In general the
+finer the spatial resolution of the data used the greater reduction in fishing
+mortality for population 3 after the closures (Figure \ref{fig:4}). The notable
+outliers are the commercial data at the coarsest spatial resolution (20 x 20)
+at a yearly and weekly timescale, where closures were nearly as effective as
+the fine-scale resolution. In this case the closures were sufficiently large to
+protect a core are of the habitat for the population, but this was achieved in
+a fairly crude manner by closing a large area - including area where the
+species was not found (Figure \ref{S-fig:17}) which may have consequences in
+terms of restricting the fishery in a much larger area than necessary. \\
 
@@
 
+%% General intro
+
 Our study evaluates the importance of data scaling and considers potential bias
 introduced through data aggregation when using fisheries data to infer
-spatio-temporal dynamics of fish populations. Understanding how fishers exploit
+spatiotemporal dynamics of fish populations. Understanding how fishers exploit
 multiple heterogeneously distributed fish populations with different catch
@@
 sampling to identify potential impacts on management advice. With modern
-management approaches increasingly employing more nuanced spatio-temporal
+management approaches increasingly employing more nuanced spatiotemporal
 approaches in order to maximise productivity while taking account of both the
 biological and human processes operating on different time-frames
-\citep{Dunn2016}, understanding assumptions behind the data used -
-increasingly a combination of logbook and positional information from vessel
-monitoring systems - is vital to ensure measures are effective. \\
+\citep{Dunn2016}, understanding assumptions behind the data used - increasingly
+a combination of logbook and positional information from vessel monitoring
+systems - is vital to ensure measures are effective. \\
+
+\subsection{Simulation dynamics}
 
 We employ a simulation approach to model each of the population and fishery
-processes in a hypothetical 'mixed fishery', allowing us to i) evaluate the
+dynamics in a hypothetical 'mixed fishery', allowing us to i) evaluate the
 consequences of different aggregation assumptions on our understanding of the
-spatio-temporal distribution of the underlying fish populations, and ii)
+spatiotemporal distribution of the underlying fish populations, and ii)
 evaluate the effectiveness of a spatial closure given those assumptions. \\
 
-Our approach captures fine scale population and fishery dynamics and their
-interaction in a way not usually possible with real data and thus not usually
-considered in fisheries simulations. While other simulation frameworks seek to
-model individual vessel dynamics based on inferred dynamics from VMS and
-logbook records \citep{Bastardie2010}, or as a system to identify measures to
-meet particular management goals \citep{Bailey2018}, our framework allows users
-to explore the assumptions in modelling observational data and evaluate the
-underlying dynamics of such approaches at a fine spatial and temporal scale.
-This offers the advantage that larger scale fishery patterns are emergent
-properties of the system rather and results can be compared to those obtained
-under a statistical modelling framework. \\
+%% USP
+Our approach is unique in that it captures fine scale population and fishery
+dynamics and their interaction in a way not usually possible with real data and
+thus not usually considered in fisheries simulations. While other simulation
+frameworks seek to model individual vessel dynamics based on inferred dynamics
+from VMS and logbook records \citep{Bastardie2010}, or as a system to identify
+measures to meet particular management goals \citep{Bailey2018}, our framework
+allows users to explore the assumptions in modelling observational data and
+evaluate the underlying dynamics of such approaches at a fine spatial and
+temporal scale.  This offers the advantage that larger scale fishery patterns
+are emergent properties of the system rather and results can be compared to
+those obtained under a statistical modelling framework. \\
 
-COMPARE AGAINST OTHER MODELS: Osmose, Atlantis,... do they use rationale actors
-and economic profit making ?
+%% Comparison to other models
+Typically, simulation models which treat fish as individuals are focussed on
+exploring the inter- and intra- specific interactions among fish populations
+(e.g. OSMOSE \cite{Shin2004}) in order to understand how they vary over space
+and time. Our focus was on understanding how fleets which exploit multiple fish
+populations realise catch distributions which may differ from the underlying
+populations. As such, we favoured a minimum realistic model of the fish
+populations after \cite{Plaganyi2014}, while incorporating fishing dynamics
+which take account of different drivers in a mechanistic way, similarly to
+other approaches \citep{Fulton2011} but at an individual vessel rather than
+fleet level.
+
+\subsection{How does sampling-derived data reflect the underlying population
+	structure?}
+
+%% Why ours is important
 
@@
 
+%% key findings in context
+
+\subsection{How does data aggregation and source impact on spatial fisheries
+	management measures?}
+
 It seems clear that spatial disaggregation is more important than the temporal
@@
 pop, but good.  Make link to other studies -- read up on these. \\
+
+\subsection{Future application for framework}
 
@@
 mgmt... Wider applicability: birds, wildlife ??
+
+\subsection{Model assumptions and caveats}
 

### 2019-07-11 analysis/Plot_fishing.R

@@ -9,13 +9,13 @@ library(ggplot2)
 
 yrs <- c(29, 46) ## years before and after the closures
 
-#timescale <- "yearly"
+timescale <- "yearly"
 #timescale <- "monthly"
-timescale <- "weekly"
+#timescale <- "weekly"
 
 load('Common_Params.RData')
 
-if(timescale == "yearly")  { Run  <- 3 }
+if(timescale == "yearly")  { Run  <- 45 }
 if(timescale == "monthly") { Run  <- 2 }
 if(timescale == "weekly")  { Run  <- 1 }
 
@@ -63,6 +63,10 @@ closed_areas$dat   <- as.numeric(closed_areas$dat)
 }
 
 
+## habitat df
+
+hab.df <- data.frame(x = rep(1:100,100), y = rep(1:100, each = 100), hab = as.vector(hab$hab$spp3))
+
 ## Find bounds of area closures
 ## But we need to be able to keep areas as contiguous
 
@@ -95,8 +99,14 @@ p2 <- ggplot(cl) + geom_polygon(aes(long, lat, group = group), colour = "red",fi
 		   alpha = 0.2, shape = "x") +
 	theme_bw() + theme(plot.margin = margin(1, 0.5, 0.5, 0.5, "cm"))
 
-plot_grid(p1,p2, labels = c("(a) before closures", "(b) after closures"), vjust = 2)
-ggsave(file = "Closure_fishing_locations_yearly.pdf", width = 16, height = 8)
+p3 <- ggplot(cl) + geom_raster(aes(x, y, alpha = hab), data = filter(hab.df, hab > 0))+ 
+	geom_polygon(aes(long, lat, group = group), colour = "red",fill = NA) +
+	expand_limits(x = c(0,100), y = c(0,100)) + facet_wrap(~year) +
+	theme_bw() + theme(plot.margin = margin(1, 0.5, 0.5, 0.5, "cm"), 
+			   legend.position = "none")
+
+plot_grid(p1, p2, p3, labels = c("(a) before closures", "(b) after closures", "(c) habitat spp3" ), vjust = 2, ncol = 1)
+ggsave(file = "Closure_fishing_locations_yearly.png", width = 6, height = 18)
 
 }
 

### 2019-07-11 write_up/mixfishsim_ecolmod.tex
Additional discussion text

@@
 other approaches \citep{Fulton2011} but at an individual vessel rather than
-fleet level.
+fleet level. We do not explicitly define fleets as rational profit maximisers
+at the outset, but consider there are several stages to development of the
+fishery; information gathering through search where the resource location is
+not known,  followed by individual learnt behaviour of profitable locations.
+This provides a realistic model of how fishing patterns are established and
+maintained to exploit an uncertain resource \citep{Mangel1983, Bailey2018}.
 
@@
 
-Our results demonstrate the importance of data scale and resolution when using
-observational data to support management measures. In doing so it highlights
-depends on scale of process: pop movement etc... Important to consider how
-fishers interact / adapt to changes with the resource and mgmt. \\
+Our results demonstrate the importance of considering data scale and resolution
+when using observational data to support management measures. We find that
+understanding of the community composition dynamics will depend on the level of
+data aggregation and that its important to consider the scale of process;
+including population movement movement rates, habitat uniformity and fishing
+targeting practices if potential biases in data are going to be addressed. Two
+contrasting approaches in this respect were the spatial closures to protect cod
+in the North Sea. In one example, large scale spatial closures were implemented
+with little success due to effort displacement to previously unfished areas
+\citep{Dinmore2003}, while in another small scale targeted spatiotemporal
+closures were considered to have some effect in reducing cod mortality without
+having to disrupt other fisheries significantly \citep{Needle2011}. These
+emphasise the importance of considering the right scale and aggregation of data
+when identifying area closures.
+NOTE: CHECK THIS SECTION, IS A BIT "LOOSE".
+\\
 
 %% key findings in context
-
 \subsection{How does data aggregation and source impact on spatial fisheries
@@
 
-It seems clear that spatial disaggregation is more important than the temporal
-disaggregation of the commercial data... WHY
+From our simulations spatial disaggregation was more important than the
+temporal disaggregation of the commercial data. This reflects the fact that
+there was greater spatial heterogeneity over the spatial domain than
+experienced in individual locations over the course of the year. This indicates
+that fixed closures, if in the right locations, when based on commercially
+derived data have the potential to reduced fishing mortality. The likely cost
+of poor spatial and temporal resolution is associated with reduced
+effectiveness and potentially closing fishing opportunities for other
+fisheries. Our study showed that fishing rates on other populations also
+changed (both up and down) as a side-effect of closures to protect one species.
+This indicates the importance in considering fishing effort reallocation
+following spatial closures, and our simulation allows us to consider the
+spatiotemporal reasons for these changes.
 
-Closure scenarios demonstrate potential tor reduce F - not as high as with real
-pop, but good.  Make link to other studies -- read up on these. \\
+\subsection{Model assumptions and caveats}
+
+We model the population and fleet dynamic processes in order to draw inference
+on the importance of data scale and aggregation in understanding and managing
+mixed fisheries and their impact on multiple fish populations. In doing so, we
+have necessarily had to make a number of simplifying assumptions. \\
+
+Fish populations in our simulations move in pre-defined timescales and
+according to fixed habitat preferences and temperature gradients. Our
+assumptions in parametrising the model (movement rates, temperature tolerances)
+will have a direct impact on our conclusions on the relative importance of
+spatial and temporal processes. These assumptions could be explored in a future
+study by varying the parameters and assessing the robustness of our
+conclusions. \\
+
+In addition, we have assumed that fishing vessels are not restricted by quota
+and therefore discarding of species for which vessels have no quota or which
+are unwanted is not taken into account. This is likely to be a significant
+source of bias in any inference using commercial data and should also be
+explored. \\
 
@@
 
-\underline{The what next:} \\
+We consider that the increased availability of high resolution catch and
+locational information from commercial fisheries will require it to be a key
+source of data for ensuring management is implemented at the right scale in
+future. For example, identifying hot-spots for bycatch reduction or identifying
+spatial overlaps in mixed fisheries \citep{Dolder2018, Gardner2008, Little2014,
+	Dedman2015, Ward2015}. Our simulation model has the potential to test
+some of the assumptions behind the modelling approaches in identifying such
+hotspots and indeed behind spatiotemporal modelling in general (e.g. comparing
+GAMs, GLMMs, Random Forests and geostatistical models under different data
+generation processes as exampled by \cite{Stock2019}). \\
 
-Real world spatiotemp closures rarely been able to consider these issues /
-designed with these issues fully in mind - NS cod closures, plaice and trevose
-box... \\
+Other novel applications of our framework could be; testing different survey
+designs given multiple species and data generating assumptions; commercial
+index standardisation methods and approaches and understanding of appropriate
+scales and data aggregations; exploring assumptions about the distribution of
+natural mortality and fishing mortality throughout the year and importance of
+capturing in-year dynamics in estimating stock status; at sea sampling scheme
+designs to deliver unbiased estimates of population parameters; testing the
+ability of commonly employed fleet dynamics models such as Random Utility
+Models to capture finescale dynamics and understand their importance. \\
 
-Use of commercial data increasing - likely to become more important in future.
-Also collaborative approach with industry, e.g. hotspot mapping, spatiotemp
-advice... \\
-
-Other potential uses of the model \\
-
-Survey design - random, fixed, stratified - all possible to explore  \\
-
-Assumptions in spatiotemporal models: GAMs, GLMMs, geostatistical models
-
-Natural mortality estimation
-
-Commercial index standardization methods - different spatial scales, individual
-vessels, data aggregation -- all these can be explored. \\
-
-Sampling scheme design \\
-
-Testing fleet dynamics models at an aggregated level \\
+\section{Conclusions}
 
@@
 mgmt... Wider applicability: birds, wildlife ??
-
-\subsection{Model assumptions and caveats}
-
-\section{Conclusions}
 

### 2019-07-12 write_up/mixfishsim_ecolmod.tex
Discussion update

@@
 temporal scale.  This offers the advantage that larger scale fishery patterns
-are emergent properties of the system rather and results can be compared to
-those obtained under a statistical modelling framework. \\
+are emergent properties of the system and results can be compared to those
+obtained under a statistical modelling framework. \\
 
@@
 (e.g. OSMOSE \cite{Shin2004}) in order to understand how they vary over space
-and time. Our focus was on understanding how fleets which exploit multiple fish
-populations realise catch distributions which may differ from the underlying
-populations. As such, we favoured a minimum realistic model of the fish
-populations after \cite{Plaganyi2014}, while incorporating fishing dynamics
-which take account of different drivers in a mechanistic way, similarly to
-other approaches \citep{Fulton2011} but at an individual vessel rather than
-fleet level. We do not explicitly define fleets as rational profit maximisers
-at the outset, but consider there are several stages to development of the
-fishery; information gathering through search where the resource location is
-not known,  followed by individual learnt behaviour of profitable locations.
-This provides a realistic model of how fishing patterns are established and
-maintained to exploit an uncertain resource \citep{Mangel1983, Bailey2018}.
+and time. Our focus was on understanding the strengths and limitations of
+inference from catch data obtained through commercial fishing activity with
+fleets exploiting multiple fish populations and realising catch distributions
+which may differ from the underlying populations. As such, we favoured a
+minimum realistic model of the fish populations \citep{Plaganyi2014}, while
+incorporating detailed fishing dynamics which take account of different drivers
+in a mechanistic way. In this way we take account of heterogeneity in fleet
+dynamics due to different preferences and drivers similarly to other approaches
+\citep{Fulton2011}, but at an individual vessel rather than fleet level. We do
+not explicitly define fleets as rational profit maximisers at the outset, but
+consider there are several stages to development of the fishery; information
+gathering through search where the resource location is not known,  followed by
+individual learnt behaviour of profitable locations.  This provides a realistic
+model of how fishing patterns are established and maintained to exploit an
+uncertain resource through an explore-exploit strategy \citep{Mangel1983,
+	Bailey2018}.
 
@@
 including population movement movement rates, habitat uniformity and fishing
-targeting practices if potential biases in data are going to be addressed. Two
-contrasting approaches in this respect were the spatial closures to protect cod
-in the North Sea. In one example, large scale spatial closures were implemented
-with little success due to effort displacement to previously unfished areas
-\citep{Dinmore2003}, while in another small scale targeted spatiotemporal
-closures were considered to have some effect in reducing cod mortality without
-having to disrupt other fisheries significantly \citep{Needle2011}. These
-emphasise the importance of considering the right scale and aggregation of data
-when identifying area closures.
-NOTE: CHECK THIS SECTION, IS A BIT "LOOSE".
-\\
+targeting practices if potential biases in data are to be understood and taken
+into account. Two contrasting real world approaches in this respect were the
+spatial closures to protect cod in the North Sea. In one example, large scale
+spatial closures were implemented with little success due to effort
+displacement to previously unfished areas \citep{Dinmore2003}, while in another
+small scale targeted spatiotemporal closures were considered to have some
+effect in reducing cod mortality without having to disrupt other fisheries
+significantly \citep{Needle2011}. These examples emphasise the importance of
+considering the right scale and aggregation of data when identifying area
+closures and the need to consider changing dynamics in the fisheries in
+response to such closures. \\
 

### 2019-07-12 write_up/mixfishsim_ecolmod.tex
Which witch is which

@@
 the \textit{RFSimulate} function of the \textit{RandomFields} R package
-\citep{Schlater2015}, which simulates a Gaussian Random Field process given a
+\citep{Schlater2015}, that simulates a Gaussian Random Field process given a
 user defined error model and correlation structure. We define a stationary
@@
 	timescale was to reflect that fish tend to aggregate in species
-	specific locations which have been observed to last around one to two
+	specific locations that have been observed to last around one to two
 	weeks \citep{Poos2007}.  Therefore this process approximated the
@@
 The fleet dynamics can be broadly categorised into three components; fleet
-targeting - which determine\replaced[id=PD]{d}{s} the fleet catch efficiency
-and preference towards a particular species; trip-level decisions, which
-determine\added[id=PD]{d} the initial location to be fished at the beginning of
+targeting - that determines\replaced[id=PD]{d}{s} the fleet catch efficiency
+and preference towards a particular species; trip-level decisions, that 
+determines\added[id=PD]{d} the initial location to be fished at the beginning of
 a trip; and within-trip decisions, determining movement from one fishing spot
@@
 grounds, and choosing randomly from the top 75 \% of fishing events
-\replaced[id=PD]{as defined by the expected profit, which has a seasonal
+\replaced[id=PD]{as defined by the expected profit, that has a seasonal
 	component}{in value}.
@@
 the current fishing location.  The movement distance retains some degree of
-stochasticity, which can be controlled separately, but is determined by the
+stochasticity, that can be controlled separately, but is determined by the
 relationship: 
@@
 where $k$ the concentration parameter from the von \replaced[id=JJ]{M}{m}ises
-distribution which we correlate with the revenue so that $k = (Rev + 1 /
+distribution that we correlate with the revenue so that $k = (Rev + 1 /
 RefRev) * max_{k}$, where $max_{k}$ is the maximum concentration value, $k$,
@@
 \ref{S-fig:5}-\ref{S-fig:7}). In addition, each of the populations has two
-defined spawning areas which result in the populations moving towards these
+defined spawning areas that result in the populations moving towards these
 areas in pre-defined weeks (Figure \ref{S-fig:2}) with population-specific
@@
 location.  This probability was based on a logistic sigmoid function with a
-lower asymptote of 0 and upper asymptote of 0.95, and a growth rate which
+lower asymptote of 0 and upper asymptote of 0.95, and a growth rate that 
 ensures the upper asymptote (where decisions are mainly based on past
@@
 \end{enumerate}
-In total 28 closure scenarios were run which represent combinations of:
+In total 28 closure scenarios were run that represent combinations of:
 
@@
 experience during the explore phase of the fishery (\added[id=PD]{Figure}
-\ref{S-fig:14}), which is the result of the randomness in the correlated random
+\ref{S-fig:14}), that is the result of the randomness in the correlated random
 walk step function, with distance moved during the exploitation phase and the
@@
 	\item \textbf{fisheries-dependent data:} the inferred population from
-		our fleet model which includes fishery-induced sampling
+		our fleet model that includes fishery-induced sampling
 		dynamics.
@@
 implemented based on the coarsest spatial (20 x 20) and temporal resolution
-(yearly) which were ineffective with all data sources. As expected, closures
+(yearly) that was ineffective with all data sources. As expected, closures
 based on the "known" population distribution were most effective, with
@@
 a fairly crude manner by closing a large area - including area where the
-species was not found (Figure \ref{S-fig:17}) which may have consequences in
+species was not found (Figure \ref{S-fig:17}) that may have consequences in
 terms of restricting the fishery in a much larger area than necessary. \\
@@
 %% Comparison to other models
-Typically, simulation models which treat fish as individuals are focussed on
+Typically, simulation models that treat fish as individuals are focussed on
 exploring the inter- and intra- specific interactions among fish populations
@@
 fleets exploiting multiple fish populations and realising catch distributions
-which may differ from the underlying populations. As such, we favoured a
+that may differ from the underlying populations. As such, we favoured a
 minimum realistic model of the fish populations \citep{Plaganyi2014}, while
-incorporating detailed fishing dynamics which take account of different drivers
+incorporating detailed fishing dynamics that take account of different drivers
 in a mechanistic way. In this way we take account of heterogeneity in fleet
@@
 In addition, we have assumed that fishing vessels are not restricted by quota
-and therefore discarding of species for which vessels have no quota or which
+and therefore discarding of species for which vessels have no quota or that 
 are unwanted is not taken into account. This is likely to be a significant

### 2019-07-12 write_up/mixfishsim_ecolmod.tex
Move discussion around

@@
 understanding of the community composition dynamics will depend on the level of
-data aggregation and that its important to consider the scale of process;
-including population movement movement rates, habitat uniformity and fishing
-targeting practices if potential biases in data are to be understood and taken
-into account. Two contrasting real world approaches in this respect were the
-spatial closures to protect cod in the North Sea. In one example, large scale
-spatial closures were implemented with little success due to effort
-displacement to previously unfished areas \citep{Dinmore2003}, while in another
-small scale targeted spatiotemporal closures were considered to have some
-effect in reducing cod mortality without having to disrupt other fisheries
-significantly \citep{Needle2011}. These examples emphasise the importance of
-considering the right scale and aggregation of data when identifying area
-closures and the need to consider changing dynamics in the fisheries in
-response to such closures. \\
-
+data aggregation and its important to consider the scale of processes;
+including population movement rates, habitat uniformity and fishing targeting
+practices if potential biases in data are to be understood and taken into
+account. 
 %% key findings in context
@@
 there was greater spatial heterogeneity over the spatial domain than
-experienced in individual locations over the course of the year. This indicates
-that fixed closures, if in the right locations, when based on commercially
-derived data have the potential to reduced fishing mortality. The likely cost
-of poor spatial and temporal resolution is associated with reduced
-effectiveness and potentially closing fishing opportunities for other
-fisheries. Our study showed that fishing rates on other populations also
-changed (both up and down) as a side-effect of closures to protect one species.
-This indicates the importance in considering fishing effort reallocation
-following spatial closures, and our simulation allows us to consider the
-spatiotemporal reasons for these changes.
+experienced in individual locations over the course of the year (Figure
+\ref{S-fig:9}). This indicates that fixed closures, at the right resolution,
+when based on commercially derived data have the potential to reduced fishing
+mortality. The likely cost of poor spatial and temporal resolution is
+associated with reduced effectiveness and potentially closing fishing
+opportunities for other fisheries. \\
+
+Two contrasting real world approaches in this respect were the spatial closures
+to protect cod in the North Sea. In one example, large scale spatial closures
+were implemented with little success due to effort displacement to previously
+unfished areas \citep{Dinmore2003}, while in another small scale targeted
+spatiotemporal closures were considered to have some effect in reducing cod
+mortality without having to disrupt other fisheries significantly
+\citep{Needle2011}. These examples emphasise the importance of considering the
+right scale and aggregation of data when identifying area closures and the need
+to consider changing dynamics in the fisheries in response to such closures. \\
+
+Our study showed that fishing rates on other populations also changed (both up
+and down) as a side-effect of closures to protect one species.  This indicates
+the importance in considering fishing effort reallocation following spatial
+closures, and our simulation allows us to consider the spatiotemporal reasons
+for these changes.
 

### 2019-07-12 write_up/mixfishsim_ecolmod.tex
References added liberally

@@
 phases of the fisheries.  \\
+
+Our framework allows users to explore the assumptions in modelling observational
+data and evaluate the underlying dynamics of such approaches at a fine spatial
+and temporal scale. \\
 
@@
 mortality are the sum of those across all fleets and vessels, where $F_{fl, v,
-	c, d, p} = E_{fl, v, c, d} \cdot Q_{fl, p} \cdot B_{c, d, p}$ with
+	c, d, p} = E_{fl, v, c, d} \cdot Q_{fl, p} \cdot D_{c, d, p}$ with
 $fl$, $v$ and $p$ the fleet, vessel and population respectively and $E$ and $Q$
-fishing effort and catchability. \todo{\added[id=CM]{[link $F$ to effort and
+fishing effort and catchability of the gear, and $D$ is the density of the
+population at the location fished. \todo{\added[id=CM]{[link $F$ to effort and
 		catchability - as I think we have F as an emergent property of
@@
 account.
+
+EXPAND - relate to survey, commercial etc.. in Figure 2
+
 %% key findings in context
@@
 
-We model the population and fleet dynamic processes in order to draw inference
-on the importance of data scale and aggregation in understanding and managing
-mixed fisheries and their impact on multiple fish populations. In doing so, we
-have necessarily had to make a number of simplifying assumptions. \\
+We model the population and fleet dynamic processes to draw inference on the
+importance of data scale and aggregation in understanding and managing mixed
+fisheries and their impact on multiple fish populations. In doing so, we have
+necessarily had to make a number of simplifying assumptions. \\
 
 Fish populations in our simulations move in pre-defined timescales and
-according to fixed habitat preferences and temperature gradients. Our
-assumptions in parametrising the model (movement rates, temperature tolerances)
-will have a direct impact on our conclusions on the relative importance of
-spatial and temporal processes. These assumptions could be explored in a future
-study by varying the parameters and assessing the robustness of our
-conclusions. \\
+according to fixed habitat preferences and temperature gradients (Figures
+\ref{S-fig:1}, \ref{S-fig:3}). Our assumptions in parametrising the model
+(movement rates, temperature tolerances) will have a direct impact on our
+conclusions on the relative importance of spatial and temporal processes. These
+assumptions could be explored in a future study by varying the parameters and
+assessing the robustness of our conclusions. For our example application we
+have chosen movement rates to reflect aggregation periods observed in past
+studies \citep{Poos2007}. \\
 
 In addition, we have assumed that fishing vessels are not restricted by quota
-and therefore discarding of species for which vessels have no quota or that 
-are unwanted is not taken into account. This is likely to be a significant
-source of bias in any inference using commercial data and should also be
-explored. \\
-
-\subsection{Future application for framework}
+and therefore discarding of species for which vessels have no quota or that are
+unwanted is not taken into account. This is likely to be a significant source
+of bias in any inference using commercial data and should also be explored. For
+example, MixFishSim could be altered to allow for spatiotemporal appraisal of
+the impact of discarding on fisher behaviour and underlying populations via
+inclusion as discarding behaviour, or through move-on rules or cessation of
+fishing activity when quota is exhausted. \\
+
+\subsection{Future applications of MixFishSim}
 
@@
 Other novel applications of our framework could be; testing different survey
-designs given multiple species and data generating assumptions; commercial
-index standardisation methods and approaches and understanding of appropriate
-scales and data aggregations; exploring assumptions about the distribution of
-natural mortality and fishing mortality throughout the year and importance of
-capturing in-year dynamics in estimating stock status; at sea sampling scheme
-designs to deliver unbiased estimates of population parameters; testing the
-ability of commonly employed fleet dynamics models such as Random Utility
-Models to capture finescale dynamics and understand their importance. \\
+designs given multiple species and data generating assumptions \citep{Xu2015};
+commercial index standardisation methods and approaches and understanding of
+appropriate scales and data aggregations and non-proportionality in catch rate
+and abundance \citep{Harley2001, Maunder2004}; exploring assumptions about the
+distribution of natural mortality and fishing mortality throughout the year and
+importance of capturing in-year dynamics in estimating stock status
+\citep{Liu2013}; at sea sampling scheme designs to deliver unbiased estimates
+of population parameters \cite{Cotter2007, Kimura2006}; adaptive management
+\citep{Walters2007, Dunn2016}; testing the ability of commonly employed fleet
+dynamics models such as Random Utility Models to capture fine scale dynamics
+and understand their importance \cite{Girardin2016}; and as a detailed
+operating model in a management strategy evaluation \cite{Mahevas2004}. \\
 

### 2019-07-12 write_up/mixfishsim_ecolmod.tex
Conclusion written

@@
 %% General intro
-
 Our study evaluates the importance of data scaling and considers potential bias
@@
 practices if potential biases in data are to be understood and taken into
-account.
-
-EXPAND - relate to survey, commercial etc.. in Figure 2
+account. \\
+
+Our simulation shows that, despite biases introduced through the fishing
+process, the commercially derived data could still inform on the key spatial
+patterns in the community structures where the fisheries occurred, which was
+spatially limited due to the ``hotspots" of commercially valuable species being
+fished. Similarly, despite the even spatial coverage the survey was able to
+capture some of the same spatial patterns as the 'real population', but missed
+others due to gaps between survey stations limiting spatial and temporal
+coverage. This provides a challenge when modelling unsampled areas in inferring
+species distribution maps, though these limitations may be overcome by
+understanding the relationship between the species and habitat covariates where
+these are known at unsampled locations \citep{Robinson2011}. \\
 
@@
 
-Bigger picture stuff::  LO, increasing desire for more nuanced spatiotemp
-mgmt... Wider applicability: birds, wildlife ??
-
-Study shows ....\\
-
-This is important because .... \\
-
-How we might apply this in future .... \\
+MixFishSim provides a detailed simulation framework to explore the interaction
+of multiple fisheries exploiting different fish populations. The framework
+enables users to evaluate assumptions in modelling commercially derived data
+through comparison to the true underlying dynamics at a fine spatial and
+temporal scale.  Understanding these dynamics, the limitations of the data and
+any potential biases that may be introduced when making inference on
+spatiotemporal interactions will enable users to identify weaknesses in
+modelling approaches and identity where data collection is needed to strengthen
+inference. \\
+
+Our application shows that inference on community dynamics may change depending
+on the scale of data aggregation. There is an important balance in ensuring
+that the data are sufficiently spatially and temporally disaggregated that the
+main features of the data are captured, yet maintaining enough data coverage
+that the features can be distinguished. We found in our application that there
+was greater spatial heterogeneity than temporal heterogeneity and that when
+using aggregated data to define spatial closures coarser temporal resolution
+(months instead of weeks) could still achieve the same results in reducing
+exploitation rates of a vulnerable species at the highest temporal resolution
+data. Conversely, reducing the spatial resolution had a negative effect on the
+effectiveness of the measures (though importantly, there was still some benefit
+even with coarse spatial resolution). \\
+
+While any findings are likely to be case specific, our findings emphasise the
+need to understand population demographics, habitat use and movement rates in
+designing any closure scenario based on observational sampling. This
+information can then be used to set the bounds on data aggregation used in
+modelling studies aimed at informing the management measures. \\
+
+MixFishSim has numerous potential additional applications as it enables the
+user to apply methods to a fisheries system where there is detailed
+understanding of underlying spatiotemporal dynamics. This enables
+identification of weaknesses or limitations which would not be possible
+otherwise. In future, we recommend use of the framework to test hypothesis that
+are otherwise unable to be analysed using real world data due to limitations of
+data collection. That way the knowledge gained through simulation can inform
+the future design of management measures.
 

### 2019-07-18 write_up/mixfishsim_ecolmod.tex
Clean up abstract
mixfish corrections

@@
 
-\replaced[id = PD]{If fisheries are to avoid unwanted catch}{To implement
+\replaced[id = PD]{If fisheries are to avoid unwanted catch,}{To implement
 	effective spatial measures to reduce discards} a good understanding of
@@
 To understand how data resolution impacts inference on mixed fisheries
-interactions, we develop a highly resolved spatiotemporal simulation model
+interactions, we developed a highly resolved spatiotemporal simulation model
 incorporating: i) delay-difference population dynamics, ii) population movement
@@
 
-Our framework allows users to explore the assumptions in modelling observational
-data and evaluate the underlying dynamics of such approaches at a fine spatial
-and temporal scale. \\
-
-We simulate 50 years of fishing and use the results from the fisheries catch to
-draw inference on the underlying population structures. We compare this
+We simulated 50 years of fishing and used the results from the fisheries catch
+to draw inference on the underlying community structures. We compared this
 inference to a simulated fixed-site sampling design commonly used for fisheries
-monitoring purposes and the true underlying population structures. We i) use
+monitoring purposes and the true underlying community structure. We i) used
 the results to establish the potential and limitations of fishery-dependent
 data in providing a robust picture of spatiotemporal distributions; and ii)
-simulate an area closure based on areas defined from the different data sources
-at a range of temporal and spatial resolutions and assess their effectiveness
+simulated an area closure based on areas defined from the different data sources
+at a range of temporal and spatial resolutions to assess their effectiveness
 on reducing catches of a fish population. \\
 
-We conclude from our simulations that commercial data, while containing bias,
-provides a useful tool for managing catches in mixed fisheries if applied at
-the correct spatiotemporal scale. \\
-
-[333 words]
+Our framework allows users to explore the assumptions in modelling
+observational data and evaluate the underlying dynamics of such approaches at a
+fine spatial and temporal scale. We conclude from our simulations that
+commercial data, while containing bias, provide a useful tool for managing
+catches in mixed fisheries if applied at the correct spatiotemporal scale. \\
 
@@
 Fishers exploit a variety of fish populations that are heterogeneously
-distributed in space and time, with varying knowledge of species distributions
-and using species non-selective fishing gear. \added[id=PD]{In doing so}
-fisheries \deleted[id=PD]{that}catch an assemblage of species
-\added[id=PD]{and}\deleted{, known as mixed fisheries} \replaced[id=JJ]{may}{,
-	when managed by single-species quotas can end up}
+distributed in space and time, with varying knowledge of species
+distributions\deleted[id=JJ]{ and using species non-selective fishing gear}.
+\added[id=PD]{In doing so} fisheries \deleted[id=PD]{that}catch an assemblage
+of species \added[id=PD]{and}\deleted{, known as mixed fisheries}
+\replaced[id=JJ]{may}{, when managed by single-species quotas can end up}
 discard\deleted[id=JJ]{ing} over-quota catch \added[id=JJ]{when managed by
@@
 
-\replaced[id=PD]{Changes to spatial fishing patterns have}{Use of spatial
-	management as a tools} been proposed as a method to reduce discards
+\replaced[id=PD]{Adaptive spatial management strategies have}{Use of spatial
+	management as a tools} been proposed as a way of reducing discards
 \added[id=PD]{\citep{Holmes2011, Little2014, Dunn2014a}}.  \deleted[id=PD]{its}
@@
 scale at which processes become important for management. Understanding the
-correct scale for spatial measures is crucial for implementation at a
+correct scale for spatial measures is crucial for implementing solutions at a
 resolution that ensures effective management \citep{Dunn2016} while minimising
-economic impact.  For example, a scale that promotes species avoidance for
-vulnerable or low quota species while allowing continuance of sustainable
-fisheries for available quota species.\\
-
-\replaced[id=PD]{Identifying}{Ensuring measures are implemented at} an
-appropriate scale has been a challenge in the past that has led to ineffectual
-measures with unintended consequences such as limited impact towards the
-management objective or increased benthic impact on previously unexploited
-areas (e.g. the cod closure in the North Sea
-\citep{Rijnsdorp2001,Dinmore2003}). \replaced[id=PD]{M}{Since then m}ore
-refined spatial information has \added[id=PD]{since} become available through
-the combination of logbook and Vessel Monitoring System (VMS) data
-\citep{Lee2010, Bastardie2010, Gerritsen2012, Mateo2016} and more real-time
-spatial management has been possible \citep[e.g.][]{Holmes2011}.  Such
+economic impact.  For example, the problem can be to identify a scale that
+promotes species avoidance for vulnerable or low quota species while allowing
+continuance of sustainable fisheries for available quota species.\\
+
+\replaced[id=PD]{Identifying}{Ensuring measures are implemented at} appropriate
+scales for spatial fisheries management has been a challenge in the past that
+has led to ineffectual measures with unintended consequences. These unintended
+consequences limited impacts towards management objectives, or increased
+benthic impact on previously unexploited areas (e.g.  the cod closure in the
+North Sea \citep{Rijnsdorp2001,Dinmore2003}). SENTENCE HERE ATTRIBUTING THE
+CHALLENGE OF IDENTIFYING APPROPRIATE SCALES TO COURSE SPATIAL INFORMATION.
+\replaced[id=PD]{M}{Since then
+	m}ore refined spatial information has \added[id=PD]{since} become
+available through the combination of logbook and Vessel Monitoring System (VMS)
+data \citep{Lee2010, Bastardie2010, Gerritsen2012, Mateo2016} and more
+real-time spatial management has been possible \citep[e.g.][]{Holmes2011}.
+Such
 information is, however, derived from an inherently biased sampling programme,
@@
 
-\replaced[id=PD]{We ask two fundamental questions regarding spatiotemporal
+\replaced[id=PD]{In order to understand the effect of spatiotemporal
+	aggregation of data we ask two fundamental questions regarding
 	inference derived from observational data:}{ and use the
@@
 \begin{enumerate}
-	\item How does sampling-derived data reflects the underlying population
-		structures? 	
+	\item How does sampling-derived data reflects the underlying community 
+		structure? 	
 	\item How does data aggregation and source impact on spatial fisheries
@@
 	how inference from fisheries-dependent and fisheries independent
-	sampling relates to the real population structure in a way we could not
+	sampling relates to the real community structure in a way we could not
 	with real data}. We ii) compare, at different spatial and temporal
@@
 
-[We find..]
-
 \section{Materials and Methods}
@@
 
-%% the tikz figure
-\clearpage
-\input{Process_model.tex}
-
 \subsection{Population dynamics}
 
-The basic population level processes are simulated using a modified two-stage
+The basic population level processes were simulated using a modified two-stage
 Deriso-Schnute delay difference model \citep{Deriso1980, Schnute1985,
@@
 	biologically relevant and computationally tractable timescale.}
-\replaced[id=PD]{Under the population dynamics module}{Here,} population
+\deleted[id=PD]{Here,}Population
 biomass growth and depletion for pre-recruits and\deleted[id=PD]{fish}
-recruited \added[id=PD]{fish}\deleted[id=PD]{to the fishery} are modelled
+recruited \added[id=PD]{fish}\deleted[id=PD]{to the fishery} were modelled
 separately as a function of previous recruited biomass, intrinsic population
 growth and recruitment functionally linked to the adult population size.
-Biomass for each cell $c$ is incremented each day $d$ as follows (the full
-parameter list is detailed in Table \ref{tab: pop_variable}): \begin{equation}
+Biomass for each cell $c$ was incremented each day $d$ as follows (the full
+parameter list is detailed in Table \ref{tab: pop_variable}): 
+\begin{equation}
 	\begin{split}
@@
 \begin{equation}
-C_{c,d} = \frac{F_{c,d}}{F_{c,d} + M_{c,d}} * (1 - e^{-(F_{c,d} + M_{c,d})}) *
-B_{c,d}
+C_{c,d} = \frac{F_{c,d}}{F_{c,d} + M_{c,d}} * (1 - e^{-(F_{c,d} + M_{c,d})})
+\cdot B_{c,d}
 \end{equation}
@@
 	\begin{split}
-	\bar{R}_{c,d} = & \frac{(\alpha * S_{c,d})}{(\beta + S_{c,d})} \\
+	\bar{R}_{c,d} = & \frac{(\alpha \cdot S_{c,d})}{(\beta + S_{c,d})} \\
 	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\sigma^2)]
@@
 	\begin{split}
-	\bar{R}_{c,d} = & B_{c,d} * e^{(\alpha - \beta * B_{c,d})} \\	
+	\bar{R}_{c,d} = & B_{c,d} \cdot e^{(\alpha - \beta \cdot B_{c,d})} \\	
    	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\log(\sigma^2))]
@@
 	employed} a Gaussian spatial process \added[id=JJ]{was employed} to
-model habitat suitability for each of the populations on a 2d grid. \\
+model habitat suitability for each of the populations on a 2d grid. JM: MENTION
+IN THE INTRODUCTION \\
 
@@
 \replaced[id=PD]{was}{is} initialised at a single location, and subsequently
-move\replaced[id=PD]{ed}{s} according to a probabilistic
+move\replaced[id=PD]{d}{s} according to a probabilistic
 distrib\added[id=PD]{u}tion based on habitat suitability (represented by the
@@
 
-During pre-defined weeks of the year the habitat quality is modified with
+During pre-defined weeks of the year the habitat suitability is modified with
 \added[id=PD]{user-defined} spawning habitat locations\deleted[id=PD]{s},
@@
 		the areas are pre-defined - I have amended to reflect and tried
-		to clarify}} \\
+		to clarify}} \\ JM: WHAT ABOUT INDIVIDUAL INTERACTIONS:w
 
@@
 The fleet dynamics can be broadly categorised into three components; fleet
-targeting - that determines\replaced[id=PD]{d}{s} the fleet catch efficiency
-and preference towards a particular species; trip-level decisions, that 
-determines\added[id=PD]{d} the initial location to be fished at the beginning of
-a trip; and within-trip decisions, determining movement from one fishing spot
-to another within a trip. Together, these elements implement an explore-exploit
-type strategy for individual vessels to maximise their catch from an unknown
-resource distribution \cite{Bailey2018}. The decision to use an individual
-based model for fishing vessels was taken because fishers are heterogeneous in
-their location choice behaviour due to different objectives, risk preference
-and targeting preference \citep{VanPutten2012a}. Therefore in the simulations
-fleet dynamics are the productive of individual experiences rather than
-pre-defined group dynamics.
+targeting - that determined the fleet catch efficiency and preference towards a
+particular species; trip-level decisions, that determined the initial location
+to be fished at the beginning of a trip; and within-trip decisions, that
+determined movement from one fishing spot to another within a trip. Together,
+these elements implemented an explore-exploit type strategy for individual
+vessels to maximise their catch from an unknown resource distribution
+\cite{Bailey2018}.  The decision to use an individual based model for fishing
+vessels was taken because fishers are heterogeneous in their location choice
+behaviour due to different objectives, risk preference and targeting preference
+\citep{VanPutten2012a}. Therefore in the simulations fleet dynamics are the
+productive of individual experiences rather than pre-defined group dynamics.
 
@@
 heavily fished areas less attractive as a future fishing location choice as
-reduced catch rates will be experienced.
+reduced catch rates will be experienced. JM: INTERFERENCE COMPETITION COULD
+ALSO BE REPRESENTED BY A LIMITATION FACTOR
 
@@
 
-\subsection{Software}
+\subsection{Software: R-package development}
 
@@
 \ref{tab:1}). Habitat preference (Figure \ref{S-fig:1}) and temperature
-tolerances (Figures \ref{S-fig:3}, \ref{S-fig:4}) were unique to each
-population resulting in differently weekly distribution patterns (Figures
-\ref{S-fig:5}-\ref{S-fig:7}). In addition, each of the populations has two
-defined spawning areas that result in the populations moving towards these
-areas in pre-defined weeks (Figure \ref{S-fig:2}) with population-specific
-movement rates (Table \ref{tab:1}). The individual habitat preferences and
-thermal tolerances result in different spatial habitat use for each population
-(Figure \ref{S-fig:9}) and consequently different seasonal exploitation
-patterns (Fishing mortality in Figure \ref{S-fig:10}).
+tolerances (Figures \ref{S-fig:3}, \ref{S-fig:4}) were defined to be unique to
+each population resulting in differently weekly distribution patterns (Figures
+\ref{S-fig:5}-\ref{S-fig:7}). In addition, each of the populations was assumed
+to have two defined spawning areas that result in the populations moving
+towards these areas in pre-defined weeks (Figure \ref{S-fig:2}) with
+population-specific movement rates (Table \ref{tab:1}). In such a
+configuration, the individual habitat preferences and thermal tolerances result
+in different spatial habitat use for each population (Figure \ref{S-fig:9}) and
+consequently different seasonal exploitation patterns (Fishing mortality in
+Figure \ref{S-fig:10}).
 
@@
 	dynamics, preferentially targeted different fish populations}.  The
-stochasticity in the random walk process ensures that within a fleet different
-vessels have slightly different spatial distributions based on individual
-experience. The step function was parametrised dynamically within the
-simulations as the maximum revenue obtainable was not known beforehand. This
-was implemented so that vessels take smaller steps when fishing at a location
-that yields landings value in the top 90th percentile of the value experienced
-in that year so far (as defined per fleet in Table \ref{tab:2}). \\
+random walk process implies that within a fleet different vessels have
+different spatial distributions based on individual experience. The step
+function was parametrised dynamically within the simulations as the maximum
+revenue obtainable was not known beforehand. This was implemented so that
+vessels take smaller steps when fishing at a location that yields landings
+value in the top 90th percentile of the value experienced in that year so far
+(as defined per fleet in Table \ref{tab:2}). \\
 
@@
 was defined as the locations where the top 70 \% of expected profit would be
-found given previous trips revenue and cost of movement to the new fishing
+found given revenue from previous trips and cost of movement to the new fishing
 location. This probability was based on a logistic sigmoid function with a
@@
 		kriging using the \emph{interp} function from the R package
-		akima \citep{Akima2006}.
+		akima \citep{Akima2006}. JM: SEE COMMENT
 	\item Close area covering top 5 \% of catch rates 
@@
 
-%%%% figures
+%%%%%%%%%%%%%%%%%
+%%%% figures %%%%
+%%%%%%%%%%%%%%%%%
+
+%% the tikz figure
+\clearpage
+\input{Process_model.tex}
+
 \begin{figure}[!ht]

### 2019-07-18 write_up/parameter_tables.tex
Clean up text
mixfish corrections

@@
 		$\tilde{R}_{c,d}$ & is the recruitment in cell $c$ for day $d$ & $d^{-1}$ \\
-		$B_{c,d}$ & is the Biomass in cell $c$ for day $d$ & $d^{-1}$ \\
+		$S_{c,d}$ & is the stock size in cell $c$ for day $d$ & $d^{-1}$ \\
 		$\alpha$ & the maximum recruitment rate & kg  \\
-		$\beta$ & the biomass required to produce half the maximum rate
+		$\beta$ & the stock size required to produce half the maximum rate
 		of recruitment & kg \\
@@
 	\hline
-	Targeting preferences &&&& \\
+	Targeting preferences & pop 2/4 & pop 1/3 & - & pop 4 & pop
+	2/3 \\
 	\hline

### 2019-07-28 write_up/mixfishsim_ecolmod.tex
Revisions

@@
 To answer these questions we i) develop a simulation model where population
-dynamics are highly-resolved in space and time\replaced[id=PD]{. Being}{ and
-	are} known \added[id=PD]{directly} rather than inferred from sampling
-or commercial catch\added[id=PD]{, we can use the population model to validate
-	how inference from fisheries-dependent and fisheries independent
-	sampling relates to the real community structure in a way we could not
-	with real data}. We ii) compare, at different spatial and temporal
-aggregations, the 'real population' distributions to samples from
+dynamics are highly-resolved in space and time by use of a Gaussian spatial
+process to define suitable habitat\replaced[id=PD]{. Precise locations being}{
+	and are} known \added[id=PD]{directly} rather than inferred from
+sampling or commercial catch\added[id=PD]{, we can use the population model to
+	validate how inference from fisheries-dependent and fisheries
+	independent sampling relates to the real community structure in a way
+	we could not with real data}. We ii) compare, at different spatial and
+temporal aggregations, the 'real population' distributions to samples from
 fisheries-dependent and fisheries independent catches to test if these are a
@@
 \deleted[id=PD]{The fishing model operated on a tow-by-tow basis, while}
-\replaced[id=PD]{P}{p}opulation dynamics (fishing and natural mortality,
-growth) operate on a daily time-step\replaced[id=PD]{, while p}{. P}opulation
-movement occurs on a weekly time-step\replaced[id=PD]{. R}{, while r}ecruitment
-\replaced[id=PD]{takes place}{occurs} periodically each year for a set time
+\replaced[id=PD]{P}{p}opulation dynamics (fishing and natural mortality which
+are instantaneous rates, growth of the population biomass) operate on a daily
+time-step\replaced[id=PD]{, while p}{. P}opulation movement occurs on a weekly
+time-step\replaced[id=PD]{. R}{, while r}ecruitment \replaced[id=PD]{takes
+	place}{occurs} periodically each year for a set time
 \replaced[id=PD]{duration}{period (e.g. 3 weeks)} specified for each
@@
 
-\replaced[id=PD]{In the model system p}{P}opulation movement is driven by
-random (diffusive) and directed (advective) processes and we incorporate
-characterisation of a number of different fishing \added[id=PD]{fleet dynamics}
-exploiting four fish populations with different spatial and population
-demographics. The following describes the implementation of each of the
-sub-modules.
+Population movement is a combination of random (diffusive) movement, governed
+by a stochastic process where movement between adjacent cells is described by a
+set of probabilities, and directed (advective) movement where at certain times
+of year the population moves towards spawning grounds by increasing the
+probabilities of moving into the spawning grounds from adjacent cells. We
+incorporate characterisation of a number of different fishing
+\added[id=PD]{fleet dynamics} exploiting four fish populations with different
+spatial and population demographics. The following describes the implementation
+of each of the sub-modules.
 
@@
 The basic population level processes were simulated using a modified two-stage
-Deriso-Schnute delay difference model \citep{Deriso1980, Schnute1985,
-	Dichmont2003} occurring at a daily time-step. \added[id=PD]{A daily
-	time-step was chosen to discretise continuous population processes on a
-	biologically relevant and computationally tractable timescale.}
-\deleted[id=PD]{Here,}Population
-biomass growth and depletion for pre-recruits and\deleted[id=PD]{fish}
-recruited \added[id=PD]{fish}\deleted[id=PD]{to the fishery} were modelled
-separately as a function of previous recruited biomass, intrinsic population
-growth and recruitment functionally linked to the adult population size.
-Biomass for each cell $c$ was incremented each day $d$ as follows (the full
-parameter list is detailed in Table \ref{tab: pop_variable}): 
+Deriso-Schnute delay difference model which models the fish populations in
+terms of aggregate biomass of recruits and mature components rather than
+keeping track of individuals\citep{Deriso1980, Schnute1985, Dichmont2003}.
+\added[id=PD]{A daily time-step was chosen to discretise continuous population
+	processes on a biologically relevant and computationally tractable
+	timescale.} \deleted[id=PD]{Here,}Population biomass growth and
+depletion for pre-recruits and\deleted[id=PD]{fish} recruited
+\added[id=PD]{fish}\deleted[id=PD]{to the fishery} were modelled separately as
+a function of previous recruited biomass, intrinsic population growth and
+recruitment functionally linked to the adult population size.  Biomass for each
+cell $c$ was incremented each day $d$ as follows (the full parameter list is
+detailed in Table \ref{tab: pop_variable}): 
 \begin{equation}
@@
 station survey design). Catches of the populations \replaced[id=JJ]{at each
-station}{present} are recorded but not removed from the population. This
+	station}{present} are recorded but not removed from the population
+(catches are assumed to have negligible impact on population dynamics). This
 provides a fishery independent snapshot of the populations at a regular spatial
@@
 	\item Interpolate across entire area at desired resolution using simple
-		kriging using the \emph{interp} function from the R package
-		akima \citep{Akima2006}. JM: SEE COMMENT
+		bivariate kriging using the \emph{interp} function from the R
+		package akima \citep{Akima2006}. This is intended to represent
+		a naive spatial model of catch rates, without knowledge of the
+		spatial population dynamics.
 	\item Close area covering top 5 \% of catch rates 
@@
 
-Vessels from the same fleet (and therefore targeting preference) exploit
-similar but slightly different fishing grounds depending on their own personal
+Vessels from the same fleet (and therefore targeting preference) may exploit
+some shared and some different fishing grounds depending on their own personal
 experience during the explore phase of the fishery (\added[id=PD]{Figure}
-\ref{S-fig:14}), that is the result of the randomness in the correlated random
-walk step function, with distance moved during the exploitation phase and the
+\ref{S-fig:14}). This results from the randomness in the correlated random walk
+step function, with distance moved during the exploitation phase and the
 direction stochastically related to the revenue experienced on the fishing
@@
 patterns seen in the weekly data, albeit missing more subtle differences. The
-yearly data results in a constant catch pattern due to the aggregation process
-(sometimes known as an aggregation bias). The commercial data on a weekly basis
-shows some of the same patterns as the 'real population', though the first
-species (in red) is less well represented and some weeks are missing catches
-from the area. The monthly data shows some consistency between the 'real
-population' and commercial data for species 2 - 4, though species 1 remains
-under-represented. On an annual basis, interestingly the commercial data under
-represents the first species (in red) while the survey over represents species
-1. This is likely due to the biases in
-commercial sampling, with the fisheries not targeting the areas where species 1
-are present, and the biases in the survey sampling from over representation of
+yearly data assumes the same proportion of each population caught at any time
+of the year due to the data aggregation. This assumption introduces
+`aggregation bias' as the data may only be representative of some point (or no
+point) in time. The commercial data on a weekly basis shows some of the same
+patterns as the 'real population', though the first species (in red) is less
+well represented and some weeks are missing catches from the area. The monthly
+data shows some consistency between the 'real population' and commercial data
+for species 2 - 4, though species 1 remains under-represented. On an annual
+basis, interestingly the commercial data under represents the first species (in
+red) while the survey over represents species
+1. This is likely due to the biases in commercial sampling, with the fisheries
+not targeting the areas where species 1 are present, and the biases in the
+survey sampling from over representation of
 the spatial distribution.

### 2019-07-29 write_up/mixfishsim_ecolmod.tex
Revisions in response to JJP and JMG

@@
 \replaced[id=PD]{Identifying}{Ensuring measures are implemented at} appropriate
-scales for spatial fisheries management has been a challenge in the past that
-has led to ineffectual measures with unintended consequences. These unintended
-consequences limited impacts towards management objectives, or increased
-benthic impact on previously unexploited areas (e.g.  the cod closure in the
-North Sea \citep{Rijnsdorp2001,Dinmore2003}). SENTENCE HERE ATTRIBUTING THE
-CHALLENGE OF IDENTIFYING APPROPRIATE SCALES TO COURSE SPATIAL INFORMATION.
-\replaced[id=PD]{M}{Since then
-	m}ore refined spatial information has \added[id=PD]{since} become
-available through the combination of logbook and Vessel Monitoring System (VMS)
-data \citep{Lee2010, Bastardie2010, Gerritsen2012, Mateo2016} and more
-real-time spatial management has been possible \citep[e.g.][]{Holmes2011}.
-Such
+spatial scales for fisheries closures has been a challenge in the past but
+identified as crucial to its success \citep{Costello2010, Dunn2016}. Further,
+poorly sited closures have led to ineffectual measures with unintended
+consequences. For example, increased benthic impact on previously unexploited
+areas was observed from the cod closure in the North Sea with a lack of
+observed intended effect in reducing cod exploitation
+\citep{Rijnsdorp2001,Dinmore2003}). \replaced[id=PD]{M}{Since then m}ore
+refined spatiotemporal information has \added[id=PD]{since} become available
+through the combination of logbook and Vessel Monitoring System (VMS) data
+\citep{Lee2010, Bastardie2010, Gerritsen2012, Mateo2016} and more real-time
+spatial management has been possible \citep[e.g.][]{Holmes2011}.  Such
 information is, however, derived from an inherently biased sampling programme,
@@
 basis, interestingly the commercial data under represents the first species (in
-red) while the survey over represents species
-1. This is likely due to the biases in commercial sampling, with the fisheries
-not targeting the areas where species 1 are present, and the biases in the
-survey sampling from over representation of
-the spatial distribution.
+red) while the survey over represents species 1. This is likely due to the
+biases in commercial sampling, with the fisheries not targeting the areas where
+species 1 are present and the survey sampling areas where species 1 is more
+abundant than on average.
 

### 2019-07-31 write_up/Supplementary.tex
Updated figures

@@
 \begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{Plots/pop_dist}
-	\caption{Simulated spatial dynamics - the four populations at four time steps.
-		}
-	\label{fig:9}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{Plots/f_dynamics}
-	\caption{f dynamics - the daily fishing mortalities, each year is a
-		different colour}
-	\label{fig:10}
-\end{figure}
-
-\begin{figure}[!ht]
 	\includegraphics[width = \linewidth]{Plots/vessel_move}
@@
 	\label{fig:12}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{Plots/vessel_move_value}
-	\caption{movement of a fleet over a single trip reference overlaid on the
-		value field (i.e. sum of the population abundance x catchability x value}
-	\label{fig:13}
 \end{figure}
@@
 
-\begin{figure}[!ht]
-	\centering
-	\includegraphics[width =0.6\linewidth]{./Plots/Closure_fishing_locations_yearly}
-	\caption{Closure fishing locations based on annual closures with a
-		coarse spatial resolution. Closure location can be seen in red
-	in relation to a) before the closure fishing locations, b) after the
-	closure fishing locations, c) species 3 habitat distribution}
-	\label{fig:17}
-\end{figure}
-
 \end{document}

### 2019-07-31 write_up/mixfishsim_ecolmod.tex
Updated figures

@@
 configuration, the individual habitat preferences and thermal tolerances result
-in different spatial habitat use for each population (Figure \ref{S-fig:9}) and
+in different spatial habitat use for each population (Figure \ref{fig:9}) and
 consequently different seasonal exploitation patterns (Fishing mortality in
-Figure \ref{S-fig:10}).
+Figure \ref{fig:10}).
 
@@
 areas where the highest revenue were experienced, as shown by
-\added[id=PD]{Figure} \ref{S-fig:13}, where several trips for the vessel
+\added[id=PD]{Figure} \ref{fig:13}, where several trips for the vessel
 overlaid on the revenue field, i.e. 
@@
 a fairly crude manner by closing a large area - including area where the
-species was not found (Figure \ref{S-fig:17}) that may have consequences in
+species was not found (Figure \ref{fig:17}) that may have consequences in
 terms of restricting the fishery in a much larger area than necessary. \\
@@
 experienced in individual locations over the course of the year (Figure
-\ref{S-fig:9}). This indicates that fixed closures, at the right resolution,
+\ref{fig:9}). This indicates that fixed closures, at the right resolution,
 when based on commercially derived data have the potential to reduced fishing
@@
 \begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{Plots/pop_dist}
+	\caption{Simulated spatial dynamics - the four populations abundance
+		(log+1) at four time steps.
+		}
+	\label{fig:9}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{Plots/f_dynamics}
+	\caption{Fishing mortality dynamics - the daily fishing mortalities
+		showing weekly and seasonal patterns in exploitation.
+		Individual years and the light grey lines, the mean of all
+		years the thick black line}
+	\label{fig:10}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{Plots/vessel_move_value}
+	\caption{movement of a fleet over a single trip reference overlaid on the
+		value field (i.e. sum of the population abundance x catchability x value}
+	\label{fig:13}
+\end{figure}
+
+\begin{figure}[!ht]
 	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_space_Rev}
@@
 
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width =0.5\linewidth]{./Plots/Closure_fishing_locations_yearly}
+	\caption{Closure fishing locations based on annual closures with a
+		coarse spatial resolution. Closure location can be seen in red
+	in relation to a) before the closure fishing locations, b) after the
+	closure fishing locations, c) species 3 habitat distribution}
+	\label{fig:17}
+\end{figure}
+
 \clearpage

### 2019-07-31 analysis/Plot_Bio.R

@@ -1,5 +1,6 @@
 
 library(MixFishSim)
+library(RColorBrewer)
 
 Run <- 0
 
@@ -21,12 +22,14 @@ plot_catch_comp(gran = c(1), logs = logs, fleets = 1:5,
 
 ## Simple plot of distribution changes over time
 
+cols <- brewer.pal(9, "BuGn")
+
 png(file = file.path("..", "write_up","Plots", "pop_dist.png"), width = 1600, height = 1600)
 par(mfrow=c(4,4), mar = c(1,1,1,1))
 
 for(j in round(seq.int(1,52,length.out = 4),0)) {
 for(i in 1:4) {
-image(seq_len(100), seq_len(100), pop[[9,j]][[i]], col = terrain.colors(100))
+image(seq_len(100), seq_len(100), log(pop[[9,j]][[i]]+1), col = cols)
 if(i==1) {text(x = 9, y = 94, labels = paste("t =",j), cex= 2, font = 2)}
 if(j==1) {text(x = 92, y = 94, labels = paste("Pop ",i), cex = 2, font = 2)}
 }

### 2019-07-31 analysis/Plots.R

@@ -14,6 +14,39 @@ load(file.path('Scenario_runs_Nov18', paste0("Scenario_", Run, ".RData")))
 plot_pop_summary(res, timestep = "annual", save = FALSE)
 
 plot_daily_fdyn(res)
+
+
+daily_fdyn <- function (results) {
+	
+	n_spp <- length(res[["pop_summary"]]) 
+	res_spp <- lapply(seq_len(n_spp), function(x) {
+ 			 x1_res <- tidyr::gather(as.data.frame(t(results[["pop_summary"]][[x]][["F.mat"]])), key = "year", factor_key = T)
+			 F_df <- data.frame("pop" = paste0("spp_", x), 
+					    "day" = rep(1:362,length.out = nrow(x1_res)),
+					    "year" = x1_res$year,
+					    data = x1_res$value)
+			 
+				  })
+	res_out <- do.call(rbind, res_spp)
+
+	return(res_out)
+
+}
+
+library(tidyverse)
+
+df <- daily_fdyn(res)
+
+mean_f <- df %>% group_by(pop, day) %>%
+	summarise(data = mean(data, na.rm = T))
+
+ggplot(filter(df, !is.na(data)), aes(x = day, y = data, group = year)) +
+	geom_line(colour = "grey", alpha = 0.4) +
+	geom_line(data = filter(mean_f,!is.na(data)), aes(group = pop),
+		  colour = "black", size = 1) +  
+	facet_wrap(~pop) +
+	theme_classic()
+	
 ggsave(file = file.path('..', 'write_up', 'Plots', 'f_dynamics.png'), width = 8, height = 8)
 
 logs <- combine_logs(res[["fleets_catches"]])

### 2019-08-02 write_up/mixfishsim_ecolmod.tex
Small change

@@
 \begin{enumerate}
-	\item How does sampling-derived data reflects the underlying community 
-		structure? 	
+	\item How does sampling-derived fisheries data reflects the underlying
+		community structure? 	
 	\item How does data aggregation and source impact on spatial fisheries
@@
 
-\subsection{How does sampling-derived data reflect the underlying population
-	structure?}
+\subsection{How does sampling-derived fisheries data reflect the underlying
+	population structure?}
 

### 2019-08-06 write_up/mixfishsim_ecolmod.tex
Demographic stochasticity

@@
 fleets exploiting multiple fish populations and realising catch distributions
-that may differ from the underlying populations. As such, we favoured a
-minimum realistic model of the fish populations \citep{Plaganyi2014}, while
-incorporating detailed fishing dynamics that take account of different drivers
-in a mechanistic way. In this way we take account of heterogeneity in fleet
-dynamics due to different preferences and drivers similarly to other approaches
-\citep{Fulton2011}, but at an individual vessel rather than fleet level. We do
-not explicitly define fleets as rational profit maximisers at the outset, but
-consider there are several stages to development of the fishery; information
-gathering through search where the resource location is not known,  followed by
-individual learnt behaviour of profitable locations.  This provides a realistic
-model of how fishing patterns are established and maintained to exploit an
-uncertain resource through an explore-exploit strategy \citep{Mangel1983,
-	Bailey2018}.
+that may differ from the underlying populations. As such, we favoured a minimum
+realistic model of the fish populations \citep{Plaganyi2014} taking account of
+environmental but not demographic stochasticity, while incorporating detailed
+fishing dynamics that take account of different drivers in a mechanistic way.
+\\
+
+Demographic stochasticity arises due to individual-level variability in time to
+reproduction and death. This form of stochasticity is often modelled by drawing
+random time intervals from a given distribution \citep{Gillespie1977}. The
+impact of demographic stochasticity depends on the population size, with the
+effects expected to decrease with increasing population size \citep{Lande2010}.
+This contrasts with environmental stochasticity, which affects all population
+sizes and is present at the population level in our model by variability in
+recruitment. \\
+
+We take account of heterogeneity in fleet dynamics due to different preferences
+and drivers similarly to other approaches \citep{Fulton2011}, but at an
+individual vessel rather than fleet level. We do not explicitly define fleets
+as rational profit maximisers at the outset, but consider there are several
+stages to development of the fishery; information gathering through search
+where the resource location is not known, followed by individual learnt
+behaviour of profitable locations.  This provides a realistic model of how
+fishing patterns are established and maintained to exploit an uncertain
+resource through an explore-exploit strategy \citep{Mangel1983, Bailey2018}.
 

### 2019-08-28 write_up/mixfishsim_ecolmod.tex
Updates to include more details in results

@@
 spatial scales for fisheries closures has been a challenge in the past but
-identified as crucial to its success \citep{Costello2010, Dunn2016}. Further,
-poorly sited closures have led to ineffectual measures with unintended
-consequences. For example, increased benthic impact on previously unexploited
-areas was observed from the cod closure in the North Sea with a lack of
-observed intended effect in reducing cod exploitation
-\citep{Rijnsdorp2001,Dinmore2003}). \replaced[id=PD]{M}{Since then m}ore
-refined spatiotemporal information has \added[id=PD]{since} become available
-through the combination of logbook and Vessel Monitoring System (VMS) data
-\citep{Lee2010, Bastardie2010, Gerritsen2012, Mateo2016} and more real-time
-spatial management has been possible \citep[e.g.][]{Holmes2011}.  Such
-information is, however, derived from an inherently biased sampling programme,
-targeted fishing, where fishers establish favoured fishing grounds through an
-explore-exploit strategy \citep{Bailey2018} where they search for areas with
-high catches and then use experience to return to areas where they've
-experienced high catch in the past.  \deleted[id=PD]{ Further, fishers
-	generally only recorded landings (not catch) on a daily
-	basis\todo{\added[id=JJ]{Its not clear what the problem is: landings
-			collected on daily basis or landings recorded rather
-			than catch}}.  This leads to questions about the
+identified as crucial to its success \citep{Costello2010, Dunn2016}, and is
+hampered where spatial information is coarse due to low resolution reporting of
+fisheries catch which is subject to aggregation across larger gridded areas
+\citep{Branch2005}. Further, coarse spatial data may lead to poorly sited closures,
+which have led to ineffectual measures with unintended consequences.  For
+example, increased benthic impact on previously unexploited areas was observed
+from the cod closure in the North Sea with a lack of observed intended effect
+in reducing cod exploitation \citep{Rijnsdorp2001,Dinmore2003}).
+\replaced[id=PD]{M}{Since then m}ore refined spatiotemporal information has
+\added[id=PD]{since} become available through the combination of logbook and
+Vessel Monitoring System (VMS) data \citep{Lee2010, Bastardie2010,
+	Gerritsen2012, Mateo2016} and more real-time spatial management has
+been possible \citep[e.g.][]{Holmes2011}.  Such information is, however,
+derived from an inherently biased sampling programme, targeted fishing, where
+fishers establish favoured fishing grounds through an explore-exploit strategy
+\citep{Bailey2018} where they search for areas with high catches and then use
+experience to return to areas where they've experienced high catch in the past.
+\deleted[id=PD]{ Further, fishers generally only recorded landings (not catch)
+	on a daily basis\todo{\added[id=JJ]{Its not clear what the problem is:
+			landings collected on daily basis or landings recorded
+			rather than catch}}.  This leads to questions about the
 	validity of inference that can be drawn from landings data assigned to
@@
 
-\replaced[id=PD]{A}{We developed and implemented a simulation model with a}
-\replaced{simulation model that is modular and discrete-event based was
-	developed. This approach enables efficient computation by allowing
-	for}{approach, where} \added[id=PD]{sub-}modules \deleted[id=PD]{are}
-implemented on time-scales appropriate to capture the characteristic of the
-\replaced[id=PD]{different processes}{process modelled} (Figure 1).
-\added[id=PD]{The following sub-modules were included to capture the full
-	system: 1) Population dynamics, 2) Recruitment dynamics, 3) Population
-	movement, 4) fishery dynamics.}\\
+\replaced[id=PD]{A}{We developed and implemented a fully spatially explicit
+	simulation model with a} \replaced{simulation model that is modular and
+	discrete-event based was developed. This approach enables efficient
+	computation by allowing for}{approach, where}
+\added[id=PD]{sub-}modules \deleted[id=PD]{are} implemented on time-scales
+appropriate to capture the characteristic of the \replaced[id=PD]{different
+	processes}{process modelled} (Figure 1).  \added[id=PD]{The following
+	sub-modules were included to capture the full system: 1) Population
+	dynamics, 2) Recruitment dynamics, 3) Population movement, 4) fishery
+	dynamics.}\\
 
 \deleted[id=PD]{The fishing model operated on a tow-by-tow basis, while}
-\replaced[id=PD]{P}{p}opulation dynamics (fishing and natural mortality which
-are instantaneous rates, growth of the population biomass) operate on a daily
-time-step\replaced[id=PD]{, while p}{. P}opulation movement occurs on a weekly
-time-step\replaced[id=PD]{. R}{, while r}ecruitment \replaced[id=PD]{takes
-	place}{occurs} periodically each year for a set time
+\replaced[id=PD]{P}{p}opulation dynamics (including fishing and natural
+mortality which are instantaneous rates, growth of the population biomass)
+operate on a daily time-step\replaced[id=PD]{, while p}{. P}opulation movement
+occurs on a weekly time-step\replaced[id=PD]{. R}{, while r}ecruitment
+\replaced[id=PD]{takes place}{occurs} periodically each year for a set time
 \replaced[id=PD]{duration}{period (e.g. 3 weeks)} specified for each
@@
 	processes on a biologically relevant and computationally tractable
-	timescale.} \deleted[id=PD]{Here,}Population biomass growth and
-depletion for pre-recruits and\deleted[id=PD]{fish} recruited
-\added[id=PD]{fish}\deleted[id=PD]{to the fishery} were modelled separately as
-a function of previous recruited biomass, intrinsic population growth and
-recruitment functionally linked to the adult population size.  Biomass for each
-cell $c$ was incremented each day $d$ as follows (the full parameter list is
-detailed in Table \ref{tab: pop_variable}): 
+	timescale.} \deleted[id=PD]{Here,}Population biomass growth was
+modelled as a function of previous recruited biomass, intrinsic population
+growth and recruitment functionally linked to the adult population size.
+Biomass for each cell $c$ was incremented each day $d$ as follows (the full
+parameter list is detailed in Table \ref{tab: pop_variable}): 
 \begin{equation}
@@
 	B_{c,d+1} = &\\
-	& (1 + \rho) B_{c,d} \cdot e^{-Z_{c,d}} - \rho \cdot e^{-Z_{c,d}} \hspace{2.9cm}
+	& (1 + \rho) B_{c,d} \cdot \mathrm{e}^{-Z_{c,d}} - \rho \cdot
+	\mathrm{e}^{-Z_{c,d}} \hspace{2.9cm}
 	\times \\  
-	& (B_{c,d-1} \cdot e^{-Z_{c,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot
+	& (B_{c,d-1} \cdot \mathrm{e}^{-Z_{c,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot
 	R_{\tilde{y}(c,y,d-1)})
@@
 \end{equation}
-where $\rho$ is Brody's coefficient, shown to be equal to $e^{-K}$ when $K$ is
+where $\rho$ is Brody's coefficient, shown to be equal to $\mathrm{e}^{-K}$ when $K$ is
 the growth rate from a von Bertalanffy logistic growth model
@@
 \begin{equation}
-C_{c,d} = \frac{F_{c,d}}{F_{c,d} + M_{c,d}} * (1 - e^{-(F_{c,d} + M_{c,d})})
+C_{c,d} = \frac{F_{c,d}}{F_{c,d} + M_{c,d}} * (1 - \mathrm{e}^{-(F_{c,d} + M_{c,d})})
 \cdot B_{c,d}
@@
 	\begin{split}
-	\bar{R}_{c,d} = & B_{c,d} \cdot e^{(\alpha - \beta \cdot B_{c,d})} \\	
+	\bar{R}_{c,d} = & B_{c,d} \cdot \mathrm{e}^{(\alpha - \beta \cdot B_{c,d})} \\	
    	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\log(\sigma^2))]
@@
 	employed} a Gaussian spatial process \added[id=JJ]{was employed} to
-model habitat suitability for each of the populations on a 2d grid. JM: MENTION
-IN THE INTRODUCTION \\
+model habitat suitability for each of the populations on a 2d grid. \\
 
@@
 \begin{equation}
-	Pr(J | I) = \frac{e^{-\lambda * d_{IJ}} \cdot
-		(Hab_{J,p}^2 \cdot Tol_{J,p,wk})}{\sum\limits_{c=1}^{C}e^{-\lambda * d} \cdot
+	Pr(J | I) = \frac{\mathrm{e}^{-\lambda * d_{IJ}} \cdot
+		(Hab_{J,p}^2 \cdot
+		Tol_{J,p,wk})}{\sum\limits_{c=1}^{C}\mathrm{e}^{-\lambda * d} \cdot
 		(Hab_{c,p}^2 \cdot Tol_{c,p,wk})}
@@
 		the areas are pre-defined - I have amended to reflect and tried
-		to clarify}} \\ JM: WHAT ABOUT INDIVIDUAL INTERACTIONS:w
+		to clarify}} \\
 
@@
 \begin{equation}
-	StepL = e^{log(\beta_{1}) + log(\beta_{2}) -
+	StepL = \mathrm{e}^{log(\beta_{1}) + log(\beta_{2}) -
 		(log(\frac{\beta_{1}}{\beta_{3}}))} * Rev
@@
 heavily fished areas less attractive as a future fishing location choice as
-reduced catch rates will be experienced. JM: INTERFERENCE COMPETITION COULD
-ALSO BE REPRESENTED BY A LIMITATION FACTOR
+reduced catch rates will be experienced.
 
@@
 	\item Interpolate across entire area at desired resolution using simple
-		bivariate kriging using the \emph{interp} function from the R
-		package akima \citep{Akima2006}. This is intended to represent
-		a naive spatial model of catch rates, without knowledge of the
-		spatial population dynamics.
+		bivariate interpolation using the \emph{interp} function from
+		the R package akima \citep{Akima2006}. This is intended to
+		represent a naive spatial model of catch rates, without
+		knowledge of the spatial population dynamics.
 	\item Close area covering top 5 \% of catch rates 
@@
 the data over a ten-year period, with weekly (top), monthly (middle) and yearly
-(bottom) catch compositions from across an aggregated 20 x 20 area. By
-comparison to the 'real population', the monthly aggregation captures the major
-patterns seen in the weekly data, albeit missing more subtle differences. The
-yearly data assumes the same proportion of each population caught at any time
-of the year due to the data aggregation. This assumption introduces
-`aggregation bias' as the data may only be representative of some point (or no
-point) in time. The commercial data on a weekly basis shows some of the same
-patterns as the 'real population', though the first species (in red) is less
-well represented and some weeks are missing catches from the area. The monthly
-data shows some consistency between the 'real population' and commercial data
-for species 2 - 4, though species 1 remains under-represented. On an annual
-basis, interestingly the commercial data under represents the first species (in
-red) while the survey over represents species 1. This is likely due to the
-biases in commercial sampling, with the fisheries not targeting the areas where
-species 1 are present and the survey sampling areas where species 1 is more
-abundant than on average.
+(bottom) catch compositions from across an aggregated 20 x 20 area. In the
+'real population', the monthly aggregation captures the major patterns of
+composition seen in the weekly data with similar mean and standard deviations.
+In the weekly data species 1 = 9.36 (3.99), species 2 = 83.2 (5.60), species 3
+= 3.57 (1.23), species 4 = 3.91 (1.59); in the monthly data species 1 = 9.23
+(3.87), species 2 = 83.3 (5.52), species 3 = 3.62 (1.15), species 4 = 3.86
+(1.52). While means were similar some of the variation was lost when aggregated
+to an annual level; species 1 = 9.90 (0.173), species 2 = 82.2 (0.308), species
+3 = 3.82 (0.119), species 4 = 4.03 (0.0502).\\
+
+The commercial data on a weekly basis shows some of the same patterns as the
+'real population', though the species 1 (in red) is less well represented and
+some weeks are missing catches from the area. Here, weekly and monthly
+compositions were nearly identical, with monthly composition of species 1 =
+0.0472 (0.0139), species 2 = 94.4 (1.47), species 3 = 3.12 (1.47), species 4 =
+2.40 (0.444). Again, yearly values head a similar mean but smaller standard
+deviation.\\
+
+The survey data was only available on an annual basis, and showed again a
+slightly different composition; species 1 = 0.372 (0.00473), species 2 = 87.7
+(0.193), species 3 = 0.729 (0.0200), species 4 = 11.2 (0.172).
 
@@
 experienced in individual locations over the course of the year (Figure
-\ref{fig:9}). This indicates that fixed closures, at the right resolution,
-when based on commercially derived data have the potential to reduced fishing
-mortality. The likely cost of poor spatial and temporal resolution is
-associated with reduced effectiveness and potentially closing fishing
-opportunities for other fisheries. \\
+\ref{fig:9}). \\
+
+The yearly data assumes the same proportion of each population caught at any
+time of the year due to the data aggregation. This assumption introduces
+`aggregation bias' as the data may only be representative of some point (or no
+point) in time. The monthly data shows some consistency between the 'real population' and
+commercial data for species 2 - 4, though species 1 remains under-represented.
+On an annual basis, interestingly the commercial data under represents the
+first species (in red) while the survey over represents species 1. This is
+likely due to the biases in commercial sampling, with the fisheries not
+targeting the areas where species 1 are present and the survey sampling areas
+where species 1 is more abundant than on average. \\
+
+This indicates that fixed closures, at the right resolution, when based on
+commercially derived data have the potential to reduced fishing mortality. The
+likely cost of poor spatial and temporal resolution is associated with reduced
+effectiveness and potentially closing fishing opportunities for other
+fisheries. \\
 
@@
 
+\input{Temp_proportions.tex}
+
 %%%%%%%%%%%%%%%%%

### 2019-08-28 analysis/KillerFigure.R

@@ -344,8 +344,9 @@ dev.off()
 ## all year, month and week combinations
 
 logs <- combine_logs(res[["fleets_catches"]])
-
 logs_wk_mn <- unique(paste(logs$month, logs$week, sep = "_"))
+
+## Need to amend to print table of percentages
 
 ## Some measure of temporal change in distribtions
 plot_temp <- function(timestep = NULL, basis = NULL) {
@@ -390,6 +391,8 @@ dataPlot <- dataPlot[order(dataPlot$year, dataPlot$month, dataPlot$week),]
 cols <- c("red", "blue", "purple", "green")
 barplot(t(dataPlot[,4:7]), names.arg = rep(paste(""), nrow(dataPlot)), col = cols, border = NA)
 
+write.csv(dataPlot, file = paste0(timestep, basis,".csv"), row.names = F)
+
 }
 
 ## Monthly
@@ -425,6 +428,7 @@ dataPlot <- dataPlot[order(dataPlot$year, dataPlot$month),]
 
 cols <- c("red", "blue", "purple", "green")
 barplot(t(dataPlot[,3:6]), names.arg = rep(paste(""), 12 * length(yr)), col = cols, border = NA)
+write.csv(dataPlot, file = paste0(timestep, basis,".csv"), row.names = F)
 
 }
 
@@ -462,6 +466,7 @@ dataPlot <- dataPlot[order(dataPlot$year),]
 
 cols <- c("red", "blue", "purple", "green")
 barplot(t(dataPlot[,2:5]), names.arg = rep(paste(""), length(yr)), col = cols, border = NA)
+write.csv(dataPlot, file = paste0(timestep, basis,".csv"), row.names = F)
 
 }
 

### 2019-08-28 analysis/Temporal_values.R

@@ -1,0 +1,36 @@
+
+week_real_pop    <- read.csv("weekreal_pop.csv")
+week_commercial  <- read.csv("weekcommercial.csv")
+month_real_pop   <- read.csv("monthreal_pop.csv")
+month_commercial <- read.csv("monthcommercial.csv") 
+year_real_pop    <- read.csv("yearreal_pop.csv")
+year_commercial  <- read.csv("yearcommercial.csv")
+year_survey      <- read.csv("yearsurvey.csv")
+
+df <- data.frame(
+	rbind(	 cbind("data_type" = "real_pop", "timescale" = "weekly", week_real_pop),
+	rbind(   cbind("data_type" = "commercial", "timescale" = "weekly", week_commercial),
+	rbind(	 cbind("data_type" = "real_pop", "timescale" = "monthly", "week"=NA, month_real_pop),
+	rbind(	 cbind("data_type" = "commercial", "timescale" = "monthly","week"=NA, month_commercial),
+	rbind(	 cbind("data_type" = "real_pop", "timescale" = "yearly", "week"=NA, "month" = NA, year_real_pop),
+	rbind(	 cbind("data_type" = "commercial", "timescale" = "yearly", "week"=NA, "month" = NA, year_commercial),
+	rbind(	 cbind("data_type" = "survey", "timescale" = "yearly", "week"=NA, "month" = NA, year_survey)
+		 )))))))
+	)
+
+library(tidyverse)
+
+df2 <- df %>% group_by(data_type, timescale) %>%
+	summarise(spp1 = 100 * mean(spp_1), sd_spp1 = 100 * sd(spp_1),
+		  spp2 = 100 * mean(spp_2), sd_spp2 = 100 * sd(spp_2),
+		  spp3 = 100 * mean(spp_3), sd_spp3 = 100 * sd(spp_3),
+		  spp4 = 100 * mean(spp_4), sd_spp4 = 100 * sd(spp_4)
+		  )
+
+
+library(xtable)
+print(xtable(df2, digits = 3, caption = "Proportions of each species at different levels of temporal aggregation",
+	     label = "tab:7"), caption.placement = "top", file =
+file.path("..","write_up", "Temp_proportions.tex"),include.rownames = FALSE,
+tabular.environment= "longtable", floating = FALSE)
+

### 2019-08-28 write_up/mixfishsim_ecolmod.tex
Sharpening up text

@@
 of spatially and temporally heterogeneous fish populations using
-species-unselective gear that can result in unintended, unwanted catch of low
-quota or protected species. Reducing these unwanted catches is crucial for
-biological and economic sustainability of `mixed fisheries' and implementation
-of an ecosystem approach to fishing. \\
+species-unselective gear. This can result in unintended, unwanted catch of low
+quota or protected species and reducing these catches is crucial for
+biological and economic sustainability of `mixed fisheries'. \\
 
@@
 advice is limited by a lack of highly resolved knowledge of population
-distributions, population movement and how fishers interact with different fish
-populations. This reflects the fact that data on fish location at high temporal
-and spatial resolutions is expensive and difficult to collect. Proxies inferred
-from either scientific surveys or commercial catch data are often used to model
-distributions, usually with sparse data at limited spatial and temporal
+distributions and movement, and how fishers interact with different fish
+populations. Because data on fish location at high temporal and spatial
+resolutions is expensive and difficult to collect proxies are usually inferred
+from scientific surveys or commercial catches with limited spatial and temporal
 resolution. \\
@@
 populations, and iii) fishery dynamics for multiple fleet characteristics based
-on species targeting under an explore-exploit strategy via a mix of correlated
-random walk movement (for exploration) and learned behaviour (for exploitation)
-phases of the fisheries.  \\
-
-We simulated 50 years of fishing and used the results from the fisheries catch
-to draw inference on the underlying community structures. We compared this
-inference to a simulated fixed-site sampling design commonly used for fisheries
-monitoring purposes and the true underlying community structure. We i) used
-the results to establish the potential and limitations of fishery-dependent
-data in providing a robust picture of spatiotemporal distributions; and ii)
-simulated an area closure based on areas defined from the different data sources
-at a range of temporal and spatial resolutions to assess their effectiveness
-on reducing catches of a fish population. \\
+on species targeting under an explore-exploit strategy. This is implemented via
+a mix of correlated random walk movement (for exploration) and learned
+behaviour (for exploitation) phases of the fisheries.  \\
+
+We simulated 50 years of fishing and used the results to draw inference on the
+underlying community structures. We compared inference from commercial catch to
+a simulated fixed-site sampling design and the true underlying community. We i)
+establish the potential limitations of fishery-dependent data in providing a
+robust picture of spatiotemporal distributions; and then ii) simulated an area
+closure based on areas defined from the different data sources at a range of
+temporal and spatial resolutions to assess their effectiveness on reducing
+catches of a fish population. \\
 
@@
 \replaced[id=PD]{Adaptive spatial management strategies have}{Use of spatial
-	management as a tools} been proposed as a way of reducing discards
-\added[id=PD]{\citep{Holmes2011, Little2014, Dunn2014a}}.  \deleted[id=PD]{its}
-Implementation of avoidance measures is, however, restricted by lack of
-knowledge of fish and fishery spatiotemporal dynamics and understanding of the
-scale at which processes become important for management. Understanding the
-correct scale for spatial measures is crucial for implementing solutions at a
-resolution that ensures effective management \citep{Dunn2016} while minimising
-economic impact.  For example, the problem can be to identify a scale that
-promotes species avoidance for vulnerable or low quota species while allowing
-continuance of sustainable fisheries for available quota species.\\
+	management as a tools} been proposed as a way of reducing overquota
+discards \added[id=PD]{\citep{Holmes2011, Little2014, Dunn2014a}}.
+\deleted[id=PD]{its} However, implementation is restricted by lack of knowledge
+of fish and fishery spatiotemporal dynamics and understanding of the scale at
+which processes become important for management. Understanding the correct
+scale for spatial measures is crucial for implementing effective solutions
+which  minimising economic impact \citep{Dunn2016}. For example, the problem
+can be to identify a scale that promotes species avoidance for vulnerable or
+low quota species while allowing continuance of sustainable fisheries for
+available quota species.\\
 
 \replaced[id=PD]{Identifying}{Ensuring measures are implemented at} appropriate
-spatial scales for fisheries closures has been a challenge in the past but
-identified as crucial to its success \citep{Costello2010, Dunn2016}, and is
-hampered where spatial information is coarse due to low resolution reporting of
-fisheries catch which is subject to aggregation across larger gridded areas
-\citep{Branch2005}. Further, coarse spatial data may lead to poorly sited closures,
-which have led to ineffectual measures with unintended consequences.  For
-example, increased benthic impact on previously unexploited areas was observed
-from the cod closure in the North Sea with a lack of observed intended effect
-in reducing cod exploitation \citep{Rijnsdorp2001,Dinmore2003}).
-\replaced[id=PD]{M}{Since then m}ore refined spatiotemporal information has
-\added[id=PD]{since} become available through the combination of logbook and
-Vessel Monitoring System (VMS) data \citep{Lee2010, Bastardie2010,
-	Gerritsen2012, Mateo2016} and more real-time spatial management has
-been possible \citep[e.g.][]{Holmes2011}.  Such information is, however,
-derived from an inherently biased sampling programme, targeted fishing, where
+spatial scales for fisheries closures has been a challenge in the past but is
+crucial to their success \citep{Costello2010, Dunn2016}. Inference is hampered
+where spatial information is coarse due to low resolution reporting of
+fisheries catch which is aggregated across larger gridded areas
+\citep{Branch2005}. Further, if data does not allow identification of spatial
+features it may lead to poorly sited closures which are ineffectual or have
+unintended consequences. For example, increased benthic impact on previously
+unexploited areas from the cod closure in the North Sea were observed without
+the intended effect of reducing cod exploitation
+\citep{Rijnsdorp2001,Dinmore2003}). \replaced[id=PD]{M}{Since then m}ore
+refined spatiotemporal information has \added[id=PD]{since} become available
+through the combination of logbook and Vessel Monitoring System (VMS) data
+\citep{Lee2010, Bastardie2010, Gerritsen2012, Mateo2016} and more real-time
+spatial management has been possible \citep[e.g.][]{Holmes2011}. However,
 fishers establish favoured fishing grounds through an explore-exploit strategy
@@
 experience to return to areas where they've experienced high catch in the past.
+This leads to an inherently biased sampling where target species are
+over-represented in catch as fishers exploit areas of high abundance.
 \deleted[id=PD]{ Further, fishers generally only recorded landings (not catch)
@@
 \replaced[id=PD]{In order to understand the effect of spatiotemporal
-	aggregation of data we ask two fundamental questions regarding
-	inference derived from observational data:}{ and use the
-	results}\deleted[id=PD]{ from the fishing model:}
+	aggregation of data and fishery targeting we ask two fundamental
+	questions regarding inference derived from observational data:}{ and
+	use the results}\deleted[id=PD]{ from the fishing model:}
 
@@
 dynamics are highly-resolved in space and time by use of a Gaussian spatial
-process to define suitable habitat\replaced[id=PD]{. Precise locations being}{
-	and are} known \added[id=PD]{directly} rather than inferred from
-sampling or commercial catch\added[id=PD]{, we can use the population model to
-	validate how inference from fisheries-dependent and fisheries
-	independent sampling relates to the real community structure in a way
-	we could not with real data}. We ii) compare, at different spatial and
-temporal aggregations, the 'real population' distributions to samples from
-fisheries-dependent and fisheries independent catches to test if these are a
-true reflection of the relative density of the populations. We then iii)
-simulate a fishery closure to protect a species based on different spatial and
-temporal data aggregations. We use these evaluations to draw inference on the
-utility of commercial data in supporting management decisions.
-\todo{\added[id=JJ]{If the paper has two goals this should be clear from the
-		start, but may be better over 2 MSs}\added[id=PD]{I would like
-		to keep both parts, but have made clearer in how its set out.
-		The closure scenarios form validation of the data aggregation,
-		rather than effectiveness of the closures themselves - so its a
-		continuation of the same question in my eyes}}\deleted[id=PD]{.
-	Further, we extend our analysis to a range of spatial and temporal
-	scales to assess the impact of these processes on the success of the
-	management measure.}\\
+process to define suitable habitat for different populations\replaced[id=PD]{.
+	Precise locations of the fish being}{ and are} known
+\added[id=PD]{directly} rather than inferred from sampling or commercial
+catch\added[id=PD]{, we can use the population model to validate how inference
+	from fisheries-dependent and fisheries independent sampling relates to
+	the real community structure in a way we could not with real data}. We
+ii) compare, at different spatial and temporal aggregations, the 'real
+population' distributions to samples from fisheries-dependent and fisheries
+independent catches to test if these are a true reflection of the relative
+density of the populations. We then iii) simulate a fishery closure to protect
+a species based on different spatial and
+temporal data aggregations. \\
+
+We use these evaluations to draw inference on the utility of commercial data in
+supporting management decisions.
 
@@
 \replaced[id=PD]{P}{p}opulation dynamics (including fishing and natural
-mortality which are instantaneous rates, growth of the population biomass)
+mortality which are instantaneous rates, and growth of the population biomass)
 operate on a daily time-step\replaced[id=PD]{, while p}{. P}opulation movement

### 2019-09-05 write_up/mixfishsim_ecolmod.tex
Trimming the fat

@@
 \begin{frontmatter}
-\title{\emph{MixFishSim}: highly resolved spatiotemporal simulations for
+\title{Working title: Highly resolved spatiotemporal simulations for
 	exploring mixed fishery dynamics}
@@
 closure based on areas defined from the different data sources at a range of
-temporal and spatial resolutions to assess their effectiveness on reducing
-catches of a fish population. \\
+temporal and spatial resolutions. We assessed the effectiveness of the closures
+in reducing catches of a fish population. \\
 
@@
 \replaced[id=PD]{Adaptive spatial management strategies have}{Use of spatial
-	management as a tools} been proposed as a way of reducing overquota
+	management as a tools} been proposed as a way of reducing over-quota
 discards \added[id=PD]{\citep{Holmes2011, Little2014, Dunn2014a}}.
@@
 
-\replaced[id=PD]{A}{We developed and implemented a fully spatially explicit
-	simulation model with a} \replaced{simulation model that is modular and
-	discrete-event based was developed. This approach enables efficient
-	computation by allowing for}{approach, where}
-\added[id=PD]{sub-}modules \deleted[id=PD]{are} implemented on time-scales
-appropriate to capture the characteristic of the \replaced[id=PD]{different
-	processes}{process modelled} (Figure 1).  \added[id=PD]{The following
-	sub-modules were included to capture the full system: 1) Population
-	dynamics, 2) Recruitment dynamics, 3) Population movement, 4) fishery
-	dynamics.}\\
+\replaced[id=PD]{An}{We developed and implemented a fully spatially explicit
+	simulation model with a} \replaced{event-based simulation model of a
+	hypothetical fishery was developed as a software package
+	(`MixFishSim'). The modular approach enabled efficient computation by allowing
+	for}{approach, where} \added[id=PD]{sub-}modules \deleted[id=PD]{are}
+implemented on time-scales appropriate to capture the characteristic of the
+\replaced[id=PD]{different processes}{process modelled} (Figure 1).
+\added[id=PD]{The following sub-modules were included to capture the full
+	system: 1) Population dynamics, 2) Recruitment dynamics, 3) Population
+	movement, 4) fishery dynamics.}\\
 
 \deleted[id=PD]{The fishing model operated on a tow-by-tow basis, while}
-\replaced[id=PD]{P}{p}opulation dynamics (including fishing and natural
-mortality which are instantaneous rates, and growth of the population biomass)
-operate on a daily time-step\replaced[id=PD]{, while p}{. P}opulation movement
-occurs on a weekly time-step\replaced[id=PD]{. R}{, while r}ecruitment
-\replaced[id=PD]{takes place}{occurs} periodically each year for a set time
-\replaced[id=PD]{duration}{period (e.g. 3 weeks)} specified for each
-population\deleted[id=PD]{.}\added[id=PD]{, while the fishing module operates
-	on a tow-by-tow basis (i.e. multiple events a day)}.
-\deleted[id=PD]{Here we describe each of the model components; 1) Population
-	dynamics, 2) Recruitment dynamics, 3) Population movement dynamics, 4)
-	fishery dynamics.}
-
-Population movement is a combination of random (diffusive) movement, governed
-by a stochastic process where movement between adjacent cells is described by a
-set of probabilities, and directed (advective) movement where at certain times
-of year the population moves towards spawning grounds by increasing the
-probabilities of moving into the spawning grounds from adjacent cells. We
-incorporate characterisation of a number of different fishing
-\added[id=PD]{fleet dynamics} exploiting four fish populations with different
-spatial and population demographics. The following describes the implementation
-of each of the sub-modules.
+\replaced[id=PD]{P}{p}opulation dynamics operate on a daily
+time-step\replaced[id=PD]{, while p}{. P}opulation movement occurs on a weekly
+time-step, with the fishing module operating on a tow-by-tow basis (i.e.
+multiple events a day).  \deleted[id=PD]{Here we describe each of the model
+components; 1) Population dynamics, 2) Recruitment dynamics, 3) Population
+movement dynamics, 4) fishery dynamics.}
 
@@
 
-Recruitment is modelled through a function relating the adult biomass to
-recruits at time of recruitment. In \emph{MixFishSim}, it can be modelled
-either either as a stochastic Beverton-Holt stock-recruit form
-\citep{Beverton1957}: 
+Recruitment is modelled through a function relating to adult biomass. In
+\emph{MixFishSim}, it can be either as a stochastic Beverton-Holt stock-recruit
+form \citep{Beverton1957}: 
 \begin{equation}
@@
 where $\alpha$ is the maximum productivity per spawner and $\beta$ the density
-dependent reduction in productivity as the SSB increases. In our example
-application the Beverton-Holt form of stock recruit relationship was used for
-all populations though either functional form can be chosen.
+dependent reduction in productivity as the SSB increases.
 
 \subsection{Population movement dynamics}
+
+Population movement is a combination of random (diffusive) movement, governed
+by a stochastic process where movement between adjacent cells is described by a
+set of probabilities, and directed (advective) movement where at certain times
+of year the population moves towards spawning grounds by increasing the
+probabilities of moving into the spawning grounds from adjacent cells. We
+incorporate characterisation of a number of different fishing
+\added[id=PD]{fleet dynamics} exploiting four fish populations with different
+spatial and population demographics. The following describes the implementation
+of each of the sub-modules.
 
@@
 	\citep{Tobler1970, F.Dormann2007}} and we change the parameters to
-implement different spatial structures for the populations. \\
-
-\replaced[id=PD]{T}{In the simulation model, t}he habitat for each of the
-populations \replaced[id=PD]{was}{is} generated \replaced[id=PD]{with}{through}
-the \textit{RFSimulate} function of the \textit{RandomFields} R package
-\citep{Schlater2015}, that simulates a Gaussian Random Field process given a
-user defined error model and correlation structure. We define a stationary
+implement different spatial structures for the different populations using the
+\textit{RandomFields} R package \citep{Schlater2015}. We define a stationary
 habitat field and combine with a temporally dynamic thermal tolerance field to
@@
 
-\added[id=PD]{The final process results in a population structure and movement
-	pattern unique to each species, with population movement occurring on a
-	weekly basis. The decision to model population movement on a weekly
-	timescale was to reflect that fish tend to aggregate in species
-	specific locations that have been observed to last around one to two
-	weeks \citep{Poos2007}.  Therefore this process approximated the
+\added[id=PD]{The final combined process results in a population structure and
+	movement pattern unique to each species, with population movement
+	occurring on a weekly basis. The decision to model population movement
+	on a weekly timescale was to reflect that fish tend to aggregate in
+	species specific locations that have been observed to last around one
+	to two weeks \citep{Poos2007}. Therefore this process approximated the
 	demographic shifts in fish populations throughout a year with seasonal
-	spawning patterns (e.g.  Figure \ref{S-fig:5}).}
+	spawning patterns (Figure \ref{S-fig:5}).}
 
@@
 vessels to maximise their catch from an unknown resource distribution
-\cite{Bailey2018}.  The decision to use an individual based model for fishing
+\citep{Bailey2018}. The decision to use an individual based model for fishing
 vessels was taken because fishers are heterogeneous in their location choice
@@
 fishing process) determine\replaced[id=PD]{d}{s} the preference of fishing
-locations for the fleet.  All species prices \replaced[id=PD]{were}{are} kept
-the same across fleets \replaced[id=PD]{and seasons}{, though can be made to
-	vary seasonally}.
+locations for the fleet.
 
@@
 where $\replaced[id=PD]{L}{C}_{p}$ is \replaced[id=PD]{landings}{catch} of a
-population $p$, and $Pr_{p}$ price of a population. Here, when fishing is
-successful vessels remain in a similar location and continue to exploit the
-local fishing grounds. When unsuccessful, they move some distance away from
-the current fishing location.  The movement distance retains some degree of
-stochasticity, that can be controlled separately, but is determined by the
+population $p$, and $Pr_{p}$ price of a population. All species prices were
+kept the same across fleets and seasons. Here, when fishing is successful
+vessels remain in a similar location and continue to exploit the local fishing
+grounds. When unsuccessful, they move some distance away from the current
+fishing location.  The movement distance retains some degree of stochasticity,
+that can be controlled separately, but is determined by the
 relationship: 
@@
 We parametrised the simulation model for four populations with different
-demographics; growth rates, natural mortality and recruitment functions (Table
+demographics; growth rates, natural mortality and recruitment parameters (Table
 \ref{tab:1}). Habitat preference (Figure \ref{S-fig:1}) and temperature

### 2019-09-05 write_up/mixfishsim_ecolmod.tex
Edited to M&M

@@
 \usepackage{enumitem}
-
+\usepackage{comment}
 % For track-changes
@@
 biological and economic sustainability of `mixed fisheries'. \\
-
+%%
 \replaced[id = PD]{If fisheries are to avoid unwanted catch,}{To implement
-	effective spatial measures to reduce discards} a good understanding of
+	effective spatial measures to reduce discards} \replaced[id = CM]{an in-depth}{a good} understanding of
 spatiotemporal fishery dynamics is required. However, traditional scientific
@@
 resolution. \\ 
-
+%%
 To understand how data resolution impacts inference on mixed fisheries
-interactions, we developed a highly resolved spatiotemporal simulation model
+interactions, we developed a highly resolved spatiotemporal \added[id=CM]{event-based} simulation model
 incorporating: i) delay-difference population dynamics, ii) population movement
@@
 behaviour (for exploitation) phases of the fisheries.  \\ 
-
-We simulated 50 years of fishing and used the results to draw inference on the
-underlying community structures. We compared inference from commercial catch to
-a simulated fixed-site sampling design and the true underlying community. We i)
+%%
+\replaced[id=CM]{Fifty}{We simulated 50} years of \added[id=CM]{sub-daily} fishing \added[id=CM]{was simulated} and used \deleted[id = CM]{the results}to draw inference on the
+underlying community structures. We compared inference\added[id=CM]{s} \added[id=CM]{based on:}\deleted[id=CM]{from} commercial catch\added[id=CM]{,} \deleted[id=CM]{to}
+a simulated fixed-site sampling \added[id=CM]{survey} design and the true underlying community. We i)
 establish the potential limitations of fishery-dependent data in providing a
@@
 closure based on areas defined from the different data sources at a range of
-temporal and spatial resolutions. We assessed the effectiveness of the closures
+temporal and spatial resolutions. \deleted{We assessed the effectiveness of the closures
 in reducing catches of a fish population. \\
-
+%%
 Our framework allows users to explore the assumptions in modelling
 observational data and evaluate the underlying dynamics of such approaches at a
-fine spatial and temporal scale. We conclude from our simulations that
+fine spatial and temporal scale.} We conclude from our \replaced[id=CM]{example framework application}{simulations} that
 commercial data, while containing bias, provide a useful tool for managing
-catches in mixed fisheries if applied at the correct spatiotemporal scale. \\
-
+catches in mixed fisheries if applied at the correct spatiotemporal scale. [NEED A LITTLE MORE DETAIL OF THE RESULTS HERE - 2 MORE SENTENCES ON KEY TAKE-HOME RESULTS]\\
+%%
 \end{abstract}
@@
 This leads to an inherently biased sampling where target species are
-over-represented in catch as fishers exploit areas of high abundance.
+over-represented in \added[id=CM]{the} catch as fishers exploit areas of high abundance.
 \deleted[id=PD]{ Further, fishers generally only recorded landings (not catch)
@@
 
-\replaced[id=PD]{In order to understand the effect of spatiotemporal
+\replaced[id=PD]{\replaced[id=CM]{To}{In order to} understand the effect of spatiotemporal
 	aggregation of data and fishery targeting we ask two fundamental
@@
 	the real community structure in a way we could not with real data}. We
-ii) compare, at different spatial and temporal aggregations, the 'real
+ii) compare, at different spatial and temporal aggregations, the \replaced[id=CM]{`}{'}real
 population' distributions to samples from fisheries-dependent and fisheries
@@
 \input{Process_model.tex}
-
+\begin{comment}
 \begin{figure}[!ht]
@@
 \end{figure}	
+\end{comment}
 

### 2019-09-10 write_up/mixfishsim_ecolmod.tex
Edited full ms

@@
 
-\usepackage{lineno,hyperref}
+\usepackage{lineno}
+\usepackage[hidelinks]{hyperref}
 \usepackage[utf8]{inputenc}
@@
 \begin{equation}
-C_{c,d} = \frac{F_{c,d}}{F_{c,d} + M_{c,d}} * (1 - \mathrm{e}^{-(F_{c,d} + M_{c,d})})
+C_{c,d} = \frac{F_{c,d}}{F_{c,d} + M_{c,d}} \deleted[id=CM]{*} \added[id=CM]{\left(}1 - \mathrm{e}^{-(F_{c,d} + M_{c,d})}\added[id=CM]{\right)}
 \cdot B_{c,d}
@@
 probabilities of moving into the spawning grounds from adjacent cells. We
-incorporate characterisation of a number of different fishing
+\replaced[id=CM]{characterise}{incorporate characterisation of} a \replaced[id=CM]{set}{number} of different fishing
 \added[id=PD]{fleet dynamics} exploiting four fish populations with different
@@
 	employed} a Gaussian spatial process \added[id=JJ]{was employed} to
-model habitat suitability for each of the populations on a 2d grid. \\
+model habitat suitability for each of the populations on a 2d grid.
 
@@
 \begin{equation}
-	Pr(J | I) = \frac{\mathrm{e}^{-\lambda * d_{IJ}} \cdot
+	\replaced[id=CM]{Pr(C_{wk+1} = J | C_{wk} =I)}{Pr(J | I)} = \frac{\mathrm{e}^{-\lambda * d_{IJ}} \cdot
 		(Hab_{J,p}^2 \cdot
@@
 temperature tolerance for cell $J$ by population $p$ in week $wk$ (see
-below).\\
+below).\deleted[id=CM]{\\}
 
@@
 		the areas are pre-defined - I have amended to reflect and tried
-		to clarify}} \\
+		to clarify}} \deleted[id=CM]{\\}
 
@@
 $\mu\added[id=PD]{_{p}}$ and $\sigma^2\added[id=PD]{_{p}}$ the mean and
-standard deviation of the population temperature tolerance. \\
+standard deviation of the population temperature tolerance. \deleted[id=CM]{\\}
 
@@
 
-The fleet dynamics can be broadly categorised into three components; fleet
+\replaced[id=CM]{F}{The f}leet dynamics can be broadly categorised into three components\replaced[id=CM]{:}{;} fleet
 targeting - that determined the fleet catch efficiency and preference towards a
-particular species; trip-level decisions, that determined the initial location
+particular species; trip-level decisions, that determine\replaced[id=CM]{s}{d} the initial location
 to be fished at the beginning of a trip; and within-trip decisions, that
-determined movement from one fishing spot to another within a trip. Together,
-these elements implemented an explore-exploit type strategy for individual
+determine\replaced[id=CM]{s}{d} movement from one fishing spot to another within a trip. Together,
+these elements implement\deleted[id=CM]{ed} an explore-exploit type strategy for individual
 vessels to maximise their catch from an unknown resource distribution
@@
 behaviour due to different objectives, risk preference and targeting preference
-\citep{VanPutten2012a}. Therefore in the simulations fleet dynamics are the
-productive of individual experiences rather than pre-defined group dynamics.
+\citep{VanPutten2012a}. Therefore in the simulations fleet dynamics \replaced[id=CM]{reflect}{are the
+productive of} individual experiences rather than pre-defined group dynamics.
 
@@
 local depletion and interference \added[id=JJ]{competition} will affect fishing
-location choice of the fleet as a whole \citep{Rijnsdorp2000, Poos2007a}. In
-order to account for this behaviour, the fishing sub-model operates spatially
+location choice of the fleet as a whole \citep{Rijnsdorp2000, Poos2007a}. \replaced[id=CM]{To}{In order to} account for this behaviour, the fishing sub-model operates spatially
 on a daily time-step so that for future days the biomass available to the
@@
 \citep{RCoreTeam2017} \replaced[id=PD]{and}{;} available as an R package from
-the authors github site (\url{www.github.com/pdolder/MixFishSim}).\\
+the author\added{'}s github site (\url{www.github.com/pdolder/MixFishSim}).\\
 
 \section{Parameterisation}
+\added[id=CM]{We parameterise \emph{MixFishSim} to investigate the influence of data aggregation on spatial inference.}
 
@@
 
-We parametrised the simulation model for four populations with different
-demographics; growth rates, natural mortality and recruitment parameters (Table
+We parametrised the simulation model for four \added[id=CM]{example} populations with different
+demographics\replaced[id=CM]{,}{;} growth rates, natural mortality and recruitment parameters (Table
 \ref{tab:1}). Habitat preference (Figure \ref{S-fig:1}) and temperature
@@
 	dynamics, preferentially targeted different fish populations}.  The
-random walk process implies that within a fleet different vessels have
+\added[id=CM]{learned} random walk process implies that within a fleet different vessels have
 different spatial distributions based on individual experience. The step
@@
 
-\subsection{Simulation dynamics}
+\subsection{\replaced[id=CM]{Emergent s}{S}imulation dynamics}
 
@@
 some shared and some different fishing grounds depending on their own personal
-experience during the explore phase of the fishery (\added[id=PD]{Figure}
+experience during the explor\replaced[id=CM]{atory}{e} phase of the fishery (\added[id=PD]{Figure}
 \ref{S-fig:14}). This results from the randomness in the correlated random walk
@@
 
-In order to answer this question we compare different spatial and temporal
-aggregations of the 'real population' distributions to:
+\replaced[id=CM]{To}{In order to} answer this question we compare different spatial and temporal
+aggregations of the \deleted[id = CM]{'}real population\deleted[id = CM]{'} distributions to:
 \begin{enumerate}[label=\alph*)]
@@
 5 x 5 grid shows similar patterns and, while losing some of the spatial detail,
-there remains good consistency between the `real population' and the commercial
+there remains good consistency between the \deleted[id = CM]{'}real population\deleted[id = CM]{'} and the commercial
 data. Survey data starts to pick out some of the similar patterns as the other
@@
 (bottom) catch compositions from across an aggregated 20 x 20 area. In the
-'real population', the monthly aggregation captures the major patterns of
+\deleted[id = CM]{'}real population\deleted[id = CM]{'}, the monthly aggregation captures the major patterns of
 composition seen in the weekly data with similar mean and standard deviations.
@@
 The commercial data on a weekly basis shows some of the same patterns as the
-'real population', though the species 1 (in red) is less well represented and
+\deleted[id = CM]{'}real population\deleted[id = CM]{'}, though the species 1 (in red) is less well represented and
 some weeks are missing catches from the area. Here, weekly and monthly
@@
 reductions in fishing mortality happened immediately after the closures,
-following which the fisheries "adapted" to the closures and fishing mortality
+following which the fisheries \replaced[id=CM]{``}{"}adapted" to the closures and fishing mortality
 increased again somewhat. The exception to the success was the closures
@@
 (yearly) that was ineffective with all data sources. As expected, closures
-based on the "known" population distribution were most effective, with
+based on the \replaced[id=CM]{``}{"}known" population distribution were most effective, with
 differing degrees of success using the commercial data. Fishing mortality rates
@@
 the fine-scale resolution. In this case the closures were sufficiently large to
-protect a core are of the habitat for the population, but this was achieved in
+protect a core are\added[id=CM]{a} of the habitat for the population, but this was achieved in
 a fairly crude manner by closing a large area - including area where the
@@
 %% General intro
-Our study evaluates the importance of data scaling and considers potential bias
+Our study \added{presents a new highly resolved fisheries simulation framework,} evaluates the importance of data scaling and considers potential bias
 introduced through data aggregation when using fisheries data to infer
@@
 management approaches increasingly employing more nuanced spatiotemporal
-approaches in order to maximise productivity while taking account of both the
+approaches \replaced[id=CM]{to}{In order to} maximise productivity while taking account of both the
 biological and human processes operating on different time-frames
@@
 We employ a simulation approach to model each of the population and fishery
-dynamics in a hypothetical 'mixed fishery', allowing us to i) evaluate the
+dynamics in a hypothetical \replaced[id=CM]{`}{'}mixed fishery', allowing us to i) evaluate the
 consequences of different aggregation assumptions on our understanding of the
@@
 practices if potential biases in data are to be understood and taken into
-account. \\
+account \added[id=CM]{(Figures X,Y,Z)}. \\
 
@@
 fished. Similarly, despite the even spatial coverage the survey was able to
-capture some of the same spatial patterns as the 'real population', but missed
+capture some of the same spatial patterns as the \replaced{`}{'}real population', but missed
 others due to gaps between survey stations limiting spatial and temporal
-coverage. This provides a challenge when modelling unsampled areas in inferring
+coverage \added[id=CM]{(Figures X,Y,Z)}. This provides a challenge when modelling unsampled areas in inferring
 species distribution maps, though these limitations may be overcome by
@@
 according to fixed habitat preferences and temperature gradients (Figures
-\ref{S-fig:1}, \ref{S-fig:3}). Our assumptions in parametrising the model
+\ref{S-fig:1}, \ref{S-fig:3}). Our assumptions in paramet\added[id=CM]{e}rising the model
 (movement rates, temperature tolerances) will have a direct impact on our
@@
 
-Other novel applications of our framework could be; testing different survey
+Other novel applications of our framework could be\replaced[id=CM]{:}{;} testing different survey
 designs given multiple species and data generating assumptions \citep{Xu2015};
@@
 \citep{Liu2013}; at sea sampling scheme designs to deliver unbiased estimates
-of population parameters \cite{Cotter2007, Kimura2006}; adaptive management
+of population parameters \citep{Cotter2007, Kimura2006}; adaptive management
 \citep{Walters2007, Dunn2016}; testing the ability of commonly employed fleet
 dynamics models such as Random Utility Models to capture fine scale dynamics
-and understand their importance \cite{Girardin2016}; and as a detailed
-operating model in a management strategy evaluation \cite{Mahevas2004}. \\
+and understand their importance \citep{Girardin2016}; and as a detailed
+operating model in a management strategy evaluation \citep{Mahevas2004}. \\
 

### 2019-09-11 write_up/mixfishsim_ecolmod.tex
Uncommented the figures
Revisions and clean up of the tex file

--- 2019-09-05 write_up/mixfishsim_ecolmod.tex
@@
 
-\replaced[id = JJ]{Most fisheries}{Fishing} exploit\deleted[id=JJ]{s} a variety 
-of spatially and temporally heterogeneous fish populations using
-species-unselective gear. This can result in unintended, unwanted catch of low
-quota or protected species and reducing these catches is crucial for
-biological and economic sustainability of `mixed fisheries'. \\
-
-\replaced[id = PD]{If fisheries are to avoid unwanted catch,}{To implement
-	effective spatial measures to reduce discards} a good understanding of
+Most fisheries exploit a variety of spatially and temporally heterogeneous fish
+populations using species-unselective gear. This can result in unintended,
+unwanted catch of low quota or protected species and reducing these catches is
+crucial for biological and economic sustainability of `mixed fisheries'. \\
+%%
+If fisheries are to avoid unwanted catch, an in-depth understanding of
 spatiotemporal fishery dynamics is required. However, traditional scientific
@@
 resolution. \\ 
-
+%%
 To understand how data resolution impacts inference on mixed fisheries
-interactions, we developed a highly resolved spatiotemporal simulation model
-incorporating: i) delay-difference population dynamics, ii) population movement
-using Gaussian Random Fields to simulate patchy, heterogeneously distributed
-populations, and iii) fishery dynamics for multiple fleet characteristics based
-on species targeting under an explore-exploit strategy. This is implemented via
-a mix of correlated random walk movement (for exploration) and learned
-behaviour (for exploitation) phases of the fisheries.  \\
-
-We simulated 50 years of fishing and used the results to draw inference on the
-underlying community structures. We compared inference from commercial catch to
-a simulated fixed-site sampling design and the true underlying community. We i)
-establish the potential limitations of fishery-dependent data in providing a
-robust picture of spatiotemporal distributions; and then ii) simulated an area
-closure based on areas defined from the different data sources at a range of
-temporal and spatial resolutions. We assessed the effectiveness of the closures
-in reducing catches of a fish population. \\
-
+interactions, we developed a highly resolved spatiotemporal
+event-based simulation model incorporating: i) delay-difference
+population dynamics, ii) population movement using Gaussian Random Fields to
+simulate patchy, heterogeneously distributed populations, and iii) fishery
+dynamics for multiple fleet characteristics based on species targeting under an
+explore-exploit strategy. This is implemented via a mix of correlated random
+walk movement (for exploration) and learned behaviour (for exploitation) phases
+of the fisheries.  \\ 
+%%
+Fifty years of sub-daily fishing was simulated and used to draw inference on
+the underlying community structures. We compared inferences based on:
+commercial catch, a simulated fixed-site sampling survey design and the true
+underlying community. We i) establish the potential limitations of
+fishery-dependent data in providing a robust picture of spatiotemporal
+distributions; and then ii) simulated an area closure based on areas defined
+from the different data sources at a range of temporal and spatial resolutions.
+\\
+%%
 Our framework allows users to explore the assumptions in modelling
 observational data and evaluate the underlying dynamics of such approaches at a
-fine spatial and temporal scale. We conclude from our simulations that
-commercial data, while containing bias, provide a useful tool for managing
-catches in mixed fisheries if applied at the correct spatiotemporal scale. \\
-
+fine spatial and temporal scale. We conclude from our example framework
+application that commercial data, while containing bias, provide a useful tool
+for managing catches in mixed fisheries if applied at the correct
+spatiotemporal scale. [NEED A LITTLE MORE DETAIL OF THE RESULTS HERE - 2 MORE
+SENTENCES ON KEY TAKE-HOME RESULTS]\\
+%%
 \end{abstract}
@@
 Fishers exploit a variety of fish populations that are heterogeneously
-distributed in space and time, with varying knowledge of species
-distributions\deleted[id=JJ]{ and using species non-selective fishing gear}.
-\added[id=PD]{In doing so} fisheries \deleted[id=PD]{that}catch an assemblage
-of species \added[id=PD]{and}\deleted{, known as mixed fisheries}
-\replaced[id=JJ]{may}{, when managed by single-species quotas can end up}
-discard\deleted[id=JJ]{ing} over-quota catch \added[id=JJ]{when managed by
-	single species quotas and fishers exhaust one or more quota. This may}
-lead to overexploitation of fish populations \added[id=JJ]{\citep{Ulrich2011a,
-		Batsleer2015}}.  \added[id=JJ]{Discarding of fish in
-	excess of quota limits the ability to maintain fishing mortality within
-	sustainable limits \citep{Alverson1994, Crowder1998, Rijnsdorp2007}}
-\deleted[id=PD]{; reducing discarding is crucial}and the ability to manage for
-the biological and economic sustainability of fisheries\deleted[id=JJ]{ and
-	implementation of an ecosystem approach to fisheries}. As such, there
-is increasing interest in technical solutions such as gear and spatial closures
-as measures to \replaced[id=PD]{reduce unwanted catch}{avoiding
-	discard\added[id=JJ]{ing of fish}} \citep{Kennelly2002, Catchpole2008,
+distributed in space and time, with varying knowledge of species distributions.
+In doing so fisheries catch an assemblage of species and may discard over-quota
+catch when managed by single species quotas and fishers exhaust one or more
+quota. This may lead to overexploitation of fish populations
+\citep{Ulrich2011a, Batsleer2015}. Discarding of fish in excess of quota limits
+the ability to maintain fishing mortality within sustainable limits
+\citep{Alverson1994, Crowder1998, Rijnsdorp2007} and the ability to manage for
+the biological and economic sustainability of fisheries. As such, there is
+increasing interest in technical solutions such as gear and spatial closures as
+measures to reduce unwanted catch \citep{Kennelly2002, Catchpole2008,
 	Bellido2011, Cosgrove2019}. \\
 
-\replaced[id=PD]{Adaptive spatial management strategies have}{Use of spatial
-	management as a tools} been proposed as a way of reducing over-quota
-discards \added[id=PD]{\citep{Holmes2011, Little2014, Dunn2014a}}.
-\deleted[id=PD]{its} However, implementation is restricted by lack of knowledge
-of fish and fishery spatiotemporal dynamics and understanding of the scale at
-which processes become important for management. Understanding the correct
-scale for spatial measures is crucial for implementing effective solutions
-which  minimising economic impact \citep{Dunn2016}. For example, the problem
-can be to identify a scale that promotes species avoidance for vulnerable or
-low quota species while allowing continuance of sustainable fisheries for
-available quota species.\\
-
-\replaced[id=PD]{Identifying}{Ensuring measures are implemented at} appropriate
-spatial scales for fisheries closures has been a challenge in the past but is
-crucial to their success \citep{Costello2010, Dunn2016}. Inference is hampered
-where spatial information is coarse due to low resolution reporting of
-fisheries catch which is aggregated across larger gridded areas
-\citep{Branch2005}. Further, if data does not allow identification of spatial
-features it may lead to poorly sited closures which are ineffectual or have
-unintended consequences. For example, increased benthic impact on previously
-unexploited areas from the cod closure in the North Sea were observed without
-the intended effect of reducing cod exploitation
-\citep{Rijnsdorp2001,Dinmore2003}). \replaced[id=PD]{M}{Since then m}ore
-refined spatiotemporal information has \added[id=PD]{since} become available
-through the combination of logbook and Vessel Monitoring System (VMS) data
-\citep{Lee2010, Bastardie2010, Gerritsen2012, Mateo2016} and more real-time
-spatial management has been possible \citep[e.g.][]{Holmes2011}. However,
-fishers establish favoured fishing grounds through an explore-exploit strategy
-\citep{Bailey2018} where they search for areas with high catches and then use
-experience to return to areas where they've experienced high catch in the past.
-This leads to an inherently biased sampling where target species are
-over-represented in catch as fishers exploit areas of high abundance.
-\deleted[id=PD]{ Further, fishers generally only recorded landings (not catch)
-	on a daily basis\todo{\added[id=JJ]{Its not clear what the problem is:
-			landings collected on daily basis or landings recorded
-			rather than catch}}.  This leads to questions about the
-	validity of inference that can be drawn from landings data assigned to
-	VMS activity pings.}\todo{\added[id=JJ]{This comes as a surprise: I
-		thought this was going to be about
-		discards}\added[id=PD]{Agree, have removed this to avoid
-		confusion}}\\
-
-\replaced[id=PD]{In order to understand the effect of spatiotemporal
-	aggregation of data and fishery targeting we ask two fundamental
-	questions regarding inference derived from observational data:}{ and
-	use the results}\deleted[id=PD]{ from the fishing model:}
+Adaptive spatial management strategies have been proposed as a way of reducing
+over-quota discards \citep{Holmes2011, Little2014, Dunn2014a}. However,
+implementation is restricted by lack of knowledge of fish and fishery
+spatiotemporal dynamics and understanding of the scale at which processes
+become important for management. Understanding the correct scale for spatial
+measures is crucial for implementing effective solutions which  minimising
+economic impact \citep{Dunn2016}. For example, the problem can be to identify a
+scale that promotes species avoidance for vulnerable or low quota species while
+allowing continuance of sustainable fisheries for available quota species.\\
+
+Identifying appropriate spatial scales for fisheries closures has been a
+challenge in the past but is crucial to their success \citep{Costello2010,
+	Dunn2016}. Inference is hampered where spatial information is coarse
+due to low resolution reporting of fisheries catch which is aggregated across
+larger gridded areas \citep{Branch2005}. Further, if data does not allow
+identification of spatial features it may lead to poorly sited closures which
+are ineffectual or have unintended consequences. For example, increased benthic
+impact on previously unexploited areas from the cod closure in the North Sea
+were observed without the intended effect of reducing cod exploitation
+\citep{Rijnsdorp2001,Dinmore2003}). More refined spatiotemporal information has
+since become available through the combination of logbook and Vessel Monitoring
+System (VMS) data \citep{Lee2010, Bastardie2010, Gerritsen2012, Mateo2016} and
+more real-time spatial management has been possible \citep[e.g.][]{Holmes2011}.
+However, fishers establish favoured fishing grounds through an explore-exploit
+strategy \citep{Bailey2018} where they search for areas with high catches and
+then use experience to return to areas where they've experienced high catch in
+the past.  This leads to an inherently biased sampling where target species are
+over-represented in the catch as fishers exploit areas of high abundance. \\
+
+To understand the effect of spatiotemporal aggregation of data and fishery
+targeting we ask two fundamental questions regarding inference derived from
+observational data:
 
@@
 dynamics are highly-resolved in space and time by use of a Gaussian spatial
-process to define suitable habitat for different populations\replaced[id=PD]{.
-	Precise locations of the fish being}{ and are} known
-\added[id=PD]{directly} rather than inferred from sampling or commercial
-catch\added[id=PD]{, we can use the population model to validate how inference
-	from fisheries-dependent and fisheries independent sampling relates to
-	the real community structure in a way we could not with real data}. We
-ii) compare, at different spatial and temporal aggregations, the 'real
-population' distributions to samples from fisheries-dependent and fisheries
-independent catches to test if these are a true reflection of the relative
-density of the populations. We then iii) simulate a fishery closure to protect
-a species based on different spatial and
-temporal data aggregations. \\
+process to define suitable habitat for different populations.  Precise
+locations of the fish being known directly rather than inferred from sampling
+or commercial catch, we can use the population model to validate how inference
+from fisheries-dependent and fisheries independent sampling relates to the real
+community structure in a way we could not with real data. We ii) compare, at
+different spatial and temporal aggregations, the real (simulated) population
+distributions to samples from fisheries-dependent and fisheries independent
+catches to test if these are a true reflection of the relative density of the
+populations. We then iii) simulate a fishery closure to protect a species based
+on different spatial and temporal data aggregations. \\
 
@@
 
-\replaced[id=PD]{An}{We developed and implemented a fully spatially explicit
-	simulation model with a} \replaced{event-based simulation model of a
-	hypothetical fishery was developed as a software package
-	(`MixFishSim'). The modular approach enabled efficient computation by allowing
-	for}{approach, where} \added[id=PD]{sub-}modules \deleted[id=PD]{are}
-implemented on time-scales appropriate to capture the characteristic of the
-\replaced[id=PD]{different processes}{process modelled} (Figure 1).
-\added[id=PD]{The following sub-modules were included to capture the full
-	system: 1) Population dynamics, 2) Recruitment dynamics, 3) Population
-	movement, 4) fishery dynamics.}\\
-
-\deleted[id=PD]{The fishing model operated on a tow-by-tow basis, while}
-\replaced[id=PD]{P}{p}opulation dynamics operate on a daily
-time-step\replaced[id=PD]{, while p}{. P}opulation movement occurs on a weekly
-time-step, with the fishing module operating on a tow-by-tow basis (i.e.
-multiple events a day).  \deleted[id=PD]{Here we describe each of the model
-components; 1) Population dynamics, 2) Recruitment dynamics, 3) Population
-movement dynamics, 4) fishery dynamics.}
+An event-based simulation model of a hypothetical fishery was developed as a
+software package (\textit{MixFishSim}). The modular approach enabled efficient
+computation by allowing for sub-modules implemented on time-scales appropriate
+to capture the characteristic of the different processes (Figure 1). The
+following sub-modules were included to capture the full system: 1) Population
+dynamics, 2) Recruitment dynamics, 3) Population movement, 4) fishery
+dynamics.\\
+
+Population dynamics operate on a daily time-step, while population movement
+occurs on a weekly time-step, with the fishing module operating on a tow-by-tow
+basis (i.e.  multiple events a day).
 
@@
 terms of aggregate biomass of recruits and mature components rather than
-keeping track of individuals\citep{Deriso1980, Schnute1985, Dichmont2003}.
-\added[id=PD]{A daily time-step was chosen to discretise continuous population
-	processes on a biologically relevant and computationally tractable
-	timescale.} \deleted[id=PD]{Here,}Population biomass growth was
-modelled as a function of previous recruited biomass, intrinsic population
-growth and recruitment functionally linked to the adult population size.
-Biomass for each cell $c$ was incremented each day $d$ as follows (the full
-parameter list is detailed in Table \ref{tab: pop_variable}): 
+keeping track of individuals\citep{Deriso1980, Schnute1985, Dichmont2003}. A
+daily time-step was chosen to discretise continuous population processes on a
+biologically relevant and computationally tractable timescale. Population
+biomass growth was modelled as a function of previous recruited biomass,
+intrinsic population growth and recruitment functionally linked to the adult
+population size.  Biomass for each cell $c$ was incremented each day $d$ as
+follows (the full parameter list is detailed in Table \ref{tab: pop_variable}): 
 \begin{equation}
@@
 \end{equation}
-where $\rho$ is Brody's coefficient, shown to be equal to $\mathrm{e}^{-K}$ when $K$ is
-the growth rate from a von Bertalanffy logistic growth model
+where $\rho$ is Brody's coefficient, shown to be equal to $\mathrm{e}^{-K}$
+when $K$ is the growth rate from a von Bertalanffy logistic growth model
 \citep{Schnute1985}. $Wt_{R-1}$ is the average weight of fish prior to
@@
 \begin{equation}
-C_{c,d} = \frac{F_{c,d}}{F_{c,d} + M_{c,d}} * (1 - \mathrm{e}^{-(F_{c,d} + M_{c,d})})
-\cdot B_{c,d}
+C_{c,d} = \frac{F_{c,d}}{F_{c,d} + M_{c,d}} \cdot \left(1 -
+	\mathrm{e}^{-(F_{c,d} + M_{c,d})}\right) \cdot B_{c,d}
 \end{equation}
@@
 fishing effort and catchability of the gear, and $D$ is the density of the
-population at the location fished. \todo{\added[id=CM]{[link $F$ to effort and
-		catchability - as I think we have F as an emergent property of
-		the fleets rather than something we solve for (I could be wrong
-		though!) - catch for a vessel is a product of catchability and
-		biomass, i.e. C = qB, but this catch is summed to solve for F.
-		So its both really]}}\\
+population at the location fished. \\
 
@@
 Recruitment is modelled through a function relating to adult biomass. In
-\emph{MixFishSim}, it can be either as a stochastic Beverton-Holt stock-recruit
+\textit{MixFishSim}, it can be either as a stochastic Beverton-Holt stock-recruit
 form \citep{Beverton1957}: 
@@
 probabilities of moving into the spawning grounds from adjacent cells. We
-incorporate characterisation of a number of different fishing
-\added[id=PD]{fleet dynamics} exploiting four fish populations with different
-spatial and population demographics. The following describes the implementation
-of each of the sub-modules.
-
-To simulate \deleted[id=JJ]{how} fish population\deleted[id=JJ]{s might be}
-distribut\replaced[id=JJ]{ion}{ed} in space and time\deleted[id=JJ]{, we
-	employed} a Gaussian spatial process \added[id=JJ]{was employed} to
-model habitat suitability for each of the populations on a 2d grid. \\
-
-\deleted[id=PD]{the habitat}We first define\added[id=PD]{d} a Gaussian random
-field process\todo{\added[id=JJ]{Not clear how habitat/GRF affect local
-		abundances, only have $B_{y,d}$}\added[id=PD]{Have included
-		cell reference, $c$ to make spatial link explicit}}, $\{S(c) :
-c \in \mathbb{R}^2\}$, \deleted[id=PD]{that is a stochastic process} where
-\added[id=PD]{for} any set of cells $c_{1}, \dots, c_{n}$ \deleted[id=PD]{where
-	for each $c_{i} \in \mathbb{R}^2$}, the joint distribution of $S =
-\{S(c1),\dots S(c_{n})\}$ is multivariate Gaussian with a \textit{Matérn}
-\deleted[id=PD]{family of}covariance structure\deleted[id=PD]{s},
-\replaced[id=PD]{where}{one where} the correlation strength weakens with
-distance\deleted[id=PD]{(i.e. the correlation between $S(x)$ and $S(x')$
-	decreases as the distance $u = ||x - x'||$ increases)}.
-\added[id=PD]{This enables us to model the spatial autocorrelation observed in
+characterise a set of different fishing fleet dynamics exploiting four fish
+populations with different spatial and population demographics. \\
+
+To simulate fish population distribution in space and time a Gaussian spatial
+process was employed to model habitat suitability for each of the populations
+on a 2d grid.  We first defined a Gaussian random field process, $\{S(c) : c \in
+\mathbb{R}^2\}$, where for any set of cells $c_{1}, \dots, c_{n}$, the joint
+distribution of $S = \{S(c1),\dots S(c_{n})\}$ is multivariate Gaussian with a
+\textit{Matérn} covariance structure, where the correlation strength weakens
+with distance. This enables us to model the spatial autocorrelation observed in
 animal populations where density is more similar in nearby locations
-	\citep{Tobler1970, F.Dormann2007}} and we change the parameters to
-implement different spatial structures for the different populations using the
+\citep{Tobler1970, F.Dormann2007} and we change the parameters to implement
+different spatial structures for the different populations using the
 \textit{RandomFields} R package \citep{Schlater2015}. We define a stationary
 habitat field and combine with a temporally dynamic thermal tolerance field to
-imitate two key drivers of population dynamics. Each population
-\replaced[id=PD]{was}{is} initialised at a single location, and subsequently
-move\replaced[id=PD]{d}{s} according to a probabilistic
-distrib\added[id=PD]{u}tion based on habitat suitability (represented by the
-normalised values from the GRFs), temperature and distance
-from current cell\replaced[id=PD]{:}{.} 
+imitate two key drivers of population dynamics. Each population was initialised
+at a single location, and subsequently moved according to a probabilistic
+distribution based on habitat suitability (represented by the normalised values
+from the GRFs), temperature and distance from current cell: 
 \begin{equation}
-	Pr(J | I) = \frac{\mathrm{e}^{-\lambda * d_{IJ}} \cdot
+	Pr(C_{wk+1} = J | C_{wk} =I) = \frac{\mathrm{e}^{-\lambda * d_{IJ}} \cdot
 		(Hab_{J,p}^2 \cdot
@@
 temperature tolerance for cell $J$ by population $p$ in week $wk$ (see
-below).\\
+below). \\
 
 During pre-defined weeks of the year the habitat suitability is modified with
-\added[id=PD]{user-defined} spawning habitat locations\deleted[id=PD]{s},
-\replaced[id=PD]{resulting in}{meaning} each population
-\replaced[id=PD]{having}{has} concentrated areas where spawning takes place. In
-the simulations the populations move\deleted[id=PD]{s} towards
-\replaced[id=PD]{these cells}{this} in the weeks prior to spawning, resulting
-in directional movement towards the spawning grounds.\todo{\added[id=JM]{What
-		does it mean concisely? Areas are assigned?} \added[id=PD]{Yes,
-		the areas are pre-defined - I have amended to reflect and tried
-		to clarify}} \\
-
-\replaced[id=JJ]{An}{, with an} advection-diffusion process\deleted[id=JJ]{to}
-control\added[id=JJ]{s}\deleted[id=JJ]{how the} population\deleted[id=JJ]{s}
-move\replaced[id=JJ]{ment}{d}, with a time-varying temperature covariate used
-to change the interaction between time and suitable habitat on a weekly
-time-step\todo{\added[id=JJ]{What have a temperature covariate? Could just use
-		time}\added[id=PD]{Was intended as some biological meaning -
-		species thermal tolerances load onto the temperature effect -
-		so could be different per species}}.  \deleted[id=JJ]{This was
-	intended to balance realism in population movement, capturing the main
-	directed and random processes, and practicality of modelling the
-	population rather than individual fish.} Each population $p$
-\replaced[id=PD]{wa}{i}s assigned a thermal tolerance with mean,
-$\mu\added[id=PD]{_{p}}$ and variance, $\sigma^2\added[id=PD]{_{p}}$ so that
+user-defined spawning habitat locations, resulting in each population having
+concentrated areas where spawning takes place. In the simulations the
+populations move towards these cells in the weeks prior to spawning, resulting
+in directional movement towards the spawning grounds. \\
+
+An advection-diffusion process controls population movement, with a
+time-varying temperature covariate used to change the interaction between time
+and suitable habitat on a weekly time-step. Each population $p$ was assigned a
+thermal tolerance with mean, $\mu_{p}$ and variance, $\sigma^2_{p}$ so that
 each cell and population temperature suitability is defined that:
 \begin{equation}
-	Tol_{c, p\added[id=PD]{, wk}} = \frac{1}{ \sqrt (2\pi \cdot \sigma^2_{p})} \cdot \exp(-
+	Tol_{c, p, wk} = \frac{1}{ \sqrt (2\pi \cdot \sigma^2_{p})} \cdot \exp(-
 		\frac{(T_{c\added[id=PD]{, wk}} - \mu_{p})^2}{2 \cdot \sigma^2_{p}} )	
 \end{equation}
-Where $Tol_{c, p, \added[id=PD]{wk}}$ is the tolerance of population $p$ for
-cell $c$ \added[id=PD]{in week $wk$}, $T_{c, \added[id=PD]{wk}}$ is the
-temperature in the cell \added[id=PD]{given the week} and
-$\mu\added[id=PD]{_{p}}$ and $\sigma^2\added[id=PD]{_{p}}$ the mean and
-standard deviation of the population temperature tolerance. \\
-
-\added[id=PD]{The final combined process results in a population structure and
-	movement pattern unique to each species, with population movement
-	occurring on a weekly basis. The decision to model population movement
-	on a weekly timescale was to reflect that fish tend to aggregate in
-	species specific locations that have been observed to last around one
-	to two weeks \citep{Poos2007}. Therefore this process approximated the
-	demographic shifts in fish populations throughout a year with seasonal
-	spawning patterns (Figure \ref{S-fig:5}).}
+Where $Tol_{c, p, wk}$ is the tolerance of population $p$ for cell $c$ in week
+$wk$, $T_{c, wk}$ is the temperature in the cell given the week and $\mu_{p}$
+and $\sigma^2_{p}$ the mean and standard deviation of the population
+temperature tolerance. \\
+
+The final combined process results in a population structure and movement
+pattern unique to each species, with population movement occurring on a weekly
+basis. The decision to model population movement on a weekly timescale was to
+reflect that fish tend to aggregate in species specific locations that have
+been observed to last around one to two weeks \citep{Poos2007}. Therefore this
+process approximated the demographic shifts in fish populations throughout a
+year with seasonal spawning patterns (Figure \ref{S-fig:5}).
 
@@
 
-The fleet dynamics can be broadly categorised into three components; fleet
+Fleet dynamics can be broadly categorised into three components: fleet
 targeting - that determined the fleet catch efficiency and preference towards a
-particular species; trip-level decisions, that determined the initial location
+particular species; trip-level decisions, that determines the initial location
 to be fished at the beginning of a trip; and within-trip decisions, that
-determined movement from one fishing spot to another within a trip. Together,
-these elements implemented an explore-exploit type strategy for individual
+determines movement from one fishing spot to another within a trip. Together,
+these elements implement an explore-exploit type strategy for individual
 vessels to maximise their catch from an unknown resource distribution
@@
 behaviour due to different objectives, risk preference and targeting preference
-\citep{VanPutten2012a}. Therefore in the simulations fleet dynamics are the
-productive of individual experiences rather than pre-defined group dynamics.
+\citep{VanPutten2012a}. Therefore in the simulations fleet dynamics reflect
+individual experiences rather than pre-defined group dynamics.
 
@@
 
-Each fleet of \textit{n} vessels \replaced[id=PD]{was}{is} characterised by
-both a general efficiency, $Q_{fl}$, and a population specific efficiency,
-${Q_{fl, p}}$.  Thus, the product of these parameters [$Q_{fl} \cdot Q_{fl,
-	p}$] affect\replaced[id=PD]{s}{ed} the overall catch rates for the
-fleet and the preferential targeting of one population over another. This, in
-combination with the parameter choice for the step-function
-\added[id=PD]{defined below} (as well as some randomness from the exploratory
-fishing process) determine\replaced[id=PD]{d}{s} the preference of fishing
-locations for the fleet.
+Each fleet of \textit{n} vessels was characterised by both a general
+efficiency, $Q_{fl}$, and a population specific efficiency, ${Q_{fl, p}}$.
+Thus, the product of these parameters [$Q_{fl} \cdot Q_{fl, p}$] affects the
+overall catch rates for the fleet and the preferential targeting of one
+population over another. This, in combination with the parameter choice for the
+step-function defined below (as well as some randomness from the exploratory
+fishing process) determined the preference of fishing locations for the fleet.
 
@@
 confirmed past activity and past catch rates are strong predictors of fishing
-location choice. For this reason, the fleet dynamics sub-model
-include\replaced[id=PD]{d}{s} a learning component, where a vessel's initial
-fishing location in a trip \replaced[id=PD]{wa}{i}s based on selecting from
-previously successful fishing locations. This \replaced[id=PD]{wa}{i}s achieved
-by \added[id=PD]{calculating an expected revenue based on the catches from
-	locations fished} in the preceding trip as well as the same month
-periods in previous years and the travel costs from the port to the fishing
-grounds, and choosing randomly from the top 75 \% of fishing events
-\replaced[id=PD]{as defined by the expected profit, that has a seasonal
-	component}{in value}.
+location choice. For this reason, the fleet dynamics sub-model included a
+learning component, where a vessel's initial fishing location in a trip was
+based on selecting from previously successful fishing locations. This was
+achieved by calculating an expected revenue based on the catches from locations
+fished in the preceding trip as well as the same month periods in previous
+years and the travel costs from the port to the fishing grounds, and choosing
+randomly from the top 75 \% of fishing events as defined by the expected
+profit, that has a seasonal component.
 
@@
 
-Fishing locations within a trip are \added[id=PD]{initially} determined by a
-modified random walk process. \added[id=PD]{As the simulation progresses the
-	within-trip decision become gradually more influenced by experience
-	gained from past fishing locations (as per the initial trip-level
-	location choice), moving location choice towards areas of higher
-	perceived profit.} A random walk was chosen for the exploratory fishing
-process as it is the simplest assumption commonly used in ecology to describe
-\added[id=PD]{optimal} animal\deleted[id=PD]{movement which}
-search\replaced[id=PD]{ strategy}{ing} for \added[id=PD]{exploiting}
-homogeneously distributed prey about which there is uncertain knowledge
+Fishing locations within a trip are initially determined by a modified random
+walk process. As the simulation progresses the within-trip decision become
+gradually more influenced by experience gained from past fishing locations (as
+per the initial trip-level location choice), moving location choice towards
+areas of higher perceived profit. A random walk was chosen for the exploratory
+fishing process as it is the simplest assumption commonly used in ecology to
+describe optimal animal search strategy for exploiting heterogeneously
+distributed prey about which there is uncertain knowledge
 \citep{Viswanathan1999}. In a random walk, movement is a stochastic process
-through a series of steps\added[id=JJ]{. These steps have a length, and a
-	direction} that can either be equal in length or take some other
-functional form. The direction of the random walk was also correlated (known as
-`persistence') providing some overall \deleted[id=PD]{location of}directional
-movement \citep{Codling2008}\deleted[id=PD]{or uncorrelated}. \\
-
-We use a \textit{\replaced[id=JJ]{Lévy flight} {lévy walk}} which is a
-particular form of random walk characterised by a heavy-tailed distribution of
-step-length\replaced[id=JJ]{. The Lévy flight}{and} has received a lot of
-attention in ecological theory in recent years as having shown to have very
-similar characteristics as those observed by animals in nature, and being a
-near optimum searching strategy for predators pursuing patchily distributed
-prey \citep{Viswanathan1999, Bartumeus2005, Sims2008}.  \citet{Bertrand2007}
-showed that Peruvian anchovy fishermen have a stochastic search pattern similar
-to that observed with a lévy flight. However, it remains a subject of debate
-\added[id=PD]{\citep[e.g. see][]{Edwards2011, Reynolds2015}}, with the
-contention that search patterns may be more simply characterised as random
-walks \citep{Sakiyama2013} with specific patterns related to the
-characteristics of the prey field \citep{Sims2012}. \\
+through a series of steps. These steps have a length, and a direction that can
+either be equal in length or take some other functional form. The direction of
+the random walk was also correlated (known as `persistence') providing some
+overall directional movement \citep{Codling2008}. \\
 
@@
 came from.  The step length (i.e. the distance travelled from the current to
-the next fishing location) is determined by \deleted[id=JJ]{relating} recent
-fishing success, measured as the summed value of fish caught (revenue, $Rev$),
+the next fishing location) is determined by relating recent
+fishing success, measured as the summed value of fish caught (revenue, $Rev$);
 \begin{equation}
@@
 \end{equation}
-where $\replaced[id=PD]{L}{C}_{p}$ is \replaced[id=PD]{landings}{catch} of a
-population $p$, and $Pr_{p}$ price of a population. All species prices were
-kept the same across fleets and seasons. Here, when fishing is successful
-vessels remain in a similar location and continue to exploit the local fishing
-grounds. When unsuccessful, they move some distance away from the current
-fishing location.  The movement distance retains some degree of stochasticity,
-that can be controlled separately, but is determined by the
-relationship: 
+where $L_{p}$ is landings of a population $p$, and $Pr_{p}$ price of a
+population. All species prices were kept the same across fleets and seasons.
+Here, when fishing is successful vessels remain in a similar location and
+continue to exploit the local fishing grounds. When unsuccessful, they move
+some distance away from the current fishing location.  The movement distance
+retains some degree of stochasticity, that can be controlled separately, but is
+determined by the relationship: 
 \begin{equation}
 	StepL = \mathrm{e}^{log(\beta_{1}) + log(\beta_{2}) -
-		(log(\frac{\beta_{1}}{\beta_{3}}))} * Rev
-\end{equation}\todo{\added[id=JJ]{So
-			step length increases with increasingly gross
-			revenue?}\added[id=PD]{No, the opposite}}
+		\left(log\left(\frac{\beta_{1}}{\beta_{3}}\right)\right)} \cdot Rev
+\end{equation}
 Where $\beta_{1}$, $\beta_{2}$ and $\beta_{3}$ are parameters determining the
@@
 	\begin{split}
- (x2, y2) =  & x1 + StepL \cdot \cos (\frac{\pi \cdot Br}{180}), \\
-             & y1 + StepL \cdot \sin (\frac{\pi \cdot Br}{180}) \\	
+ (x2, y2) =  & x1 + L \cdot \cos \left(\frac{\pi \cdot Br}{180}\right), \\
+             & y1 + L \cdot \sin \left(\frac{\pi \cdot Br}{180}\right) \\	
  with  \hspace{0.5cm}     & Br_{t-1} < 180, Br_{t} = 180 + \sim vm[(0,360), k] \\
@@
 \end{equation}
-where $k$ the concentration parameter from the von \replaced[id=JJ]{M}{m}ises
-distribution that we correlate with the revenue so that $k = (Rev + 1 /
-RefRev) * max_{k}$, where $max_{k}$ is the maximum concentration value, $k$,
-and $RefRev$ is parametrised as for $\beta_{3}$ in the step length function. A
-realised example of the step length and turning angle relationships to revenue
-can be seen at Figure \ref{S-fig:15}.
+where $L$ is the step length, $k$ the concentration parameter from the von
+Mises distribution that we correlate with the revenue so
+that $k = (Rev + 1 / RefRev) * max_{k}$, where $max_{k}$ is the maximum
+concentration value, $k$, and $RefRev$ is parametrised as for $\beta_{3}$ in
+the step length function. A realised example of the step length and turning
+angle relationships to revenue can be seen at Figure \ref{S-fig:15}.
 
@@
 \citep{Gillis1998}. If several vessels are fishing on the same patch of fish,
-local depletion and interference \added[id=JJ]{competition} will affect fishing
-location choice of the fleet as a whole \citep{Rijnsdorp2000, Poos2007a}. In
-order to account for this behaviour, the fishing sub-model operates spatially
-on a daily time-step so that for future days the biomass available to the
-fishery is reduced in the areas fished. The cumulative effect is to make
-heavily fished areas less attractive as a future fishing location choice as
-reduced catch rates will be experienced.
+local depletion and interference competition will affect fishing location
+choice of the fleet as a whole \citep{Rijnsdorp2000, Poos2007a}.  To account
+for this behaviour, the fishing sub-model operates spatially on a daily
+time-step so that for future days the biomass available to the fishery is
+reduced in the areas fished. The cumulative effect is to make heavily fished
+areas less attractive as a future fishing location choice as reduced catch
+rates will be experienced.
 
@@
 begins each year at the same time for a given number of stations (a fixed
-station survey design). Catches of the populations \replaced[id=JJ]{at each
-	station}{present} are recorded but not removed from the population
-(catches are assumed to have negligible impact on population dynamics). This
-provides a fishery independent snapshot of the populations at a regular spatial
-\replaced[id=JJ]{intervals}{distribution} each year, similar to scientific
+station survey design). Catches of the populations at each station are recorded
+but not removed from the population (catches are assumed to have negligible
+impact on population dynamics). This provides a fishery independent snapshot of
+the populations at a regular spatial intervals each year, similar to scientific
 surveys undertaken by fisheries research agencies. \\
@@
 The simulation framework is implemented in the statistical software package R
-\citep{RCoreTeam2017} \replaced[id=PD]{and}{;} available as an R package from
-the authors github site (\url{www.github.com/pdolder/MixFishSim}).\\
+\citep{RCoreTeam2017} and available as an R package from the author's github
+site (\url{www.github.com/pdolder/MixFishSim}).\\
 
 \section{Parameterisation}
+We parameterise \textit{MixFishSim} to investigate the influence of data
+aggregation on spatial inference.
 
@@
 
-We parametrised the simulation model for four populations with different
-demographics; growth rates, natural mortality and recruitment parameters (Table
-\ref{tab:1}). Habitat preference (Figure \ref{S-fig:1}) and temperature
-tolerances (Figures \ref{S-fig:3}, \ref{S-fig:4}) were defined to be unique to
-each population resulting in differently weekly distribution patterns (Figures
-\ref{S-fig:5}-\ref{S-fig:7}). In addition, each of the populations was assumed
-to have two defined spawning areas that result in the populations moving
-towards these areas in pre-defined weeks (Figure \ref{S-fig:2}) with
-population-specific movement rates (Table \ref{tab:1}). In such a
-configuration, the individual habitat preferences and thermal tolerances result
-in different spatial habitat use for each population (Figure \ref{fig:9}) and
-consequently different seasonal exploitation patterns (Fishing mortality in
-Figure \ref{fig:10}).
+We parametrised the simulation model for four example populations with
+different demographics, growth rates, natural mortality and recruitment
+parameters (Table \ref{tab:1}). Habitat preference (Figure \ref{S-fig:1}) and
+temperature tolerances (Figures \ref{S-fig:3}, \ref{S-fig:4}) were defined to
+be unique to each population resulting in differently weekly distribution
+patterns (Figures \ref{S-fig:5}-\ref{S-fig:7}). In addition, each of the
+populations was assumed to have two defined spawning areas that result in the
+populations moving towards these areas in pre-defined weeks (Figure
+\ref{S-fig:2}) with population-specific movement rates (Table \ref{tab:1}). In
+such a configuration, the individual habitat preferences and thermal tolerances
+result in different spatial habitat use for each population (Figure
+\ref{fig:9}) and consequently different seasonal exploitation patterns (Fishing
+mortality in Figure \ref{fig:10}).
 
@@
 The fleets were parametrised to reflect five different characteristic fisheries
-with unique exploitation dynamics (Table \ref{tab:2}).  \replaced[id=PD]{By
-	setting different catchability parameters ($Q_{fl, p}$) we create
-	different targeting preferences between the fleets and hence spatial
-	dynamics}{This ensures that different fleets have different spatial
-	dynamics, preferentially targeted different fish populations}.  The
-random walk process implies that within a fleet different vessels have
-different spatial distributions based on individual experience. The step
-function was parametrised dynamically within the simulations as the maximum
-revenue obtainable was not known beforehand. This was implemented so that
-vessels take smaller steps when fishing at a location that yields landings
-value in the top 90th percentile of the value experienced in that year so far
-(as defined per fleet in Table \ref{tab:2}). \\
+with unique exploitation dynamics (Table \ref{tab:2}). By setting different
+catchability parameters ($Q_{fl, p}$) we create different targeting preferences
+between the fleets and hence spatial dynamics.  The learned random walk process
+implies that within a fleet different vessels have different spatial
+distributions based on individual experience. The step function was
+parametrised dynamically within the simulations as the maximum revenue
+obtainable was not known beforehand. This was implemented so that vessels take
+smaller steps when fishing at a location that yields landings value in the top
+90th percentile of the value experienced in that year so far (as defined per
+fleet in Table \ref{tab:2}). \\
 
@@
 The survey simulation was set up with a fixed gridded station design with 100
-stations fished each year, starting on day 92 \added[id=PD]{and ending on day
-	112 (5 stations per day)} with same catchability parameters for all
-populations ($Q_{p} = 1$). This approximates a real world survey design with
-limited seasonal and spatial coverage.
+stations fished each year, starting on day 92 and ending on day 112 (5 stations
+per day) with same catchability parameters for all populations ($Q_{p} = 1$).
+This approximates a real world survey design with limited seasonal and spatial
+coverage.
 
@@
 
-To illustrate the capabilities of \emph{MixFishSim}, we investigate the
+To illustrate the capabilities of \textit{MixFishSim}, we investigate the
 influence of the temporal and spatial resolution of different data sources on
@@
 populations. Fishing takes place four times a day per vessel and five days a
-week, while population movement is every week.
-
-We allow the simulation to run unrestricted for 30 years\todo{\added[id=JJ]{Is
-		there equilibrium after 5 years or still some trend in B?
-	}\added[id=PD]{I have rerun to ensure some steady state dynamics}},
-then implement spatial closed areas for the last 20 years of the simulation
-based on data (either derived from the commercial catches,
-fisheries-independent survey or the 'real population') used at different
-spatial and temporal scales. \\
+week, while population movement is every week. \\
+
+\textit{How does sampling-derived fisheries data reflect the underlying
+	population structure?} \\
+
+To answer this question we compare different spatial and temporal aggregations
+of the real population distributions to:
+\begin{enumerate}[label=\alph*)]
+	\item \textbf{fisheries-independent data:} the inferred population from
+		a fixed-site sampling survey design as commonly used for
+		fisheries monitoring purposes;
+	\item \textbf{fisheries-dependent data:} the inferred population from
+		our fleet model that includes fishery-induced sampling
+		dynamics.
+\end{enumerate}
+
+We allow the simulation to run unrestricted for 30 years, then implement
+spatial closed areas for the last 20 years of the simulation based on data
+(either derived from the commercial catches, fisheries-independent survey or
+the real population used at different spatial and temporal scales. \\
 
 The following steps are undertaken to determine closures:
-\todo{\added[id=JJ]{Procedure unclear. Refer to symbols in methods section or
-		switch order starting with description of data type
-		etc..}\added[id=PD]{Yes, will redo}}
+
 \begin{enumerate}
-	\item Extract data source
-	\item Aggregate according to desired spatial and temporal resolution
+	\item Extract data source (real population, commercial or survey), 
+	\item Aggregate according to desired spatial and temporal resolution,
 	\item Interpolate across entire area at desired resolution using simple
@@
 	\item \textbf{data types:} commercial logbook data, survey data and
-		`real population',
+		real population,
 	\item \textbf{temporal resolutions:} weekly, monthly and yearly
@@
 
-\subsection{Simulation dynamics}
+\subsection{Emergent simulation dynamics}
 
@@
 areas where the highest revenue were experienced, as shown by
-\added[id=PD]{Figure} \ref{fig:13}, where several trips for the vessel
-overlaid on the revenue field, i.e. 
-$$\sum^c_{c=1}\sum^s_{s=1} B_{s,c} \cdot Q_{s,c}$$
+\added[id=PD]{Figure} \ref{fig:13}, where several trips for the vessel overlaid
+on the revenue field, i.e. $$\sum^c_{c=1}\sum^s_{s=1} B_{s,c} \cdot Q_{s,c}$$
 
@@
 some shared and some different fishing grounds depending on their own personal
-experience during the explore phase of the fishery (\added[id=PD]{Figure}
-\ref{S-fig:14}). This results from the randomness in the correlated random walk
-step function, with distance moved during the exploitation phase and the
-direction stochastically related to the revenue experienced on the fishing
-ground (\replaced[id=PD]{Figure}{while}
-\ref{S-fig:15}).\todo{\added[id=JJ]{Move some of the supplementary figures to
-		the manuscript}}
+experience during the exploratory phase of the fishery (Figure \ref{S-fig:14}).
+This results from the randomness in the correlated random walk step function,
+with distance moved during the exploitation phase and the direction
+stochastically related to the revenue experienced on the fishing ground (Figure
+\ref{S-fig:15}).
 
@@
 	population structure?}
-
-In order to answer this question we compare different spatial and temporal
-aggregations of the 'real population' distributions to:
-\begin{enumerate}[label=\alph*)]
-	\item \textbf{fisheries-independent data:} the inferred population from
-		a fixed-site sampling survey design as commonly used for
-		fisheries monitoring purposes;
-	\item \textbf{fisheries-dependent data:} the inferred population from
-		our fleet model that includes fishery-induced sampling
-		dynamics.
-\end{enumerate}
 
@@
 5 x 5 grid shows similar patterns and, while losing some of the spatial detail,
-there remains good consistency between the `real population' and the commercial
+there remains good consistency between the real population and the commercial
 data. Survey data starts to pick out some of the similar patterns as the other
@@
 the spatial resolutions for all data sources, and some differences between the
-survey, commercial and 'real population' data emerge. \\
+survey, commercial and real population data emerge. \\
 
@@
 the data over a ten-year period, with weekly (top), monthly (middle) and yearly
-(bottom) catch compositions from across an aggregated 20 x 20 area. In the
-'real population', the monthly aggregation captures the major patterns of
-composition seen in the weekly data with similar mean and standard deviations.
-In the weekly data species 1 = 9.36 (3.99), species 2 = 83.2 (5.60), species 3
-= 3.57 (1.23), species 4 = 3.91 (1.59); in the monthly data species 1 = 9.23
-(3.87), species 2 = 83.3 (5.52), species 3 = 3.62 (1.15), species 4 = 3.86
-(1.52). While means were similar some of the variation was lost when aggregated
-to an annual level; species 1 = 9.90 (0.173), species 2 = 82.2 (0.308), species
-3 = 3.82 (0.119), species 4 = 4.03 (0.0502).\\
+(bottom) catch compositions from across an aggregated 20 x 20 area. In the real
+population, the monthly aggregation captures the major patterns of composition
+seen in the weekly data with the percentage of different species in the catch
+having similar mean and standard deviations.  In the weekly data species 1 =
+9.36 (3.99), species 2 = 83.2 (5.60), species 3 = 3.57 (1.23), species 4 = 3.91
+(1.59); in the monthly data species 1 = 9.23 (3.87), species 2 = 83.3 (5.52),
+species 3 = 3.62 (1.15), species 4 = 3.86 (1.52). While means were similar some
+of the variation was lost when aggregated to an annual level; species 1 = 9.90
+(0.173), species 2 = 82.2 (0.308), species 3 = 3.82 (0.119), species 4 = 4.03
+(0.0502).\\
 
 The commercial data on a weekly basis shows some of the same patterns as the
-'real population', though the species 1 (in red) is less well represented and
+real population, though the species 1 (in red) is less well represented and
 some weeks are missing catches from the area. Here, weekly and monthly
@@
 reductions in fishing mortality happened immediately after the closures,
-following which the fisheries "adapted" to the closures and fishing mortality
+following which the fisheries ``adapted" to the closures and fishing mortality
 increased again somewhat. The exception to the success was the closures
@@
 (yearly) that was ineffective with all data sources. As expected, closures
-based on the "known" population distribution were most effective, with
+based on the ``known" population distribution were most effective, with
 differing degrees of success using the commercial data. Fishing mortality rates
@@
 the fine-scale resolution. In this case the closures were sufficiently large to
-protect a core are of the habitat for the population, but this was achieved in
+protect a core area of the habitat for the population, but this was achieved in
 a fairly crude manner by closing a large area - including area where the
-species was not found (Figure \ref{fig:17}) that may have consequences in
-terms of restricting the fishery in a much larger area than necessary. \\
+species was not found (Figure \ref{fig:17}) that may have consequences in terms
+of restricting the fishery in a much larger area than necessary. \\
 
@@
 %% General intro
-Our study evaluates the importance of data scaling and considers potential bias
+Our study presents a new highly resolved fisheries simulation framework,
+evaluates the importance of data scaling and considers potential bias
 introduced through data aggregation when using fisheries data to infer
@@
 management approaches increasingly employing more nuanced spatiotemporal
-approaches in order to maximise productivity while taking account of both the
-biological and human processes operating on different time-frames
-\citep{Dunn2016}, understanding assumptions behind the data used - increasingly
-a combination of logbook and positional information from vessel monitoring
-systems - is vital to ensure measures are effective. \\
+approaches to maximise productivity while taking account of both the biological
+and human processes operating on different time-frames \citep{Dunn2016},
+understanding assumptions behind the data used - increasingly a combination of
+logbook and positional information from vessel monitoring systems - is vital to
+ensure measures are effective. \\
 
@@
 We employ a simulation approach to model each of the population and fishery
-dynamics in a hypothetical 'mixed fishery', allowing us to i) evaluate the
+dynamics in a hypothetical `mixed fishery', allowing us to i) evaluate the
 consequences of different aggregation assumptions on our understanding of the
@@
 fished. Similarly, despite the even spatial coverage the survey was able to
-capture some of the same spatial patterns as the 'real population', but missed
+capture some of the same spatial patterns as the real population, but missed
 others due to gaps between survey stations limiting spatial and temporal
-coverage. This provides a challenge when modelling unsampled areas in inferring
-species distribution maps, though these limitations may be overcome by
-understanding the relationship between the species and habitat covariates where
-these are known at unsampled locations \citep{Robinson2011}. \\
+coverage \added[id=CM]{(Figures X,Y,Z)}. This provides a challenge when
+modelling unsampled areas in inferring species distribution maps, though these
+limitations may be overcome by understanding the relationship between the
+species and habitat covariates where these are known at unsampled locations
+\citep{Robinson2011}. \\
 
@@
 `aggregation bias' as the data may only be representative of some point (or no
-point) in time. The monthly data shows some consistency between the 'real population' and
-commercial data for species 2 - 4, though species 1 remains under-represented.
-On an annual basis, interestingly the commercial data under represents the
-first species (in red) while the survey over represents species 1. This is
-likely due to the biases in commercial sampling, with the fisheries not
-targeting the areas where species 1 are present and the survey sampling areas
-where species 1 is more abundant than on average. \\
-
-This indicates that fixed closures, at the right resolution, when based on
-commercially derived data have the potential to reduced fishing mortality. The
-likely cost of poor spatial and temporal resolution is associated with reduced
-effectiveness and potentially closing fishing opportunities for other
-fisheries. \\
+point) in time. The monthly data shows some consistency between the real
+population and commercial data for species 2 - 4, though species 1 remains
+under-represented.  On an annual basis, interestingly the commercial data under
+represents the first species (in red) while the survey over represents species
+1. This is likely due to the biases in commercial sampling, with the fisheries
+not targeting the areas where species 1 are present and the survey sampling
+areas where species 1 is more abundant than on average. This indicates that
+fixed closures, at the right resolution, when based on commercially derived
+data have the potential to reduced fishing mortality. The likely cost of poor
+spatial and temporal resolution is associated with reduced effectiveness and
+potentially closing fishing opportunities for other fisheries. \\
 
@@
 according to fixed habitat preferences and temperature gradients (Figures
-\ref{S-fig:1}, \ref{S-fig:3}). Our assumptions in parametrising the model
+\ref{S-fig:1}, \ref{S-fig:3}). Our assumptions in parameterising the model
 (movement rates, temperature tolerances) will have a direct impact on our
@@
 of bias in any inference using commercial data and should also be explored. For
-example, MixFishSim could be altered to allow for spatiotemporal appraisal of
-the impact of discarding on fisher behaviour and underlying populations via
-inclusion as discarding behaviour, or through move-on rules or cessation of
-fishing activity when quota is exhausted. \\
-
-\subsection{Future applications of MixFishSim}
+example, \textit{MixFishSim} could be altered to allow for spatiotemporal
+appraisal of the impact of discarding on fisher behaviour and underlying
+populations via inclusion as discarding behaviour, or through move-on rules or
+cessation of fishing activity when quota is exhausted. \\
+
+\subsection{Future applications of \textit{MixFishSim}}
 
@@
 
-Other novel applications of our framework could be; testing different survey
+Other novel applications of our framework could be: testing different survey
 designs given multiple species and data generating assumptions \citep{Xu2015};
@@
 
-MixFishSim provides a detailed simulation framework to explore the interaction
-of multiple fisheries exploiting different fish populations. The framework
-enables users to evaluate assumptions in modelling commercially derived data
-through comparison to the true underlying dynamics at a fine spatial and
-temporal scale.  Understanding these dynamics, the limitations of the data and
-any potential biases that may be introduced when making inference on
-spatiotemporal interactions will enable users to identify weaknesses in
+\textit{MixFishSim} provides a detailed simulation framework to explore the
+interaction of multiple fisheries exploiting different fish populations. The
+framework enables users to evaluate assumptions in modelling commercially
+derived data through comparison to the true underlying dynamics at a fine
+spatial and temporal scale.  Understanding these dynamics, the limitations of
+the data and any potential biases that may be introduced when making inference
+on spatiotemporal interactions will enable users to identify weaknesses in
 modelling approaches and identity where data collection is needed to strengthen
@@
 
-MixFishSim has numerous potential additional applications as it enables the
-user to apply methods to a fisheries system where there is detailed
+\textit{MixFishSim} has numerous potential additional applications as it
+enables the user to apply methods to a fisheries system where there is detailed
 understanding of underlying spatiotemporal dynamics. This enables
@@
 \input{Process_model.tex}
-
+%\begin{comment}
 \begin{figure}[!ht]
@@
 \end{figure}	
+%\end{comment}
 

### 2019-09-14 write_up/mixfishsim_ecolmod.tex
revising abstract

@@
 
-Most fisheries exploit a variety of spatially and temporally heterogeneous fish
-populations using species-unselective gear. This can result in unintended,
-unwanted catch of low quota or protected species and reducing these catches is
-crucial for biological and economic sustainability of `mixed fisheries'. \\
-%%
-If fisheries are to avoid unwanted catch, an in-depth understanding of
-spatiotemporal fishery dynamics is required. However, traditional scientific
-advice is limited by a lack of highly resolved knowledge of population
-distributions and movement, and how fishers interact with different fish
-populations. Because data on fish location at high temporal and spatial
-resolutions is expensive and difficult to collect proxies are usually inferred
-from scientific surveys or commercial catches with limited spatial and temporal
-resolution. \\ 
 %%
@@
 Fishers exploit a variety of fish populations that are heterogeneously
-distributed in space and time, with varying knowledge of species distributions.
-In doing so fisheries catch an assemblage of species and may discard over-quota
-catch when managed by single species quotas and fishers exhaust one or more
-quota. This may lead to overexploitation of fish populations
-\citep{Ulrich2011a, Batsleer2015}. Discarding of fish in excess of quota limits
-the ability to maintain fishing mortality within sustainable limits
-\citep{Alverson1994, Crowder1998, Rijnsdorp2007} and the ability to manage for
-the biological and economic sustainability of fisheries. As such, there is
-increasing interest in technical solutions such as gear and spatial closures as
-measures to reduce unwanted catch \citep{Kennelly2002, Catchpole2008,
-	Bellido2011, Cosgrove2019}. \\
-
-Adaptive spatial management strategies have been proposed as a way of reducing
-over-quota discards \citep{Holmes2011, Little2014, Dunn2014a}. However,
-implementation is restricted by lack of knowledge of fish and fishery
-spatiotemporal dynamics and understanding of the scale at which processes
-become important for management. Understanding the correct scale for spatial
-measures is crucial for implementing effective solutions which  minimising
-economic impact \citep{Dunn2016}. For example, the problem can be to identify a
-scale that promotes species avoidance for vulnerable or low quota species while
-allowing continuance of sustainable fisheries for available quota species.\\
+distributed in space and time with varying knowledge of species distributions.
+As fishers do not have full control over what species they select in `mixed
+fisheries' this can result in catch of low quota or protected species. This
+leads to discarding of over-quota catch if it is a species for which they have
+no quota, limiting control over fishing mortality \citep{Alverson1994,
+	Crowder1998, Rijnsdorp2007} and the ability to manage fisheries for the
+biological and economic sustainability \citep{Ulrich2011a, Batsleer2015}.\\
+
+There is increasing interest in technical solutions such as gear and spatial
+closures as measures to reduce unwanted catch \citep{Kennelly2002,
+	Catchpole2008, Bellido2011, Cosgrove2019} and adaptive spatial
+management strategies have been proposed as a way of reducing over-quota
+discards \citep{Holmes2011, Little2014, Dunn2014a}. However, if fisheries are
+to reduce unwanted catch through spatial avoidance, an in-depth understanding
+of spatiotemporal fishery dynamics is required. Implementation of spatial
+measures is hampered by a lack of knowledge of fish and fishery spatiotemporal
+dynamics and understanding of the scale at which processes become important for
+management. \\
+
+Understanding the correct scale for spatial measures is also crucial as it
+enables implementation of effective solutions which minimise economic impact
+\citep{Dunn2016}. For example, the problem can be to identify a scale that
+promotes species avoidance for vulnerable or low quota species while allowing
+continuance of sustainable fisheries for available quota species. Identifying
+the correct spatial scale remains a challenge because data on fish location at
+high temporal and spatial resolutions is expensive and difficult to collect and
+proxies are usually inferred from scientific surveys or commercial catches with
+limited spatial and temporal resolution. \\
 
 Identifying appropriate spatial scales for fisheries closures has been a
-challenge in the past but is crucial to their success \citep{Costello2010,
-	Dunn2016}. Inference is hampered where spatial information is coarse
-due to low resolution reporting of fisheries catch which is aggregated across
-larger gridded areas \citep{Branch2005}. Further, if data does not allow
-identification of spatial features it may lead to poorly sited closures which
-are ineffectual or have unintended consequences. For example, increased benthic
-impact on previously unexploited areas from the cod closure in the North Sea
-were observed without the intended effect of reducing cod exploitation
-\citep{Rijnsdorp2001,Dinmore2003}). More refined spatiotemporal information has
-since become available through the combination of logbook and Vessel Monitoring
-System (VMS) data \citep{Lee2010, Bastardie2010, Gerritsen2012, Mateo2016} and
-more real-time spatial management has been possible \citep[e.g.][]{Holmes2011}.
-However, fishers establish favoured fishing grounds through an explore-exploit
-strategy \citep{Bailey2018} where they search for areas with high catches and
-then use experience to return to areas where they've experienced high catch in
-the past.  This leads to an inherently biased sampling where target species are
+highlighted as crucial to their success \citep{Costello2010, Dunn2016}.
+Inference is hampered where spatial information is coarse due to low resolution
+reporting of fisheries catch which is aggregated across larger gridded areas
+\citep{Branch2005}. Further, if data does not allow identification of spatial
+features it may lead to poorly sited closures which are ineffectual or have
+unintended consequences. For example, increased benthic impact on previously
+unexploited areas from the cod closure in the North Sea were observed without
+the intended effect of reducing cod exploitation
+\citep{Rijnsdorp2001,Dinmore2003}).\\
+
+More refined spatiotemporal information has since become available through the
+combination of logbook and Vessel Monitoring System (VMS) data \citep{Lee2010,
+	Bastardie2010, Gerritsen2012, Mateo2016} and more real-time spatial
+management has been possible \citep[e.g.][]{Holmes2011}.  However, fishers
+establish favoured fishing grounds through an explore-exploit strategy
+\citep{Bailey2018} where they search for areas with high catches and then use
+experience to return to areas where they've experienced high catch in the past.
+This leads to an inherently biased sampling where target species are
 over-represented in the catch as fishers exploit areas of high abundance. \\

### 2019-09-16 write_up/Supplementary.tex
Text revisions

@@
 \begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{Plots/vessel_move}
-	\caption{vessel movement - a single trip movement for one vessel}
-	\label{fig:11}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width = \linewidth]{Plots/vessel_multi_move}
-	\caption{vessel movement for multiple trips from a single vessel. Note
-	the movement off the side pops up the other side, but is joined by a
-	line across the grid. This is from the torus approach rather than the
-	edges being barriers}
-	\label{fig:12}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{Plots/fleet_moves}
-	\caption{An entire fleets (20 vessels) movement for a single trip}
-	\label{fig:14}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../tests/plots/step_function}
-	\caption{Realised step function - the step function as realised for a
-		single fleet. For turning angles, it can be seen that at higher
-	values, the turning range is less}
-	\label{fig:15}
-\end{figure}
-
-\begin{figure}[!ht]
 	\includegraphics[width = \linewidth]{./Plots/Matern}

### 2019-09-16 write_up/mixfishsim_ecolmod.tex
Text revisions

@@
 \author[3]{Jean-Marc Guarini}
-\author[4]{Jan Jaap Poos}
+\author[4,5]{Jan Jaap Poos}
 
@@
 	Netherlands}
+\address[5]{Aquaculture and Fisheries Group, Wageningen University \& Research,
+	Zodiac Building 122, De Elst 1, 6708 WD Wageningen, the Netherlands}
 
@@
 concentration value, $k$, and $RefRev$ is parametrised as for $\beta_{3}$ in
-the step length function. A realised example of the step length and turning
-angle relationships to revenue can be seen at Figure \ref{S-fig:15}.
+the step length function.
 
@@
 populations moving towards these areas in pre-defined weeks (Figure
-\ref{S-fig:2}) with population-specific movement rates (Table \ref{tab:1}). In
-such a configuration, the individual habitat preferences and thermal tolerances
-result in different spatial habitat use for each population (Figure
-\ref{fig:9}) and consequently different seasonal exploitation patterns (Fishing
-mortality in Figure \ref{fig:10}).
+\ref{S-fig:2}) with population-specific movement rates (Table \ref{tab:1}).
 
@@
 
+Individual habitat preferences and thermal tolerances result in different
+spatial habitat use for each population (Figure \ref{fig:9}) and consequently
+different seasonal exploitation patterns (Fishing mortality in Figure
+\ref{fig:10}).
+
 It can be seen from a single vessels movements during a trip that the vessel
-exploits four different fishing grounds, three of them multiple times (Figure
-\ref{S-fig:11}), while across several trips fishing grounds that are further
-apart are fished (Figure \ref{S-fig:12}). These different locations relate to
+exploits three different fishing grounds, each of them multiple times (Figure
+\ref{fig:mv}(A)), while across several trips fishing grounds that are further
+apart are fished (Figure \ref{fig:mv} (B)). These different locations relate to
 areas where the highest revenue were experienced, as shown by
-\added[id=PD]{Figure} \ref{fig:13}, where several trips for the vessel overlaid
-on the revenue field, i.e. $$\sum^c_{c=1}\sum^s_{s=1} B_{s,c} \cdot Q_{s,c}$$
+\added[id=PD]{Figure} \ref{fig:13}, where several vessels tracks are
+overlaid on the revenue field, i.e. $$\sum^c_{c=1}\sum^s_{s=1} B_{s,c} \cdot
+Q_{s,c}$$
 
@@
 some shared and some different fishing grounds depending on their own personal
-experience during the exploratory phase of the fishery (Figure \ref{S-fig:14}).
+experience during the exploratory phase of the fishery (Figure \ref{fig:mv} (C)).
 This results from the randomness in the correlated random walk step function,
@@
 stochastically related to the revenue experienced on the fishing ground (Figure
-\ref{S-fig:15}).
+\ref{fig:mv} (D)).
 
@@
 
-Figure \ref{fig:1} shows the aggregated catch composition from each of the data
-sources over a ten-year period (to average seasonal patterns) at different
-spatial resolutions. The finer spatial grid for the real population (top left)
-and commercial data (top middle) show visually similar patterns, though there
-are large unsampled areas in the commercial data from a lack of fishing
-activity (particularly in the lower left part of the sampling domain). The
-survey data at this spatial resolution displays very sparse information about
-the spatial distributions of the populations. The slightly aggregated data on a
-5 x 5 grid shows similar patterns and, while losing some of the spatial detail,
-there remains good consistency between the real population and the commercial
-data. Survey data starts to pick out some of the similar patterns as the other
-data sources, but lacks spatiotemporal coverage. The spatial catch information
-on a 10 x 10 and 20 x 20 grid lose a significant amount of information about
-the spatial resolutions for all data sources, and some differences between the
-survey, commercial and real population data emerge. \\
-
-Figure \ref{fig:2} shows the consequences of different temporal aggregations of
-the data over a ten-year period, with weekly (top), monthly (middle) and yearly
-(bottom) catch compositions from across an aggregated 20 x 20 area. In the real
-population, the monthly aggregation captures the major patterns of composition
-seen in the weekly data with the percentage of different species in the catch
-having similar mean and standard deviations.  In the weekly data species 1 =
-9.36 (3.99), species 2 = 83.2 (5.60), species 3 = 3.57 (1.23), species 4 = 3.91
-(1.59); in the monthly data species 1 = 9.23 (3.87), species 2 = 83.3 (5.52),
-species 3 = 3.62 (1.15), species 4 = 3.86 (1.52). While means were similar some
-of the variation was lost when aggregated to an annual level; species 1 = 9.90
-(0.173), species 2 = 82.2 (0.308), species 3 = 3.82 (0.119), species 4 = 4.03
-(0.0502).\\
+The aggregated catch composition from each of the data sources over a ten-year
+period (which shows average seasonal patterns) at different spatial resolutions
+highlights different patterns in perceived community structure depending on the
+data source and aggregation level (Figure \ref{fig:1}). The finer spatial grid
+for the real population (top left) and commercial data (top middle) show
+visually similar patterns, though there are large unsampled areas in the
+commercial data from a lack of fishing activity (particularly in the lower left
+part of the sampling domain). The survey data at this spatial resolution
+displays very sparse information about the spatial distributions of the
+populations. The slightly aggregated data on a 5 x 5 grid shows similar
+patterns and, while losing some of the spatial detail, there remains good
+consistency between the real population and the commercial data. Survey data
+starts to pick out some of the similar patterns as the other data sources, but
+lacks spatiotemporal coverage. The spatial catch information on a 10 x 10 and
+20 x 20 grid lose a significant amount of information about the spatial
+resolutions for all data sources, and some differences between the survey,
+commercial and real population data emerge. \\
+
+Different perceptions of the proportion of each stock in an area are seen when
+we aggregate the data over a smaller geographical region at different
+timescales, with weekly (top), monthly (middle) and yearly (bottom) catch
+compositions from across an aggregated 20 x 20 area (Figure \ref{fig:2}). In
+the real population, the monthly aggregation captures the major patterns of
+composition seen in the weekly data with the percentage of different species in
+the catch having similar mean and standard deviations.  In the weekly data
+species 1 = 9.36 (3.99), species 2 = 83.2 (5.60), species 3 = 3.57 (1.23),
+species 4 = 3.91 (1.59); in the monthly data species 1 = 9.23 (3.87), species 2
+= 83.3 (5.52), species 3 = 3.62 (1.15), species 4 = 3.86 (1.52). While means
+were similar some of the variation was lost when aggregated to an annual level;
+species 1 = 9.90 (0.173), species 2 = 82.2 (0.308), species 3 = 3.82 (0.119),
+species 4 = 4.03 (0.0502).\\
 
@@
 \begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{Plots/Combined_Movement}
+	\caption{(A) The fishing locations (points) and movements (lines) of a
+	single vessel during a trip overlaid on the relative value of a fishing
+	site; (B) the fishing locations of the vessel over several trips (value
+field changes over the period so not shown); (C) the locations of multiple
+vessels from the same fleet overlaid on the value field, (D) the realised step
+distance and turning angles for a single vessel over the simulation}
+	\label{fig:mv}
+\end{figure}
+
+\begin{figure}[!ht]
 	\includegraphics[width = \linewidth]{Plots/vessel_move_value}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_space_Rev}
+	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_space_Rev2}
 	\caption{Data aggregation at different spatial resolutions over a
@@
 \begin{figure}[!ht]
-	\includegraphics[width =\linewidth]{../analysis/Data_Aggregation_time_Rev}
+	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_time_Rev2}
 	\caption{Data aggregation at different temporal resolutions over a

### 2019-09-16 R/plot_fleet_trip.R

@@ -10,17 +10,62 @@
 #' @param trip_no is a Numeric for the trip you wish to plot
 
 #' @examples
-#' plot_fleet_trip(logs = logs, fleet_no = 1, year_trip = 1, trip_no = 1)
+#' plot_fleet_trip(logs = logs, fleet_no = 1, year_trip = 1, trip_no = 1,
+#' pop_bios = NULL, fleets_init = NULL)
 
 #' @export
 
-plot_fleet_trip <- function (logs = logs, fleet_no = 1, year_trip = 1, trip_no = 1) {
+plot_fleet_trip <- function (logs = logs, fleet_no = 1, year_trip = 1, trip_no = 1,
+			 pop_bios = NULL, fleets_init = NULL, sim_init = NULL) {
 
 require(ggplot2)
 require(dplyr)
 
 log <- filter(as.data.frame(logs), fleet %in% fleet_no, year %in% year_trip, trip %in% trip_no)
 
-print(ggplot(log, aes(x = x, y = y)) + geom_point(aes(colour = factor(vessel))) + geom_path(aes(colour = factor(vessel))))
+log$vessel <-as.factor(log$vessel)
+
+if(is.null(pop_bios)) {
+print(ggplot(log, aes(x = x, y = y)) + 
+      geom_point(aes(colour = vessel)) +
+      geom_path(aes(colour = vessel)) + 
+      theme_bw()) 
+}
+
+
+if(!is.null(pop_bios)) {
+
+## Extract pop biomasses
+Bs <- pop_bios[[year_trip, trip_no]]
+
+## Create value field for fleet
+
+Value <- lapply(names(Bs), function(x) {
+		     fleets_init[["fleet_params"]][[fleet_no]][["VPT"]][[x]] * 
+			     fleets_init[["fleet_params"]][[fleet_no]][["Qs"]][[x]] *
+			     Bs[[x]]
+		     })
+
+TotVal <- Reduce("+", Value)
+
+TotValDF <- tidyr::gather(as.data.frame(TotVal), factor_key = TRUE)
+TotValDF$x <- rep(seq_len(sim_init[["idx"]][["nrows"]]), times = sim_init[["idx"]][["nrows"]])
+TotValDF$y <- rep(seq_len(sim_init[["idx"]][["ncols"]]), each = sim_init[["idx"]][["ncols"]])
+
+
+print(ggplot(TotValDF, aes(x = x, y = y)) + geom_tile(aes(fill = value)) +
[…]

### 2019-09-16 R/plot_realised_stepF.R

@@ -21,8 +21,8 @@ plot_realised_stepF <- function(logs = logs, fleet_no = 1, vessel_no = 1) {
 	plot(stepDF[["val"]][1:c(nrow(stepDF)-1)], stepDF[["stepD"]][2:nrow(stepDF)], main = "Realised step distances", xlab = "value", ylab = "step distance")
 
 
-	plot(stepDF[["val"]][1:c(nrow(stepDF)-1)],
+	return(print(plot(stepDF[["val"]][1:c(nrow(stepDF)-1)],
      stepDF[["angles"]][1:c(nrow(stepDF)-1)]- 
      stepDF[["angles"]][2:nrow(stepDF)], main = "Relalised turning angles", xlab = "value", ylab = "change in angle")
-
+))
 }

### 2019-09-16 R/plot_vessel_move.R

@@ -27,10 +27,16 @@ require(dplyr)
 
 log <- filter(as.data.frame(logs), fleet %in% fleet_no, vessel %in% vessel_no, year %in% year_trip, trip %in% trip_no)
 
+log$trip <- as.factor(log$trip)
 
 if(is.null(fleets_init) | is.null(pop_bios)) {
 
-print(ggplot(log, aes(x = x, y = y, group = paste(vessel, trip))) + geom_point(aes(colour = tow)) + geom_path(aes(colour = tow))+ expand_limits(y = c(0,sim_init[["idx"]][["ncols"]]), x = c(0,sim_init[["idx"]][["nrows"]])))
+return(print(ggplot(log, aes(x = x, y = y, group = paste(vessel, trip))) +
+      geom_point(aes(colour = trip)) +
+      geom_path(aes(colour = trip))+ theme_bw() +
+      expand_limits(y = c(0,sim_init[["idx"]][["ncols"]]), 
+		    x = c(0,sim_init[["idx"]][["nrows"]])) + 
+	     theme(legend.position = "none")))
 
 }
 
@@ -42,7 +48,8 @@ Bs <- pop_bios[[year_trip, trip_no]]
 ## Create value field for fleet
 
 Value <- lapply(names(Bs), function(x) {
-		     fleets_init[["fleet_params"]][[fleet_no]][["VPT"]][[x]] * fleets_init[["fleet_params"]][[fleet_no]][["Qs"]][[x]] *
+		     fleets_init[["fleet_params"]][[fleet_no]][["VPT"]][[x]] * 
+			     fleets_init[["fleet_params"]][[fleet_no]][["Qs"]][[x]] *
 			     Bs[[x]]
 		     })
 
@@ -52,8 +59,15 @@ TotValDF <- tidyr::gather(as.data.frame(TotVal), factor_key = TRUE)
 TotValDF$x <- rep(seq_len(sim_init[["idx"]][["nrows"]]), times = sim_init[["idx"]][["nrows"]])
 TotValDF$y <- rep(seq_len(sim_init[["idx"]][["ncols"]]), each = sim_init[["idx"]][["ncols"]])
 
-print(ggplot(TotValDF, aes(x = x, y = y)) + geom_tile(aes(fill = value)) +
[…]

### 2019-09-16 analysis/KillerFigure.R

@@ -152,12 +152,14 @@ catch_hans <- make.xyz(x = catch_hans$grid_x,y = catch_hans$grid_y,z = catch_han
 
 catch_comp <- list(catch_hans = catch_hans, catch_grid = catch_grid)
 
-cols <- c("red", "blue", "purple", "green")
+#cols <- c("red", "blue", "purple", "green")
+cols <- c("#E66101", "#FDB863", "#B2ABD2", "#5E3C99") 
 
 #par(mar = c(0,0,0,0), pty = 'm')
 basemap(xlim = c(0,100), ylim = c(0,100), xlab = "", ylab = "", bg = "white", xaxt = 'n', yaxt = "n")
 draw.barplot2D(catch_comp[[1]]$x,catch_comp[[1]]$y,z = catch_comp[[1]]$z, width = gran,
-	       height = gran, xlab = "", ylab = "", col = cols, lwd.frame = 0, col.frame = "white")
+	       height = gran, xlab = "", ylab = "", col = cols, lwd.frame = 0, 
+	       col.frame = "white", border = NA)
 
 
 }
@@ -177,7 +179,7 @@ load(file.path('.', 'Common_Params.RData'))
 
 ## Commercial
 dataIn <- get_data(basis = 'commercial', yr = yr, mn = mn, wk = wk, dataIn = res[["fleets_catches"]]) 
-plot_comp(gran = 1, dataIn = dataIn)
+plot_comp(gran = 20, dataIn = dataIn)
 
 ## Survey
 dataIn <- get_data(basis = 'survey', yr = yr, mn = mn, wk = wk, dataIn = res[["survey"]][["log.mat"]]) 
@@ -192,7 +194,7 @@ plot_comp(gran = 1, dataIn = dataIn)
 ## Setting out the plot
 ##setEPS()
 ##postscript('Data_Aggregation_space.eps', width = 8 * 2, height = 8 * 3, bg = "white")
-pdf('Data_Aggregation_space_Rev.pdf', width = 8 * 2, height = 8 * 3, bg = "white")
+pdf('Data_Aggregation_space_Rev2.pdf', width = 8 * 2, height = 8 * 3, bg = "white")
 
 par(oma = c(12,2,12,12), mar = c(0,0,0,0), mfrow = c(4,3))
 
@@ -229,7 +231,7 @@ mtext(text = "Real Population        Commercial Data     Survey Data", side = 3,
[…]

### 2019-09-16 analysis/Plots.R

@@ -51,8 +51,9 @@ ggsave(file = file.path('..', 'write_up', 'Plots', 'f_dynamics.png'), width = 8,
 
 logs <- combine_logs(res[["fleets_catches"]])
 
-plot_vessel_move(sim_init = sim, logs = logs, fleet_no = 3, vessel_no = 14,
-       year_trip = 30, trip_no = 1)
+plot_vessel_move(sim_init = sim, logs = logs, fleet_no = 3, fleets_init = fleets, 
+		 vessel_no = 14,
+       year_trip = 30, trip_no = 1, pop_bios = res[["pop_bios"]])
 ggsave(file = file.path("..", "write_up", "Plots", "vessel_move.png"), width = 8, height = 8)
 
 
@@ -77,4 +78,64 @@ plot_realised_stepF(logs = logs, fleet_no = 3, vessel_no = 2)
 dev.off()
 
 
+### New panel plot combing for manuscript
+logs <- combine_logs(res[["fleets_catches"]])
+
+
+source("../R/plot_vessel_move.R")
+
+p1 <- plot_vessel_move(sim_init = sim, logs = logs, fleet_no = 3, fleets_init = fleets, 
+		 vessel_no = 14,  year_trip = 30, trip_no = 1, pop_bios = res[["pop_bios"]])
+
+p2 <- plot_vessel_move(logs = logs, fleet_no = 3, vessel_no = 4, year_trip = 30, trip_no =  1:12)
+
+source("../R/plot_fleet_trip.R")
+
+
+p3 <- plot_fleet_trip(logs = logs, fleet_no = 3, year_trip = 30, trip_no = 2,
+		      fleets_init = fleets, pop_bios = res[["pop_bios"]], 
+		      sim_init = sim)
+
+## Recreate step function plots in ggplot
+
+stepDF <- dplyr::filter(as.data.frame(logs), fleet == 3, vessel == 2)
+
+## Lag the data
+	stepDF$val_lagged    <- c(stepDF$val[1:nrow(stepDF)-1],NA)
+	stepDF$step_lagged   <- c(stepDF$stepD[2:nrow(stepDF)],NA)
+	stepDF$angles_lagged <- c(stepDF$angles[2:nrow(stepDF)],NA)
+
+	plot(stepDF$val_lagged, stepDF$step_lagged, main = "Realised step distances", xlab = "value", ylab = "step distance")
[…]

### 2019-09-16 write_up/mixfishsim_ecolmod.tex
JJP comments

@@
 measures is hampered by a lack of knowledge of fish and fishery spatiotemporal
-dynamics and understanding of the scale at which processes become important for
-management. \\
-
-Understanding the correct scale for spatial measures is also crucial as it
-enables implementation of effective solutions which minimise economic impact
-\citep{Dunn2016}. For example, the problem can be to identify a scale that
-promotes species avoidance for vulnerable or low quota species while allowing
-continuance of sustainable fisheries for available quota species. Identifying
-the correct spatial scale remains a challenge because data on fish location at
-high temporal and spatial resolutions is expensive and difficult to collect and
-proxies are usually inferred from scientific surveys or commercial catches with
-limited spatial and temporal resolution. \\
+dynamics and understanding of the scale at which these processes become
+important for management. \\
+
+Understanding the correct scale for spatial management measures to be effective
+is also crucial as it enables implementation of effective solutions which
+minimise economic impact \citep{Dunn2016}. For example, the problem can be to
+identify a scale that promotes species avoidance for vulnerable or low quota
+species while allowing continuance of sustainable fisheries for available quota
+species. Identifying the correct spatial scale remains a challenge because data
+on fish location at high temporal and spatial resolutions is expensive and
+difficult to collect and proxies are usually inferred from scientific surveys
+or commercial catches with limited spatial and temporal resolution. \\
 
@@
 highlighted as crucial to their success \citep{Costello2010, Dunn2016}.
-Inference is hampered where spatial information is coarse due to low resolution
-reporting of fisheries catch which is aggregated across larger gridded areas
-\citep{Branch2005}. Further, if data does not allow identification of spatial
-features it may lead to poorly sited closures which are ineffectual or have
-unintended consequences. For example, increased benthic impact on previously
-unexploited areas from the cod closure in the North Sea were observed without
-the intended effect of reducing cod exploitation
-\citep{Rijnsdorp2001,Dinmore2003}).\\
+Inference on fisheries spatial dynamics is hampered where spatial information
+is coarse due to low resolution reporting of fisheries catch which is
+aggregated across larger gridded areas \citep{Branch2005}. Further, if data
+does not allow identification of spatial features it may lead to poorly sited
+closures which are ineffectual or have unintended consequences. For example,
+increased benthic impact on previously unexploited areas from the cod closure
+in the North Sea were observed without the intended effect of reducing cod
+exploitation \citep{Rijnsdorp2001,Dinmore2003}).\\
 
@@
 establish favoured fishing grounds through an explore-exploit strategy
-\citep{Bailey2018} where they search for areas with high catches and then use
-experience to return to areas where they've experienced high catch in the past.
-This leads to an inherently biased sampling where target species are
-over-represented in the catch as fishers exploit areas of high abundance. \\
+\citep{Rijnsdorp2011, Bailey2018} where they search for areas with high catches
+and then use experience to return to areas where they've experienced high catch
+in the past.  This leads to an inherently biased sampling where target species
+are over-represented in the catch as fishers exploit areas of high abundance.
+\\
 
 To understand the effect of spatiotemporal aggregation of data and fishery
-targeting we ask two fundamental questions regarding inference derived from
-observational data:
+targeting on our understanding of fish communities we ask two fundamental
+questions regarding inference derived from observational data:
 
 \begin{enumerate}
-	\item How does sampling-derived fisheries data reflects the underlying
-		community structure? 	
-	\item How does data aggregation and source impact on spatial fisheries
-	management measures?
+	\item Do different source of sampling-derived fisheries data
+		reflects the underlying community structure or represent a
+		biased picture? 	
+	\item How does data aggregation and data source impact on the success
+		of spatial fisheries management measures?
 \end{enumerate}
@@
 To answer these questions we i) develop a simulation model where population
-dynamics are highly-resolved in space and time by use of a Gaussian spatial
-process to define suitable habitat for different populations.  Precise
-locations of the fish being known directly rather than inferred from sampling
+dynamics are highly-resolved in space and time, using a Gaussian spatial
+process to define suitable habitat for different populations. As the precise
+locations of the fish are known directly rather than inferred from sampling
 or commercial catch, we can use the population model to validate how inference
@@
 represents the proportion of fish recruited during that day for the year, while
-$R_{c,\tilde{y}}$ is the annual recruits in cell $c$ for year $y$. \\
+$R_{\tilde{y},c}$ is the annual recruits in year $y$ for cell $c$. \\
 
@@
 
-Recruitment is modelled through a function relating to adult biomass. In
-\textit{MixFishSim}, it can be either as a stochastic Beverton-Holt stock-recruit
-form \citep{Beverton1957}: 
+Recruitment is modelled as a function of adult biomass. In
+\textit{MixFishSim}, it can either take the form of a stochastic Beverton-Holt
+stock recruitment relationship, or a stochastic Ricker stock recruitment
+relationship. The Beverton-Holt relationship is defined as\citep{Beverton1957}: 
 \begin{equation}
@@
 stock size and $\sigma^2$ the variability in the recruitment due to stochastic
-processes, or a stochastic Ricker form \citep{Ricker1954}:
+processes, the stochastic Ricker form \citep{Ricker1954}:
 \begin{equation}
@@
 
-Population movement is a combination of random (diffusive) movement, governed
-by a stochastic process where movement between adjacent cells is described by a
-set of probabilities, and directed (advective) movement where at certain times
-of year the population moves towards spawning grounds by increasing the
-probabilities of moving into the spawning grounds from adjacent cells. We
-characterise a set of different fishing fleet dynamics exploiting four fish
-populations with different spatial and population demographics. \\
+Population movement is a combination of directed (advective) movement where at
+certain times of year the population moves towards spawning grounds by
+increasing the probabilities of moving into the spawning grounds from adjacent
+cells, and random (diffusive) movement, governed by a stochastic process where
+movement between adjacent cells is described by a set of probabilities.\\
 
@@
 animal populations where density is more similar in nearby locations
-\citep{Tobler1970, F.Dormann2007} and we change the parameters to implement
-different spatial structures for the different populations using the
+\citep{Tobler1970, F.Dormann2007, Poos2007} and we change the parameters to
+implement different spatial structures for the different populations using the
 \textit{RandomFields} R package \citep{Schlater2015}. We define a stationary
-habitat field and combine with a temporally dynamic thermal tolerance field to
+habitat field and combine it with a temporally dynamic thermal tolerance field to
 imitate two key drivers of population dynamics. Each population was initialised
-at a single location, and subsequently moved according to a probabilistic
-distribution based on habitat suitability (represented by the normalised values
+at a single location, and subsequently moved across the entire space according
+to a probabilistic distribution based on habitat suitability (represented by
+the normalised values
 from the GRFs), temperature and distance from current cell: 
 \begin{equation}
-	Pr(C_{wk+1} = J | C_{wk} =I) = \frac{\mathrm{e}^{-\lambda * d_{IJ}} \cdot
+	Pr(C_{wk+1} = J | C_{wk} =I) = \frac{\mathrm{e}^{-\lambda \cdot d_{IJ}} \cdot
 		(Hab_{J,p}^2 \cdot
-		Tol_{J,p,wk})}{\sum\limits_{c=1}^{C}\mathrm{e}^{-\lambda * d} \cdot
+		Tol_{J,p,wk})}{\sum\limits_{c=1}^{C}\mathrm{e}^{-\lambda \cdot d} \cdot
 		(Hab_{c,p}^2 \cdot Tol_{c,p,wk})}
@@
 user-defined spawning habitat locations, resulting in each population having
-concentrated areas where spawning takes place. In the simulations the
-populations move towards these cells in the weeks prior to spawning, resulting
-in directional movement towards the spawning grounds. \\
-
-An advection-diffusion process controls population movement, with a
-time-varying temperature covariate used to change the interaction between time
-and suitable habitat on a weekly time-step. Each population $p$ was assigned a
-thermal tolerance with mean, $\mu_{p}$ and variance, $\sigma^2_{p}$ so that
-each cell and population temperature suitability is defined that:
+concentrated areas where spawning takes place. The populations then move towards
+these cells in the weeks prior to spawning, resulting in directional movement
+towards the spawning grounds. \\
+
+A time-varying temperature covariate changes the interaction between
+time and suitable habitat on a weekly time-step. Each population $p$ was
+assigned a thermal tolerance with mean, $\mu_{p}$ and variance, $\sigma^2_{p}$
+so that each cell and population temperature suitability is defined that:
 \begin{equation}
@@
 to be fished at the beginning of a trip; and within-trip decisions, that
-determines movement from one fishing spot to another within a trip. Together,
-these elements implement an explore-exploit type strategy for individual
-vessels to maximise their catch from an unknown resource distribution
-\citep{Bailey2018}. The decision to use an individual based model for fishing
-vessels was taken because fishers are heterogeneous in their location choice
-behaviour due to different objectives, risk preference and targeting preference
-\citep{VanPutten2012a}. Therefore in the simulations fleet dynamics reflect
-individual experiences rather than pre-defined group dynamics.
+determines movement from one fishing spot to another within a trip. An
+explore-exploit type strategy was implemented in the model that combined these
+three components for individual vessels to maximise their catch from an unknown
+resource distribution \citep{Bailey2018}. The decision to use an individual
+based model for fishing vessels was taken because fishers are heterogeneous in
+their location choice behaviour due to different objectives, risk preference
+and targeting preference \citep{VanPutten2012a}. Therefore in the simulations
+fleet dynamics reflect individual experiences rather than pre-defined group
+dynamics.
 
@@
 Each fleet of \textit{n} vessels was characterised by both a general
-efficiency, $Q_{fl}$, and a population specific efficiency, ${Q_{fl, p}}$.
-Thus, the product of these parameters [$Q_{fl} \cdot Q_{fl, p}$] affects the
-overall catch rates for the fleet and the preferential targeting of one
-population over another. This, in combination with the parameter choice for the
-step-function defined below (as well as some randomness from the exploratory
-fishing process) determined the preference of fishing locations for the fleet.
-
-\subsubsection{Trip-level decisions}
-
-Several studies \citep[e.g.][]{Hutton2004, Tidd2012, Girardin2015} have
-confirmed past activity and past catch rates are strong predictors of fishing
-location choice. For this reason, the fleet dynamics sub-model included a
-learning component, where a vessel's initial fishing location in a trip was
-based on selecting from previously successful fishing locations. This was
-achieved by calculating an expected revenue based on the catches from locations
-fished in the preceding trip as well as the same month periods in previous
-years and the travel costs from the port to the fishing grounds, and choosing
-randomly from the top 75 \% of fishing events as defined by the expected
-profit, that has a seasonal component.
-
-\subsubsection{Within-trip decisions}
+efficiency, $Q_{fl}$, and a population specific efficiency, ${Q_{fl, p}}$ which
+are each bound by [0,1]. The product of these parameters [$Q_{fl} \cdot
+Q_{fl, p}$] affects the overall catch rates for the fleet and the preferential
+targeting of one population over another. This, in combination with the
+parameter choice for the step-function defined below (as well as some
+randomness from the exploratory fishing process) determined the preference of
+fishing locations for the fleet.
+
+\subsubsection{Decision about where to fish at the start of the trip}
+
+Several studies \citep[for a review]{Girardin2016} have confirmed past activity
+and past catch rates are strong predictors of fishing location choice. For this
+reason, the fleet dynamics sub-model included a learning component, where a
+vessel's initial fishing location in a trip was based on selecting from
+previously successful fishing locations. This was achieved by calculating an
+expected revenue based on the catches from locations fished in the preceding
+trip as well as the same month periods in previous years and the travel costs
+from the port to the fishing grounds. Then a vessel chooses randomly from the
+top 75 \% of fishing events as defined by the expected profit, that has a
+seasonal component.
+
+\subsubsection{Decision about where to fish within the trip}
 
@@
 
-With increasing probability throughout the simulation, fishing locations were
-chosen based on experience of profitable catches built up in the same month
-from previous years and from the previous trip. 'Profitable' in this context
-was defined as the locations where the top 70 \% of expected profit would be
-found given revenue from previous trips and cost of movement to the new fishing
-location. This probability was based on a logistic sigmoid function with a
-lower asymptote of 0 and upper asymptote of 0.95, and a growth rate that
-ensures the upper asymptote (where decisions are mainly based on past
+Fishing locations were chosen based on random search and, with increasing
+proportion as time progressed, experience of profitable catches built up in the
+same month from previous years and from the previous trip.  'Profitable' in
+this context was defined as the locations where the top 70 \% of expected
+profit would be found given revenue from previous trips and cost of movement to
+the new fishing location. This probability was based on a logistic sigmoid
+function with a lower asymptote of 0 and upper asymptote of 0.95, and a growth
+rate that ensures the upper asymptote (where decisions are mainly based on past
 knowledge) is reached approximately halfway through the simulation.  \\
@@
 spatial habitat use for each population (Figure \ref{fig:9}) and consequently
-different seasonal exploitation patterns (Fishing mortality in Figure
-\ref{fig:10}).
+different seasonal exploitation patterns (Figure \ref{fig:10}).
 
@@
 fleets exploiting multiple fish populations and realising catch distributions
-that may differ from the underlying populations. As such, we favoured a minimum
-realistic model of the fish populations \citep{Plaganyi2014} taking account of
-environmental but not demographic stochasticity, while incorporating detailed
-fishing dynamics that take account of different drivers in a mechanistic way.
-\\
+that may differ from the underlying populations [[\citep{Gillis2008}]]. As
+such, we favoured a minimum realistic model of the fish populations
+\citep{Plaganyi2014} taking account of environmental but not demographic
+stochasticity, while incorporating detailed fishing dynamics that take account
+of different drivers in a mechanistic way.  \\
 

### 2019-09-17 write_up/mixfishsim_ecolmod.tex
Text tweaks

@@
 As fishers do not have full control over what species they select in `mixed
-fisheries' this can result in catch of low quota or protected species. This
-leads to discarding of over-quota catch if it is a species for which they have
-no quota, limiting control over fishing mortality \citep{Alverson1994,
+fisheries' this can result in catch of low quota or protected species. If
+fishers discard over-quota catch of a species for which they have no quota, it
+limits our ability to control fishing mortality \citep{Alverson1994,
 	Crowder1998, Rijnsdorp2007} and the ability to manage fisheries for the
@@
 to reduce unwanted catch through spatial avoidance, an in-depth understanding
-of spatiotemporal fishery dynamics is required. Implementation of spatial
-measures is hampered by a lack of knowledge of fish and fishery spatiotemporal
-dynamics and understanding of the scale at which these processes become
-important for management. \\
+of spatiotemporal fishery dynamics is required. \\
 
 Understanding the correct scale for spatial management measures to be effective
-is also crucial as it enables implementation of effective solutions which
-minimise economic impact \citep{Dunn2016}. For example, the problem can be to
-identify a scale that promotes species avoidance for vulnerable or low quota
-species while allowing continuance of sustainable fisheries for available quota
-species. Identifying the correct spatial scale remains a challenge because data
-on fish location at high temporal and spatial resolutions is expensive and
-difficult to collect and proxies are usually inferred from scientific surveys
-or commercial catches with limited spatial and temporal resolution. \\
+is crucial as it enables implementation of effective solutions which minimise
+economic impact \citep{Dunn2016}. For example, the problem can be to identify a
+scale that promotes species avoidance for vulnerable or low quota species while
+allowing continuance of sustainable fisheries for available quota species.
+Identifying the correct spatial scale remains a challenge because data on fish
+location at high temporal and spatial resolutions is expensive and difficult to
+collect and proxies are usually inferred from scientific surveys or commercial
+catches with limited spatial and temporal resolution. Thus, implementation of
+spatial measures is hampered by a lack of knowledge of fish and fishery
+spatiotemporal dynamics and understanding of the scale at which these processes
+become important for management. \\ \\
 
@@
 are over-represented in the catch as fishers exploit areas of high abundance.
-\\
+There is a need to understand the influence of these biases on any spatial
+management measures which are implemented based on inference from commercial
+landings or catch data. \\
 
 To understand the effect of spatiotemporal aggregation of data and fishery
-targeting on our understanding of fish communities we ask two fundamental
-questions regarding inference derived from observational data:
+targeting on our perception of spatial abundance of different fish populations
+we ask two fundamental questions regarding inference derived from observational
+data:
 
@@
 	\item Do different source of sampling-derived fisheries data
-		reflects the underlying community structure or represent a
-		biased picture? 	
+		reflects the underlying community structure? 	
 	\item How does data aggregation and data source impact on the success

### 2019-09-17 write_up/mixfishsim_ecolmod.tex
JJP comments

@@
 	Pakefield Road, Lowestoft, UK}
-\address[3]{\replaced[id=JM]{Sorbonne Université, Faculty of
-		Sciences}{Université Pierre et Marie Curie}, 4 Place Jussieu,
-	75005 Paris, France}
+\address[3]{Sorbonne Université, Faculty of Sciences, 4 Place Jussieu, 75005
+	Paris, France}
 \address[4]{Wageningen Marine Research, Haringkade 1 1976 CP IJmuiden,
@@
 To understand how data resolution impacts inference on mixed fisheries
-interactions, we developed a highly resolved spatiotemporal
-event-based simulation model incorporating: i) delay-difference
-population dynamics, ii) population movement using Gaussian Random Fields to
-simulate patchy, heterogeneously distributed populations, and iii) fishery
-dynamics for multiple fleet characteristics based on species targeting under an
-explore-exploit strategy. This is implemented via a mix of correlated random
-walk movement (for exploration) and learned behaviour (for exploitation) phases
-of the fisheries.  \\ 
+interactions, we developed a highly resolved spatiotemporal discrete-event
+simulation model incorporating: i) delay-difference population dynamics, ii)
+population movement using Gaussian Random Fields to simulate patchy,
+heterogeneously distributed populations, and iii) fishery dynamics for multiple
+fleet characteristics based on species targeting under an explore-exploit
+strategy. This is implemented via a mix of correlated random walk movement (for
+exploration) and learned behaviour (for exploitation) phases of the fisheries.
+\\ 
 %%
@@
 
-An event-based simulation model of a hypothetical fishery was developed as a
-software package (\textit{MixFishSim}). The modular approach enabled efficient
-computation by allowing for sub-modules implemented on time-scales appropriate
-to capture the characteristic of the different processes (Figure 1). The
-following sub-modules were included to capture the full system: 1) Population
-dynamics, 2) Recruitment dynamics, 3) Population movement, 4) fishery
-dynamics.\\
+A Discrete-event simulation (DES) model of a hypothetical fishery was developed
+as a software package (\textit{MixFishSim}). The modular approach enabled
+efficient computation by allowing for sub-modules implemented on time-scales
+appropriate to capture the characteristic of the different processes (Figure
+1). The following sub-modules were included to capture the full system: 1)
+Population dynamics, 2) Recruitment dynamics, 3) Population movement, 4)
+fishery dynamics.\\
 
@@
 represents the proportion of fish recruited during that day for the year, while
-$R_{\tilde{y},c}$ is the annual recruits in year $y$ for cell $c$. \\
+$R_{c,\tilde{y},d}$ is the annual recruits in year $y$ and day $d$ for cell
+$c$. \\
 
@@
 and vessels in cell $c$ for the population during the day $d$, and $B_{c,d}$
-the daily biomass for the population in the cell. Here, catch and fishing
-mortality are the sum of those across all fleets and vessels, where $F_{fl, v,
-	c, d, p} = E_{fl, v, c, d} \cdot Q_{fl, p} \cdot D_{c, d, p}$ with
-$fl$, $v$ and $p$ the fleet, vessel and population respectively and $E$ and $Q$
-fishing effort and catchability of the gear, and $D$ is the density of the
-population at the location fished. \\
+the daily biomass for the population in the cell. Here, catch is the sum of
+those across all fleets and vessels, $C_{c, d} =
+\sum\limits_{fl=1}^{fl}\sum\limits_{v=1}^{v} E_{fl, v, c, d} \cdot Q_{fl} \cdot
+D_{c, d}$ with $fl$ and $v$ the fleet and vessel respectively and
+$E_{fl,v,c,d}$ and $Q_{fl}$ fishing effort and catchability of the gear, and
+$D_{c,d}$ is the density of the population at the location fished. \\
 
@@
 \begin{equation}
-	Pr(C_{wk+1} = J | C_{wk} =I) = \frac{\mathrm{e}^{-\lambda \cdot d_{IJ}} \cdot
+	Pr(C_{wk+1} = J | C_{wk} =I) = \frac{\mathrm{e}^{-\lambda \cdot d_{I,J}} \cdot
 		(Hab_{J,p}^2 \cdot
@@
 \end{equation}
-Where $d_{IJ}$ is the euclidean distance between cell $I$ and cell $J$,
-$\lambda$ is a given rate of decay, $Hab_{J,p}^2$ is the squared index of
-habitat suitability for cell $J$ and population $p$, with $Tol_{J,p,wk}$ the
-temperature tolerance for cell $J$ by population $p$ in week $wk$ (see
+Where $d_{I,J}$ is the euclidean distance between cell $I$ and cell $J$,
+$\lambda$ is a given rate of decay, $Hab_{c,p}^2$ is the squared index of
+habitat suitability for cell $c$ and population $p$, with $Tol_{c,p,wk}$ the
+temperature tolerance for cell $c$ by population $p$ in week $wk$ (see
 below). \\
@@
 user-defined spawning habitat locations, resulting in each population having
-concentrated areas where spawning takes place. The populations then move towards
-these cells in the weeks prior to spawning, resulting in directional movement
-towards the spawning grounds. \\
-
-A time-varying temperature covariate changes the interaction between
-time and suitable habitat on a weekly time-step. Each population $p$ was
-assigned a thermal tolerance with mean, $\mu_{p}$ and variance, $\sigma^2_{p}$
-so that each cell and population temperature suitability is defined that:
+concentrated areas where spawning takes place. The populations then move
+towards these cells in the weeks prior to spawning, resulting in directional
+movement towards the spawning grounds. \\
+
+A time-varying temperature covariate changes the interaction between time and
+suitable habitat on a weekly time-step. Each population $p$ was assigned a
+thermal tolerance with mean, $\mu_{p}$ and variance, $\sigma^2_{p}$ so that
+each cell and population temperature suitability is defined that:
 \begin{equation}
 	Tol_{c, p, wk} = \frac{1}{ \sqrt (2\pi \cdot \sigma^2_{p})} \cdot \exp(-
-		\frac{(T_{c\added[id=PD]{, wk}} - \mu_{p})^2}{2 \cdot \sigma^2_{p}} )	
+		\frac{(T_{c, wk} - \mu_{p})^2}{2 \cdot \sigma^2_{p}} )	
 \end{equation}
@@
 their location choice behaviour due to different objectives, risk preference
-and targeting preference \citep{VanPutten2012a}. Therefore in the simulations
-fleet dynamics reflect individual experiences rather than pre-defined group
+and targeting preference \citep{VanPutten2012a, Boonstra2015}. Therefore fleet
+dynamics are emergent from individual dynamics rather than pre-defined group
 dynamics.
@@
 \begin{equation}
-Rev = \sum_{p=1}^{P} \replaced[id=PD]{L}{C}_{p} \cdot Pr_{p} 
+Rev_{c,d} = \sum_{p=1}^{P} L_{c,d,p} \cdot Pr_{p} 
 \end{equation}
-where $L_{p}$ is landings of a population $p$, and $Pr_{p}$ price of a
+where $L_{c,d,p}$ is landings of a population $p$, and $Pr_{p}$ price of a
 population. All species prices were kept the same across fleets and seasons.
@@
 \begin{equation}
-	StepL = \mathrm{e}^{log(\beta_{1}) + log(\beta_{2}) -
-		\left(log\left(\frac{\beta_{1}}{\beta_{3}}\right)\right)} \cdot Rev
+	Le = \mathrm{e}^{log(\beta_{1}) + log(\beta_{2}) -
+		\left(log\left(\frac{\beta_{1}}{\beta_{3}}\right)\right) \cdot Rev
+} 
 \end{equation}
@@
 	\begin{split}
- (x2, y2) =  & x1 + L \cdot \cos \left(\frac{\pi \cdot Br}{180}\right), \\
-             & y1 + L \cdot \sin \left(\frac{\pi \cdot Br}{180}\right) \\	
+ (x2, y2) =  & x1 + Le \cdot \cos \left(\frac{\pi \cdot Br}{180}\right), \\
+             & y1 + Le \cdot \sin \left(\frac{\pi \cdot Br}{180}\right) \\	
  with  \hspace{0.5cm}     & Br_{t-1} < 180, Br_{t} = 180 + \sim vm[(0,360), k] \\
@@
 \end{equation}
-where $L$ is the step length, $k$ the concentration parameter from the von
-Mises distribution that we correlate with the revenue so
-that $k = (Rev + 1 / RefRev) * max_{k}$, where $max_{k}$ is the maximum
-concentration value, $k$, and $RefRev$ is parametrised as for $\beta_{3}$ in
-the step length function.
+where $Le$ is the step length, $k$ the concentration parameter from the von
+Mises distribution that we correlate with the revenue so that $k = (Rev + 1 /
+RefRev) \cdot max_{k}$, where $max_{k}$ is the maximum concentration value,
+$k$, and $RefRev$ is parametrised as for $\beta_{3}$ in the step length
+function.
 
@@
 apart are fished (Figure \ref{fig:mv} (B)). These different locations relate to
-areas where the highest revenue were experienced, as shown by
-\added[id=PD]{Figure} \ref{fig:13}, where several vessels tracks are
-overlaid on the revenue field, i.e. $$\sum^c_{c=1}\sum^s_{s=1} B_{s,c} \cdot
-Q_{s,c}$$
+areas where the highest revenue were experienced, as shown by Figure
+\ref{fig:mv} (D), where several vessels tracks are overlaid on the revenue
+field, i.e. $$\sum^c_{c=1}\sum^s_{s=1} B_{s,c} \cdot Q_{s,c}$$
 
@@
 exploring the inter- and intra- specific interactions among fish populations
-(e.g. OSMOSE \cite{Shin2004}) in order to understand how they vary over space
+(e.g. OSMOSE; \cite{Shin2004}) in order to understand how they vary over space
 and time. Our focus was on understanding the strengths and limitations of
@@
 fleets exploiting multiple fish populations and realising catch distributions
-that may differ from the underlying populations [[\citep{Gillis2008}]]. As
-such, we favoured a minimum realistic model of the fish populations
-\citep{Plaganyi2014} taking account of environmental but not demographic
-stochasticity, while incorporating detailed fishing dynamics that take account
-of different drivers in a mechanistic way.  \\
+that may differ from the underlying populations, as identified by
+\cite{Gillis2008}. As such, we favoured a minimum realistic model of the fish
+populations \citep{Plaganyi2014} taking account of environmental but not
+demographic stochasticity, while incorporating detailed fishing dynamics that
+take account of different drivers in a mechanistic way.  \\
 
@@
 practices if potential biases in data are to be understood and taken into
-account \added[id=CM]{(Figures X,Y,Z)}. \\
+account (Figures X,Y,Z). \\
 
@@
 others due to gaps between survey stations limiting spatial and temporal
-coverage \added[id=CM]{(Figures X,Y,Z)}. This provides a challenge when
+coverage (Figures X,Y,Z). This provides a challenge when
 modelling unsampled areas in inferring species distribution maps, though these
@@
 	\includegraphics[width = \linewidth]{Plots/pop_dist}
-	\caption{Simulated spatial dynamics - the four populations abundance
-		(log+1) at four time steps.
-		}
+	\caption{Spatial density (log abundance) for each of the four
+		populations at four time steps. The darker the colour the
+		greater the density of the population. Note that you can see
+		the diagonal isotropic patterns in populations 2 and 3 and
+		concentrated spawning areas in the second row of the panels
+		(t=18) }
 	\label{fig:9}
@@
 	\caption{Fishing mortality dynamics - the daily fishing mortalities
-		showing weekly and seasonal patterns in exploitation.
-		Individual years and the light grey lines, the mean of all
-		years the thick black line}
+		across the entire spatial domain showing weekly and seasonal
+		patterns in exploitation.  Individual years and the light grey
+		lines, the mean of all years the thick black line}
 	\label{fig:10}
@@
 	\caption{(A) The fishing locations (points) and movements (lines) of a
-	single vessel during a trip overlaid on the relative value of a fishing
-	site; (B) the fishing locations of the vessel over several trips (value
-field changes over the period so not shown); (C) the locations of multiple
-vessels from the same fleet overlaid on the value field, (D) the realised step
-distance and turning angles for a single vessel over the simulation}
+		single vessel during a trip overlaid on the relative value of a
+		fishing site; (B) the fishing locations of the vessel over
+		several trips (value field changes over the period so not
+		shown). Note that the field is wrapped on a torus so that
+		distances between opposite side of the spatial domain are
+		considered next to each other, hence apparent large movements;
+		(C) the locations of multiple vessels from the same fleet
+		overlaid on the value field, (D) the realised step distance and
+		turning angles for a single vessel over the simulation}
 	\label{fig:mv}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{Plots/vessel_move_value}
-	\caption{movement of a fleet over a single trip reference overlaid on the
-		value field (i.e. sum of the population abundance x catchability x value}
-	\label{fig:13}
 \end{figure}
@@
 		trends. Line colour denotes the timescale, while linestyle
-		denotes the spatial resolution.}
+		denotes the spatial resolution. The vertical dashed line
+		indicates the onset of the spatial closures.}
 	\label{fig:3}

### 2019-09-17 write_up/parameter_tables.tex
JJP comments

@@
 		population $p$ & - \\
-		$Tol_{c,p,wk}$ & Thermal tolerance for population $p$ in cell
-		$c$ at week $wk$ & - \\
-		$d_{IJ}$ & euclidean distance between cell $I$ and cell $J$ & - \\
+		$Tol_{c,wk,p}$ & Thermal tolerance for in cell $c$ at week $wk$
+		for population $p$ & - \\
+		$d_{I,J}$ & euclidean distance between cell $I$ and cell $J$ & - \\
 		\bottomrule
@@
 		\hspace{0.1cm} kg$^{-1}$ \\
-		StepL & Step length for vessel & euclidean distance \\
+		Le & Step length for vessel & euclidean distance \\
 		Br & Bearing & degrees \\

### 2019-09-17 write_up/F_changes.tex
All revisions to figures

--- 2019-02-19 write_up/F_changes.tex
@@
-% latex table generated in R 3.5.2 by xtable 1.8-3 package
-% Tue Feb 19 17:00:17 2019
-\begin{longtable}{rllrrrlllr}
+% latex table generated in R 3.6.1 by xtable 1.8-4 package
+% Tue Sep 17 17:32:36 2019
+\begin{longtable}{rlrrrllr}
 \caption{Fishing mortality effects of the
@@
   \hline
-scenario & metric & pop & before & after & diff & timescale & basis & data\_type & resolution \\ 
+Scenario No & Population & F before & F after & \% F change & data type & timescale & resolution \\ 
   \hline
-  9 & F & spp\_3 & 1.08 & 0.29 & -73.47 & weekly & high\_pop & real\_pop & 1.00 \\ 
-   10 & F & spp\_3 & 1.08 & 0.29 & -72.94 & monthly & high\_pop & real\_pop & 1.00 \\ 
-   11 & F & spp\_3 & 1.08 & 0.35 & -68.04 & yearly & high\_pop & real\_pop & 1.00 \\ 
-   45 & F & spp\_3 & 1.08 & 0.58 & -46.70 & yearly & high\_pop & commercial & 20.00 \\ 
-    1 & F & spp\_3 & 1.08 & 0.58 & -46.21 & weekly & high\_pop & commercial & 1.00 \\ 
-   23 & F & spp\_3 & 1.08 & 0.59 & -45.27 & weekly & high\_pop & real\_pop & 5.00 \\ 
-    2 & F & spp\_3 & 1.08 & 0.59 & -45.06 & monthly & high\_pop & commercial & 1.00 \\ 
-    7 & F & spp\_3 & 1.08 & 0.60 & -44.48 & yearly & high\_pop & survey & 1.00 \\ 
-   24 & F & spp\_3 & 1.08 & 0.61 & -43.20 & monthly & high\_pop & real\_pop & 5.00 \\ 
-    3 & F & spp\_3 & 1.08 & 0.64 & -40.82 & yearly & high\_pop & commercial & 1.00 \\ 
-   25 & F & spp\_3 & 1.08 & 0.65 & -39.94 & yearly & high\_pop & real\_pop & 5.00 \\ 
-   17 & F & spp\_3 & 1.08 & 0.67 & -38.11 & yearly & high\_pop & commercial & 5.00 \\ 
-   15 & F & spp\_3 & 1.08 & 0.71 & -34.38 & weekly & high\_pop & commercial & 5.00 \\ 
-   43 & F & spp\_3 & 1.08 & 0.71 & -34.31 & weekly & high\_pop & commercial & 20.00 \\ 
-   16 & F & spp\_3 & 1.08 & 0.73 & -32.58 & monthly & high\_pop & commercial & 5.00 \\ 
-   51 & F & spp\_3 & 1.08 & 0.78 & -27.92 & weekly & high\_pop & real\_pop & 20.00 \\ 
-   37 & F & spp\_3 & 1.08 & 0.78 & -27.76 & weekly & high\_pop & real\_pop & 10.00 \\ 
-   39 & F & spp\_3 & 1.08 & 0.79 & -26.98 & yearly & high\_pop & real\_pop & 10.00 \\ 
-   38 & F & spp\_3 & 1.08 & 0.81 & -25.47 & monthly & high\_pop & real\_pop & 10.00 \\ 
-   21 & F & spp\_3 & 1.08 & 0.81 & -25.21 & yearly & high\_pop & survey & 5.00 \\ 
-   35 & F & spp\_3 & 1.08 & 0.81 & -25.05 & yearly & high\_pop & survey & 10.00 \\ 
-   44 & F & spp\_3 & 1.08 & 0.87 & -19.91 & monthly & high\_pop & commercial & 20.00 \\ 
-   52 & F & spp\_3 & 1.08 & 0.88 & -18.39 & monthly & high\_pop & real\_pop & 20.00 \\ 
-   30 & F & spp\_3 & 1.08 & 0.96 & -11.06 & monthly & high\_pop & commercial & 10.00 \\ 
-   29 & F & spp\_3 & 1.08 & 0.98 & -9.80 & weekly & high\_pop & commercial & 10.00 \\ 
-   31 & F & spp\_3 & 1.08 & 1.03 & -4.36 & yearly & high\_pop & commercial & 10.00 \\ 
-   53 & F & spp\_3 & 1.08 & 1.06 & -1.64 & yearly & high\_pop & real\_pop & 20.00 \\ 
-   49 & F & spp\_3 & 1.08 & 1.07 & -1.01 & yearly & high\_pop & survey & 20.00 \\ 
+  9 & Population 3 & 1.08 & 0.29 & -73.47 & True Population & weekly & 1.00 \\ 
+   10 & Population 3 & 1.08 & 0.29 & -72.94 & True Population & monthly & 1.00 \\ 
+   11 & Population 3 & 1.08 & 0.35 & -68.04 & True Population & yearly & 1.00 \\ 
+   45 & Population 3 & 1.08 & 0.58 & -46.70 & commercial & yearly & 20.00 \\ 
+    1 & Population 3 & 1.08 & 0.58 & -46.21 & commercial & weekly & 1.00 \\ 
+   23 & Population 3 & 1.08 & 0.59 & -45.27 & True Population & weekly & 5.00 \\ 
+    2 & Population 3 & 1.08 & 0.59 & -45.06 & commercial & monthly & 1.00 \\ 
+    7 & Population 3 & 1.08 & 0.60 & -44.48 & survey & yearly & 1.00 \\ 
+   24 & Population 3 & 1.08 & 0.61 & -43.20 & True Population & monthly & 5.00 \\ 
+    3 & Population 3 & 1.08 & 0.64 & -40.82 & commercial & yearly & 1.00 \\ 
+   25 & Population 3 & 1.08 & 0.65 & -39.94 & True Population & yearly & 5.00 \\ 
+   17 & Population 3 & 1.08 & 0.67 & -38.11 & commercial & yearly & 5.00 \\ 
+   15 & Population 3 & 1.08 & 0.71 & -34.38 & commercial & weekly & 5.00 \\ 
+   43 & Population 3 & 1.08 & 0.71 & -34.31 & commercial & weekly & 20.00 \\ 
+   16 & Population 3 & 1.08 & 0.73 & -32.58 & commercial & monthly & 5.00 \\ 
+   51 & Population 3 & 1.08 & 0.78 & -27.92 & True Population & weekly & 20.00 \\ 
+   37 & Population 3 & 1.08 & 0.78 & -27.76 & True Population & weekly & 10.00 \\ 
+   39 & Population 3 & 1.08 & 0.79 & -26.98 & True Population & yearly & 10.00 \\ 
+   38 & Population 3 & 1.08 & 0.81 & -25.47 & True Population & monthly & 10.00 \\ 
+   21 & Population 3 & 1.08 & 0.81 & -25.21 & survey & yearly & 5.00 \\ 
+   35 & Population 3 & 1.08 & 0.81 & -25.05 & survey & yearly & 10.00 \\ 
+   44 & Population 3 & 1.08 & 0.87 & -19.91 & commercial & monthly & 20.00 \\ 
+   52 & Population 3 & 1.08 & 0.88 & -18.39 & True Population & monthly & 20.00 \\ 
+   30 & Population 3 & 1.08 & 0.96 & -11.06 & commercial & monthly & 10.00 \\ 
+   29 & Population 3 & 1.08 & 0.98 & -9.80 & commercial & weekly & 10.00 \\ 
+   31 & Population 3 & 1.08 & 1.03 & -4.36 & commercial & yearly & 10.00 \\ 
+   53 & Population 3 & 1.08 & 1.06 & -1.64 & True Population & yearly & 20.00 \\ 
+   49 & Population 3 & 1.08 & 1.07 & -1.01 & survey & yearly & 20.00 \\ 
    \hline

### 2019-09-17 write_up/mixfishsim_ecolmod.tex
All revisions to figures

@@
 \usepackage{booktabs}
-%\usepackage[textsize=scriptsize]{todonotes}
-\usepackage[textsize=scriptsize, disable]{todonotes}  %% to turn off notes
 \usepackage{eurosym}
@@
 To answer this question we compare different spatial and temporal aggregations
-of the real population distributions to:
+of the true population distributions to:
 \begin{enumerate}[label=\alph*)]
@@
 (either derived from the commercial catches, fisheries-independent survey or
-the real population used at different spatial and temporal scales. \\
+the true population used at different spatial and temporal scales. \\
 
@@
 \begin{enumerate}
-	\item Extract data source (real population, commercial or survey), 
+	\item Extract data source (true population, commercial or survey), 
 	\item Aggregate according to desired spatial and temporal resolution,
@@
 	\item \textbf{data types:} commercial logbook data, survey data and
-		real population,
+		true population,
 	\item \textbf{temporal resolutions:} weekly, monthly and yearly
@@
 data source and aggregation level (Figure \ref{fig:1}). The finer spatial grid
-for the real population (top left) and commercial data (top middle) show
+for the true population (top left) and commercial data (top middle) show
 visually similar patterns, though there are large unsampled areas in the
@@
 patterns and, while losing some of the spatial detail, there remains good
-consistency between the real population and the commercial data. Survey data
+consistency between the true population and the commercial data. Survey data
 starts to pick out some of the similar patterns as the other data sources, but
@@
 resolutions for all data sources, and some differences between the survey,
-commercial and real population data emerge. \\
+commercial and true population data emerge. \\
 
@@
 compositions from across an aggregated 20 x 20 area (Figure \ref{fig:2}). In
-the real population, the monthly aggregation captures the major patterns of
+the true population, the monthly aggregation captures the major patterns of
 composition seen in the weekly data with the percentage of different species in
@@
 The commercial data on a weekly basis shows some of the same patterns as the
-real population, though the species 1 (in red) is less well represented and
+true population, though the species 1 (in red) is less well represented and
 some weeks are missing catches from the area. Here, weekly and monthly
@@
 practices if potential biases in data are to be understood and taken into
-account (Figures X,Y,Z). \\
+account (Figures \ref{fig:9}, \ref{fig:mv}). \\
 
@@
 fished. Similarly, despite the even spatial coverage the survey was able to
-capture some of the same spatial patterns as the real population, but missed
+capture some of the same spatial patterns as the true population, but missed
 others due to gaps between survey stations limiting spatial and temporal
-coverage (Figures X,Y,Z). This provides a challenge when
+coverage (Figure \ref{fig:1}). This provides a challenge when
 modelling unsampled areas in inferring species distribution maps, though these
@@
 %\begin{comment}
+
 \begin{figure}[!ht]
@@
 		concentrated spawning areas in the second row of the panels
-		(t=18) }
+		(t=18).}
 	\label{fig:9}
@@
 		patterns in exploitation.  Individual years and the light grey
-		lines, the mean of all years the thick black line}
+		lines, the mean of all years the thick black line.}
 	\label{fig:10}
@@
 	\caption{(A) The fishing locations (points) and movements (lines) of a
-		single vessel during a trip overlaid on the relative value of a
-		fishing site; (B) the fishing locations of the vessel over
-		several trips (value field changes over the period so not
-		shown). Note that the field is wrapped on a torus so that
-		distances between opposite side of the spatial domain are
+		single vessel during a trip overlaid on the revenue of a
+		fishing site (catch x price); (B) the fishing locations of the
+		vessel over several trips (value field changes over the period
+		so not shown). Note that the field is wrapped on a torus so
+		that distances between opposite side of the spatial domain are
 		considered next to each other, hence apparent large movements;
@@
 		overlaid on the value field, (D) the realised step distance and
-		turning angles for a single vessel over the simulation}
+		turning angles for a single vessel over the simulation.}
 	\label{fig:mv}
@@
 	\caption{Data aggregation at different spatial resolutions over a
-		ten year period}
+		ten year period.}
 	\label{fig:1}
@@
 	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_time_Rev2}
-	\caption{Data aggregation at different temporal resolutions over a
-		ten-year period}
+	\caption{Proportion of each population (y axis) for data aggregated at
+		different temporal resolutions. Data is aggregated over a
+		ten-year period for an area 20 x 20. Each bar represents either
+		a week, month or year respectively.}
 	\label{fig:2}
@@
 	\caption{Comparison of closure scenarios effect on fishing mortality
-		trends. Line colour denotes the timescale, while linestyle
-		denotes the spatial resolution. The vertical dashed line
+		trends. Line colour denotes timescale, while linestyle
+		denotes spatial resolution. The vertical dashed line
 		indicates the onset of the spatial closures.}
@@
 	in relation to a) before the closure fishing locations, b) after the
-	closure fishing locations, c) species 3 habitat distribution}
+	closure fishing locations, c) species 3 habitat distribution.}
 	\label{fig:17}

### 2019-09-17 R/plot_fleet_trip.R

@@ -29,7 +29,8 @@ if(is.null(pop_bios)) {
 print(ggplot(log, aes(x = x, y = y)) + 
       geom_point(aes(colour = vessel)) +
       geom_path(aes(colour = vessel)) + 
-      theme_bw()) 
+      theme_bw() + xlab("x distance") + ylab("y distance")
+      )
 }
 
 
@@ -60,7 +61,9 @@ print(ggplot(TotValDF, aes(x = x, y = y)) + geom_tile(aes(fill = value)) +
 	theme_bw() + #scale_colour_gradient(low = "red", high = "darkred") + 
 	expand_limits(y = c(0,sim_init[["idx"]][["ncols"]]), 
 		      x = c(0,sim_init[["idx"]][["nrows"]])) +
-      theme(legend.position = "none")
+      theme(legend.position = "none") +
+      xlab("x distance") + ylab("y distance")
+
 	
 	)
 

### 2019-09-17 R/plot_vessel_move.R

@@ -36,7 +36,9 @@ return(print(ggplot(log, aes(x = x, y = y, group = paste(vessel, trip))) +
       geom_path(aes(colour = trip))+ theme_bw() +
       expand_limits(y = c(0,sim_init[["idx"]][["ncols"]]), 
 		    x = c(0,sim_init[["idx"]][["nrows"]])) + 
-	     theme(legend.position = "none")))
+	     theme(legend.position = "none") + ylab("y distance") + 
+	     xlab("x distance")
+	     ))
 
 }
 
@@ -66,7 +68,8 @@ return(print(ggplot(TotValDF, aes(x = x, y = y)) + geom_tile(aes(fill = value)) 
 	theme_bw() + scale_colour_gradient(low = "red", high = "darkred") + 
 	expand_limits(y = c(0,sim_init[["idx"]][["ncols"]]), 
 		      x = c(0,sim_init[["idx"]][["nrows"]])) + 
-       theme(legend.position = "none")
+       theme(legend.position = "none")+ ylab("y distance") + 
+	     xlab("x distance")
 ))
 
 }

### 2019-09-17 analysis/KillerFigure.R

@@ -227,10 +227,10 @@ plot_comp(gran = 20, dataIn = dataIn)
 dataIn <- get_data(basis = 'survey', yr = yr, mn = mn, wk = wk, dataIn = res[["survey"]][["log.mat"]]) 
 plot_comp(gran = 20, dataIn = dataIn)
 
-mtext(text = "Real Population        Commercial Data     Survey Data", side = 3, line = 2, outer = T, font = 2,   cex = 3 ) ## top
-mtext(text = "20 x 20 pt                        10 x 10  pt                         5 x 5 pt                     1 x 1 pt", side = 4, line = 2, outer = T, font = 2, cex  = 3) ## right side
+mtext(text = "True Population     Commercial Data        Survey Data", side = 3, line = 2, outer = T, font = 2,   cex = 3 ) ## top
+mtext(text = "20 x 20                         10 x 10                           5 x 5                      1 x 1 ", side = 4, line = 2, outer = T, font = 2, cex  = 3) ## right side
 
-legend(x = -250, y = -10, legend = c("Pop 1", "Pop 2", "Pop 3", "Pop 4"),
+legend(x = -330, y = -10, legend = c("Population 1", "Population 2", "Population 3", "Population 4"),
             fill = c("#E66101", "#FDB863", "#B2ABD2", "#5E3C99"), ncol = 4, xpd = NA, bty = "n", cex = 4)
  
 dev.off()
@@ -506,10 +506,10 @@ plot_temp(timestep = 'year', basis = 'real_pop')
 plot_temp(timestep = 'year', basis = 'commercial')
 plot_temp(timestep = 'year', basis = 'survey')
 
-mtext(text = "Real Population        Commercial Data     Survey Data", side = 3, line = 2, outer = T, font = 2,   cex = 3 ) ## top
+mtext(text = "True Population  Commercial Data        Survey Data", side = 3, line = 2, outer = T, font = 2,   cex = 3 ) ## top
 mtext(text = "yearly                                     monthly                                       weekly", side = 4, line = 2, outer = T, font = 2, cex  = 3) ## right side
 
-legend(x = -20, y = 0, legend = c("Pop 1", "Pop 2", "Pop 3", "Pop 4"),
+legend(x = -25, y = 0, legend = c("Population 1", "Population 2", "Population 3", "Population 4"),
             fill = c("#E66101", "#FDB863", "#B2ABD2", "#5E3C99"), ncol = 4, xpd = NA, bty = "n", cex = 4)
  
 dev.off()

### 2019-09-17 analysis/Plot_Bio.R

@@ -25,13 +25,13 @@ plot_catch_comp(gran = c(1), logs = logs, fleets = 1:5,
 cols <- brewer.pal(9, "BuGn")
 
 png(file = file.path("..", "write_up","Plots", "pop_dist.png"), width = 1600, height = 1600)
-par(mfrow=c(4,4), mar = c(1,1,1,1))
+par(mfrow=c(4,4), oma = c(4,4,4,4), mar = c(1,1,1,1))
 
 for(j in round(seq.int(1,52,length.out = 4),0)) {
 for(i in 1:4) {
 image(seq_len(100), seq_len(100), log(pop[[9,j]][[i]]+1), col = cols)
-if(i==1) {text(x = 9, y = 94, labels = paste("t =",j), cex= 2, font = 2)}
-if(j==1) {text(x = 92, y = 94, labels = paste("Pop ",i), cex = 2, font = 2)}
+if(i==1) {text(x = 17, y = 94, labels = paste("week =",j), cex= 3, font = 2, col = "blue")}
+if(j==1) {text(x = 78, y = 94, labels = paste("Population ",i), cex = 3, font = 2, col = "blue")}
 }
 
 }

### 2019-09-17 analysis/Plot_fishing.R

@@ -90,22 +90,27 @@ cl <- do.call(rbind, cl)
 p1 <- ggplot(filter(logs, closure == "before"), aes(x = x , y = y)) +
 	geom_point(colour = "blue", alpha = 0.2, shape = "x") +
 	expand_limits(x = c(0,100), y = c(0,100)) + facet_wrap(~year) +
-	theme_bw() + theme(plot.margin = margin(1, 0.5, 0.5, 0.5, "cm"))
+	theme_bw() + theme(plot.margin = margin(1, 0.5, 0.5, 0.5, "cm")) +
+	xlab("x distance") + ylab("y distance")
 
 p2 <- ggplot(cl) + geom_polygon(aes(long, lat, group = group), colour = "red",fill = NA) +
 	expand_limits(x = c(0,100), y = c(0,100)) + facet_wrap(~year) +
 	geom_point(aes(x = x, y = y), colour = "blue", 
 		   data = filter(logs, closure == "after"), 
 		   alpha = 0.2, shape = "x") +
-	theme_bw() + theme(plot.margin = margin(1, 0.5, 0.5, 0.5, "cm"))
+	theme_bw() + theme(plot.margin = margin(1, 0.5, 0.5, 0.5, "cm"))+
+	xlab("x distance") + ylab("y distance")
+
 
 p3 <- ggplot(cl) + geom_raster(aes(x, y, alpha = hab), data = filter(hab.df, hab > 0))+ 
 	geom_polygon(aes(long, lat, group = group), colour = "red",fill = NA) +
 	expand_limits(x = c(0,100), y = c(0,100)) + facet_wrap(~year) +
 	theme_bw() + theme(plot.margin = margin(1, 0.5, 0.5, 0.5, "cm"), 
-			   legend.position = "none")
+			   legend.position = "none") +
+	xlab("x distance") + ylab("y distance")
 
-plot_grid(p1, p2, p3, labels = c("(a) before closures", "(b) after closures", "(c) habitat spp3" ), vjust = 2, ncol = 1)
+
+plot_grid(p1, p2, p3, labels = c("(a) before closures", "(b) after closures", "(c) habitat Population 3" ), vjust = 2, ncol = 1)
 ggsave(file = "Closure_fishing_locations_yearly.png", width = 6, height = 18)
 
 }

### 2019-09-17 analysis/Plots.R

@@ -40,12 +40,26 @@ df <- daily_fdyn(res)
 mean_f <- df %>% group_by(pop, day) %>%
 	summarise(data = mean(data, na.rm = T))
 
+## relabel for plot
+df$pop[df$pop == "spp_1"] <- "Population 1"
+df$pop[df$pop == "spp_2"] <- "Population 2"
+df$pop[df$pop == "spp_3"] <- "Population 3"
+df$pop[df$pop == "spp_4"] <- "Population 4"
+
+mean_f$pop[mean_f$pop == "spp_1"] <- "Population 1"
+mean_f$pop[mean_f$pop == "spp_2"] <- "Population 2"
+mean_f$pop[mean_f$pop == "spp_3"] <- "Population 3"
+mean_f$pop[mean_f$pop == "spp_4"] <- "Population 4"
+
+
 ggplot(filter(df, !is.na(data)), aes(x = day, y = data, group = year)) +
 	geom_line(colour = "grey", alpha = 0.4) +
 	geom_line(data = filter(mean_f,!is.na(data)), aes(group = pop),
 		  colour = "black", size = 1) +  
 	facet_wrap(~pop) +
-	theme_classic()
+	theme_classic() + 
+	ylab(expression(Fishing~mortality~day^{-1})) +
+	xlab("Day") 
 	
 ggsave(file = file.path('..', 'write_up', 'Plots', 'f_dynamics.png'), width = 8, height = 8)
 
@@ -105,8 +119,8 @@ stepDF <- dplyr::filter(as.data.frame(logs), fleet == 3, vessel == 2)
 	stepDF$step_lagged   <- c(stepDF$stepD[2:nrow(stepDF)],NA)
 	stepDF$angles_lagged <- c(stepDF$angles[2:nrow(stepDF)],NA)
 
-	plot(stepDF$val_lagged, stepDF$step_lagged, main = "Realised step distances", xlab = "value", ylab = "step distance")
-	plot(stepDF$val_lagged, stepDF$angles_lagged, main = "Realised turning angles", xlab = "value", ylab = "change in angle")
+	plot(stepDF$val_lagged, stepDF$step_lagged, main = "Realised step distances", xlab = "value (Euros)", ylab = "step distance")
+	plot(stepDF$val_lagged, stepDF$angles_lagged, main = "Realised turning angles", xlab = "value (Euros)", ylab = "change in angle")
 
 
[…]

### 2019-09-17 analysis/Plots_Combined.R

@@ -137,7 +137,18 @@ Fs <- filter(combined, metric == "F", basis == "high_pop", pop == "spp_3")
 Fs[,c(4:6)] <- round(Fs[,c(4:6)], 2)
 Fs <- Fs[order(Fs$pop, Fs$diff),]
 
-colnames(Fs)[4:6] <- c("f_before", "f_after", "f_change")
+colnames(Fs)[4:6] <- c("F before", "F after", "F change")
+
+Fs$pop[Fs$pop == "spp_1"] <- "Population 1"
+Fs$pop[Fs$pop == "spp_2"] <- "Population 2"
+Fs$pop[Fs$pop == "spp_3"] <- "Population 3"
+Fs$pop[Fs$pop == "spp_4"] <- "Population 4"
+
+Fs$data_type[Fs$data_type == "real_pop"] <- "True Population"
+
+Fs <- Fs[c("scenario", "pop", "F before", "F after", "F change", "data_type", "timescale", "resolution")]
+
+colnames(Fs) <- c("Scenario No", "Population", "F before", "F after", "% F change", "data type", "timescale", "resolution")
 
 print(xtable(Fs, digits = 2, caption = "Fishing mortality effects of the
 	     closure scenarios (ordered by most effective first)", label =
@@ -190,17 +201,29 @@ combined_pop_an$year <- as.numeric(combined_pop_an$year) # to fix x-axis breaks
 
 combined_pop_an$res <- as.factor(combined_pop_an$res)
 
+
+combined_pop_an$pop[combined_pop_an$pop == "spp_1"] <- "Population 1"
+combined_pop_an$pop[combined_pop_an$pop == "spp_2"] <- "Population 2"
+combined_pop_an$pop[combined_pop_an$pop == "spp_3"] <- "Population 3"
+combined_pop_an$pop[combined_pop_an$pop == "spp_4"] <- "Population 4"
+
+combined_pop_an$data_type[combined_pop_an$data_type == "real_pop"]  <- "True Population"
+
+
 png('F_trendsREV.png', units = "in", height = 8, width = 9, res = 600)
+
 ggplot(filter(combined_pop_an,basis == 'high_pop', metric == 'F'), 
        aes(x = year, y = data, group = combined)) + 
-geom_line(aes(colour = timescale, linetype = res), size = 1) + 
+geom_line(aes(colour = timescale, linetype = res), size = 1) +
+scale_linetype_manual(values = rev(1:4)) + 
[…]

### 2019-09-17 analysis/Temporal_values.R

@@ -27,9 +27,28 @@ df2 <- df %>% group_by(data_type, timescale) %>%
 		  spp4 = 100 * mean(spp_4), sd_spp4 = 100 * sd(spp_4)
 		  )
 
+df2 <- df2 %>% as.data.frame()
+
+df2$data_type[df2$data_type == "real_pop"]  <- "True Population"
+
+colnames(df2) <- c("Data type", "Timescale", "Pop 1", "SD Pop 1",
+ "Pop 2", "SD Pop 2",
+ "Pop 3", "SD Pop 3",
+ "Pop 4", "SD Pop 4"
+)
+
+df2$"Population 1" <- paste0(round(df2$"Pop 1",3), "(",round(df2$"SD Pop 1",3),")")
+df2$"Population 2" <- paste0(round(df2$"Pop 2",3), "(",round(df2$"SD Pop 2",3),")")
+df2$"Population 3" <- paste0(round(df2$"Pop 3",3), "(",round(df2$"SD Pop 3",3),")")
+df2$"Population 4" <- paste0(round(df2$"Pop 4",3), "(",round(df2$"SD Pop 4",3),")")
+
+df2 <- df2 %>% select("Data type", "Timescale", 
+		      "Population 1", "Population 2", 
+		      "Population 3", "Population 4")
+
 
 library(xtable)
-print(xtable(df2, digits = 3, caption = "Proportions of each species at different levels of temporal aggregation",
+print(xtable(df2, digits = 3, caption = "Mean and standard deviation of proportions of each species at different levels of temporal aggregation",
 	     label = "tab:7"), caption.placement = "top", file =
 file.path("..","write_up", "Temp_proportions.tex"),include.rownames = FALSE,
 tabular.environment= "longtable", floating = FALSE)

### 2019-09-17 analysis/effectiveness_plot.R

@@ -78,6 +78,14 @@ dev.off()
 ## re-order so focus species is first
 f_diff$fpop <- factor(f_diff$pop, levels = c("spp_3", "spp_1", "spp_2", "spp_4"))
 
+levels(f_diff$fpop)[levels(f_diff$fpop) == "spp_1"] <- "Population 1"
+levels(f_diff$fpop)[levels(f_diff$fpop) == "spp_2"] <- "Population 2"
+levels(f_diff$fpop)[levels(f_diff$fpop) == "spp_3"] <- "Population 3"
+levels(f_diff$fpop)[levels(f_diff$fpop) == "spp_4"] <- "Population 4"
+
+f_diff$data_type[f_diff$data_type == "real_pop"] <- "True Population"
+
+
 pdf("f_diff_effectiveness.pdf", height = 6, width = 8)
 ggplot(f_diff, aes(x = resolution, y = diff))+
     geom_line(aes(colour = data_type)) +
@@ -93,10 +101,11 @@ dev.off()
 png("f_diff_effectiveness.png", units = "in", height = 8, width = 9, res = 600)
 
 ggplot(f_diff, aes(x = resolution, y = diff))+
-    geom_line(aes(colour = data_type), size = 2) +
+    geom_line(aes(colour = data_type, linetype = data_type), size = 2) +
     facet_grid(timescale ~ fpop) +
     geom_hline(yintercept = 0, linetype = 2, size = 1) +
     scale_colour_manual("Data source", values = c("#d95f02", "#7570b3", "#1b9e77")) +
+    scale_linetype_manual("Data source", values = 1:3) + 
     theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
 	  axis.text = element_text(size = 14, face = "bold"),
 	  axis.title = element_text(size = 14, face = "bold")) +

### 2019-09-17 write_up/mixfishsim_ecolmod.tex
Replace "species x" with "population x"

@@
 the catch having similar mean and standard deviations.  In the weekly data
-species 1 = 9.36 (3.99), species 2 = 83.2 (5.60), species 3 = 3.57 (1.23),
-species 4 = 3.91 (1.59); in the monthly data species 1 = 9.23 (3.87), species 2
-= 83.3 (5.52), species 3 = 3.62 (1.15), species 4 = 3.86 (1.52). While means
+population 1 = 9.36 (3.99), population 2 = 83.2 (5.60), population 3 = 3.57 (1.23),
+population 4 = 3.91 (1.59); in the monthly data population 1 = 9.23 (3.87), population 2
+= 83.3 (5.52), population 3 = 3.62 (1.15), population 4 = 3.86 (1.52). While means
 were similar some of the variation was lost when aggregated to an annual level;
-species 1 = 9.90 (0.173), species 2 = 82.2 (0.308), species 3 = 3.82 (0.119),
-species 4 = 4.03 (0.0502).\\
+population 1 = 9.90 (0.173), population 2 = 82.2 (0.308), population 3 = 3.82 (0.119),
+population 4 = 4.03 (0.0502).\\
 
 The commercial data on a weekly basis shows some of the same patterns as the
-true population, though the species 1 (in red) is less well represented and
+true population, though the population 1 (in red) is less well represented and
 some weeks are missing catches from the area. Here, weekly and monthly
-compositions were nearly identical, with monthly composition of species 1 =
-0.0472 (0.0139), species 2 = 94.4 (1.47), species 3 = 3.12 (1.47), species 4 =
+compositions were nearly identical, with monthly composition of population 1 =
+0.0472 (0.0139), population 2 = 94.4 (1.47), population 3 = 3.12 (1.47), population 4 =
 2.40 (0.444). Again, yearly values head a similar mean but smaller standard
@@
 The survey data was only available on an annual basis, and showed again a
-slightly different composition; species 1 = 0.372 (0.00473), species 2 = 87.7
-(0.193), species 3 = 0.729 (0.0200), species 4 = 11.2 (0.172).
+slightly different composition; population 1 = 0.372 (0.00473), population 2 = 87.7
+(0.193), population 3 = 0.729 (0.0200), population 4 = 11.2 (0.172).
 
@@
 this to assess the efficacy of a closure in reducing fishing mortality on
-species 3, given availability of data and its use at different resolutions in
+population 3, given availability of data and its use at different resolutions in
 order to evaluate the trade-offs in data sources.
@@
 fishery closure was successful in reducing fishing mortality on the species of
-interest (species 3; Figure \ref{fig:3}), though interestingly the largest
+interest (population 3; Figure \ref{fig:3}), though interestingly the largest
 reductions in fishing mortality happened immediately after the closures,
@@
 point) in time. The monthly data shows some consistency between the real
-population and commercial data for species 2 - 4, though species 1 remains
+population and commercial data for population 2 - 4, though population 1 remains
 under-represented.  On an annual basis, interestingly the commercial data under
@@
 1. This is likely due to the biases in commercial sampling, with the fisheries
-not targeting the areas where species 1 are present and the survey sampling
-areas where species 1 is more abundant than on average. This indicates that
+not targeting the areas where population 1 are present and the survey sampling
+areas where population 1 is more abundant than on average. This indicates that
 fixed closures, at the right resolution, when based on commercially derived
@@
 		coarse spatial resolution. Closure location can be seen in red
-	in relation to a) before the closure fishing locations, b) after the
-	closure fishing locations, c) species 3 habitat distribution.}
+		box in relation to a) before the closure fishing locations, b)
+		after the closure fishing locations, c) population 3 habitat
+		distribution.}
 	\label{fig:17}

### 2019-09-17 write_up/mixfishsim_ecolmod.tex
Minor tweak

@@
 heterogeneously distributed populations, and iii) fishery dynamics for multiple
-fleet characteristics based on species targeting under an explore-exploit
+fleet characteristics based on population targeting under an explore-exploit
 strategy. This is implemented via a mix of correlated random walk movement (for
@@
 The final combined process results in a population structure and movement
-pattern unique to each species, with population movement occurring on a weekly
+pattern unique to each population, with population movement occurring on a weekly
 basis. The decision to model population movement on a weekly timescale was to
@@
 targeting - that determined the fleet catch efficiency and preference towards a
-particular species; trip-level decisions, that determines the initial location
+particular population; trip-level decisions, that determines the initial location
 to be fished at the beginning of a trip; and within-trip decisions, that
@@
 Q_{fl, p}$] affects the overall catch rates for the fleet and the preferential
-targeting of one population over another. This, in combination with the
+targeting of one species over another. This, in combination with the
 parameter choice for the step-function defined below (as well as some
@@
 where $L_{c,d,p}$ is landings of a population $p$, and $Pr_{p}$ price of a
-population. All species prices were kept the same across fleets and seasons.
+population. All population prices were kept the same across fleets and seasons.
 Here, when fishing is successful vessels remain in a similar location and
@@
 \begin{enumerate}[label=\alph*)]
-	\item \textbf{fisheries-independent data:} the inferred population from
-		a fixed-site sampling survey design as commonly used for
+	\item \textbf{fisheries-independent data:} the inferred population
+		density from a fixed-site sampling survey design as commonly
+		used for
 		fisheries monitoring purposes;
-	\item \textbf{fisheries-dependent data:} the inferred population from
-		our fleet model that includes fishery-induced sampling
-		dynamics.
+	\item \textbf{fisheries-dependent data:} the inferred population
+		density from our fleet model that includes fishery-induced
+		sampling dynamics.
 \end{enumerate}
@@
 	\item \textbf{closure basis:} highest 5 \%  of catch rates for the
-		protected species
+		protected population
 \end{itemize}
@@
 the true population, the monthly aggregation captures the major patterns of
-composition seen in the weekly data with the percentage of different species in
-the catch having similar mean and standard deviations.  In the weekly data
-population 1 = 9.36 (3.99), population 2 = 83.2 (5.60), population 3 = 3.57 (1.23),
-population 4 = 3.91 (1.59); in the monthly data population 1 = 9.23 (3.87), population 2
-= 83.3 (5.52), population 3 = 3.62 (1.15), population 4 = 3.86 (1.52). While means
-were similar some of the variation was lost when aggregated to an annual level;
-population 1 = 9.90 (0.173), population 2 = 82.2 (0.308), population 3 = 3.82 (0.119),
-population 4 = 4.03 (0.0502).\\
+composition seen in the weekly data with the percentage of different
+populations in the catch having similar mean and standard deviations.  In the
+weekly data population 1 = 9.36 (3.99), population 2 = 83.2 (5.60), population
+3 = 3.57 (1.23), population 4 = 3.91 (1.59); in the monthly data population 1 =
+9.23 (3.87), population 2 = 83.3 (5.52), population 3 = 3.62 (1.15), population
+4 = 3.86 (1.52). While means were similar some of the variation was lost when
+aggregated to an annual level; population 1 = 9.90 (0.173), population 2 = 82.2
+(0.308), population 3 = 3.82 (0.119), population 4 = 4.03 (0.0502).\\
 

### 2019-09-17 write_up/mixfishsim_ecolmod.tex
Updated abstract

@@
 To understand how data resolution impacts inference on mixed fisheries
-interactions, we developed a highly resolved spatiotemporal discrete-event
+interactions we developed a highly resolved spatiotemporal discrete-event
 simulation model incorporating: i) delay-difference population dynamics, ii)
@@
 %%
-Fifty years of sub-daily fishing was simulated and used to draw inference on
-the underlying community structures. We compared inferences based on:
-commercial catch, a simulated fixed-site sampling survey design and the true
-underlying community. We i) establish the potential limitations of
+Fifty years of sub-daily fishing activity was simulated and used to draw
+inference on the underlying community structures. We compared inferences based
+on: commercial catch, a simulated fixed-site sampling survey design and the
+true underlying populations. We i) establish the potential limitations of
 fishery-dependent data in providing a robust picture of spatiotemporal
@@
 observational data and evaluate the underlying dynamics of such approaches at a
-fine spatial and temporal scale. We conclude from our example framework
-application that commercial data, while containing bias, provide a useful tool
-for managing catches in mixed fisheries if applied at the correct
-spatiotemporal scale. [NEED A LITTLE MORE DETAIL OF THE RESULTS HERE - 2 MORE
-SENTENCES ON KEY TAKE-HOME RESULTS]\\
+fine spatial and temporal scale. In application to a mixed fishery exploiting
+four different populations we found different spatial patterns were evident and
+that the effectiveness of the spatial closure reduced when data were aggregated
+across larger spatial areas. However, aggregation across time periods has less
+of a negative impact on the closure success and while not as effective as when
+based on on the true population, closures based on high catch rates observed in
+commercial data could still reduce fishing on a protected species. \\
+
+We conclude from our example framework application that commercial data, while
+containing bias, provide a useful tool for managing catches in mixed fisheries
+if applied at the correct spatiotemporal scale. \\
 %%
@@
 distributed in space and time with varying knowledge of species distributions.
-As fishers do not have full control over what species they select in `mixed
-fisheries' this can result in catch of low quota or protected species. If
-fishers discard over-quota catch of a species for which they have no quota, it
-limits our ability to control fishing mortality \citep{Alverson1994,
-	Crowder1998, Rijnsdorp2007} and the ability to manage fisheries for the
-biological and economic sustainability \citep{Ulrich2011a, Batsleer2015}.\\
+As fishers do not have full control over what species they select when fishing
+in `mixed fisheries' it can result in catch of low quota or protected species.
+If over-quota catch of a species for which they have no quota is discarded
+without being accounted for it limits our ability to control fishing mortality
+\citep{Alverson1994, Crowder1998, Rijnsdorp2007} and the ability to manage
+fisheries for the biological and economic sustainability \citep{Ulrich2011a,
+	Batsleer2015}.\\
 
@@
 compositions were nearly identical, with monthly composition of population 1 =
-0.0472 (0.0139), population 2 = 94.4 (1.47), population 3 = 3.12 (1.47), population 4 =
-2.40 (0.444). Again, yearly values head a similar mean but smaller standard
-deviation.\\
+0.0472 (0.0139), population 2 = 94.4 (1.47), population 3 = 3.12 (1.47),
+population 4 = 2.40 (0.444). Again, yearly values head a similar mean but
+smaller standard deviation.\\
 
 The survey data was only available on an annual basis, and showed again a
-slightly different composition; population 1 = 0.372 (0.00473), population 2 = 87.7
-(0.193), population 3 = 0.729 (0.0200), population 4 = 11.2 (0.172).
+slightly different composition; population 1 = 0.372 (0.00473), population 2 =
+87.7 (0.193), population 3 = 0.729 (0.0200), population 4 = 11.2 (0.172).
 

### 2019-09-18 write_up/mixfishsim_ecolmod.tex
Nothing

@@
 strategy. This is implemented via a mix of correlated random walk movement (for
-exploration) and learned behaviour (for exploitation) phases of the fisheries.
-\\ 
+exploration) and learned behaviour (for exploitation) phases of the fisheries. \\ 
 %%
@@
 distributions; and then ii) simulated an area closure based on areas defined
-from the different data sources at a range of temporal and spatial resolutions.
-\\
+from the different data sources at a range of temporal and spatial resolutions.\\
 %%

### 2019-09-24 write_up/mixfishsim_ecolmod.tex
text updates in response to JMG and JJP

@@
 \usepackage{comment}
-% For track-changes
-%\usepackage[draft]{changes}
-\usepackage[final]{changes} %% to turn off changes
-\definechangesauthor[color = red]{JM}
-\definechangesauthor[color = blue]{PD}
-\definechangesauthor[color = green!40!black]{JJ}
-\definechangesauthor[color = purple]{CM}
 
@@
 	B_{c,d+1} = &\\
-	& (1 + \rho) B_{c,d} \cdot \mathrm{e}^{-Z_{c,d}} - \rho \cdot
+	& \left(1 + \rho \right) B_{c,d} \cdot \mathrm{e}^{-Z_{c,d}} - \rho \cdot
 	\mathrm{e}^{-Z_{c,d}} \hspace{2.9cm}
 	\times \\  
-	& (B_{c,d-1} \cdot \mathrm{e}^{-Z_{c,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot
-	R_{\tilde{y}(c,y,d-1)})
-	\hspace{0.4cm} + \\
-	& Wt_{R} \cdot \alpha_{d} \cdot R_{\tilde{y}(c,y,d)} 
+	& \left(B_{c,d-1} \cdot \mathrm{e}^{-Z_{c,d-1}} + Wt_{R-1} \cdot \left( \alpha_{d-1} \cdot
+	R_{\tilde{y}(c)}\right) \right)
+	\hspace{0.9cm} + \\
+	& Wt_{R} \cdot \left( \alpha_{d} \cdot R_{\tilde{y}(c) \right)}
 	\end{split}
@@
 represents the proportion of fish recruited during that day for the year, while
-$R_{c,\tilde{y},d}$ is the annual recruits in year $y$ and day $d$ for cell
-$c$. \\
+$R_{c,\tilde{y}(c)}$ is the annual recruits in year $y$ for cell $c$. \\
 
@@
 those across all fleets and vessels, $C_{c, d} =
-\sum\limits_{fl=1}^{fl}\sum\limits_{v=1}^{v} E_{fl, v, c, d} \cdot Q_{fl} \cdot
+\sum\limits_{fl=1}^{FL}\sum\limits_{v=1}^{V} E_{fl, v, c, d} \cdot Q_{fl} \cdot
 D_{c, d}$ with $fl$ and $v$ the fleet and vessel respectively and
@@
 \end{equation}
-Where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
+where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
 biomass (SSB) required to produce half the maximum stock size, $S$ current
 stock size and $\sigma^2$ the variability in the recruitment due to stochastic
-processes, the stochastic Ricker form \citep{Ricker1954}:
+processes. The stochastic Ricker form \citep{Ricker1954} is:
 \begin{equation}
@@
 stations fished each year, starting on day 92 and ending on day 112 (5 stations
-per day) with same catchability parameters for all populations ($Q_{p} = 1$).
+per day) with same catchability parameter ($Q_{p} = 1$) for all populations $p$.
 This approximates a real world survey design with limited seasonal and spatial
@@
 \ref{fig:mv} (D), where several vessels tracks are overlaid on the revenue
-field, i.e. $$\sum^c_{c=1}\sum^s_{s=1} B_{s,c} \cdot Q_{s,c}$$
+field, i.e. $$Rev_{c} = \sum^P_{p=1} B_{c,p} \cdot Q_{fl,p} \cdot Pr_{p}$$
 
@@
 
-\section*{Abbreviations} Detail any unusual ones used.
-
-\section*{Acknowledgements} those providing help during the research..
-
 \section*{Funding} This work was supported by the MARES doctoral training

### 2019-09-24 write_up/F_changes.tex
JJP updates

@@
 % latex table generated in R 3.6.1 by xtable 1.8-4 package
-% Tue Sep 17 17:32:36 2019
-\begin{longtable}{rlrrrllr}
+% Tue Sep 24 20:53:17 2019
+\begin{longtable}{rrrllr}
 \caption{Fishing mortality effects of the
-	     closure scenarios (ordered by most effective first)} \\ 
+     closure scenarios on population 3 (ordered by most effective
+first). The fishing mortality
+     rate before the closure was 1.08.} \\ 
   \hline
-Scenario No & Population & F before & F after & \% F change & data type & timescale & resolution \\ 
+Scenario No & F after closure & \% F change & data type & timescale & resolution \\ 
   \hline
-  9 & Population 3 & 1.08 & 0.29 & -73.47 & True Population & weekly & 1.00 \\ 
-   10 & Population 3 & 1.08 & 0.29 & -72.94 & True Population & monthly & 1.00 \\ 
-   11 & Population 3 & 1.08 & 0.35 & -68.04 & True Population & yearly & 1.00 \\ 
-   45 & Population 3 & 1.08 & 0.58 & -46.70 & commercial & yearly & 20.00 \\ 
-    1 & Population 3 & 1.08 & 0.58 & -46.21 & commercial & weekly & 1.00 \\ 
-   23 & Population 3 & 1.08 & 0.59 & -45.27 & True Population & weekly & 5.00 \\ 
-    2 & Population 3 & 1.08 & 0.59 & -45.06 & commercial & monthly & 1.00 \\ 
-    7 & Population 3 & 1.08 & 0.60 & -44.48 & survey & yearly & 1.00 \\ 
-   24 & Population 3 & 1.08 & 0.61 & -43.20 & True Population & monthly & 5.00 \\ 
-    3 & Population 3 & 1.08 & 0.64 & -40.82 & commercial & yearly & 1.00 \\ 
-   25 & Population 3 & 1.08 & 0.65 & -39.94 & True Population & yearly & 5.00 \\ 
-   17 & Population 3 & 1.08 & 0.67 & -38.11 & commercial & yearly & 5.00 \\ 
-   15 & Population 3 & 1.08 & 0.71 & -34.38 & commercial & weekly & 5.00 \\ 
-   43 & Population 3 & 1.08 & 0.71 & -34.31 & commercial & weekly & 20.00 \\ 
-   16 & Population 3 & 1.08 & 0.73 & -32.58 & commercial & monthly & 5.00 \\ 
-   51 & Population 3 & 1.08 & 0.78 & -27.92 & True Population & weekly & 20.00 \\ 
-   37 & Population 3 & 1.08 & 0.78 & -27.76 & True Population & weekly & 10.00 \\ 
-   39 & Population 3 & 1.08 & 0.79 & -26.98 & True Population & yearly & 10.00 \\ 
-   38 & Population 3 & 1.08 & 0.81 & -25.47 & True Population & monthly & 10.00 \\ 
-   21 & Population 3 & 1.08 & 0.81 & -25.21 & survey & yearly & 5.00 \\ 
-   35 & Population 3 & 1.08 & 0.81 & -25.05 & survey & yearly & 10.00 \\ 
-   44 & Population 3 & 1.08 & 0.87 & -19.91 & commercial & monthly & 20.00 \\ 
-   52 & Population 3 & 1.08 & 0.88 & -18.39 & True Population & monthly & 20.00 \\ 
-   30 & Population 3 & 1.08 & 0.96 & -11.06 & commercial & monthly & 10.00 \\ 
-   29 & Population 3 & 1.08 & 0.98 & -9.80 & commercial & weekly & 10.00 \\ 
-   31 & Population 3 & 1.08 & 1.03 & -4.36 & commercial & yearly & 10.00 \\ 
-   53 & Population 3 & 1.08 & 1.06 & -1.64 & True Population & yearly & 20.00 \\ 
-   49 & Population 3 & 1.08 & 1.07 & -1.01 & survey & yearly & 20.00 \\ 
+  9 & 0.29 & -73.47 & true Population & weekly & 1.00 \\ 
+   10 & 0.29 & -72.94 & true Population & monthly & 1.00 \\ 
+   11 & 0.35 & -68.04 & true Population & yearly & 1.00 \\ 
+   45 & 0.58 & -46.70 & commercial & yearly & 20.00 \\ 
+    1 & 0.58 & -46.21 & commercial & weekly & 1.00 \\ 
+   23 & 0.59 & -45.27 & true Population & weekly & 5.00 \\ 
+    2 & 0.59 & -45.06 & commercial & monthly & 1.00 \\ 
+    7 & 0.60 & -44.48 & survey & yearly & 1.00 \\ 
+   24 & 0.61 & -43.20 & true Population & monthly & 5.00 \\ 
+    3 & 0.64 & -40.82 & commercial & yearly & 1.00 \\ 
+   25 & 0.65 & -39.94 & true Population & yearly & 5.00 \\ 
+   17 & 0.67 & -38.11 & commercial & yearly & 5.00 \\ 
+   15 & 0.71 & -34.38 & commercial & weekly & 5.00 \\ 
+   43 & 0.71 & -34.31 & commercial & weekly & 20.00 \\ 
+   16 & 0.73 & -32.58 & commercial & monthly & 5.00 \\ 
+   51 & 0.78 & -27.92 & true Population & weekly & 20.00 \\ 
+   37 & 0.78 & -27.76 & true Population & weekly & 10.00 \\ 
+   39 & 0.79 & -26.98 & true Population & yearly & 10.00 \\ 
+   38 & 0.81 & -25.47 & true Population & monthly & 10.00 \\ 
+   21 & 0.81 & -25.21 & survey & yearly & 5.00 \\ 
+   35 & 0.81 & -25.05 & survey & yearly & 10.00 \\ 
+   44 & 0.87 & -19.91 & commercial & monthly & 20.00 \\ 
+   52 & 0.88 & -18.39 & true Population & monthly & 20.00 \\ 
+   30 & 0.96 & -11.06 & commercial & monthly & 10.00 \\ 
+   29 & 0.98 & -9.80 & commercial & weekly & 10.00 \\ 
+   31 & 1.03 & -4.36 & commercial & yearly & 10.00 \\ 
+   53 & 1.06 & -1.64 & true Population & yearly & 20.00 \\ 
+   49 & 1.07 & -1.01 & survey & yearly & 20.00 \\ 
    \hline

### 2019-09-24 write_up/mixfishsim_ecolmod.tex
JJP updates

@@
 \textit{RandomFields} R package \citep{Schlater2015}. We define a stationary
-habitat field and combine it with a temporally dynamic thermal tolerance field to
-imitate two key drivers of population dynamics. Each population was initialised
-at a single location, and subsequently moved across the entire space according
-to a probabilistic distribution based on habitat suitability (represented by
-the normalised values
-from the GRFs), temperature and distance from current cell: 
+habitat field with an anisotropic pattern (to simulate a depth gradient) and
+combine it with a temporally dynamic thermal tolerance field to imitate two key
+drivers of population dynamics. Each population was initialised at a single
+location, and subsequently moved across the entire space according to a
+probabilistic distribution based on habitat suitability (represented by the
+normalised values from the GRFs), temperature and distance from current cell: 
 \begin{equation}
@@
 from the port to the fishing grounds. Then a vessel chooses randomly from the
-top 75 \% of fishing events as defined by the expected profit, that has a
-seasonal component.
+top 70 \% of fishing events (defined as the `threshold') in terms of expected
+profit within that season.
 
@@
 \clearpage
-\footnotesize
 \input{F_changes.tex}
 
+\clearpage
 \input{Temp_proportions.tex}
@@
 		populations at four time steps. The darker the colour the
-		greater the density of the population. Note that you can see
-		the diagonal isotropic patterns in populations 2 and 3 and
-		concentrated spawning areas in the second row of the panels
+		greater the density of the population. Note that a diagonal
+		anisotropic pattern representing a depth gradient can be
+		clearly seen in populations 2 and 3. The concentrated spawning
+		areas are also visible in the second row of the panels
 		(t=18).}
@@
 		single vessel during a trip overlaid on the revenue of a
-		fishing site (catch x price); (B) the fishing locations of the
-		vessel over several trips (value field changes over the period
-		so not shown). Note that the field is wrapped on a torus so
-		that distances between opposite side of the spatial domain are
-		considered next to each other, hence apparent large movements;
+		fishing site (landings x price); (B) the fishing locations of
+		the vessel over several trips (value field changes over the
+		period so not shown). Note that movements are a mixture of
+		correlated random walk and experience-based, and that the field
+		is wrapped on a torus so that distances between opposite side
+		of the spatial domain are considered next to each other. For
+		these reasons there are moves larger than the step length in D;
 		(C) the locations of multiple vessels from the same fleet

### 2019-09-24 write_up/parameter_tables.tex
JJP updates

--- 2019-07-18 write_up/parameter_tables.tex
@@
 	\centering
-	\caption{Description of variables for population dynamics sub-module}
+	\caption{Description of variables for population and recruitment
+		dynamics sub-modules.}
 	\label{tab: pop_variable}
@@
 		$\tilde{R}_{c,d}$ & is the recruitment in cell $c$ for day $d$ & $d^{-1}$ \\
-		$S_{c,d}$ & is the stock size in cell $c$ for day $d$ & $d^{-1}$ \\
-		$\alpha$ & the maximum recruitment rate & kg  \\
+		$B_{c,d}$ & biomass in cell $c$ for day $d$ & $d^{-1}$ \\
+		$\alpha$ & the maximum recruitment rate (Beverton Holt)
+		or maximum productivity per spawner (Ricker) & kg  \\
 		$\beta$ & the stock size required to produce half the maximum rate
-		of recruitment & kg \\
+		of recruitment (Beverton Holt) or density dependent reduction
+		in productivity per capita of SSB & kg \\
 		\bottomrule
@@
 	\centering
-	\caption{Description of variables for population movement sub-module}
+	\caption{Description of variables for population movement sub-module.}
 	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
@@
 		Variable & Meaning & Units \\
-		\hline
-		\multicolumn{3}{c}{\textbf{Population movement dynamics}} \\
-		\hhline{===}
-		\multicolumn{3}{l}{\textit{Habitat model}} \\
-		\hline
-		a & b & c \\
 		\hline
@@
 		\hline
-		$\lambda$ & decay rate for population movement & - \\
-		$Hab^{2}_{c,p}$ & Square of habitat suitability for cell $c$ and
+		$\lambda$ & Decay rate for population movement & - \\
+		$Hab_{c,p}$ & Habitat suitability for cell $c$ and
 		population $p$ & - \\
-		$Tol_{c,p,wk}$ & Thermal tolerance for population $p$ in cell
-		$c$ at week $wk$ & - \\
-		$d_{IJ}$ & euclidean distance between cell $I$ and cell $J$ & - \\
+		$Tol_{c,wk,p}$ & Thermal tolerance for in cell $c$ at week $wk$
+		for population $p$ & - \\
+		$d_{I,J}$ & Euclidean distance between cell $I$ and cell $J$ & - \\
 		\bottomrule
@@
 	\centering
-	\caption{Description of variables for fleet dynamics sub-module}
+	\caption{Description of variables for fleet dynamics sub-module.}
 	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
@@
 		\hline
-		\multicolumn{3}{c}{\textbf{Short-term fleet dynamics}} \\
-		\hhline{===}
 		$Rev$ & Revenue from fishing tow & \euro \\
@@
 		\hspace{0.1cm} kg$^{-1}$ \\
-		StepL & Step length for vessel & euclidean distance \\
+		Le & Step length for vessel & - \\
 		Br & Bearing & degrees \\
-		$k$ & Concentration parameter for Von mises distribution & - \\
+		$k$ & Concentration parameter for von mises distribution & - \\
 		$\beta_{1}$ & shape parameter for step function & - \\
@@
 \begin{table}[!ht]
-\caption{Population dynamics and movement parameter setting}
+\caption{Population dynamics and movement parameter settings.}
 	\begin{tabular}{ p{4cm } p{2cm} p{2cm} p{2cm} p{2cm}}
@@
 	50,60,30,40; 80,90,90,90 & 30,34,10,20; 60,70,20,30 & 50,55,80,85; 30,40,30,40 \\
-	Spawning multiplier & 10 & 10 & 10 & 10 \\
-	Movement $\lambda$ & 0.1 & 0.1 & 0.1 & 0.1 \\
+	Spawning multiplier = 10 & & & & \\
+	Movement $\lambda$ = 0.1 & & & & \\
 	\hline
@@
 	Starting Biomass & 1e5 & 2e5 & 1e5 & 1e4 \\
-	Beverton-Holt Recruit 'a' & 6 & 27 & 18 & 0.3  \\
-	Beverton-Holt Recruit 'b' & 4 & 4 & 11 & 0.5 \\
+	Beverton-Holt Recruit $\alpha$ & 6 & 27 & 18 & 0.3  \\
+	Beverton-Holt Recruit $\beta$ & 4 & 4 & 11 & 0.5 \\
 	Beverton-Holt Recruit $\sigma^2$ & 0.7 & 0.6 & 0.7 & 0.6 \\
@@
 	Spawn week & 16-18 & 16-19 & 16-18 & 18-20 \\
-	$K$ & 0.3 & 0.3 & 0.3 & 0.3 \\
-	$wt$ & 1 & 1 & 1 & 1 \\
-	$wt_{d-1}$ & 0.1 & 0.1 & 0.1 & 0.1 \\
+	$K$ = 0.3 & & & & \\
+	$wt$ = 1 & & & & \\
+	$wt_{d-1}$ = 0.1 & & & &  \\
 	M (annual) & 0.2 & 0.1 & 0.2 & 0.1 \\
@@
 \begin{table}[!ht]
-\caption{Fleet dynamics parameter setting}
-\begin{tabular}{ p{4cm } p{1cm} p{1cm} p{1cm} p{1cm} p{1cm}}
+\caption{Fleet dynamics parameter setting.}
+\begin{tabular}{ p{4cm } p{1.2cm} p{1.2cm} p{1.2cm} p{1.2cm} p{1.2cm}}
 	\hline
@@
 	\hline
-	Price Pop1 & 100 & 100 & 100 & 100 & 100 \\
-	Price Pop2 & 200 & 200 & 200 & 200 & 200 \\
-	Price Pop3 & 350 & 350 & 350 & 350 & 350 \\
-	Price Pop4 & 600 & 600 & 600 & 600 & 600 \\
-	$Q$ Pop1 & 0.01 & 0.02 & 0.02 & 0.01 & 0.01 \\
-	$Q$ Pop2 & 0.02 & 0.01 & 0.02 & 0.01 & 0.03\\
-	$Q$ Pop3 & 0.01 & 0.02 & 0.02 & 0.01 & 0.02 \\
-	$Q$ Pop4 & 0.02 & 0.01 & 0.02 & 0.05 & 0.01 \\
+	Price $Pr_{p}1$ = 100 & & & & & \\
+	Price $Pr_{p}2$ = 200 & & & & & \\
+	Price $Pr_{p}3$ = 350 & & & & & \\
+	Price $Pr_{p}4$ = 600 & & & & & \\
+	$Q_{p}$ & 0.01 & 0.02 & 0.02 & 0.01 & 0.01 \\
+	$Q_{p}$ & 0.02 & 0.01 & 0.02 & 0.01 & 0.03\\
+	$Q_{p}$ & 0.01 & 0.02 & 0.02 & 0.01 & 0.02 \\
+	$Q_{p}$ & 0.02 & 0.01 & 0.02 & 0.05 & 0.01 \\
 	\hline
@@
 	step function $rate$ & 20 & 30 & 25 & 35 & 20 \\
-	Past Knowledge & T & T & T & T & T \\
-	Past Year \& Month & T & T & T & T & T \\
-	Past Trip & T & T & T & T & T \\
+	Past Knowledge = TRUE & & & & & \\
 	Threshold & 0.7 & 0.7 & 0.7 & 0.7 & 0.7 \\

### 2019-09-24 R/plot_vessel_move.R

@@ -29,6 +29,9 @@ log <- filter(as.data.frame(logs), fleet %in% fleet_no, vessel %in% vessel_no, y
 
 log$trip <- as.factor(log$trip)
 
+## We need to identify trips that are jumps across the taurus
+log$move_type <- ifelse(!is.na(log$stepD), "CRW", "Experience")
+
 if(is.null(fleets_init) | is.null(pop_bios)) {
 
 return(print(ggplot(log, aes(x = x, y = y, group = paste(vessel, trip))) +
@@ -37,8 +40,11 @@ return(print(ggplot(log, aes(x = x, y = y, group = paste(vessel, trip))) +
       expand_limits(y = c(0,sim_init[["idx"]][["ncols"]]), 
 		    x = c(0,sim_init[["idx"]][["nrows"]])) + 
 	     theme(legend.position = "none") + ylab("y distance") + 
-	     xlab("x distance")
+	     xlab("x distance")+ 
+	expand_limits(y = c(0,sim_init[["idx"]][["ncols"]]), 
+		      x = c(0,sim_init[["idx"]][["nrows"]])
 	     ))
+)
 
 }
 

### 2019-09-24 analysis/Plots.R

@@ -58,7 +58,7 @@ ggplot(filter(df, !is.na(data)), aes(x = day, y = data, group = year)) +
 		  colour = "black", size = 1) +  
 	facet_wrap(~pop) +
 	theme_classic() + 
-	ylab(expression(Fishing~mortality~day^{-1})) +
+	ylab(expression(Fishing~mortality~(day^{-1}))) +
 	xlab("Day") 
 	
 ggsave(file = file.path('..', 'write_up', 'Plots', 'f_dynamics.png'), width = 8, height = 8)
@@ -99,9 +99,9 @@ logs <- combine_logs(res[["fleets_catches"]])
 source("../R/plot_vessel_move.R")
 
 p1 <- plot_vessel_move(sim_init = sim, logs = logs, fleet_no = 3, fleets_init = fleets, 
-		 vessel_no = 14,  year_trip = 30, trip_no = 1, pop_bios = res[["pop_bios"]])
+		 vessel_no = 4,  year_trip = 30, trip_no = 1, pop_bios = res[["pop_bios"]])
 
-p2 <- plot_vessel_move(logs = logs, fleet_no = 3, vessel_no = 4, year_trip = 30, trip_no =  1:12)
+p2 <- plot_vessel_move(sim_init = sim, logs = logs, fleet_no = 3, vessel_no = 4, year_trip = 30, trip_no =  1:12)
 
 source("../R/plot_fleet_trip.R")
 

### 2019-09-24 analysis/Plots_Combined.R

@@ -144,14 +144,16 @@ Fs$pop[Fs$pop == "spp_2"] <- "Population 2"
 Fs$pop[Fs$pop == "spp_3"] <- "Population 3"
 Fs$pop[Fs$pop == "spp_4"] <- "Population 4"
 
-Fs$data_type[Fs$data_type == "real_pop"] <- "True Population"
+Fs$data_type[Fs$data_type == "real_pop"] <- "true Population"
 
-Fs <- Fs[c("scenario", "pop", "F before", "F after", "F change", "data_type", "timescale", "resolution")]
+Fs <- Fs[c("scenario", "F after", "F change", "data_type", "timescale", "resolution")]
 
-colnames(Fs) <- c("Scenario No", "Population", "F before", "F after", "% F change", "data type", "timescale", "resolution")
+colnames(Fs) <- c("Scenario No", "F after closure", "% F change", "data type", "timescale", "resolution")
 
 print(xtable(Fs, digits = 2, caption = "Fishing mortality effects of the
-	     closure scenarios (ordered by most effective first)", label =
+	     closure scenarios on population 3 (ordered by most effective
+						first). The fishing mortality
+	     rate before the closure was 1.08.", label =
 	     "tab:6"), caption.placement = "top", file =
 file.path("..","write_up", "F_changes.tex"),include.rownames = FALSE,
 tabular.environment= "longtable", floating = FALSE)

### 2019-09-29 write_up/mixfishsim_ecolmod.tex
Response to JJP comments

@@
 \sum\limits_{fl=1}^{FL}\sum\limits_{v=1}^{V} E_{fl, v, c, d} \cdot Q_{fl} \cdot
-D_{c, d}$ with $fl$ and $v$ the fleet and vessel respectively and
-$E_{fl,v,c,d}$ and $Q_{fl}$ fishing effort and catchability of the gear, and
-$D_{c,d}$ is the density of the population at the location fished. \\
+D_{c, d}$ with $fl$ and $FL$ the fleet and total number of fleets, $v$ and $V$
+the vessel and total number of vessels respectively and $E_{fl,v,c,d}$ and
+$Q_{fl}$ fishing effort and catchability of the gear, and $D_{c,d}$ is the
+density of the population at the location fished. \\
 
@@
 process was employed to model habitat suitability for each of the populations
-on a 2d grid.  We first defined a Gaussian random field process, $\{S(c) : c \in
-\mathbb{R}^2\}$, where for any set of cells $c_{1}, \dots, c_{n}$, the joint
-distribution of $S = \{S(c1),\dots S(c_{n})\}$ is multivariate Gaussian with a
-\textit{Matérn} covariance structure, where the correlation strength weakens
-with distance. This enables us to model the spatial autocorrelation observed in
-animal populations where density is more similar in nearby locations
-\citep{Tobler1970, F.Dormann2007, Poos2007} and we change the parameters to
-implement different spatial structures for the different populations using the
-\textit{RandomFields} R package \citep{Schlater2015}. We define a stationary
-habitat field with an anisotropic pattern (to simulate a depth gradient) and
-combine it with a temporally dynamic thermal tolerance field to imitate two key
-drivers of population dynamics. Each population was initialised at a single
-location, and subsequently moved across the entire space according to a
-probabilistic distribution based on habitat suitability (represented by the
-normalised values from the GRFs), temperature and distance from current cell: 
+on a 2d grid.  We first defined a Gaussian random field process, $\{S(c) : c
+\in \mathbb{R}^2\}$, where for any set of cells $c_{1}, \dots, c_{n}$, the
+joint distribution of $S = \{S(c1),\dots S(c_{n})\}$ is multivariate Gaussian
+with a \textit{Matérn} covariance structure, where the correlation strength
+weakens with distance controlled by two parameters, with $\nu$ a scale
+parameter in the units of distance and $\kappa$ a shape parameter which
+determines the smoothness of the process. This enables us to model the spatial
+autocorrelation observed in animal populations where density is more similar in
+nearby locations \citep{Tobler1970, F.Dormann2007, Poos2007} and we change the
+parameters to implement different spatial structures for the different
+populations using the \textit{RandomFields} R package \citep{Schlater2015}. We
+define a stationary habitat field with an anisotropic pattern (to simulate a
+depth gradient) and combine it with a temporally dynamic thermal tolerance
+field to imitate two key drivers of population dynamics without modelling the
+processes explicitly. Each population was initialised at a single location, and
+subsequently moved across the entire space according to a probabilistic
+distribution based on habitat suitability (represented by the normalised values
+from the GRFs), temperature and distance from current cell: 
 \begin{equation}
@@
 
-\subsubsection{Decision about where to fish at the start of the trip}
-
-Several studies \citep[for a review]{Girardin2016} have confirmed past activity
+\subsubsection{Decision about where to fish at the start of a trip}
+
+Several studies \citep[for a review see][]{Girardin2016} have confirmed past activity
 and past catch rates are strong predictors of fishing location choice. For this
@@
 
-\subsubsection{Decision about where to fish within the trip}
+\subsubsection{Decision about where to fish within a trip}
 
@@
 shape of the step function in its relation to revenue, so that, a step from
-(x1,y1) to (x2, y2) is defined by:
+($x_{t}$,$y_{t}$) to ($x_{t+1}$, $y_{t+1}$) is defined by:
 \begin{equation}
 	\begin{split}
- (x2, y2) =  & x1 + Le \cdot \cos \left(\frac{\pi \cdot Br}{180}\right), \\
-             & y1 + Le \cdot \sin \left(\frac{\pi \cdot Br}{180}\right) \\	
- with  \hspace{0.5cm}     & Br_{t-1} < 180, Br_{t} = 180 + \sim vm[(0,360), k] \\
- 			  & Br_{t-1} > 180, Br_{t} = 180 - \sim vm[(0,360), k] \\
+ (x_{t+1}, y_{t+1}) =  & x_{t} + Le \cdot \cos \left(\frac{\pi \cdot
+		 Br_{t+1}}{180}\right), \\ & y_{t} + Le \cdot \sin
+ \left(\frac{\pi \cdot Br_{t+1}}{180}\right) \\	
+ when  \hspace{0.5cm}     & Br_{t} < 180, Br_{t+1} = 180 + \sim vm[(0,360), k] \\
+ 			  & Br_{t} > 180, Br_{t+1} = 180 - \sim vm[(0,360), k] \\
 	\end{split}
 \end{equation}
-where $Le$ is the step length, $k$ the concentration parameter from the von
-Mises distribution that we correlate with the revenue so that $k = (Rev + 1 /
-RefRev) \cdot max_{k}$, where $max_{k}$ is the maximum concentration value,
-$k$, and $RefRev$ is parametrised as for $\beta_{3}$ in the step length
-function.
+where $Le$ is the step length, $Br_t$ is the bearing at time $t$, $k$ the
+concentration parameter from the von Mises distribution that we correlate with
+the revenue so that $k = (Rev + 1 / RefRev) \cdot max_{k}$, where $max_{k}$ is
+the maximum concentration value, $k$, and $RefRev$ is parametrised as for
+$\beta_{3}$ in the step length function.
 
@@
 		greater the density of the population. Note that a diagonal
-		anisotropic pattern representing a depth gradient can be
+		anisotropic pattern (mimicking a depth gradient) can be
 		clearly seen in populations 2 and 3. The concentrated spawning
@@
 		period so not shown). Note that movements are a mixture of
-		correlated random walk and experience-based, and that the field
-		is wrapped on a torus so that distances between opposite side
-		of the spatial domain are considered next to each other. For
-		these reasons there are moves larger than the step length in D;
-		(C) the locations of multiple vessels from the same fleet
-		overlaid on the value field, (D) the realised step distance and
-		turning angles for a single vessel over the simulation.}
+		correlated random walk (solid lines) and experience-based
+		(dashed lines), and that the field is wrapped on a torus so
+		that opposite sides of the spatial domain are considered next
+		door; (C) the locations of multiple vessels from the
+		same fleet overlaid on the value field, (D) the realised step
+		distance and turning angles for a single vessel over the
+		simulation.}
 	\label{fig:mv}

### 2019-09-29 write_up/parameter_tables.tex
Response to JJP comments

@@
 		\hline
-		$T_{c,wk}$ & Temperature for cell in week & $^\circ$C \\
-		$\mu_{p}$ & Mean of the thermal tolerance for population & $^\circ$C \\
+		$T_{c,wk}$ & Temperature for cell $c$ in week $wk$ & $^\circ$C \\
+		$\mu_{p}$ & Mean of the thermal tolerance for population $p$ & $^\circ$C \\
 		$\sigma^{2}_{p}$ & Standard deviation of thermal tolerance for
-		the population & $^\circ$C \\
+		population $p$ & $^\circ$C \\
 		\hline
@@
 		Le & Step length for vessel & - \\
-		Br & Bearing & degrees \\
+		$Br$ & Bearing & degrees \\
 		$k$ & Concentration parameter for von mises distribution & - \\
@@
 	step function $\beta_2$ & 10 & 15 & 8 & 12 & 7 \\
-	step function $\beta_3$ & Q90 & Q90 & Q85 & Q90 & Q80 \\
+	step function $\beta_3$, the landings value $nth$ quantile &
+	90 & 90 & 85 & 90 & 80 \\
 	step function $rate$ & 20 & 30 & 25 & 35 & 20 \\

### 2019-09-29 R/plot_fleet_trip.R

@@ -25,10 +25,18 @@ log <- filter(as.data.frame(logs), fleet %in% fleet_no, year %in% year_trip, tri
 
 log$vessel <-as.factor(log$vessel)
 
+## We need to identify trips that are jumps across the taurus
+log$move_type[2:nrow(log)] <- ifelse(!is.na(log$stepD[1:(nrow(log)-1)]), "CRW", "Experience")
+log$move_type[2:nrow(log)] <- ifelse(log$move_type[2:nrow(log)] == "CRW" & log$stepD[1:(nrow(log)-1)] > 10, "OutsideMove", log$move_type[2:nrow(log)])
+
+
+
 if(is.null(pop_bios)) {
 print(ggplot(log, aes(x = x, y = y)) + 
       geom_point(aes(colour = vessel)) +
-      geom_path(aes(colour = vessel)) + 
+      geom_path(data = filter(log, move_type == "CRW"), aes(colour = vessel)) +
+      geom_path(data = filter(log, move_type == "Experience"), aes(colour = vessel)) +
+      geom_path(data = filter(log, move_type == "OutsideMove"), aes(colour = vessel)) +
       theme_bw() + xlab("x distance") + ylab("y distance")
       )
 }
@@ -57,7 +65,9 @@ TotValDF$y <- rep(seq_len(sim_init[["idx"]][["ncols"]]), each = sim_init[["idx"]
 print(ggplot(TotValDF, aes(x = x, y = y)) + geom_tile(aes(fill = value)) +
 	scale_fill_gradient2(low = "blue", high = "darkblue") +
 	geom_point(data = log, aes(colour = vessel)) +
-        geom_path(data = log, aes(colour = vessel)) + 
+	geom_path(data = filter(log, move_type == "CRW"), aes(colour = vessel), linetype = "solid") +
+      	geom_path(data = filter(log, move_type == "Experience"), aes(colour = vessel), linetype = "longdash") +
+      	geom_path(data = filter(log, move_type == "OutsideMove"), aes(colour = vessel), linetype = "twodash") +
 	theme_bw() + #scale_colour_gradient(low = "red", high = "darkred") + 
 	expand_limits(y = c(0,sim_init[["idx"]][["ncols"]]), 
 		      x = c(0,sim_init[["idx"]][["nrows"]])) +

### 2019-09-29 R/plot_vessel_move.R

@@ -31,12 +31,16 @@ log$trip <- as.factor(log$trip)
 
 ## We need to identify trips that are jumps across the taurus
 log$move_type <- ifelse(!is.na(log$stepD), "CRW", "Experience")
+log$move_type <- ifelse(log$move_type == "CRW" & log$stepD > 10, "OutsideMove", log$move_type)
 
 if(is.null(fleets_init) | is.null(pop_bios)) {
 
 return(print(ggplot(log, aes(x = x, y = y, group = paste(vessel, trip))) +
       geom_point(aes(colour = trip)) +
-      geom_path(aes(colour = trip))+ theme_bw() +
+      geom_path(data = filter(log, move_type == "CRW"),aes(colour = trip), linetype = "solid")+ 
+      geom_path(data = filter(log, move_type == "Experience"),aes(colour = trip), linetype = "longdash")+ 
+      geom_path(data = filter(log, move_type == "OutsideMove"),aes(colour = trip), linetype = "twodash")+ 
+      theme_bw() +
       expand_limits(y = c(0,sim_init[["idx"]][["ncols"]]), 
 		    x = c(0,sim_init[["idx"]][["nrows"]])) + 
 	     theme(legend.position = "none") + ylab("y distance") + 

### 2019-10-06 write_up/mixfishsim_ecolmod.tex
Response to JJP comments

@@
 parameters (Table \ref{tab:1}). Habitat preference (Figure \ref{S-fig:1}) and
-temperature tolerances (Figures \ref{S-fig:3}, \ref{S-fig:4}) were defined to
-be unique to each population resulting in differently weekly distribution
-patterns (Figures \ref{S-fig:5}-\ref{S-fig:7}). In addition, each of the
-populations was assumed to have two defined spawning areas that result in the
-populations moving towards these areas in pre-defined weeks (Figure
+temperature (Figures \ref{S-fig:3}, with temperature tolerance \ref{S-fig:4})
+defined to be unique to each population resulting in differently weekly
+distribution patterns (Figures \ref{S-fig:5}-\ref{S-fig:7}). In addition, each
+of the populations was assumed to have two defined spawning areas that result
+in the populations moving towards these areas in pre-defined weeks (Figure
 \ref{S-fig:2}) with population-specific movement rates (Table \ref{tab:1}).
@@
 Survey closures were on an annual basis only, as this was the most temporally
-resolved survey data available.
+resolved survey data available. We evaluated the factors contributing to the
+success of the closures through a regression tree (using the R package REEMtree
+\citep{Sela2012}) to identify the factor most contributing to differences in
+fishing mortality before and after the closure.
 
@@
 populations in the catch having similar mean and standard deviations.  In the
-weekly data population 1 = 9.36 (3.99), population 2 = 83.2 (5.60), population
-3 = 3.57 (1.23), population 4 = 3.91 (1.59); in the monthly data population 1 =
-9.23 (3.87), population 2 = 83.3 (5.52), population 3 = 3.62 (1.15), population
-4 = 3.86 (1.52). While means were similar some of the variation was lost when
-aggregated to an annual level; population 1 = 9.90 (0.173), population 2 = 82.2
-(0.308), population 3 = 3.82 (0.119), population 4 = 4.03 (0.0502).\\
+weekly data population 1 = 9.36\% (SD = 3.99), population 2 = 83.2\% (5.60),
+population 3 = 3.57\% (1.23), population 4 = 3.91\% (1.59); in the monthly data
+population 1 = 9.23\% (3.87), population 2\% = 83.3 (5.52), population 3 =
+3.62\% (1.15), population 4 = \%3.86 (1.52). While means were similar some of
+the variation was lost when aggregated to an annual level; population 1 =
+9.90\% (0.173), population 2 = 82.2\% (0.308), population 3 = 3.82\% (0.119),
+population 4 = 4.03\% (0.0502).\\
 
@@
 compositions were nearly identical, with monthly composition of population 1 =
-0.0472 (0.0139), population 2 = 94.4 (1.47), population 3 = 3.12 (1.47),
-population 4 = 2.40 (0.444). Again, yearly values head a similar mean but
+0.0472\% (0.0139), population 2 = 94.4\% (1.47), population 3 = 3.12\% (1.47),
+population 4 = 2.40\% (0.444). Again, yearly values head a similar mean but
 smaller standard deviation.\\
@@
 The survey data was only available on an annual basis, and showed again a
-slightly different composition; population 1 = 0.372 (0.00473), population 2 =
-87.7 (0.193), population 3 = 0.729 (0.0200), population 4 = 11.2 (0.172).
+slightly different composition; population 1 = 0.372\% (0.00473), population 2
+= 87.7\% (0.193), population 3 = 0.729\% (0.0200), population 4 = 11.2\%
+(0.172).
 
@@
 
-The trend in fishing mortality for each species show that in most cases the
-fishery closure was successful in reducing fishing mortality on the species of
-interest (population 3; Figure \ref{fig:3}), though interestingly the largest
-reductions in fishing mortality happened immediately after the closures,
-following which the fisheries ``adapted" to the closures and fishing mortality
-increased again somewhat. The exception to the success was the closures
-implemented based on the coarsest spatial (20 x 20) and temporal resolution
-(yearly) that was ineffective with all data sources. As expected, closures
-based on the ``known" population distribution were most effective, with
-differing degrees of success using the commercial data. Fishing mortality rates
-on the other species changed in different proportions, depending on whether the
-displaced fishing effort moved to areas where the populations were found in
-greater or lesser density. \\
-
-A regression tree (using the R package REEMtree \citep{Sela2012}) highlights
-that the factor most contributing to differences in fishing mortality before
-and after the closure was the population (72 \% showing that the closures were
+In most cases the fishery closure was successful in reducing fishing mortality
+on the species of interest (population 3; Figure \ref{fig:3}), though
+interestingly the largest reductions in fishing mortality happened immediately
+after the closures, following which the fisheries ``adapted" to the closures
+and fishing mortality increased again somewhat. The exception to the success
+was the closures implemented based on the coarsest spatial (20 x 20) and
+temporal resolution (yearly) that was ineffective (i.e. failed to reduce
+fishing mortality) with all data sources. As expected, closures based on the
+``known" population distribution were most effective, with differing degrees of
+success using the commercial data. Fishing mortality rates on the other species
+changed in different proportions, depending on whether the displaced fishing
+effort moved to areas where the populations were found in greater or lesser
+density. \\
+
+The factor most contributing to differences in fishing mortality before and
+after the closure was the population (72 \% showing that the closures were
 effective for population 3), followed by data resolution (21 \%), data type (7
@@
 %% General intro
-Our study presents a new highly resolved fisheries simulation framework,
-evaluates the importance of data scaling and considers potential bias
-introduced through data aggregation when using fisheries data to infer
-spatiotemporal dynamics of fish populations. Understanding how fishers exploit
-multiple heterogeneously distributed fish populations with different catch
-limits or conservation status requires detailed understanding of the overlap of
+Our study presents a new highly resolved fisheries simulation framework to
+evaluate the importance of data scaling and considers potential bias introduced
+through data aggregation when using fisheries data to infer spatiotemporal
+dynamics of fish populations. Understanding how fishers exploit multiple
+heterogeneously distributed fish populations with different catch limits or
+conservation status requires detailed understanding of the overlap of
 resources; this is difficult to achieve using conventional modelling approaches
@@
 spatiotemporal closures were considered to have some effect in reducing cod
-mortality without having to disrupt other fisheries significantly
+mortality without having to disrupt other fisheries substantially
 \citep{Needle2011}. These examples emphasise the importance of considering the
@@
 
-We model the population and fleet dynamic processes to draw inference on the
+We modelled the population and fleet dynamic processes to draw inference on the
 importance of data scale and aggregation in understanding and managing mixed
-fisheries and their impact on multiple fish populations. In doing so, we have
+fisheries and their impact on multiple fish populations. In doing so, we
 necessarily had to make a number of simplifying assumptions. \\
@@
 		(dashed lines), and that the field is wrapped on a torus so
-		that opposite sides of the spatial domain are considered next
-		door; (C) the locations of multiple vessels from the
+		that opposite sides of the spatial domain are considered
+		spatially close; (C) the locations of multiple vessels from the
 		same fleet overlaid on the value field, (D) the realised step

### 2019-10-06 write_up/mixfishsim_ecolmod.tex
Added new plot

@@
 species was not found (Figure \ref{fig:17}) that may have consequences in terms
-of restricting the fishery in a much larger area than necessary. \\
+of restricting the fishery in a much larger area than necessary. We found that
+these trade-offs existed, with high catches maintained with an effective
+closure when the highest resolution data was used, with the effect being linear
+when the true population distribution was known and also persisting for
+closures based on commercial information (Figure \ref{fig:ce}).\\
 
@@
 spatial and temporal resolution is associated with reduced effectiveness and
-potentially closing fishing opportunities for other fisheries. \\
+potentially closing fishing opportunities for other fisheries (Figure
+\ref{fig:ce}). \\
 
@@
 \end{figure}
+
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width =\linewidth]{./Plots/Closure_effectiveness_CF}
+	\caption{Effectiveness of closure with regards to reducing fishing
+		mortality on protected population (further left on x-axis is
+		best) and maintaining high catches in the fishery (highest on
+		y-axis is best). The grey line indicates the direction of the
+		trade-off between reducing fishing mortality and overall
+		catches.}
+	\label{fig:ce}
+\end{figure}
+
 %\end{comment}

### 2019-10-06 analysis/Plots_Combined.R

@@ -267,4 +267,26 @@ ggsave('C_trendsREV.png', width = 10, height = 8)
 
 
 
+####################################################
+#
+# F population 3 vs total catch
+#
+####################################################
 
+## Closure year starts at 30
+
+
+z_f <- filter(combined_pop_an, basis == "high_pop", metric %in% "F", pop == "Population 3", as.numeric(year) > 39) %>%
+	group_by(scenario, timescale, res, data_type) %>% summarise(f = mean(data))
+
+z_c <- filter(combined_pop_an, basis == "high_pop", metric == "Catch", as.numeric(year) > 39) %>%
+	group_by(scenario, timescale, res, data_type, year) %>% summarise(catch = sum(data)) %>%
+	group_by(scenario, timescale, res, data_type) %>% summarise(catch = mean(catch))
+
+ z <- merge(z_f, z_c, by = c("scenario","timescale", "res", "data_type"))
+
+ggplot(z, aes(x = f, y = catch)) +
+	geom_text(aes(colour = timescale, label = res)) +
+	facet_wrap(~data_type) + stat_ellipse(aes(colour = res, group = timescale)) +
+	theme_bw() + xlab("mean F on population 3 (year 39 - 50)") +
+	ylab("mean catch all populations (year 39 - 50)")

### 2019-10-08 write_up/Supplementary.tex
Text updates to JJP

@@
 
-\title{MixFishSim: Supplementary Figures and Tables}
+\title{MixFishSim: Supplementary Figures}
 
@@
 	\includegraphics[width = \linewidth]{../analysis/habitat}
-	\caption{habitat preference}
+	\caption{Habitat preference: the distribution of suitable habitat for
+		each population, with the darker colour showing greater
+		suitability.}
 	\label{fig:1}
@@
 	\includegraphics[width = \linewidth]{../analysis/habitat_spwn}
-	\caption{spawning habitat preference}
+	\caption{Spawning habitat preference: the habitat suitability during
+		spawning periods for each population.}
 	\label{fig:2}
@@
 	\includegraphics[width = \linewidth]{Plots/Temperature_gradient}
-	\caption{Spatiotemporal temperature gradient}
+	\caption{Spatiotemporal temperature gradient: The temperature gradient
+	for each time step (weeks, shown in top right corner of each panel.)}
 	\label{fig:3}
@@
 	\includegraphics[width = \linewidth]{Plots/Species_tolerances}
-	\caption{Species thermal tolerances}
+	\caption{Species thermal tolerances: The tolerance of each population
+		to different temperatures (x-axis) shown as a probability
+		density function.}
 	\label{fig:4}
@@
 	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_1}
-	\caption{Spatiotemporal habitat suitability - population 1}
+	\caption{Spatiotemporal habitat suitability - the suitability habitat
+		(for Population 1) for 52 separate weeks.}
 	\label{fig:5}
@@
 	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_2}
-	\caption{Spatiotemporal habitat suitability - population 2}
+	\caption{Spatiotemporal habitat suitability - the suitability habitat
+		(for Population 2) for 52 separate weeks.}
 	\label{fig:6}
@@
 	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_3}
-	\caption{Spatiotemporal habitat suitability - population 3}
+	\caption{Spatiotemporal habitat suitability - the suitability habitat
+		(for Population 3) for 52 separate weeks}
 	\label{fig:7}
@@
 	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_4}
-	\caption{Spatiotemporal habitat suitability - population 4}
+	\caption{Spatiotemporal habitat suitability - the suitability habitat
+		(for Population 4) for 52 separate weeks}
 	\label{fig:8}

### 2019-10-08 write_up/mixfishsim_ecolmod.tex
Update figure
Text updates to JJP

@@
 distribution based on habitat suitability (represented by the normalised values
-from the GRFs), temperature and distance from current cell: 
+from the GRFs), temperature tolerance and distance from current cell: 
 \begin{equation}
@@
 Where $d_{I,J}$ is the euclidean distance between cell $I$ and cell $J$,
-$\lambda$ is a given rate of decay, $Hab_{c,p}^2$ is the squared index of
-habitat suitability for cell $c$ and population $p$, with $Tol_{c,p,wk}$ the
-temperature tolerance for cell $c$ by population $p$ in week $wk$ (see
-below). \\
+$\lambda$ is a given rate of decay, $Hab_{c,p}$ is the index of habitat
+suitability for cell $c$ and population $p$, with $Tol_{c,p,wk}$ the
+temperature tolerance for cell $c$ by population $p$ in week $wk$ (see below).
+\\
 
@@
 suitable habitat on a weekly time-step. Each population $p$ was assigned a
-thermal tolerance with mean, $\mu_{p}$ and variance, $\sigma^2_{p}$ so that
-each cell and population temperature suitability is defined that:
+thermal tolerance with mean, $\mu_{p}$ and standard deviation, $\sigma_{p}$ so that
+each cell and population temperature tolerance is defined that:
 \begin{equation}
@@
 $wk$, $T_{c, wk}$ is the temperature in the cell given the week and $\mu_{p}$
-and $\sigma^2_{p}$ the mean and standard deviation of the population
-temperature tolerance. \\
+and $\sigma_{p}$ the mean and standard deviation of the population temperature
+tolerance. \\
 
@@
 		best) and maintaining high catches in the fishery (highest on
-		y-axis is best). The grey line indicates the direction of the
+		y-axis is best). The numbers indicate the spatial resolution of
+		the data, while grey lines indicate the direction of the
 		trade-off between reducing fishing mortality and overall

### 2019-10-08 write_up/parameter_tables.tex
Small update to Table 4
Text updates to JJP

@@
 		$\mu_{p}$ & Mean of the thermal tolerance for population $p$ & $^\circ$C \\
-		$\sigma^{2}_{p}$ & Standard deviation of thermal tolerance for
+		$\sigma_{p}$ & Standard deviation of thermal tolerance for
 		population $p$ & $^\circ$C \\
@@
 	\hline
-	$\mu$ & 12 & 15 & 17 & 14 \\
-	$\sigma^2$ & 8 & 9 & 7 & 10 \\
+	$\mu_{p}$ & 12 & 15 & 17 & 14 \\
+	$\sigma_{p}^2$ & 8 & 9 & 7 & 10 \\
 	\hline

### 2019-10-11 write_up/cover_letter.tex
Adding cover letter and highlights

\documentclass[12pt]{letter}
\usepackage[margin=2.54cm, a4paper]{geometry}
\signature{\vspace*{-1cm} 
	Paul Dolder \\ 
	Dr C\'oil\'in Minto\\ 
	Prof Jean-Marc Guarini \\
	Dr Jan Jaap Poos}
\address{Paul Dolder \\
	Marine and Freshwater Research Centre \\ 
	Galway-Mayo Institute of Technology \\ 
	Dublin Road \\ 
	Galway \\ 
	Ireland}

\begin{document}

\begin{letter}{Prof. Brian D. Fath \\ Department of Biological Sciences \\
		Towson University \\ 8000 York Road \\ Towson \\ Maryland 21252 \\ USA}
\opening{Dear Professor Fath,}

We would like to submit an \emph{Original research} paper titled \emph{`Highly
	resolved spatiotemporal simulations for exploring mixed fisheries
	dynamics'} for consideration in \emph{Ecological modelling}. In this
paper we develop and apply a simulation model of a ecological-fishery system
where individual fishing vessels exploit multiple heterogeneously distributed
fish stocks with full spatiotemporal population dynamics. In it we explore the
importance of spatial and temporal scale when modelling fishery interactions,
particularly in relation to modelling observational data from a system with
preferential sampling.\\

Our study tackles the issue of how fishers exploit a dynamic natural resource
with uncertain knowledge of its distribution. We detail how this affects our
understanding of the fisheries interactions with multiple fish populations,
which cannot be achieved with a conventional modelling approach. By capturing
dynamics observed in fisheries data in a novel simulation model where the
entire dynamics of the system (including the true spatial distribution of the
populations) are known, we expose that degrading the spatial and temporal
resolution of data through aggregation reduces our ability to define effective
spatial management measures. This would not of been possible without the highly
details and resolved simulation approach used here. The model has many
potential additional applications which we discuss, with the model made
available as an R software package for users to explore.\\

Should you consider our work suitable for review, we would like to suggest the
following associate editor and potential reviewers with a rationale below each:

\begin{itemize} 
	\item {\bf Associate Editor} Prof. Terrance Quinn II, College of
		Fisheries and Oceans, University of Fairbanks, Alaska
		(tjquinnii@alaska.edu).\\ 
	\item {\bf Reviewer} Dr David Peel, Commonwealth Scientific and
		Industrial Research Organisation (CSIRO), Castray Esplanade,
		Hobart TAS 7000, Australia (david.peel@csiro.au). \\
		Established expert in finite mixture modelling.  
	\item {\bf Reviewer} Dr John Morrengiello, University of Melbourne,
		Melbourne, Australia (john.morrongiello@unimelb.edu.au) \\
		Early career scientist with expertise in quantitative aquatic
		ecology and evolution along with publications on growth
		modelling.  
	\item {\bf Reviewer} Dr Ken Newman, U.S. Fish and Wildlife Service,
		Lodi Fish and Wildlife Office, 850 Guild Avenue, Lodi, CA
		95240, USA (Ken\_Newman@fws.gov)\\ Established expert in
		mathematical and applied statistics with application to natural
		resource management.  
\end{itemize}

Thank you for your time and consideration.

\closing{Yours Sincerely,} \end{letter}

\end{document}

### 2019-10-11 write_up/highlights.tex
Adding cover letter and highlights

--- 2019-10-11 write_up/cover_letter.tex
@@
-\documentclass[12pt]{letter}
-\usepackage[margin=2.54cm, a4paper]{geometry}
-\signature{\vspace*{-1cm} 
-	Paul Dolder \\ 
-	Dr C\'oil\'in Minto\\ 
-	Prof Jean-Marc Guarini \\
-	Dr Jan Jaap Poos}
-\address{Paul Dolder \\
-	Marine and Freshwater Research Centre \\ 
-	Galway-Mayo Institute of Technology \\ 
-	Dublin Road \\ 
-	Galway \\ 
-	Ireland}
+\documentclass{article}
 
@@
 
-\begin{letter}{Prof. Brian D. Fath \\ Department of Biological Sciences \\
-		Towson University \\ 8000 York Road \\ Towson \\ Maryland 21252 \\ USA}
-\opening{Dear Professor Fath,}
+\begin{itemize}
 
-We would like to submit an \emph{Original research} paper titled \emph{`Highly
-	resolved spatiotemporal simulations for exploring mixed fisheries
-	dynamics'} for consideration in \emph{Ecological modelling}. In this
-paper we develop and apply a simulation model of a ecological-fishery system
-where individual fishing vessels exploit multiple heterogeneously distributed
-fish stocks with full spatiotemporal population dynamics. In it we explore the
-importance of spatial and temporal scale when modelling fishery interactions,
-particularly in relation to modelling observational data from a system with
-preferential sampling.\\
+	\item one
+	\item two
+	\item three
+	\item four
+	\item five 
+	\item six
 
-Our study tackles the issue of how fishers exploit a dynamic natural resource
-with uncertain knowledge of its distribution. We detail how this affects our
-understanding of the fisheries interactions with multiple fish populations,
-which cannot be achieved with a conventional modelling approach. By capturing
-dynamics observed in fisheries data in a novel simulation model where the
-entire dynamics of the system (including the true spatial distribution of the
-populations) are known, we expose that degrading the spatial and temporal
-resolution of data through aggregation reduces our ability to define effective
-spatial management measures. This would not of been possible without the highly
-details and resolved simulation approach used here. The model has many
-potential additional applications which we discuss, with the model made
-available as an R software package for users to explore.\\
-
-Should you consider our work suitable for review, we would like to suggest the
-following associate editor and potential reviewers with a rationale below each:
-
-\begin{itemize} 
-	\item {\bf Associate Editor} Prof. Terrance Quinn II, College of
-		Fisheries and Oceans, University of Fairbanks, Alaska
-		(tjquinnii@alaska.edu).\\ 
-	\item {\bf Reviewer} Dr David Peel, Commonwealth Scientific and
-		Industrial Research Organisation (CSIRO), Castray Esplanade,
-		Hobart TAS 7000, Australia (david.peel@csiro.au). \\
-		Established expert in finite mixture modelling.  
-	\item {\bf Reviewer} Dr John Morrengiello, University of Melbourne,
-		Melbourne, Australia (john.morrongiello@unimelb.edu.au) \\
-		Early career scientist with expertise in quantitative aquatic
-		ecology and evolution along with publications on growth
-		modelling.  
-	\item {\bf Reviewer} Dr Ken Newman, U.S. Fish and Wildlife Service,
-		Lodi Fish and Wildlife Office, 850 Guild Avenue, Lodi, CA
-		95240, USA (Ken\_Newman@fws.gov)\\ Established expert in
-		mathematical and applied statistics with application to natural
-		resource management.  
 \end{itemize}
 
-Thank you for your time and consideration.
-
-\closing{Yours Sincerely,} \end{letter}
-
 \end{document}

### 2019-10-11 write_up/mixfishsim_ecolmod.tex
Adding cover letter and highlights

@@
 \cortext[c]{Corresponding author}
-\ead{paul.dolder@gmit.ie}
+\ead{paul.dolder@research.gmit.ie}
 
@@
 \begin{keyword}
-Some\sep keywords \sep here. Max 6 
+spatiotemporal \sep mixed fisheries \sep individual based \sep spatial
+management \sep homogeneity \sep  preferential sampling
 \MSC[2010] 00-01\sep  99-00
@@
 program (MARES\_14\_15) and the Centre for Environment, Fisheries and
-Aquaculture Science seedcorn program (DP227AC).
+Aquaculture Science seedcorn program (DP227AC). The authors declare no
+competing interests.
+
+\section*{CRediT author statement} \textbf{Paul Dolder:} Conceptualisation,
+methodology, software, writing - original draft. \textbf{Cóilín Minto:}
+Conceptualisation, Methodology, writing - review and editing, supervision,
+funding acquisition. textbf{Jean-Marc Guarini:} methodology, writing - review
+and editing, funding acquisition, supervision. \textbf{Jan Jaap Poos:}
+methodology, writing - review and editing, supervision. \
 
@@
 	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_space_Rev2}
-	\caption{Data aggregation at different spatial resolutions over a
+	\caption{[Colour] Data aggregation at different spatial resolutions over a
 		ten year period.}
@@
 	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_time_Rev2}
-	\caption{Proportion of each population (y axis) for data aggregated at
+	\caption{[Colour]Proportion of each population (y axis) for data aggregated at
 		different temporal resolutions. Data is aggregated over a
@@
 	\includegraphics[width = \linewidth]{../analysis/F_trendsREV}
-	\caption{Comparison of closure scenarios effect on fishing mortality
+	\caption{[Colour]Comparison of closure scenarios effect on fishing mortality
 		trends. Line colour denotes timescale, while linestyle
@@
 	\includegraphics[width =\linewidth]{./Plots/Closure_effectiveness_CF}
-	\caption{Effectiveness of closure with regards to reducing fishing
+	\caption{[Colour]Effectiveness of closure with regards to reducing fishing
 		mortality on protected population (further left on x-axis is

### 2019-10-13 write_up/cover_letter.tex
Remove the covering letter

@@
 	dynamics'} for consideration in \emph{Ecological modelling}. In this
-paper we develop and apply a simulation model of a ecological-fishery system
-where individual fishing vessels exploit multiple heterogeneously distributed
-fish stocks with full spatiotemporal population dynamics. In it we explore the
-importance of spatial and temporal scale when modelling fishery interactions,
-particularly in relation to modelling observational data from a system with
-preferential sampling.\\
+paper we develop a simulation model (\emph{MixFishSim}) of a ecological-fishery
+system where individual fishing vessels exploit multiple heterogeneously
+distributed fish populations with full spatiotemporal population dynamics.
+Using\emph{MixFishSim} we address critically important sampling issues which as
+the importance of spatial and temporal scale when modelling fishery
+interactions, particularly in relation to modelling observational data from a
+system with preferential sampling.\\
 
-Our study tackles the issue of how fishers exploit a dynamic natural resource
-with uncertain knowledge of its distribution. We detail how this affects our
-understanding of the fisheries interactions with multiple fish populations,
-which cannot be achieved with a conventional modelling approach. By capturing
-dynamics observed in fisheries data in a novel simulation model where the
-entire dynamics of the system (including the true spatial distribution of the
-populations) are known, we expose that degrading the spatial and temporal
-resolution of data through aggregation reduces our ability to define effective
-spatial management measures. This would not of been possible without the highly
-details and resolved simulation approach used here. The model has many
-potential additional applications which we discuss, with the model made
-available as an R software package for users to explore.\\
+Our approach incorporates, in an emergent manner, how fishers exploit a dynamic
+natural resource with uncertain knowledge of its distribution. We detail how
+this affects our understanding of the fisheries interactions with multiple fish
+populations, which cannot be achieved with conventional modelling approaches.
+By capturing dynamics observed in fisheries data in a novel simulation model
+where the entire dynamics of the system (including the true spatial
+distribution of the populations) are known, we expose that degrading the
+spatial and temporal resolution of data through aggregation reduces our ability
+to define effective spatial management measures. This would not of been
+possible without the highly details and resolved simulation approach used here.
+The framework has many potential additional applications (e.g. monitoring
+survey design, index standardisation for fisheries assessment, in-year fishery
+and biological modelling, testing adaptive management approaches, comparison of
+heuristic and mechanistic fishery effort dynamics models among others).
+MixFishSim is made available as a documented R software package for users to
+explore.\\
 
 Should you consider our work suitable for review, we would like to suggest the
-following associate editor and potential reviewers with a rationale below each:
+following potential reviewers:
 
 \begin{itemize} 
-	\item {\bf Associate Editor} Prof. Terrance Quinn II, College of
-		Fisheries and Oceans, University of Fairbanks, Alaska
-		(tjquinnii@alaska.edu).\\ 
-	\item {\bf Reviewer} Dr David Peel, Commonwealth Scientific and
-		Industrial Research Organisation (CSIRO), Castray Esplanade,
-		Hobart TAS 7000, Australia (david.peel@csiro.au). \\
-		Established expert in finite mixture modelling.  
-	\item {\bf Reviewer} Dr John Morrengiello, University of Melbourne,
-		Melbourne, Australia (john.morrongiello@unimelb.edu.au) \\
-		Early career scientist with expertise in quantitative aquatic
-		ecology and evolution along with publications on growth
-		modelling.  
-	\item {\bf Reviewer} Dr Ken Newman, U.S. Fish and Wildlife Service,
-		Lodi Fish and Wildlife Office, 850 Guild Avenue, Lodi, CA
-		95240, USA (Ken\_Newman@fws.gov)\\ Established expert in
-		mathematical and applied statistics with application to natural
-		resource management.  
+	\item \textbf{Dr Tom Carruthers:} Expert in data limited fisheries and
+		spatial fisheries models. Assistant Professor, University of British
+		Columba, Institute for the Ocean and Fisheries, Room 335, 2202
+		Main Mall, Vancouver, British
+		Columbia, Canada. Email: t.carruthers@oceans.ubc.ca.\\ 
+	\item \textbf{Dr Coby Needle:} Expert in spatial fisheries modelling.
+		Marine Scotland, Marine Laboratory 375 Victoria Road, Aberdeen,
+		AB11 9DB, Scotland, UK. Email: coby.needle@gov.scot. \\   
+	\item \textbf{Prof. Richard Bailey:} Expert in coupled
+		human-environment interactions. St Catherine's College, Oxford
+		University, Manor Road, Oxford, OX1 3UJ. Email:
+		richard.bailey@ouce.ox.ac.uk. 
+	\item \textbf{Prof. Edward Codling:} Expert in animal movement
+		behaviour and marine fisheries systems. STEM 5.11, University
+		of Essex, Colchester Campus, Wivenhoe Park, Colchester, CO4
+		3SQ, UK. Email:ecodling@essex.ac.uk.  
 \end{itemize}

### 2019-10-13 write_up/CreDit.tex
Final steps before submission

\documentclass{article}

\usepackage[utf8]{inputenc}
\begin{document}

CRediT author statement:

\begin{itemize}
	\item \textbf{Paul Dolder:} Conceptualisation, methodology, software,
		writing - original draft. 
	\item \textbf{Cóilín Minto:} Conceptualisation, Methodology, writing - review
	and editing, supervision, funding acquisition. 
	\item \textbf{Jean-Marc Guarini:} methodology, writing - review and
		editing, funding acquisition, supervision. 
	\item \textbf{Jan Jaap Poos:} methodology, writing - review and
		editing, supervision. \

\end{itemize}

\end{document}

### 2019-10-13 write_up/highlights.tex
Final steps before submission

@@
 
-	\item one
-	\item two
-	\item three
-	\item four
-	\item five 
-	\item six
+	\item We developed a highly spatially resolved discrete-event
+		simulation model of mixed fishery interactions with multiple
+		populations.	
+	\item The simulation framework incorporates i) delay-difference population
+		dynamics, ii) population movement using Gaussian Markov Fields
+		to simulate patchy, heterogeneously distribution populations,
+		and iii) individual-based fishery dynamics for multiple fleet
+		characteristics using an explore-exploit strategy.
+	\item The framework allows users to explore assumptions in modelling
+		observational data and examine dynamics at a fine
+		spatiotemporal scale. 
+	\item We simulate fifty years of multiple fisheries exploiting four
+		separate populations with different demographics and find
+		nuanced spatio-temporal patterns in exploitation.
+	\item A simulated spatial closure shows that when aggregating point
+		data on fishing activity to a grid, the scale of aggregation
+		matters for the ability to achieve fishery-conservation
+		objectives.
+	\item The simulation framework is available as an R package and we
+		suggest multiple potential uses of the package (e.g. survey
+		design evaluation, testing index standardisation, in-year
+		fishery and biological modelling) for researchers.
 

### 2019-10-13 write_up/mixfishsim_ecolmod.tex
Final steps before submission

@@
 spatiotemporal \sep mixed fisheries \sep individual based \sep spatial
-management \sep homogeneity \sep  preferential sampling
+management \sep heterogeneity \sep  preferential sampling
 \MSC[2010] 00-01\sep  99-00
@@
 highlights different patterns in perceived community structure depending on the
-data source and aggregation level (Figure \ref{fig:1}). The finer spatial grid
-for the true population (top left) and commercial data (top middle) show
-visually similar patterns, though there are large unsampled areas in the
-commercial data from a lack of fishing activity (particularly in the lower left
-part of the sampling domain). The survey data at this spatial resolution
-displays very sparse information about the spatial distributions of the
-populations. The slightly aggregated data on a 5 x 5 grid shows similar
-patterns and, while losing some of the spatial detail, there remains good
-consistency between the true population and the commercial data. Survey data
-starts to pick out some of the similar patterns as the other data sources, but
+data source and aggregation level (Figure \ref{fig:1}; visualised using
+\cite{Gerritsen2014}). The finer spatial grid for the true population (top
+left) and commercial data (top middle) show visually similar patterns, though
+there are large unsampled areas in the commercial data from a lack of fishing
+activity (particularly in the lower left part of the sampling domain). The
+survey data at this spatial resolution displays very sparse information about
+the spatial distributions of the populations. The slightly aggregated data on a
+5 x 5 grid shows similar patterns and, while losing some of the spatial detail,
+there remains good consistency between the true population and the commercial
+data. Survey data starts to pick out some of the similar patterns as the other
+data sources, but
 lacks spatiotemporal coverage. The spatial catch information on a 10 x 10 and
@@
 
-\section*{CRediT author statement} \textbf{Paul Dolder:} Conceptualisation,
-methodology, software, writing - original draft. \textbf{Cóilín Minto:}
-Conceptualisation, Methodology, writing - review and editing, supervision,
-funding acquisition. textbf{Jean-Marc Guarini:} methodology, writing - review
-and editing, funding acquisition, supervision. \textbf{Jan Jaap Poos:}
-methodology, writing - review and editing, supervision. \
-
 \section*{Appendices}

### 2019-12-16 write_up/reviewer_response.tex
Responding to reviewer comments

\documentclass{article}

\usepackage[a4paper, margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{lscape}
\usepackage{longtable}
\usepackage{hhline}
\usepackage{booktabs}

\begin{document}

\large

Address here: cover letter on other computer. \\
\\
Dear xyz, \\
RE: Ms. No. ECOMOD-19-631 \\
\\
Thank you for your email of 5 December 2019 with a favourable review of our
manuscript submission. We have reviewed all the comments made by the editor and
the two reviewers and adjusted the manuscript accordingly. We thank the
reviewers for a constructive review which undoubtedly improves the manuscript
and we found little reason to disagree with their comments. A summary of our
changes are presented overleaf. \\

We look forward to hearing back positively on these changes, and publication of
the manuscript in Ecological Modelling. \\
\\
Kind Regards,\\
\\
Paul J. Dolder, Cóilín Minto, Jean-Marc Guarini \& Jan Jaap Poos

\newpage

\begin{landscape}

\underline{Editor's comments} \\
\\
\textit{
After considering the comments of the two reviewers, which are provided below,
I think your manuscript should be acceptable for publication after satisfactory
revision.  Please address the reviewers' comments when revising your
manuscript.  Thank you again for submitting your manuscript to Ecological
Modelling.
} \\

Thank you for your comments, we have provided a detailed response to each of
the points made by the reviewers; we hope this satisfies your requirements and
look forward to seeing the manuscript published. \\

\underline{Reviewer 1 comments} \\

\textit{This paper introduces a simulation framework for assessing the effects
	of different spatial and temporal observation scales on management of
	mixed fisheries. An application of the framework is presented, and the
	findings from the example application provided insights into the
	importance of data resolution on design and effectiveness of closed
	areas. The model code is included as an R package so that other
	researchers will be able to implement it readily to address a wide
	variety of management questions. The question of appropriate scales is
	an important one, and I think this will be a valuable tool for
	researchers and managers. I recommend that it be published after minor
	revisions.} \\

Thank etc..

\large
	\begin{center}
	\begin{longtable}{p{12cm} | p{12cm}}
%	\caption{Highly resolved spatiotemporal simulations for exploring mixed
%	fishery dynamics}
		\toprule
		Comment & Response \\
		\\
		\hline
		\\
		\textbf{Abstract} & \\
\\
I think it would be helpful to mention the name of the R package (MixFishSim)
that accompanies this paper somewhere in the abstract. People will search for
the package name, it would be nice if the term was included in the abstract so
the paper will show up in the search too. & Thank you, we agree and have
included in the first sentence of the abstract. \\
\\
"true underlying populations" - somehow make sure readers know this is
referring to simulated populations. & We have changed to "true (simulated)
underlying populations" \\
\\
Could add something like "bycatch avoidance", or something like that, somewhere
in key words or abstract; people searching for that term would be glad to find
this paper, I would think! & \\
\\
I think the abstract could be streamlined a bit. You seem to have 2 major
objectives with this paper: 1) introducing and describing the simulation
framework that could answer a number of important management questions, and 2)
demonstrating its usefulness with an example application. One full paragraph
for each should be adequate, with a conclusion that states the usefulness of
the framework for answering a number of fisheries management questions.  & \\
\\
		\hline
		\textbf{Introduction} &  \\
\\
Nice introduction to the need for the simulation framework & Thank you, we have
kept this text unchanged. \\
\\
Line 62: "Do different sources of sampling-derived fisheries data reflect"… &
Thanks, corrected. \\
\\
		\hline
		\textbf{Methods} &  \\
\\
Why was the Matern covariance structure chosen? I am just curious about this;
does it reflect the spatial autocorrelation of animal distributions better than
a Gaussian or other type of covariance structure? & \\
\\
It would be helpful to have explanation of thermal tolerance earlier than line
155 & \\
\\
The paragraph starting at line 179 would be helpful to have at the beginning of
the section & \\
\\
Line 187, make tenses consistent (e.g. determined vs. determines) - also this
sentence is a little awkward to read. & \\
\\
		\hline
		\textbf{Results} &  \\
\\
Line 376: What does "Visualized using Gerritsen (2014)" mean? & \\
\\
Line 397: Are these the same figures in Table 7? If so, just refer to the table
and summarize & \\
\\
Line 400: move \% sign & This has been corrected. [Note, may be redundant if
change text] \\
\\
Line 406: "(in red)" - leave reference to color for figure legend & Removed
reference to color. \\
\\
Line 410: "Again" doesn't need to be there, same in line 413 & Agree, it has
been removed. \\
\\
Line 416: This section is a little confusing and needs to be refined/streamlined. & \\
\\
Line 418: This paragraph should be in methods. But you did it for all
populations, right? Not just population 3? & \\
\\
		\hline
		\textbf{Discussion / Conclusion} &  \\
\\
The discussion and conclusion overlap a bit; I felt I was reading similar
things over again; perhaps these can be streamlined? & \\
\\
Line 560: change "reduced" to "reduce" & Thank you, corrected. \\
\\
Line 663: change "hypothesis" to "hypotheses" & Done. \\
\\
		\hline
		\textbf{Figures} &  \\
\\
Figure 1: nicely summarizes the model. It took me a little bit to figure out
that "Rec" referred to recruitment - even though it was in the legend (I missed
it when I read it the first time)… is it possible to choose an abbreviation
that makes it more obvious, maybe something like "Recruit" or  even "Recr"? It
also occurs to me that there is an opportunity to introduce the terminology
from your R package here to make it very clear to the people using your code
how the functions work together… this is only an idea though… or maybe a
similar figure could be included with the vignette. & \\
\\
Figure 5: Do the colors indicate the dominant population in each cell? It is
hard to imagine that one would assume only the presence of specific population
in the cell? Or do I have the wrong idea about what the plot is showing? & \\
\\
Figure 9: So the top two panels show spatial distribution for population 3?
That needs to be added to the legend. Also there should be a red box on the top
plot too. & \\
\\
Figure 10: I really like this plot! Very effective. & \\
		\bottomrule
	\end{longtable}

\end{center}

\underline{Reviewer 2 comments} \\

\textit{The paper Dolder et al. presents a new highly resolved spatiotemporal
	model that simulates populations of species and fishery dynamics to
	assess if data from commercial catches and fixed-site sampling surveys
	on different spatiotemporal scales represent the real distribution of
	the populations, and if these data are effective to base  management
	programs. Moreover, they presents other applications of the model.} \\

\textit{This is a very interesting paper, and the model provides several
	applications for management programs. I have only few greater questions
	and some small issues, most of them about the presentation of the
	information.}  \\

Thank etc..

\begin{center}

\large

	\begin{longtable}{p{12cm} | p{12cm}}
%	\caption{Highly resolved spatiotemporal simulations for exploring mixed
%	fishery dynamics}
		\toprule
		Comment & Response \\
		\\
		\hline
		\\
	\textbf{General comments} &  \\
\\
		 How many species does the model simulate? The authors refer to
		 the issue of catching unwanted species (vulnerable or low
		 quota species) when available quota species is caught, and it
		 suggested me that populations of different species is modeled
		 at the same time. However, they  did not describe how many
		 species could be simulated in each simulation, only that four
		 populations were simulated. Does the populations simulated in
		 different simulations, or all of them are simulated
		 simultaneously? The results indicate that the four populations
		 were simulated in the same simulation. Please, clarify this in
		 the MM.  &  \\
\\
There are too many figures and they should be better edited. Why the name of
the row and columns are inside the graphics? The axes scales and the axes title
should be greater. I would also send the figure 2, 3 and 9 as supplementary
data.  & \\
\\
The legends of the supplementary figures should be more informative. In the
Figure S2, what the light gray spots are? Habitat preference? Are the squares
the spawning areas? In the figure S3, are each square a week?  & \\
\\
I am not native English, but the language seems good for me. However, I missed
several commas along the text that make the sentences too long and hard to
understand. I suggest a revision of this.  & \\

		\hline

	\textbf{Small issues} &  \\
\\
Line 14 - 18: This phrase is too long and hard to understand. Please, rephrase
this in shorter sentences to clarify this idea. & \\
\\
Lines 20 - 43: These two paragraphs seem redundant.  & \\
\\
Line 68 - 72: The authors mentioned that the MixFishSim could be used to infer
if fisheries data are the real community structure. I suggest adding one or two
phrases to explain how the model could help in this. & \\
\\
Line 90. The authors presented the time-step of each module, except the
Recruitment dynamics. The recruitment dynamics probably follow the population
dynamic, but it would be interesting present this explicitly. & \\
\\
Line 282: How these population parameters were selected? Randomly? Using real
data? Or the authors only created them? & \\
\\
Line 426: What does adapted means in this context? Exploring new opened areas?
& \\
\\
Line 613: Do not use parenthesis inside of other parenthesis. & We have changed
to ", e.g." from "( e.g." to eliminate one set of parenthesis. \\
\\
Table 2 and table 3 are not cited in the text Citation of the supplementary
figures are out of order & \\
\\
Figure 3: Individual years ARE the light grey lines    & Thanks! Corrected. \\
\\
Figure 4. What do the purple spots represent? Describe these spots in the
capture Figure 7. Add what " res"  means in the caption.  & \\
\\
Figure 8. What F means? & \\
\\
		\bottomrule
	\end{longtable}

\end{center}

\end{landscape}

\end{document}

### 2019-12-16 write_up/mixfishsim_ecolmod_revisions.tex
Responding to reviewer comments

--- 2019-10-13 write_up/mixfishsim_ecolmod.tex
@@
 
+\usepackage[draft]{changes}
+
 \modulolinenumbers[1]
@@
 \cortext[c]{Corresponding author}
-\ead{paul.dolder@research.gmit.ie}
+\ead{paul.dolder@cefas.co.uk}
 
@@
 interactions we developed a highly resolved spatiotemporal discrete-event
-simulation model incorporating: i) delay-difference population dynamics, ii)
-population movement using Gaussian Random Fields to simulate patchy,
-heterogeneously distributed populations, and iii) fishery dynamics for multiple
-fleet characteristics based on population targeting under an explore-exploit
-strategy. This is implemented via a mix of correlated random walk movement (for
-exploration) and learned behaviour (for exploitation) phases of the fisheries. \\ 
+simulation model ('MixFishSim`) incorporating: i) delay-difference population
+dynamics, ii) population movement using Gaussian Random Fields to simulate
+patchy, heterogeneously distributed populations, and iii) fishery dynamics for
+multiple fleet characteristics based on population targeting under an
+explore-exploit strategy. This is implemented via a mix of correlated random
+walk movement (for exploration) and learned behaviour (for exploitation) phases
+of the fisheries. \\ 
 %%
@@
 on: commercial catch, a simulated fixed-site sampling survey design and the
-true underlying populations. We i) establish the potential limitations of
-fishery-dependent data in providing a robust picture of spatiotemporal
-distributions; and then ii) simulated an area closure based on areas defined
-from the different data sources at a range of temporal and spatial resolutions.\\
+true \added{(simulated)} underlying populations. We i) establish the potential
+limitations of fishery-dependent data in providing a robust picture of
+spatiotemporal distributions; and then ii) simulated an area closure based on
+areas defined from the different data sources at a range of temporal and
+spatial resolutions.\\
 %%
@@
 	\item Do different source of sampling-derived fisheries data
-		reflects the underlying community structure? 	
+		reflect\deleted{s} the underlying community structure? 	
 	\item How does data aggregation and data source impact on the success
@@
 population 1 = 9.23\% (3.87), population 2\% = 83.3 (5.52), population 3 =
-3.62\% (1.15), population 4 = \%3.86 (1.52). While means were similar some of
-the variation was lost when aggregated to an annual level; population 1 =
-9.90\% (0.173), population 2 = 82.2\% (0.308), population 3 = 3.82\% (0.119),
-population 4 = 4.03\% (0.0502).\\
+3.62\% (1.15), population 4 = \deleted{\%}3.86\added{\%} (1.52). While means
+were similar some of the variation was lost when aggregated to an annual level;
+population 1 = 9.90\% (0.173), population 2 = 82.2\% (0.308), population 3 =
+3.82\% (0.119), population 4 = 4.03\% (0.0502).\\
 
 The commercial data on a weekly basis shows some of the same patterns as the
-true population, though the population 1 (in red) is less well represented and
-some weeks are missing catches from the area. Here, weekly and monthly
-compositions were nearly identical, with monthly composition of population 1 =
-0.0472\% (0.0139), population 2 = 94.4\% (1.47), population 3 = 3.12\% (1.47),
-population 4 = 2.40\% (0.444). Again, yearly values head a similar mean but
-smaller standard deviation.\\
+true population, though the population 1 \deleted{(in red)} is less well
+represented and some weeks are missing catches from the area. Here, weekly and
+monthly compositions were nearly identical, with monthly composition of
+population 1 = 0.0472\% (0.0139), population 2 = 94.4\% (1.47), population 3 =
+3.12\% (1.47), population 4 = 2.40\% (0.444). \deleted{Again, y}\added{Y}early
+values head a similar mean but smaller standard deviation.\\
 
@@
 fixed closures, at the right resolution, when based on commercially derived
-data have the potential to reduced fishing mortality. The likely cost of poor
-spatial and temporal resolution is associated with reduced effectiveness and
-potentially closing fishing opportunities for other fisheries (Figure
-\ref{fig:ce}). \\
+data have the potential to reduce\deleted{d} fishing mortality. The likely cost
+of poor spatial and temporal resolution is associated with reduced
+effectiveness and potentially closing fishing opportunities for other fisheries
+(Figure \ref{fig:ce}). \\
 
@@
 some of the assumptions behind the modelling approaches in identifying such
-hotspots and indeed behind spatiotemporal modelling in general (e.g. comparing
+hotspots and indeed behind spatiotemporal modelling in general\replaced{,}{ (}e.g. comparing
 GAMs, GLMMs, Random Forests and geostatistical models under different data
-generation processes as exampled by \cite{Stock2019}). \\
+generation processes as exampled by \cite{Stock2019}deleted{)}. \\
 
@@
 identification of weaknesses or limitations which would not be possible
-otherwise. In future, we recommend use of the framework to test hypothesis that
-are otherwise unable to be analysed using real world data due to limitations of
-data collection. That way the knowledge gained through simulation can inform
-the future design of management measures.
+otherwise. In future, we recommend use of the framework to test
+hypothes\replaced{e}{i}s that are otherwise unable to be analysed using real
+world data due to limitations of data collection. That way the knowledge gained
+through simulation can inform the future design of management measures.
 
@@
 		across the entire spatial domain showing weekly and seasonal
-		patterns in exploitation.  Individual years and the light grey
-		lines, the mean of all years the thick black line.}
+		patterns in exploitation.  Individual years a\replaced{re}{nd}
+		the light grey lines, the mean of all years the thick black
+		line.}
 	\label{fig:10}

### 2019-12-16 tests/build.R
Started vignette

@@ -6,6 +6,8 @@ reload()
 #load_all()
 document()
 
+build_vignettes()
+
 install()
 
 ## Note: document with 

### 2019-12-19 R/create_hab.R
Updated vignette

@@ -82,13 +82,7 @@ hab <- 	lapply(seq_len(n.spp), function(i) {
 	# Plot
 	if(plot.dist == TRUE) {
 	png(filename = paste0(plot.file,'/','habitat','.png'), width = 800, height = 800)
-	par(mfrow = c(ceiling(sqrt(n.spp)), ceiling(n.spp/ceiling(sqrt(n.spp)))), mar = c(2, 2, 2, 2))
-	for (i in seq(n.spp)) {
-	image(hab[[paste0('spp',i)]], cex.axis = 1.5, cex.main = 2, col = grey(seq(1,0,l = 51)), axes = F)
-	axis(1, at = seq(0, 1, by = 0.2), labels = seq(0, nrows, by = nrows/5))
-	axis(2, at = seq(0, 1, by = 0.2), labels = seq(0, ncols, by = ncols/5))
-	text(0.5, 0.98, labels = paste('habitat spp =', i), cex = 2)
-		}
+	plot_habitat(hab)
 	dev.off()
 	}
 
@@ -125,13 +119,7 @@ spwn <- matrix(rep(0.5, nrows * ncols), nc = ncols)
 	# Plot
 	if(plot.dist == TRUE & !is.null(spawn_areas)) {
 	png(filename = paste0(plot.file,'/','habitat_spwn','.png'), width = 800, height = 800)
-	par(mfrow = c(ceiling(sqrt(n.spp)), ceiling(n.spp/ceiling(sqrt(n.spp)))), mar = c(2, 2, 2, 2))
-	for (i in seq(n.spp)) {
-	image(spwn_hab[[paste0('spp',i)]], cex.axis = 1.5, cex.main = 2, col = grey(seq(1,0,l = 51)), axes = F)
-	axis(1, at = seq(0, 1, by = 0.2), labels = seq(0, nrows, by = nrows/5))
-	axis(2, at = seq(0, 1, by = 0.2), labels = seq(0, ncols, by = ncols/5))
-	text(0.5, 0.98, labels = paste('habitat spp =', i), cex = 2)
-		}
+	plot_habitat(spwn_hab)
 	dev.off()
 	}
 

### 2019-12-19 R/plot_habitat.R

@@ -1,0 +1,33 @@
+#' @title Plot the habitat distribution fields for all populations
+#'
+#' @description \code{plot_habitat} is a function to plot the habitat spatial
+#' fields.
+#'
+#' @param hab is the habitat to plot, either unadjusted or adjusted for
+#' spawning area. 
+
+#' @return Silently plots the habitat fields (can be either the unadjusted
+#' habitat, or including the spawning adjustment).
+
+#' @examples
+#' plot_habitat(hab = hab)
+
+#' @export
+
+plot_habitat <- function(hab = hab) {
+
+	n.spp <- length(hab)
+	nrows <- dim(hab[[1]])[1]
+	ncols <- dim(hab[[1]])[2]
+
+	par(mfrow = c(ceiling(sqrt(n.spp)), ceiling(n.spp/ceiling(sqrt(n.spp)))), mar = c(2, 2, 2, 2))
+	for(i in seq(n.spp)) {
+	image(hab[[paste0("spp", i)]], cex.axis = 1.5, cex.main = 2, col = grey(seq(1,0, l = 51)), axes = F)
+	axis(1, at = seq(0, 1, by = 0.2), labels = seq(0, nrows, by = nrows/5))
+	axis(2, at = seq(0, 1, by = 0.2), labels = seq(0, ncols, by = ncols/5))
+	text(0.5, 0.98, labels = paste("habitat spp = ", i), cex = 1)
+	}
+	
+}
+
+

### 2019-12-19 R/plot_spatiotemp_hab.R

@@ -12,7 +12,7 @@
 
 #' @export
 
-plot_spatiotemp_hab <- function(hab = NULL, moveCov = NULL, plot.file = getwd(), spwn_wk = NULL) {
+plot_spatiotemp_hab <- function(hab = NULL, moveCov = NULL, plot.file = NULL, spwn_wk = NULL) {
 
 	nrows <- nrow(hab[["hab"]][[1]]) 
 	ncols <- ncol(hab[["hab"]][[1]])
@@ -21,7 +21,9 @@ plot_spatiotemp_hab <- function(hab = NULL, moveCov = NULL, plot.file = getwd(),
 for(s in seq_len(length(hab[["hab"]]))) {
 
 	nt <- length(moveCov[["cov.matrix"]])
+	if(!is.null(plot.file)) {
 	png(filename = paste0(plot.file,'/','habitat_spatiotemp_spp_',s,'.png'), width = 800, height = 800)
+	}
 	par(mfrow = c(ceiling(sqrt(nt)), ceiling(nt/ceiling(sqrt(nt)))), mar = c(1, 1, 1, 1))
 
 	for(i in seq_len(nt)) {

### 2019-12-19 R/run_sim.R

@@ -60,6 +60,8 @@ close_count <- 0 # counter for recording closures
 
 # preallocate closure list
 
+if(is.null(closure)) { CalcClosures  <- FALSE }
+
 if(!is.null(closure)) {
 	
 	
@@ -143,6 +145,7 @@ Pop_move <- ifelse(week.breaks[t] != week.breaks[t+1], TRUE, FALSE) ## weekly po
 Update   <- ifelse(day.breaks[t] != day.breaks[t+1], TRUE, FALSE) ## weekly pop records 
 
 ## Closure switch, when to recalculate the closed areas
+
 
 if(!is.null(closure)) {
 if(t==1 & !closeArea) {CalcClosures  <-  FALSE }

### 2019-12-20 R/plot_pop_summary.R
Updated vignette

@@ -46,7 +46,7 @@ plot_pop_summary <- function(results = res, timestep = 'daily', save = FALSE, sa
 
 	if(timestep == "daily") {
 	require(ggplot2)
-	print(ggplot(results_df, aes(x = julien_day, y = data, group = 2)) + geom_point() + facet_wrap(pop ~ metric, scale = "free"))
+	print(ggplot(results_df, aes(x = julien_day, y = data, group = 2)) + geom_point() + facet_grid(pop ~ metric, scale = "free"))
 	}
 	
 	if(timestep == "annual") {
@@ -60,7 +60,7 @@ plot_pop_summary <- function(results = res, timestep = 'daily', save = FALSE, sa
 	results_df_annual <- rbind(results_df_an1, results_df_an2) 
 
 	print(ggplot(results_df_annual, aes(x = year, y = data, group = 2)) + geom_point() + geom_line() + 
-	facet_wrap(pop ~ metric, scale = "free") + expand_limits(y = 0))
+	facet_grid(pop ~ metric, scale = "free") + expand_limits(y = 0))
 	}
 
 	if(save == TRUE) {

### 2019-12-20 R/run_sim.R

@@ -93,7 +93,7 @@ names(MoveProb)      <- paste0("spp", seq_len(n_spp))
 names(MoveProb_spwn) <- paste0("spp", seq_len(n_spp))
 
 ## Avoid printing every tow
-print.seq <- seq(1, ntow, 20)
+print.seq <- seq(1, ntow, 100)
 
 
 ## Closure?
@@ -182,7 +182,7 @@ CalcClosures <- ifelse(week.breaks[t] != week.breaks[t-1], TRUE, FALSE)
 
 if(Recruit) { # Check for new week
 
-print("Recruiting")
+##print("Recruiting")
 
     ## Check if its a recruitment week for the population
  Rec <- lapply(paste0("spp", seq_len(n_spp)), function(s) {
@@ -335,7 +335,7 @@ catches <- lapply(seq_len(n_fleets), function(fl) {
 
 if(Pop_dyn) {
 
-print("Delay-difference model")
+##print("Delay-difference model")
 
 ## Calculate the fishing mortalities
 # 1. Sum all fleet catches - DONE
@@ -385,7 +385,7 @@ B <- Bp1
 
 if(sim_init[["brk.idx"]][["day.breaks"]][t] %in% survey[["log.mat"]][,"day"] & !is.null(survey)) {
 
-print("undertaking scientific survey")
+##print("undertaking scientific survey")
 
 # doy and y
   doy <- sim_init[["brk.idx"]][["day.breaks"]][t]
@@ -425,7 +425,7 @@ log.mat[log.mat[,"day"]==doy & log.mat[,"year"]==y,paste0("spp",s)][i]  <-  	B[[
 
 
 if(Pop_move) {
-	print("Moving populations")
+##	print("Moving populations")
 
 	### With covariates ###
 
@@ -562,7 +562,7 @@ pop_bios <- NULL
 # Update weekly / annual records at pop level
 
 if(Update) {
-print("Recording metrics")
+##print("Recording metrics")
 
 for(s in paste0("spp", seq_len(n_spp))) {
 

### 2019-12-20 tests/build.R

@@ -1,6 +1,6 @@
 library(devtools)
 
-build()
+build(vignettes = FALSE)
 reload()
 
 #load_all()

### 2019-12-20 write_up/reviewer_response.tex
Updated response to reviewers

@@
 \\
-Thank you for your email of 5 December 2019 with a favourable review of our
-manuscript submission. We have reviewed all the comments made by the editor and
-the two reviewers and adjusted the manuscript accordingly. We thank the
-reviewers for a constructive review which undoubtedly improves the manuscript
-and we found little reason to disagree with their comments. A summary of our
-changes are presented overleaf. \\
+Thank you for your email of 5 December 2019 with the favourable 'minor
+revisions` review of our manuscript submission. We have reviewed all the
+comments made by the editor and the two reviewers and addressed them
+accordingly. We thank the reviewers for a constructive review which undoubtedly
+improves the manuscript and we found little reason to disagree with their
+comments. A summary of our changes are presented overleaf.  \\
 
@@
 \\
-		\hline
+		hline
 		\textbf{Methods} &  \\
@@
 does it reflect the spatial autocorrelation of animal distributions better than
-a Gaussian or other type of covariance structure? & \\
+a Gaussian or other type of covariance structure? & We used the Matérn
+covariance structure as it allows for a non-linear decrease in correlation as
+distance increases and is flexible, in that it reverts to an exponential form
+under specific conditions. As such it is capable of taking any number of forms,
+as required. Alternative covariance structures could also be used, but Matérn
+is the most commonly used. We've added text to say "We use the most commonly
+used Matérn covariance structure as it is a flexible form that under certain
+conditions is of the same form as an exponential function and it enables us to
+model the spatial autocorrelation observed in animal populations where density
+is more similar in nearby locations, but that correlation decreases
+non-linearly...." \\ 
 \\
 It would be helpful to have explanation of thermal tolerance earlier than line
-155 & \\
+155 & We have now added a sentence at the beginning of the section that reads
+"[described by a set of probabilities] which are affected by the suitability of
+habitat, temperature in a cell and the thermal tolerance of a population to
+that temperature." \\
 \\
 The paragraph starting at line 179 would be helpful to have at the beginning of
-the section & \\
+the section & Agree, we have moved this to now be the second paragraph in the
+section. \\
 \\
 Line 187, make tenses consistent (e.g. determined vs. determines) - also this
-sentence is a little awkward to read. & \\
+sentence is a little awkward to read. & We have changed so that it reads in the
+past tense and rewritten the paragraph to improve readability. \\
 \\

### 2019-12-20 write_up/mixfishsim_ecolmod_revisions.tex
Updated response to reviewers

@@
 cells, and random (diffusive) movement, governed by a stochastic process where
-movement between adjacent cells is described by a set of probabilities.\\
+movement between adjacent cells is described by a set of probabilities
+\added{which are affected by the suitability of habitat, temperature in a cell
+	and the thermal tolerance of a population to that temperature}.\\
+
+\added{The combined process results in a population structure and movement
+pattern unique to each population, with population movement occurring on a weekly
+basis. The decision to model population movement on a weekly timescale was to
+reflect that fish tend to aggregate in species specific locations that have
+been observed to last around one to two weeks \citep{Poos2007}. Therefore this
+process approximated the demographic shifts in fish populations throughout a
+year with seasonal spawning patterns }(Figure \ref{S-fig:5}).
 
@@
 parameter in the units of distance and $\kappa$ a shape parameter which
-determines the smoothness of the process. This enables us to model the spatial
-autocorrelation observed in animal populations where density is more similar in
-nearby locations \citep{Tobler1970, F.Dormann2007, Poos2007} and we change the
-parameters to implement different spatial structures for the different
-populations using the \textit{RandomFields} R package \citep{Schlater2015}. We
-define a stationary habitat field with an anisotropic pattern (to simulate a
-depth gradient) and combine it with a temporally dynamic thermal tolerance
-field to imitate two key drivers of population dynamics without modelling the
-processes explicitly. Each population was initialised at a single location, and
-subsequently moved across the entire space according to a probabilistic
-distribution based on habitat suitability (represented by the normalised values
-from the GRFs), temperature tolerance and distance from current cell: 
+determines the smoothness of the process. \added{We use the most commonly used
+	Matérn covariance structure as it is a flexible form that under certain
+	conditions is of the same form as an exponential function and
+	it}\deleted{This} enables us to model the spatial autocorrelation
+observed in animal populations where density is more similar in nearby
+locations, \added{but that correlation decreases non-linearly}
+\citep{Tobler1970, F.Dormann2007, Poos2007}. We change the parameters to
+implement different spatial structures for the different populations using the
+\textit{RandomFields} R package \citep{Schlater2015}. We define a stationary
+habitat field with an anisotropic pattern (to simulate a depth gradient) and
+combine it with a temporally dynamic thermal tolerance field to imitate two key
+drivers of population dynamics without modelling the processes explicitly. Each
+population was initialised at a single location, and subsequently moved across
+the entire space according to a probabilistic distribution based on habitat
+suitability (represented by the normalised values from the GRFs), temperature
+tolerance and distance from current cell: 
 \begin{equation}
@@
 
-The final combined process results in a population structure and movement
+\deleted{The final combined process results in a population structure and movement
 pattern unique to each population, with population movement occurring on a weekly
@@
 process approximated the demographic shifts in fish populations throughout a
-year with seasonal spawning patterns (Figure \ref{S-fig:5}).
+year with seasonal spawning patterns (Figure \ref{S-fig:5}).}
 
@@
 
-Fleet dynamics can be broadly categorised into three components: fleet
-targeting - that determined the fleet catch efficiency and preference towards a
-particular population; trip-level decisions, that determines the initial location
-to be fished at the beginning of a trip; and within-trip decisions, that
-determines movement from one fishing spot to another within a trip. An
-explore-exploit type strategy was implemented in the model that combined these
-three components for individual vessels to maximise their catch from an unknown
-resource distribution \citep{Bailey2018}. The decision to use an individual
-based model for fishing vessels was taken because fishers are heterogeneous in
-their location choice behaviour due to different objectives, risk preference
-and targeting preference \citep{VanPutten2012a, Boonstra2015}. Therefore fleet
-dynamics are emergent from individual dynamics rather than pre-defined group
-dynamics.
+Fleet dynamics \replaced{were}{can be }broadly categorised into three
+components. \textit{Fleet targeting} \replaced{determined}{determines} the
+fleet catch efficiency and preference towards a particular population;
+\textit{trip-level decisions} \replaced{determined}{that determines} the
+initial location to be fished at the beginning of a trip; and
+\textit{within-trip decisions}\replaced{determined fishing locations}{, that
+	determines movement from one fishing spot to another} within a trip.
+\replaced{This results in an explore-exploit strategy}{ was implemented in the
+	model that combined these three components} for individual vessels to
+maximise their catch from an unknown resource distribution \citep{Bailey2018}.
+The decision to use an individual based model for fishing vessels was taken
+because fishers are heterogeneous in their location choice behaviour due to
+different objectives, risk preference and targeting preference
+\citep{VanPutten2012a, Boonstra2015}.  Therefore fleet dynamics are emergent
+from individual dynamics rather than pre-defined group dynamics.
 
@@
 
-\section{Parameterisation}
-We parameterise \textit{MixFishSim} to investigate the influence of data
+\section{Model calibration}
+We calibrate \textit{MixFishSim} to investigate the influence of data
 aggregation on spatial inference.
@@
 
-We parametrised the simulation model for four example populations with
+We calibrated the simulation model for four example populations with
 different demographics, growth rates, natural mortality and recruitment
-parameters (Table \ref{tab:1}). Habitat preference (Figure \ref{S-fig:1}) and
+(Table \ref{tab:1}). Habitat preference (Figure \ref{S-fig:1}) and
 temperature (Figures \ref{S-fig:3}, with temperature tolerance \ref{S-fig:4})
@@
 
-\subsection{Fleet parametrisation}
-
-The fleets were parametrised to reflect five different characteristic fisheries
+\subsection{Fleet calibration}
+
+The fleets were calibrated to reflect five different characteristic fisheries
 with unique exploitation dynamics (Table \ref{tab:2}). By setting different
-catchability parameters ($Q_{fl, p}$) we create different targeting preferences
-between the fleets and hence spatial dynamics.  The learned random walk process
-implies that within a fleet different vessels have different spatial
-distributions based on individual experience. The step function was
-parametrised dynamically within the simulations as the maximum revenue
+catchability coefficients ($Q_{fl, p}$) we create different targeting
+preferences between the fleets and hence spatial dynamics.  The learned random
+walk process implies that within a fleet different vessels have different
+spatial distributions based on individual experience. The step function was
+calibrated dynamically within the simulations as the maximum revenue
 obtainable was not known beforehand. This was implemented so that vessels take
@@
 
-The aggregated catch composition from each of the data sources over a ten-year
-period (which shows average seasonal patterns) at different spatial resolutions
-highlights different patterns in perceived community structure depending on the
-data source and aggregation level (Figure \ref{fig:1}; visualised using
-\cite{Gerritsen2014}). The finer spatial grid for the true population (top
-left) and commercial data (top middle) show visually similar patterns, though
-there are large unsampled areas in the commercial data from a lack of fishing
-activity (particularly in the lower left part of the sampling domain). The
-survey data at this spatial resolution displays very sparse information about
-the spatial distributions of the populations. The slightly aggregated data on a
-5 x 5 grid shows similar patterns and, while losing some of the spatial detail,
-there remains good consistency between the true population and the commercial
-data. Survey data starts to pick out some of the similar patterns as the other
-data sources, but
-lacks spatiotemporal coverage. The spatial catch information on a 10 x 10 and
-20 x 20 grid lose a significant amount of information about the spatial
-resolutions for all data sources, and some differences between the survey,
-commercial and true population data emerge. \\
+The \deleted{aggregated }catch composition\added{aggregated at different
+	spatial resolutions} from each of the data sources (\deleted{which
+	shows }average seasonal patterns over a ten-year period) highlights
+different patterns in perceived community structure depending on the data
+source and aggregation level (Figure \ref{fig:1}). The finer spatial grid for
+the true population (top left) and commercial data (top middle) show visually
+similar patterns, though there are large unsampled areas in the commercial data
+from a lack of fishing activity (particularly in the lower left part of the
+sampling domain). The survey data at this spatial resolution displays very
+sparse information about the spatial distributions of the populations. The
+slightly aggregated data on a 5 x 5 grid shows similar patterns and, while
+losing some of the spatial detail, there remains good consistency between the
+true population and the commercial data. Survey data starts to pick out some of
+the similar patterns as the other data sources, but lacks spatiotemporal
+coverage. The spatial catch information on a 10 x 10 and 20 x 20 grid lose a
+significant amount of information about the spatial resolutions for all data
+sources, and some differences between the survey, commercial and true
+population data emerge. \\
 
@@
 according to fixed habitat preferences and temperature gradients (Figures
-\ref{S-fig:1}, \ref{S-fig:3}). Our assumptions in parameterising the model
+\ref{S-fig:1}, \ref{S-fig:3}). Our assumptions in calibrating the model
 (movement rates, temperature tolerances) will have a direct impact on our
@@
 	\caption{[Colour] Data aggregation at different spatial resolutions over a
-		ten year period.}
+		ten year period. The figure shows catch composition at each
+		spatial unit as visualised using \cite{Gerritsen2014} mapplots
+		R package.}
 	\label{fig:1}

### 2020-01-05 write_up/reviewer_response.tex
Addressing reviewer comments

@@
-\documentclass{article}
+\documentclass[10pt]{letter}
 
-\usepackage[a4paper, margin=1in]{geometry}
+\usepackage[margin=2.54cm, a4paper]{geometry}
 \usepackage[utf8]{inputenc}
@@
 
+\signature{\vspace*{-1cm} 
+	Paul Dolder \\ 
+	Dr C\'oil\'in Minto\\ 
+	Prof Jean-Marc Guarini \\
+	Dr Jan Jaap Poos}
+\address{Paul Dolder \\
+	Marine and Freshwater Research Centre \\ 
+	Galway-Mayo Institute of Technology \\ 
+	Dublin Road \\ 
+	Galway \\ 
+	Ireland}
+
 \begin{document}
 
-\large
+\begin{large}
 
-Address here: cover letter on other computer. \\
-\\
-Dear xyz, \\
+\begin{letter}{Prof. Brian D. Fath \\ Department of Biological Sciences \\
+		Towson University \\ 8000 York Road \\ Towson \\ Maryland 21252 \\ USA}
+\opening{Dear Professor Fath,}
+
 RE: Ms. No. ECOMOD-19-631 \\
@@
 \\
-Kind Regards,\\
-\\
-Paul J. Dolder, Cóilín Minto, Jean-Marc Guarini \& Jan Jaap Poos
+
+\closing{Yours Sincerely,}
+
+\end{letter}
+
+\end{large}
 
@@
 \\
-Line 376: What does "Visualized using Gerritsen (2014)" mean? & \\
+Line 376: What does "Visualized using Gerritsen (2014)" mean? & This was poorly
+worded. In hindsight, this should also been in the caption of Figure 5, where
+we've now added: "The figure shows catch composition at each spatial unit
+represented by a square pie chart of the four populations. The area of each
+colour is proportionate to the weight of each population caught in that unit.
+Figure produced with the R package 'mapplots' (Gerritsen et al 2014). \\
 \\
 Line 397: Are these the same figures in Table 7? If so, just refer to the table
-and summarize & \\
+and summarize & Thanks, we agree this improves readability and the three final
+paragraphs in section 4.2 have been revised accordingly. \\
 \\
@@
 Line 418: This paragraph should be in methods. But you did it for all
-populations, right? Not just population 3? & \\
+populations, right? Not just population 3? & That's correct, the closures
+affected all populations but the closures were targeted to reduce fishing
+mortality on population 3. We have clarified and moved to the methods section.
+\\
 \\
@@
 how the functions work together… this is only an idea though… or maybe a
-similar figure could be included with the vignette. & \\
+similar figure could be included with the vignette. & We have changed to 'Recr'
+to make clearer. Rather than change the schematic, we have included a short
+example vignette demonstrating the use of the code - hoping that this will
+increase accessibility and further uptake. \\
 \\
@@
 hard to imagine that one would assume only the presence of specific population
-in the cell? Or do I have the wrong idea about what the plot is showing? & \\
+in the cell? Or do I have the wrong idea about what the plot is showing? & Each
+cell has the four colours in proportion of the weight of each population caught
+(as a square pie chart) - we've clarified this in the figure caption. \\
 \\
+Figure 6: Add what the different colors mean to the legend & This is already
+included \\
 Figure 9: So the top two panels show spatial distribution for population 3?
 That needs to be added to the legend. Also there should be a red box on the top
-plot too. & \\
+plot too. & The top two panels show the spatial distribution of the fishing
+effort before (a) and after (b) the spatial closures, while the bottom (c)
+shows the suitable habitat for the population. We've clarified in the figure
+caption. \\
 \\
-Figure 10: I really like this plot! Very effective. & \\
+Figure 10: I really like this plot! Very effective. & Thanks! \\
 		\bottomrule
@@
 		 were simulated in the same simulation. Please, clarify this in
-		 the MM.  &  \\
+		 the MM.  & Thanks, a good point and we now emphasis that the
+		 framework allows the user to define as many species as
+		 required. There will be some computational/memory cap but we
+		 see no reasons why you could not include 10s or more. We chose
+		 four to keep the analysis more tractable. All the populations
+		 are part of the same system, irrespective of the number of
+		 species included (though they do not interact, for example,
+		 through predator-prey relationships).\\
 \\
@@
 if fisheries data are the real community structure. I suggest adding one or two
-phrases to explain how the model could help in this. & \\
+phrases to explain how the model could help in this. & We explain that as our
+community structure is simulated and therefore known, by comparing our inferred
+community structure from commercial catches with our known true structure we
+can understand how biases introduced by using commercial fishing as a sample
+effects our understanding. We believe this point is adequately covered as
+currently written.\\
 \\
@@
 Recruitment dynamics. The recruitment dynamics probably follow the population
-dynamic, but it would be interesting present this explicitly. & \\
+dynamic, but it would be interesting present this explicitly. & Recruitment
+occurs along with other population dynamics, but only during defined periods
+for each population. We've clarified by saying "Population dynamics operate on
+a daily time-step \textit{(with recruitment occurring only during defined
+	seasons for each population), while..}\\
 \\
 Line 282: How these population parameters were selected? Randomly? Using real
-data? Or the authors only created them? & \\
+data? Or the authors only created them? & The demographics were defined by the
+authors to broadly reflect a four-species assemblage found in a typical
+demersal fishery. We have clarified by including the sentence:  "The population
+demographics were defined to broadly represent three mobile low-medium value
+groundfish species and one high value species with low mobility, with the
+dynamics hypothetical but as you might expect to find in a typical demersal
+fishery." \\ 
 \\ 
-Line 426: What does adapted means in this context? Exploring new opened areas?
-& \\
+Line 426: What does adapted means in this context? Exploring
+new opened areas?
+& Yes, we have clarified in the text that "the fisheries "adapted" to the
+closures textit{by fishing new areas of high abundance to fish}\\
 \\
@@
 Table 2 and table 3 are not cited in the text Citation of the supplementary
-figures are out of order & \\
+figures are out of order & This is now corrected with references inserted for
+Table 2 and 3 and the supplementary figures reorded. \\
 \\
@@
 Figure 4. What do the purple spots represent? Describe these spots in the
-capture Figure 7. Add what " res"  means in the caption.  & \\
+capture & This has been clarified to be the revenue at each location (darker
+the area, higher the revenue). \\
+Figure 7. Add what " res"  means in the caption.  & Have clarified in the
+legend text that it means "resolution" \\
 \\
-Figure 8. What F means? & \\
+Figure 8. What F means? & Changed to read "Fishing mortality" \\
 \\

### 2020-01-05 write_up/Process_model.tex
Addressing reviewer comments

@@
 \node [term, join, fill=lcfree!25] (p1){Sample catch};
-\node [test, densely dotted] (t1) {if $(Rec)$};
+\node [test, densely dotted] (t1) {if $(Recr)$};
 \node [test, join, densely dotted] (t2) {if (Pop Movement)};
@@
 	the white boxes are the time steps at which processes occur; $t$ = tow,
-	$tmax$ is the total number of tows; (Rec), (Pop Movement), (Pop
+	$tmax$ is the total number of tows; (Recr), (Pop Movement), (Pop
 	Dynamics) logic gates for recruitment periods, population movement and

### 2020-01-05 write_up/mixfishsim_ecolmod_revisions.tex
Addressing reviewer comments

@@
 
-Population dynamics operate on a daily time-step, while population movement
-occurs on a weekly time-step, with the fishing module operating on a tow-by-tow
-basis (i.e.  multiple events a day).
+Population dynamics \added{for any number of species, as chosen by the user}
+operate on a daily time-step \added{(with recruitment occurring only during
+	defined seasons for each population)}, while population movement occurs
+on a weekly time-step, with the fishing module operating on a tow-by-tow basis
+(i.e.  multiple events a day). \\
 
@@
 	& \left(B_{c,d-1} \cdot \mathrm{e}^{-Z_{c,d-1}} + Wt_{R-1} \cdot \left( \alpha_{d-1} \cdot
-	R_{\tilde{y}(c)}\right) \right)
+	R_{\tilde{y}\left(c\right)}\right) \right)
 	\hspace{0.9cm} + \\
-	& Wt_{R} \cdot \left( \alpha_{d} \cdot R_{\tilde{y}(c) \right)}
+	& Wt_{R} \cdot \left( \alpha_{d} \cdot R_{\tilde{y} \left(c\right)}
+	\right) \\
 	\end{split}
@@
 and $\sigma_{p}$ the mean and standard deviation of the population temperature
-tolerance. \\
+tolerance. The variables, their meaning and units for population movement is
+provided in Table \ref{tab:pop_move}. \\
 
@@
 reflect that fish tend to aggregate in species specific locations that have
-been observed to last around one to two weeks \citep{Poos2007}. Therefore this
+been observed to last around one to two weeks (Poos et al 2007). Therefore this
 process approximated the demographic shifts in fish populations throughout a
@@
 the maximum concentration value, $k$, and $RefRev$ is parametrised as for
-$\beta_{3}$ in the step length function.
+$\beta_{3}$ in the step length function. Details of the variables, meaning and
+units for fleet dynamics are provided in Table \ref{tab:fleet_dyn}.
 
@@
 
-We calibrated the simulation model for four example populations with
-different demographics, growth rates, natural mortality and recruitment
-(Table \ref{tab:1}). Habitat preference (Figure \ref{S-fig:1}) and
-temperature (Figures \ref{S-fig:3}, with temperature tolerance \ref{S-fig:4})
-defined to be unique to each population resulting in differently weekly
-distribution patterns (Figures \ref{S-fig:5}-\ref{S-fig:7}). In addition, each
-of the populations was assumed to have two defined spawning areas that result
-in the populations moving towards these areas in pre-defined weeks (Figure
-\ref{S-fig:2}) with population-specific movement rates (Table \ref{tab:1}).
+We calibrated the simulation model for four example populations with different
+demographics, growth rates, natural mortality and recruitment (Table
+\ref{tab:1}). Habitat preference (Figure \ref{S-fig:1}) and temperature
+(Figures \ref{S-fig:3}, with temperature tolerance \ref{S-fig:4}) defined to be
+unique to each population resulting in differently weekly distribution patterns
+(Figures \ref{S-fig:5}-\ref{S-fig:7}). In addition, each of the populations was
+assumed to have two defined spawning areas that result in the populations
+moving towards these areas in pre-defined weeks (Figure \ref{S-fig:2}) with
+population-specific movement rates (Table \ref{tab:1}).  \added{The population
+demographics were defined to broadly represent three mobile low-medium value
+groundfish species and one high value species with low mobility, with the
+dynamics hypothetical but as you might expect to find in a typical demersal
+fishery.}
 
@@
 (either derived from the commercial catches, fisheries-independent survey or
-the true population used at different spatial and temporal scales. \\
+the true population) used at different spatial and temporal scales. \\
 
@@
 
-Survey closures were on an annual basis only, as this was the most temporally
-resolved survey data available. We evaluated the factors contributing to the
-success of the closures through a regression tree (using the R package REEMtree
-\citep{Sela2012}) to identify the factor most contributing to differences in
-fishing mortality before and after the closure.
+\added{We implemented a series of spatial closures targeted at reducing fishing
+	mortality on population 3, given the different data sources and spatial
+	and temporal resolutions above. We use the effectiveness of these
+	closures in reducing fishing mortality as a way of evaluating the
+	trade-offs in data sources and resolution.} Survey closures were on an
+annual basis only, as this was the most temporally resolved survey data
+available. We evaluated the factors contributing to the success of the closures
+through a regression tree (using the R package REEMtree \citep{Sela2012}) to
+identify the factor most contributing to differences in fishing mortality
+before and after the closure.
 
@@
 Different perceptions of the proportion of each stock in an area are seen when
-we aggregate the data over a smaller geographical region at different
-timescales, with weekly (top), monthly (middle) and yearly (bottom) catch
-compositions from across an aggregated 20 x 20 area (Figure \ref{fig:2}). In
-the true population, the monthly aggregation captures the major patterns of
-composition seen in the weekly data with the percentage of different
-populations in the catch having similar mean and standard deviations.  In the
-weekly data population 1 = 9.36\% (SD = 3.99), population 2 = 83.2\% (5.60),
-population 3 = 3.57\% (1.23), population 4 = 3.91\% (1.59); in the monthly data
-population 1 = 9.23\% (3.87), population 2\% = 83.3 (5.52), population 3 =
-3.62\% (1.15), population 4 = \deleted{\%}3.86\added{\%} (1.52). While means
-were similar some of the variation was lost when aggregated to an annual level;
-population 1 = 9.90\% (0.173), population 2 = 82.2\% (0.308), population 3 =
-3.82\% (0.119), population 4 = 4.03\% (0.0502).\\
+we aggregate the data at different timescales, with weekly (top), monthly
+(middle) and yearly (bottom) catch compositions from across an aggregated 20 x
+20 area showing different patterns (Figure \ref{fig:2}). In the true
+population, the monthly aggregation captures the major patterns of composition
+seen in the weekly data with the percentage of different populations in the
+catch having similar mean and standard deviations (Table \ref{tab:7}). In the
+weekly and monthly data population 2 dominates. However, some of the variation
+was lost when aggregated to an annual level, as indicated from the lower
+standard deviations (Table \ref{tab:7}).\\
 
@@
 represented and some weeks are missing catches from the area. Here, weekly and
-monthly compositions were nearly identical, with monthly composition of
-population 1 = 0.0472\% (0.0139), population 2 = 94.4\% (1.47), population 3 =
-3.12\% (1.47), population 4 = 2.40\% (0.444). \deleted{Again, y}\added{Y}early
-values head a similar mean but smaller standard deviation.\\
+monthly compositions were nearly identical (Figure \ref{fig:2}; Table
+\ref{tab:7}). \deleted{Again, y}\added{Y}early values head a similar mean but
+smaller standard deviation.\\
 
 The survey data was only available on an annual basis, and showed again a
-slightly different composition; population 1 = 0.372\% (0.00473), population 2
-= 87.7\% (0.193), population 3 = 0.729\% (0.0200), population 4 = 11.2\%
-(0.172).
+slightly different composition from the true population and the commercial
+data; in particular a greater proportion of population 4 (Figure \ref{fig:2}).
 
@@
 
-We implemented a spatial closure using the different data sources and spatial
-and temporal aggregations as outlined in the protocol in Section 3.4. We used
-this to assess the efficacy of a closure in reducing fishing mortality on
-population 3, given availability of data and its use at different resolutions in
-order to evaluate the trade-offs in data sources.
+\deleted{We implemented a spatial closure using the different data sources and
+	spatial and temporal aggregations as outlined in the protocol in
+	Section 3.4. We used this to assess the efficacy of a closure in
+	reducing fishing mortality on population 3, given availability of data
+	and its use at different resolutions in order to evaluate the
+	trade-offs in data sources. }
 
@@
 after the closures, following which the fisheries ``adapted" to the closures
-and fishing mortality increased again somewhat. The exception to the success
-was the closures implemented based on the coarsest spatial (20 x 20) and
-temporal resolution (yearly) that was ineffective (i.e. failed to reduce
-fishing mortality) with all data sources. As expected, closures based on the
-``known" population distribution were most effective, with differing degrees of
-success using the commercial data. Fishing mortality rates on the other species
-changed in different proportions, depending on whether the displaced fishing
-effort moved to areas where the populations were found in greater or lesser
-density. \\
+\added{by finding new areas of high abundance to fish} and fishing mortality
+increased again somewhat. The exception to the success was the closures
+implemented based on the coarsest spatial (20 x 20) and temporal resolution
+(yearly) that was ineffective (i.e. failed to reduce fishing mortality) with
+all data sources. As expected, closures based on the ``known" population
+distribution were most effective, with differing degrees of success using the
+commercial data. Fishing mortality rates on the other species changed in
+different proportions, depending on whether the displaced fishing effort moved
+to areas where the populations were found in greater or lesser density. \\
 
@@
 		single vessel during a trip overlaid on the revenue of a
-		fishing site (landings x price); (B) the fishing locations of
-		the vessel over several trips (value field changes over the
-		period so not shown). Note that movements are a mixture of
-		correlated random walk (solid lines) and experience-based
-		(dashed lines), and that the field is wrapped on a torus so
-		that opposite sides of the spatial domain are considered
-		spatially close; (C) the locations of multiple vessels from the
-		same fleet overlaid on the value field, (D) the realised step
-		distance and turning angles for a single vessel over the
-		simulation.}
+		fishing site (landings x price; darker purple = higher
+		revenue); (B) the fishing locations of the vessel over several
+		trips (value field changes over the period so not shown). Note
+		that movements are a mixture of correlated random walk (solid
+		lines) and experience-based (dashed lines), and that the field
+		is wrapped on a torus so that opposite sides of the spatial
+		domain are considered spatially close; (C) the locations of
+		multiple vessels from the same fleet overlaid on the value
+		field, (D) the realised step distance and turning angles for a
+		single vessel over the simulation.}
 	\label{fig:mv}
@@
 	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_space_Rev2}
-	\caption{[Colour] Data aggregation at different spatial resolutions over a
-		ten year period. The figure shows catch composition at each
-		spatial unit as visualised using \cite{Gerritsen2014} mapplots
-		R package.}
+	\caption{[Colour] Data aggregation at different spatial resolutions
+		over a ten year period. \added{The figure shows catch
+			composition at each spatial unit represented by a
+			square pie chart of the four populations. The area of
+			each colour is proportionate to the weight of each
+			population caught in that unit. Figure produced using
+			the R package 'mapplots' (\cite{Gerritsen2014}.}}
 	\label{fig:1}
@@
 	\includegraphics[width =0.5\linewidth]{./Plots/Closure_fishing_locations_yearly}
-	\caption{Closure fishing locations based on annual closures with a
-		coarse spatial resolution. Closure location can be seen in red
-		box in relation to a) before the closure fishing locations, b)
-		after the closure fishing locations, c) population 3 habitat
-		distribution.}
+	\caption{The location of fishing effort before the spatial closure (a)
+		and after the spatial closure (b), and the suitable habitat for
+		population 3 (c). The site of the closure can be seen in the
+		red box on all three panels.}
 	\label{fig:17}

### 2020-01-05 analysis/Plot_fishing.R

@@ -86,8 +86,10 @@ return(cbind(polyr, data.frame(year = y)))
 }
 cl <- lapply(yrs[2], function(x) make_ggpoly(y = x))
 cl <- do.call(rbind, cl)
+cl <- cl[,1:7]
 
 p1 <- ggplot(filter(logs, closure == "before"), aes(x = x , y = y)) +
+	geom_polygon(data = cl, aes(long, lat, group = group), colour = "red",fill = NA) +
 	geom_point(colour = "blue", alpha = 0.2, shape = "x") +
 	expand_limits(x = c(0,100), y = c(0,100)) + facet_wrap(~year) +
 	theme_bw() + theme(plot.margin = margin(1, 0.5, 0.5, 0.5, "cm")) +
@@ -104,7 +106,7 @@ p2 <- ggplot(cl) + geom_polygon(aes(long, lat, group = group), colour = "red",fi
 
 p3 <- ggplot(cl) + geom_raster(aes(x, y, alpha = hab), data = filter(hab.df, hab > 0))+ 
 	geom_polygon(aes(long, lat, group = group), colour = "red",fill = NA) +
-	expand_limits(x = c(0,100), y = c(0,100)) + facet_wrap(~year) +
+	expand_limits(x = c(0,100), y = c(0,100))+
 	theme_bw() + theme(plot.margin = margin(1, 0.5, 0.5, 0.5, "cm"), 
 			   legend.position = "none") +
 	xlab("x distance") + ylab("y distance")

### 2020-01-05 analysis/Plots_Combined.R

@@ -212,12 +212,18 @@ combined_pop_an$pop[combined_pop_an$pop == "spp_4"] <- "Population 4"
 combined_pop_an$data_type[combined_pop_an$data_type == "real_pop"]  <- "True Population"
 
 
+library(viridis)
+
+colnames(combined_pop_an)[9] <- "resolution"
+
+
 png('F_trendsREV.png', units = "in", height = 8, width = 9, res = 600)
 
 ggplot(filter(combined_pop_an,basis == 'high_pop', metric == 'F'), 
        aes(x = year, y = data, group = combined)) + 
-geom_line(aes(colour = timescale, linetype = res), size = 1) +
+geom_line(aes(colour = timescale, linetype = resolution)) +
 scale_linetype_manual(values = rev(1:4)) + 
+scale_colour_manual("Data source", values = c("#d95f02", "#7570b3", "#1b9e77")) +
 facet_grid(data_type ~pop) + expand_limits(y = 0) +theme_bw() +
 geom_vline(xintercept = 30, linetype = 2, colour = "grey") + ylab("Fishing mortality") +
 theme(axis.text.x = element_text(hjust = 0),

### 2020-01-05 analysis/effectiveness_plot.R

@@ -110,7 +110,7 @@ ggplot(f_diff, aes(x = resolution, y = diff))+
 	  axis.text = element_text(size = 14, face = "bold"),
 	  axis.title = element_text(size = 14, face = "bold")) +
     xlab("Spatial resolution (high to low)") +
-    ylab("Percentage difference in F before and after closure")
+    ylab("Percentage difference in Fishing mortality before and after closure")
 dev.off()
 
 

### 2020-01-05 write_up/reviewer_response.tex
Small corrections to reviewer response

@@
 155 & We have now added a sentence at the beginning of the section that reads
-"[described by a set of probabilities] which are affected by the suitability of
+``[described by a set of probabilities] which are affected by the suitability of
 habitat, temperature in a cell and the thermal tolerance of a population to
@@
 worded. In hindsight, this should also been in the caption of Figure 5, where
-we've now added: "The figure shows catch composition at each spatial unit
+we've now added: ``The figure shows catch composition at each spatial unit
 represented by a square pie chart of the four populations. The area of each
 colour is proportionate to the weight of each population caught in that unit.
-Figure produced with the R package 'mapplots' (Gerritsen et al 2014). \\
+Figure produced with the R package 'mapplots' (Gerritsen et al 2014)." \\
 \\
@@
 Figure 6: Add what the different colors mean to the legend & This is already
-included \\
+included as the legend shows which population is represented by which colour. \\
+\\
 Figure 9: So the top two panels show spatial distribution for population 3?
@@
 occurs along with other population dynamics, but only during defined periods
-for each population. We've clarified by saying "Population dynamics operate on
+for each population. We've clarified by saying ``Population dynamics operate on
 a daily time-step \textit{(with recruitment occurring only during defined
-	seasons for each population), while..}\\
+	seasons for each population),} while.." \\
 \\
@@
 authors to broadly reflect a four-species assemblage found in a typical
-demersal fishery. We have clarified by including the sentence:  "The population
+demersal fishery. We have clarified by including the sentence:  ``The population
 demographics were defined to broadly represent three mobile low-medium value
@@
 new opened areas?
-& Yes, we have clarified in the text that "the fisheries "adapted" to the
+& Yes, we have clarified in the text that ``the fisheries "adapted" to the
 closures textit{by fishing new areas of high abundance to fish}\\
@@
 Line 613: Do not use parenthesis inside of other parenthesis. & We have changed
-to ", e.g." from "( e.g." to eliminate one set of parenthesis. \\
+from ``( e.g." to ``, e.g." to eliminate one set of parenthesis. \\
 \\
@@
 the area, higher the revenue). \\
-Figure 7. Add what " res"  means in the caption.  & Have clarified in the
-legend text that it means "resolution" \\
 \\
-Figure 8. What F means? & Changed to read "Fishing mortality" \\
+Figure 7. Add what ``res"  means in the caption.  & Have clarified in the
+legend text that it means ``resolution" \\
+\\
+Figure 8. What F means? & Changed to read ``Fishing mortality" \\
 \\

### 2020-01-10 write_up/mixfishsim_ecolmod_revisions.tex
Changed title
updated abstract

@@
 \begin{frontmatter}
-\title{Working title: Highly resolved spatiotemporal simulations for
+\title{Highly resolved spatiotemporal simulations for
 	exploring mixed fishery dynamics}
@@
 dynamics, ii) population movement using Gaussian Random Fields to simulate
-patchy, heterogeneously distributed populations, and iii) fishery dynamics for
-multiple fleet characteristics based on population targeting under an
-explore-exploit strategy. This is implemented via a mix of correlated random
-walk movement (for exploration) and learned behaviour (for exploitation) phases
-of the fisheries. \\ 
+patchy, heterogeneously distributed \added{and moving fish} populations, and
+iii) fishery dynamics for multiple fleet characteristics based on population
+targeting under an explore-exploit strategy.\deleted{ This is implemented via a mix of
+correlated random walk movement (for exploration) and learned behaviour (for
+exploitation) phases of the fisheries. }\\ 
 %%
-Fifty years of sub-daily fishing activity was simulated and used to draw
-inference on the underlying community structures. We compared inferences based
-on: commercial catch, a simulated fixed-site sampling survey design and the
-true \added{(simulated)} underlying populations. We i) establish the potential
+\deleted{Fifty years of sub-daily fishing activity was simulated and used to
+	draw inference on the underlying community structures. W}\added{We
+	applied the framework to draw}\deleted{compared} inference\deleted{s}
+\added{on community structure} \added{when using data generated from
+}\deleted{based on}: commercial catch, a simulated fixed-site sampling survey
+design and the true \added{(simulated)} underlying populations.
+\deleted{W}\added{In doing so w}e \deleted{i)}establish the potential
 limitations of fishery-dependent data in providing a robust picture of
-spatiotemporal distributions; and then ii) simulated an area closure based on
-areas defined from the different data sources at a range of temporal and
-spatial resolutions.\\
-%%
-Our framework allows users to explore the assumptions in modelling
-observational data and evaluate the underlying dynamics of such approaches at a
-fine spatial and temporal scale. In application to a mixed fishery exploiting
-four different populations we found different spatial patterns were evident and
-that the effectiveness of the spatial closure reduced when data were aggregated
-across larger spatial areas. However, aggregation across time periods has less
-of a negative impact on the closure success and while not as effective as when
-based on on the true population, closures based on high catch rates observed in
-commercial data could still reduce fishing on a protected species. \\
-
-We conclude from our example framework application that commercial data, while
+spatiotemporal distributions\deleted{; and then ii) simulated an area closure
+	based on areas defined from the different data sources at a range of
+	temporal and spatial resolutions.}\deleted{Our framework allows users
+	to explore the assumptions in modelling observational data and evaluate
+	the underlying dynamics of such approaches at a fine spatial and
+	temporal scale. In application to a mixed fishery exploiting four
+	different populations w} \added{W}e found different spatial patterns
+were evident and that the effectiveness of the spatial closure reduced when
+data were aggregated across larger spatial areas. \deleted{; and then
+	ii)}\added{We then simulated an area closure based on areas defined
+	from the different data sources at a range of temporal and spatial
+	resolutions.} Aggregation across time periods has less of a negative
+impact on the closure success than over space.\deleted{ and w}\added{W}hile not
+as effective as when based on on the true population, closures based on high
+catch rates observed in commercial data were still able to reduce fishing on a
+protected species. \\
+
+\added{Our framework allows users to explore the assumptions in modelling
+	observational data and evaluate the underlying dynamics of such
+	approaches at a fine spatial and temporal scale. }\added{From our
+	application w}\deleted{W}e conclude that commercial data, while
 containing bias, provide a useful tool for managing catches in mixed fisheries
@@
 spatiotemporal \sep mixed fisheries \sep individual based \sep spatial
-management \sep heterogeneity \sep  preferential sampling
+management \sep heterogeneity \sep bycatch avoidance 
 \MSC[2010] 00-01\sep  99-00
@@
 In most cases the fishery closure was successful in reducing fishing mortality
-on the species of interest (population 3; Figure \ref{fig:3}), though
-interestingly the largest reductions in fishing mortality happened immediately
-after the closures, following which the fisheries ``adapted" to the closures
-\added{by finding new areas of high abundance to fish} and fishing mortality
-increased again somewhat. The exception to the success was the closures
-implemented based on the coarsest spatial (20 x 20) and temporal resolution
-(yearly) that was ineffective (i.e. failed to reduce fishing mortality) with
-all data sources. As expected, closures based on the ``known" population
-distribution were most effective, with differing degrees of success using the
-commercial data. Fishing mortality rates on the other species changed in
-different proportions, depending on whether the displaced fishing effort moved
-to areas where the populations were found in greater or lesser density. \\
+on the species of interest (population 3; Figure \ref{fig:3}). Interestingly
+the largest reductions in fishing mortality happened immediately after the
+closures, following which the fisheries ``adapted" to the closures \added{by
+	finding new areas of high abundance to fish which led to} fishing
+mortality increasing again, though not to past levels. The exception to the
+success was the closures implemented based on the coarsest spatial (20 x 20)
+and temporal resolution (yearly) that was ineffective (i.e. failed to reduce
+fishing mortality) with all data sources. As expected, closures based on the
+``known" population distribution were most effective, with differing degrees of
+success using the commercial data. Fishing mortality rates on the other species
+changed in different proportions, depending on whether the displaced fishing
+effort moved to areas where the populations were found in greater or lesser
+density. \\
 

### 2020-01-11 write_up/Supplementary.tex
Addressing reviewer comments
Figure revisions

@@
 \begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{Plots/pop_dist}
+	\caption{Spatial density (log abundance) for each of the four
+		populations at four time steps. The darker the colour the
+		greater the density of the population. Note that a diagonal
+		anisotropic pattern (mimicking a depth gradient) can be
+		clearly seen in populations 2 and 3. The concentrated spawning
+		areas are also visible in the second row of the panels
+		(t=18).}
+	\label{fig:9}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{Plots/f_dynamics}
+	\caption{Fishing mortality dynamics - the daily fishing mortalities
+		across the entire spatial domain showing weekly and seasonal
+		patterns in exploitation.  Individual years are the light grey
+		lines, the mean of all years the thick black line.}
+	\label{fig:10}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_1}
+	\caption{Spatiotemporal habitat suitability - the suitability habitat
+		(for Population 1) for 52 separate weeks.}
+	\label{fig:5}
+\end{figure}
+
+\begin{figure}[!ht]
 	\includegraphics[width = \linewidth]{../analysis/habitat}
@@
 	\label{fig:1}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../analysis/habitat_spwn}
-	\caption{Spawning habitat preference: the habitat suitability during
-		spawning periods for each population.}
-	\label{fig:2}
 \end{figure}
@@
 \begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_1}
-	\caption{Spatiotemporal habitat suitability - the suitability habitat
-		(for Population 1) for 52 separate weeks.}
-	\label{fig:5}
-\end{figure}
-
-\begin{figure}[!ht]
 	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_2}
@@
 \begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_4}
-	\caption{Spatiotemporal habitat suitability - the suitability habitat
-		(for Population 4) for 52 separate weeks}
-	\label{fig:8}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{./Plots/Matern}
-	\caption{Example of different implementation of the Matern correlation
-	function on autocorrelation distance}
-	\label{fig:16}
+	\includegraphics[width = \linewidth]{../analysis/habitat_spwn}
+	\caption{Spawning habitat preference: the habitat suitability during
+		spawning periods for each population.}
+	\label{fig:2}
 \end{figure}

### 2020-01-11 write_up/mixfishsim_ecolmod_revisions.tex
Figure revisions

@@
 Individual habitat preferences and thermal tolerances result in different
-spatial habitat use for each population (Figure \ref{fig:9}) and consequently
-different seasonal exploitation patterns (Figure \ref{fig:10}).
+spatial habitat use for each population (Figure \ref{S-fig:9}) and consequently
+different seasonal exploitation patterns (Figure \ref{S-fig:10}).
 
@@
 closures, following which the fisheries ``adapted" to the closures \added{by
-	finding new areas of high abundance to fish which led to} fishing
-mortality increasing again, though not to past levels. The exception to the
-success was the closures implemented based on the coarsest spatial (20 x 20)
-and temporal resolution (yearly) that was ineffective (i.e. failed to reduce
-fishing mortality) with all data sources. As expected, closures based on the
-``known" population distribution were most effective, with differing degrees of
-success using the commercial data. Fishing mortality rates on the other species
-changed in different proportions, depending on whether the displaced fishing
-effort moved to areas where the populations were found in greater or lesser
-density. \\
+	finding new areas of high abundance to fish. This led to} fishing
+mortality increasing again, though not to past levels (Figure \ref{fig:3}).
+The exception to the success was the closures implemented based on the coarsest
+spatial (20 x 20) and temporal resolution (yearly) that was ineffective (i.e.
+failed to reduce fishing mortality) with all data sources. As expected,
+closures based on the ``known" population distribution were most effective,
+with differing degrees of success using the commercial data. Fishing mortality
+rates on the other species changed in different proportions, depending on
+whether the displaced fishing effort moved to areas where the populations were
+found in greater or lesser density. \\
 
@@
 measures to meet particular management goals \citep{Bailey2018}, our framework
-allows users to explore the assumptions in modelling observational data and
-evaluate the underlying dynamics of such approaches at a fine spatial and
-temporal scale.  This offers the advantage that larger scale fishery patterns
-are emergent properties of the system and results can be compared to those
-obtained under a statistical modelling framework. \\
+allows users to explore \deleted{the} assumptions in modelling observational
+data and \added{to} evaluate the underlying dynamics of such approaches at
+\deleted{a} fine spatial and temporal scale\added{s}.  This offers the
+advantage that larger scale fishery patterns are emergent properties of the
+system and results can be compared to those obtained under a statistical
+modelling framework. \\
 
@@
 inference from catch data obtained through commercial fishing activity with
-fleets exploiting multiple fish populations and realising catch distributions
-that may differ from the underlying populations, as identified by
+fleets exploiting multiple fish populations\added{. This shows how}\deleted{
+	and} realis\added{ed}\deleted{ing} catch distributions \deleted{that
+}may differ from the underlying populations, as identified by
 \cite{Gillis2008}. As such, we favoured a minimum realistic model of the fish
@@
 practices if potential biases in data are to be understood and taken into
-account (Figures \ref{fig:9}, \ref{fig:mv}). \\
+account (Figures \ref{S-fig:9}, \ref{fig:mv}). \\
 
@@
 experienced in individual locations over the course of the year (Figure
-\ref{fig:9}). \\
+\ref{S-fig:9}). \\
 
@@
 GAMs, GLMMs, Random Forests and geostatistical models under different data
-generation processes as exampled by \cite{Stock2019}deleted{)}. \\
+generation processes as exampled by \cite{Stock2019}\deleted{)}. \\
 
@@
 
-\section*{Funding} This work was supported by the MARES doctoral training
-program (MARES\_14\_15) and the Centre for Environment, Fisheries and
-Aquaculture Science seedcorn program (DP227AC). The authors declare no
-competing interests.
+\section*{Funding and Acknowledgements} This work was supported by the MARES
+doctoral training program (MARES\_14\_15) and the Centre for Environment,
+Fisheries and Aquaculture Science seedcorn program (DP227AC).\added{ We thank
+	two anonymous reviewers for their helpful comments which greatly
+	improved the final manuscript.} The authors declare no competing
+interests.
 
@@
 %\begin{comment}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{Plots/pop_dist}
-	\caption{Spatial density (log abundance) for each of the four
-		populations at four time steps. The darker the colour the
-		greater the density of the population. Note that a diagonal
-		anisotropic pattern (mimicking a depth gradient) can be
-		clearly seen in populations 2 and 3. The concentrated spawning
-		areas are also visible in the second row of the panels
-		(t=18).}
-	\label{fig:9}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{Plots/f_dynamics}
-	\caption{Fishing mortality dynamics - the daily fishing mortalities
-		across the entire spatial domain showing weekly and seasonal
-		patterns in exploitation.  Individual years a\replaced{re}{nd}
-		the light grey lines, the mean of all years the thick black
-		line.}
-	\label{fig:10}
-\end{figure}
 
@@
 			population caught in that unit. Figure produced using
-			the R package 'mapplots' (\cite{Gerritsen2014}.}}
+			the R package 'mapplots' (\cite{Gerritsen2014}.}
+	}
 	\label{fig:1}
@@
 \begin{figure}[!ht]
-	\includegraphics[width =\linewidth]{../analysis/f_diff_effectiveness}
+	\includegraphics[width =\linewidth]{./Plots/f_diff_effectiveness}
 	\caption{Comparison of closure scenario effectiveness based on
@@
 	\includegraphics[width =0.5\linewidth]{./Plots/Closure_fishing_locations_yearly}
-	\caption{The location of fishing effort before the spatial closure (a)
-		and after the spatial closure (b), and the suitable habitat for
-		population 3 (c). The site of the closure can be seen in the
-		red box on all three panels.}
+	\caption{The location of fishing effort, (a) before the spatial closure
+		and (b) after the spatial closure (years in panel), and (c) the
+		suitable habitat for population 3. The site of the closure
+		can be seen in the red box on all three panels.}
 	\label{fig:17}

### 2020-01-11 R/plot_fleet_trip.R

@@ -37,7 +37,11 @@ print(ggplot(log, aes(x = x, y = y)) +
       geom_path(data = filter(log, move_type == "CRW"), aes(colour = vessel)) +
       geom_path(data = filter(log, move_type == "Experience"), aes(colour = vessel)) +
       geom_path(data = filter(log, move_type == "OutsideMove"), aes(colour = vessel)) +
-      theme_bw() + xlab("x distance") + ylab("y distance")
+      theme_bw() +
+      theme(axis.text = element_text(size = 12, face = "bold"),
+	   axis.title = element_text(size = 14, face = "bold")
+		   ) +
+      xlab("x distance") + ylab("y distance")
       )
 }
 
@@ -71,7 +75,10 @@ print(ggplot(TotValDF, aes(x = x, y = y)) + geom_tile(aes(fill = value)) +
 	theme_bw() + #scale_colour_gradient(low = "red", high = "darkred") + 
 	expand_limits(y = c(0,sim_init[["idx"]][["ncols"]]), 
 		      x = c(0,sim_init[["idx"]][["nrows"]])) +
-      theme(legend.position = "none") +
+      theme(legend.position = "none",
+   	axis.text = element_text(size = 12, face = "bold"),
+	axis.title = element_text(size = 14, face = "bold")
+	    ) +
       xlab("x distance") + ylab("y distance")
 
 	

### 2020-01-11 R/plot_vessel_move.R

@@ -43,7 +43,11 @@ return(print(ggplot(log, aes(x = x, y = y, group = paste(vessel, trip))) +
       theme_bw() +
       expand_limits(y = c(0,sim_init[["idx"]][["ncols"]]), 
 		    x = c(0,sim_init[["idx"]][["nrows"]])) + 
-	     theme(legend.position = "none") + ylab("y distance") + 
+	     theme(legend.position = "none",
+		   axis.text = element_text(size = 12, face = "bold"),
+		   axis.title = element_text(size = 14, face = "bold")
+		   ) +
+	     ylab("y distance") + 
 	     xlab("x distance")+ 
 	expand_limits(y = c(0,sim_init[["idx"]][["ncols"]]), 
 		      x = c(0,sim_init[["idx"]][["nrows"]])
@@ -78,7 +82,10 @@ return(print(ggplot(TotValDF, aes(x = x, y = y)) + geom_tile(aes(fill = value)) 
 	theme_bw() + scale_colour_gradient(low = "red", high = "darkred") + 
 	expand_limits(y = c(0,sim_init[["idx"]][["ncols"]]), 
 		      x = c(0,sim_init[["idx"]][["nrows"]])) + 
-       theme(legend.position = "none")+ ylab("y distance") + 
+       theme(legend.position = "none",
+	     axis.text = element_text(size = 12, face = "bold"),
+	     axis.title = element_text(size = 14, face = "bold"))+ 
+	     ylab("y distance") + 
 	     xlab("x distance")
 ))
 

### 2020-01-11 analysis/Plot_fishing.R

@@ -92,7 +92,11 @@ p1 <- ggplot(filter(logs, closure == "before"), aes(x = x , y = y)) +
 	geom_polygon(data = cl, aes(long, lat, group = group), colour = "red",fill = NA) +
 	geom_point(colour = "blue", alpha = 0.2, shape = "x") +
 	expand_limits(x = c(0,100), y = c(0,100)) + facet_wrap(~year) +
-	theme_bw() + theme(plot.margin = margin(1, 0.5, 0.5, 0.5, "cm")) +
+	theme_bw() + theme(plot.margin = margin(1, 0.5, 0.5, 0.5, "cm"), 
+			   axis.text = element_text(size = 12, face = "bold"),
+			   axis.title = element_text(size = 14, face = "bold"),
+			   strip.text = element_text(size = 14, face = "bold")
+			   ) +
 	xlab("x distance") + ylab("y distance")
 
 p2 <- ggplot(cl) + geom_polygon(aes(long, lat, group = group), colour = "red",fill = NA) +
@@ -100,14 +104,21 @@ p2 <- ggplot(cl) + geom_polygon(aes(long, lat, group = group), colour = "red",fi
 	geom_point(aes(x = x, y = y), colour = "blue", 
 		   data = filter(logs, closure == "after"), 
 		   alpha = 0.2, shape = "x") +
-	theme_bw() + theme(plot.margin = margin(1, 0.5, 0.5, 0.5, "cm"))+
+	theme_bw() + theme(plot.margin = margin(1, 0.5, 0.5, 0.5, "cm"), 
+			   axis.text = element_text(size = 12, face = "bold"),
+			   axis.title = element_text(size = 14, face = "bold"),
+			   strip.text = element_text(size = 14, face = "bold")
+			   ) +
 	xlab("x distance") + ylab("y distance")
 
 
 p3 <- ggplot(cl) + geom_raster(aes(x, y, alpha = hab), data = filter(hab.df, hab > 0))+ 
 	geom_polygon(aes(long, lat, group = group), colour = "red",fill = NA) +
 	expand_limits(x = c(0,100), y = c(0,100))+
-	theme_bw() + theme(plot.margin = margin(1, 0.5, 0.5, 0.5, "cm"), 
+	theme_bw() + theme(plot.margin = margin(1, 0.5, 0.5, 0.5, "cm"),  
+			   axis.text = element_text(size = 12, face = "bold"),
+			   axis.title = element_text(size = 14, face = "bold"),
[…]

### 2020-01-11 analysis/Plots.R

@@ -136,6 +136,10 @@ colnames(stepDF2)[3] <- "data"
 
 p4 <- ggplot(stepDF2, aes(x = value, y = data)) +
 	geom_point() + theme_bw() +
+	theme(axis.text = element_text(size = 12, face = "bold"),
+	      axis.title = element_text(size = 14, face = "bold"),
+	      strip.text = element_text(size = 12, face = "bold")
+	      ) +
 	facet_wrap(~variable, ncol = 2, scale = "free") +
 	ylab("step distance or turning angle") + 
 	xlab("value (Euros)")

### 2020-01-11 analysis/Plots_Combined.R

@@ -229,9 +229,11 @@ geom_vline(xintercept = 30, linetype = 2, colour = "grey") + ylab("Fishing morta
 theme(axis.text.x = element_text(hjust = 0),
       panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
 	  axis.text = element_text(size = 12, face = "bold"),
-	  axis.title = element_text(size = 12, face = "bold")) + 
-		  scale_x_continuous(breaks = seq(0,50,10)) + 
-		  xlab("Year") + ylab(expression(Fishing~mortality~year^{-1}))
+	  axis.title = element_text(size = 12, face = "bold"),
+	  strip.text = element_text(size = 12, face = "bold")
+	  ) + 
+scale_x_continuous(breaks = seq(0,50,10)) + 
+xlab("Year") + ylab(expression(Fishing~mortality~year^{-1}))
 dev.off()
 
 ggplot(filter(combined_pop_an,basis == 'high_pop', metric == 'F', pop == "spp_3"), 
@@ -283,22 +285,26 @@ ggsave('C_trendsREV.png', width = 10, height = 8)
 
 
 z_f <- filter(combined_pop_an, basis == "high_pop", metric %in% "F", pop == "Population 3", as.numeric(year) > 39) %>%
-	group_by(scenario, timescale, res, data_type) %>% summarise(f = mean(data))
+	group_by(scenario, timescale, resolution, data_type) %>% summarise(f = mean(data))
 
 z_c <- filter(combined_pop_an, basis == "high_pop", metric == "Catch", as.numeric(year) > 39) %>%
-	group_by(scenario, timescale, res, data_type, year) %>% summarise(catch = sum(data)) %>%
-	group_by(scenario, timescale, res, data_type) %>% summarise(catch = mean(catch))
+	group_by(scenario, timescale, resolution, data_type, year) %>% summarise(catch = sum(data)) %>%
+	group_by(scenario, timescale, resolution, data_type) %>% summarise(catch = mean(catch))
 
- z <- merge(z_f, z_c, by = c("scenario","timescale", "res", "data_type"))
+ z <- merge(z_f, z_c, by = c("scenario","timescale", "resolution", "data_type"))
 
  z$data_type <- factor(z$data_type)
  z$data_type <- factor(z$data_type, levels = c("True Population", "commercial", "survey"))
 
 ggplot(z, aes(x = f, y = catch/1e3)) +
 	geom_point(aes(colour = timescale), shape = 1, size = 6) +
[…]

### 2020-01-11 analysis/effectiveness_plot.R

@@ -108,7 +108,9 @@ ggplot(f_diff, aes(x = resolution, y = diff))+
     scale_linetype_manual("Data source", values = 1:3) + 
     theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
 	  axis.text = element_text(size = 14, face = "bold"),
-	  axis.title = element_text(size = 14, face = "bold")) +
+	  axis.title = element_text(size = 14, face = "bold"),
+	  strip.text = element_text(size = 12, face = "bold")
+	  )+
     xlab("Spatial resolution (high to low)") +
     ylab("Percentage difference in Fishing mortality before and after closure")
 dev.off()

### 2020-01-11 write_up/Supplementary.tex
Final bits reviewers comments

@@
 	\caption{Fishing mortality dynamics - the daily fishing mortalities
-		across the entire spatial domain showing weekly and seasonal
-		patterns in exploitation.  Individual years are the light grey
-		lines, the mean of all years the thick black line.}
+		aggregated across the entire spatial domain showing weekly and
+		seasonal patterns in exploitation. Individual years are the
+		light grey lines, the mean of all years the thick black line.}
 	\label{fig:10}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_1}
-	\caption{Spatiotemporal habitat suitability - the suitability habitat
-		(for Population 1) for 52 separate weeks.}
-	\label{fig:5}
 \end{figure}
@@
 	\label{fig:1}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{../analysis/habitat_spwn}
+	\caption{Spawning habitat preference: the habitat suitability during
+		spawning periods for each population. The darker the colour,
+		the more suitable the habitat. The location of the spawning
+		habitat is highlighted by the squares in each panel.}
+	\label{fig:2}
 \end{figure}
@@
 \begin{figure}[!ht]
+	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_1}
+	\caption{Spatiotemporal habitat suitability - the suitability habitat
+		(for Population 1) for 52 separate weeks. The darker the
+		colour, the more suitable the habitat for the population given
+	the habitat and temperature tolerance.}
+	\label{fig:5}
+\end{figure}
+
+\begin{figure}[!ht]
 	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_2}
 	\caption{Spatiotemporal habitat suitability - the suitability habitat
-		(for Population 2) for 52 separate weeks.}
+		(for Population 2) for 52 separate weeks. The darker the
+		colour, the more suitable the habitat for the population given
+	the habitat and temperature tolerance.}
 	\label{fig:6}
@@
 	\caption{Spatiotemporal habitat suitability - the suitability habitat
-		(for Population 3) for 52 separate weeks}
+		(for Population 3) for 52 separate weeks. The darker the
+		colour, the more suitable the habitat for the population given
+	the habitat and temperature tolerance.}
 	\label{fig:7}
@@
 \begin{figure}[!ht]
-	\includegraphics[width = \linewidth]{../analysis/habitat_spwn}
-	\caption{Spawning habitat preference: the habitat suitability during
-		spawning periods for each population.}
-	\label{fig:2}
+	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_4}
+	\caption{Spatiotemporal habitat suitability - the suitability habitat
+		(for Population 4) for 52 separate weeks. The darker the
+		colour, the more suitable the habitat for the population given
+	the habitat and temperature tolerance.}
+	\label{fig:8}
 \end{figure}

### 2020-01-11 write_up/mixfishsim_ecolmod_revisions.tex
Final bits reviewers comments

@@
 There is increasing interest in technical solutions such as gear and spatial
-closures as measures to reduce unwanted catch \citep{Kennelly2002,
-	Catchpole2008, Bellido2011, Cosgrove2019} and adaptive spatial
-management strategies have been proposed as a way of reducing over-quota
-discards \citep{Holmes2011, Little2014, Dunn2014a}. However, if fisheries are
-to reduce unwanted catch through spatial avoidance, an in-depth understanding
-of spatiotemporal fishery dynamics is required. \\
+closures as measures to reduce unwanted catch\added{ which is often discarded}
+\citep{Kennelly2002, Catchpole2008, Bellido2011, Cosgrove2019}\added{.
+	A}\deleted{ and a}daptive spatial management strategies have been
+proposed as a way of reducing over-quota discards \citep{Holmes2011,
+	Little2014, Dunn2014a}. However, if fisheries are to reduce unwanted
+catch through spatial avoidance, an in-depth understanding of spatiotemporal
+fishery dynamics is required. \\
 

### 2020-01-17 write_up/mixfishsim_ecolmod_revisions.tex
Revisions per Coilin comments

@@
 	resolutions.} Aggregation across time periods has less of a negative
-impact on the closure success than over space.\deleted{ and w}\added{W}hile not
+impact on the closure success than over space. \deleted{ and w}\added{W}hile not
 as effective as when based on on the true population, closures based on high
@@
 protected species. \\ 
-
+%%
 \added{Our framework allows users to explore the assumptions in modelling
 	observational data and evaluate the underlying dynamics of such
-	approaches at a fine spatial and temporal scale. }\added{From our
-	application w}\deleted{W}e conclude that commercial data, while
-containing bias, provide a useful tool for managing catches in mixed fisheries
-if applied at the correct spatiotemporal scale. \\
+	approaches at a fine spatial and temporal scale. From our application
+	w}\deleted{W}e conclude that commercial data, while containing bias,
+provide a useful tool for managing catches in mixed fisheries if applied at the
+correct spatiotemporal scale. \\
 %%
@@
 initial location to be fished at the beginning of a trip; and
-\textit{within-trip decisions}\replaced{determined fishing locations}{, that
+\textit{within-trip decisions} \replaced{determined fishing locations}{, that
 	determines movement from one fishing spot to another} within a trip.
@@
 some of the assumptions behind the modelling approaches in identifying such
-hotspots and indeed behind spatiotemporal modelling in general\replaced{,}{ (}e.g. comparing
-GAMs, GLMMs, Random Forests and geostatistical models under different data
-generation processes as exampled by \cite{Stock2019}\deleted{)}. \\
+hotspots and indeed behind spatiotemporal modelling in general\replaced{, }{
+	(}e.g. comparing GAMs, GLMMs, Random Forests and geostatistical models
+under different data generation processes as exampled by
+\cite{Stock2019}\deleted{)}. \\
 
@@
 			square pie chart of the four populations. The area of
-			each colour is proportionate to the weight of each
+			each colour is proportional to the weight of each
 			population caught in that unit. Figure produced using

### 2020-01-17 write_up/mixfishsim_ecolmod_revisions.tex
Edited to M&M

--- 2020-01-11 write_up/mixfishsim_ecolmod_revisions.tex
@@
 
-\usepackage[draft]{changes}
+\usepackage[draft]{changes}%\usepackage[draft]{changes}
 
@@
 
-\address[1]{Galway-Mayo Institute of Technology (GMIT), Dublin Road, Galway,
+\address[1]{Marine and Freshwater Research Centre, Galway-Mayo Institute of Technology (GMIT), Dublin Road, Galway,
 	Ireland} 
@@
 interactions we developed a highly resolved spatiotemporal discrete-event
-simulation model ('MixFishSim`) incorporating: i) delay-difference population
+simulation model (`MixFishSim')\textcolor{blue}{[CM: I think \emph{MixFishSim} is more effective]} incorporating: i) delay-difference population
 dynamics, ii) population movement using Gaussian Random Fields to simulate
@@
 	draw inference on the underlying community structures. W}\added{We
-	applied the framework to draw}\deleted{compared} inference\deleted{s}
-\added{on community structure} \added{when using data generated from
-}\deleted{based on}: commercial catch, a simulated fixed-site sampling survey
+	applied `MixFishSim' to\deleted{draw}}\deleted{compared} infer\deleted{ence}\deleted{s}
+\added{\deleted{on}community structure} \added{when using data generated from:}
+\deleted{based on}commercial catch, a\deleted{simulated} fixed-site sampling survey
 design and the true \added{(simulated)} underlying populations.
-\deleted{W}\added{In doing so w}e \deleted{i)}establish the potential
-limitations of fishery-dependent data in providing a robust picture of
-spatiotemporal distributions\deleted{; and then ii) simulated an area closure
+\deleted{W}\deleted{\added{In doing so w}}\added{W}e \added{thereby} \deleted{i)}establish the potential
+limitations of fishery-dependent data in providing a robust \replaced{characterisation}{picture} of
+spatiotemporal distributions.\deleted{; and then ii) simulated an area closure
 	based on areas defined from the different data sources at a range of
@@
 	temporal scale. In application to a mixed fishery exploiting four
-	different populations w} \added{W}e found different spatial patterns
-were evident and that the effectiveness of the spatial closure reduced when
+	different populations w} \deleted{\added{W}e found d}\added{D}ifferent spatial patterns
+were evident and \deleted{that }the effectiveness of the spatial closure reduced when
 data were aggregated across larger spatial areas. \deleted{; and then
-	ii)}\added{We then simulated an area closure based on areas defined
+	ii)}\deleted{\added{We then simulated an area closure based on areas defined
 	from the different data sources at a range of temporal and spatial
-	resolutions.} Aggregation across time periods has less of a negative
-impact on the closure success than over space.\deleted{ and w}\added{W}hile not
+	resolutions.}} \added{A simulated area closure showed that} \replaced{a}{A}ggregation across time periods has less of a negative
+impact on the closure success than \added{aggregation} over space. \deleted{ and w}\added{W}hile not
 as effective as when based on on the true population, closures based on high
@@
 
-\added{Our framework allows users to explore the assumptions in modelling
+\added{\replaced{MixFishSim}{Our framework} allows users to explore the assumptions in modelling
 	observational data and evaluate the underlying dynamics of such
@@
 
-Identifying appropriate spatial scales for fisheries closures has been a
-highlighted as crucial to their success \citep{Costello2010, Dunn2016}.
+Identifying appropriate spatial scales for fisheries closures \deleted{has been a
+highlighted a}\added{i}s crucial to their success \citep{Costello2010, Dunn2016}.
 Inference on fisheries spatial dynamics is hampered where spatial information
@@
 does not allow identification of spatial features it may lead to poorly sited
-closures which are ineffectual or have unintended consequences. For example,
+closures \replaced{that}{which} are ineffectual or have unintended consequences. For example,
 increased benthic impact on previously unexploited areas from the cod closure
@@
 \citep{Rijnsdorp2011, Bailey2018} where they search for areas with high catches
-and then use experience to return to areas where they've experienced high catch
+and then use experience to return to areas where they have experienced high catch
 in the past. This leads to an inherently biased sampling where target species
@@
 \begin{enumerate}
-	\item Do different source of sampling-derived fisheries data
+	\item Do different source\added{s} of sampling-derived fisheries data
 		reflect\deleted{s} the underlying community structure? 	
-	\item How does data aggregation and data source impact on the success
+	\item How do\deleted{es} data aggregation and data source impact on the success
 		of spatial fisheries management measures?
@@
 different spatial and temporal aggregations, the real (simulated) population
-distributions to samples from fisheries-dependent and fisheries independent
+distributions to samples from fisheries-dependent and fisheries independent \textcolor{blue}{[CM: hyphenate or don't both, i.e., fishery-independent]}
 catches to test if these are a true reflection of the relative density of the
@@
 proportion as time progressed, experience of profitable catches built up in the
-same month from previous years and from the previous trip.  'Profitable' in
+same month from previous years and from the previous trip.  `Profitable' in
 this context was defined as the locations where the top 70 \% of expected
@@
 			population caught in that unit. Figure produced using
-			the R package 'mapplots' (\cite{Gerritsen2014}.}
+			the R package `mapplots' (\cite{Gerritsen2014}.}
 	}

### 2020-01-26 write_up/mixfishsim_ecolmod_revisions.tex
Incorparting Coilin and Jean-Marc's comments

@@
 
-\usepackage[draft]{changes}%\usepackage[draft]{changes}
+\usepackage[final]{changes}
 
@@
 interactions we developed a highly resolved spatiotemporal discrete-event
-simulation model (`MixFishSim')\textcolor{blue}{[CM: I think \emph{MixFishSim} is more effective]} incorporating: i) delay-difference population
-dynamics, ii) population movement using Gaussian Random Fields to simulate
-patchy, heterogeneously distributed \added{and moving fish} populations, and
-iii) fishery dynamics for multiple fleet characteristics based on population
-targeting under an explore-exploit strategy.\deleted{ This is implemented via a mix of
-correlated random walk movement (for exploration) and learned behaviour (for
-exploitation) phases of the fisheries. }\\ 
+simulation model \emph{MixFishSim} incorporating: i) delay-difference
+population dynamics, ii) population movement using Gaussian Random Fields to
+simulate patchy, heterogeneously distributed \added{and moving fish}
+populations, and iii) fishery dynamics for multiple fleet characteristics based
+on population targeting under an explore-exploit strategy.\deleted{ This is
+	implemented via a mix of correlated random walk movement (for
+	exploration) and learned behaviour (for exploitation) phases of the
+	fisheries. }\\ 
 %%
@@
 	draw inference on the underlying community structures. W}\added{We
-	applied `MixFishSim' to\deleted{draw}}\deleted{compared} infer\deleted{ence}\deleted{s}
-\added{\deleted{on}community structure} \added{when using data generated from:}
-\deleted{based on}commercial catch, a\deleted{simulated} fixed-site sampling survey
-design and the true \added{(simulated)} underlying populations.
-\deleted{W}\deleted{\added{In doing so w}}\added{W}e \added{thereby} \deleted{i)}establish the potential
-limitations of fishery-dependent data in providing a robust \replaced{characterisation}{picture} of
-spatiotemporal distributions.\deleted{; and then ii) simulated an area closure
-	based on areas defined from the different data sources at a range of
-	temporal and spatial resolutions.}\deleted{Our framework allows users
-	to explore the assumptions in modelling observational data and evaluate
-	the underlying dynamics of such approaches at a fine spatial and
-	temporal scale. In application to a mixed fishery exploiting four
-	different populations w} \deleted{\added{W}e found d}\added{D}ifferent spatial patterns
-were evident and \deleted{that }the effectiveness of the spatial closure reduced when
-data were aggregated across larger spatial areas. \deleted{; and then
-	ii)}\deleted{\added{We then simulated an area closure based on areas defined
-	from the different data sources at a range of temporal and spatial
-	resolutions.}} \added{A simulated area closure showed that} \replaced{a}{A}ggregation across time periods has less of a negative
-impact on the closure success than \added{aggregation} over space. \deleted{ and w}\added{W}hile not
-as effective as when based on on the true population, closures based on high
-catch rates observed in commercial data were still able to reduce fishing on a
-protected species. \\
-
-\added{\replaced{MixFishSim}{Our framework} allows users to explore the assumptions in modelling
+	applied \emph{MixFishSim} to\deleted{draw}}\deleted{compared}
+infer\deleted{ence}\deleted{s} \added{\deleted{on}community structure}
+\added{when using data generated from:} \deleted{based on}commercial catch,
+a\deleted{simulated} fixed-site sampling survey design and the true
+\added{(simulated)} underlying populations.  \deleted{W}\deleted{\added{In
+		doing so w}}\added{W}e \added{thereby} \deleted{i)}establish
+the potential limitations of fishery-dependent data in providing a robust
+\replaced{characterisation}{picture} of spatiotemporal distributions.\deleted{;
+	and then ii) simulated an area closure based on areas defined from the
+	different data sources at a range of temporal and spatial
+	resolutions.}\deleted{Our framework allows users to explore the
+	assumptions in modelling observational data and evaluate the underlying
+	dynamics of such approaches at a fine spatial and temporal scale. In
+	application to a mixed fishery exploiting four different populations w}
+\deleted{\added{W}e found d}\added{D}ifferent spatial patterns were evident and
+\deleted{that }the effectiveness of the spatial closure reduced when data were
+aggregated across larger spatial areas. \deleted{; and then
+	ii)}\deleted{\added{We then simulated an area closure based on areas
+		defined from the different data sources at a range of temporal
+		and spatial resolutions.}} \added{A simulated area
+	closure showed that} \replaced{a}{A}ggregation across time periods has
+less of a negative impact on the closure success than \added{aggregation} over
+space. \deleted{ and w}\added{W}hile not as effective as when based on on the
+true population, closures based on high catch rates observed in commercial data
+were still able to reduce fishing on a protected species. \\
+
+\added{Our framework allows users to explore the assumptions in modelling
 	observational data and evaluate the underlying dynamics of such
-	approaches at a fine spatial and temporal scale. }\added{From our
+	approaches at a fine spatial and temporal resolutions. From our
 	application w}\deleted{W}e conclude that commercial data, while
@@
 process to define suitable habitat for different populations. As the precise
-locations of the fish are known directly rather than inferred from sampling
-or commercial catch, we can use the population model to validate how inference
-from fisheries-dependent and fisheries independent sampling relates to the real
+locations of the fish are known directly rather than inferred from sampling or
+commercial catch, we can use the population model to validate how inference
+from fisheries-dependent and fisheries-independent sampling relates to the real
 community structure in a way we could not with real data. We ii) compare, at
 different spatial and temporal aggregations, the real (simulated) population
-distributions to samples from fisheries-dependent and fisheries independent \textcolor{blue}{[CM: hyphenate or don't both, i.e., fishery-independent]}
+distributions to samples from fisheries-dependent and fisheries-independent
 catches to test if these are a true reflection of the relative density of the
@@
 efficient computation by allowing for sub-modules implemented on time-scales
-appropriate to capture the characteristic of the different processes (Figure
-1). The following sub-modules were included to capture the full system: 1)
-Population dynamics, 2) Recruitment dynamics, 3) Population movement, 4)
+appropriate to capture \deleted{the }characteristic\added{s} of the different processes (Figure
+1). \replaced{S}{The following s}ub-modules \deleted{were included }to capture the full system \added{comprised}: 1)
+\replaced{p}{P}opulation dynamics, 2) \replaced{r}{R}ecruitment dynamics, 3) \replaced{p}{P}opulation movement, 4)
 fishery dynamics.\\
 
-Population dynamics \added{for any number of species, as chosen by the user}
+Population dynamics \added{for any number of species, as chosen by the user,}
 operate on a daily time-step \added{(with recruitment occurring only during
@@
 on a weekly time-step, with the fishing module operating on a tow-by-tow basis
-(i.e.  multiple events a day). \\
+(i.e.\added{,} multiple events a day). \\
 
@@
 The basic population level processes were simulated using a modified two-stage
-Deriso-Schnute delay difference model which models the fish populations in
+Deriso-Schnute delay difference model \replaced{that}{which} models the fish populations in
 terms of aggregate biomass of recruits and mature components rather than
-keeping track of individuals\citep{Deriso1980, Schnute1985, Dichmont2003}. A
+keeping track of individuals \citep{Deriso1980, Schnute1985, Dichmont2003}. A
 daily time-step was chosen to discretise continuous population processes on a
@@
 population size.  Biomass for each cell $c$ was incremented each day $d$ as
-follows (the full parameter list is detailed in Table \ref{tab: pop_variable}): 
+follows (\replaced{see}{the full parameter list is detailed in } Table \ref{tab: pop_variable} \added{for all parameter details}): 
 \begin{equation}
@@
 	\times \\  
-	& \left(B_{c,d-1} \cdot \mathrm{e}^{-Z_{c,d-1}} + Wt_{R-1} \cdot \left( \alpha_{d-1} \cdot
+	& \left(B_{c,d-1} \cdot \mathrm{e}^{-Z_{c,d-1}} + W_{R-1} \cdot \left( \alpha_{d-1} \cdot
 	R_{\tilde{y}\left(c\right)}\right) \right)
 	\hspace{0.9cm} + \\
-	& Wt_{R} \cdot \left( \alpha_{d} \cdot R_{\tilde{y} \left(c\right)}
+	& W_{R} \cdot \left( \alpha_{d} \cdot R_{\tilde{y} \left(c\right)}
 	\right) \\
@@
 \end{equation}
-where $\rho$ is Brody's coefficient, shown to be equal to $\mathrm{e}^{-K}$
-when $K$ is the growth rate from a von Bertalanffy logistic growth model
-\citep{Schnute1985}. $Wt_{R-1}$ is the average weight of fish prior to
-recruitment, while $Wt_{R}$ is the average recruited weight. $\alpha_{d}$
-represents the proportion of fish recruited during that day for the year, while
-$R_{c,\tilde{y}(c)}$ is the annual recruits in year $y$ for cell $c$. \\
+where $\rho$ is Brody's coefficient\textcolor{blue}{(Check)}, shown to be equal
+to $\mathrm{e}^{-K}$ when $K$ is the \deleted{growth }rate \added{at which the
+	asymptote is approached} from a von Bertalanffy \deleted{logistic
+}growth model \citep{Schnute1985}. $W_{R-1}$ is the average weight of fish
+prior to recruitment, while $W_{R}$ is the average recruited weight.
+$\alpha_{d}$ represents the proportion of fish recruited during that day for
+the year, while $R_{c,\tilde{y}(c)}$ is the annual recruits in year $y$ for
+cell $c$. \\
 
@@
 those across all fleets and vessels, $C_{c, d} =
-\sum\limits_{fl=1}^{FL}\sum\limits_{v=1}^{V} E_{fl, v, c, d} \cdot Q_{fl} \cdot
-D_{c, d}$ with $fl$ and $FL$ the fleet and total number of fleets, $v$ and $V$
-the vessel and total number of vessels respectively and $E_{fl,v,c,d}$ and
-$Q_{fl}$ fishing effort and catchability of the gear, and $D_{c,d}$ is the
-density of the population at the location fished. \\
+\sum\limits_{fl=1}^{FL}\sum\limits_{v=1}^{V_{fl}} E_{fl, v, c, d} \cdot Q_{fl}
+\cdot D_{c, d}$ with $fl$ and $FL$ the fleet and total number of fleets, $v$
+and $V_{fl}$ the vessel and total number of vessels per fleet respectively and
+$E_{fl,v,c,d}$ and $Q_{fl}$ fishing effort and catchability of the gear, and
+$D_{c,d}$ is the density of the population at the location fished. \\
 
@@
 	\begin{split}
-	\bar{R}_{c,d} = & \frac{(\alpha \cdot S_{c,d})}{(\beta + S_{c,d})} \\
-	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\sigma^2)]
+	\bar{R}_{c,d} = & \frac{(\alpha \deleted{\cdot} S_{c,d})}{(\beta + S_{c,d})} \\
+	     \added{\ln(}R_{c,d}\added{)} \sim & \deleted{\log} N[(\replaced{\ln}{\log}(\bar{R}_{c,d}),\sigma^2)]
 	\end{split}
@@
 	\bar{R}_{c,d} = & B_{c,d} \cdot \mathrm{e}^{(\alpha - \beta \cdot B_{c,d})} \\	
-   	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\log(\sigma^2))]
+	\ln(R_{c,d}) \sim & N[(\ln(\bar{R}_{c,d}),\sigma^2)]
 	\end{split}
 \end{equation}
-where $\alpha$ is the maximum productivity per spawner and $\beta$ the density
-dependent reduction in productivity as the SSB increases.
+where $\alpha$ is the maximum productivity per spawner and $\beta$ the
+density-dependent reduction in productivity as the SSB increases.
 
@@
 cells, and random (diffusive) movement, governed by a stochastic process where
-movement between adjacent cells is described by a set of probabilities
-\added{which are affected by the suitability of habitat, temperature in a cell
-	and the thermal tolerance of a population to that temperature}.\\
+movement between adjacent cells is described by a set of probabilities.
+\added{Stochastic probabilities are affected by the suitability of habitat,
+	temperature in a cell and the thermal tolerance of a population to that
+	temperature}.\\
 
 \added{The combined process results in a population structure and movement
-pattern unique to each population, with population movement occurring on a weekly
-basis. The decision to model population movement on a weekly timescale was to
-reflect that fish tend to aggregate in species specific locations that have
-been observed to last around one to two weeks \citep{Poos2007}. Therefore this
-process approximated the demographic shifts in fish populations throughout a
-year with seasonal spawning patterns }(Figure \ref{S-fig:5}).
+	pattern unique to each population, with population movement occurring
+	on a weekly basis. \replaced{M}{The decision to m}odel\added{ing}
+	population movement on a weekly timescale\deleted{ was to}
+	reflect\added{s} that fish tend to aggregate in
+	species\added{-}specific locations\deleted{ that have been} observed to
+	last \replaced{between}{around } one \replaced{and}{to} two weeks
+	\citep{Poos2007}. Therefore this process approximated the demographic
+	shifts in fish populations throughout a year with seasonal spawning
+	patterns }(Figure \ref{S-fig:5}).
 
@@
 determines the smoothness of the process. \added{We use the most commonly used
-	Matérn covariance structure as it is a flexible form that under certain
-	conditions is of the same form as an exponential function and
+	Matérn covariance structure as it is a flexible form that \replaced{contains the}{under certain
+	conditions is of the same form as an} exponential \added{and double exponential as special cases}\deleted{ function} and
 	it}\deleted{This} enables us to model the spatial autocorrelation
 observed in animal populations where density is more similar in nearby
-locations, \added{but that correlation decreases non-linearly}
+locations\deleted{, \added{but that correlation decreases non-linearly}}
 \citep{Tobler1970, F.Dormann2007, Poos2007}. We change the parameters to
@@
 
-A time-varying temperature covariate changes the interaction between time and
+A time-varying temperature covariate changes the \deleted{interaction between time and}
 suitable habitat on a weekly time-step. Each population $p$ was assigned a
 thermal tolerance with mean, $\mu_{p}$ and standard deviation, $\sigma_{p}$ so that
-each cell and population temperature tolerance is defined that:
+each cell and population temperature tolerance is defined \replaced{as}{that}:
 \begin{equation}
-	Tol_{c, p, wk} = \frac{1}{ \sqrt (2\pi \cdot \sigma^2_{p})} \cdot \exp(-
-		\frac{(T_{c, wk} - \mu_{p})^2}{2 \cdot \sigma^2_{p}} )	
+	Tol_{c, p, wk} = \frac{1}{ \sqrt{2\pi  \sigma^2_{p}}}  \exp \left(-
+		\frac{(T_{c, wk} - \mu_{p})^2}{2  \sigma^2_{p}} \right)	
 \end{equation}
@@
 and $\sigma_{p}$ the mean and standard deviation of the population temperature
-tolerance. The variables, their meaning and units for population movement is
-provided in Table \ref{tab:pop_move}. \\
+tolerance \replaced{(see Table \ref{tab:pop_move} for variable descriptions).}{. The variables, their meaning and units for population movement is
+provided in Table \ref{tab:pop_move}}. \\
 
@@
 
-Each fleet of \textit{n} vessels was characterised by both a general
+Each fleet of \textit{$n_{fl}$} vessels was characterised by both a general
 efficiency, $Q_{fl}$, and a population specific efficiency, ${Q_{fl, p}}$ which
-are each bound by [0,1]. The product of these parameters [$Q_{fl} \cdot
-Q_{fl, p}$] affects the overall catch rates for the fleet and the preferential
-targeting of one species over another. This, in combination with the
-parameter choice for the step-function defined below (as well as some
-randomness from the exploratory fishing process) determined the preference of
-fishing locations for the fleet.
+are each bound by [0,1]. The product of these parameters [$Q_{fl} \cdot Q_{fl,
+	p}$] affects the overall catch rates for the fleet and the preferential
+targeting of one species over another. This, in combination with the parameter
+choice for the step-function defined below (as well as some randomness from the
+exploratory fishing process) determined the preference of fishing locations for
+the fleet.
 
@@
 retains some degree of stochasticity, that can be controlled separately, but is
-determined by the relationship: 
+determined by the relationship: (\textcolor{blue}{[CM: use $\ln$ where we use the natural logarithm.
+Double-check this equation is right as per the code.
+As it looks different here: \url{https://github.com/pdolder/MixFishSim/blob/master/R/step_length.R]}.
+There it looks to simplify to $b_2(b_1/b_2)^{Rev/b_3}$, assuming parameters are positive.})
 \begin{equation}
@@
 
-\subsection{Fisheries independent survey}
+\subsection{Fisheries-independent survey}
 
@@
 population-specific movement rates (Table \ref{tab:1}).  \added{The population
-demographics were defined to broadly represent three mobile low-medium value
+demographics were chosen to broadly represent three mobile low-medium value
 groundfish species and one high value species with low mobility, with the
-dynamics hypothetical but as you might expect to find in a typical demersal
+dynamics hypothetical but \deleted{as you} might \added{be} expect\added{ed} \deleted{to find }in a typical demersal
 fishery.}
@@
 
-The fleets were calibrated to reflect five different characteristic fisheries
+\replaced{F}{The f}leets were calibrated to reflect five different characteristic fisheries
 with unique exploitation dynamics (Table \ref{tab:2}). By setting different
 catchability coefficients ($Q_{fl, p}$) we create different targeting
-preferences between the fleets and hence spatial dynamics.  The learned random
+preferences between the fleets and hence \added{different} spatial dynamics.  The learned random
 walk process implies that within a fleet different vessels have different
@@
 the new fishing location. This probability was based on a logistic sigmoid
-function with a lower asymptote of 0 and upper asymptote of 0.95, and a growth
-rate that ensures the upper asymptote (where decisions are mainly based on past
+function with a lower asymptote of 0 and upper asymptote of 0.95, and a \replaced{slope}{growth
+rate} that ensures the upper asymptote (where decisions are mainly based on past
 knowledge) is reached approximately halfway through the simulation.  \\
@@
 stations fished each year, starting on day 92 and ending on day 112 (5 stations
-per day) with same catchability parameter ($Q_{p} = 1$) for all populations $p$.
+per day) with same catchability parameter ($Q_{p} = 1$) for all populations\deleted{ $p$}.
 This approximates a real world survey design with limited seasonal and spatial
@@
 		knowledge of the spatial population dynamics.
-	\item Close area covering top 5 \% of catch rates 
+	\item Close area covering top 5 \% of catch rates.
 \end{enumerate}
@@
 		grid and 20 x 20 grid,
-	\item \textbf{closure basis:} highest 5 \%  of catch rates for the
-		protected population
+
 \end{itemize}
@@
 exploits three different fishing grounds, each of them multiple times (Figure
-\ref{fig:mv}(A)), while across several trips fishing grounds that are further
-apart are fished (Figure \ref{fig:mv} (B)). These different locations relate to
+\ref{fig:mv}A), while across several trips fishing grounds that are further
+apart are fished (Figure \ref{fig:mv}B). These different locations relate to
 areas where the highest revenue were experienced, as shown by Figure
-\ref{fig:mv} (D), where several vessels tracks are overlaid on the revenue
-field, i.e. $$Rev_{c} = \sum^P_{p=1} B_{c,p} \cdot Q_{fl,p} \cdot Pr_{p}$$
+\ref{fig:mv}D, where several vessels tracks are overlaid on the revenue
+field.
 
@@
 
-The \deleted{aggregated }catch composition\added{aggregated at different
+\deleted{The }\deleted{aggregated }\replaced{C}{c}atch composition \added{aggregated at different
 	spatial resolutions} from each of the data sources (\deleted{which
@@
 from a lack of fishing activity (particularly in the lower left part of the
-sampling domain). The survey data at this spatial resolution displays very
+sampling domain). \replaced{S}{The s}urvey data at this spatial resolution displays very
 sparse information about the spatial distributions of the populations. The
@@
 
-The commercial data on a weekly basis shows some of the same patterns as the
-true population, though the population 1 \deleted{(in red)} is less well
-represented and some weeks are missing catches from the area. Here, weekly and
-monthly compositions were nearly identical (Figure \ref{fig:2}; Table
-\ref{tab:7}). \deleted{Again, y}\added{Y}early values head a similar mean but
-smaller standard deviation.\\
-
-The survey data was only available on an annual basis, and showed again a
-slightly different composition from the true population and the commercial
-data; in particular a greater proportion of population 4 (Figure \ref{fig:2}).
+\replaced{Weekly}{The} commercial data \deleted{on a weekly basis }shows some
+of the same patterns as the true population, though \deleted{the }population 1
+\deleted{(in red)} is less well represented and some weeks are missing catches
+from the area. Here, weekly and monthly compositions were nearly identical
+(Figure \ref{fig:2}; Table \ref{tab:7}). \deleted{Again, y}\added{Y}early
+values h\deleted{e}ad a similar mean but smaller standard deviation. The survey
+data was only available on an annual basis, and showed again a slightly
+different composition from the true population and the commercial data; in
+particular a greater proportion of population 4 (Figure \ref{fig:2}).
 
@@
 after the closure was the population (72 \% showing that the closures were
-effective for population 3), followed by data resolution (21 \%), data type (7
+effective for population 3), followed by \added{spatial} data resolution (21 \%), data type (7
 \%) with the least important factor the timescale ($<$ 1 \%). In general the
@@
 practices if potential biases in data are to be understood and taken into
-account (Figures \ref{S-fig:9}, \ref{fig:mv}). \\
+account (Figures \ref{fig:mv} and \ref{S-fig:9}). \\
 
@@
 spatially limited due to the ``hotspots" of commercially valuable species being
-fished. Similarly, despite the even spatial coverage the survey was able to
-capture some of the same spatial patterns as the true population, but missed
+fished. Similarly, despite \deleted{the }even spatial coverage the survey \deleted{was able to
+}capture\added{d} some of the same spatial patterns as the true population, but missed
 others due to gaps between survey stations limiting spatial and temporal
@@
 there was greater spatial heterogeneity over the spatial domain than
-experienced in individual locations over the course of the year (Figure
+experienced in \replaced{given}{individual} locations over the course of the year (Figure
 \ref{S-fig:9}). \\
@@
 point) in time. The monthly data shows some consistency between the real
-population and commercial data for population 2 - 4, though population 1 remains
-under-represented.  On an annual basis, interestingly the commercial data under
-represents the first species (in red) while the survey over represents species
-1. This is likely due to the biases in commercial sampling, with the fisheries
-not targeting the areas where population 1 are present and the survey sampling
-areas where population 1 is more abundant than on average. This indicates that
-fixed closures, at the right resolution, when based on commercially derived
-data have the potential to reduce\deleted{d} fishing mortality. The likely cost
-of poor spatial and temporal resolution is associated with reduced
-effectiveness and potentially closing fishing opportunities for other fisheries
-(Figure \ref{fig:ce}). \\
+population and commercial data for population 2 - 4, though population 1
+remains under-represented.  On an annual basis, interestingly the commercial
+data under represents the first species while the survey over represents
+species 1. This is likely due to the biases in commercial sampling, with the
+fisheries not targeting the areas where population 1 are present and the survey
+sampling areas where population 1 is more abundant than on average. This
+indicates that fixed closures, at the right resolution, when based on
+commercially derived data have the potential to reduce\deleted{d} fishing
+mortality. The likely cost of poor spatial and temporal resolution is
+associated with reduced effectiveness and potentially closing fishing
+opportunities for other fisheries (Figure \ref{fig:ce}). \\
 
@@
 and down) as a side-effect of closures to protect one species.  This indicates
-the importance in considering fishing effort reallocation following spatial
+the importance \replaced{of}{in} considering fishing effort reallocation following spatial
 closures, and our simulation allows us to consider the spatiotemporal reasons
@@
 We consider that the increased availability of high resolution catch and
-locational information from commercial fisheries will require it to be a key
+locational information from commercial fisheries will \replaced{make}{require} it \deleted{to be }a key
 source of data for ensuring management is implemented at the right scale in
@@
 importance of capturing in-year dynamics in estimating stock status
-\citep{Liu2013}; at sea sampling scheme designs to deliver unbiased estimates
+\citep{Liu2013}; at\added{-}sea sampling scheme designs to deliver unbiased estimates
 of population parameters \citep{Cotter2007, Kimura2006}; adaptive management
@@
 main features of the data are captured, yet maintaining enough data coverage
-that the features can be distinguished. We found in our application that there
-was greater spatial heterogeneity than temporal heterogeneity and that when
-using aggregated data to define spatial closures coarser temporal resolution
-(months instead of weeks) could still achieve the same results in reducing
-exploitation rates of a vulnerable species at the highest temporal resolution
-data. Conversely, reducing the spatial resolution had a negative effect on the
-effectiveness of the measures (though importantly, there was still some benefit
-even with coarse spatial resolution). \\
-
-While any findings are likely to be case specific, our findings emphasise the
-need to understand population demographics, habitat use and movement rates in
-designing any closure scenario based on observational sampling. This
-information can then be used to set the bounds on data aggregation used in
-modelling studies aimed at informing the management measures. \\
-
-\textit{MixFishSim} has numerous potential additional applications as it
+that the features can be distinguished. We found \deleted{in our application
+}greater spatial than temporal heterogeneity. When using aggregated data to
+define spatial closures coarser temporal resolution (months instead of weeks)
+could still achieve the same results in reducing exploitation rates of a
+vulnerable species at the highest temporal resolution data. Conversely,
+reducing the spatial resolution had a negative effect on the effectiveness of
+the measures \deleted{(}though\added{,} importantly, there was still some
+benefit even with coarse spatial resolution\deleted{)}. \\
+
+While \deleted{any findings are likely to be} case\added{-}specific, our
+findings emphasise the need to understand population demographics, habitat use
+and movement rates in designing any closure scenario based on observational
+sampling. This information can then be used to set the bounds on data
+aggregation used in modelling studies aimed at informing the management
+measures. \\
+
+\deleted{\textit{MixFishSim} has numerous potential additional applications as it
 enables the user to apply methods to a fisheries system where there is detailed
@@
 world data due to limitations of data collection. That way the knowledge gained
-through simulation can inform the future design of management measures.
+through simulation can inform the future design of management measures.}
 
@@
 
-\section*{Appendices}
+\newpage
 

### 2020-01-26 write_up/parameter_tables.tex
Addressing reviewer comments
Incorparting Coilin and Jean-Marc's comments

@@
 		$C_{c,d}$ & Catch from cell $c$ for day $d$ & kg \\
-		$F_{c,d}$ & Instantaneous rate of fishing mortality in cell $c$
-		on day $d$ & - \\
-		$M_{c,d}$ & Instantaneous rate of natural mortality in cell $c$
-		on day $d$ & - \\
+		$F_{c,d}$ & Rate of fishing mortality in cell $c$
+		on day $d$ & $d^{-1}$ \\
+		$M_{c,d}$ & Rate of natural mortality in cell $c$
+		on day $d$ & $d^{-1}$ \\
 		$B_{c,d}$ & Biomass in cell $c$ on day $d$ & kg \\
@@
 		\hhline{===}
-		$\tilde{R}_{c,d}$ & is the recruitment in cell $c$ for day $d$ & $d^{-1}$ \\
-		$B_{c,d}$ & biomass in cell $c$ for day $d$ & $d^{-1}$ \\
+		$\tilde{R}_{c,d}$ & is the number of fish recruited in cell $c$ for day $d$ & $d^{-1}$ \\
 		$\alpha$ & the maximum recruitment rate (Beverton Holt)
-		or maximum productivity per spawner (Ricker) & kg  \\
+		or maximum productivity per spawner (Ricker) & number fish  \\
 		$\beta$ & the stock size required to produce half the maximum rate
 		of recruitment (Beverton Holt) or density dependent reduction
-		in productivity per capita of SSB & kg \\
+		in productivity per capita of SSB & number fish \\
 		\bottomrule
@@
 	\caption{Description of variables for population movement sub-module.}
+	\label{tab:pop_move}
 	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
@@
 	\caption{Description of variables for fleet dynamics sub-module.}
+	\label{tab:fleet_dyn}
 	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
@@
 		$L_{p}$ & Landings of population $p$ & kg \\
-		$Pr_{p}$ & Average price of population $p$ & \euro
-		\hspace{0.1cm} kg$^{-1}$ \\
+		$Pr_{p}$ & Average price of population $p$ & \euro.kg$^{-1}$ \\
 		Le & Step length for vessel & - \\

### 2020-01-31 write_up/reviewer_response_seperate.tex
Revised manuscript

--- 2019-12-20 write_up/reviewer_response.tex
@@
 \usepackage{booktabs}
-
+\usepackage{xcolor}
+%%\usepackage[final]{changes}
 \begin{document}
-
-\large
-
-Address here: cover letter on other computer. \\
-\\
-Dear xyz, \\
-RE: Ms. No. ECOMOD-19-631 \\
-\\
-Thank you for your email of 5 December 2019 with the favourable 'minor
-revisions` review of our manuscript submission. We have reviewed all the
-comments made by the editor and the two reviewers and addressed them
-accordingly. We thank the reviewers for a constructive review which undoubtedly
-improves the manuscript and we found little reason to disagree with their
-comments. A summary of our changes are presented overleaf.  \\
-
-We look forward to hearing back positively on these changes, and publication of
-the manuscript in Ecological Modelling. \\
-\\
-Kind Regards,\\
-\\
-Paul J. Dolder, Cóilín Minto, Jean-Marc Guarini \& Jan Jaap Poos
-
-\newpage
-
-\begin{landscape}
 
@@
 Modelling.
-} \\
+}
 
 Thank you for your comments, we have provided a detailed response to each of
-the points made by the reviewers; we hope this satisfies your requirements and
-look forward to seeing the manuscript published. \\
+the points made by the reviewers along with a track-changed (as well as a
+`clean') revision of the manuscript. In addition, we provide a short vignette
+detailing an example application and R code for the framework, which we hope
+will widen accessibility and take up of the modelling framework. We hope that
+together this satisfies your requirements and look forward to seeing the
+manuscript published. \\
 
@@
 	researchers and managers. I recommend that it be published after minor
-	revisions.} \\
+	revisions.}
 
-Thank etc..
+Thank you, we are grateful for your comments that have improved our manuscript
+and look forward to our work reaching and being used by a broad audience.
 
-\large
 	\begin{center}
-	\begin{longtable}{p{12cm} | p{12cm}}
+	\begin{longtable}{p{8cm} | p{8cm}}
 %	\caption{Highly resolved spatiotemporal simulations for exploring mixed
@@
 		\\
-		\textbf{Abstract} & \\
+\textbf{Asbstract} & \\
 \\
@@
 the package name, it would be nice if the term was included in the abstract so
-the paper will show up in the search too. & Thank you, we agree and have
-included in the first sentence of the abstract. \\
+the paper will show up in the search too. & We have included
+\textit{MixFishSim} in the first sentence of the abstract. \\
 \\
-"true underlying populations" - somehow make sure readers know this is
+``true underlying populations" - somehow make sure readers know this is
 referring to simulated populations. & We have changed to "true (simulated)
-underlying populations" \\
+underlying populations" on line 10 of the abstract. \\
 \\
@@
 in key words or abstract; people searching for that term would be glad to find
-this paper, I would think! & \\
+this paper, I would think! & Done, see keywords. \\ 
 \\
@@
 for each should be adequate, with a conclusion that states the usefulness of
-the framework for answering a number of fisheries management questions.  & \\
+the framework for answering a number of fisheries management questions.  &
+We've worked to shorten and strengthen the abstract as suggested. \\
 \\
 \hline
+\\
 \textbf{Introduction} &  \\
 \\
-Nice introduction to the need for the simulation framework & Thank you, we have
-kept this text unchanged. \\
+Line 62: ``Do different sources of sampling-derived fisheries data reflect"… &
+Corrected at line 73. \\
 \\
-Line 62: "Do different sources of sampling-derived fisheries data reflect"… &
-Thanks, corrected. \\
-\\
-		hline
+
 		\textbf{Methods} &  \\
@@
 a Gaussian or other type of covariance structure? & We used the Matérn
-covariance structure as it allows for a non-linear decrease in correlation as
-distance increases and is flexible, in that it reverts to an exponential form
-under specific conditions. As such it is capable of taking any number of forms,
-as required. Alternative covariance structures could also be used, but Matérn
-is the most commonly used. We've added text to say "We use the most commonly
+covariance structure as it is flexible, and contains the exponential form as a
+special case.  We've added text at line 170 to say ``We use the most commonly
 used Matérn covariance structure as it is a flexible form that under certain
@@
 It would be helpful to have explanation of thermal tolerance earlier than line
-155 & We have now added a sentence at the beginning of the section that reads
-"[described by a set of probabilities] which are affected by the suitability of
-habitat, temperature in a cell and the thermal tolerance of a population to
-that temperature." \\
+155 & We have now added a sentence at the beginning of the section (lines 153 -
+154) that reads ``described by a set of probabilities.  Stochastic
+probabilities are affected by the suitability of habitat, temperature in a cell
+and the thermal tolerance of a population to that temperature." \\
 \\
@@
 Line 187, make tenses consistent (e.g. determined vs. determines) - also this
-sentence is a little awkward to read. & We have changed so that it reads in the
-past tense and rewritten the paragraph to improve readability. \\
+sentence is a little awkward to read. & We have changed lines 208 - 218
+so that it reads in the past tense and rewritten the paragraph to improve
+readability. \\
 \\
 \hline
+\\
 \textbf{Results} &  \\
 \\
-Line 376: What does "Visualized using Gerritsen (2014)" mean? & \\
+Line 376: What does ``Visualized using Gerritsen (2014)" mean? & We've now
+added to the caption of Current Figure 3: ``The figure shows catch composition
+at each spatial unit represented by a square pie chart of the four populations.
+The area of each colour is proportional to the weight of each population caught
+in that unit. Figure produced with the R package `mapplots' (Gerritsen et al
+2014)." \\ 
 \\
 Line 397: Are these the same figures in Table 7? If so, just refer to the table
-and summarize & \\
+and summarize & Yes, they are the same and we agree this change improves
+readability and the two final paragraphs in section 4.2 (lines 424 - 432) have
+been revised accordingly. \\ 
 \\
-Line 400: move \% sign & This has been corrected. [Note, may be redundant if
-change text] \\
+Line 400: move \% sign & This paragraph has been revised so the point
+	is redundant. \\
 \\
-Line 406: "(in red)" - leave reference to color for figure legend & Removed
-reference to color. \\
+Line 406: ``(in red)" - leave reference to color for figure legend & Removed
+reference to color on line 435. \\
 \\
-Line 410: "Again" doesn't need to be there, same in line 413 & Agree, it has
-been removed. \\
+Line 410: ``Again" doesn't need to be there, same in line 413 & Agree, it has
+been removed on line 430. \\
 \\
-Line 416: This section is a little confusing and needs to be refined/streamlined. & \\
+Line 416: This section is a little confusing and needs to be
+refined/streamlined. & We have now revised this section to clarify and improve
+readability. For example, shortening sentences and ensuring one point is made
+per sentence (lines 443 - 455). \\
 \\
 Line 418: This paragraph should be in methods. But you did it for all
-populations, right? Not just population 3? & \\
+populations, right? Not just population 3? & That's correct, the closures
+affected all populations but the closures were targeted to reduce fishing
+mortality on population 3. We have clarified and moved to the methods section
+now at lines 378 - 386.
+\\
 \\
 \hline
+\\
 \textbf{Discussion / Conclusion} &  \\
@@
 The discussion and conclusion overlap a bit; I felt I was reading similar
-things over again; perhaps these can be streamlined? & \\
+things over again; perhaps these can be streamlined? & We have reviewed but
+believe each paragraph makes an independent point except the final paragraph,
+which does repeat some of the previous conclusions. As such, we have removed
+the final paragraph of the conclusions. \\
 \\
-Line 560: change "reduced" to "reduce" & Thank you, corrected. \\
+Line 560: change ``reduced" to ``reduce" & Done on line 581. \\
 \\
-Line 663: change "hypothesis" to "hypotheses" & Done. \\
+Line 663: change ``hypothesis" to ``hypotheses" & This paragraph has now been
+removed at the suggestion of reviewer 2. \\
 \\
 \hline
+\\
 \textbf{Figures} &  \\
@@
 Figure 1: nicely summarizes the model. It took me a little bit to figure out
-that "Rec" referred to recruitment - even though it was in the legend (I missed
-it when I read it the first time)… is it possible to choose an abbreviation
-that makes it more obvious, maybe something like "Recruit" or  even "Recr"? It
-also occurs to me that there is an opportunity to introduce the terminology
-from your R package here to make it very clear to the people using your code
-how the functions work together… this is only an idea though… or maybe a
-similar figure could be included with the vignette. & \\
+that ``Rec" referred to recruitment - even though it was in the legend (I
+missed it when I read it the first time)… is it possible to choose an
+abbreviation that makes it more obvious, maybe something like ``Recruit" or
+even ``Recr"? It also occurs to me that there is an opportunity to introduce
+the terminology from your R package here to make it very clear to the people
+using your code how the functions work together… this is only an idea though…
+or maybe a similar figure could be included with the vignette. & We have
+changed to `Recr' to make clearer. Rather than change the schematic, we have
+included a short example vignette demonstrating the use of the code to increase
+accessibility and further uptake. \\
 \\
@@
 hard to imagine that one would assume only the presence of specific population
-in the cell? Or do I have the wrong idea about what the plot is showing? & \\
+in the cell? Or do I have the wrong idea about what the plot is showing? & Each
+cell has the four colours in proportion of the weight of each population caught
+(as a square pie chart) - we've clarified this in the figure caption. \\
+\\
+Figure 6: Add what the different colors mean to the legend & This is already
+included as the legend shows which population is represented by which colour. \\
 \\
@@
 That needs to be added to the legend. Also there should be a red box on the top
-plot too. & \\
-\\
-Figure 10: I really like this plot! Very effective. & \\
+plot too. & The top two panels show the spatial distribution of the fishing
+effort before (a) and after (b) the spatial closures, while the bottom (c)
+shows the suitable habitat for the population. We've clarified in the figure
+caption. \\ 
 \bottomrule
@@
 
-Thank etc..
+We thank the reviewer for their comments and suggestions that have greatly
+improved the presentation and interpretation of our methods and results.
 
@@
 
-\large
-
-	\begin{longtable}{p{12cm} | p{12cm}}
+	\begin{longtable}{p{8cm} | p{8cm}}
 %	\caption{Highly resolved spatiotemporal simulations for exploring mixed
@@
 		 quota species) when available quota species is caught, and it
-		 suggested me that populations of different species is modeled
+		 suggested me that populations of different species is modelled
 		 at the same time. However, they  did not describe how many
@@
 		 were simulated in the same simulation. Please, clarify this in
-		 the MM.  &  \\
+		 the MM.  & We now emphasise on line 100 that the framework
+		 allows the user to define as many species as required. There
+		 will be some computational/memory cap but we see no reasons
+		 why you could not include 10s or more. We chose four to keep
+		 the analysis more tractable. All the populations are part of
+		 the same system, irrespective of the number of species
+		 included, hence they are simulated in the same simulation.\\
 \\
@@
 should be greater. I would also send the figure 2, 3 and 9 as supplementary
-data.  & \\
+data.  & We have revised the main figures to increase text size and changed to
+bold font; we have also moved figures 2 and 3 to the supplementary figures. We
+have retained figure 9 (Current Figure 7) as we believe it gives understanding
+to the fishery - population interactions before and after the spatial closures
+which is important for the narrative of the example application. \\
 \\
@@
 Figure S2, what the light gray spots are? Habitat preference? Are the squares
-the spawning areas? In the figure S3, are each square a week?  & \\
+the spawning areas? In the figure S3, are each square a week?  & We have
+revised the captions for the supplementary figures to provide additional
+information, including the issues you've identified. Specifically, Figure S2
+(Current Figure S3): ``with the darker colour showing greater habitat
+suitability". Figure S3 (Current Figure S7): the caption reads ``for 52 separate
+weeks"
+
 \\
@@
 several commas along the text that make the sentences too long and hard to
-understand. I suggest a revision of this.  & \\
+understand. I suggest a revision of this.  & We have revised the text to ensure
+readability. \\
 
 \hline
-
+\\
 \textbf{Small issues} &  \\
@@
 Line 14 - 18: This phrase is too long and hard to understand. Please, rephrase
-this in shorter sentences to clarify this idea. & \\
+this in shorter sentences to clarify this idea. & These sentences have been
+revised to clarify in lines 14 - 21.  \\
 \\
-Lines 20 - 43: These two paragraphs seem redundant.  & \\
+Lines 20 - 43: These two paragraphs seem redundant. & We believe these
+paragraphs set the context for an important premise of the paper: That
+identifying the correct spatial scale for management is important to achieve
+the anticipated outcomes; particularly in mixed fisheries where there is a
+`cost' through loss of fishing opportunities for other fisheries which
+management seeks to minimise. However, we have revised at lines 23 - 34 to make
+our point clearer to the reader. \\
 \\
@@
 if fisheries data are the real community structure. I suggest adding one or two
-phrases to explain how the model could help in this. & \\
+phrases to explain how the model could help in this. & We explain that as our
+community structure is simulated and therefore known, by comparing our inferred
+community structure from commercial catches with our known true structure we
+can understand how biases introduced by using commercial fishing as a sample
+affects our understanding. These points are covered on lines 79 - 83.\\
 \\
@@
 Recruitment dynamics. The recruitment dynamics probably follow the population
-dynamic, but it would be interesting present this explicitly. & \\
+dynamic, but it would be interesting present this explicitly. & Recruitment
+occurs along with other population dynamics, but only during defined periods
+for each population. We've clarified by saying in lines 100 - 102 ``Population
+dynamics for any number of species, as chosen by the user, operate on a daily
+time-step \textit{(with recruitment occurring only during defined seasons for
+	each population),} while.."
+\\
 \\
 Line 282: How these population parameters were selected? Randomly? Using real
-data? Or the authors only created them? & \\
+data? Or the authors only created them? & The demographic parameters were
+chosen by the authors to broadly reflect population dynamics for a four-species
+assemblage representing species typically found in a demersal fishery. We have
+clarified by including in lines 310 - 313 the sentence: ``The population
+demographics were chosen to broadly represent three mobile low-medium value
+groundfish species and one high value species with low mobility, with the
+dynamics hypothetical but as you might expect to find in a typical demersal
+fishery." \\
 \\ 
 Line 426: What does adapted means in this context? Exploring new opened areas?
-& \\
+& Yes, we have clarified in the text on lines 446 - 447 that the
+fisheries ``adapted" to the closures textit{by fishing new areas of high
+	abundance to fish}\\
 \\
 Line 613: Do not use parenthesis inside of other parenthesis. & We have changed
-to ", e.g." from "( e.g." to eliminate one set of parenthesis. \\
+on lines 632 from ``( e.g." to ``, e.g." to eliminate one set of parentheses.
+\\
 \\
 Table 2 and table 3 are not cited in the text Citation of the supplementary
-figures are out of order & \\
+figures are out of order & This is now corrected with references inserted for
+Table 2 (line 204) and Table 3 (line 274) and the supplementary figures
+reordered. \\
 \\
-Figure 3: Individual years ARE the light grey lines    & Thanks! Corrected. \\
+Figure 3: Individual years ARE the light grey lines    & Corrected. \\
 \\
 Figure 4. What do the purple spots represent? Describe these spots in the
-capture Figure 7. Add what " res"  means in the caption.  & \\
+capture & This has been clarified (in Current Figure 2) to be the revenue at
+each location (darker areas indicate higher revenue). \\ 
 \\
-Figure 8. What F means? & \\
+Figure 7. Add what ``res"  means in the caption.  & Have clarified in the
+legend text that it means ``resolution" \\
+\\
+Figure 8. What F means? & Changed to read ``Fishing mortality" \\
 \\
@@
 
-\end{landscape}
-
 \end{document}

### 2020-01-31 write_up/mixfishsim_ecolmod_revisions_clean.tex
Revised manuscript

--- 2020-01-26 write_up/mixfishsim_ecolmod_revisions.tex
@@
-\documentclass[review]{elsarticle}
+\documentclass[preprint]{elsarticle}
 
@@
 
-\usepackage[final]{changes}
+%%\usepackage[final]{changes}
 
@@
 \bibliographystyle{model2-names.bst}\biboptions{authoryear}
+
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 \author[1]{Cóilín Minto}
+\ead{coilin.minto@gmit.ie}
 \author[3]{Jean-Marc Guarini}
+\ead{jean-marc.guarini@upmc.fr}
 \author[4,5]{Jan Jaap Poos}
-
-\address[1]{Marine and Freshwater Research Centre, Galway-Mayo Institute of Technology (GMIT), Dublin Road, Galway,
-	Ireland} 
+\ead{janjaap.poos@wur.nl}
+
+\address[1]{Marine and Freshwater Research Centre, Galway-Mayo Institute of
+	Technology (GMIT), Dublin Road, Galway, Ireland} 
 \address[2]{Centre for Environment, Fisheries and Aquaculture Science (Cefas),
@@
 population dynamics, ii) population movement using Gaussian Random Fields to
-simulate patchy, heterogeneously distributed \added{and moving fish}
-populations, and iii) fishery dynamics for multiple fleet characteristics based
-on population targeting under an explore-exploit strategy.\deleted{ This is
-	implemented via a mix of correlated random walk movement (for
-	exploration) and learned behaviour (for exploitation) phases of the
-	fisheries. }\\ 
+simulate patchy, heterogeneously distributed and moving fish populations, and
+iii) fishery dynamics for multiple fleet characteristics based on population
+targeting under an explore-exploit strategy. \\
+
 %%
-\deleted{Fifty years of sub-daily fishing activity was simulated and used to
-	draw inference on the underlying community structures. W}\added{We
-	applied \emph{MixFishSim} to\deleted{draw}}\deleted{compared}
-infer\deleted{ence}\deleted{s} \added{\deleted{on}community structure}
-\added{when using data generated from:} \deleted{based on}commercial catch,
-a\deleted{simulated} fixed-site sampling survey design and the true
-\added{(simulated)} underlying populations.  \deleted{W}\deleted{\added{In
-		doing so w}}\added{W}e \added{thereby} \deleted{i)}establish
-the potential limitations of fishery-dependent data in providing a robust
-\replaced{characterisation}{picture} of spatiotemporal distributions.\deleted{;
-	and then ii) simulated an area closure based on areas defined from the
-	different data sources at a range of temporal and spatial
-	resolutions.}\deleted{Our framework allows users to explore the
-	assumptions in modelling observational data and evaluate the underlying
-	dynamics of such approaches at a fine spatial and temporal scale. In
-	application to a mixed fishery exploiting four different populations w}
-\deleted{\added{W}e found d}\added{D}ifferent spatial patterns were evident and
-\deleted{that }the effectiveness of the spatial closure reduced when data were
-aggregated across larger spatial areas. \deleted{; and then
-	ii)}\deleted{\added{We then simulated an area closure based on areas
-		defined from the different data sources at a range of temporal
-		and spatial resolutions.}} \added{A simulated area
-	closure showed that} \replaced{a}{A}ggregation across time periods has
-less of a negative impact on the closure success than \added{aggregation} over
-space. \deleted{ and w}\added{W}hile not as effective as when based on on the
-true population, closures based on high catch rates observed in commercial data
-were still able to reduce fishing on a protected species. \\
-
-\added{Our framework allows users to explore the assumptions in modelling
-	observational data and evaluate the underlying dynamics of such
-	approaches at a fine spatial and temporal resolutions. From our
-	application w}\deleted{W}e conclude that commercial data, while
-containing bias, provide a useful tool for managing catches in mixed fisheries
-if applied at the correct spatiotemporal scale. \\
+We applied \emph{MixFishSim} to infer community structure when using data
+generated from: commercial catch, a fixed-site sampling survey design and the
+true (simulated) underlying populations. In doing so we thereby establish the
+potential limitations of fishery-dependent data in providing a robust
+characterisation of spatiotemporal distributions. Different spatial patterns
+were evident and the effectiveness of the spatial closure reduced when data
+were aggregated across larger spatial areas. A simulated area closure showed
+that aggregation across time periods has less of a negative impact on the
+closure success than aggregation over space. While not as effective as when
+based on on the true population, closures based on high catch rates observed in
+commercial data were still able to reduce fishing on a protected species. \\
+
+Our framework allows users to explore the assumptions in modelling
+observational data and evaluate the underlying dynamics of such approaches at a
+fine spatial and temporal resolutions. From our application we conclude that
+commercial data, while containing bias, provide a useful tool for managing
+catches in mixed fisheries if applied at the correct spatiotemporal scale. \\
 %%
@@
 Fishers exploit a variety of fish populations that are heterogeneously
-distributed in space and time with varying knowledge of species distributions.
-As fishers do not have full control over what species they select when fishing
-in `mixed fisheries' it can result in catch of low quota or protected species.
-If over-quota catch of a species for which they have no quota is discarded
-without being accounted for it limits our ability to control fishing mortality
+distributed in space and time. Fishers generally only have partial knowledge of
+species distributions and so limited control over what species they select when
+fishing in `mixed fisheries'. This results in catches of vulnerable species and
+species with low-quota. These species may be thrown overboard in a process
+called discarding and discarding catches that are not recorded leads to biased
+perception of the effects of fisheries on ecosystems. Ultimately the
+unaccounted discards limit our ability to control fishing mortality
 \citep{Alverson1994, Crowder1998, Rijnsdorp2007} and the ability to manage
-fisheries for the biological and economic sustainability \citep{Ulrich2011a,
+biological and economic sustainability of fisheries \citep{Ulrich2011a,
 	Batsleer2015}.\\
 
-There is increasing interest in technical solutions such as gear and spatial
-closures as measures to reduce unwanted catch\added{ which is often discarded}
-\citep{Kennelly2002, Catchpole2008, Bellido2011, Cosgrove2019}\added{.
-	A}\deleted{ and a}daptive spatial management strategies have been
-proposed as a way of reducing over-quota discards \citep{Holmes2011,
-	Little2014, Dunn2014a}. However, if fisheries are to reduce unwanted
-catch through spatial avoidance, an in-depth understanding of spatiotemporal
-fishery dynamics is required. \\
-
-Understanding the correct scale for spatial management measures to be effective
-is crucial as it enables implementation of effective solutions which minimise
-economic impact \citep{Dunn2016}. For example, the problem can be to identify a
-scale that promotes species avoidance for vulnerable or low quota species while
-allowing continuance of sustainable fisheries for available quota species.
-Identifying the correct spatial scale remains a challenge because data on fish
-location at high temporal and spatial resolutions is expensive and difficult to
-collect and proxies are usually inferred from scientific surveys or commercial
-catches with limited spatial and temporal resolution. Thus, implementation of
-spatial measures is hampered by a lack of knowledge of fish and fishery
-spatiotemporal dynamics and understanding of the scale at which these processes
-become important for management. \\ \\
-
-Identifying appropriate spatial scales for fisheries closures \deleted{has been a
-highlighted a}\added{i}s crucial to their success \citep{Costello2010, Dunn2016}.
-Inference on fisheries spatial dynamics is hampered where spatial information
-is coarse due to low resolution reporting of fisheries catch which is
-aggregated across larger gridded areas \citep{Branch2005}. Further, if data
-does not allow identification of spatial features it may lead to poorly sited
-closures \replaced{that}{which} are ineffectual or have unintended consequences. For example,
-increased benthic impact on previously unexploited areas from the cod closure
-in the North Sea were observed without the intended effect of reducing cod
-exploitation \citep{Rijnsdorp2001,Dinmore2003}).\\
-
-More refined spatiotemporal information has since become available through the
-combination of logbook and Vessel Monitoring System (VMS) data \citep{Lee2010,
-	Bastardie2010, Gerritsen2012, Mateo2016} and more real-time spatial
-management has been possible \citep[e.g.][]{Holmes2011}.  However, fishers
+There is increasing interest in technical solutions such as gear adaptations
+and spatial closures as measures to reduce discarding of unwanted catches
+\citep{Kennelly2002, Catchpole2008, Bellido2011, Cosgrove2019}. Adaptive
+spatial management strategies have been proposed as a way of reducing
+over-quota discards \citep{Holmes2011, Little2014, Dunn2014a}. However, to
+reduce unwanted catch through spatial measures requires an in-depth
+understanding of the spatiotemporal dynamics of the fishery. \\
+
+Effective spatial management requires implementation at appropriate spatial
+scales. These spatial scales shape the trade-offs between protection of
+populations and economic impacts on fisheries \citep{Dunn2016}. In mixed
+fisheries, the problem is to identify a scale that promotes species avoidance
+for vulnerable or low-quota species while allowing continuance of sustainable
+fisheries for available quota species. Identifying the appropriate spatial
+scale remains challenging because collecting data on fish distribution at high
+temporal and spatial resolutions is expensive and difficult. Proxies for the
+spatial distributions are usually inferred from fisheries-dependent data or
+from fisheries-independent data. Fisheries-dependent data includes all data on
+catch and effort from commercial fishing operations while fisheries-independent
+data includes data collected on board scientific research vessels. \\
+
+Inferences on fish distributions are hampered where spatial and temporal
+information is coarse. Sampling designs for scientific research vessel surveys
+generally aim for unbiased estimates of local abundance. However, high costs of
+these surveys generally results in restrictions in terms the number of samples.
+As a result, sampling is usually restricted to a few weeks a year, and sampling
+stations are usually coarsely spaced. Moreover, the gear chosen for the survey
+determines the selectivity for certain species and size classes within fish
+communities. This selectivity determines the usefulness of relative occurrence
+in survey catches as proxies for abundances in the fish communities. \\
+
+Proxies for spatial distribution derived from commercial fisheries in theory
+allow for much larger sample sizes. These commercial fisheries are often at sea
+throughout the year, making may fishing hauls. However, spatial information
+from fisheries is often limited because data on catch and effort is collected
+or aggregated across larger gridded areas \citep{Branch2005}. If spatially
+aggregated data does not allow identification of spatial features it may lead
+to poorly designed spatial management measures that are ineffectual or have
+unintended consequences \citep{Costello2010, Dunn2016}. For example, increased
+benthic impact on previously unexploited  areas from the cod closure in the
+North Sea were observed without the intended effect of reducing cod
+exploitation \citep{Rijnsdorp2001,Dinmore2003}. \\
+
+Even where high-resolution spatiotemporal information is available \citep[see
+e.g.][]{Lee2010, Bastardie2010, Gerritsen2012, Mateo2016} commercial catch per
+unit of effort may still be biased because of fisheries dynamics. Fishers
 establish favoured fishing grounds through an explore-exploit strategy
 \citep{Rijnsdorp2011, Bailey2018} where they search for areas with high catches
-and then use experience to return to areas where they have experienced high catch
-in the past. This leads to an inherently biased sampling where target species
-are over-represented in the catch as fishers exploit areas of high abundance.
-There is a need to understand the influence of these biases on any spatial
-management measures which are implemented based on inference from commercial
-landings or catch data. \\
+and then use experience to return to areas where they have experienced high
+catch in the past. This leads to inherently biased sampling where target
+species are over-represented in the catch because fishers exploit areas of high
+abundance. For effective adaptive spatial management the effects of
+spatiotemporal aggregation in data and fishery targeting need to be understood.
+\\
 
@@
 \begin{enumerate}
-	\item Do different source\added{s} of sampling-derived fisheries data
-		reflect\deleted{s} the underlying community structure? 	
-	\item How do\deleted{es} data aggregation and data source impact on the success
-		of spatial fisheries management measures?
+	\item Do different sources of sampling-derived fisheries data reflect
+		the underlying community structure? 	
+	\item How do data aggregation and data source impact on the success of
+		spatial fisheries management measures?
 \end{enumerate}
@@
 efficient computation by allowing for sub-modules implemented on time-scales
-appropriate to capture \deleted{the }characteristic\added{s} of the different processes (Figure
-1). \replaced{S}{The following s}ub-modules \deleted{were included }to capture the full system \added{comprised}: 1)
-\replaced{p}{P}opulation dynamics, 2) \replaced{r}{R}ecruitment dynamics, 3) \replaced{p}{P}opulation movement, 4)
-fishery dynamics.\\
-
-Population dynamics \added{for any number of species, as chosen by the user,}
-operate on a daily time-step \added{(with recruitment occurring only during
-	defined seasons for each population)}, while population movement occurs
-on a weekly time-step, with the fishing module operating on a tow-by-tow basis
-(i.e.\added{,} multiple events a day). \\
+appropriate to capture the characteristics of the different processes (Figure
+\ref{fig:model}). Sub-modules to capture the full system comprised: 1) population
+dynamics, 2) recruitment dynamics, 3) population movement, 4) fishery
+dynamics.\\
+
+Population dynamics for any number of species, as chosen by the user, operate
+on a daily time-step (with recruitment occurring only during defined seasons
+for each population), while population movement occurs on a weekly time-step,
+with the fishing module operating on a tow-by-tow basis (i.e., multiple events
+a day). \\
 
@@
 The basic population level processes were simulated using a modified two-stage
-Deriso-Schnute delay difference model \replaced{that}{which} models the fish populations in
-terms of aggregate biomass of recruits and mature components rather than
-keeping track of individuals \citep{Deriso1980, Schnute1985, Dichmont2003}. A
-daily time-step was chosen to discretise continuous population processes on a
+Deriso-Schnute delay difference model that models the fish populations in terms
+of aggregate biomass of recruits and mature components rather than keeping
+track of individuals \citep{Deriso1980, Schnute1985, Dichmont2003}. A daily
+time-step was chosen to discretise continuous population processes on a
 biologically relevant and computationally tractable timescale. Population
@@
 population size. Biomass for each cell $c$ was incremented each day $d$ as
-follows (\replaced{see}{the full parameter list is detailed in } Table \ref{tab: pop_variable} \added{for all parameter details}): 
+follows (see Table \ref{tab: pop_variable} for all parameter details): 
 \begin{equation}
@@
 \end{equation}
-where $\rho$ is Brody's coefficient\textcolor{blue}{(Check)}, shown to be equal
-to $\mathrm{e}^{-K}$ when $K$ is the \deleted{growth }rate \added{at which the
-	asymptote is approached} from a von Bertalanffy \deleted{logistic
-}growth model \citep{Schnute1985}. $W_{R-1}$ is the average weight of fish
-prior to recruitment, while $W_{R}$ is the average recruited weight.
-$\alpha_{d}$ represents the proportion of fish recruited during that day for
-the year, while $R_{c,\tilde{y}(c)}$ is the annual recruits in year $y$ for
-cell $c$. \\
+where $\rho$ is Ford's growth coefficient shown to be equal to
+$\mathrm{e}^{-K}$ when $K$ is the Brody growth coefficient, the rate at which
+the asymptote is approached from a von Bertalanffy growth model
+\citep{Schnute1985}. $W_{R-1}$ is the average weight of fish prior to
+recruitment, while $W_{R}$ is the average recruited weight. $\alpha_{d}$
+represents the proportion of fish recruited during that day for the year, while
+$R_{c,\tilde{y}(c)}$ is the annual recruits in year $y$ for cell $c$. \\
 
@@
 	\begin{split}
-	\bar{R}_{c,d} = & \frac{(\alpha \deleted{\cdot} S_{c,d})}{(\beta + S_{c,d})} \\
-	     \added{\ln(}R_{c,d}\added{)} \sim & \deleted{\log} N[(\replaced{\ln}{\log}(\bar{R}_{c,d}),\sigma^2)]
+	\bar{R}_{c,d} = & \frac{(\alpha S_{c,d})}{(\beta + S_{c,d})} \\
+	     \ln(R_{c,d}) \sim & N[(\ln(\bar{R}_{c,d}),\sigma^2)]
 	\end{split}
@@
 movement between adjacent cells is described by a set of probabilities.
-\added{Stochastic probabilities are affected by the suitability of habitat,
+Stochastic probabilities are affected by the suitability of habitat,
 temperature in a cell and the thermal tolerance of a population to that
-	temperature}.\\
-
-\added{The combined process results in a population structure and movement
-	pattern unique to each population, with population movement occurring
-	on a weekly basis. \replaced{M}{The decision to m}odel\added{ing}
-	population movement on a weekly timescale\deleted{ was to}
-	reflect\added{s} that fish tend to aggregate in
-	species\added{-}specific locations\deleted{ that have been} observed to
-	last \replaced{between}{around } one \replaced{and}{to} two weeks
-	\citep{Poos2007}. Therefore this process approximated the demographic
-	shifts in fish populations throughout a year with seasonal spawning
-	patterns }(Figure \ref{S-fig:5}).
+temperature.\\
+
+The combined process results in a population structure and movement pattern
+unique to each population, with population movement occurring on a weekly
+basis. Modelling population movement on a weekly timescale reflects that fish
+tend to aggregate in species-specific locations that have been observed to last
+between one and two weeks \citep{Poos2007}. Therefore this process approximated
+the demographic shifts in fish populations throughout a year with seasonal
+spawning patterns (Figure \ref{S-fig:5}). \\
 
@@
 \in \mathbb{R}^2\}$, where for any set of cells $c_{1}, \dots, c_{n}$, the
-joint distribution of $S = \{S(c1),\dots S(c_{n})\}$ is multivariate Gaussian
-with a \textit{Matérn} covariance structure, where the correlation strength
-weakens with distance controlled by two parameters, with $\nu$ a scale
+joint distribution of $S = \{S(c_{1}),\dots S(c_{n})\}$ is multivariate
+Gaussian with a \textit{Matérn} covariance structure, where the correlation
+strength weakens with distance controlled by two parameters, with $\nu$ a scale
 parameter in the units of distance and $\kappa$ a shape parameter which
-determines the smoothness of the process. \added{We use the most commonly used
-	Matérn covariance structure as it is a flexible form that \replaced{contains the}{under certain
-	conditions is of the same form as an} exponential \added{and double exponential as special cases}\deleted{ function} and
-	it}\deleted{This} enables us to model the spatial autocorrelation
-observed in animal populations where density is more similar in nearby
-locations\deleted{, \added{but that correlation decreases non-linearly}}
-\citep{Tobler1970, F.Dormann2007, Poos2007}. We change the parameters to
-implement different spatial structures for the different populations using the
-\textit{RandomFields} R package \citep{Schlater2015}. We define a stationary
-habitat field with an anisotropic pattern (to simulate a depth gradient) and
-combine it with a temporally dynamic thermal tolerance field to imitate two key
-drivers of population dynamics without modelling the processes explicitly. Each
-population was initialised at a single location, and subsequently moved across
-the entire space according to a probabilistic distribution based on habitat
-suitability (represented by the normalised values from the GRFs), temperature
-tolerance and distance from current cell: 
+determines the smoothness of the process. We use the most commonly used Matérn
+covariance structure as it is a flexible form that contains the exponential and
+double exponential as special cases and it enables us to model the spatial
+autocorrelation observed in animal populations where density is more similar in
+nearby locations \citep{Tobler1970, F.Dormann2007, Poos2007}. \\
+
+We change the parameters to implement different spatial structures for the
+different populations using the \textit{RandomFields} R package
+\citep{Schlater2015}. We define a stationary habitat field with an anisotropic
+pattern (to simulate a depth gradient) and combine it with a temporally dynamic
+thermal tolerance field to imitate two key drivers of population dynamics
+without modelling the processes explicitly. Each population was initialised at
+a single location, and subsequently moved across the entire space according to
+a probabilistic distribution based on habitat suitability (represented by the
+normalised values from the GRFs), temperature tolerance and distance from
+current cell: 
 \begin{equation}
@@
 
-A time-varying temperature covariate changes the \deleted{interaction between time and}
+A time-varying temperature covariate changes the interaction between time and
 suitable habitat on a weekly time-step. Each population $p$ was assigned a
-thermal tolerance with mean, $\mu_{p}$ and standard deviation, $\sigma_{p}$ so that
-each cell and population temperature tolerance is defined \replaced{as}{that}:
+thermal tolerance with mean, $\mu_{p}$ and standard deviation, $\sigma_{p}$ so
+that each cell and population temperature tolerance is defined as:
 \begin{equation}
@@
 and $\sigma_{p}$ the mean and standard deviation of the population temperature
-tolerance \replaced{(see Table \ref{tab:pop_move} for variable descriptions).}{. The variables, their meaning and units for population movement is
-provided in Table \ref{tab:pop_move}}. \\
-
-\deleted{The final combined process results in a population structure and movement
-pattern unique to each population, with population movement occurring on a weekly
-basis. The decision to model population movement on a weekly timescale was to
-reflect that fish tend to aggregate in species specific locations that have
-been observed to last around one to two weeks (Poos et al 2007). Therefore this
-process approximated the demographic shifts in fish populations throughout a
-year with seasonal spawning patterns (Figure \ref{S-fig:5}).}
+tolerance (see Table \ref{tab:pop_move} for variable descriptions). \\
 
@@
 
-Fleet dynamics \replaced{were}{can be }broadly categorised into three
-components. \textit{Fleet targeting} \replaced{determined}{determines} the
-fleet catch efficiency and preference towards a particular population;
-\textit{trip-level decisions} \replaced{determined}{that determines} the
-initial location to be fished at the beginning of a trip; and
-\textit{within-trip decisions} \replaced{determined fishing locations}{, that
-	determines movement from one fishing spot to another} within a trip.
-\replaced{This results in an explore-exploit strategy}{ was implemented in the
-	model that combined these three components} for individual vessels to
-maximise their catch from an unknown resource distribution \citep{Bailey2018}.
-The decision to use an individual based model for fishing vessels was taken
-because fishers are heterogeneous in their location choice behaviour due to
-different objectives, risk preference and targeting preference
-\citep{VanPutten2012a, Boonstra2015}.  Therefore fleet dynamics are emergent
-from individual dynamics rather than pre-defined group dynamics.
+Fleet dynamics were broadly categorised into three components. \textit{Fleet
+	targeting} determined the fleet catch efficiency and preference towards
+a particular population; \textit{trip-level decisions} determined the initial
+location to be fished at the beginning of a trip; and \textit{within-trip
+	decisions} determined fishing locations within a trip. This results in
+an explore-exploit strategy for individual vessels to maximise their catch from
+an unknown resource distribution \citep{Bailey2018}. The decision to use an
+individual based model for fishing vessels was taken because fishers are
+heterogeneous in their location choice behaviour due to different objectives,
+risk preference and targeting preference \citep{VanPutten2012a, Boonstra2015}.
+Therefore fleet dynamics are emergent from individual dynamics rather than
+pre-defined group dynamics.
 
@@
 
-Several studies \citep[for a review see][]{Girardin2016} have confirmed past activity
-and past catch rates are strong predictors of fishing location choice. For this
-reason, the fleet dynamics sub-model included a learning component, where a
-vessel's initial fishing location in a trip was based on selecting from
+Several studies \citep[for a review see][]{Girardin2016} have confirmed past
+activity and past catch rates are strong predictors of fishing location choice.
+For this reason, the fleet dynamics sub-model included a learning component,
+where a vessel's initial fishing location in a trip was based on selecting from
 previously successful fishing locations. This was achieved by calculating an
@@
 retains some degree of stochasticity, that can be controlled separately, but is
-determined by the relationship: (\textcolor{blue}{[CM: use $\ln$ where we use the natural logarithm.
-Double-check this equation is right as per the code.
-As it looks different here: \url{https://github.com/pdolder/MixFishSim/blob/master/R/step_length.R]}.
-There it looks to simplify to $b_2(b_1/b_2)^{Rev/b_3}$, assuming parameters are positive.})
+determined by the relationship: 
 \begin{equation}
-	Le = \mathrm{e}^{log(\beta_{1}) + log(\beta_{2}) -
-		\left(log\left(\frac{\beta_{1}}{\beta_{3}}\right)\right) \cdot Rev
+	Le = \mathrm{e}^{\textrm{ln}(\beta_{1}) + \textrm{ln}(\beta_{2}) -
+		\left(\textrm{ln}\left(\frac{\beta_{1}}{\beta_{3}}\right)\right) \cdot Rev
 } 
@@
 moving towards these areas in pre-defined weeks (Figure \ref{S-fig:2}) with
-population-specific movement rates (Table \ref{tab:1}).  \added{The population
+population-specific movement rates (Table \ref{tab:1}). The population
 demographics were chosen to broadly represent three mobile low-medium value
 groundfish species and one high value species with low mobility, with the
-dynamics hypothetical but \deleted{as you} might \added{be} expect\added{ed} \deleted{to find }in a typical demersal
-fishery.}
+dynamics hypothetical but might be expected in a typical demersal fishery.
 
@@
 
-\replaced{F}{The f}leets were calibrated to reflect five different characteristic fisheries
-with unique exploitation dynamics (Table \ref{tab:2}). By setting different
+Fleets were calibrated to reflect five different characteristic fisheries with
+unique exploitation dynamics (Table \ref{tab:2}). By setting different
 catchability coefficients ($Q_{fl, p}$) we create different targeting
-preferences between the fleets and hence \added{different} spatial dynamics.  The learned random
-walk process implies that within a fleet different vessels have different
-spatial distributions based on individual experience. The step function was
-calibrated dynamically within the simulations as the maximum revenue
-obtainable was not known beforehand. This was implemented so that vessels take
-smaller steps when fishing at a location that yields landings value in the top
-90th percentile of the value experienced in that year so far (as defined per
-fleet in Table \ref{tab:2}). \\
+preferences between the fleets and hence different spatial dynamics. The
+learned random walk process implies that within a fleet different vessels have
+different spatial distributions based on individual experience. The step
+function was calibrated dynamically within the simulations as the maximum
+revenue obtainable was not known beforehand. This was implemented so that
+vessels take smaller steps when fishing at a location that yields landings
+value in the top 90th percentile of the value experienced in that year so far
+(as defined per fleet in Table \ref{tab:2}). \\
 
@@
 the new fishing location. This probability was based on a logistic sigmoid
-function with a lower asymptote of 0 and upper asymptote of 0.95, and a \replaced{slope}{growth
-rate} that ensures the upper asymptote (where decisions are mainly based on past
+function with a lower asymptote of 0 and upper asymptote of 0.95, and a slope
+that ensures the upper asymptote (where decisions are mainly based on past
 knowledge) is reached approximately halfway through the simulation.  \\
@@
 stations fished each year, starting on day 92 and ending on day 112 (5 stations
-per day) with same catchability parameter ($Q_{p} = 1$) for all populations\deleted{ $p$}.
+per day) with same catchability parameter ($Q_{p} = 1$) for all populations.
 This approximates a real world survey design with limited seasonal and spatial
@@
 
-\added{We implemented a series of spatial closures targeted at reducing fishing
-	mortality on population 3, given the different data sources and spatial
-	and temporal resolutions above. We use the effectiveness of these
-	closures in reducing fishing mortality as a way of evaluating the
-	trade-offs in data sources and resolution.} Survey closures were on an
-annual basis only, as this was the most temporally resolved survey data
-available. We evaluated the factors contributing to the success of the closures
-through a regression tree (using the R package REEMtree \citep{Sela2012}) to
-identify the factor most contributing to differences in fishing mortality
-before and after the closure.
+We implemented a series of spatial closures targeted at reducing fishing
+mortality on population 3, given the different data sources and spatial and
+temporal resolutions above. We use the effectiveness of these closures in
+reducing fishing mortality as a way of evaluating the trade-offs in data
+sources and resolution. Survey closures were on an annual basis only, as this
+was the most temporally resolved survey data available. We evaluated the
+factors contributing to the success of the closures through a regression tree
+(using the R package REEMtree \citep{Sela2012}) to identify the factor most
+contributing to differences in fishing mortality before and after the closure.
 
@@
 areas where the highest revenue were experienced, as shown by Figure
-\ref{fig:mv}D, where several vessels tracks are overlaid on the revenue
-field.
+\ref{fig:mv}D, where several vessels tracks are overlaid on the revenue field.
+\\
 
@@
 
-\deleted{The }\deleted{aggregated }\replaced{C}{c}atch composition \added{aggregated at different
-	spatial resolutions} from each of the data sources (\deleted{which
-	shows }average seasonal patterns over a ten-year period) highlights
+Catch composition aggregated at different spatial resolutions from each of the
+data sources (average seasonal patterns over a ten-year period) highlights
 different patterns in perceived community structure depending on the data
@@
 from a lack of fishing activity (particularly in the lower left part of the
-sampling domain). \replaced{S}{The s}urvey data at this spatial resolution displays very
-sparse information about the spatial distributions of the populations. The
-slightly aggregated data on a 5 x 5 grid shows similar patterns and, while
-losing some of the spatial detail, there remains good consistency between the
-true population and the commercial data. Survey data starts to pick out some of
-the similar patterns as the other data sources, but lacks spatiotemporal
-coverage. The spatial catch information on a 10 x 10 and 20 x 20 grid lose a
-significant amount of information about the spatial resolutions for all data
-sources, and some differences between the survey, commercial and true
-population data emerge. \\
+sampling domain). Survey data at this spatial resolution
+displays very sparse information about the spatial distributions of the
+populations. The slightly aggregated data on a 5 x 5 grid shows similar
+patterns and, while losing some of the spatial detail, there remains good
+consistency between the true population and the commercial data. Survey data
+starts to pick out some of the similar patterns as the other data sources, but
+lacks spatiotemporal coverage. The spatial catch information on a 10 x 10 and
+20 x 20 grid lose a significant amount of information about the spatial
+resolutions for all data sources, and some differences between the survey,
+commercial and true population data emerge. \\
 
@@
 
-\replaced{Weekly}{The} commercial data \deleted{on a weekly basis }shows some
-of the same patterns as the true population, though \deleted{the }population 1
-\deleted{(in red)} is less well represented and some weeks are missing catches
+Weekly commercial data shows some of the same patterns as the true population,
+though population 1 is less well represented and some weeks are missing catches
 from the area. Here, weekly and monthly compositions were nearly identical
-(Figure \ref{fig:2}; Table \ref{tab:7}). \deleted{Again, y}\added{Y}early
-values h\deleted{e}ad a similar mean but smaller standard deviation. The survey
-data was only available on an annual basis, and showed again a slightly
-different composition from the true population and the commercial data; in
-particular a greater proportion of population 4 (Figure \ref{fig:2}).
+(Figure \ref{fig:2}; Table \ref{tab:7}). Yearly values had a similar mean but
+smaller standard deviation. The survey data was only available on an annual
+basis, and showed again a slightly different composition from the true
+population and the commercial data; in particular a greater proportion of
+population 4 (Figure \ref{fig:2}).
 
@@
 	management measures?}
-
-\deleted{We implemented a spatial closure using the different data sources and
-	spatial and temporal aggregations as outlined in the protocol in
-	Section 3.4. We used this to assess the efficacy of a closure in
-	reducing fishing mortality on population 3, given availability of data
-	and its use at different resolutions in order to evaluate the
-	trade-offs in data sources. }
 
@@
 the largest reductions in fishing mortality happened immediately after the
-closures, following which the fisheries ``adapted" to the closures \added{by
-	finding new areas of high abundance to fish. This led to} fishing
-mortality increasing again, though not to past levels (Figure \ref{fig:3}).
-The exception to the success was the closures implemented based on the coarsest
-spatial (20 x 20) and temporal resolution (yearly) that was ineffective (i.e.
-failed to reduce fishing mortality) with all data sources. As expected,
-closures based on the ``known" population distribution were most effective,
-with differing degrees of success using the commercial data. Fishing mortality
-rates on the other species changed in different proportions, depending on
-whether the displaced fishing effort moved to areas where the populations were
-found in greater or lesser density. \\
+closures, following which the fisheries ``adapted" to the closures by finding
+new areas of high abundance to fish. This led to fishing mortality increasing
+again, though not to past levels (Figure \ref{fig:3}). The exception to the
+success was the closures implemented based on the coarsest spatial (20 x 20)
+and temporal resolution (yearly) that was ineffective (i.e. failed to reduce
+fishing mortality) with all data sources. As expected, closures based on the
+``known" population distribution were most effective, with differing degrees of
+success using the commercial data. Fishing mortality rates on the other species
+changed in different proportions, depending on whether the displaced fishing
+effort moved to areas where the populations were found in greater or lesser
+density. \\
 
@@
 after the closure was the population (72 \% showing that the closures were
-effective for population 3), followed by \added{spatial} data resolution (21 \%), data type (7
-\%) with the least important factor the timescale ($<$ 1 \%). In general the
-finer the spatial resolution of the data used the greater reduction in fishing
-mortality for population 3 after the closures (Figure \ref{fig:4}). The notable
-outliers are the commercial data at the coarsest spatial resolution (20 x 20)
-at a yearly and weekly timescale, where closures were nearly as effective as
-the fine-scale resolution. In this case the closures were sufficiently large to
-protect a core area of the habitat for the population, but this was achieved in
-a fairly crude manner by closing a large area - including area where the
-species was not found (Figure \ref{fig:17}) that may have consequences in terms
-of restricting the fishery in a much larger area than necessary. We found that
-these trade-offs existed, with high catches maintained with an effective
-closure when the highest resolution data was used, with the effect being linear
-when the true population distribution was known and also persisting for
-closures based on commercial information (Figure \ref{fig:ce}).\\
+effective for population 3), followed by spatial data resolution (21 \%), data
+type (7 \%) with the least important factor the timescale ($<$ 1 \%). In
+general the finer the spatial resolution of the data used the greater reduction
+in fishing mortality for population 3 after the closures (Figure \ref{fig:4}).
+The notable outliers are the commercial data at the coarsest spatial resolution
+(20 x 20) at a yearly and weekly timescale, where closures were nearly as
+effective as the fine-scale resolution. In this case the closures were
+sufficiently large to protect a core area of the habitat for the population,
+but this was achieved in a fairly crude manner by closing a large area -
+including area where the species was not found (Figure \ref{fig:17}) that may
+have consequences in terms of restricting the fishery in a much larger area
+than necessary. We found that these trade-offs existed, with high catches
+maintained with an effective closure when the highest resolution data was used,
+with the effect being linear when the true population distribution was known
+and also persisting for closures based on commercial information (Figure
+\ref{fig:ce}).\\
 
@@
 measures to meet particular management goals \citep{Bailey2018}, our framework
-allows users to explore \deleted{the} assumptions in modelling observational
-data and \added{to} evaluate the underlying dynamics of such approaches at
-\deleted{a} fine spatial and temporal scale\added{s}.  This offers the
-advantage that larger scale fishery patterns are emergent properties of the
-system and results can be compared to those obtained under a statistical
-modelling framework. \\
+allows users to explore assumptions in modelling observational data and to
+evaluate the underlying dynamics of such approaches at fine spatial and
+temporal scales. This offers the advantage that larger scale fishery
+patterns are emergent properties of the system and results can be compared to
+those obtained under a statistical modelling framework. \\
 
@@
 inference from catch data obtained through commercial fishing activity with
-fleets exploiting multiple fish populations\added{. This shows how}\deleted{
-	and} realis\added{ed}\deleted{ing} catch distributions \deleted{that
-}may differ from the underlying populations, as identified by
+fleets exploiting multiple fish populations. This shows how realised catch
+distributions may differ from the underlying populations, as identified by
 \cite{Gillis2008}. As such, we favoured a minimum realistic model of the fish
@@
 spatially limited due to the ``hotspots" of commercially valuable species being
-fished. Similarly, despite \deleted{the }even spatial coverage the survey \deleted{was able to
-}capture\added{d} some of the same spatial patterns as the true population, but missed
-others due to gaps between survey stations limiting spatial and temporal
-coverage (Figure \ref{fig:1}). This provides a challenge when
-modelling unsampled areas in inferring species distribution maps, though these
-limitations may be overcome by understanding the relationship between the
-species and habitat covariates where these are known at unsampled locations
-\citep{Robinson2011}. \\
+fished. Similarly, despite even spatial coverage the survey captured some of
+the same spatial patterns as the true population, but missed others due to gaps
+between survey stations limiting spatial and temporal coverage (Figure
+\ref{fig:1}). This provides a challenge when modelling unsampled areas in
+inferring species distribution maps, though these limitations may be overcome
+by understanding the relationship between the species and habitat covariates
+where these are known at unsampled locations \citep{Robinson2011}. \\
 
@@
 there was greater spatial heterogeneity over the spatial domain than
-experienced in \replaced{given}{individual} locations over the course of the year (Figure
+experienced in given locations over the course of the year (Figure
 \ref{S-fig:9}). \\
@@
 indicates that fixed closures, at the right resolution, when based on
-commercially derived data have the potential to reduce\deleted{d} fishing
-mortality. The likely cost of poor spatial and temporal resolution is
-associated with reduced effectiveness and potentially closing fishing
-opportunities for other fisheries (Figure \ref{fig:ce}). \\
+commercially derived data have the potential to reduce fishing mortality. The
+likely cost of poor spatial and temporal resolution is associated with reduced
+effectiveness and potentially closing fishing opportunities for other fisheries
+(Figure \ref{fig:ce}). \\
 
@@
 and down) as a side-effect of closures to protect one species. This indicates
-the importance \replaced{of}{in} considering fishing effort reallocation following spatial
+the importance of considering fishing effort reallocation following spatial
 closures, and our simulation allows us to consider the spatiotemporal reasons
@@
 We consider that the increased availability of high resolution catch and
-locational information from commercial fisheries will \replaced{make}{require} it \deleted{to be }a key
-source of data for ensuring management is implemented at the right scale in
-future. For example, identifying hot-spots for bycatch reduction or identifying
-spatial overlaps in mixed fisheries \citep{Dolder2018, Gardner2008, Little2014,
+locational information from commercial fisheries will make it a key source of
+data for ensuring management is implemented at the right scale in future. For
+example, identifying hot-spots for bycatch reduction or identifying spatial
+overlaps in mixed fisheries \citep{Dolder2018, Gardner2008, Little2014,
 	Dedman2015, Ward2015}. Our simulation model has the potential to test
 some of the assumptions behind the modelling approaches in identifying such
-hotspots and indeed behind spatiotemporal modelling in general\replaced{, }{
-	(}e.g. comparing GAMs, GLMMs, Random Forests and geostatistical models
-under different data generation processes as exampled by
-\cite{Stock2019}\deleted{)}. \\
+hotspots and indeed behind spatiotemporal modelling in general, e.g. comparing
+GAMs, GLMMs, Random Forests and geostatistical models under different data
+generation processes as exampled by \cite{Stock2019}. \\
 
@@
 importance of capturing in-year dynamics in estimating stock status
-\citep{Liu2013}; at\added{-}sea sampling scheme designs to deliver unbiased estimates
+\citep{Liu2013}; at-sea sampling scheme designs to deliver unbiased estimates
 of population parameters \citep{Cotter2007, Kimura2006}; adaptive management
@@
 main features of the data are captured, yet maintaining enough data coverage
-that the features can be distinguished. We found \deleted{in our application
-}greater spatial than temporal heterogeneity. When using aggregated data to
-define spatial closures coarser temporal resolution (months instead of weeks)
-could still achieve the same results in reducing exploitation rates of a
-vulnerable species at the highest temporal resolution data. Conversely,
-reducing the spatial resolution had a negative effect on the effectiveness of
-the measures \deleted{(}though\added{,} importantly, there was still some
-benefit even with coarse spatial resolution\deleted{)}. \\
-
-While \deleted{any findings are likely to be} case\added{-}specific, our
-findings emphasise the need to understand population demographics, habitat use
-and movement rates in designing any closure scenario based on observational
-sampling. This information can then be used to set the bounds on data
-aggregation used in modelling studies aimed at informing the management
-measures. \\
-
-\deleted{\textit{MixFishSim} has numerous potential additional applications as it
-enables the user to apply methods to a fisheries system where there is detailed
-understanding of underlying spatiotemporal dynamics. This enables
-identification of weaknesses or limitations which would not be possible
-otherwise. In future, we recommend use of the framework to test
-hypothes\replaced{e}{i}s that are otherwise unable to be analysed using real
-world data due to limitations of data collection. That way the knowledge gained
-through simulation can inform the future design of management measures.}
+that the features can be distinguished. We found greater spatial than temporal
+heterogeneity. When using aggregated data to define spatial closures coarser
+temporal resolution (months instead of weeks) could still achieve the same
+results in reducing exploitation rates of a vulnerable species at the highest
+temporal resolution data. Conversely, reducing the spatial resolution had a
+negative effect on the effectiveness of the measures though, importantly, there
+was still some benefit even with coarse spatial resolution. \\
+
+While case-specific, our findings emphasise the need to understand population
+demographics, habitat use and movement rates in designing any closure scenario
+based on observational sampling. This information can then be used to set the
+bounds on data aggregation used in modelling studies aimed at informing the
+management measures. \\
 
@@
 doctoral training program (MARES\_14\_15) and the Centre for Environment,
-Fisheries and Aquaculture Science seedcorn program (DP227AC).\added{ We thank
+Fisheries and Aquaculture Science seedcorn program (DP227AC). We thank
 	two anonymous reviewers for their helpful comments which greatly
-	improved the final manuscript.} The authors declare no competing
+	improved the final manuscript. The authors declare no competing
 interests.
@@
 \begin{figure}[!ht]
-	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_space_Rev2}
-	\caption{[Colour] Data aggregation at different spatial resolutions
-		over a ten year period. \added{The figure shows catch
+	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_space_Rev3}
+	\caption{[Colour online]Data aggregation at different spatial resolutions
+		over a ten year period. The figure shows catch
 			composition at each spatial unit represented by a
@@
 			population caught in that unit. Figure produced using
-			the R package `mapplots' (\cite{Gerritsen2014}.}
+			the R package `mapplots' (\cite{Gerritsen2014}.
 	}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_time_Rev2}
-	\caption{[Colour]Proportion of each population (y axis) for data aggregated at
-		different temporal resolutions. Data is aggregated over a
-		ten-year period for an area 20 x 20. Each bar represents either
-		a week, month or year respectively.}
+	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_time_Rev3}
+	\caption{[Colour online]Proportion of each population (y axis) for data
+		aggregated at different temporal resolutions. Data is
+		aggregated over a ten-year period for an area 20 x 20. Each bar
+		represents either a week, month or year respectively.}
 	\label{fig:2}
@@
 	\includegraphics[width = \linewidth]{../analysis/F_trendsREV}
-	\caption{[Colour]Comparison of closure scenarios effect on fishing mortality
-		trends. Line colour denotes timescale, while linestyle
-		denotes spatial resolution. The vertical dashed line
+	\caption{[Colour online]Comparison of closure scenarios effect on
+		fishing mortality trends. Line colour denotes timescale, while
+		linestyle denotes spatial resolution. The vertical dashed line
 		indicates the onset of the spatial closures.}
@@
 		and (b) after the spatial closure (years in panel), and (c) the
-		suitable habitat for population 3. The site of the closure
-		can be seen in the red box on all three panels.}
+		suitable habitat for population 3. The site of the closure can
+		be seen in the red box on all three panels.}
 	\label{fig:17}
@@
 	\includegraphics[width =\linewidth]{./Plots/Closure_effectiveness_CF}
-	\caption{[Colour]Effectiveness of closure with regards to reducing fishing
-		mortality on protected population (further left on x-axis is
-		best) and maintaining high catches in the fishery (highest on
-		y-axis is best). The numbers indicate the spatial resolution of
-		the data, while grey lines indicate the direction of the
-		trade-off between reducing fishing mortality and overall
-		catches.}
+	\caption{[Colour online]Effectiveness of closure with regards to
+		reducing fishing mortality on protected population (further
+		left on x-axis is best) and maintaining high catches in the
+		fishery (highest on y-axis is best). The numbers indicate the
+		spatial resolution of the data, while grey lines indicate the
+		direction of the trade-off between reducing fishing mortality
+		and overall catches.}
 	\label{fig:ce}

### 2020-01-31 write_up/parameter_tables.tex
Revised manuscript

@@
 		$R_{c, \tilde{y}}$  &Annualy recruited fish in cell &  yr\textsuperscript{-1} \\
-		$\rho$ & Brody's growth coefficient & yr\textsuperscript{-1} \\
+		$\rho$ & Ford's growth coefficient & yr\textsuperscript{-1} \\
 		$Wt_{R}$ & Weight of a fully recruited fish & kg \\
@@
 		$Rev$ & Revenue from fishing tow & \euro \\
+		$RefRev$ & Reference revenue for determining the step function
+		& \euro \\
 		$L_{p}$ & Landings of population $p$ & kg \\
@@
 	\hline
-	step function $\beta_1$ & 1 & 2 & 1 & 2 & 3 \\
-	step function $\beta_2$ & 10 & 15 & 8 & 12 & 7 \\
-	step function $\beta_3$, the landings value $nth$ quantile &
+	$\beta_1$ & 1 & 2 & 1 & 2 & 3 \\
+	$\beta_2$ & 10 & 15 & 8 & 12 & 7 \\
+	$\beta_3$, the landings value $nth$ quantile &
 	90 & 90 & 85 & 90 & 80 \\

### 2020-01-31 analysis/KillerFigure.R

@@ -175,7 +175,7 @@ mn <- 1:12
 
 ## Load the results
 load(file.path('.', 'Scenario_runs_Nov18', paste0('Scenario_', 0, '.RData')))
-load(file.path('.', 'Common_Params.RData'))
+load(file.path('.', 'Scenario_runs_Nov18', 'Common_Params.RData'))
 
 ## Commercial
 dataIn <- get_data(basis = 'commercial', yr = yr, mn = mn, wk = wk, dataIn = res[["fleets_catches"]]) 
@@ -194,9 +194,9 @@ plot_comp(gran = 1, dataIn = dataIn)
 ## Setting out the plot
 ##setEPS()
 ##postscript('Data_Aggregation_space.eps', width = 8 * 2, height = 8 * 3, bg = "white")
-pdf('Data_Aggregation_space_Rev2.pdf', width = 8 * 2, height = 8 * 3, bg = "white")
+pdf('Data_Aggregation_space_Rev3.pdf', width = 8 * 2, height = 8 * 3, bg = "white")
 
-par(oma = c(12,2,12,12), mar = c(0,0,0,0), mfrow = c(4,3))
+par(oma = c(12,6,12,12), mar = c(0,0,0,0), mfrow = c(4,3))
 
 ## real pop 
 dataIn <- get_data(basis = 'real_pop', yr = yr, mn = mn, wk = wk, dataIn = res[["pop_bios"]], sim_init = sim)
@@ -229,6 +229,9 @@ plot_comp(gran = 20, dataIn = dataIn)
 
 mtext(text = "True Population     Commercial Data        Survey Data", side = 3, line = 2, outer = T, font = 2,   cex = 3 ) ## top
 mtext(text = "20 x 20                         10 x 10                           5 x 5                      1 x 1 ", side = 4, line = 2, outer = T, font = 2, cex  = 3) ## right side
+
+mtext(text = "x-distance (0 - 100)", side = 1, line = 2, outer = T, font = 2, cex = 1.5)
+mtext(text = "y-distance (0 - 100)", side = 2, line = 2, outer = T, font = 2, cex = 1.5)
 
 legend(x = -330, y = -10, legend = c("Population 1", "Population 2", "Population 3", "Population 4"),
             fill = c("#E66101", "#FDB863", "#B2ABD2", "#5E3C99"), ncol = 4, xpd = NA, bty = "n", cex = 4)
[…]
